### 2021-09-07 paper/pears.tex
updated abstract and isolation criteria section and included new appendix

\documentclass[twocolumn]{aastex63}

\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand\msun{\rm{M}_{\odot}}
\newcommand\ID{\textit{Illustris-Dark}}
\newcommand\IH{\textit{Illustris-Hydro}}
\newcommand\SUBFIND{\texttt{SUBFIND}}
\definecolor{mypink}{RGB}{232,132,161}
\newcommand{\kc}[1]{\textcolor{mypink}{\textbf{#1}} }
\newcommand{\gb}[1]{\textcolor{olive}{\textbf{#1}} }
%\newcolumntype{H}{>{\setbox0=\hbox\bgroup}c<{\egroup}@{}}
%\usepackage{subcaption}
\usepackage{nicefrac}
\usepackage{soul}
% \usepackage{amssymb}

% \graphicspath{{./}{figures/}}
% \graphicspath{{../}{figures/}}

% \shorttitle{Sample article}
% \shortauthors{Schwarz et al.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Occurance rate of galaxy pairs across cosmic time:\\ Local Group analogs in a cosmological context}
\correspondingauthor{Katie Chamberlain}
\email{katiechambe@email.arizona.edu}

\author[0000-0001-8765-8670]{Katie Chamberlain}
\affil{Steward Observatory, University of Arizona\\
933 North Cherry Avenue\\
Tucson, AZ, 85721, USA}
\author{Gurtina Besla}
\affil{Steward Observatory, University of Arizona\\
933 North Cherry Avenue\\
Tucson, AZ, 85721, USA}
\begin{abstract}

  % \textbf{Context} 
  Dwarf galaxies are extremely common at all redshifts and often exhibit morphological disturbances that do not primarily result from galaxy mergers. As such, pair fractions, rather than morphological indicators (asymmetry, concentration) are needed to infer dwarf galaxy  merger rates from observational surveys.
  However, in contrast to massive galaxies ($5\times 10^9\leq$ $\rm M_{prim,*} \leq 1\times 10^{11} \msun$), pair fractions for dwarf galaxies ($10^8 < \rm M_* < 5 \times 10^9 \msun$) have been theoretically constrained only at low redshift.
  % \\\textbf{Aims}
  We aim to quantify the occurence rates and kinematics of isolated dwarf and massive galaxy pairs from $z=0-4$ in the Illustris and IllustrisTNG cosmological simulations.
  % \\\textbf{Methods} 
  Dwarf and massive subhalo pairs are identified in each snapshot of the Illustris \texttt{SUBFIND} catalogs. 
  % \\\textbf{Results} 
  We find that roughly 8-10\% of dwarf galaxies will have major companion (stellar mass ratio $>1:4$) at $z=0$, increasing steadily before plateauing in \ID(\IH) at 16\%(12\%) by $z\sim 2$. The occurence rate of dwarf galaxies with minor companions (stellar mass ratios between $1:10$ and $1:4$) is roughly constant at $\sim 2.5\%$ from $z=1-4$. In contrast, the occurence rate of major and minor massive galaxy pairs remains approximately constant across time, as massive galaxies have a major (minor) companion $\sim18\%$ ($\sim14\%$) of the time.
  % \\\textbf{Conclusions} 
  This suggests that the hierarchical evolution of dwarf galaxies may proceed differently than that of massive galaxies. LMC-SMC mass analogs (dwarf minor pairs) are twice as common at redshifts greater than 2, but the present day LMC-SMC system is dynamically rare at all redshifts (in terms of pair separation and velocity). The M31-M33 pair is dynamically typical of massive minor pairs at $z\approx0$, while the MW-LMC has unusually high velocities and low relative separations for a major massive pair at low redshift. Baryonic physics impacts the occurence rate of galaxy pairs and systematically changes the kinematics of dwarf pairs, suggesting observations of dwarf galaxy pairs can be used to test subgrid physics in cosmological simulations.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} \label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%
Galaxy mergers are responsible for many physical processes that shape galactic evolution, including triggered star formation~\citep{mihos96, hopkins13, patton20,hani20}, increased AGN activity~\citep{hopkins08,comerford15,ellison19}, and galaxy morphology~\citep[e.g.,][]{rg17}. Dwarf galaxies  make up a majority of the galaxy population at all redshifts (REF) and are also expected to undergo interactions and merge. Such processes may be important to understand the growth and evolution of intermediate mass black holes, which are often found to be ``wandering" in low mass galaxy hosts~\citep{stemo20,reines20}. Despite the ubiquity of dwarf galaxies in the universe, we do not have a clear path to constrain the merger rates of these systems observationally or to place known interacting dwarf galaxy systems (stellar mass $1\times10^8<M_* < 5\times10^9\msun$) in a cosmological context.

Massive galaxy ($M_* > 5\times10^9\msun$) mergers and interactions can be observationally identified using methods like asymmetry and concentration measures~\citep{conselice2000, lotz04}. Numerous studies have used these measures to study the merger and interaction rates of massive galaxies as a function of time~\citep[e.g.,][]{lotz11,casteels14}.

However, \citet{martin21} showed that mergers only account for 10\% of morphological disturbances in dwarfs, and that a majority of their morphological disturbances derive from non-merger interactions, such as gas inflows/outflows, close passages, and fly-bys. This means that the typical methods of classifying interactions and mergers for massive galaxies are unlikely to be robust in lower mass regimes. This is particularly true at high redshift, when gas accretion along filaments is expected to be more significant~\citep{keres09}. Thus, it is critical to establish an alternative, cosmologically consistent, way to determine merger and interaction rates for dwarf galaxy pairs from observations.

Another observational technique to determine merger/interaction rates relies upon the pair fraction: the ratio of the number of host galaxies with a companion to the number of potential hosts. Pair fractions for massive galaxies have been measured observationally as a function of time~\citep[e.g.,][]{lotz08,conselice09}, and calibrated against theoretical simulations to determine observability timescales that enable the translation of pair fractions to merger rates \citep{lotz11,kaviraj15,snyder17,qu17,oleary21b}.
In contrast, pair fractions for dwarf primaries are only starting to be measured at high redshift \citep[e.g.][]{ventou17} and have only been studied with small sample size or calibrated against simulations at low redshift \citep{besla18, casteels14,stierwalt15, pearson18}. Thus we are currently missing a theoretical framework to interpret future high redshift observations of dwarf pairs, i.e. with \textit{JWST}. In this study, we quantify the dwarf galaxy pair fraction as a function of time out to $z\sim$4, and compare these results to the massive galaxy pair fraction, using the N-body and hydrodynamic \textit{Illustris-1} cosmological simulations~\citep{vogelsberger14A,nelson15}.

There are examples of galaxy pairs involving dwarf galaxies in our Local Group, including the M31-M33, MW-LMC, and the LMC-SMC (Magellanic Clouds; MCs) systems. The frequency of such pairs have been studied extensively observationally and theoretically at low redshift.
In SDSS DR7, it is found that 11\% of MW/M31-like objects have one massive satellite (LMC/M33 analog) within 150 kpc and 300 km s$^{-1}$~\citep{liu11}. Within 250 kpc, the frequency increases to 42\% (Tollerud 2011). % , robotham12
This is in agreement with $\Lambda$CDM predictions \citep{busha11, bk11, patel17a, gonzalez13}. 
% check gonzalez
Furthermore, 4-6\% of LMC/M33 analogs in both SDSS and cosmological simulations are expected to have a companion at least as massive as an SMC in the field \citep{besla18, sales11}. %% ADD SALES RESULTS ?      
% add how defined here

However, we do not how common these pair configurations are as a function of time in the $\Lambda$CDM framework, leaving open the question as to whether our Local Group is unique in time. 
Recent advances in astrometry have furthermore enabled the measurement of 6D phase space information for these Local Group galaxy pairs.  
In this study, we will examine whether not only the frequency, but also the dynamics of pairs in our Local Group are unique \textit{across cosmic time}.
% HOW DO MASSIVE PAIRS SCALE TO DWARF REGIME

The Local Group also contains a massive major galaxy pair (stellar mass ratio $>$1:4), the MW-M31. For low redshift (z$<$ $\sim$.1) massive galaxies (M$_\ast > 10^{10}$ M$_\odot$), the fraction of major pairs are expected to increase as a function of mass \citep{casteels14}, resulting in major merger rates that rise  with higher mass~\citep{rg15,ventou17,oleary21b}. Additionally, the fraction of major pairs is also measured to increase with increasing redshift~\citep{deravel09,bundy09,duncan19}. In particular \citet{duncan19} find no strong evolution in the relative number of minor to major mergers for massive hosts out to z$<$3. But it is unclear whether these trends for the frequency of major pairs will be the same if the host mass is in the dwarf galaxy regime.

It is important to study the dwarf and massive host regimes separately, as baryonic physics, including gravitational tides, star formation, and outflows, impacts the growth of dwarf galaxies more strongly~\citep{bullockbk17,jeon19,jeon21}. For example, it has been shown that baryonic physics implemented in the \IH\ simulation suppresses the abundance of low mass subhalos ($\leq$10$^{10}\msun$), but such a suppression is not present for massive halos~\citep{chua17}. Thus, the pair fractions and dynamics of dwarf major and minor pairs may change drastically between the dark-matter-only and full-physics simulations, with less differences for massive  pairs. In this study, we illustrate that the impact of baryonic physics on the growth of low mass halos in cosmological simulations may be directly testable with pair fraction observations.

Here we present the first cosmologically motivated constraints on the dwarf pair fraction for major and minor pairs as a function of time. We compare these results to those found for massive major and minor pairs, and address the differences in expected pair fractions between the N-body and full hydrodynamic simulations. This work will furthermore, self-consistently, place known galaxy pairs in our Local Group in a cosmological and temporal context.  In Sec.~\ref{sec:methods}, we introduce the simulations and selection criteria used to perform the analysis of our sample of pairs. In Sec.~\ref{sec:results}, we present the results of this pair fraction study, including preliminary results on the kinematics of dwarf pairs over cosmic time. In Sec.~\ref{sec:discussion}, we discuss the implications of our results on interpretations of future surveys, and what this could mean for constraints of feedback mechanisms in cosmological simulations. In Sec.~\ref{sec:conclusions} we present a summary of the main conclusions of this work, including expected pair fractions for dwarf and massive galaxy pairs.

%%%%%%%%%%%%%%%%%
\section{Sample Selection} \label{sec:methods}
%%%%%%%%%%%%%%%%%
Our sample of dwarf galaxy pairs and massive galaxy pairs from cosmological simulations was chosen following a strict set of selection criteria. In Sec.~\ref{sec:simData} we will detail the simulations from which we collected our data, Sec.~\ref{sec:abundanceMatching} explains the abundance matching prescription used to associate dark matter halos with stellar masses, and Sec.~\ref{sec:selectionCrit} outlines the isolation and mass criteria used to identify our sample.

\subsection{Simulation data}\label{sec:simData}
We utilize data from the \textit{Illustris Project} ~\citep{vogelsberger14A,nelson15}, a set of N-body and hydrodynamic cosmological simulations, to statistically analyse the occurrence rates of dwarf and massive dark matter subhalo pairs over cosmic time. In particular, we are using the highest resolution dark matter only simulation, \textit{Illustris-1-Dark}, and the  full hydrodynamic simulation, \textit{Illustris-1} (hereafter \textit{Illustris-Dark} and \textit{Illustris-Hydro} respectively, see Table~\ref{table:illustris}).
Each of these simulations follows the dynamical evolution of $1820^3$ dark matter particles from $z=127$ to $z=0$ through a periodic volume of $106.5^3$ Mpc$^3$. The Illustris simulations use a cosmology that is consistent with \textit{WMAP-9} ~\citep{hinshaw13}: $\Omega_m = 0.2726$, $\Omega_\Lambda = 0.7274$, $\Omega_b = 0.0456$, $\sigma_8 = 0.809$, $n_s=0.963$, and $h=0.704$.

% Maybe doesn't need whole paragraph but, about dark vs. hydro
We are utilizing data from both \textit{Illustris-Dark} and \textit{Illustris-Hydro} to study the effect of baryonic content on the subhalos. As dwarf subhalos have more shallow dark matter potentials than their more massive counterparts, they are more likely to be subject to disruption caused by baryonic feedback at higher redshifts, which may result in fewer low mass subhalo pairs in \textit{Illustris-Hydro}.

% Subfind paragraph: 
We use catalogs of dark matter halos and their associated subhalos identified in each simulation using the \texttt{SUBFIND} algorithm ~\citep{springel01,dolag09}. Dark matter halos were identified using the Friends-of-Friends (FoF) algorithm ~\citep{davis85}, which links particles that have separations less than $0.2d$, where $d$ is the mean inter-particle separation. Each FoF group, which we will further refer to as a ``group", was further divided into over-dense and gravitationally bound dark matter subhalos.

% Sublink paragraph:
In order to trace the growth and histories of our subhalos, we are using the merger trees provided by the \texttt{SUBLINK} algorithm \citep{gomez15}, which tracks subhalos between snapshots using their particle data. These merger trees provide information about the kinematics and mass growth of subhalos in both \textit{Illustris-Dark} and \textit{Illustris-Hydro}, and in particular will be used to provide the maximal masses of each of the subhalos we investigate.

The lower mass threshold for subhalos that constitute our dwarf pairs have a halo mass greater than $1\times10^9\msun$, such that each of our halos are resolved into at least 130 particles in \textit{Illustris-Dark} and 150 particles in \textit{Illustris-Hydro}. 
% \kc{add explanation for why 100 particles is good enough for the resolution we're looking for.}

\begin{table}[htb]
\begin{tabular}{lll}
 & Illustris-Dark & Illustris-Hydro \\\hline\hline
 L$_{\rm Box}$ [Mpc] & 106.5 & 106.5 \\
m$_{\rm DM}$ [M$_\odot$] & 7.5$\times10^6$ & 6.3$\times10^6$ \\\hline
\end{tabular}
\caption{\label{table:illustris}Parameters of the Illustris simulations used in this analysis.}
\end{table}
% when i start using TNG can add this!
% \begin{table*}[htb]
% \begin{tabular}{lllll}
%  & Illustris-Dark & Illustris-Hydro & IllustrisTNG-Dark & IllustrisTNG-Hydro\\\hline\hline
%  L$_{\rm Box}$ [Mpc] & 106.5 & 106.5 & 110.7 & 110.7 \\
% m$_{\rm DM}$ [M$_\odot$] & 7.5$\times10^6$ & 6.3$\times10^6$ & 8.9$\times10^6$ & $7.5\times10^6$\\\hline
% \end{tabular}
% \caption{Parameters of the Illustris simulations used in this analysis.}
% \end{table*}

\begin{table*}[htb]
  \begin{center}
    \begin{tabular}{lcc}
     & Dwarf Pairs & Massive Pairs \\\hline\hline
    Group Mass & $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ & $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$  \\
    % Subhalo Max Mass &  &  \\
    Subhalo Current Mass & $>1\times10^{10} \msun$ & $> 5\times10^{11} \msun$ \\
    Primary &$1\times10^{8} < \rm M_* < 5\times10^{9} \msun$ & $5\times10^{9} < \rm M_* < 1\times10^{11} \msun$\\\hline
    \end{tabular}
    \caption{\label{table:mass}Selection criteria for dwarf and massive pairs.}
  \end{center}
    \end{table*}

\subsection{Abundance matching}\label{sec:abundanceMatching}
Although \textit{Illustris-Hydro} provides stellar masses for all subhalos, however these reported masses are higher than observations suggest~\citep{genel14}. We assign stellar masses to dark matter halos in a consistent way between both \ID\ and \IH using the abundance matching (AM) prescription of \citet{moster13} to associate each dark matter halo with a stellar mass.

The AM relationship at low stellar masses has a large spread, thus a subhalo with a dark matter halo mass of $10^{11}$ may be associated with a stellar mass anywhere between $1.2\times10^{8} - 5\times10^{9}\rm M_\odot$, as can be seen in Fig.~\ref{fig:abundanceMatching}.

There are two inputs to the AM relationship: dark matter mass and redshift. As shown recently by \citet{munshi21}, the relationship between stellar mass and peak halo mass of dwarf subhalos in the Marvel and Justice League simulations is much tighter than the relationship between the stellar mass and halo mass of subhalos at $z=0$. We use the maximal dark matter mass of the halo to ensure that the stellar mass associated with each subhalo reflects the shape of the dark matter profile in the inner regions of the subhalo, thus preventing us from assigning very low stellar masses to halos that have been stripped of %a lot of 
their outer dark matter mass by recent interactions. We evaluate the AM relation using the redshift of the halo at the snapshot that we are interested in, rather than the redshift of the halo at its maximal mass, in order to account for ongoing star formation past peak halo mass.

For the collection of subhalos identified at each snapshot of the simulation, the stellar masses are drawn from the gaussian sampled AM relation. We thus generate 50 realizations for the stellar mass distribution of the same subhalo population in order to account for uncertainties in the AM relation. Each realization is treated as an independent sample of galaxies, where computed properties (stellar masses, relative speeds, etc) are averaged over each realization. We report the mean of all realizations and error bars indicate the 1$\sigma$ dispersion across the realizations.

\begin{figure}[htb]
  \centering
  \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/z0.png}
  \caption{\label{fig:abundanceMatching} Abundance matching relationship of \citet{moster13} at z=0 for dark matter halo masses between $10^{10}$ and $10^{14} \msun$. Note that at halo masses below $\sim10^{12} \msun$, there is more spread in stellar mass at fixed halo mass compared to halos with $\rm M_{H} > \sim10^{12} \msun$. This effect is illustrated by the vertical lines at $10^{11}\msun$ and $10^{13}\msun$. %\gb{might be useful here to indicate with horizontal lines the stellar mass range for the dwarf systems and the massive galaxy systems} 
  }
\end{figure}

\subsection{Selection criteria}\label{sec:selectionCrit}
In this section, we will outline the selection criteria used to identify dwarf subhalo and massive subhalo pairs in the \ID\ and \IH\ simulations. In short, we first make a series of mass cuts on the group mass to constrain the masses of the halos that may be contained in the group and to ensure that the systems are relatively isolated. Then, the subhalos of each identified isolated group undergo further mass cuts until we are left with a sample of both dwarf and massive subhalo pairs. A summary of the mass criteria used for our selection can be found in Table~\ref{table:mass}.

\subsubsection{Isolation}
We are interested in the occurrence rates of subhalo pairs in pristine environments to ensure that the dynamics of the subhalos in groups are unaffected by nearby massive perturbers.

FoF groups are large collections of nearby associated particles throughout the Illustris simulation. As there is no boundedness criteria for these groups, we wanted to ensure that pulling pairs of subhalos from FoF groups would yield a sample of subhalos that were dynamically unperturbed by more massive nearby structures. We calculated the isolation fraction 
\begin{equation}
f_{\rm iso} = N_{\rm Hill} / N_{\rm FoF}
\end{equation}
where $N_{\rm Hill}$ is the number of pairs of subhalos that satisfy the Hill radius criterion (see Appendix~\ref{app:hill}), and $N_{\rm FoF}$ is the number of pairs from FoF groups, and found that $>99.8\%$ of all pairs identified in FoF groups are considered isolated by the more stringent Hill radius criterion. We thus used these FoF groups as a proxy for isolation, and considered \textit{all} pairs from FoF groups isolated.

\subsubsection{Group mass cuts}
% why group cuts
We first make a series of cuts on the group masses reported in the \ID and \IH catalogs at each snapshot out to $z\sim12$. Since we are interested in subhalo pairs in two different mass regimes, we will use different mass criteria to isolate groups that may contain dwarf pairs, and groups that may contain more massive galaxy pairs. As mentioned, we do not search for dwarf pairs in massive groups 
since the central subhalos of these more massive groups would perturb the dwarf system.

% actual numerical values of 
Group mass cuts are performed on the group mass provided in the SUBFIND catalogs, \texttt{Group\_M\_TopHat200}, which is the total mass enclosed in a sphere whose mean density is $\rho_c \Delta_c$. The {\bf dwarf groups} must have a group mass $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ while {\bf massive groups} have mass $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$. These dwarf and massive group masses are roughly representative of Magellanic Cloud analogs~\citep{besla12,moster13} and Local Group analogs respectively~\citep{vdm12ii}.

In addition to %overall 
group mass cuts, we ensure that each group has at least one subhalo that satisfies the following properties:
\begin{itemize}
    \item \textit{dwarf} - maximal halo mass is $8\times10^{10} < \rm M_{\rm max} < 5\times10^{11} \rm M_\odot$ with mass at the snapshot of interest M$_{\rm snap} > 1\times10^{10} \rm M_\odot$
    \item \textit{massive} - maximal halo mass is $1\times10^{12} < \rm M_{max} < 4\times10^{12} \rm M_\odot$ with mass at the snapshot of interest M$_{\rm snap} > 5\times10^{11} \rm M_\odot$. 
\end{itemize}
This ensures that each group has at least one subhalo that will serve as a primary galaxy for the catalog after stellar mass cuts are applied (Sec.~\ref{sec:primaries}).

We only consider subhalos in each of these groups that have subhalo masses $M_{H}>10^9M_{\odot}$ at the given snapshot. This ensures that each dwarf pair will consist of subhalos that are resolved into more than 100 dark matter particles at the snapshot of interest.

In practice we find that some low mass groups consist of a set of subhalos with only one or two subhalos with mass above our lower mass threshold of $10^9\msun$, while the remaining subhalos have lower mass. We refer to these types of groups as ``One Subhalo'' and ``Two Subhalo'' groups respectively, since they contain either one or two candidate primaries. Groups with three or more subhalos passing this lower mass threshold are called ``Three+ Subhalo'' groups.

\begin{table*}[htb]
  \begin{center}
\begin{tabular}{ccccc|cccc}
    & \multicolumn{4}{c}{Dwarfs} & \multicolumn{4}{c}{Massive} \\\hline\hline
    z = &0&1&2&4&0&1&2&4 \\ \hline
    Isolated Groups & \# & \# &\# &\#&\#&\#&\#&\#\\
Primaries &  & &&&&&& \\
Pairs &  & &&&&&& \\
Major Pairs &  & &&&&&& \\
Minor Pairs &  & &&&&&& \\
Minor+ Pairs &  & &&&&&& \\\hline
\end{tabular}
\end{center}
\caption{\label{table:counts}\kc{Placeholder for now} Number of groups, primaries, and pairs}
\end{table*}

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_counts.png}
    \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_counts.png}
    \caption{\label{fig:counts} The number of dwarf (top) and massive (bottom) groups primaries identified in each of the \textit{Illustris-Dark} and \textit{Illustris-Hydro}. The linestyle represents the different types of groups where the primaries are identified. The dotted (dashed) lines show the number of primaries in
    groups with only one (two) subhalo(s) with subhalo mass greater than $10^9 \rm M_\odot$. Dot dashed lines show the number of primaries in 
    groups with three or more subhalos with a mass greater than $10^9 \rm M_\odot$. We find that \textit{Illustris-Hydro} has significantly many more primaries in single and double-subhalo groups, which may be a result of different dwarf merger rates in the two simulations. Since there are many more single-subhalo dwarf groups in \textit{Illustris-Hydro}, the fraction of primaries with a companion will be significantly suppressed compared to \textit{Illustris-Dark}.
    There are almost no massive groups that contain only one or two subhalos that pass our lower subhalo mass threshold, thus nearly 100\% of the identified primaries are in groups with at least 3 massive subhalos.}
  \end{figure}

\subsubsection{Dwarf and Massive Primaries}\label{sec:primaries}
Dwarf and massive primaries are defined to be the most massive subhalo in each group with the following properties:
\begin{itemize}
  \item \textit{dwarf} - stellar mass between $10^8 \leq \rm M_{prim,*} \leq 5\times 10^9 \msun$
  \item \textit{massive} - stellar mass between $5\times 10^9 \rm M_{prim,*} \leq 1\times 10^{11} \msun$.
\end{itemize}
We make mass cuts using the stellar masses of the subhalos in order to best compare our results with observational studies. %as this is the data that we will be collecting observationally. Thus, making cuts on the stellar masses of these subhalos allows us to more directly apply our results to observational studies.

The average number of dwarf and massive primary subhalos  %at each of the considered redshifts 
is plotted as a function of redshift in Fig.~\ref{fig:counts}.%, and 
A subset of this data can be found in Table~\ref{table:counts}. Also plotted is the number of primaries in groups with the marked number of companions.

We find that the number of dwarf primaries increases from $z=4$ to about $z\sim0.5$, at which point the number of primaries decreases by approximately 15\% approaching $z=0$. There are significant differences in the number of dwarf primaries that belong to One- and Two-Subhalo Groups in \ID\ and \IH. \IH\ boasts about $2\times$ more primaries in One-Subhalo groups, 1.5-2$\times$ more primaries in Two-Subhalo Groups, and ~0.6$\times$ fewer Three-Subhalo groups than \ID.

The number of massive primaries increases consistently from high to low redshift. There are very few massive groups with only one or two large ($\rm M_{H} > 10^9\sun$) subhalos, since groups of this mass scale typically host at least one large subhalo and its companions and satellites. Thus, almost 100\% of the massive primaries reside in ``Three-Subhalo'' groups.

\subsubsection{Pairs}
The different pair types are defined to contain a dwarf or massive primary subhalo with a secondary subhalo:
\begin{itemize}
    \item \textit{Major Pairs}: with stellar mass $M_{\rm sec,*}$ such that $1/4 \leq M_{\rm sec,*}/M_{\rm prim,*} \leq 1$.
    \item \textit{Minor pairs}: with stellar mass $M_{\rm sec,*}$ such that $1/10 \leq M_{\rm sec,*}/M_{\rm prim,*} \leq 1/4$.
    \item \textit{Minor+ Pairs}: with stellar mass $M_{\rm sec,*}$ such that $M_{\rm sec,*}/M_{\rm prim,*} \leq 1/4$. This set of pairs \textit{includes} the whole set of minor pairs, but also includes pairs whose mass ratio is less than 1/10. 
\end{itemize}
The MCs, as well as the MW+LMC system and M31+M33 system, have a stellar mass ratio of approximately 1/10, and thus would be classified as minor pairs according to our analysis. All pairs must be separated by at least 15 physical kpc so that the pairs are well resolved into individual component subhalos in \SUBFIND.

%
%%
%%%
%%%%
%%%
%%
%

%%%%%%%%%%%%%%%%%
\section{Results}\label{sec:results}
%%%%%%%%%%%%%%%%%
After collecting our sample of dwarf and massive pairs, we analyzed the frequency of occurrence as well as their properties, such as mass ratio and average kinematics of the pairs, as a function of time. By comparing results for groups identified in \ID\ and \IH , we can compare the effect that feedback prescriptions may have on the formation of low mass dwarf pairs vs. massive pairs, and search for differences in their kinematics, which ultimately dictate their merger rates.

Although we collected pairs out to redshift $z\sim12$, the number of identified primaries drops significantly approaching $z\sim4$. As such, the following analysis will focus only on a redshift range of $z=0-\sim4$, where the statistics are more meaningful. In Sec.~\ref{sec:ratios}, we will discuss the stellar, current halo, and maximum halo mass ratios for our sample, which will enable us to examine the mass evolution of these systems. In Sec.~\ref{sec:pairFracs}, we present the main data product of this paper, namely the pair fractions for dwarf and massive major and minor pairs in \ID\ and \IH. In Sec.~\ref{sec:kinematics}, we discuss our findings on the kinematics of our population of pairs.

%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %
% description of the stellar and halo mass evolution
\subsection{Stellar and Halo Masses and Ratios}\label{sec:ratios}
\begin{figure*}[htb]
    \centering
    \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_stellarMass.png}
    \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_stellarMass.png}
    \caption{\label{fig:stellarMass} The average stellar mass of primaries identified in the \ID\ (left) and \IH\ simulations, as a function of redshift. (Top) Mean stellar masses of dwarf pair primaries, where the shaded regions indicate the $1\sigma$ spread computed over 50 realizations of AM relation per snapshot. %dwarf pairs. 
    (Bottom) The same as Top panels, but for the primaries of massive pairs. For dwarf pairs, the average primary stellar mass of minor pairs is much higher than for major pairs, although is roughly the same for massive pairs. The average primary stellar mass increases as a function of time for both dwarf and massive pairs. There are no major differences between the primary stellar masses in \ID\ and \IH, which indicates that the max subhalo masses of the primaries in each of the simulations is roughly equivalent.
     \kc{not sure why the spread of all massive pairs is so small.... gotta check that!}}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_massRatio.png}
  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_massRatio.png}
  \caption{\label{fig:massRatios} 
  The median and 25\%-75\% interquartile range of stellar, current subhalo, and maximum subhalo mass ratios of major (solid) and minor (dashed) pairs in \ID\ and \IH\ for both dwarf and massive regimes. As expected, the stellar mass ratios for major and minor pairs, as well as dwarf and massive pairs, are nearly identical between \ID\ and \IH, as we are using the same stellar mass cuts to define these populations of subhalo pairs in %between 
  each simulation.
  In all cases, the ratio of current subhalo masses as a function of time is always smaller than the max halo ratio. This indicates that the secondaries may be losing a significant portion of their mass to the primary between the time of max mass and the snapshot of interest. 
  %\kc{why don't these lines converge at high z?}. \gb{Can you quote the mean values of interest?}
  }
\end{figure*}

In Fig.~\ref{fig:stellarMass}, we show the average stellar masses of the primaries of major and minor dwarf and massive pairs identified in \ID\ and \IH. We find that the average stellar masses of primaries increases over time, typically peaking at or near $z=0$. The average stellar mass of the primaries of minor and minor+ \textit{dwarf} pairs is much greater than for major pairs across both simulations. There are two explanations for this effect. Firstly, if many major pairs merge by low redshift, leaving behind a more massive central halo and smaller minor satellites, the expected stellar mass of primaries of minor pairs would be significantly higher than the stellar masses of primaries in major pairs. Secondly, because of the stellar mass floor applied to the dwarf sample, only the largest dwarf primaries are contained in the set of minor and minor+ pairs. %, since smaller primaries could not have companions with low enough stellar masses to pass both our lower mass floor and be included in the selection of minor pairs. 
However, the average stellar mass of major and minor massive pairs is roughly similar. Since the lower mass floor for massive secondaries is lower than for primaries (see Sec.~\ref{sec:selectionCrit}), minor massive pairs may have lower mass primaries than possible for the same range of stellar mass ratios for dwarfs.

The stellar and dark matter mass ratios between galaxies or subhalos impact the timescale for the interactions that will occur between pairs owing to dynamical friction (in addition to kinematics, see Sec.~\ref{sec:kinematics}). Interacting subhalos of roughly equal mass may end up tearing each other apart and recombining as a completely new composite subhalo. However, when a large subhalo interacts with a much less massive minor companion, the minor companion may disrupt, forming stellar streams around the more massive primary, with very little disruption to the primary. Separating our collection of pairs by mass ratios will allow us to explore dynamics and interactions separately in these two regimes~\citep{cox08}.
%https://ui.adsabs.harvard.edu/abs/2008MNRAS.384..386C/abstract

In the following discussion, stellar mass ratios will refer to the AM stellar mass of the secondary companion subhalo over the AM stellar mass of the primary. Halo mass ratios refer to the subhalo mass of the secondary reported in the simulation catalog at that redshift, over the subhalo mass of the primary at that redshift. Maximum (max) halo mass ratio refers to the maximum or ``peak'' subhalo mass ever achieved by the secondary subhalo, over the peak subhalo mass achieved by the primary at any point in their evolution. Thus, stellar and halo mass ratios are calculated using values of the stellar and halo masses at the current snapshot, while the max mass ratio may use subhalo masses for the primary and secondary from different snapshots.

We present the median stellar mass ratios, current halo mass ratios, and maximum mass ratios for dwarf and massive major and minor pairs in Fig.~\ref{fig:massRatios}. Since pairs are selected based on their stellar mass ratios in each of the stellar mass realizations, the median stellar mass ratios of major and minor pairs is relatively flat across all redshifts and shows little difference between \ID\ and \IH.

Since the stellar mass of each subhalo is assigned based on the subhalo`s maximal mass, we find, as expected, that the max mass ratio to evolve with redshift in the same way as the %stellar mass to halo mass 
AM relationship for a fixed stellar mass ratio.

However, the halo mass ratio may tell us about how these halos have evolved since they achieved their peak halo masses, including owing to interactions. In particular, we find that in all cases the halo mass ratio falls well below the max halo mass ratio, implying that the secondaries may be losing much of their peak halo mass, potentially to the primaries, thus reducing the halo mass ratio at each redshift.

The time evolution of the
The halo mass ratio for dwarf pairs increases as a function of time, 
%suggesting that, on average, the secondaries are becoming more massive with respect to their primaries, 
which could indicate that a number of high mass ratio (minor) pairs have merged by low redshift.
% GB NOTE TO THINK MORE ABOUT THIS 
However, this is not the case for massive galaxies. Rather, the median halo mass ratio remains approximately constant throughout the considered redshift range.

% \kc{make plots of the halo mass, max mass, etc for prims and secos to confirm suspicions}

% dwarf pairs vs. massive pairs
To understand the evolution of max mass ratios for massive pairs, it is important to remember that the abundance matching relationship is quite shallow at high subhalo masses and low redshifts. This means that, for a fixed stellar mass ratio, the possible corresponding halo ratio drops, as shown by the max halo mass ratio of massive pairs dipping below the stellar mass ratio at low redshift in Fig.~\ref{fig:massRatios}. 
%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %

%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %
% Pair fractions - description of pair frac plots! 
\subsection{Pair fractions}\label{sec:pairFracs}

\begin{figure*}
  \centering
  \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_fractions.png}
  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_fractions.png}
  \caption{\label{fig:pairFrac} The fraction of primary subhalos with companions of different types, relative to all primary subhalos, is plotted as a function of redshift. Results for \ID\ are on the left and for \IH\ on the right. Dwarf Pairs are in the top panels and Massive Pairs are shown in the bottom panels. (Blue) All dwarf (massive) primaries with any companion that passes the lower stellar mass threshold of $10^8 \msun$ ($10^9 \msun$). The fraction of dwarf galaxy pairs of all types decreases steadily from $z\sim2.5$ to today. Massive galaxy pairs demonstrate the opposite behavior, increasing with decreasing redshift. (Purple) Primaries with a companion with a stellar mass ratio between $1$ and $\frac{1}{4}$ (major pairs). Massive major pairs show little evolution with redshift and good agreement between \ID\ and \IH\. In contrast, the fraction of dwarf major pairs increases with redshift, peaking at $z\sim$2. The fraction is lower in \IH\ than in \ID\. (Yellow) Primaries with a companion with a stellar mass ratio between $\frac{1}{4}$ and $\frac{1}{10}$ (minor pairs). In all cases the fraction of minor pairs rises slightly with increasing redshift. (Orange) Primaries with a companion with a stellar mass ratio less than $\frac{1}{4}$ and a stellar mass greater than $10^8 M_\odot$ (minor+ pairs). Dwarf minor+ pair fractions show little evolution with redshift, while massive minor+ pair fractions increase with decreasing redshift.
% \kc{add blurb about how the relative ratio of major pair fractions to minor pair fraction may be something that's testable to distinguish between baryonic physics implementations at low mass scales.} \gb{state values throughout, might want to include different line types in the future} 
}
\end{figure*}

Pair fractions provide insight as to how likely it is to find two galaxies very nearby each other in observations. Pair fractions can be used to back out merger rates from observations where other traditional methods of determining merger rates, such as asymmetry and concentration parameters, may fail. However, as pair fractions have only been calibrated as a function of time for massive pairs, it is important to separately determine expected pair fractions for dwarf pairs, rather than simply extrapolating the results for massive pairs.

After each group's primary was identified, we considered the second most massive halo by stellar mass, and sorted the pairs by stellar mass ratio. The pair fraction was calculated as
$$\rm F_{pair} = \frac{\rm N_{comp}}{\rm N_{prims}},$$
where $\rm N_{comp}$ is the number of pairs with a companion of a certain type (i.e., a major or minor companion), and $\rm N_{prims}$ is the number of primaries. These values are computed for each stellar mass realization independently, and are then averaged for each snapshot. In Fig.\ref{fig:pairFrac}, we show the pair fractions of different pair types as a function of time out to $z\sim4$. The shaded regions represent the $1\sigma$ error on the average of the pair fraction over time, computed by conducting 50 realizations of the stellar catalog at each redshift by sampling the AM relation.

We found that dwarf primaries are much more likely to have at least one major companion at redshifts $z>2$ than at $z=0$: approximately 10\% (8\%) of primaries in \textit{Illustris-Dark} (\textit{Illustris-Hydro}) have a major companion at high redshifts ($z>2$), though this fraction drops to 4\% by $z=0$ in both simulations. The fraction of primaries with a minor companion remains approximately constant from redshift $z=0-4$: $\sim$3-4\%($\sim$5\%) of primaries have a minor (minor+) companion in both \textit{Illustris-Dark} and \textit{Illustris-Hydro}.

There is a slight suppression (between 1-4\%) in the dwarf pair fractions in \IH. As can be seen in Fig.~\ref{fig:counts}, \IH\ contains many more One-subhalo groups than \ID, the number of potential primary subhalos with no companions is much higher, resulting in a decrease in the pair fractions across all pair types between \textit{Illustris-Dark} and \IH.

The pair fraction of massive subhalos evolves dramatically differently than their dwarf counterparts, with the pair fraction either remaining constant or \textit{increasing} at low redshifts, and is much higher than the fraction of dwarf primaries with companions. In particular, the fraction of massive primaries with at least one major companion in \ID\ remains approximately constant for redshifts of $z=0-4$ at between $15-20\%$, while the same pair fraction in \IH\ increases from $\sim12\%$ to $20\%$ by $z=0$.

There is a slight difference between the behavior of the fraction of massive primaries in \ID\ and \IH\ for ``All Pairs'' and major pairs. In particular, there is a sharp uptick in the fraction of primaries with these types of companions at $z\sim1$ in only \ID. This fraction then declines to $z\sim$0.2, then rises sharply to $z=0$. While the sharp rise at low redshift is seen in \IH\ as well, the sharp increase at $z=1$ is not present. This means that there is a significant difference in the fraction of primaries expected with a major companion between the two simulations. In particular, the fraction of major pairs peaks at $z=0$ in \IH, while the fraction of major pairs in \ID is smaller than at $z=1-3$. This simulation-dependent behavior is not present in the minor pairs.

There is a difference 
%\gb{quantify} 
in the relative pair fractions of major and minor dwarf pairs at high redshift, since there is such a dramatic suppression of the fraction of primaries with a major companion. If this can be observationally constrained, it may help us to test %say something} about 
the baryonic physics implemented in cosmological hydrodynamic simulations. %the full hydrodynamic simulation and its impact on dwarf subhalos.
%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %

%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %
% 
\subsection{Kinematics}\label{sec:kinematics}
 We analyzed the average separations and relative velocities of dwarf and massive identified pairs in \ID\ and \IH. We found that there are discrepancies between the kinematics of pairs in the two simulations.

 In all cases of massive and dwarf pairs, \IH\ boasts typically much higher relative velocities ($\sim20-40$km/s higher) between major pairs than \ID. While this velocity separation is less extreme for minor pairs ($\sim5-15$km/s higher), it is still evident, especially at higher redshifts ($z>2$).

 \subsubsection{Separations}
 \begin{figure*}
  \centering
  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_separations.png}
  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_separations.png}
  \caption{\label{fig:separations} The mean magnitude of the relative 3D separation between primary and secondary subhalos in \ID\ and \IH\ as a function of time for dwarf and massive major (left) and minor (right) pairs. The drastic increase in average separation between subhalos as a function of time may indicate that only the longest-living, wide-separation circular-orbit pairs remain at low redshifts, since a majority of low separation pairs may have merged by low redshift. A more detailed analysis of the orbits of these systems will be the subject of future work.
  (Left) Major pairs exhibit a small ($\sim 20$ kpc) separation difference between simulations across all redshifts for both dwarf and massive pairs. 
  This may be due in part to a difference in the major merger timescales between the two simulations. 
  (Right) Minor pairs exhibit roughly the same behavior for separations over time between the two simulations.
  % GB : i would leave the below to the main text. 
  %There is a population of low-separation subhalo pairs in \ID that cannot be matched to equivalent pairs in \IH. If merger timescales are lower or dynamical friction operates more efficiently in the hydro simulation, this could explain the lack of low separation subhalo pairs in \IH and, thus, the discrepancy between the two simulations.
    %\gb{include LMC etc systems}.  
  }
\end{figure*}

Because this study utilizes subhalos selected in
%Using 
cosmological simulations, we can extract the
%means we get 
full 6D-phase information for subhalos, such as 3D position and velocity vectors. 
%about the positions and velocities of the subhalos, and 
We thus do not have to worry about projection effects artificially introducing projected pairs to our dataset. This also means that we can study the evolution of the physical separations of the subhalo pairs and how it might be impacted by mass scale or simulation physics. % and determine the characteristic behaviors of these systems.

In Fig.~\ref{fig:separations}, we show the average separation of our selection of pairs (major and minor pairs, dwarf and massive galaxy pairs) selected in both the \ID\ and \IH simulations.

We find that the average separation of all pair types increases towards lower redshift. This could indicate that the small separation pairs are merging, leaving behind the population of pairs that have longer-lived orbits. Alternatively, the population of pairs picked out with our selection criteria may be very different between lower and higher redshift. Following high redshift pairs and establishing their orbits through to $z=0$ will be the subject of future work.

There is a slight ($\sim$20 kpc), but systematic, separation difference between major pairs in \ID\ and \IH\ in both of the dwarf and massive galaxy regimes. When we considered only subhalos that had separations $> 80$ kpc, the separation difference was resolved between the two simulations, indicating that a low separation population of pairs is absent in \IH. This population of subhalos may have merged earlier in the simulation. This will be studied in future orbital studies.

On average, minor pairs have much lower average separations than major pairs. This trend holds true between both simulations and both mass ranges. Interestingly, the separation discrepancy does not appear for minor pairs, which suffer less dynamical friction, supporting the hypothesis that major close pairs are being missed or merging faster in the \IH simulation.

\subsubsection{Velocities}

%% velocities 
\begin{figure*}
  \centering
  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_velocities.png}
  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_velocities.png}
  \caption{\label{fig:velocities}The mean magnitude of the relative 3D velocity between primary and secondary subhalos in \textit{Illustris-Dark} and \textit{Illustris-Hydro} as a function of time for major (left) and minor (right) pairs. The relative velocities decrease significantly throughout time for all dwarf and massive galaxy pairs. Note that the relative velocities are systematically higher for all pairs in \textit{Illustris-Hydro} (by 15-50 km/s), though the differences are smaller for minor pairs and at low redshift. This discrepancy is likely related to the similar discrepancy seen in the separations (Fig.~\ref{fig:separations}).% The collection of low-separation pairs in \textit{Illustris-Dark} that do not have counterparts in \textit{Illustris-Hydro} also had very low velocities, thus accounting for the difference between the dark and hydro simulations.
%   \kc{can include line for LMC+SMC, MW+M31 (120 Van der marel from HST), M31+M33 and the meanings behind them. (MW+LMC is up at 320 and is at peri so this makes sense.) also need to talk about the low separation without the abundance matching bit}
}
\end{figure*}

Figure~\ref{fig:velocities} illustrates the magnitude of the mean relative 3D velocities between all pair types in both simulations. The relative velocities decrease significantly throughout time for all pairs, where massive pairs have speeds of order 100 km/s larger than dwarf pairs. 
% GB ;is the evolution with time steeper for the hydro case in the massive galaxies than in the dwarf galaxies?

There is a significant $\sim$15km/s ($\sim$30-50km/s) velocity offset between major dwarf (massive) pairs in \ID\ versus \IH. Additionally, a small ($\sim$5-10km/s) velocity separation exists between minor pairs. While this velocity separation is suppressed at very low redshifts for both pair types, the vast spread between velocities suggests a significant orbital/dynamic evolution between pairs in the simulations.

When we exclude all pairs with relative separations $<80$kpc from our analysis, the stark velocity differences between \ID\ and \IH\ are resolved, implying that the ``missing'' population of low separation halos in \IH\ is also responsible for this velocity offset.

In the future, we will include studies of the tangential vs. radial velocities to provide a first order guess about the orbital trajectories of the these systems to determine if they on average are on infalling or radial orbits. 
%\kc{Could do like.... radial/tangential velocity as a funciton of separation? did I do that already?}

%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %

%\kc{make velocity vs. separation plot for hydro vs dark, dwarf and massive galaxies! Major pairs? Or major AND minor? }

%%%%%%%%%%%%%%%%%
\section{Discussion}\label{sec:discussion}
%%%%%%%%%%%%%%%%%
%% summary table! %%
\begin{table*}[tb]
  \begin{center}
\begin{tabular}{ccccc|cccc}
& \multicolumn{2}{c}{Dwarf} & \multicolumn{2}{c}{Massive} & \multicolumn{4}{c}{Local Group Analogs} \\\hline\hline
    & Major Pairs & Minor Pairs & Major Pairs & Minor Pairs & MW-M31 & M31-M33 & MW-LMC& LMC-SMC\\\hline\hline
$\rm M_{*,prim}$ & \# & \# &\# &\#&\#&\#&\#&\#\\
\end{tabular}
\end{center}
\caption{\label{table:summary}\kc{Placeholder for now} Summary table with all values from z=0 (and maybe z=1,2,3,etc)}
\end{table*}
%%                 %%

We analyzed a set of dwarf galaxy pairs and massive galaxy pairs from the \textit{Illustris-1} simulation to place constraints on the cosmologically expected fractions of major and minor pairs as a function of time. Our goals include identifying any differences in the behavior of pairs as a function of primary mass (dwarf or massive galaxy) and simulation physics. Here we use our results to place Local Group Pairs in a cosmological and temporal context (Sec.~\ref{sec:LGimplications}). We further discuss implications of our findings for cosmological simulations with baryonic physics (Sec.~\ref{sec:baryonImpact}). Finally, we briefly compare to existing literature (Sec.~\ref{sec:litcompare}).%Finally we discuss the implications of our work for future extragalactic surveys at high redshift (Section ).
%We found that 
%\kc{What we did. What we found. Stuff that doesn't fit into the subsections}

\subsection{Implications for Local Group Pairs}\label{sec:LGimplications}
\citet{patel17a} showed that the existence of the MW-LMC and M31-M33 pairs, are typical of minor massive pairs at low redshift. However, while the M31-M33 interaction may be characteristic of minor massive pairs, they show that the MW and LMC interaction is dynamically unique, since very high velocity and low separation pairs are dynamically rare at $z=0$. We found that typical minor massive pairs have separations between 200-300kpc and relative velocities between 160-200kpc at low redshifts ($z<$0.5). Since the M31-M33 pair has a current separation of $\sim$200kpc and relative velocity $\sim$200km/s, and the MW-LMC pair has a separation of $\sim$50kpc and relative velocity of $\sim$320km/s, our results are in good agreement with \citet{patel17a}. However, while the MW-LMC kinematics may not be typical at low redshift, they are more characteristic of higher redshift ($z>2$) minor massive pairs, where separations are on average $<$150kpc and velocities exceed 240km/s.

Since the MCs are at a separation of only $23kpc$ and have a relative velocity of $103km/s \pm26$~\cite{zivick18}, the combination of separations and velocities is non-typical, as this separation is uncommon at low redshift, while these velocities are uncommon at higher redshift. These kinematic differences can be potentially reconciled by the presence of the MW, and the study of the dynamics of triples will be the topic of future work.

%It is thought that the LMC+SMC system fell into the MW halo recently ($<$2Gyr ago) and is currently making its first pericentric passage around the MW~\citep{besla10,bk11} (patel20). This means that the MC-system system spent a majority of their interaction history in a more isolated environment than the MW halo. However, we have no idea if the characteristics of the orbital models for the MCs are typical of dwarf pairs in isolation.

%  120km/s  and a separation of 782kpc$\pm$25 \cite{mcconnachie05} HST proper motions and GAIA proper motions total speed ranges from -- to -- and the separation is high! So MW-M31 is not typical, and is true at all points in time for groups of this mass.

While \citet{besla18} finds that 70-85\% of dwarf pairs in their sample are major pairs, we find that between 40-45\% of all pairs are major pairs, although this fraction increases at higher redshift to $\sim$60-65\%. The stellar mass range of our study includes stellar masses down to $10^8\msun$ while the \citet[]{besla18} study includes stellar masses down to $2\times10^8$. Our lower stellar mass limits and ability to ensure that pairs are associated in the same group may increase the number of dwarf minor pairs in our sample.

\subsection{Impact of Mass Scales and Baryonic Physics}\label{sec:baryonImpact}
The mass scale of our galaxy pairs heavily influences the behaviour of the pair fractions as a function of time. The pair fractions of dwarf major pairs are $\sim$4\% at z=0 in both simulations, however the pair fraction grows steadily and peaks at $z=2$, where the values plateau. This time-dependent evolution is very different from our results for massive pairs, since massive major pair fractions stay roughly constant or \textit{decrease} at higher redshift. This indicates that the evolution of dwarf and massive galaxy pairs proceeds very differently and on different timescales.

We also found that the evolution of dwarf pair fractions between $z=0-4$ is dramatically different between \ID\ and \IH. In particular, the pair fractions in \IH\ are approximately $20-25\%$ lower than those of \ID. This suppression effect is not seen with massive pairs, implying that the implementation of baryonic physics in \IH\ impacts the evolution of dwarf pairs much more strongly than massive pairs.

\subsection{Comparison to existing work}\label{sec:litcompare}
% Although dwarf pairs such as the Magellanic Clouds are rare at low redshift ~\citep{besla18}, many more dwarf pairs may be observable with future high redshift observations! We expect that at $z\sim2$, roughly 10\% of roughly LMC-mass dwarfs will have at least one major companion, and an additional 4\% will have at least one minor companion.

%GB: Discuss here general trends -- expected behavior as a function of time. and relative trends between massive vs low mass or major vs minor pairs. 
\citet{lotz08} finds that the merger fraction of massive major galaxy pairs (M$_*>10^{10}\msun$) is approximately constant at 10$\pm$2\% between $0.2<z<1.2$, which is consistent with our findings that massive major pair fraction evolves very little (only $\pm$2\%) as a function of redshift. While the redshift evolution of our pairs is consistent with \citet{lotz08}, we do find higher pair fractions across this same redshift range (with pair fractions ranging between 16-20\%), which may be due to our increased sample of massive major pairs at high separation.

\citet[]{casteels14} found that the major merger fraction for galaxies with $10^{9.5}< M_* < 10^{11.5}\msun$ (roughly equivalent to our massive pair criteria) is approximately 1.3-2\% at low redshift, but increased to $4\%$ at lower masses. We find that massive major pairs have a pair fraction of $f_{pair}\sim18-20$\% at low redshift, which is inconsistent with the \citet{casteels14} work, but close to 4\% for dwarf galaxy major pairs, which is consistent with observations. However, \citet{casteels14} uses morphological signatures of mergers to calculate merger fractions. Since massive galaxies will only have morphological signatures from recent close passages of other massive galaxies, these methods will preferentially select close pairs compared to larger separation pairs. Since our study includes many low redshift, highly separated pairs, it is not unreasonable to assume that the major pair fraction difference between the two studies arises from these selection criteria.

\citet{duncan19} found that the observational massive major pair fraction increases with redshift from $z=0$ (where f$_{pair}\sim0.07$) to $z=4$ (f$_{pair}\sim0.2$). This is in contrast to our finding that the massive major pair fraction is constant/slightly decreasing from $z=0-4$ (from f$_{pair}\sim0.2$ to f$_{pair}\sim0.14$)). This is likely due to the strict projected separation cuts that are made on the observational data, where massive major pairs must have $5<r_{proj}<30kpc$, while our massive major pairs includes low separation \textit{and} high separation (r$_{sep}>$30kpc) pairs. This accounts for our inflated pair fraction at all redshifts compared to the \citet[]{duncan19} work.

In general, our study finds inflated pair fraction results because of our ability to determine associated, but well separated, dwarf and massive galaxy pairs.

% https://ui.adsabs.harvard.edu/abs/2019ApJ...872...24V/abstract
  % v 34 36, 123 25, 19 37 km s . M31,DR2 HST
% https://ui.adsabs.harvard.edu/abs/2020arXiv201209204S/abstract

% Zivick https://iopscience.iop.org/article/10.3847/1538-4357/aad4b0/pdf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}\label{sec:conclusions}
In this paper we presented a study of isolated pairs of dwarf and massive subhalos in the large volume cosmological simulation \textit{Illustris-1}, using data from both the N-body (dark matter only) and full hydrodynamic simulations, \textit{Illustris-Dark} and \textit{Illustris-Hydro} respectively. Our criteria requires that all pairs are a part of the same FoF group (see Sec.~\ref{sec:selectionCrit}). We ensure isolation of our selection of pairs using a Hill Radius criteria to ensure that pairs are not gravitationally influenced by nearby massive perturbers.

We define dwarf galaxies as having stellar mass $10^8\msun <M_* < 5\times10^9 \msun$, and massive galaxies as $5\times10^9<M_*<10^{11}\msun$. Major pairs have secondary to primary stellar mass ratios between 1-1:4, minor pairs have stellar mass ratios between 1:4-1:10, and minor+ pairs have stellar mass ratios $<$1:4, thus including the population of minor pairs.

We found that there is a difference in the evolution of the pair fraction for dwarf pairs and massive pairs over time, and that baryonic physics has an impact on the expected pair fractions and kinematics of these systems.

% state a main high level conclusion - are the pair fractions different between massive galaxies and dwarfs ? (which is more common, is their behavior with z the same?)  Does hydrodynamics matter?

Our pair fraction results are summarized as follows:

% Dwarf Pairs : 
(i.) \textbf{The pair fractions for all dwarf primaries with a companion with stellar mass $>10^8\msun$ (All Pairs) peaks at $z=2$ and remains constant to $z=4$.} In \ID, the pair fraction is approximately $8\%$ at $z=0$ and increases to peak at 16\% at $z=2$, while in \IH, the pair fraction is $8\%$ at $z=0$, increasing to $\sim$12\% at $z=2$. In both simulations, the trends with redshift are determined by the major pairs, which are the most common class of dwarf galaxy pair at all redshifts.

(ii.) \textbf{Magellanic Cloud mass analogs (dwarf minor pairs) are approximately 1.5x more common at $z>2$ than at the present day.} In \IH, $\sim$2-3\% of dwarf primaries (LMC analogs) host a minor companion (SMC analog) across all redshifts, with only a slight increase in the pair fraction between $z=0$ and $z=2$. There is slightly more evolution in the case of \ID, with $\sim$4\% of primaries hosting a minor companion for $z>2$, and declining to 2\% at $z=0$. Thus, we expect to find isolated minor dwarf pairs with approximately the same frequency out to $z=4$.

(iii.) \textbf{Dwarf primaries are 2-2.5$\times$ more likely to have major companions at $z>2$ than at $z=0$.} We expect that roughly $\sim$4\% of dwarf primaries will have a major companion at $z=0$, increasing to $z=2$ before leveling off at 10\% (8\%) in \ID\ (\IH) for $z>2$.

% comparison between dark and hydro with dwarfs
(iv.) \textbf{The pair fraction of dwarf primaries with companions of all types (major, minor, minor+) is between $1-4\%$ less common in \IH\ than in \ID.} This indicates that the baryonic physics of the \IH simulation has a non-negligible impact on the expected pair fractions for low mass systems. The same suppression of pair fractions for these pair types is not seen for massive pairs.

% Massive galaxies 
(v.) \textbf{The pair fractions for all massive galaxy primaries with a companion with a stellar mass $>10^8 \msun$ increases over time and peaks between $z=0-1$.} This behaviour is primarily driven by the pair fraction of massive minor+ pairs, as the pair fractions for massive major and minor pairs is relatively flat across $z=0-4$. This is very different than the behaviour of low mass galaxy pairs, where the major dwarf pairs drive the evolution of pair fractions for dwarf pairs.

(vi.) \textbf{$\sim$15\% of MW/M31 analogs host a LMC/M33 mass analog at all redshifts (minor pairs for massive galaxies).}  The behavior is similar in \ID and \IH. It is also similar to the behavior of dwarf galaxy minor pairs (LMC/SMC analogs) with time. % MW/LMC and M31/M33 analogs are only slightly more common at $z>1$ than at z=0.}

(vii.) \textbf{The frequency of MW-M31-type pairs (major massive galaxy pairs) may be impacted by baryonic physics,} as demonstrated by differences in the time evolution of pair fractions between \ID\ and \IH. In the case of \ID, the pair fraction of massive major pairs is $\sim$17-18\% at $z=0$, and increases to roughly $20\%$ between $z=1-3$. However, in \IH, the pair fraction of massive major pairs peaks at 20\% at $z=0$, and declines steadily to $15\%$ at $z=4$. The evolution of major galaxy pairs is markedly different than for dwarf galaxies

(viii.) \textbf{These results are/are not consistent with observations.}

Our results for pairs in terms of their kinematics are as follows:

(i.) \textbf{The relative separation between dwarf (massive) galaxy major pairs increases by $\sim$100kpc ($\sim$250kpc) from $z=4$ to $z=0$.} The minor pairs show similar trends with the relative separations increasing by $\sim$90kpc ($\sim$180kpc) from $z=4$ to $z=0$. There is a relative separation difference between major pairs in \ID\ vs. \IH of approximately 10-15kpc (20-40kpc), with average separations higher across all redshifts in \IH. At $z=0$, the average separation of dwarf minor pairs is $\sim$140-150 in both simulations.

(ii.) \textbf{The relative velocities of between dwarf (massive) galaxy major pairs decreases by $\sim$30km/s ($\sim$90km/s) from $z=4$ to $z=0$.} The dwarf (massive) minor pairs show similar trends, where the average velocity decreases by $40$km/s ($100$km/s) from $z=4$ to $z=0$. There is a significant impact on the average velocities of pairs in this sample from baryonic physics, as there is a velocity separation between the two simulations of approximately $20$km/s (40km/s) for dwarf (massive)  major pairs, and 10km/s (20km/s) for dwarf (massive) minor pairs.

(iii.) \textbf{The MCs are dynamically unique compared to the population of dwarf minor pairs at $z=0$.} Their separation is much smaller and their velocities much larger than is typical for dwarf minor pairs.

(iv.) \textbf{While the M31-M33 pair is dynamically typical of massive minor pairs at low redshift, the MW-LMC pair is extremely unique both in terms of its small separation and large velocities.}

(v.) \textbf{MW-M31 pair has lower relative velocities and higher separations than typical massive major pairs at low redshift.}

We've shown that there is a difference in pair fractions between dwarf pairs and massive pairs. In addition, baryonic effects implemented in \IH\ have a non-negligible impact on the behaviour of the evolution of pair fractions and on the typical kinematics, and we'll be able to see how these discrepancies play out in the era of \textit{JWST.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Post prelim focus}
% After prelim I will work on:
% \begin{itemize}
%   \item adding TNG results!
%   \item completing this study for 1000 realizations of the abundance matching prescription
% \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{aasjournal}
\bibliography{biblio2021.bib}

\appendix{Hill Radius Criteria\label{app:hill}}
The Hill radius is the distance from the center of a group, $G$, at which circular orbits of particles within $G$ will no longer be stable due to the presence of a massive perturber $P$.

The Hill radius is defined as:
\begin{equation}
  R_{\rm Hill} = R_{\rm sep} \bigg( \frac{ M_{\rm G} }{ 3M_{\rm P} } \bigg)^{1/3},
\end{equation}
where $M_{\rm P}$ is the mass of the perturber, $M_{\rm G}$ is the mass of the group under consideration, and $R_{\rm sep}$ is the physical separation between the two groups ~\citep{hahn09}.
\l
As the Hill radius is a measure of the distance from center that particles in $G$ can sustain circular orbits, we consider the group $G$ isolated if the radius of the group is less than the Hill radius. 
The radius of the group is taken to be \texttt{Group\_R\_TopHat200} provided in the \texttt{SUBFIND} catalog, which is the radius of a sphere, centered on the group, whose mean density is $\rho_c \Delta_c$, where $\rho_c$ is the critical density of the universe and $\Delta_c$ is given by the spherical top-hat collapse model of \citet{brynorman98}. This ensures that the particles belonging to $G$ are gravitationally bound to $G$ and that the intrinsic dynamics of the subhalo pairs contained within are not affected by massive perturbers.

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-09-09 pears/utils/get_groups.py
finished and written ecsv files!!!

@@ -14,6 +14,9 @@ __status__ = "Beta -- forever."
 import numpy as np
 from utils.read_group_cats import ReadCats
 from utils.paths import SetupPaths
+from astropy.table import QTable
+import astropy.units as u
+# import pandas as pd
 
 
 class GetGroups:
@@ -37,7 +40,7 @@ class GetGroups:
         subfindID: int
             the ID number of the subhalo at the corresponding snapshot
         sim: str
-            "Illustris" or "IllustrisTNG"
+            "Illustris" or "TNG"
             to specify which simulation
         physics: str
             "dark" or "hydro"
@@ -72,119 +75,64 @@ class GetGroups:
         self.scale = 1/(1+self.redshift)
 
         # to pull out all of the groups within the bounds
-        self.mvirs_phys = self.mvirs/self.h
-        self.rvirs_phys = self.rvirs*self.scale
+        # Note: virial mass and virial radius are both in physical units
+        self.mvirs_phys = self.mvirs/self.h 
+        self.rvirs_phys = self.rvirs*self.scale/self.h
         low_cut = (self.mvirs_phys > self.group_min)
         high_cut = (self.mvirs_phys < self.group_max)
         non_zero = self.mvirs != 0 
         mass_cut =  low_cut&high_cut&non_zero
 
+        # find the Group ID #s of all groups that pass the cut
         self.pass_numbers = np.where(mass_cut==True)[0]
-        self.pass_mass = self.mvirs_phys[self.pass_numbers]
-        self.pass_mass = self.rvirs_phys[self.pass_numbers]
+        self.pass_mvir = self.mvirs_phys[self.pass_numbers]
+        self.pass_rvir = self.rvirs_phys[self.pass_numbers]
         self.pass_nsubs = self.nsubs[self.pass_numbers]
-
-        print('alright now lets see if she breaks')
-
-        self.pass_isoflag = self.get_isolation_flag(self.pass_numbers)
-        
-
-
-    
-
-
-
-
-
-    def get_isolation_flag(self, group_number):
-        xLo, xHi, yLo, yHi, zLo, zHi = subbox(groupPos[groupNum]) # in ckpc/h   
-        xGrps, yGrps, zGrps = groupPos[:,0], groupPos[:,1], groupPos[:,2]
[…]

### 2022-06-24 pears/utils/make_1pair.py
updated make files for rerun post download of tng dark files

@@ -21,7 +21,7 @@ paths = SetupPaths()
 subhalo_path = f"{sim}_{snapshot}.hdf5"
 subhalo_data = h5py.File(f"{paths.path_subhalos}{subhalo_path}", "r")
 
-savepath = f"{sim}_{snapshot}_1pair.hdf5"
+savepath = f"{sim}_{snapshot}_1pair_medstel.hdf5"
 f = h5py.File(f"{paths.path_pairs}{savepath}", 'w')
 
 redshift = subhalo_data["Header"].attrs["Redshift"]
@@ -77,7 +77,8 @@ for phys in ["dark","hydro"]:
                                  "Sub2 Vel": [],
                                  "Separation": [],
                                  "RelVel": [],
-                                 "Stellar Mass Ratio": [] }
+                                 "Stellar Mass Ratio": [],
+                                 "Stellar Mass Realization": []}
 
         ## create dictionary of subhalo info
         for key,val in subhalo_data[phys][size].items():
@@ -99,19 +100,25 @@ for phys in ["dark","hydro"]:
                 
                 # can change these to be by stellar mass instead! 
                 #currently halo mass! 
-                primary_loc = 0
-                secondary_loc = 1
+                meds = shortlist["Subhalo Med Stellar Mass"]
+                primary_loc = np.where(meds==np.max(meds))
+                
+                meds_sansmax = np.where(meds==np.max(meds), 0, meds)
+                secondary_loc = np.where(meds==np.max(meds_sansmax))
 
-                id1 = shortlist['Subhalo ID'][primary_loc]
-                id2 = shortlist['Subhalo ID'][secondary_loc]
-                mass1 = shortlist['Subhalo Mass'][primary_loc]
-                mass2 = shortlist['Subhalo Mass'][secondary_loc]
-                stel1 = shortlist['Subhalo Stellar Masses'][primary_loc][0]
-                stel2 =  shortlist['Subhalo Stellar Masses'][secondary_loc][0]
-                pos1 = shortlist['Subhalo Pos'][primary_loc]
-                pos2 = shortlist['Subhalo Pos'][secondary_loc]
-                vel1 = shortlist['Subhalo Vel'][primary_loc]
-                vel2 = shortlist['Subhalo Vel'][secondary_loc]
+                id1 = shortlist['Subhalo ID'][primary_loc][0]
+                id2 = shortlist['Subhalo ID'][secondary_loc][0]
[…]

### 2022-06-24 pears/utils/make_am_realizations.py

@@ -61,7 +61,7 @@ for ind in range(len( subhalo_data[list(subhalo_data.keys())[0]] )):
                                 samples=num_reals).stellar_mass()[0]
         medstar = AbundanceMatching(maxmass=halo_maxmass*1e10, 
                                     redshift=redshift,
-                                    samples=num_reals).stellar_mass(med=True)[0]
+                                    samples=1).stellar_mass(med=True)
 
     stellar_reals.append(stars/1e10) # in units of 1e10 Msun
     stellar_med.append(medstar/1e10)

### 2022-06-24 pears/utils/make_groups.py

@@ -2,67 +2,61 @@ import h5py
 import numpy as np
 from utils.get_groups import GetGroups
 from utils.paths import SetupPaths
+import sys
 
 paths = SetupPaths()
 
-snaps = {}
+snap = int(sys.argv[1])
+sim = str(sys.argv[2])
 
-snaps["Illustris"] = np.arange(0,136,1)
-snaps["TNG"] = np.arange(0,100)
+#create the hdf5 file!
+savepath = f"{sim}_{snap}.hdf5"
+f = h5py.File(f"{paths.path_groups}{savepath}", 'w')
 
+success=False
+for phys in ["dark","hydro"]:
+    for s in ["dwarf","massive"]:
+        try:
+            inst = GetGroups( snapshot=snap, 
+                    sim=sim,
+                    physics=phys,
+                    size=s)
 
-# snaps["Illustris"] = np.arange(130,136,1)
-# snaps["TNG"] = np.arange(95,100,1)
+            group_dict = {"Group Number":inst.pass_numbers, 
+                        "Group Mass":inst.pass_mvir, 
+                        "Group Radius":inst.pass_rvir, 
+                        "Nsubs":inst.pass_nsubs}
 
-for sim in ["Illustris","TNG"]:
-    for snap in snaps[sim]:
+            units_dict = {"Group Number":"Group Number in Subfind Catalogs", 
+                "Group Mass":"Physical mass from Group_M_TopHat200 -- 1e10 Msun", 
+                "Group Radius":"Physical radius from Group_R_TopHat200 -- kpc", 
+                "Nsubs":"Number of subhalos in group"}
 
-        #create the hdf5 file!
-        savepath = f"{sim}_{snap}.hdf5"
-        f = h5py.File(f"{paths.path_groups}{savepath}", 'w')
+            for key, val in group_dict.items():
+                dset = f.create_dataset(f'/{phys}/{s}/{key}', 
+                                        shape=val.shape,
+                                        dtype=val.dtype)
+                dset.attrs[key] = units_dict[key]
+                dset[:] = val
 
-        success=False
-        for phys in ["dark","hydro"]:
-            for s in ["dwarf","massive"]:
-                try:
-                    inst = GetGroups( snapshot=snap, 
-                            sim=sim,
-                            physics=phys,
-                            size=s)
+            success = True
 
-                    group_dict = {"Group Number":inst.pass_numbers, 
-                                "Group Mass":inst.pass_mvir, 
[…]

### 2022-06-24 pears/utils/make_subhalos.py

@@ -5,6 +5,7 @@ in the groups of interest!
 
 import h5py
 import numpy as np
+import sys
 from utils.get_groups import GetGroups
 from utils.paths import SetupPaths
 
@@ -21,6 +22,8 @@ f = h5py.File(f"{paths.path_subhalos}{savepath}", 'w')
 
 success=False
 for phys in ["dark","hydro"]:
+    if phys =="hydro":
+        continue
     try:
         am_file_path = f"{sim}_{phys}_{snap}.hdf5"
         am_masses = h5py.File(f"{paths.path_am_mass}{am_file_path}", "r")

### 2022-06-24 pears.tex
deploy: 387cec828f5ed98811ea00b0a0ec776d421e60c3

--- 2021-09-07 paper/pears.tex
@@
 
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/z0.png}
-  \caption{\label{fig:abundanceMatching} Abundance matching relationship of \citet{moster13} at z=0 for dark matter halo masses between $10^{10}$ and $10^{14} \msun$.
+% \begin{figure}[htb]
+%   \centering
+%   \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/z0.png}
+%   \caption{\label{fig:abundanceMatching} Abundance matching relationship of \citet{moster13} at z=0 for dark matter halo masses between $10^{10}$ and $10^{14} \msun$.
 Note that at halo masses below $\sim10^{12} \msun$, there is more spread in stellar mass at fixed halo mass compared to halos with $\rm M_{H} > \sim10^{12} \msun$.
@@
 %\gb{might be useful here to indicate with horizontal lines the stellar mass range for the dwarf systems and the massive galaxy systems}
-  }
-\end{figure}
+%   }
+% \end{figure}
 
@@
 
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_counts.png}
-    \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_counts.png}
-    \caption{\label{fig:counts} The number of dwarf (top) and massive (bottom) groups primaries identified in each of the \textit{Illustris-Dark} and \textit{Illustris-Hydro}.
+% \begin{figure}[htb]
+%     \centering
+%     \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_counts.png}
+%     \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_counts.png}
+%     \caption{\label{fig:counts} The number of dwarf (top) and massive (bottom) groups primaries identified in each of the \textit{Illustris-Dark} and \textit{Illustris-Hydro}.
 The linestyle represents the different types of groups where the primaries are identified.
 The dotted (dashed) lines show the number of primaries in
-    groups with only one (two) subhalo(s) with subhalo mass greater than $10^9 \rm M_\odot$. Dot dashed lines show the number of primaries in 
-    groups with three or more subhalos with a mass greater than $10^9 \rm M_\odot$.
+%     groups with only one (two) subhalo(s) with subhalo mass greater than $10^9 \rm M_\odot$. Dot dashed lines show the number of primaries in 
+%     groups with three or more subhalos with a mass greater than $10^9 \rm M_\odot$.
 We find that \textit{Illustris-Hydro} has significantly many more primaries in single and double-subhalo groups, which may be a result of different dwarf merger rates in the two simulations.
 Since there are many more single-subhalo dwarf groups in \textit{Illustris-Hydro}, the fraction of primaries with a companion will be significantly suppressed compared to \textit{Illustris-Dark}.
-    There are almost no massive groups that contain only one or two subhalos that pass our lower subhalo mass threshold, thus nearly 100\% of the identified primaries are in groups with at least 3 massive subhalos.}
-  \end{figure}
+%     There are almost no massive groups that contain only one or two subhalos that pass our lower subhalo mass threshold, thus nearly 100\% of the identified primaries are in groups with at least 3 massive subhalos.}
+%   \end{figure}
 
@@
 \subsection{Stellar and Halo Masses and Ratios}\label{sec:ratios}
-\begin{figure*}[htb]
-    \centering
-    \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_stellarMass.png}
-    \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_stellarMass.png}
-    \caption{\label{fig:stellarMass} The average stellar mass of primaries identified in the \ID\ (left) and \IH\ simulations, as a function of redshift.
+% \begin{figure*}[htb]
+%     \centering
+%     \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_stellarMass.png}
+%     \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_stellarMass.png}
+%     \caption{\label{fig:stellarMass} The average stellar mass of primaries identified in the \ID\ (left) and \IH\ simulations, as a function of redshift.
 (Top) Mean stellar masses of dwarf pair primaries, where the shaded regions indicate the $1\sigma$ spread computed over 50 realizations of AM relation per snapshot.
 %dwarf pairs.
-    (Bottom) The same as Top panels, but for the primaries of massive pairs.
+%     (Bottom) The same as Top panels, but for the primaries of massive pairs.
 For dwarf pairs, the average primary stellar mass of minor pairs is much higher than for major pairs, although is roughly the same for massive pairs.
@@
 There are no major differences between the primary stellar masses in \ID\ and \IH, which indicates that the max subhalo masses of the primaries in each of the simulations is roughly equivalent.
-     \kc{not sure why the spread of all massive pairs is so small.... gotta check that!}}
-\end{figure*}
+%      \kc{not sure why the spread of all massive pairs is so small.... gotta check that!}}
+% \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_massRatio.png}
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_massRatio.png}
-  \caption{\label{fig:massRatios} 
-  The median and 25\%-75\% interquartile range of stellar, current subhalo, and maximum subhalo mass ratios of major (solid) and minor (dashed) pairs in \ID\ and \IH\ for both dwarf and massive regimes.
+% \begin{figure*}
+%   \centering
+%   \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_massRatio.png}
+%   \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_massRatio.png}
+%   \caption{\label{fig:massRatios} 
+%   The median and 25\%-75\% interquartile range of stellar, current subhalo, and maximum subhalo mass ratios of major (solid) and minor (dashed) pairs in \ID\ and \IH\ for both dwarf and massive regimes.
 As expected, the stellar mass ratios for major and minor pairs, as well as dwarf and massive pairs, are nearly identical between \ID\ and \IH, as we are using the same stellar mass cuts to define these populations of subhalo pairs in %between
-  each simulation.
-  In all cases, the ratio of current subhalo masses as a function of time is always smaller than the max halo ratio.
+%   each simulation.
+%   In all cases, the ratio of current subhalo masses as a function of time is always smaller than the max halo ratio.
 This indicates that the secondaries may be losing a significant portion of their mass to the primary between the time of max mass and the snapshot of interest.
-  %\kc{why don't these lines converge at high z?}. \gb{Can you quote the mean values of interest?}
-  }
-\end{figure*}
+%   %\kc{why don't these lines converge at high z?}. \gb{Can you quote the mean values of interest?}
+%   }
+% \end{figure*}
 
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_fractions.png}
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_fractions.png}
-  \caption{\label{fig:pairFrac} The fraction of primary subhalos with companions of different types, relative to all primary subhalos, is plotted as a function of redshift.
+% \begin{figure*}
+%   \centering
+%   \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_fractions.png}
+%   \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_fractions.png}
+%   \caption{\label{fig:pairFrac} The fraction of primary subhalos with companions of different types, relative to all primary subhalos, is plotted as a function of redshift.
 Results for \ID\ are on the left and for \IH\ on the right.
@@
 Dwarf minor+ pair fractions show little evolution with redshift, while massive minor+ pair fractions increase with decreasing redshift.
-% \kc{add blurb about how the relative ratio of major pair fractions to minor pair fraction may be something that's testable to distinguish between baryonic physics implementations at low mass scales.} \gb{state values throughout, might want to include different line types in the future}
-}
-\end{figure*}
+% % \kc{add blurb about how the relative ratio of major pair fractions to minor pair fraction may be something that's testable to distinguish between baryonic physics implementations at low mass scales.} \gb{state values throughout, might want to include different line types in the future}
+% }
+% \end{figure*}
 
@@
  \subsubsection{Separations}
- \begin{figure*}
-  \centering
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_separations.png}
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_separations.png}
-  \caption{\label{fig:separations} The mean magnitude of the relative 3D separation between primary and secondary subhalos in \ID\ and \IH\ as a function of time for dwarf and massive major (left) and minor (right) pairs.
+%  \begin{figure*}
+%   \centering
+%   \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_separations.png}
+%   \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_separations.png}
+%   \caption{\label{fig:separations} The mean magnitude of the relative 3D separation between primary and secondary subhalos in \ID\ and \IH\ as a function of time for dwarf and massive major (left) and minor (right) pairs.
 The drastic increase in average separation between subhalos as a function of time may indicate that only the longest-living, wide-separation circular-orbit pairs remain at low redshifts, since a majority of low separation pairs may have merged by low redshift.
 A more detailed analysis of the orbits of these systems will be the subject of future work.
-  (Left) Major pairs exhibit a small ($\sim 20$ kpc) separation difference between simulations across all redshifts for both dwarf and massive pairs. 
-  This may be due in part to a difference in the major merger timescales between the two simulations. 
-  (Right) Minor pairs exhibit roughly the same behavior for separations over time between the two simulations.
-  % GB : i would leave the below to the main text. 
-  %There is a population of low-separation subhalo pairs in \ID that cannot be matched to equivalent pairs in \IH.
+%   (Left) Major pairs exhibit a small ($\sim 20$ kpc) separation difference between simulations across all redshifts for both dwarf and massive pairs. 
+%   This may be due in part to a difference in the major merger timescales between the two simulations. 
+%   (Right) Minor pairs exhibit roughly the same behavior for separations over time between the two simulations.
+%   % GB : i would leave the below to the main text. 
+%   %There is a population of low-separation subhalo pairs in \ID that cannot be matched to equivalent pairs in \IH.
 If merger timescales are lower or dynamical friction operates more efficiently in the hydro simulation, this could explain the lack of low separation subhalo pairs in \IH and, thus, the discrepancy between the two simulations.
-    %\gb{include LMC etc systems}.  
-  }
-\end{figure*}
+%     %\gb{include LMC etc systems}.  
+%   }
+% \end{figure*}
 
@@
 %% velocities 
-\begin{figure*}
-  \centering
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_velocities.png}
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_velocities.png}
-  \caption{\label{fig:velocities}The mean magnitude of the relative 3D velocity between primary and secondary subhalos in \textit{Illustris-Dark} and \textit{Illustris-Hydro} as a function of time for major (left) and minor (right) pairs.
+% \begin{figure*}
+%   \centering
+%   \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_velocities.png}
+%   \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_velocities.png}
+%   \caption{\label{fig:velocities}The mean magnitude of the relative 3D velocity between primary and secondary subhalos in \textit{Illustris-Dark} and \textit{Illustris-Hydro} as a function of time for major (left) and minor (right) pairs.
 The relative velocities decrease significantly throughout time for all dwarf and massive galaxy pairs.
@@
 This discrepancy is likely related to the similar discrepancy seen in the separations (Fig.~\ref{fig:separations}).% The collection of low-separation pairs in \textit{Illustris-Dark} that do not have counterparts in \textit{Illustris-Hydro} also had very low velocities, thus accounting for the difference between the dark and hydro simulations.
-%   \kc{can include line for LMC+SMC, MW+M31 (120 Van der marel from HST), M31+M33 and the meanings behind them.
+% %   \kc{can include line for LMC+SMC, MW+M31 (120 Van der marel from HST), M31+M33 and the meanings behind them.
 (MW+LMC is up at 320 and is at peri so this makes sense.) also need to talk about the low separation without the abundance matching bit}
-}
-\end{figure*}
+% }
+% \end{figure*}
 

### 2022-11-03 pears/utils/abundance_matching.py
adding few months worth of progress

@@ -23,6 +23,7 @@ __status__ = "Beta - forever~"
 __date__   = "May 2019 - edited Oct. 2021"
 
 from numpy.random import normal
+from numpy import where
 
 class AbundanceMatching:
     def __init__(self, maxmass, redshift, samples):
@@ -92,14 +93,16 @@ class AbundanceMatching:
         gamma11 = self.getvals(self.gamma11vec, med)
     
         logM = self.func(M10, M11)
-        N = self.func(N10, N11)
+        Nany = self.func(N10, N11)
+        Nmed = self.func( self.getvals(self.N10vec, "True"), self.getvals(self.N11vec, "True") )
+        Npos = where(Nany < 0, Nmed, Nany)
         beta = self.func(beta10, beta11)
         gamma = self.func(gamma10, gamma11)
 
         M1 = 10**logM
         A = (self.maxmass/M1)**(-beta)
         B = (self.maxmass/M1)**(gamma)
-        SHMratio = 2*N*(A+B)**-1
+        SHMratio = 2*Npos*(A+B)**-1
         return SHMratio
 
     def stellar_mass(self,med=False):

### 2022-11-03 pears/utils/get_groups.py

@@ -63,7 +63,7 @@ class GetGroups:
 
         elif self.size == "massive":
             self.group_min = 100
-            self.group_max = 400
+            self.group_max = 650
 
         self.group_min = self.kwargs.pop("group_mass_min", self.group_min)
         self.group_max = self.kwargs.pop("group_mass_max", self.group_max)
@@ -73,12 +73,14 @@ class GetGroups:
 
         elif self.sim == "TNG":
             self.little_h = 0.6774
+
         
         ReadCats.__init__(
             self, 
             snapshot=self.snapshot, 
             sim=self.sim, 
-            physics=self.physics
+            physics=self.physics,
+            **self.kwargs
             )
         self.scale = 1/(1+self.redshift)
 

### 2022-11-03 pears/utils/get_summary_data.py

@@ -1,0 +1,253 @@
+""" 
+Dependencies:
+-------------
+
+"""
+__author__ = "Katie Chamberlain"
+__status__ = "Beta - forever~"
+__date__   = "July 2022"
+
+import sys
+import h5py
+import numpy as np
+from utils.paths import SetupPaths
+
+paths = SetupPaths()
+  
+    
+class compile_summary:
+    
+    def __init__(
+        self,
+        sim="Illustris", 
+        phys="dark",
+        size="dwarf",
+        subset="major",
+        **kwargs
+        ):
+    
+        """
+        Collects the 
+
+        Parameters:
+        -----------
+        sim: str
+            "Illustris" or "TNG"
+            to specify which simulation
+        physics: str
+            "dark" or "hydro"
+            to specify which simulation
+        size: str
+            "dwarf" or "massive"
+        subset: str
+            to specify the subset
+            choose from: major, minor, all
+        """
+        
+        self.sim = sim
+        self.phys = phys
+        self.size = size
+        self.subset = subset
+        self.kwargs = kwargs
+        self.redcutoff = self.kwargs.pop("redshift_cutoff", 1000)
+        
+
+    def get_data(self):
+        
+        summarydata = {"Redshift":[],
+                            "Snapshot":[],
+                            "Number pairs":[],
+                            "Number primaries":[],
+                            "Ratio pairs":[],
+                            "Median Separation": [],
+                            "Median Separation Quartiles": [],
+                            "Mean Separation": [],
+                            "Mean Separation Std": [],
+                            "Median RelVel": [],
+                            "Median RelVel Quartiles": [],
+                            "Mean RelVel": [],
+                            "Mean RelVel Std": [],
+                            "Mean Lowsep Counts": [],
+                            "Mean Lowsep Counts Std": []}
+        
+        self.snapshots = {"Illustris":np.arange(0,136), 
+                     "TNG":np.arange(0,100)}
+        
+        for snapshot in self.snapshots[self.sim]:
+            pair_path = f"{self.sim}_{snapshot}_10.hdf5"
+            pair_data = h5py.File(f"{paths.path_pairs}{pair_path}", "r")
+            
+      
+
+            try:
+                data = pair_data[self.phys]
+                red_coor = pair_data['Header'].attrs['Redshift']
+
+            except KeyError:
+                print(f"{snapshot} does not exist -- skipping")
+
+            else:
+                if red_coor < self.redcutoff:
+                    med_mask = np.array(data["Realization"]) == -1
+
[…]

### 2022-11-03 pears/utils/make_am_realizations.py

@@ -58,7 +58,7 @@ for ind in range(len( subhalo_data[list(subhalo_data.keys())[0]] )):
     else:
         stars = AbundanceMatching(maxmass=halo_maxmass*1e10, 
                                 redshift=redshift,
-                                samples=num_reals).stellar_mass()[0]
+                                samples=num_reals).stellar_mass()
         medstar = AbundanceMatching(maxmass=halo_maxmass*1e10, 
                                     redshift=redshift,
                                     samples=1).stellar_mass(med=True)

### 2022-11-03 pears/utils/make_max_mass_file.py

@@ -29,7 +29,7 @@ elif sim == "TNG":
     little_h = 0.6774
 
 kwargs = {"group_mass_min": 8,
-          "group_mass_max": 500,
+          "group_mass_max": 650,
           "little_h": little_h}
 
 for phys in ["hydro","dark"]:

### 2022-11-03 pears/utils/make_pairs.py

@@ -1,0 +1,293 @@
+'''
+This script uses sorts through the catalog of subhalos to find pairs for the 
+this realization of AM masses
+'''
+import sys
+import h5py
+import numpy as np
+from utils.get_groups import GetGroups
+from utils.paths import SetupPaths
+from vectorCorrection import vectorCorrection as vector
+
+snapshot = int(sys.argv[1])
+sim = str(sys.argv[2])
+num_reals = int(sys.argv[3])
+
+realNumbs = np.arange(-1,num_reals+1,1)
+paths = SetupPaths()
+
+## find subhalos for this simulation and snapshot #
+subhalo_path = f"{sim}_{snapshot}.hdf5"
+subhalo_data = h5py.File(f"{paths.path_subhalos}{subhalo_path}", "r")
+
+savepath = f"{sim}_{snapshot}_10.hdf5"
+f = h5py.File(f"{paths.path_pairs}{savepath}", 'w')
+
+redshift = subhalo_data["Header"].attrs["Redshift"]
+scale = 1 / (1 + redshift)
+
+units_dict = {
+    "Group ID":"Group Number in Subfind Catalogs", 
+    "Group Mass":"Physical mass from Group_M_TopHat200 -- 1e10 Msun",
+    "Group Radius":"Physical radius from Group_R_TopHat200 -- kpc",
+    "Group Nsubs":"Number of subhalos in group",
+    "Sub1 ID":  "Subhalo ID at current snapshot",
+    "Sub2 ID":  "Subhalo ID at current snapshot",
+    "Sub1 Mass": "Subhalo mass at current snapshot -- 1e10 Msun",
+    "Sub2 Mass": "Subhalo mass at current snapshot -- 1e10 Msun",
+    "Sub1 Stellar Mass": "Stellar masses from abundance matching -- 1e10 Msun",
+    "Sub2 Stellar Mass": "Stellar masses from abundance matching -- 1e10 Msun",
+    "Sub1 Pos": "Subhalo physical position in box x,y,z -- kpc",
+    "Sub2 Pos": "Subhalo physical position in box x,y,z -- kpc",
+    "Sub1 Vel": "Subhalo velocity in vx, vy, vz -- km/s",
+    "Sub2 Vel": "Subhalo velocity in vx, vy, vz -- km/s",
+    "Sub1 MassType": "Mass of bound particles - gas, DM, empty, tracers, stars, BHs -- in 1e10 Msun",
[…]

### 2022-11-03 pears/utils/make_pairs_sizespecific.py

@@ -1,0 +1,193 @@
+'''
+This script uses sorts through the catalog of subhalos to find pairs for the 
+this realization of AM masses
+'''
+import sys
+import h5py
+import numpy as np
+from utils.get_groups import GetGroups
+from utils.paths import SetupPaths
+from vectorCorrection import vectorCorrection as vector
+
+snapshot = int(sys.argv[1])
+sim = str(sys.argv[2])
+num_reals = int(sys.argv[3])
+
+# snapshot = int(135)
+# sim = str("Illustris")
+# num_reals = int(sys.argv[4])
+
+paths = SetupPaths()
+
+## find subhalos for this simulation and snapshot #
+subhalo_path = f"{sim}_{snapshot}.hdf5"
+subhalo_data = h5py.File(f"{paths.path_subhalos}{subhalo_path}", "r")
+
+savepath = f"{sim}_{snapshot}_10.hdf5"
+f = h5py.File(f"{paths.path_pairs}{savepath}", 'w')
+
+redshift = subhalo_data["Header"].attrs["Redshift"]
+scale = 1 / (1 + redshift)
+
+units_dict = {
+    "Group ID":"Group Number in Subfind Catalogs", 
+    "Group Mass":"Physical mass from Group_M_TopHat200 -- 1e10 Msun",
+    "Group Radius":"Physical radius from Group_R_TopHat200 -- kpc",
+    "Group Nsubs":"Number of subhalos in group",
+    "Sub1 ID":  "Subhalo ID at current snapshot",
+    "Sub2 ID":  "Subhalo ID at current snapshot",
+    "Sub1 Mass": "Subhalo mass at current snapshot -- 1e10 Msun",
+    "Sub2 Mass": "Subhalo mass at current snapshot -- 1e10 Msun",
+    "Sub1 Stellar Mass": "Stellar masses from abundance matching -- 1e10 Msun",
+    "Sub2 Stellar Mass": "Stellar masses from abundance matching -- 1e10 Msun",
+    "Sub1 Pos": "Subhalo physical position in box x,y,z -- kpc",
+    "Sub2 Pos": "Subhalo physical position in box x,y,z -- kpc",
+    "Sub1 Vel": "Subhalo velocity in vx, vy, vz -- km/s",
+    "Sub2 Vel": "Subhalo velocity in vx, vy, vz -- km/s",
+    "Separation": "Physical separation between primary and secondary in kpc",
+    "RelVel": "Relative velocity between primary and secondary in km/s",
[…]

### 2022-11-03 pears/utils/make_pairs_summary.py

@@ -1,0 +1,293 @@
+'''
+This script reads in all of the pair data and creates summary statistics for the data
+'''
+
+import sys
+import h5py
+import numpy as np
+from utils.paths import SetupPaths
+
+paths = SetupPaths()
+
+savepath = f"summarydata.hdf5"
+f = h5py.File(f"{paths.path_pairs}{savepath}", 'w')
+f.close()
+
+# for sim in ["Illustris","TNG"]:
+sim = "Illustris" # for now
+numsnaps = {"Illustris":135,"TNG":99}
+
+# for phys in ["dark","hydro"]:
+phys = "dark"
+
+# for size in ["dwarf","massive"]:
+size = "dwarf"
+
+
+
+# begin collecting summary statistics
+######
+
+for snapshot in np.arange(0,numsnaps[sim]+1):
+    pair_path = f"{sim}_{snapshot}.hdf5"
+    pair_data = h5py.File(f"{paths.path_pairs}{pair_path}", "r")
+    
+    try: 
+        pairs_subset = pair_data[phys][size] # pairs e.g. in Illustris dark, dwarf or massive
+        
+        primstells = np.array(pairs_subset["Sub1 Stellar Mass"])
+        
+        med = np.array(pairs_subset["Realization"]) == -1
+        
+        # primary stellar mass will be different for dwarf and massive pairs!~
+        if size == "dwarf":
+            primary_analog = (primstells > 0.01) & (primstells < 0.5)
+        elif size == "massive":
+            primary_analog = (primstells > 0.5) & (primstells < 2.5)
+            
+        allprim = primary_analog
+        
+        # masks on mass ratio
+        big = np.array(pairs_subset["Stellar Mass Ratio"]) > 1/4
+        small = np.array(pairs_subset["Stellar Mass Ratio"]) > 1/10
+        major = primary_analog & big 
+        minor = primary_analog & ~big & small
+        
+        # masks on separation
+        lowsep = np.array(pairs_subset["Separation"]) <= 50
+        highsep = np.array(pairs_subset["Separation"]) > 50
+        close = primary_analog & lowsep
+        far = primary_analog & highsep
+        
+        # for subset in ["all","major","minor"]:
+        subset = "median"
+        
+        summary_dict[subset] = {"Redshift":[],
+                                "Median Separation": [],
+                                "Median Separation Quartiles": [],
+                                "Mean Separation": [],
+                                "Mean Separation Std": [],
+                                "Median RelVel": [],
[…]

### 2022-11-03 pears/utils/make_subhalos.py

@@ -20,10 +20,46 @@ sim = str(sys.argv[2])
 savepath = f"{sim}_{snap}.hdf5"
 f = h5py.File(f"{paths.path_subhalos}{savepath}", 'w')
 
+# list of all kwargs, note that dark sims will not have last 5 fields
+keysel_list = ['GroupPos','Group_M_TopHat200', 
+            'Group_R_TopHat200','GroupNsubs',
+            'GroupFirstSub',
+            'SubhaloGrNr','SubhaloMass',
+            'SubhaloPos','SubhaloVel' ,
+            'SubhaloBHMass','SubhaloBHMdot',
+            'SubhaloSFR','SubhaloSFRinRad',
+            'SubhaloGasMetallicity','SubhaloMassType']
+
+kwargs = {"group_mass_min": 8,
+          "group_mass_max": 650,
+          "keysel":keysel_list} 
+
+base_units = {
+            "Group ID":"Group Number in Subfind Catalogs", 
+            "Group Mass":"Physical mass from Group_M_TopHat200 -- 1e10 Msun", 
+            "Group Radius":"Physical radius from Group_R_TopHat200 -- kpc", 
+            "Nsubs":"Number of subhalos in group",
+            "Subhalo ID": "Subhalo ID at current snapshot",
+            "Subhalo Mass": "Subhalo mass at current snapshot -- 1e10 Msun",
+            "Subhalo Pos":"Subhalo physical position in box x,y,z -- kpc",
+            "Subhalo Vel":"Subhalo velocity in vx, vy, vz -- km/s",
+            "Subhalo Max Mass": "Maximum mass ever achieved by the subhalo -- 1e10 Msun",
+            "Subhalo Max Mass Snap": "Snapshot at which maximum halo mass is achieved",
+            "Subhalo Stellar Masses": "Stellar masses from abundance matching -- 1e10 Msun",
+            "Subhalo Med Stellar Mass":"Median stellar mass from abundance matching -- 1e10 Msun",
+            "SubhaloMassType": "Mass of bound particles - gas, DM, empty, tracers, stars, BHs -- in 1e10 Msun"
+            }
+
+hydro_units = {
+            "SubhaloBHMass": "Sum of the masses of all blackholes in this subhalo -- 1e10 Msun",
+            "SubhaloBHMdot": "Instantaneous accretion rates of all blackholes in subhalo -- 1e10 Msun / 0.978Gyr",
[…]

### 2022-11-03 pears/utils/make_subhalos_sizespecific.py

@@ -1,0 +1,155 @@
+'''
+This script uses the get_groups class to save the properties of all subhalos
+in the groups of interest!
+'''
+
+import h5py
+import numpy as np
+import sys
+from utils.get_groups import GetGroups
+from utils.paths import SetupPaths
+
+paths = SetupPaths()
+
+# snaps = {}
+
+snap = int(sys.argv[1])
+sim = str(sys.argv[2])
+
+#create the hdf5 file!
+savepath = f"{sim}_{snap}.hdf5"
+f = h5py.File(f"{paths.path_subhalos}{savepath}", 'w')
+
+# list of all kwargs, note that dark sims will not have last 5 fields
+kwargs = {"keysel":['GroupPos','Group_M_TopHat200', 
+            'Group_R_TopHat200','GroupNsubs',
+            'GroupFirstSub',
+            'SubhaloGrNr','SubhaloMass',
+            'SubhaloPos','SubhaloVel' ,
+            'SubhaloBHMass','SubhaloBHMdot',
+            'SubhaloSFR','SubhaloSFRinRad',
+            'SubhaloGasMetallicity','SubhaloMassType']} 
+
+base_units = {
+            "Group ID":"Group Number in Subfind Catalogs", 
+            "Group Mass":"Physical mass from Group_M_TopHat200 -- 1e10 Msun", 
+            "Group Radius":"Physical radius from Group_R_TopHat200 -- kpc", 
+            "Nsubs":"Number of subhalos in group",
+            "Subhalo ID": "Subhalo ID at current snapshot",
+            "Subhalo Mass": "Subhalo mass at current snapshot -- 1e10 Msun",
+            "Subhalo Pos":"Subhalo physical position in box x,y,z -- kpc",
+            "Subhalo Vel":"Subhalo velocity in vx, vy, vz -- km/s",
+            "Subhalo Max Mass": "Maximum mass ever achieved by the subhalo -- 1e10 Msun",
+            "Subhalo Max Mass Snap": "Snapshot at which maximum halo mass is achieved",
+            "Subhalo Stellar Masses": "Stellar masses from abundance matching -- 1e10 Msun",
+            "Subhalo Med Stellar Mass":"Median stellar mass from abundance matching -- 1e10 Msun",
+            "SubhaloMassType": "Mass of bound particles - gas, DM, empty, tracers, stars, BHs -- in 1e10 Msun"
+            }
+
+hydro_units = {
[…]

### 2022-11-03 pears/utils/read_group_cats.py

@@ -25,7 +25,8 @@ class ReadCats:
         self,
         snapshot,
         sim = "Illustris",
-        physics ="dark"
+        physics ="dark",
+        **kwargs,
         ):
         """
         Reads group catalog for correct simulation and physics
@@ -34,17 +35,12 @@ class ReadCats:
         ----------
         snapshot: int
             the number of the snapshot with the corresponding subhalo ID
-        subfindID: int
-            the ID number of the subhalo at the corresponding snapshot
         sim: str
             "Illustris" or "TNG"
             to specify which simulation
         physics: str
             "dark" or "hydro"
             to specify which simulation
-        kwargs: dict
-            little_h: float
-                definition of little h, default h=0.702
 
         Outputs:
         --------
@@ -55,6 +51,17 @@ class ReadCats:
         self.snapshot = snapshot 
         self.sim = sim
         self.physics = physics
+        self.kwargs = kwargs
+        
+        
+        self.keysel_default =  [
+            'GroupPos','Group_M_TopHat200', 
+            'Group_R_TopHat200','GroupNsubs',
+            'GroupFirstSub',
+            'SubhaloGrNr','SubhaloMass',
+            'SubhaloPos','SubhaloVel' ]
+        
+        self.keysel = self.kwargs.pop("keysel", self.keysel_default)
 
         SetupPaths.__init__(self)
         
@@ -81,20 +88,15 @@ class ReadCats:
             raise AttributeError("Unrecognized simulation type: \
                   Failed to construct path to catalog")
 
-        keysel = [
-            'GroupPos','Group_M_TopHat200', 
-            'Group_R_TopHat200','GroupNsubs',
-            'GroupFirstSub',
-            'SubhaloGrNr','SubhaloMass',
-            'SubhaloPos','SubhaloVel'
-            ]
 
         self.catalog = readSub.subfind_catalog(
             basedir=self.catpath,
             snapnum=self.snapshot,
-            keysel=keysel
+            keysel=self.keysel
             )
-
+        
+        
+        # note if keysel does not include at least all of these, will throw error
         self.groupPos = self.catalog.GroupPos
         self.mvirs = self.catalog.Group_M_TopHat200
         self.rvirs = self.catalog.Group_R_TopHat200

### 2022-11-03 pears/utils/testinputs.py

@@ -1,0 +1,23 @@
+__author__ = "Katie Chamberlain"
+__status__ = "Beta - forever~"
+__date__   = "September 2021"
+
+import numpy as np
+from utils.read_group_cats import ReadCats
+from utils.merger_trees import TraceMergerTree
+from utils.get_groups import GetGroups
+from utils.paths import SetupPaths
+
+import sys
+# from astropy.table import QTable
+# import astropy.units as u
+
+snap = int(sys.argv[1])
+simulation = str(sys.argv[2])
+
+print(snap)
+print(simulation)
+print(type(snap))
+print(type(simulation))
+
+print(simulation=="Illustris")

### 2022-11-04 paper/pears.tex
i promise i changed something
pls compile?
paper template w light outlining

@@
-\documentclass[twocolumn]{aastex63}
+\documentclass[twocolumn]{aastex631}
 
-\newcommand\aastex{AAS\TeX}
-\newcommand\latex{La\TeX}
-\newcommand\msun{\rm{M}_{\odot}}
-\newcommand\ID{\textit{Illustris-Dark}}
-\newcommand\IH{\textit{Illustris-Hydro}}
-\newcommand\SUBFIND{\texttt{SUBFIND}}
-\definecolor{mypink}{RGB}{232,132,161}
-\newcommand{\kc}[1]{\textcolor{mypink}{\textbf{#1}} }
-\newcommand{\gb}[1]{\textcolor{olive}{\textbf{#1}} }
-%\newcolumntype{H}{>{\setbox0=\hbox\bgroup}c<{\egroup}@{}}
-%\usepackage{subcaption}
-\usepackage{nicefrac}
-\usepackage{soul}
-% \usepackage{amssymb}
+% Packages
+\usepackage{microtype}  % ALWAYS!
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{multirow}
 
-% \graphicspath{{./}{figures/}}
-% \graphicspath{{../}{figures/}}
+\definecolor{pink}{RGB}{232,132,161}
+\definecolor{yellow}{RGB}{255,213,0}
 
-% \shorttitle{Sample article}
-% \shortauthors{Schwarz et al.}
+\newcommand{\kc}[1]{\textcolor{yellow}{\textbf{kc: #1}} }
+% \newcommand{\ecite}[1]{\textcolor{pink}{\textbf{: #1}} }
+% \newcommand{\e}[1]{\textcolor{yellow}{\textbf{: #1}} }
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand{\remove}[1]{\textcolor{red}{#1}}
+\newcommand{\add}[1]{\textcolor{green}{#1}}
+
+\newcommand{\mlg}{\ensuremath{M_{\rm LG}}}
+\newcommand{\mmto}{\ensuremath{M_{\rm M31}}}
+\newcommand{\mmw}{\ensuremath{M_{\rm MW}}}
+\newcommand{\vtan}{\ensuremath{v_\textrm{tan}}}
+\newcommand{\vrad}{\ensuremath{v_\textrm{rad}}}
+\newcommand{\mud}{\ensuremath{\mu_\delta}}
+\newcommand{\mua}{\ensuremath{\mu_\alpha^*}}
+\newcommand{\bov}{\ensuremath{\boldsymbol{v}}}
+\newcommand{\boldx}{\ensuremath{\boldsymbol{x}}}
+\newcommand{\vtrav}{\ensuremath{\bov_{\rm travel}}}
+\newcommand{\xtrav}{\ensuremath{\boldx_{\rm travel}}}
+\newcommand{\pos}[2]{\ensuremath{\boldx_{\rm #1 \to #2}}}
+\newcommand{\vel}[2]{\ensuremath{\bov_{\rm #1 \to #2}}}
+\newcommand{\mwbary}{\ensuremath{\textrm{MW}_\textrm{bary}}}
+\newcommand{\mwouter}{\ensuremath{\textrm{MW}_\textrm{halo}}}
+\newcommand{\mwdisk}{\ensuremath{\textrm{MW}_\textrm{disk}}}
+\newcommand{\reflabel}[1]{\ensuremath{^{\mbox{\scriptsize{#1}}}}}
+
+% Style tweaks
+% \renewcommand{\twocolumngrid}{\onecolumngrid}
+% \setlength{\parindent}{1.1\baselineskip}
+% \sloppy\sloppypar\raggedbottom\frenchspacing
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\shorttitle{Frequency of galaxy pairs}
+\shortauthors{Chamberlain et al.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\graphicspath{{./}{figures/}}
+\input{math_definitions.tex}
+
+% Affiliations
+\newcommand{\affuofa}{University of Arizona, 933 N. Cherry Ave,
+    Tucson, AZ 85721, USA}
+
+%% This is the end of the preamble.  Indicate the beginning of the
+%% manuscript itself with \begin{document}.
+
 \begin{document}
 
-\title{Occurance rate of galaxy pairs across cosmic time:\\ Local Group analogs in a cosmological context}
-\correspondingauthor{Katie Chamberlain}
-\email{katiechambe@email.arizona.edu}
+\title{
+  Frequency of galaxy pairs in the Illustris and Illustris TNG cosmological simulations
+}
 
-\author[0000-0001-8765-8670]{Katie Chamberlain}
-\affil{Steward Observatory, University of Arizona\\
-933 North Cherry Avenue\\
-Tucson, AZ, 85721, USA}
-\author{Gurtina Besla}
-\affil{Steward Observatory, University of Arizona\\
-933 North Cherry Avenue\\
-Tucson, AZ, 85721, USA}
+\author[0000-0001-8765-8670]{Katie~Chamberlain}
+\affiliation{\affuofa}
+
+\author[0000-0003-0715-2173]{Gurtina Besla}
+\affiliation{\affuofa}
+
 \begin{abstract}
-
-  % \textbf{Context} 
-  Dwarf galaxies are extremely common at all redshifts and often exhibit morphological disturbances that do not primarily result from galaxy mergers.
-As such, pair fractions, rather than morphological indicators (asymmetry, concentration) are needed to infer dwarf galaxy  merger rates from observational surveys.
-  However, in contrast to massive galaxies ($5\times 10^9\leq$ $\rm M_{prim,*} \leq 1\times 10^{11} \msun$), pair fractions for dwarf galaxies ($10^8 < \rm M_* < 5 \times 10^9 \msun$) have been theoretically constrained only at low redshift.
-  % \\\textbf{Aims}
-  We aim to quantify the occurence rates and kinematics of isolated dwarf and massive galaxy pairs from $z=0-4$ in the Illustris and IllustrisTNG cosmological simulations.
-  % \\\textbf{Methods} 
-  Dwarf and massive subhalo pairs are identified in each snapshot of the Illustris \texttt{SUBFIND} catalogs. 
-  % \\\textbf{Results} 
-  We find that roughly 8-10\% of dwarf galaxies will have major companion (stellar mass ratio $>1:4$) at $z=0$, increasing steadily before plateauing in \ID(\IH) at 16\%(12\%) by $z\sim 2$.
-The occurence rate of dwarf galaxies with minor companions (stellar mass ratios between $1:10$ and $1:4$) is roughly constant at $\sim 2.5\%$ from $z=1-4$.
-In contrast, the occurence rate of major and minor massive galaxy pairs remains approximately constant across time, as massive galaxies have a major (minor) companion $\sim18\%$ ($\sim14\%$) of the time.
-  % \\\textbf{Conclusions} 
-  This suggests that the hierarchical evolution of dwarf galaxies may proceed differently than that of massive galaxies.
-LMC-SMC mass analogs (dwarf minor pairs) are twice as common at redshifts greater than 2, but the present day LMC-SMC system is dynamically rare at all redshifts (in terms of pair separation and velocity).
-The M31-M33 pair is dynamically typical of massive minor pairs at $z\approx0$, while the MW-LMC has unusually high velocities and low relative separations for a major massive pair at low redshift.
-Baryonic physics impacts the occurence rate of galaxy pairs and systematically changes the kinematics of dwarf pairs, suggesting observations of dwarf galaxy pairs can be used to test subgrid physics in cosmological simulations.
-
 \end{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction} \label{sec:intro}
-%%%%%%%%%%%%%%%%%%%%%%
-Galaxy mergers are responsible for many physical processes that shape galactic evolution, including triggered star formation~\citep{mihos96, hopkins13, patton20,hani20}, increased AGN activity~\citep{hopkins08,comerford15,ellison19}, and galaxy morphology~\citep[e.g.,][]{rg17}.
-Dwarf galaxies  make up a majority of the galaxy population at all redshifts (REF) and are also expected to undergo interactions and merge.
-Such processes may be important to understand the growth and evolution of intermediate mass black holes, which are often found to be ``wandering" in low mass galaxy hosts~\citep{stemo20,reines20}.
-Despite the ubiquity of dwarf galaxies in the universe, we do not have a clear path to constrain the merger rates of these systems observationally or to place known interacting dwarf galaxy systems (stellar mass $1\times10^8<M_* < 5\times10^9\msun$) in a cosmological context.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+\label{sec:intro}
 
-Massive galaxy ($M_* > 5\times10^9\msun$) mergers and interactions can be observationally identified using methods like asymmetry and concentration measures~\citep{conselice2000, lotz04}.
-Numerous studies have used these measures to study the merger and interaction rates of massive galaxies as a function of time~\citep[e.g.,][]{lotz11,casteels14}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Methods}
+\label{sec:methods}
+\begin{itemize}
+  \item Introduce simulations
+  \item outline selection steps
+  \item dwarf pairs
+  \item massive pairs
+  \item include table with parameters used for pairs
+  \item plots
+    \begin{itemize}
+      \item distribution plots
+      \item counts plots
+    \end{itemize}
+\end{itemize}
 
-However, \citet{martin21} showed that mergers only account for 10\% of morphological disturbances in dwarfs, and that a majority of their morphological disturbances derive from non-merger interactions, such as gas inflows/outflows, close passages, and fly-bys.
-This means that the typical methods of classifying interactions and mergers for massive galaxies are unlikely to be robust in lower mass regimes.
-This is particularly true at high redshift, when gas accretion along filaments is expected to be more significant~\citep{keres09}.
-Thus, it is critical to establish an alternative, cosmologically consistent, way to determine merger and interaction rates for dwarf galaxy pairs from observations.
-
-Another observational technique to determine merger/interaction rates relies upon the pair fraction: the ratio of the number of host galaxies with a companion to the number of potential hosts.
-Pair fractions for massive galaxies have been measured observationally as a function of time~\citep[e.g.,][]{lotz08,conselice09}, and calibrated against theoretical simulations to determine observability timescales that enable the translation of pair fractions to merger rates \citep{lotz11,kaviraj15,snyder17,qu17,oleary21b}.
-In contrast, pair fractions for dwarf primaries are only starting to be measured at high redshift \citep[e.g.][]{ventou17} and have only been studied with small sample size or calibrated against simulations at low redshift \citep{besla18, casteels14,stierwalt15, pearson18}.
-Thus we are currently missing a theoretical framework to interpret future high redshift observations of dwarf pairs, i.e.
-with \textit{JWST}.
-In this study, we quantify the dwarf galaxy pair fraction as a function of time out to $z\sim$4, and compare these results to the massive galaxy pair fraction, using the N-body and hydrodynamic \textit{Illustris-1} cosmological simulations~\citep{vogelsberger14A,nelson15}.
-
-There are examples of galaxy pairs involving dwarf galaxies in our Local Group, including the M31-M33, MW-LMC, and the LMC-SMC (Magellanic Clouds; MCs) systems.
-The frequency of such pairs have been studied extensively observationally and theoretically at low redshift.
-In SDSS DR7, it is found that 11\% of MW/M31-like objects have one massive satellite (LMC/M33 analog) within 150 kpc and 300 km s$^{-1}$~\citep{liu11}.
-Within 250 kpc, the frequency increases to 42\% (Tollerud 2011).
-% , robotham12
-This is in agreement with $\Lambda$CDM predictions \citep{busha11, bk11, patel17a, gonzalez13}. 
-% check gonzalez
-Furthermore, 4-6\% of LMC/M33 analogs in both SDSS and cosmological simulations are expected to have a companion at least as massive as an SMC in the field \citep{besla18, sales11}.
-%% ADD SALES RESULTS ?
-% add how defined here
-
-However, we do not how common these pair configurations are as a function of time in the $\Lambda$CDM framework, leaving open the question as to whether our Local Group is unique in time. 
-Recent advances in astrometry have furthermore enabled the measurement of 6D phase space information for these Local Group galaxy pairs.  
-In this study, we will examine whether not only the frequency, but also the dynamics of pairs in our Local Group are unique \textit{across cosmic time}.
-% HOW DO MASSIVE PAIRS SCALE TO DWARF REGIME
-
-The Local Group also contains a massive major galaxy pair (stellar mass ratio $>$1:4), the MW-M31.
-For low redshift (z$<$ $\sim$.1) massive galaxies (M$_\ast > 10^{10}$ M$_\odot$), the fraction of major pairs are expected to increase as a function of mass \citep{casteels14}, resulting in major merger rates that rise  with higher mass~\citep{rg15,ventou17,oleary21b}.
-Additionally, the fraction of major pairs is also measured to increase with increasing redshift~\citep{deravel09,bundy09,duncan19}.
-In particular \citet{duncan19} find no strong evolution in the relative number of minor to major mergers for massive hosts out to z$<$3.
-But it is unclear whether these trends for the frequency of major pairs will be the same if the host mass is in the dwarf galaxy regime.
-
-It is important to study the dwarf and massive host regimes separately, as baryonic physics, including gravitational tides, star formation, and outflows, impacts the growth of dwarf galaxies more strongly~\citep{bullockbk17,jeon19,jeon21}.
-For example, it has been shown that baryonic physics implemented in the \IH\ simulation suppresses the abundance of low mass subhalos ($\leq$10$^{10}\msun$), but such a suppression is not present for massive halos~\citep{chua17}.
-Thus, the pair fractions and dynamics of dwarf major and minor pairs may change drastically between the dark-matter-only and full-physics simulations, with less differences for massive  pairs.
-In this study, we illustrate that the impact of baryonic physics on the growth of low mass halos in cosmological simulations may be directly testable with pair fraction observations.
-
-Here we present the first cosmologically motivated constraints on the dwarf pair fraction for major and minor pairs as a function of time.
-We compare these results to those found for massive major and minor pairs, and address the differences in expected pair fractions between the N-body and full hydrodynamic simulations.
-This work will furthermore, self-consistently, place known galaxy pairs in our Local Group in a cosmological and temporal context.
-In Sec.~\ref{sec:methods}, we introduce the simulations and selection criteria used to perform the analysis of our sample of pairs.
-In Sec.~\ref{sec:results}, we present the results of this pair fraction study, including preliminary results on the kinematics of dwarf pairs over cosmic time.
-In Sec.~\ref{sec:discussion}, we discuss the implications of our results on interpretations of future surveys, and what this could mean for constraints of feedback mechanisms in cosmological simulations.
-In Sec.~\ref{sec:conclusions} we present a summary of the main conclusions of this work, including expected pair fractions for dwarf and massive galaxy pairs.
-
-%%%%%%%%%%%%%%%%%
-\section{Sample Selection} \label{sec:methods}
-%%%%%%%%%%%%%%%%%
-Our sample of dwarf galaxy pairs and massive galaxy pairs from cosmological simulations was chosen following a strict set of selection criteria.
-In Sec.~\ref{sec:simData} we will detail the simulations from which we collected our data, Sec.~\ref{sec:abundanceMatching} explains the abundance matching prescription used to associate dark matter halos with stellar masses, and Sec.~\ref{sec:selectionCrit} outlines the isolation and mass criteria used to identify our sample.
-
-\subsection{Simulation data}\label{sec:simData}
-We utilize data from the \textit{Illustris Project} ~\citep{vogelsberger14A,nelson15}, a set of N-body and hydrodynamic cosmological simulations, to statistically analyse the occurrence rates of dwarf and massive dark matter subhalo pairs over cosmic time.
-In particular, we are using the highest resolution dark matter only simulation, \textit{Illustris-1-Dark}, and the  full hydrodynamic simulation, \textit{Illustris-1} (hereafter \textit{Illustris-Dark} and \textit{Illustris-Hydro} respectively, see Table~\ref{table:illustris}).
-Each of these simulations follows the dynamical evolution of $1820^3$ dark matter particles from $z=127$ to $z=0$ through a periodic volume of $106.5^3$ Mpc$^3$.
-The Illustris simulations use a cosmology that is consistent with \textit{WMAP-9} ~\citep{hinshaw13}: $\Omega_m = 0.2726$, $\Omega_\Lambda = 0.7274$, $\Omega_b = 0.0456$, $\sigma_8 = 0.809$, $n_s=0.963$, and $h=0.704$.
-
-% Maybe doesn't need whole paragraph but, about dark vs. hydro
-We are utilizing data from both \textit{Illustris-Dark} and \textit{Illustris-Hydro} to study the effect of baryonic content on the subhalos.
-As dwarf subhalos have more shallow dark matter potentials than their more massive counterparts, they are more likely to be subject to disruption caused by baryonic feedback at higher redshifts, which may result in fewer low mass subhalo pairs in \textit{Illustris-Hydro}.
-
-% Subfind paragraph: 
-We use catalogs of dark matter halos and their associated subhalos identified in each simulation using the \texttt{SUBFIND} algorithm ~\citep{springel01,dolag09}.
-Dark matter halos were identified using the Friends-of-Friends (FoF) algorithm ~\citep{davis85}, which links particles that have separations less than $0.2d$, where $d$ is the mean inter-particle separation.
-Each FoF group, which we will further refer to as a ``group", was further divided into over-dense and gravitationally bound dark matter subhalos.
-
-% Sublink paragraph:
-In order to trace the growth and histories of our subhalos, we are using the merger trees provided by the \texttt{SUBLINK} algorithm \citep{gomez15}, which tracks subhalos between snapshots using their particle data.
-These merger trees provide information about the kinematics and mass growth of subhalos in both \textit{Illustris-Dark} and \textit{Illustris-Hydro}, and in particular will be used to provide the maximal masses of each of the subhalos we investigate.
-
-The lower mass threshold for subhalos that constitute our dwarf pairs have a halo mass greater than $1\times10^9\msun$, such that each of our halos are resolved into at least 130 particles in \textit{Illustris-Dark} and 150 particles in \textit{Illustris-Hydro}.
-% \kc{add explanation for why 100 particles is good enough for the resolution we're looking for.}
-
-\begin{table}[htb]
-\begin{tabular}{lll}
- & Illustris-Dark & Illustris-Hydro \\\hline\hline
- L$_{\rm Box}$ [Mpc] & 106.5 & 106.5 \\
-m$_{\rm DM}$ [M$_\odot$] & 7.5$\times10^6$ & 6.3$\times10^6$ \\\hline
-\end{tabular}
-\caption{\label{table:illustris}Parameters of the Illustris simulations used in this analysis.}
-\end{table}
-% when i start using TNG can add this!
-% \begin{table*}[htb]
-% \begin{tabular}{lllll}
-%  & Illustris-Dark & Illustris-Hydro & IllustrisTNG-Dark & IllustrisTNG-Hydro\\\hline\hline
-%  L$_{\rm Box}$ [Mpc] & 106.5 & 106.5 & 110.7 & 110.7 \\
-% m$_{\rm DM}$ [M$_\odot$] & 7.5$\times10^6$ & 6.3$\times10^6$ & 8.9$\times10^6$ & $7.5\times10^6$\\\hline
-% \end{tabular}
-% \caption{Parameters of the Illustris simulations used in this analysis.}
-% \end{table*}
-
+% selection criterion
 \begin{table*}[htb]
@@
     % Subhalo Max Mass &  &  \\
-    Subhalo Current Mass & $>1\times10^{10} \msun$ & $> 5\times10^{11} \msun$ \\
-    Primary &$1\times10^{8} < \rm M_* < 5\times10^{9} \msun$ & $5\times10^{9} < \rm M_* < 1\times10^{11} \msun$\\\hline
+    Subhalo Current Mass & $>1\times10^{10} \Msun$ & $> 5\times10^{11} \Msun$ \\
+    Primary &$1\times10^{8} < \rm M_* < 5\times10^{9} \Msun$ & $5\times10^{9} < \rm M_* < 1\times10^{11} \Msun$\\\hline
     \end{tabular}
@@
 
-\subsection{Abundance matching}\label{sec:abundanceMatching}
-Although \textit{Illustris-Hydro} provides stellar masses for all subhalos, however these reported masses are higher than observations suggest~\citep{genel14}.
-We assign stellar masses to dark matter halos in a consistent way between both \ID\ and \IH using the abundance matching (AM) prescription of \citet{moster13} to associate each dark matter halo with a stellar mass.
+% equivalent snapshot table
+\begin{table}[]
+  \centering
+  \begin{tabular}{l|cc}
+    \hline \hline
+   & Illustris & TNG  \\ 
+  \hline
+  z = 0   &   135  &   99   \\
+  z = 1   &   85   &   50   \\
+  z = 2   &   68   &   33   \\
+  z = 3   &   60   &   25   \\
+  z = 4   &   54   &   21   \\
+  \hline \hline
+  \end{tabular}
+  \caption{\label{tab:equiv-snapshot} The snapshot number of the original \ill\ and the \tng\ simulations at redshifts $z=0-4$.}
+\end{table}
 
-The AM relationship at low stellar masses has a large spread, thus a subhalo with a dark matter halo mass of $10^{11}$ may be associated with a stellar mass anywhere between $1.2\times10^{8} - 5\times10^{9}\rm M_\odot$, as can be seen in Fig.~\ref{fig:abundanceMatching}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+\label{sec:results}
 
-There are two inputs to the AM relationship: dark matter mass and redshift.
-As shown recently by \citet{munshi21}, the relationship between stellar mass and peak halo mass of dwarf subhalos in the Marvel and Justice League simulations is much tighter than the relationship between the stellar mass and halo mass of subhalos at $z=0$.
-We use the maximal dark matter mass of the halo to ensure that the stellar mass associated with each subhalo reflects the shape of the dark matter profile in the inner regions of the subhalo, thus preventing us from assigning very low stellar masses to halos that have been stripped of %a lot of
-their outer dark matter mass by recent interactions.
-We evaluate the AM relation using the redshift of the halo at the snapshot that we are interested in, rather than the redshift of the halo at its maximal mass, in order to account for ongoing star formation past peak halo mass.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
+\label{sec:discussion}
 
-For the collection of subhalos identified at each snapshot of the simulation, the stellar masses are drawn from the gaussian sampled AM relation.
-We thus generate 50 realizations for the stellar mass distribution of the same subhalo population in order to account for uncertainties in the AM relation.
-Each realization is treated as an independent sample of galaxies, where computed properties (stellar masses, relative speeds, etc) are averaged over each realization.
-We report the mean of all realizations and error bars indicate the 1$\sigma$ dispersion across the realizations.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary and Conclusions}
+\label{sec:summary}
 
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/z0.png}
-  \caption{\label{fig:abundanceMatching} Abundance matching relationship of \citet{moster13} at z=0 for dark matter halo masses between $10^{10}$ and $10^{14} \msun$.
-Note that at halo masses below $\sim10^{12} \msun$, there is more spread in stellar mass at fixed halo mass compared to halos with $\rm M_{H} > \sim10^{12} \msun$.
-This effect is illustrated by the vertical lines at $10^{11}\msun$ and $10^{13}\msun$.
-%\gb{might be useful here to indicate with horizontal lines the stellar mass range for the dwarf systems and the massive galaxy systems}
-  }
-\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsection{Selection criteria}\label{sec:selectionCrit}
-In this section, we will outline the selection criteria used to identify dwarf subhalo and massive subhalo pairs in the \ID\ and \IH\ simulations.
-In short, we first make a series of mass cuts on the group mass to constrain the masses of the halos that may be contained in the group and to ensure that the systems are relatively isolated.
-Then, the subhalos of each identified isolated group undergo further mass cuts until we are left with a sample of both dwarf and massive subhalo pairs.
-A summary of the mass criteria used for our selection can be found in Table~\ref{table:mass}.
-
-\subsubsection{Isolation}
-We are interested in the occurrence rates of subhalo pairs in pristine environments to ensure that the dynamics of the subhalos in groups are unaffected by nearby massive perturbers.
-
-FoF groups are large collections of nearby associated particles throughout the Illustris simulation.
-As there is no boundedness criteria for these groups, we wanted to ensure that pulling pairs of subhalos from FoF groups would yield a sample of subhalos that were dynamically unperturbed by more massive nearby structures.
-We calculated the isolation fraction
-\begin{equation}
-f_{\rm iso} = N_{\rm Hill} / N_{\rm FoF}
-\end{equation}
-where $N_{\rm Hill}$ is the number of pairs of subhalos that satisfy the Hill radius criterion (see Appendix~\ref{app:hill}), and $N_{\rm FoF}$ is the number of pairs from FoF groups, and found that $>99.8\%$ of all pairs identified in FoF groups are considered isolated by the more stringent Hill radius criterion.
-We thus used these FoF groups as a proxy for isolation, and considered \textit{all} pairs from FoF groups isolated.
-
-\subsubsection{Group mass cuts}
-% why group cuts
-We first make a series of cuts on the group masses reported in the \ID and \IH catalogs at each snapshot out to $z\sim12$.
-Since we are interested in subhalo pairs in two different mass regimes, we will use different mass criteria to isolate groups that may contain dwarf pairs, and groups that may contain more massive galaxy pairs.
-As mentioned, we do not search for dwarf pairs in massive groups
-since the central subhalos of these more massive groups would perturb the dwarf system.
-
-% actual numerical values of 
-Group mass cuts are performed on the group mass provided in the SUBFIND catalogs, \texttt{Group\_M\_TopHat200}, which is the total mass enclosed in a sphere whose mean density is $\rho_c \Delta_c$.
-The {\bf dwarf groups} must have a group mass $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ while {\bf massive groups} have mass $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$.
-These dwarf and massive group masses are roughly representative of Magellanic Cloud analogs~\citep{besla12,moster13} and Local Group analogs respectively~\citep{vdm12ii}.
-
-In addition to %overall 
-group mass cuts, we ensure that each group has at least one subhalo that satisfies the following properties:
-\begin{itemize}
-    \item \textit{dwarf} - maximal halo mass is $8\times10^{10} < \rm M_{\rm max} < 5\times10^{11} \rm M_\odot$ with mass at the snapshot of interest M$_{\rm snap} > 1\times10^{10} \rm M_\odot$
-    \item \textit{massive} - maximal halo mass is $1\times10^{12} < \rm M_{max} < 4\times10^{12} \rm M_\odot$ with mass at the snapshot of interest M$_{\rm snap} > 5\times10^{11} \rm M_\odot$. 
-\end{itemize}
-This ensures that each group has at least one subhalo that will serve as a primary galaxy for the catalog after stellar mass cuts are applied (Sec.~\ref{sec:primaries}).
-
-We only consider subhalos in each of these groups that have subhalo masses $M_{H}>10^9M_{\odot}$ at the given snapshot.
-This ensures that each dwarf pair will consist of subhalos that are resolved into more than 100 dark matter particles at the snapshot of interest.
-
-In practice we find that some low mass groups consist of a set of subhalos with only one or two subhalos with mass above our lower mass threshold of $10^9\msun$, while the remaining subhalos have lower mass.
-We refer to these types of groups as ``One Subhalo'' and ``Two Subhalo'' groups respectively, since they contain either one or two candidate primaries.
-Groups with three or more subhalos passing this lower mass threshold are called ``Three+ Subhalo'' groups.
-
-\begin{table*}[htb]
-  \begin{center}
-\begin{tabular}{ccccc|cccc}
-    & \multicolumn{4}{c}{Dwarfs} & \multicolumn{4}{c}{Massive} \\\hline\hline
-    z = &0&1&2&4&0&1&2&4 \\ \hline
-    Isolated Groups & \# & \# &\# &\#&\#&\#&\#&\#\\
-Primaries &  & &&&&&& \\
-Pairs &  & &&&&&& \\
-Major Pairs &  & &&&&&& \\
-Minor Pairs &  & &&&&&& \\
-Minor+ Pairs &  & &&&&&& \\\hline
-\end{tabular}
-\end{center}
-\caption{\label{table:counts}\kc{Placeholder for now} Number of groups, primaries, and pairs}
-\end{table*}
-
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_counts.png}
-    \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_counts.png}
-    \caption{\label{fig:counts} The number of dwarf (top) and massive (bottom) groups primaries identified in each of the \textit{Illustris-Dark} and \textit{Illustris-Hydro}.
-The linestyle represents the different types of groups where the primaries are identified.
-The dotted (dashed) lines show the number of primaries in
-    groups with only one (two) subhalo(s) with subhalo mass greater than $10^9 \rm M_\odot$. Dot dashed lines show the number of primaries in 
-    groups with three or more subhalos with a mass greater than $10^9 \rm M_\odot$.
-We find that \textit{Illustris-Hydro} has significantly many more primaries in single and double-subhalo groups, which may be a result of different dwarf merger rates in the two simulations.
-Since there are many more single-subhalo dwarf groups in \textit{Illustris-Hydro}, the fraction of primaries with a companion will be significantly suppressed compared to \textit{Illustris-Dark}.
-    There are almost no massive groups that contain only one or two subhalos that pass our lower subhalo mass threshold, thus nearly 100\% of the identified primaries are in groups with at least 3 massive subhalos.}
-  \end{figure}
-
-\subsubsection{Dwarf and Massive Primaries}\label{sec:primaries}
-Dwarf and massive primaries are defined to be the most massive subhalo in each group with the following properties:
-\begin{itemize}
-  \item \textit{dwarf} - stellar mass between $10^8 \leq \rm M_{prim,*} \leq 5\times 10^9 \msun$
-  \item \textit{massive} - stellar mass between $5\times 10^9 \rm M_{prim,*} \leq 1\times 10^{11} \msun$.
-\end{itemize}
-We make mass cuts using the stellar masses of the subhalos in order to best compare our results with observational studies.
-%as this is the data that we will be collecting observationally.
-Thus, making cuts on the stellar masses of these subhalos allows us to more directly apply our results to observational studies.
-
-The average number of dwarf and massive primary subhalos  %at each of the considered redshifts 
-is plotted as a function of redshift in Fig.~\ref{fig:counts}.%, and 
-A subset of this data can be found in Table~\ref{table:counts}. Also plotted is the number of primaries in groups with the marked number of companions.
-
-We find that the number of dwarf primaries increases from $z=4$ to about $z\sim0.5$, at which point the number of primaries decreases by approximately 15\% approaching $z=0$.
-There are significant differences in the number of dwarf primaries that belong to One- and Two-Subhalo Groups in \ID\ and \IH.
-\IH\ boasts about $2\times$ more primaries in One-Subhalo groups, 1.5-2$\times$ more primaries in Two-Subhalo Groups, and ~0.6$\times$ fewer Three-Subhalo groups than \ID.
-
-The number of massive primaries increases consistently from high to low redshift.
-There are very few massive groups with only one or two large ($\rm M_{H} > 10^9\sun$) subhalos, since groups of this mass scale typically host at least one large subhalo and its companions and satellites.
-Thus, almost 100\% of the massive primaries reside in ``Three-Subhalo'' groups.
-
-\subsubsection{Pairs}
-The different pair types are defined to contain a dwarf or massive primary subhalo with a secondary subhalo:
-\begin{itemize}
-    \item \textit{Major Pairs}: with stellar mass $M_{\rm sec,*}$ such that $1/4 \leq M_{\rm sec,*}/M_{\rm prim,*} \leq 1$.
-    \item \textit{Minor pairs}: with stellar mass $M_{\rm sec,*}$ such that $1/10 \leq M_{\rm sec,*}/M_{\rm prim,*} \leq 1/4$.
-    \item \textit{Minor+ Pairs}: with stellar mass $M_{\rm sec,*}$ such that $M_{\rm sec,*}/M_{\rm prim,*} \leq 1/4$.
-This set of pairs \textit{includes} the whole set of minor pairs, but also includes pairs whose mass ratio is less than 1/10.
-\end{itemize}
-The MCs, as well as the MW+LMC system and M31+M33 system, have a stellar mass ratio of approximately 1/10, and thus would be classified as minor pairs according to our analysis.
-All pairs must be separated by at least 15 physical kpc so that the pairs are well resolved into individual component subhalos in \SUBFIND.
-
-%
-%%
-%%%
-%%%%
-%%%
-%%
-%
-
-%%%%%%%%%%%%%%%%%
-\section{Results}\label{sec:results}
-%%%%%%%%%%%%%%%%%
-After collecting our sample of dwarf and massive pairs, we analyzed the frequency of occurrence as well as their properties, such as mass ratio and average kinematics of the pairs, as a function of time.
-By comparing results for groups identified in \ID\ and \IH , we can compare the effect that feedback prescriptions may have on the formation of low mass dwarf pairs vs.
-massive pairs, and search for differences in their kinematics, which ultimately dictate their merger rates.
-
-Although we collected pairs out to redshift $z\sim12$, the number of identified primaries drops significantly approaching $z\sim4$.
-As such, the following analysis will focus only on a redshift range of $z=0-\sim4$, where the statistics are more meaningful.
-In Sec.~\ref{sec:ratios}, we will discuss the stellar, current halo, and maximum halo mass ratios for our sample, which will enable us to examine the mass evolution of these systems.
-In Sec.~\ref{sec:pairFracs}, we present the main data product of this paper, namely the pair fractions for dwarf and massive major and minor pairs in \ID\ and \IH.
-In Sec.~\ref{sec:kinematics}, we discuss our findings on the kinematics of our population of pairs.
-
-%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %
-% description of the stellar and halo mass evolution
-\subsection{Stellar and Halo Masses and Ratios}\label{sec:ratios}
-\begin{figure*}[htb]
-    \centering
-    \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_stellarMass.png}
-    \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_stellarMass.png}
-    \caption{\label{fig:stellarMass} The average stellar mass of primaries identified in the \ID\ (left) and \IH\ simulations, as a function of redshift.
-(Top) Mean stellar masses of dwarf pair primaries, where the shaded regions indicate the $1\sigma$ spread computed over 50 realizations of AM relation per snapshot.
-%dwarf pairs.
-    (Bottom) The same as Top panels, but for the primaries of massive pairs.
-For dwarf pairs, the average primary stellar mass of minor pairs is much higher than for major pairs, although is roughly the same for massive pairs.
-The average primary stellar mass increases as a function of time for both dwarf and massive pairs.
-There are no major differences between the primary stellar masses in \ID\ and \IH, which indicates that the max subhalo masses of the primaries in each of the simulations is roughly equivalent.
-     \kc{not sure why the spread of all massive pairs is so small.... gotta check that!}}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_massRatio.png}
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_massRatio.png}
-  \caption{\label{fig:massRatios} 
-  The median and 25\%-75\% interquartile range of stellar, current subhalo, and maximum subhalo mass ratios of major (solid) and minor (dashed) pairs in \ID\ and \IH\ for both dwarf and massive regimes.
-As expected, the stellar mass ratios for major and minor pairs, as well as dwarf and massive pairs, are nearly identical between \ID\ and \IH, as we are using the same stellar mass cuts to define these populations of subhalo pairs in %between
-  each simulation.
-  In all cases, the ratio of current subhalo masses as a function of time is always smaller than the max halo ratio.
-This indicates that the secondaries may be losing a significant portion of their mass to the primary between the time of max mass and the snapshot of interest.
-  %\kc{why don't these lines converge at high z?}. \gb{Can you quote the mean values of interest?}
-  }
-\end{figure*}
-
-In Fig.~\ref{fig:stellarMass}, we show the average stellar masses of the primaries of major and minor dwarf and massive pairs identified in \ID\ and \IH.
-We find that the average stellar masses of primaries increases over time, typically peaking at or near $z=0$.
-The average stellar mass of the primaries of minor and minor+ \textit{dwarf} pairs is much greater than for major pairs across both simulations.
-There are two explanations for this effect.
-Firstly, if many major pairs merge by low redshift, leaving behind a more massive central halo and smaller minor satellites, the expected stellar mass of primaries of minor pairs would be significantly higher than the stellar masses of primaries in major pairs.
-Secondly, because of the stellar mass floor applied to the dwarf sample, only the largest dwarf primaries are contained in the set of minor and minor+ pairs.
-%, since smaller primaries could not have companions with low enough stellar masses to pass both our lower mass floor and be included in the selection of minor pairs.
-However, the average stellar mass of major and minor massive pairs is roughly similar.
-Since the lower mass floor for massive secondaries is lower than for primaries (see Sec.~\ref{sec:selectionCrit}), minor massive pairs may have lower mass primaries than possible for the same range of stellar mass ratios for dwarfs.
-
-The stellar and dark matter mass ratios between galaxies or subhalos impact the timescale for the interactions that will occur between pairs owing to dynamical friction (in addition to kinematics, see Sec.~\ref{sec:kinematics}).
-Interacting subhalos of roughly equal mass may end up tearing each other apart and recombining as a completely new composite subhalo.
-However, when a large subhalo interacts with a much less massive minor companion, the minor companion may disrupt, forming stellar streams around the more massive primary, with very little disruption to the primary.
-Separating our collection of pairs by mass ratios will allow us to explore dynamics and interactions separately in these two regimes~\citep{cox08}.
-%https://ui.adsabs.harvard.edu/abs/2008MNRAS.384..386C/abstract
-
-In the following discussion, stellar mass ratios will refer to the AM stellar mass of the secondary companion subhalo over the AM stellar mass of the primary.
-Halo mass ratios refer to the subhalo mass of the secondary reported in the simulation catalog at that redshift, over the subhalo mass of the primary at that redshift.
-Maximum (max) halo mass ratio refers to the maximum or ``peak'' subhalo mass ever achieved by the secondary subhalo, over the peak subhalo mass achieved by the primary at any point in their evolution.
-Thus, stellar and halo mass ratios are calculated using values of the stellar and halo masses at the current snapshot, while the max mass ratio may use subhalo masses for the primary and secondary from different snapshots.
-
-We present the median stellar mass ratios, current halo mass ratios, and maximum mass ratios for dwarf and massive major and minor pairs in Fig.~\ref{fig:massRatios}.
-Since pairs are selected based on their stellar mass ratios in each of the stellar mass realizations, the median stellar mass ratios of major and minor pairs is relatively flat across all redshifts and shows little difference between \ID\ and \IH.
-
-Since the stellar mass of each subhalo is assigned based on the subhalo`s maximal mass, we find, as expected, that the max mass ratio to evolve with redshift in the same way as the %stellar mass to halo mass
-AM relationship for a fixed stellar mass ratio.
-
-However, the halo mass ratio may tell us about how these halos have evolved since they achieved their peak halo masses, including owing to interactions.
-In particular, we find that in all cases the halo mass ratio falls well below the max halo mass ratio, implying that the secondaries may be losing much of their peak halo mass, potentially to the primaries, thus reducing the halo mass ratio at each redshift.
-
-The time evolution of the
-The halo mass ratio for dwarf pairs increases as a function of time, 
-%suggesting that, on average, the secondaries are becoming more massive with respect to their primaries, 
-which could indicate that a number of high mass ratio (minor) pairs have merged by low redshift.
-% GB NOTE TO THINK MORE ABOUT THIS 
-However, this is not the case for massive galaxies. Rather, the median halo mass ratio remains approximately constant throughout the considered redshift range.
-
-% \kc{make plots of the halo mass, max mass, etc for prims and secos to confirm suspicions}
-
-% dwarf pairs vs. massive pairs
-To understand the evolution of max mass ratios for massive pairs, it is important to remember that the abundance matching relationship is quite shallow at high subhalo masses and low redshifts.
-This means that, for a fixed stellar mass ratio, the possible corresponding halo ratio drops, as shown by the max halo mass ratio of massive pairs dipping below the stellar mass ratio at low redshift in Fig.~\ref{fig:massRatios}.
-%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %
-
-%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %
-% Pair fractions - description of pair frac plots! 
-\subsection{Pair fractions}\label{sec:pairFracs}
-
-\begin{figure*}
-  \centering
-  \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_fractions.png}
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_fractions.png}
-  \caption{\label{fig:pairFrac} The fraction of primary subhalos with companions of different types, relative to all primary subhalos, is plotted as a function of redshift.
-Results for \ID\ are on the left and for \IH\ on the right.
-Dwarf Pairs are in the top panels and Massive Pairs are shown in the bottom panels.
-(Blue) All dwarf (massive) primaries with any companion that passes the lower stellar mass threshold of $10^8 \msun$ ($10^9 \msun$).
-The fraction of dwarf galaxy pairs of all types decreases steadily from $z\sim2.5$ to today.
-Massive galaxy pairs demonstrate the opposite behavior, increasing with decreasing redshift.
-(Purple) Primaries with a companion with a stellar mass ratio between $1$ and $\frac{1}{4}$ (major pairs).
-Massive major pairs show little evolution with redshift and good agreement between \ID\ and \IH\.
-In contrast, the fraction of dwarf major pairs increases with redshift, peaking at $z\sim$2.
-The fraction is lower in \IH\ than in \ID\.
-(Yellow) Primaries with a companion with a stellar mass ratio between $\frac{1}{4}$ and $\frac{1}{10}$ (minor pairs).
-In all cases the fraction of minor pairs rises slightly with increasing redshift.
-(Orange) Primaries with a companion with a stellar mass ratio less than $\frac{1}{4}$ and a stellar mass greater than $10^8 M_\odot$ (minor+ pairs).
-Dwarf minor+ pair fractions show little evolution with redshift, while massive minor+ pair fractions increase with decreasing redshift.
-% \kc{add blurb about how the relative ratio of major pair fractions to minor pair fraction may be something that's testable to distinguish between baryonic physics implementations at low mass scales.} \gb{state values throughout, might want to include different line types in the future}
-}
-\end{figure*}
-
-Pair fractions provide insight as to how likely it is to find two galaxies very nearby each other in observations.
-Pair fractions can be used to back out merger rates from observations where other traditional methods of determining merger rates, such as asymmetry and concentration parameters, may fail.
-However, as pair fractions have only been calibrated as a function of time for massive pairs, it is important to separately determine expected pair fractions for dwarf pairs, rather than simply extrapolating the results for massive pairs.
-
-After each group's primary was identified, we considered the second most massive halo by stellar mass, and sorted the pairs by stellar mass ratio. The pair fraction was calculated as
-$$\rm F_{pair} = \frac{\rm N_{comp}}{\rm N_{prims}},$$
-where $\rm N_{comp}$ is the number of pairs with a companion of a certain type (i.e., a major or minor companion), and $\rm N_{prims}$ is the number of primaries.
-These values are computed for each stellar mass realization independently, and are then averaged for each snapshot.
-In Fig.\ref{fig:pairFrac}, we show the pair fractions of different pair types as a function of time out to $z\sim4$.
-The shaded regions represent the $1\sigma$ error on the average of the pair fraction over time, computed by conducting 50 realizations of the stellar catalog at each redshift by sampling the AM relation.
-
-We found that dwarf primaries are much more likely to have at least one major companion at redshifts $z>2$ than at $z=0$: approximately 10\% (8\%) of primaries in \textit{Illustris-Dark} (\textit{Illustris-Hydro}) have a major companion at high redshifts ($z>2$), though this fraction drops to 4\% by $z=0$ in both simulations.
-The fraction of primaries with a minor companion remains approximately constant from redshift $z=0-4$: $\sim$3-4\%($\sim$5\%) of primaries have a minor (minor+) companion in both \textit{Illustris-Dark} and \textit{Illustris-Hydro}.
-
-There is a slight suppression (between 1-4\%) in the dwarf pair fractions in \IH.
-As can be seen in Fig.~\ref{fig:counts}, \IH\ contains many more One-subhalo groups than \ID, the number of potential primary subhalos with no companions is much higher, resulting in a decrease in the pair fractions across all pair types between \textit{Illustris-Dark} and \IH.
-
-The pair fraction of massive subhalos evolves dramatically differently than their dwarf counterparts, with the pair fraction either remaining constant or \textit{increasing} at low redshifts, and is much higher than the fraction of dwarf primaries with companions.
-In particular, the fraction of massive primaries with at least one major companion in \ID\ remains approximately constant for redshifts of $z=0-4$ at between $15-20\%$, while the same pair fraction in \IH\ increases from $\sim12\%$ to $20\%$ by $z=0$.
-
-There is a slight difference between the behavior of the fraction of massive primaries in \ID\ and \IH\ for ``All Pairs'' and major pairs.
-In particular, there is a sharp uptick in the fraction of primaries with these types of companions at $z\sim1$ in only \ID.
-This fraction then declines to $z\sim$0.2, then rises sharply to $z=0$.
-While the sharp rise at low redshift is seen in \IH\ as well, the sharp increase at $z=1$ is not present.
-This means that there is a significant difference in the fraction of primaries expected with a major companion between the two simulations.
-In particular, the fraction of major pairs peaks at $z=0$ in \IH, while the fraction of major pairs in \ID is smaller than at $z=1-3$.
-This simulation-dependent behavior is not present in the minor pairs.
-
-There is a difference 
-%\gb{quantify} 
-in the relative pair fractions of major and minor dwarf pairs at high redshift, since there is such a dramatic suppression of the fraction of primaries with a major companion.
-If this can be observationally constrained, it may help us to test %say something} about
-the baryonic physics implemented in cosmological hydrodynamic simulations. %the full hydrodynamic simulation and its impact on dwarf subhalos.
-%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %
-
-%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %
-% 
-\subsection{Kinematics}\label{sec:kinematics}
- We analyzed the average separations and relative velocities of dwarf and massive identified pairs in \ID\ and \IH.
-We found that there are discrepancies between the kinematics of pairs in the two simulations.
-
- In all cases of massive and dwarf pairs, \IH\ boasts typically much higher relative velocities ($\sim20-40$km/s higher) between major pairs than \ID.
-While this velocity separation is less extreme for minor pairs ($\sim5-15$km/s higher), it is still evident, especially at higher redshifts ($z>2$).
-
- \subsubsection{Separations}
- \begin{figure*}
-  \centering
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_separations.png}
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_separations.png}
-  \caption{\label{fig:separations} The mean magnitude of the relative 3D separation between primary and secondary subhalos in \ID\ and \IH\ as a function of time for dwarf and massive major (left) and minor (right) pairs.
-The drastic increase in average separation between subhalos as a function of time may indicate that only the longest-living, wide-separation circular-orbit pairs remain at low redshifts, since a majority of low separation pairs may have merged by low redshift.
-A more detailed analysis of the orbits of these systems will be the subject of future work.
-  (Left) Major pairs exhibit a small ($\sim 20$ kpc) separation difference between simulations across all redshifts for both dwarf and massive pairs. 
-  This may be due in part to a difference in the major merger timescales between the two simulations. 
-  (Right) Minor pairs exhibit roughly the same behavior for separations over time between the two simulations.
-  % GB : i would leave the below to the main text. 
-  %There is a population of low-separation subhalo pairs in \ID that cannot be matched to equivalent pairs in \IH.
-If merger timescales are lower or dynamical friction operates more efficiently in the hydro simulation, this could explain the lack of low separation subhalo pairs in \IH and, thus, the discrepancy between the two simulations.
-    %\gb{include LMC etc systems}.  
-  }
-\end{figure*}
-
-Because this study utilizes subhalos selected in
-%Using 
-cosmological simulations, we can extract the
-%means we get 
-full 6D-phase information for subhalos, such as 3D position and velocity vectors. 
-%about the positions and velocities of the subhalos, and 
-We thus do not have to worry about projection effects artificially introducing projected pairs to our dataset.
-This also means that we can study the evolution of the physical separations of the subhalo pairs and how it might be impacted by mass scale or simulation physics.
-% and determine the characteristic behaviors of these systems.
-
-In Fig.~\ref{fig:separations}, we show the average separation of our selection of pairs (major and minor pairs, dwarf and massive galaxy pairs) selected in both the \ID\ and \IH simulations.
-
-We find that the average separation of all pair types increases towards lower redshift.
-This could indicate that the small separation pairs are merging, leaving behind the population of pairs that have longer-lived orbits.
-Alternatively, the population of pairs picked out with our selection criteria may be very different between lower and higher redshift.
-Following high redshift pairs and establishing their orbits through to $z=0$ will be the subject of future work.
-
-There is a slight ($\sim$20 kpc), but systematic, separation difference between major pairs in \ID\ and \IH\ in both of the dwarf and massive galaxy regimes.
-When we considered only subhalos that had separations $> 80$ kpc, the separation difference was resolved between the two simulations, indicating that a low separation population of pairs is absent in \IH.
-This population of subhalos may have merged earlier in the simulation.
-This will be studied in future orbital studies.
-
-On average, minor pairs have much lower average separations than major pairs.
-This trend holds true between both simulations and both mass ranges.
-Interestingly, the separation discrepancy does not appear for minor pairs, which suffer less dynamical friction, supporting the hypothesis that major close pairs are being missed or merging faster in the \IH simulation.
-
-\subsubsection{Velocities}
-
-%% velocities 
-\begin{figure*}
-  \centering
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_velocities.png}
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_velocities.png}
-  \caption{\label{fig:velocities}The mean magnitude of the relative 3D velocity between primary and secondary subhalos in \textit{Illustris-Dark} and \textit{Illustris-Hydro} as a function of time for major (left) and minor (right) pairs.
-The relative velocities decrease significantly throughout time for all dwarf and massive galaxy pairs.
-Note that the relative velocities are systematically higher for all pairs in \textit{Illustris-Hydro} (by 15-50 km/s), though the differences are smaller for minor pairs and at low redshift.
-This discrepancy is likely related to the similar discrepancy seen in the separations (Fig.~\ref{fig:separations}).% The collection of low-separation pairs in \textit{Illustris-Dark} that do not have counterparts in \textit{Illustris-Hydro} also had very low velocities, thus accounting for the difference between the dark and hydro simulations.
-%   \kc{can include line for LMC+SMC, MW+M31 (120 Van der marel from HST), M31+M33 and the meanings behind them.
-(MW+LMC is up at 320 and is at peri so this makes sense.) also need to talk about the low separation without the abundance matching bit}
-}
-\end{figure*}
-
-Figure~\ref{fig:velocities} illustrates the magnitude of the mean relative 3D velocities between all pair types in both simulations.
-The relative velocities decrease significantly throughout time for all pairs, where massive pairs have speeds of order 100 km/s larger than dwarf pairs.
-% GB ;is the evolution with time steeper for the hydro case in the massive galaxies than in the dwarf galaxies?
-
-There is a significant $\sim$15km/s ($\sim$30-50km/s) velocity offset between major dwarf (massive) pairs in \ID\ versus \IH.
-Additionally, a small ($\sim$5-10km/s) velocity separation exists between minor pairs.
-While this velocity separation is suppressed at very low redshifts for both pair types, the vast spread between velocities suggests a significant orbital/dynamic evolution between pairs in the simulations.
-
-When we exclude all pairs with relative separations $<80$kpc from our analysis, the stark velocity differences between \ID\ and \IH\ are resolved, implying that the ``missing'' population of low separation halos in \IH\ is also responsible for this velocity offset.
-
-In the future, we will include studies of the tangential vs.
-radial velocities to provide a first order guess about the orbital trajectories of the these systems to determine if they on average are on infalling or radial orbits.
-%\kc{Could do like.... radial/tangential velocity as a funciton of separation? did I do that already?}
-
-%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %
-
-%\kc{make velocity vs. separation plot for hydro vs dark, dwarf and massive galaxies! Major pairs? Or major AND minor? }
-
-%%%%%%%%%%%%%%%%%
-\section{Discussion}\label{sec:discussion}
-%%%%%%%%%%%%%%%%%
-%% summary table! %%
-\begin{table*}[tb]
-  \begin{center}
-\begin{tabular}{ccccc|cccc}
-& \multicolumn{2}{c}{Dwarf} & \multicolumn{2}{c}{Massive} & \multicolumn{4}{c}{Local Group Analogs} \\\hline\hline
-    & Major Pairs & Minor Pairs & Major Pairs & Minor Pairs & MW-M31 & M31-M33 & MW-LMC& LMC-SMC\\\hline\hline
-$\rm M_{*,prim}$ & \# & \# &\# &\#&\#&\#&\#&\#\\
-\end{tabular}
-\end{center}
-\caption{\label{table:summary}\kc{Placeholder for now} Summary table with all values from z=0 (and maybe z=1,2,3,etc)}
-\end{table*}
-%%                 %%
-
-We analyzed a set of dwarf galaxy pairs and massive galaxy pairs from the \textit{Illustris-1} simulation to place constraints on the cosmologically expected fractions of major and minor pairs as a function of time.
-Our goals include identifying any differences in the behavior of pairs as a function of primary mass (dwarf or massive galaxy) and simulation physics.
-Here we use our results to place Local Group Pairs in a cosmological and temporal context (Sec.~\ref{sec:LGimplications}).
-We further discuss implications of our findings for cosmological simulations with baryonic physics (Sec.~\ref{sec:baryonImpact}).
-Finally, we briefly compare to existing literature (Sec.~\ref{sec:litcompare}).%Finally we discuss the implications of our work for future extragalactic surveys at high redshift (Section ).
-%We found that 
-%\kc{What we did. What we found. Stuff that doesn't fit into the subsections}
-
-\subsection{Implications for Local Group Pairs}\label{sec:LGimplications}
-\citet{patel17a} showed that the existence of the MW-LMC and M31-M33 pairs, are typical of minor massive pairs at low redshift.
-However, while the M31-M33 interaction may be characteristic of minor massive pairs, they show that the MW and LMC interaction is dynamically unique, since very high velocity and low separation pairs are dynamically rare at $z=0$.
-We found that typical minor massive pairs have separations between 200-300kpc and relative velocities between 160-200kpc at low redshifts ($z<$0.5).
-Since the M31-M33 pair has a current separation of $\sim$200kpc and relative velocity $\sim$200km/s, and the MW-LMC pair has a separation of $\sim$50kpc and relative velocity of $\sim$320km/s, our results are in good agreement with \citet{patel17a}.
-However, while the MW-LMC kinematics may not be typical at low redshift, they are more characteristic of higher redshift ($z>2$) minor massive pairs, where separations are on average $<$150kpc and velocities exceed 240km/s.
-
-Since the MCs are at a separation of only $23kpc$ and have a relative velocity of $103km/s \pm26$~\cite{zivick18}, the combination of separations and velocities is non-typical, as this separation is uncommon at low redshift, while these velocities are uncommon at higher redshift.
-These kinematic differences can be potentially reconciled by the presence of the MW, and the study of the dynamics of triples will be the topic of future work.
-
-%It is thought that the LMC+SMC system fell into the MW halo recently ($<$2Gyr ago) and is currently making its first pericentric passage around the MW~\citep{besla10,bk11} (patel20).
-This means that the MC-system system spent a majority of their interaction history in a more isolated environment than the MW halo.
-However, we have no idea if the characteristics of the orbital models for the MCs are typical of dwarf pairs in isolation.
-
-%  120km/s  and a separation of 782kpc$\pm$25 \cite{mcconnachie05} HST proper motions and GAIA proper motions total speed ranges from -- to -- and the separation is high!
-So MW-M31 is not typical, and is true at all points in time for groups of this mass.
-
-While \citet{besla18} finds that 70-85\% of dwarf pairs in their sample are major pairs, we find that between 40-45\% of all pairs are major pairs, although this fraction increases at higher redshift to $\sim$60-65\%.
-The stellar mass range of our study includes stellar masses down to $10^8\msun$ while the \citet[]{besla18} study includes stellar masses down to $2\times10^8$.
-Our lower stellar mass limits and ability to ensure that pairs are associated in the same group may increase the number of dwarf minor pairs in our sample.
-
-\subsection{Impact of Mass Scales and Baryonic Physics}\label{sec:baryonImpact}
-The mass scale of our galaxy pairs heavily influences the behaviour of the pair fractions as a function of time.
-The pair fractions of dwarf major pairs are $\sim$4\% at z=0 in both simulations, however the pair fraction grows steadily and peaks at $z=2$, where the values plateau.
-This time-dependent evolution is very different from our results for massive pairs, since massive major pair fractions stay roughly constant or \textit{decrease} at higher redshift.
-This indicates that the evolution of dwarf and massive galaxy pairs proceeds very differently and on different timescales.
-
-We also found that the evolution of dwarf pair fractions between $z=0-4$ is dramatically different between \ID\ and \IH.
-In particular, the pair fractions in \IH\ are approximately $20-25\%$ lower than those of \ID.
-This suppression effect is not seen with massive pairs, implying that the implementation of baryonic physics in \IH\ impacts the evolution of dwarf pairs much more strongly than massive pairs.
-
-\subsection{Comparison to existing work}\label{sec:litcompare}
-% Although dwarf pairs such as the Magellanic Clouds are rare at low redshift ~\citep{besla18}, many more dwarf pairs may be observable with future high redshift observations!
-We expect that at $z\sim2$, roughly 10\% of roughly LMC-mass dwarfs will have at least one major companion, and an additional 4\% will have at least one minor companion.
-
-%GB: Discuss here general trends -- expected behavior as a function of time. and relative trends between massive vs low mass or major vs minor pairs. 
-\citet{lotz08} finds that the merger fraction of massive major galaxy pairs (M$_*>10^{10}\msun$) is approximately constant at 10$\pm$2\% between $0.2<z<1.2$, which is consistent with our findings that massive major pair fraction evolves very little (only $\pm$2\%) as a function of redshift.
-While the redshift evolution of our pairs is consistent with \citet{lotz08}, we do find higher pair fractions across this same redshift range (with pair fractions ranging between 16-20\%), which may be due to our increased sample of massive major pairs at high separation.
-
-\citet[]{casteels14} found that the major merger fraction for galaxies with $10^{9.5}< M_* < 10^{11.5}\msun$ (roughly equivalent to our massive pair criteria) is approximately 1.3-2\% at low redshift, but increased to $4\%$ at lower masses.
-We find that massive major pairs have a pair fraction of $f_{pair}\sim18-20$\% at low redshift, which is inconsistent with the \citet{casteels14} work, but close to 4\% for dwarf galaxy major pairs, which is consistent with observations.
-However, \citet{casteels14} uses morphological signatures of mergers to calculate merger fractions.
-Since massive galaxies will only have morphological signatures from recent close passages of other massive galaxies, these methods will preferentially select close pairs compared to larger separation pairs.
-Since our study includes many low redshift, highly separated pairs, it is not unreasonable to assume that the major pair fraction difference between the two studies arises from these selection criteria.
-
-\citet{duncan19} found that the observational massive major pair fraction increases with redshift from $z=0$ (where f$_{pair}\sim0.07$) to $z=4$ (f$_{pair}\sim0.2$).
-This is in contrast to our finding that the massive major pair fraction is constant/slightly decreasing from $z=0-4$ (from f$_{pair}\sim0.2$ to f$_{pair}\sim0.14$)).
-This is likely due to the strict projected separation cuts that are made on the observational data, where massive major pairs must have $5<r_{proj}<30kpc$, while our massive major pairs includes low separation \textit{and} high separation (r$_{sep}>$30kpc) pairs.
-This accounts for our inflated pair fraction at all redshifts compared to the \citet[]{duncan19} work.
-
-In general, our study finds inflated pair fraction results because of our ability to determine associated, but well separated, dwarf and massive galaxy pairs.
-
-% https://ui.adsabs.harvard.edu/abs/2019ApJ...872...24V/abstract
-  % v 34 36, 123 25, 19 37 km s . M31,DR2 HST
-% https://ui.adsabs.harvard.edu/abs/2020arXiv201209204S/abstract
-
-% Zivick https://iopscience.iop.org/article/10.3847/1538-4357/aad4b0/pdf
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}\label{sec:conclusions}
-In this paper we presented a study of isolated pairs of dwarf and massive subhalos in the large volume cosmological simulation \textit{Illustris-1}, using data from both the N-body (dark matter only) and full hydrodynamic simulations, \textit{Illustris-Dark} and \textit{Illustris-Hydro} respectively.
-Our criteria requires that all pairs are a part of the same FoF group (see Sec.~\ref{sec:selectionCrit}).
-We ensure isolation of our selection of pairs using a Hill Radius criteria to ensure that pairs are not gravitationally influenced by nearby massive perturbers.
-
-We define dwarf galaxies as having stellar mass $10^8\msun <M_* < 5\times10^9 \msun$, and massive galaxies as $5\times10^9<M_*<10^{11}\msun$.
-Major pairs have secondary to primary stellar mass ratios between 1-1:4, minor pairs have stellar mass ratios between 1:4-1:10, and minor+ pairs have stellar mass ratios $<$1:4, thus including the population of minor pairs.
-
-We found that there is a difference in the evolution of the pair fraction for dwarf pairs and massive pairs over time, and that baryonic physics has an impact on the expected pair fractions and kinematics of these systems.
-
-% state a main high level conclusion - are the pair fractions different between massive galaxies and dwarfs ? (which is more common, is their behavior with z the same?)  Does hydrodynamics matter?
-
-Our pair fraction results are summarized as follows:
-
-% Dwarf Pairs : 
-(i.) \textbf{The pair fractions for all dwarf primaries with a companion with stellar mass $>10^8\msun$ (All Pairs) peaks at $z=2$ and remains constant to $z=4$.} In \ID, the pair fraction is approximately $8\%$ at $z=0$ and increases to peak at 16\% at $z=2$, while in \IH, the pair fraction is $8\%$ at $z=0$, increasing to $\sim$12\% at $z=2$.
-In both simulations, the trends with redshift are determined by the major pairs, which are the most common class of dwarf galaxy pair at all redshifts.
-
-(ii.) \textbf{Magellanic Cloud mass analogs (dwarf minor pairs) are approximately 1.5x more common at $z>2$ than at the present day.} In \IH, $\sim$2-3\% of dwarf primaries (LMC analogs) host a minor companion (SMC analog) across all redshifts, with only a slight increase in the pair fraction between $z=0$ and $z=2$.
-There is slightly more evolution in the case of \ID, with $\sim$4\% of primaries hosting a minor companion for $z>2$, and declining to 2\% at $z=0$.
-Thus, we expect to find isolated minor dwarf pairs with approximately the same frequency out to $z=4$.
-
-(iii.) \textbf{Dwarf primaries are 2-2.5$\times$ more likely to have major companions at $z>2$ than at $z=0$.} We expect that roughly $\sim$4\% of dwarf primaries will have a major companion at $z=0$, increasing to $z=2$ before leveling off at 10\% (8\%) in \ID\ (\IH) for $z>2$.
-
-% comparison between dark and hydro with dwarfs
-(iv.) \textbf{The pair fraction of dwarf primaries with companions of all types (major, minor, minor+) is between $1-4\%$ less common in \IH\ than in \ID.} This indicates that the baryonic physics of the \IH simulation has a non-negligible impact on the expected pair fractions for low mass systems.
-The same suppression of pair fractions for these pair types is not seen for massive pairs.
-
-% Massive galaxies 
-(v.) \textbf{The pair fractions for all massive galaxy primaries with a companion with a stellar mass $>10^8 \msun$ increases over time and peaks between $z=0-1$.} This behaviour is primarily driven by the pair fraction of massive minor+ pairs, as the pair fractions for massive major and minor pairs is relatively flat across $z=0-4$.
-This is very different than the behaviour of low mass galaxy pairs, where the major dwarf pairs drive the evolution of pair fractions for dwarf pairs.
-
-(vi.) \textbf{$\sim$15\% of MW/M31 analogs host a LMC/M33 mass analog at all redshifts (minor pairs for massive galaxies).}  The behavior is similar in \ID and \IH.
-It is also similar to the behavior of dwarf galaxy minor pairs (LMC/SMC analogs) with time.
-% MW/LMC and M31/M33 analogs are only slightly more common at $z>1$ than at z=0.}
-
-(vii.) \textbf{The frequency of MW-M31-type pairs (major massive galaxy pairs) may be impacted by baryonic physics,} as demonstrated by differences in the time evolution of pair fractions between \ID\ and \IH.
-In the case of \ID, the pair fraction of massive major pairs is $\sim$17-18\% at $z=0$, and increases to roughly $20\%$ between $z=1-3$.
-However, in \IH, the pair fraction of massive major pairs peaks at 20\% at $z=0$, and declines steadily to $15\%$ at $z=4$.
-The evolution of major galaxy pairs is markedly different than for dwarf galaxies
-
-(viii.) \textbf{These results are/are not consistent with observations.}
-
-Our results for pairs in terms of their kinematics are as follows:
-
-(i.) \textbf{The relative separation between dwarf (massive) galaxy major pairs increases by $\sim$100kpc ($\sim$250kpc) from $z=4$ to $z=0$.} The minor pairs show similar trends with the relative separations increasing by $\sim$90kpc ($\sim$180kpc) from $z=4$ to $z=0$.
-There is a relative separation difference between major pairs in \ID\ vs.
-\IH of approximately 10-15kpc (20-40kpc), with average separations higher across all redshifts in \IH.
-At $z=0$, the average separation of dwarf minor pairs is $\sim$140-150 in both simulations.
-
-(ii.) \textbf{The relative velocities of between dwarf (massive) galaxy major pairs decreases by $\sim$30km/s ($\sim$90km/s) from $z=4$ to $z=0$.} The dwarf (massive) minor pairs show similar trends, where the average velocity decreases by $40$km/s ($100$km/s) from $z=4$ to $z=0$.
-There is a significant impact on the average velocities of pairs in this sample from baryonic physics, as there is a velocity separation between the two simulations of approximately $20$km/s (40km/s) for dwarf (massive)  major pairs, and 10km/s (20km/s) for dwarf (massive) minor pairs.
-
-(iii.) \textbf{The MCs are dynamically unique compared to the population of dwarf minor pairs at $z=0$.} Their separation is much smaller and their velocities much larger than is typical for dwarf minor pairs.
-
-(iv.) \textbf{While the M31-M33 pair is dynamically typical of massive minor pairs at low redshift, the MW-LMC pair is extremely unique both in terms of its small separation and large velocities.}
-
-(v.) \textbf{MW-M31 pair has lower relative velocities and higher separations than typical massive major pairs at low redshift.}
-
-We've shown that there is a difference in pair fractions between dwarf pairs and massive pairs.
-In addition, baryonic effects implemented in \IH\ have a non-negligible impact on the behaviour of the evolution of pair fractions and on the typical kinematics, and we'll be able to see how these discrepancies play out in the era of \textit{JWST.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section{Post prelim focus}
-% After prelim I will work on:
-% \begin{itemize}
-%   \item adding TNG results!
-%   \item completing this study for 1000 realizations of the abundance matching prescription
-% \end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliography{refs}{}
 \bibliographystyle{aasjournal}
-\bibliography{biblio2021.bib}
-
-\appendix{Hill Radius Criteria\label{app:hill}}
-The Hill radius is the distance from the center of a group, $G$, at which circular orbits of particles within $G$ will no longer be stable due to the presence of a massive perturber $P$.
-
-The Hill radius is defined as:
-\begin{equation}
-  R_{\rm Hill} = R_{\rm sep} \bigg( \frac{ M_{\rm G} }{ 3M_{\rm P} } \bigg)^{1/3},
-\end{equation}
-where $M_{\rm P}$ is the mass of the perturber, $M_{\rm G}$ is the mass of the group under consideration, and $R_{\rm sep}$ is the physical separation between the two groups ~\citep{hahn09}.
-\l
-As the Hill radius is a measure of the distance from center that particles in $G$ can sustain circular orbits, we consider the group $G$ isolated if the radius of the group is less than the Hill radius.
-The radius of the group is taken to be \texttt{Group\_R\_TopHat200} provided in the \texttt{SUBFIND} catalog, which is the radius of a sphere, centered on the group, whose mean density is $\rho_c \Delta_c$, where $\rho_c$ is the critical density of the universe and $\Delta_c$ is given by the spherical top-hat collapse model of \citet{brynorman98}.
-This ensures that the particles belonging to $G$ are gravitationally bound to $G$ and that the intrinsic dynamics of the subhalo pairs contained within are not affected by massive perturbers.
 
 \end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-11-10 pears/utils/counts.py
get unpaired halos and pairs

@@ -15,14 +15,13 @@ from utils.paths import SetupPaths
 paths = SetupPaths()
   
     
-class compile_summary:
+class summary:
     
     def __init__(
         self,
         sim="Illustris", 
         phys="dark",
         size="dwarf",
-        subset="major",
         **kwargs
         ):
     
@@ -39,53 +38,46 @@ class compile_summary:
             to specify which simulation
         size: str
             "dwarf" or "massive"
-        subset: str
-            to specify the subset
-            choose from: major, minor, all
         """
         
         self.sim = sim
         self.phys = phys
         self.size = size
-        self.subset = subset
         self.kwargs = kwargs
         self.redcutoff = self.kwargs.pop("redshift_cutoff", 1000)
         
 
-    def get_data(self):
+    def get_counts(self):
         
-        summarydata = {"Redshift":[],
-                            "Snapshot":[],
-                            "Number pairs":[],
-                            "Number primaries":[],
-                           # "Number tertiaries":[],
-                            "Ratio pairs":[],
-                            "Median Separation": [],
-                            "Median Separation Quartiles": [],
-                            "Mean Separation": [],
-                            "Mean Separation Std": [],
-                            "Median RelVel": [],
-                            "Median RelVel Quartiles": [],
-                            "Mean RelVel": [],
-                            "Mean RelVel Std": [],
-                            "Mean Lowsep Counts": [],
-                            "Mean Lowsep Counts Std": []}
+#         summarydata = {"Redshift":[],
+#                             "Snapshot":[],
+#                             "Number pairs":[],
+#                             "Number primaries":[],
+#                             "Ratio pairs":[],
+#                             "Median Separation": [],
+#                             "Median Separation Quartiles": [],
+#                             "Mean Separation": [],
+#                             "Mean Separation Std": [],
+#                             "Median RelVel": [],
+#                             "Median RelVel Quartiles": [],
+#                             "Mean RelVel": [],
+#                             "Mean RelVel Std": [],
+#                             "Mean Lowsep Counts": [],
+#                             "Mean Lowsep Counts Std": []}
 #         summarydata = {}
         
-        self.snapshots = {"Illustris":np.arange(0,136), 
-                     "TNG":np.arange(0,100)}
+        self.snapshots = {"Illustris":np.arange(0,136), "TNG":np.arange(0,100)}
         
         for snapshot in self.snapshots[self.sim]:
             pair_path = f"{self.sim}_{snapshot}_10.hdf5"
[…]

### 2022-11-10 pears/utils/make_pairs.py

@@ -280,7 +280,7 @@ for phys in ["dark","hydro"]:
 
     for key, val in pair_data.items():
         val = np.array(val)
-        dset = f.create_dataset(f'/{phys}/{key}', 
+        dset = f.create_dataset(f'/pairs/{phys}/{key}', 
                                 shape=val.shape,
                                 dtype=val.dtype)
         dset.attrs[key] = units_dict[key]

### 2022-11-10 pears/utils/make_unpaired.py

@@ -1,0 +1,155 @@
+'''
+This script uses sorts through the catalog of subhalos to find pairs for the 
+this realization of AM masses
+'''
+import sys
+import h5py
+import numpy as np
+from utils.get_groups import GetGroups
+from utils.paths import SetupPaths
+from vectorCorrection import vectorCorrection as vector
+
+snapshot = int(sys.argv[1])
+sim = str(sys.argv[2])
+num_reals = int(sys.argv[3])
+
+realNumbs = np.arange(-1,num_reals+1,1)
+paths = SetupPaths()
+
+## find subhalos for this simulation and snapshot #
+subhalo_path = f"{sim}_{snapshot}.hdf5"
+subhalo_data = h5py.File(f"{paths.path_subhalos}{subhalo_path}", "r")
+
+savepath = f"{sim}_{snapshot}_10.hdf5"
+# f = h5py.File(f"{paths.path_pairs}{savepath}", 'w')
+
+redshift = subhalo_data["Header"].attrs["Redshift"]
+scale = 1 / (1 + redshift)
+
+units_dictionary = {"Group ID": "Group Number in Subfind Catalogs", 
+          "Group Mass": "Physical mass from Group_M_TopHat200 -- 1e10 Msun",
+          "Group Radius": "Physical radius from Group_R_TopHat200 -- kpc",
+          "Group Nsubs": "Number of subhalos in group",
+          "Sub1 ID": "Subhalo ID at current snapshot",
+          "Sub1 Mass": "Subhalo mass at current snapshot -- 1e10 Msun",
+          "Sub1 Stellar Mass": "Stellar masses from abundance matching -- 1e10 Msun",
+          "Sub1 Pos": "Subhalo physical position in box x,y,z -- kpc",
+          "Sub1 Vel": "Subhalo velocity in vx, vy, vz -- km/s",
+          "Sub1 MassType": "Mass of bound particles - gas, DM, empty, tracers, stars, BHs -- in 1e10 Msun",
+          "Sub1 BHMass": "Sum of the masses of all blackholes -- 1e10 Msun",
+          "Sub1 BHMdot": "Instantaneous accretion rates of all blackholes -- 1e10 Msun / 0.978Gyr",
+          "Sub1 SFR": "Sum of the individual SFRs of all gas cells in subhalo -- Msun / yr",
+          "Sub1 SFRinRad": "Sum of SFRs of all gas cells within twice the stellar half mass radius -- Msun / yr",
[…]

### 2022-11-10 pears/utils/median_realization.py

@@ -1,0 +1,243 @@
+'''
+The median AM realization
+'''
+
+import sys
+import h5py
+import numpy as np
+from utils.get_groups import GetGroups
+from utils.paths import SetupPaths
+from vectorCorrection import vectorCorrection as vector
+
+paths = SetupPaths()
+
+snapshot = int(sys.argv[1])
+sim = str(sys.argv[2])
+
+## find subhalos for this simulation and snapshot ##
+subhalo_path = f"{sim}_{snapshot}.hdf5"
+subhalo_data = h5py.File(f"{paths.path_subhalos}{subhalo_path}", "r")
+redshift = subhalo_data["Header"].attrs["Redshift"]
+scale = 1 / (1 + redshift)
+
+## create file for data collection ##
+savepath = f"{paths.path_median}{sim}_{snapshot}.hdf5"
+f = h5py.File(savepath, 'w')
+
+header_dict = {"Snapshot": snapshot,
+               "Redshift": redshift,
+               "Scale": scale,
+               "Simulation": sim}
+
+dset = f.create_group('/Header')
+for key in header_dict.keys():
+    dset.attrs[key] = header_dict[key]
+f.close()
+
+units_dictionary = {"Group ID": "Group Number in Subfind Catalogs", 
+          "Group Mass": "Physical mass from Group_M_TopHat200 -- 1e10 Msun",
+          "Group Radius": "Physical radius from Group_R_TopHat200 -- kpc",
+          "Group Nsubs": "Number of subhalos in group",
+          "Sub1 ID": "Subhalo ID at current snapshot",
+          "Sub1 Mass": "Subhalo mass at current snapshot -- 1e10 Msun",
+          "Sub1 Stellar Mass": "Stellar masses from abundance matching -- 1e10 Msun",
+          "Sub1 Pos": "Subhalo physical position in box x,y,z -- kpc",
+          "Sub1 Vel": "Subhalo velocity in vx, vy, vz -- km/s",
+          "Sub1 MassType": "Mass of bound particles - gas, DM, empty, tracers, stars, BHs -- in 1e10 Msun",
+          "Sub1 BHMass": "Sum of the masses of all blackholes -- 1e10 Msun",
+          "Sub1 BHMdot": "Instantaneous accretion rates of all blackholes -- 1e10 Msun / 0.978Gyr",
+          "Sub1 SFR": "Sum of the individual SFRs of all gas cells in subhalo -- Msun / yr",
[…]

### 2022-11-10 pears/utils/paths.py

@@ -45,3 +45,5 @@ class SetupPaths:
         self.path_am_mass = self.path_data + "am_masses/"
         self.path_snapdata = self.path_data + "snapdata/"
         self.path_pairs = self.path_data + "pairs/"
+        self.path_median = self.path_data + "median_realization/"
+        self.path_simstars = self.path_data + "simulation_mstar/"

### 2022-11-10 pears/utils/unit_dictionary.py

@@ -1,0 +1,33 @@
+# units_dict = {
+#     "Group ID":"Group Number in Subfind Catalogs", 
+#     "Group Mass":"Physical mass from Group_M_TopHat200 -- 1e10 Msun",
+#     "Group Radius":"Physical radius from Group_R_TopHat200 -- kpc",
+#     "Group Nsubs":"Number of subhalos in group",
+#     "Sub1 ID":  "Subhalo ID at current snapshot",
+#     "Sub2 ID":  "Subhalo ID at current snapshot",
+#     "Sub1 Mass": "Subhalo mass at current snapshot -- 1e10 Msun",
+#     "Sub2 Mass": "Subhalo mass at current snapshot -- 1e10 Msun",
+#     "Sub1 Stellar Mass": "Stellar masses from abundance matching -- 1e10 Msun",
+#     "Sub2 Stellar Mass": "Stellar masses from abundance matching -- 1e10 Msun",
+#     "Sub1 Pos": "Subhalo physical position in box x,y,z -- kpc",
+#     "Sub2 Pos": "Subhalo physical position in box x,y,z -- kpc",
+#     "Sub1 Vel": "Subhalo velocity in vx, vy, vz -- km/s",
+#     "Sub2 Vel": "Subhalo velocity in vx, vy, vz -- km/s",
+#     "Sub1 MassType": "Mass of bound particles - gas, DM, empty, tracers, stars, BHs -- in 1e10 Msun",
+#     "Sub2 MassType": "Mass of bound particles - gas, DM, empty, tracers, stars, BHs -- in 1e10 Msun",
+#     "Separation": "Physical separation between primary and secondary in kpc",
+#     "RelVel": "Relative velocity between primary and secondary in km/s",
+#     "Stellar Mass Ratio": "Stellar mass ratio of secondary over primary", # in this case- it's by primary subhalo mass
+#     "Realization": "Stellar mass realization (0-1000)",
+#     "Sub1 BHMass": "Sum of the masses of all blackholes -- 1e10 Msun",
+#     "Sub2 BHMass": "Sum of the masses of all blackholes -- 1e10 Msun",
+#     "Sub1 BHMdot": "Instantaneous accretion rates of all blackholes -- 1e10 Msun / 0.978Gyr",
+#     "Sub2 BHMdot": "Instantaneous accretion rates of all blackholes -- 1e10 Msun / 0.978Gyr",
[…]

### 2022-11-11 pears/utils/make_unpaired.py
adding code and notebook to make count plots

@@ -40,7 +40,9 @@ units_dictionary = {"Group ID": "Group Number in Subfind Catalogs",
           "Sub1 BHMdot": "Instantaneous accretion rates of all blackholes -- 1e10 Msun / 0.978Gyr",
           "Sub1 SFR": "Sum of the individual SFRs of all gas cells in subhalo -- Msun / yr",
           "Sub1 SFRinRad": "Sum of SFRs of all gas cells within twice the stellar half mass radius -- Msun / yr",
-          "Sub1 GasMetallicity": "Mz/Mtot, where Z = any element above He within 2x stellar half mass radius -- unitless"}
+          "Sub1 GasMetallicity": "Mz/Mtot, where Z = any element above He within 2x stellar half mass radius -- unitless",
+          "Realization": "Stellar mass realization (0-1000)"
+}
 
 # header already exists since running this file after the pair creation file
 
@@ -71,7 +73,8 @@ for phys in ["dark","hydro"]:
                  "Sub1 BHMdot": [],
                  "Sub1 SFR": [],
                  "Sub1 SFRinRad": [],
-                 "Sub1 GasMetallicity": []}
+                 "Sub1 GasMetallicity": [],
+                 "Realization":[]}
 
     ## create a dictionary of arrays from subhalo data
     subhalo_dictionary = {}
@@ -126,7 +129,8 @@ for phys in ["dark","hydro"]:
                               "Sub1 BHMdot": subBHMdot,
                               "Sub1 SFR": subSFR,
                               "Sub1 SFRinRad": subSFRinRad,
-                              "Sub1 GasMetallicity": subGasMet}
+                              "Sub1 GasMetallicity": subGasMet,
+                              "Realization": realization}
                                      
                     for key in unpaired_data.keys():
                         unpaired_data[key].append(single[key])
@@ -139,14 +143,15 @@ for phys in ["dark","hydro"]:
 
 
     f = h5py.File(f"{paths.path_pairs}{savepath}", 'r+')
-
+    
     for key, val in unpaired_data.items():
         val = np.array(val)
         dset = f.create_dataset(f'/unpaired/{phys}/{key}', 
                                 shape=val.shape,
                                 dtype=val.dtype)
         dset.attrs[key] = units_dictionary[key]
-        dset[:] = val
+        dset[:] = val 
+    
     f.close()
     print(f"successfully wrote unpaired halos for {sim} {phys} to {savepath}")
     print(f"saved data for", unpaired_data.keys())

### 2022-11-11 paper/pears.tex
added counts plots and draft captions

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\graphicspath{{./}{figures/}}
+\graphicspath{{./}{../plots/pairs_plots/}}
 \input{math_definitions.tex}
@@
 \begin{table*}[htb]
-  \begin{center}
+  \centering
     \begin{tabular}{lcc}
@@
     \caption{\label{table:mass}Selection criteria for dwarf and massive pairs.}
-  \end{center}
     \end{table*}
@@
     \end{table}
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{counts_dwarfs.png}
+  \caption{Median counts of dwarf primaries in \ill{} and \tng{} \kc{add "dwarf" somewhere to plot}.
+The number of dwarf primaries peaks at $z~0.75$.
+TNG has higher halo count than Illustris.
+However, the difference between the number of halos in both dark simulations is substantial.
+Additionally, in Illustris, hydro halos outnumber dark halos.
+In TNG, the opposite is true, where dark halos outnumber hydro halos.
+In Illustris, this can be accounted for by the discrepant number of unpaired halos (dotted), while in TNG, the difference is dominated by pairs.
+    }
+  \label{fig:counts-dwarfs}
+\end{figure*}
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{counts_massive.png}
+  \caption{No turn over, instead, monotonically increasing towards a peak at low z.
+No significant fraction of halos that are lone subhalos.
+The largest differences between the hydro and dark simulations in both cases are at low z, where the counts start to diverge.
+TNG has a higher number of massive halos primaries than Illustris.
+The difference between dark and hydro is large in TNG, and at low z, the main driver of this difference is in the pairs, as opposed to the lone halos.
+This is not the case in Illustris, where both the pairs and unpaired halos contribute equally to the difference between dark and hydro, in opposite way!
+Weird… \kc{add "massive" somewhere to plot}
+    }
+  \label{fig:counts-massive}
+\end{figure*}
 

### 2022-11-15 pears/utils/get_summary_data.py
adding m31 stuff i did for ekta and distribution plots

@@ -120,7 +120,7 @@ class compile_summary:
                         countarray.append(counts/numprims)
 
                     masks = {"primaries":primary_analog,
-                             "allpairs":primary_analog & minsep,
+                             "allpairs":primary_analog & minsep,  # this should be & pairs
                              "median": primary_analog & med_mask,
                              "major":majors & primary_analog & minsep, 
                              "minor":minors & primary_analog & minsep,

### 2022-11-16 paper/pears.tex
adding simulation methodology

@@
 \title{
-  Frequency of galaxy pairs in the Illustris and Illustris TNG cosmological simulations
+  Frequency of galaxy pairs in the Illustris and IllustrisTNG cosmological simulations
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-\label{sec:intro}
+\section{Introduction} \label{sec:intro}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Methods}
-\label{sec:methods}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Sample selection}\label{sec:methods}
+Our sample data was obtained using a strict set of selection criteria, as outlined in this section.
+In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulations utilized in this study.
+Sec.~\ref{sec:methods-am} explains the abudance matching prescription used to associate stellar masses with the dark matter subhalos.
+Sec.~\ref{sec:methods-crit} provides a detailed outline of our selection criteria and process for picking pairs.
+Finally, Sec.~\ref{sec:methods-counts} gives an overview of the properties of our sample.
+
+%%%%%%%%%%%
+%%%%%%%%%%%
+\subsection{Simulation details}\label{sec:methods-sims}
+% what is it that we are trying to study? why use illustris?
+To understand the occurance rate and separations of typical galaxy pairs in a cosmological context, we require a simulation that provides a large statistical sample of pairs in both the dwarf and massive galaxy regime.
+Thus, we are limited in our simulation choice to large-volume cosmological simulations. 
+However, we also require high resolution simulations such that the dwarf subhalos are resolved well enough to ensure robust statistics at the low mass end, and so we are not limited by our inability to resolve objects down to halo masses of $M_{\rm halo}\approx1\times 10^9\, \Msun$.
+
+% Baryonic processes
+Baryonic process are known to affect the dark matter halo structure of low mass ($M_*<1\times10^9\Msun$) subhalos in simulations~\citep[see e.g.][and references therein]{Sales:2022}.
+Additionally, the shallow potential well of dwarf galaxies compared to their massive counterparts may lend themselves more easily to disruption from baryonic processes such as supernova feedback, which could change the occurance rate of low mass subhalos in hydrodynamic simulations \kc{check and see if they looked at this in the TNG100 galaxy paper}.
+To study the effect of baryonic processes on the rate and separation of pairs, we require cosmological simulations which have both dark matter only runs and to full hydrodynamics.
+
+% details of Illustris and Illustris TNG
+The \textit{Illustris Project} ~\citep{vogelsberger14A,nelson15} and \textit{IllustrisTNG Project}~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} are a set of N-body and hydrodynamic cosmological simulations which are perfectly suited for such a study.
+We use the dark matter only and full hydrodynamic runs of both the \ill-1 and \tng100-1 simulations to explore the connection between pairs and baryonic processes. 
+Each of these simulations follows the dynamical evolution of $1820^3$ dark matter particles from $z=127$ to $z=0$ through a periodic volume of roughly $100^3$ Mpc$^3$. 
+The \ill{} simulations follow a cosmology consistent with \textit{WMAP-9}~\citep{hinshaw13}, while the \tng{} simulations are consistent with \textit{Planck2015}~\citep{Planck2015}.
+Specifically, we use the \textit{Illustris-1-Dark}, \textit{Illustris-1}, \textit{TNG100-1-Dark}, and \textit{TNG100-1} simulations (hereafter \illd, \illh, \tngd, and \tngh{} respectively, see Table~\ref{table:sim} for details).
+
+% deets on the hydrodynamics of 
+\kc{hydrodynamics details on the difference between the two hydro simulations. also include differences between the two dark simulations, if there are any besides the cosmology. }
+
+% subfind, sublink, and groups and subhalos
+We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm ~\citep{springel01,dolag09}. 
+These catalogs consist of halos (or "groups"), defined using the Friends-of-Friends (FoF) algorithm~\citep{davis85} to link nearby particles, and their associated subhalos, which are over-dense and gravitationally bound dark matter structures.
+We also use the merger trees provided by the \texttt{SUBLINK} algorithm \citep{gomez15}, which tracks subhalos between snapshots using their particle data, in order to trace the mass growth and merger histories of our subhalos.
+
+\begin{table*}[htb]
+\begin{tabular}{l|llll}
+ & \illd & \illh & \tngd & \tngh\\\hline\hline
+ L$_{\rm Box}$ [Mpc] & 106.5 & 106.5 & 110.7 & 110.7 \\
+m$_{\rm DM}$ [M$_\odot$] & 7.5$\times10^6$ & 6.3$\times10^6$ & 8.9$\times10^6$ & $7.5\times10^6$\\
+m$_{\rm gas}$ & -- & $1.3\times 10^{6}$ & -- & $1.4\times 10^{6}$ \\\hline
+
+\end{tabular}
+\caption{\label{table:sim}Parameters of the Illustris simulations used in this analysis.}
+\end{table*}
+
+%%%%%%%%%%%
+%%%%%%%%%%%
+\subsection{Abundance matching prescription}\label{sec:methods-am}
+As our goal is to compare between dark matter only and full hydrodynamic
+simulations,
+
+\subsection{Selection criteria}\label{sec:methods-crit}
+\begin{enumerate}
+  \item Select groups in some group range that encompasses MCs and MW-M31
+  \item For every subhalo in every group with halo mass >1e9Msun, use merger trees to get the maximum masses.
+  \item Generate 1000 stellar mass realization using abundance matching so we can account for the spread in the relationship
+  \item Generate catalog at each redshift containing: 
+  \begin{itemize}
+    \item For each realization, and in each group with a single subhalo, add the subhalo and it's properties to a catalog of single halos.
+    \item For each realization, and in each group with 2+ halos, find most massive halo by stellar mass, and the second most massive halo by stellar mass, then add to pair catalog. 
+    \item If a group has 3+ halos, check the stellar mass of the third most massive object, and see if it is a major/minor companion of the secondary. If not, teritary flag = 0. Otherwise =1.
+  \end{itemize}
+  \item Select dwarf primaries: for full catalog, most massive halo (in "pairs") or single halos with stellar mass $1\times10^{8} < \msam < 5\times10^{9} \Msun$. 
+  \item Select dwarf pairs: for full pair catalog, any pair with stellar mass ratio between 1-1/4 (major pairs) or between 1/4-1/10 (minor pairs).
+All pairs is the union of these two sets.
+Any pair or single halo that is outside of these two sets is an "unpaired" halo.
+Note that unpaired can still have very minor companions.
+\end{enumerate}
+
+The lower mass threshold for subhalos that constitute our dwarf pairs have a halo mass greater than $1\times10^9\Msun$, such that each of our halos are resolved into at least 100 particles in each simulation.
+\kc{why 100?}
+
+\subsection{Counts and distributions}\label{sec:methods-counts}
+
 \begin{itemize}
@@
      & Dwarf Pairs & Massive Pairs \\\hline\hline
-    Group Mass & $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ & $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$  \\
+    % Group Mass & $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ & $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$  \\
     % Subhalo Max Mass &  &  \\
-    Subhalo Current Mass & $>1\times10^{10} \Msun$ & $> 5\times10^{11} \Msun$ \\
-    Primary &$1\times10^{8} < \rm M_* < 5\times10^{9} \Msun$ & $5\times10^{9} < \rm M_* < 1\times10^{11} \Msun$\\\hline
+    % Subhalo Current Mass & $>1\times10^{10} \Msun$ & $> 5\times10^{11} \Msun$ \\
+    Primary &$1\times10^{8} < \msam < 5\times10^{9} \Msun$ & $5\times10^{9} < \msam < 1\times10^{11} \Msun$\\\hline
     \end{tabular}
@@
 % equivalent snapshot table
-\begin{table}[]
+\begin{table*}[]
   \centering
-  \begin{tabular}{l|cc}
+  \begin{tabular}{l|cc|cccc} % increase this to 7 columns
     \hline \hline
-   & Illustris & TNG  \\ 
+   & \multicolumn{2}{c|}{Snapshot number} & \multicolumn{4}{c}{Number of primaries}\\
+   & \ill & \tng  & \illd & \illh & \tngd & \tngh \\ 
   \hline
-  z = 0   &   135  &   99   \\
-  z = 1   &   85   &   50   \\
-  z = 2   &   68   &   33   \\
-  z = 3   &   60   &   25   \\
-  z = 4   &   54   &   21   \\
+  z = 0   &   135  &   99   &&&&\\
+  z = 1   &   85   &   50   &&&&\\
+  z = 2   &   68   &   33   &&&&\\
+  z = 3   &   60   &   25   &&&&\\
+  % z = 3.7   &   54   &   21   \\
   \hline \hline
   \end{tabular}
-  \caption{\label{tab:equiv-snapshot} The snapshot number of the original \ill\ and the \tng\ simulations at redshifts $z=0-4$.}
-    \end{table}
+  \caption{\label{tab:equiv-snapshot} The snapshot number of the original \ill\ and the \tng\ simulations at redshifts $z=0-3$, as well as the number of total dwarf (massive) primaries that were selected with $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$ ($5\times 10^{9} < \msam < 1\times 10^{11} \rm M_\odot$) in XX abundance matching realizations.
+\kc{fill in with numbers after doing more realizations} \kc{include takeaway}}
+  \end{table*}
 
+%%%%%%%%%%%%%%%%%%%
+%% dwarf figures %%
+%%%%%%%%%%%%%%%%%%%
 \begin{figure*}[htb]
@@
   \centering
+  \includegraphics[width=\textwidth]{distributions_mass_dwarf.png}
+  \caption{Normalized distribution of the subhalo mass of dwarf primaries at four different redshifts.
+The subhalos in the dark and hydro simulations for both \ill{} (turquoise and light blue) and \tng{} (red and light pink) were chosen such that the stellar mass from the abundance matching prescription is $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$.
+The black dashed lines represent the distribution of halos chosen by \mssim.
+  The mass distributions for \illd{} and \illh{} are nearly identical at all redshifts, however, while the mass distribution for halos chosen by their simulation stellar mass closely match the \ill{} distribution at $z=0$, the \mssim{} distribution skews towards lower subhalo masses than the \msam{} distributions at $z=1,2,3$.
+Similarly, the \tngd{} and \tngh{} distrbutions are consistent at all redshifts, however the population of subhalos chosen by simulation stellar mass have higher masses at $z=0$ and lower masses at $z=1,2,3$ than the \msam{} distributions.
+  The approximate equivalence of the dark and hydro distributions in both simulations confirm that we are investigating a similar population of halos between the dark and hydro runs of each simulation.
+Additionally, the distributions for \ill{} and \tng{} follow the same evolution over time, so the population of subhalos we are considering is consistent between simulations.
+    }
+  \label{fig:dist-mass-dwarf}
+\end{figure*}
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{distributions_stellarmass_dwarf.png}
+  \caption{Normalized distribution of the stellar mass from abundance matching of dwarf primaries at four different redshifts.
+The subhalos in the dark and hydro simulations for both \ill{} (turquoise and light blue) and \tng{} (red and light pink) were chosen such that the stellar mass from the abundance matching prescription is $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$.
+  The black solid lines represent the simulation values of the stellar mass for the same population of halos chosen by their abundance matching stellar mass. 
+  The black dashed lines represent the distribution of halos chosen by their simulation stellar mass, $1\times 10^{8} < \mssim < 5\times 10^{9} \rm M_\odot$.
+  The mass distributions for \illd{} and \illh{}, as well as \tngd{} and \tngh{}, are nearly identical at all redshifts. 
+  However, the distributions chosen by the simulation stellar mass differ drastically between the two simulations.
+At $z=0$, there are many more low \mssim{} halos in \tng{} than in \ill{}.
+In addition, the simulation stellar masses in the \ill{} simulation tend to be more massive than those from abundance matching at all redshifts.
+  The abundance matching stellar mass and simulation stellar mass distributions in \tng{} are similar at $z=1,2,3$, with more low stellar mass halos in the abundance matching case, while at $z=0$, the simulation stellar masses are significantly lower than the distribution from abundance matching.
+  \kc{what does this mean?? } 
+    }
+    \label{fig:dist-stellmass-dwarf}
+
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%
+%% massive figures %%
+%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[htb]
+  \centering
   \includegraphics[width=\textwidth]{counts_massive.png}
@@
 
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{distributions_mass_massive.png}
+  \caption{There is little variation between dark and hydro, and Illustris and TNG.
+Like the dwarf primaries, the distribution of selected primaries by simulation mass at z=0 in Illustris nearly overlays the distribution from the am mass.
+In addition, the z=0 sim mass selection in TNG is a higher mass distribution than those selected by am mass.
+It appears that the mass distributions in both Illustris and TNG change significantly between z=3 and z=0, but the sim selected list in TNG does not change.
+However, for both simulation, at z=1,2,3, the am mass selected primaries have, on average, higher mass than the sim mass selected primaries.
+\kc{add takeaway}
+    }
+  \label{fig:dist-mass-massive}
+\end{figure*}
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{distributions_stellarmass_massive.png}
+  \caption{The dark and hydro distributions, as well as the Illustris and TNG distributions, are all similar.
+There is also good agreement with the stellar mass of halos selected with the simulation stellar mass (this tells me that the AM relationship better matches what we see in sims at high mass but not at low mass).
+The black solid line does not match well, but I'll be removing it anyways.
+\kc{ add takeaway message}
+    }
+  \label{fig:dist-stellmass-massive}
+\end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Results}

### 2022-11-17 paper/pears.tex
adding math defs and some refs

@@
 m$_{\rm gas}$ & -- & $1.3\times 10^{6}$ & -- & $1.4\times 10^{6}$ \\\hline
-
 \end{tabular}
@@
 \subsection{Abundance matching prescription}\label{sec:methods-am}
-As our goal is to compare between dark matter only and full hydrodynamic
-simulations,
+% Why do we need stellar masses?
+One of the goals of this study is to determine the impact of baryonic physics on the occurance rate and typical separations of galaxy \kc{subhalo?} pairs in cosmological simulations. 
+However, selecting halo pairs by stellar mass ratio using the stellar masses provided by the simulations is not possible in the dark matter only runs. 
+Thus, in order ensure the dark matter only and full hydrodynamic samples are self-consistent, we need to associate each of the selected subhalos with a realistic stellar mass.
 
+% What is abundance matching
+Abundance matching is one such method of associating a dark matter halo with a stellar mass, assuming a galaxy would form in a halo of that mass.
+
+However, there is large scatter in the stellar-mass-halo-mass (SMHM) relationship, especially in the dwarf halo regime.
+
+% How do we utilize it? 
+In particular, we use the abundance matching relationship presented in~\citet{moster13}, which provides an analytic recipe to paint stellar masses onto dark matter halos. 
+The~\citet{moster13} relationship is a redshift-evolving function of the halo mass, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.
+\kc{why moster instead of another AM relationship? most closely represent data at lower mass? }
+
+To assign stellar masses to each of the dark matter halos, we assume that the stellar mass of both the primary and secondary halo can change as a function of redshift after the secondary has entered the primary's halo and do not immediately cease star formation.
+This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{geha13} which finds that isolated dwarfs ($>1\Mpc$ from a MW-type galaxy) are often star forming and rarely quenched.
+Additionally,~\citet{Munshi2021} found that the stellar mass of subhalos at $z=0$ in the XX simulations are more closely correlated with the peak halo mass than the $z=0$ halo mass for halos with peak halo mass $10^8<M_{\rm peak}<10^{11} \Msun$.
+
+Thus, we treat each of the subhalos as centrals according to the~\citet{moster13} prescription, using the current snapshot redshift and the peak halo mass of the subhalo to calculate the stellar mass.
+This additionally allows us remain robust to scenarios in which a secondary may have formed most of its stars, and then lost a significant portion of its dark matter content through tidal interactions with a primary, but will retain the bulk of its stellar content.
+
+We create 1000 stellar mass realizations from the SMHM relationship, thus accounting for the systematic uncerntainy in subhalo stellar masses, which will allow us to average our results over all 1000 realizations
+
+%%%%%%%%%%%
+%%%%%%%%%%%
 \subsection{Selection criteria}\label{sec:methods-crit}

### 2023-02-01 paper/pears.tex
first draft captions

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\graphicspath{{./}{../plots/pairs_plots/}}
+\graphicspath{{./}{../plots/paper1/}}
 \input{math_definitions.tex}
@@
 \title{
-  Frequency of galaxy pairs in the Illustris and IllustrisTNG cosmological simulations
+  Frequency of dwarf and massive galaxy pairs in the IllustrisTNG cosmological simulation
 }
@@
 \begin{abstract}
+  \todo{REMEMBER TO USE 100-1000 REALS IN PLOTS}
+  \todo{Include ticks on top and right axis as well}
 \end{abstract}
@@
 
-We create 1000 stellar mass realizations from the SMHM relationship, thus accounting for the systematic uncerntainy in subhalo stellar masses, which will allow us to average our results over all 1000 realizations
-
+We create 1000 stellar mass realizations from the SMHM relationship, thus accounting for the systematic uncerntainy in subhalo stellar masses.
+Each realization is treated as an independent sample, such that computed properties (pair frequency, separations, etc) are given as the median each realization.
+We report the mean of all realizations and error bars indicate the 1$\sigma$ dispersion across the realizations.
 %%%%%%%%%%%
@@
 \subsection{Selection criteria}\label{sec:methods-crit}
+In this section, we outline the selection criteria used to select dwarf and massive subhalo pairs. 
+The same selection criteria is utilized for all four simulations (\illd, \illh, \tngd, and \tngh)
+In short, blah. 
+Detailed steps are as follows.
+
+\subsubsection{Isolation}
+As we are interested in the frequency and separations of galaxy pairs that are undisturbed by nearby massive perturbers, we select subhalo pairs as the most massive subhalos of their group halos. 
+We have confirmed that nearly 100\% of the the most massive subhalos in each group are outside of the Hill radius of any nearby subhalo with greater mass, and are thus a rough isolation criteria is inherent in our selection.
+
+\textbf{Definitions:} each of these defines the subhalo at a single snapshot and for a single realization.
+\begin{itemize}
+  \item Primary - Most massive subhalo in a group by stellar mass
+  \item Secondary - 
+  \item Major pair - A pair of subhalos consisting of a primary and secondary with stellar mass ratio $1/4 < \rm M_{*,sec}/M_{*, prim} < 1$
+  \item Minor pair - A pair of subhalos consisting of a primary and secondary with stellar mass ratio $1/10 < \rm M_{*,sec}/M_{*, prim} < 1/4$
+\end{itemize}
+Note that the subhalo that is assigned as primary or secondary may change between stellar mass realizations.
+
 \begin{enumerate}
@@
 \kc{why 100?}
+
+\subsubsection{Primary subhalos}\label{sec:methods-crit-prims}
+
+\subsubsection{Primary subhalos}\label{sec:methods-crit-pairs}
+
+\subsubsection{Stellar masses from the hydro sims}
 
@@
   \hline
-  z = 0   &   135  &   99   &&&&\\
-  z = 1   &   85   &   50   &&&&\\
-  z = 2   &   68   &   33   &&&&\\
-  z = 3   &   60   &   25   &&&&\\
+  z = 0   &   135  &   99   & $11431.5_{-24.42}^{68.38}$ & $12650.0_{-25.84}^{46.84}$ & $13255.0_{-32.60}^{56.72}$ & $12035.0_{-69.24}^{20.36}$\\
+  z = 1   &   85   &   50   &  $14769.0_{-30.24}^{47.28}$ & $16568.0_{-32.20}^{69.60}$ & $17445.5_{-40.86}^{51.90}$ & $15946.5_{-59.38}^{39.22}$ \\
+  z = 2   &   68   &   33   &  $12602.5_{-31.98}^{45.94}$ & $14174.0_{-12.48}^{62.32}$ & $15413.5_{-34.62}^{28.86}$ & $14334.0_{-29.44}^{45.24}$ \\
+  z = 3   &   60   &   25   &     $8533.5_{-54.50}^{39.46}$ & $9390.0_{-63.40}^{41.32}$ & $10901.0_{-44.64}^{46.56}$ & $10106.5_{-47.90}^{39.74}$  \\
   % z = 3.7   &   54   &   21   \\
@@
   \end{tabular}
-  \caption{\label{tab:equiv-snapshot} The snapshot number of the original \ill\ and the \tng\ simulations at redshifts $z=0-3$, as well as the number of total dwarf (massive) primaries that were selected with $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$ ($5\times 10^{9} < \msam < 1\times 10^{11} \rm M_\odot$) in XX abundance matching realizations.
+  \caption{\label{tab:equiv-snapshot} The snapshot number of the original \ill\ and the \tng\ simulations at redshifts $z=0-3$, as well as the median number dwarf (massive) primaries that were selected with $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$ ($5\times 10^{9} < \msam < 1\times 10^{11} \rm M_\odot$) in XX abundance matching realizations.
 \kc{fill in with numbers after doing more realizations} \kc{include takeaway}}
   \end{table*}
+
+  \begin{figure*}[htb]
+    \centering
+    \includegraphics[width=\textwidth]{counts.png}
+    \caption{Median number of dwarf and massive primaries and pairs per abundance matching realization as a function of redshift, with shaded regions showing the $1^{\rm st}$ and 99$^{\rm th}$ percentiles.
+There are approximately 8 times as many dwarf primaries as massive primaries.
+There are fewer primaries and pairs at higher redshift, and the number of dwarf and massive primaries peaks around $z=1$.
+The evolution of the number of primaries is roughly similar between dwarf and massive galaxies, though the number of dwarf primaries drops steeply from $z=1$ to $z=0$.
+\textbf{However, the behaviour of the pair counts differs drastically between dwarf and massive pairs.} The number of dwarf pairs peaks around $z=2$, while the number of massive pairs increases nearly monotonically from $z=4-0$.
+Thus, the rate of dwarf pairs and massive pairs \textit{per primary} will evolve distinctly in the dwarf and massive pair case.
+      }
+    \label{fig:counts}
+  \end{figure*}
 
@@
 %%%%%%%%%%%%%%%%%%%
-\begin{figure*}[htb]
-  \centering
-  \includegraphics[width=\textwidth]{counts_dwarfs.png}
-  \caption{Median counts of dwarf primaries in \ill{} and \tng{} \kc{add "dwarf" somewhere to plot}.
-The number of dwarf primaries peaks at $z~0.75$.
-TNG has higher halo count than Illustris.
-However, the difference between the number of halos in both dark simulations is substantial.
-Additionally, in Illustris, hydro halos outnumber dark halos.
-In TNG, the opposite is true, where dark halos outnumber hydro halos.
-In Illustris, this can be accounted for by the discrepant number of unpaired halos (dotted), while in TNG, the difference is dominated by pairs.
-    }
-  \label{fig:counts-dwarfs}
-\end{figure*}
-
-\begin{figure*}[htb]
-  \centering
-  \includegraphics[width=\textwidth]{distributions_mass_dwarf.png}
-  \caption{Normalized distribution of the subhalo mass of dwarf primaries at four different redshifts.
-The subhalos in the dark and hydro simulations for both \ill{} (turquoise and light blue) and \tng{} (red and light pink) were chosen such that the stellar mass from the abundance matching prescription is $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$.
-The black dashed lines represent the distribution of halos chosen by \mssim.
-  The mass distributions for \illd{} and \illh{} are nearly identical at all redshifts, however, while the mass distribution for halos chosen by their simulation stellar mass closely match the \ill{} distribution at $z=0$, the \mssim{} distribution skews towards lower subhalo masses than the \msam{} distributions at $z=1,2,3$.
-Similarly, the \tngd{} and \tngh{} distrbutions are consistent at all redshifts, however the population of subhalos chosen by simulation stellar mass have higher masses at $z=0$ and lower masses at $z=1,2,3$ than the \msam{} distributions.
-  The approximate equivalence of the dark and hydro distributions in both simulations confirm that we are investigating a similar population of halos between the dark and hydro runs of each simulation.
-Additionally, the distributions for \ill{} and \tng{} follow the same evolution over time, so the population of subhalos we are considering is consistent between simulations.
-    }
-  \label{fig:dist-mass-dwarf}
-\end{figure*}
-
-\begin{figure*}[htb]
-  \centering
-  \includegraphics[width=\textwidth]{distributions_stellarmass_dwarf.png}
-  \caption{Normalized distribution of the stellar mass from abundance matching of dwarf primaries at four different redshifts.
-The subhalos in the dark and hydro simulations for both \ill{} (turquoise and light blue) and \tng{} (red and light pink) were chosen such that the stellar mass from the abundance matching prescription is $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$.
-  The black solid lines represent the simulation values of the stellar mass for the same population of halos chosen by their abundance matching stellar mass. 
-  The black dashed lines represent the distribution of halos chosen by their simulation stellar mass, $1\times 10^{8} < \mssim < 5\times 10^{9} \rm M_\odot$.
-  The mass distributions for \illd{} and \illh{}, as well as \tngd{} and \tngh{}, are nearly identical at all redshifts. 
-  However, the distributions chosen by the simulation stellar mass differ drastically between the two simulations.
-At $z=0$, there are many more low \mssim{} halos in \tng{} than in \ill{}.
-In addition, the simulation stellar masses in the \ill{} simulation tend to be more massive than those from abundance matching at all redshifts.
-  The abundance matching stellar mass and simulation stellar mass distributions in \tng{} are similar at $z=1,2,3$, with more low stellar mass halos in the abundance matching case, while at $z=0$, the simulation stellar masses are significantly lower than the distribution from abundance matching.
-  \kc{what does this mean?? } 
-    }
-    \label{fig:dist-stellmass-dwarf}
-
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%
-%% massive figures %%
-%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[htb]
-  \centering
-  \includegraphics[width=\textwidth]{counts_massive.png}
-  \caption{No turn over, instead, monotonically increasing towards a peak at low z.
-No significant fraction of halos that are lone subhalos.
-The largest differences between the hydro and dark simulations in both cases are at low z, where the counts start to diverge.
-TNG has a higher number of massive halos primaries than Illustris.
-The difference between dark and hydro is large in TNG, and at low z, the main driver of this difference is in the pairs, as opposed to the lone halos.
-This is not the case in Illustris, where both the pairs and unpaired halos contribute equally to the difference between dark and hydro, in opposite way!
-Weird… \kc{add "massive" somewhere to plot}
-    }
-  \label{fig:counts-massive}
-\end{figure*}
-
-\begin{figure*}[htb]
-  \centering
-  \includegraphics[width=\textwidth]{distributions_mass_massive.png}
-  \caption{There is little variation between dark and hydro, and Illustris and TNG.
-Like the dwarf primaries, the distribution of selected primaries by simulation mass at z=0 in Illustris nearly overlays the distribution from the am mass.
-In addition, the z=0 sim mass selection in TNG is a higher mass distribution than those selected by am mass.
-It appears that the mass distributions in both Illustris and TNG change significantly between z=3 and z=0, but the sim selected list in TNG does not change.
-However, for both simulation, at z=1,2,3, the am mass selected primaries have, on average, higher mass than the sim mass selected primaries.
-\kc{add takeaway}
-    }
-  \label{fig:dist-mass-massive}
-\end{figure*}
-
-\begin{figure*}[htb]
-  \centering
-  \includegraphics[width=\textwidth]{distributions_stellarmass_massive.png}
-  \caption{The dark and hydro distributions, as well as the Illustris and TNG distributions, are all similar.
-There is also good agreement with the stellar mass of halos selected with the simulation stellar mass (this tells me that the AM relationship better matches what we see in sims at high mass but not at low mass).
-The black solid line does not match well, but I'll be removing it anyways.
-\kc{ add takeaway message}
-    }
-  \label{fig:dist-stellmass-massive}
-\end{figure*}
 
@@
 \label{sec:results}
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{pairratio.png}
+  \caption{Median fraction (and 1-99 percentile shaded regions) of dwarf (green) or massive (pink) primaries with a major (left) or minor (right) companion.
+The fraction of massive primaries with a major or minor companion remains approximately constant for $z>1$, while at $z<\sim0.5$ the pair fraction increases sharply to $z=0$.
+However, the pair fraction for dwarf pairs evolves significantly differently to massive galaxy pairs.
+The fraction of dwarf primaries with a companion is approximately constant for $z>2$, but decreases monotonically from $z=2$ to $z=0$.
+The vast difference between the dwarf and massive pair fractions suggests \todo{XX - that pairs at different mass scales evolve differently ?
+Thus, can't just assume a massive pair fraction for a lower mass regime}.
+    }
+  \label{fig:pairratio}
+\end{figure*}
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{separations.png}
+  \caption{Median physical separation (in kpc) and 1-99 percentile shaded regions of 1000 abundance matching realizations as a function of redshift for dwarf pairs (left, green), and massive pairs (right, pink).
+Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
+Minor dwarf pairs tend to be $\sim10-20\kpc$ closer than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs.
+In general, as the redshift \textit{decreases} toward $z=0$, the average physical separation of a dwarf or massive pair \textit{increases}.
+The increase in low redshift median separations suggests that low separation pairs undergo mergers that remove them from the sample at later snapshots, thus increasing the median separation over time.
+The evolution of massive pair separations is approximately linear for $z>1$, increasing sharply for $z<0$, while the evolution of the dwarf pairs closely resembles a power law distrbution across the whole redshift range from $z=0-4$.
+    }
+  \label{fig:sep}
+\end{figure*}
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{separations_distributions.png}
+  \caption{Normalized physical separation distribution for dwarf and massive pairs (top/green and bottom/pink, respectively) from $z=0$ (left) to $z=3$ (right).
+Major pairs are shown as solid lines, while minor pairs are dashed.
+  Both dwarf and massive pairs have narrow distributions about low separations at high redshifts, and a wider distribution of separations at lower redshift. 
+  \todo{would it be instructive to make this plot, unnormalized, with z=0-3 on same plot to see if low sep pop numbers change drastically}
+  \textbf{Takeaway from this plot?}.
+The number of widely separated pairs at low redshift is much greater than at high redshift, so these pairs either form late, or move apart from each other.
+Also note than many of the close pairs at high z may merge by $z=0$.
+    }
+  \label{fig:sep-dist}
+\end{figure*}
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{separations_scaled.png}
+  \caption{Median scaled separation (separation of a pair divided by the virial radius of its group) as a function of redshift.
+Dwarf pairs (major (solid) and minor (dashed)) tend to have smaller scaled separations at lower redshifts, leveling out between $z=0-1$.
+In particular, the secondaries of dwarf major pairs at $z>2$ tend to live more than one virial radius away from the primary.
+Massive major pairs at low redshift tend to have smaller scaled separations  at $z<\sim2$, but vary significantly at higher redshifts.
+  Minor pairs (right), both dwarf and massive, tend to have smaller separations, tending to live closer than one virial radius between the primary and secondary.
+Massive minor pairs tend to have smaller scaled separations compared to dwarf pairs at all redshifts.
+  \textbf{The difference between the scaled separations of dwarf and massive pairs highlights the mass dependence of the physical distribution of halo pairs, i.e., dwarf pairs are not simply a smaller scale version of massive pairs.}
+    }
+  \label{fig:sep-scaled}
+\end{figure*}
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{velocities.png}
+  \caption{Median relative velocity (in \kms) and 1-99 percentile shaded regions of 1000 abundance matching realizations as a function of redshift for dwarf pairs (left, green) and massive pairs (right, pink).
+Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
+Major and minor pairs (in both the dwarf and massive regime) tend to have approximately the same median relative velocity.
+In addition, as the redshift \textit{decreases} toward $z=0$, the average relative velocity of a pair \textit{decreases} as well.
+The overall behavior of the redshift evolution is nearly identical for dwarf and massive pairs (though note that the massive pairs have \textit{much} higher relative velocities than the dwarf pairs at all redshifts.)
+    }
+  \label{fig:vel}
+\end{figure*}
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{velocities_distributions.png}
+  \caption{
+  Normalized velocity distribution for dwarf and massive pairs (top/green and bottom/pink, respectively) from $z=0$ (left) to $z=3$ (right).
+Major pairs are shown as solid lines, while minor pairs are dashed.
+  The distribution of relative velocities for dwarf and massive pairs move to slightly lower velocities at lower redshifts.
+The distribution of velocities for major and minor pairs is roughly equivalent.
+  \textbf{Takeaway from this plot?}. 
+  \kc{caption}
+    }
+  \label{fig:vel-dist}
+\end{figure*}
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{velocities_scaled.png}
+  \caption{Median scaled velocity (relative velocity of a pair divided by the virial velocity, defined as the circular velocity at the virial radius of the group \todo{need to remove the 2 in the virial radius calc!}) as a function of redshift.
+  Major pairs are on the left (solid lines), minor pairs are on the right in dashed lines.
+  All sets of pairs show an increase in scaled velocity at lower redshifts. 
+  \textbf{Despite the difference between dwarf and massive pairs in physical distribution as indicated by the plot of scaled separations (Figure~\ref{fig:sep-scaled}), the scaled velocity distribution of pairs indicates that dwarf and massive galaxy pairs operate similarly in velocity space.
+There is little to no mass dependence on the scaled velocity of dwarf or massive pairs.}
+    }
+  \label{fig:vel-scaled}
+\end{figure*}
 

### 2023-02-04 paper/pears.tex
updated figures to include differences

@@
 Note that the subhalo that is assigned as primary or secondary may change between stellar mass realizations.
+Also note\kc{that this method may yield pairs where the secondary has a higher subhalo mass than the primary.
+This one happens ~XX\% of the time.}
 
@@
     \caption{Median number of dwarf and massive primaries and pairs per abundance matching realization as a function of redshift, with shaded regions showing the $1^{\rm st}$ and 99$^{\rm th}$ percentiles.
+The number of dwarf and massive primaries peaks around $z=1$, and there are fewer primaries and pairs at higher redshift, and .
+The evolution of the number of primaries is roughly similar between dwarf and massive galaxies, though the number of dwarf primaries drops steeply from $z=1$ to $z=0$.
+The number of dwarf pairs peaks around $z=2$, while the number of massive pairs increases nearly monotonically from $z=4-0$.
 There are approximately 8 times as many dwarf primaries as massive primaries.
-There are fewer primaries and pairs at higher redshift, and the number of dwarf and massive primaries peaks around $z=1$.
-The evolution of the number of primaries is roughly similar between dwarf and massive galaxies, though the number of dwarf primaries drops steeply from $z=1$ to $z=0$.
-\textbf{However, the behaviour of the pair counts differs drastically between dwarf and massive pairs.} The number of dwarf pairs peaks around $z=2$, while the number of massive pairs increases nearly monotonically from $z=4-0$.
-Thus, the rate of dwarf pairs and massive pairs \textit{per primary} will evolve distinctly in the dwarf and massive pair case.
       }
     \label{fig:counts}
+  \end{figure*}
+
+  \begin{figure*}[htb]
+    \centering
+    \includegraphics[width=\textwidth]{stellarmass_distribution.png}
+    \caption{\kc{caption}
+      }
+    \label{fig:massratio}
   \end{figure*}
@@
 \section{Results}
+\subsection{Pair ratios}
+Thus, the rate of dwarf pairs and massive pairs \textit{per primary} will evolve distinctly in the dwarf and massive pair case.
+
 \label{sec:results}
@@
 The fraction of dwarf primaries with a companion is approximately constant for $z>2$, but decreases monotonically from $z=2$ to $z=0$.
-The vast difference between the dwarf and massive pair fractions suggests \todo{XX - that pairs at different mass scales evolve differently ?
-Thus, can't just assume a massive pair fraction for a lower mass regime}.
+\kc{include more numbers including the difference between the ratios.
+"Evolves distinctly"}
     }
@@
 
+\subsection{Kinematic evolution}
+
 \begin{figure*}[htb]
   \centering
-  \includegraphics[width=\textwidth]{separations.png}
+  \includegraphics[width=\textwidth]{separation.png}
   \caption{Median physical separation (in kpc) and 1-99 percentile shaded regions of 1000 abundance matching realizations as a function of redshift for dwarf pairs (left, green), and massive pairs (right, pink).
@@
 In general, as the redshift \textit{decreases} toward $z=0$, the average physical separation of a dwarf or massive pair \textit{increases}.
-The increase in low redshift median separations suggests that low separation pairs undergo mergers that remove them from the sample at later snapshots, thus increasing the median separation over time.
 The evolution of massive pair separations is approximately linear for $z>1$, increasing sharply for $z<0$, while the evolution of the dwarf pairs closely resembles a power law distrbution across the whole redshift range from $z=0-4$.
+\kc{add difference plot!}
     }
@@
   \centering
-  \includegraphics[width=\textwidth]{separations_distributions.png}
+  \includegraphics[width=\textwidth]{separation_distribution.png}
   \caption{Normalized physical separation distribution for dwarf and massive pairs (top/green and bottom/pink, respectively) from $z=0$ (left) to $z=3$ (right).
@@
   \todo{would it be instructive to make this plot, unnormalized, with z=0-3 on same plot to see if low sep pop numbers change drastically}
-  \textbf{Takeaway from this plot?}.
-The number of widely separated pairs at low redshift is much greater than at high redshift, so these pairs either form late, or move apart from each other.
-Also note than many of the close pairs at high z may merge by $z=0$.
+  Also note than many of the close pairs at high z may merge by $z=0$. \kc{add median line to plot}
     }
@@
   \centering
-  \includegraphics[width=\textwidth]{separations_scaled.png}
-  \caption{Median scaled separation (separation of a pair divided by the virial radius of its group) as a function of redshift.
-Dwarf pairs (major (solid) and minor (dashed)) tend to have smaller scaled separations at lower redshifts, leveling out between $z=0-1$.
-In particular, the secondaries of dwarf major pairs at $z>2$ tend to live more than one virial radius away from the primary.
-Massive major pairs at low redshift tend to have smaller scaled separations  at $z<\sim2$, but vary significantly at higher redshifts.
-  Minor pairs (right), both dwarf and massive, tend to have smaller separations, tending to live closer than one virial radius between the primary and secondary.
-Massive minor pairs tend to have smaller scaled separations compared to dwarf pairs at all redshifts.
-  \textbf{The difference between the scaled separations of dwarf and massive pairs highlights the mass dependence of the physical distribution of halo pairs, i.e., dwarf pairs are not simply a smaller scale version of massive pairs.}
-    }
-  \label{fig:sep-scaled}
-\end{figure*}
-
-\begin{figure*}[htb]
-  \centering
-  \includegraphics[width=\textwidth]{velocities.png}
+  \includegraphics[width=\textwidth]{velocity.png}
   \caption{Median relative velocity (in \kms) and 1-99 percentile shaded regions of 1000 abundance matching realizations as a function of redshift for dwarf pairs (left, green) and massive pairs (right, pink).
@@
   \centering
-  \includegraphics[width=\textwidth]{velocities_distributions.png}
+  \includegraphics[width=\textwidth]{velocity_distribution.png}
   \caption{
@@
 The distribution of velocities for major and minor pairs is roughly equivalent.
-  \textbf{Takeaway from this plot?}. 
   \kc{caption}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
+\label{sec:discussion}
+
+Pair ratio fig.
+-- The vast difference between the dwarf and massive pair fractions suggests \todo{XX - that pairs at different mass scales evolve differently ?
+Thus, can't just assume a massive pair fraction for a lower mass regime}
+
+Mean separation fig.
+-- The increase in low redshift median separations suggests that low separation pairs undergo mergers that remove them from the sample at later snapshots, thus increasing the median separation over time.
+
+Separation dist fig. -- The number of widely separated pairs at low redshift is much greater than at high redshift, so these pairs either form late, or move apart from each other.
+
+Scaled sep fig.
+-- \textbf{The difference between the scaled separations of dwarf and massive pairs highlights the mass dependence of the physical distribution of halo pairs, i.e., dwarf pairs are not simply a smaller scale version of massive pairs.}
+
+Scaled vel fig.
+--   \textbf{Despite the difference between dwarf and massive pairs in physical distribution as indicated by the plot of scaled separations (Figure~\ref{fig:sep-scaled}), the scaled velocity distribution of pairs indicates that dwarf and massive galaxy pairs operate similarly in velocity space.
+There is little to no mass dependence on the scaled velocity of dwarf or massive pairs.}
+
 \begin{figure*}[htb]
   \centering
-  \includegraphics[width=\textwidth]{velocities_scaled.png}
+  \includegraphics[width=\textwidth]{scaledsep.png}
+  \caption{Median scaled separation (separation of a pair divided by the virial radius of its group) as a function of redshift.
+Dwarf pairs (major (solid) and minor (dashed)) tend to have smaller scaled separations at lower redshifts, leveling out between $z=0-1$.
+In particular, the secondaries of dwarf major pairs at $z>2$ tend to live more than one virial radius away from the primary.
+Massive major pairs at low redshift tend to have smaller scaled separations  at $z<\sim2$, but vary significantly at higher redshifts.
+  Minor pairs (right), both dwarf and massive, tend to have smaller separations, tending to live closer than one virial radius between the primary and secondary.
+Massive minor pairs tend to have smaller scaled separations compared to dwarf pairs at all redshifts.
+    }
+  \label{fig:sep-scaled}
+\end{figure*}
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{scaledsep_distribution.png}
+  \caption{\kc{to write}}
+  \label{fig:sep-scaled-dist}
+\end{figure*}
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{scaledvel.png}
   \caption{Median scaled velocity (relative velocity of a pair divided by the virial velocity, defined as the circular velocity at the virial radius of the group \todo{need to remove the 2 in the virial radius calc!}) as a function of redshift.
   Major pairs are on the left (solid lines), minor pairs are on the right in dashed lines.
-  All sets of pairs show an increase in scaled velocity at lower redshifts. 
-  \textbf{Despite the difference between dwarf and massive pairs in physical distribution as indicated by the plot of scaled separations (Figure~\ref{fig:sep-scaled}), the scaled velocity distribution of pairs indicates that dwarf and massive galaxy pairs operate similarly in velocity space.
-There is little to no mass dependence on the scaled velocity of dwarf or massive pairs.}
-    }
+  All sets of pairs show an increase in scaled velocity at lower redshifts.}
   \label{fig:vel-scaled}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-\label{sec:discussion}
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{scaledvel_distribution.png}
+  \caption{\kc{to write}}
+  \label{fig:vel-scaled-dist}
+\end{figure*}
+
+\kc{add discussion subsection titles}
+\subsection{Dwarf and massive pair kinematic differences}
+\subsection{Comparison to literature}
+\subsection{Implications for observations}
 

### 2023-02-07 pears/utils/make_pairs.py
updates to make pairs job and py scripts

@@ -13,7 +13,7 @@ snapshot = int(sys.argv[1])
 sim = str(sys.argv[2])
 num_reals = int(sys.argv[3])
 
-realNumbs = np.arange(-1,num_reals+1,1)
+realNumbs = np.arange(-1,num_reals,1)
 paths = SetupPaths()
 
 ## find subhalos for this simulation and snapshot #
@@ -44,6 +44,7 @@ units_dict = {
     "Sub1 MassType": "Mass of bound particles - gas, DM, empty, tracers, stars, BHs -- in 1e10 Msun",
     "Sub2 MassType": "Mass of bound particles - gas, DM, empty, tracers, stars, BHs -- in 1e10 Msun",
     "Separation": "Physical separation between primary and secondary in kpc",
+    "Comoving Separation":"Comoving separation between primary and secondary in ckpc",
     "RelVel": "Relative velocity between primary and secondary in km/s",
     "Stellar Mass Ratio": "Stellar mass ratio of secondary over primary", # in this case- it's by primary subhalo mass
     "Realization": "Stellar mass realization (0-1000)",
@@ -100,6 +101,8 @@ def testthird(shortlist, stells, stel2, real):
 
 ## ensure that the dark and/or hydro file exists before operating
 for phys in ["dark","hydro"]:
+    if phys == "dark":
+        continue
     try: 
         subhalo_data[phys]
 
@@ -126,6 +129,7 @@ for phys in ["dark","hydro"]:
                  "Sub1 Vel": [],
                  "Sub2 Vel": [],
                  "Separation": [],
+                 "Comoving Separation": [],
                  "RelVel": [],
                  "Stellar Mass Ratio": [],
                  "Realization": [],
@@ -226,6 +230,9 @@ for phys in ["dark","hydro"]:
                     
                     pos1 = shortlist['Subhalo Pos'][primary_loc][0]
                     pos2 = shortlist['Subhalo Pos'][secondary_loc][0]
+                    copos1 = shortlist['Subhalo Pos'][primary_loc][0]/scale
+                    copos2 = shortlist['Subhalo Pos'][secondary_loc][0]/scale
+                    
                     vel1 = shortlist['Subhalo Vel'][primary_loc][0]
                     vel2 = shortlist['Subhalo Vel'][secondary_loc][0]
 
@@ -237,8 +244,11 @@ for phys in ["dark","hydro"]:
                         
                     boxsize = 75000.0 # in cMpc/h
                     boxsize_phys = boxsize * scale / little_h    
[…]

### 2023-02-07 pears/utils/make_unpaired.py

@@ -13,7 +13,7 @@ snapshot = int(sys.argv[1])
 sim = str(sys.argv[2])
 num_reals = int(sys.argv[3])
 
-realNumbs = np.arange(-1,num_reals+1,1)
+realNumbs = np.arange(-1,num_reals,1)
 paths = SetupPaths()
 
 ## find subhalos for this simulation and snapshot #
@@ -50,6 +50,8 @@ class SkipFragmentedSubhalo(Exception): pass
 
 ## ensure that the dark and/or hydro file exists before operating
 for phys in ["dark","hydro"]:
+    if phys=="dark":
+        continue
     try: 
         subhalo_data[phys]
 

### 2023-02-09 paper/pears.tex
adding updated captions

@@
     \includegraphics[width=\textwidth]{counts.png}
-    \caption{Median number of dwarf and massive primaries and pairs per abundance matching realization as a function of redshift, with shaded regions showing the $1^{\rm st}$ and 99$^{\rm th}$ percentiles.
-The number of dwarf and massive primaries peaks around $z=1$, and there are fewer primaries and pairs at higher redshift, and .
-The evolution of the number of primaries is roughly similar between dwarf and massive galaxies, though the number of dwarf primaries drops steeply from $z=1$ to $z=0$.
-The number of dwarf pairs peaks around $z=2$, while the number of massive pairs increases nearly monotonically from $z=4-0$.
+    \caption{(Top) Median number of dwarf (left) and massive (right) primaries and pairs per abundance matching realization as a function of redshift.
+    Shaded regions show the $1^{\rm st}$ and 99$^{\rm th}$ percentile values of the medians of all realizations. 
     There are approximately 8 times as many dwarf primaries as massive primaries. 
+    % dwarf galaxies
+    The dwarf primary count (green solid line in top left panel) is at a minimum at $z=4$, rises to a maximum of $\sim15000$ halos per realization by $z=1$, then decreases by $\sim16\%$ to 12000 halos at $z=0$.
+The dwarf pair count (green dashed line), on the other hand, peaks at $z\sim2$ with 3000 pairs, and decreases to a minimum of about 1000 pairs at $z=0$.
+    % Massive galaxies (right)
+    The massive primary count (pink solid line in top right panel) behaves similarly to the dwarf primary count, with a minimum count at $z=4$ which rises to a maximum of $\sim2000$ halos per realization at $z\sim1$, then decreases slightly by $\sim5\%$ to $\sim$1800 halos by $z=0$.
+    Unlike dwarf pairs whose pair count peaks at $z=2$, pair count for massive galaxies (pink dashed line) follows similar behavior to the total massive primary count, with a minimum at $z=4$, and increasing to $z=\sim 1$ before leveling off.
+At very low redshift, the pair count and primary count have opposite behavior, with the pair count \textit{increasing} at very low redshifts of $z=0-0.25$ and \textit{peaking} at $z=0$.
+    (Bottom) Fraction of pairs per primary as a function of redshift (i.e., the ratio between dotted line and solid line in each column).
+Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$.
+The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.
+    \todo{(replace with 1000 realizations fig)}
       }
@@
     \includegraphics[width=\textwidth]{stellarmass_distribution.png}
-    \caption{\kc{caption}
+    \caption{\todo{caption, add z=4}
       }
@@
   \includegraphics[width=\textwidth]{pairratio.png}
-  \caption{Median fraction (and 1-99 percentile shaded regions) of dwarf (green) or massive (pink) primaries with a major (left) or minor (right) companion.
-The fraction of massive primaries with a major or minor companion remains approximately constant for $z>1$, while at $z<\sim0.5$ the pair fraction increases sharply to $z=0$.
+  \caption{(Top) Median fraction (and 1-99 percentile shaded regions) of dwarf (green) or massive (pink) primaries with a major (left) or minor (right) companion.
+Shaded regions show the $$-$$ percentile range of the median pair fractions of each realization.
+  % 
+  (Bottom) The median subtracted difference between the massive pair frction and the dwarf pair fraction, with the $$-$$ percentile range shaded. 
+  The fraction of massive primaries with a major or minor companion remains approximately constant for $z>1$, and increases sharply  $z<\sim0.25$ the pair fraction increases sharply to $z=0$.
 However, the pair fraction for dwarf pairs evolves significantly differently to massive galaxy pairs.
 The fraction of dwarf primaries with a companion is approximately constant for $z>2$, but decreases monotonically from $z=2$ to $z=0$.
-\kc{include more numbers including the difference between the ratios.
-"Evolves distinctly"}
+\todo{finish caption, replace plot w 1000 reals vers., add 0 horizon}
     }
@@
 The evolution of massive pair separations is approximately linear for $z>1$, increasing sharply for $z<0$, while the evolution of the dwarf pairs closely resembles a power law distrbution across the whole redshift range from $z=0-4$.
-\kc{add difference plot!}
+\todo{finish caption, replace with 1000 reals plot}
     }
@@
   Both dwarf and massive pairs have narrow distributions about low separations at high redshifts, and a wider distribution of separations at lower redshift. 
-  \todo{would it be instructive to make this plot, unnormalized, with z=0-3 on same plot to see if low sep pop numbers change drastically}
-  Also note than many of the close pairs at high z may merge by $z=0$. \kc{add median line to plot}
+  \kc{would it be instructive to make this plot, unnormalized, with z=0-3 on same plot to see if low sep pop numbers change drastically}
+  Also note than many of the close pairs at high z may merge by $z=0$. \todo{change color of med lines, add z=4, replace with 1000 reals }
     }
@@
 In addition, as the redshift \textit{decreases} toward $z=0$, the average relative velocity of a pair \textit{decreases} as well.
-The overall behavior of the redshift evolution is nearly identical for dwarf and massive pairs (though note that the massive pairs have \textit{much} higher relative velocities than the dwarf pairs at all redshifts.)
+The overall behavior of the redshift evolution is nearly identical for dwarf and massive pairs (though note that the massive pairs have \textit{much} higher relative velocities than the dwarf pairs at all redshifts.) \todo{reaplace with 1000 reals, finish caption, add 0 horizon line}
     }
@@
 The distribution of velocities for major and minor pairs is roughly equivalent.
-  \kc{caption}
+  \todo{finish caption, change color of med lines, add z=4, replace with 1000 reals }
     }
@@
 Massive minor pairs tend to have smaller scaled separations compared to dwarf pairs at all redshifts.
+  \todo{replace with 1000 reals fig, finish caption, add 0 horizon line}
     }
@@
   \includegraphics[width=\textwidth]{scaledsep_distribution.png}
-  \caption{\kc{to write}}
+  \caption{\todo{finish caption, 1000 reals, change median color, add z=4}}
   \label{fig:sep-scaled-dist}
@@
   \includegraphics[width=\textwidth]{scaledvel.png}
-  \caption{Median scaled velocity (relative velocity of a pair divided by the virial velocity, defined as the circular velocity at the virial radius of the group \todo{need to remove the 2 in the virial radius calc!}) as a function of redshift.
+  \caption{Median scaled velocity (relative velocity of a pair divided by the virial velocity), defined as the circular velocity at the virial radius of the group as a function of redshift. 
   Major pairs are on the left (solid lines), minor pairs are on the right in dashed lines.
-  All sets of pairs show an increase in scaled velocity at lower redshifts.}
+  All sets of pairs show an increase in scaled velocity at lower redshifts.
+  \todo{finish caption, replace with 1000 reals, add 0 horizon line}
+  }
   \label{fig:vel-scaled}
@@
   \includegraphics[width=\textwidth]{scaledvel_distribution.png}
-  \caption{\kc{to write}}
+  \caption{\todo{finish caption, 1000 reals, change median color, add z=4}}
   \label{fig:vel-scaled-dist}

### 2023-02-09 paper/pears.tex
Updates from Overleaf
slight change to second caption

@@
 \newcommand{\kc}[1]{\textcolor{yellow}{\textbf{kc: #1}} }
+\newcommand{\gb}[1]{\textcolor{yellow}{\textbf{g: #1}} }
 % \newcommand{\ecite}[1]{\textcolor{pink}{\textbf{: #1}} }
@@
     \centering
-    \includegraphics[width=\textwidth]{counts.png}
+    \includegraphics[width=\textwidth]{counts_1000.png}
     \caption{(Top) Median number of dwarf (left) and massive (right) primaries and pairs per abundance matching realization as a function of redshift.
-    Shaded regions show the $1^{\rm st}$ and 99$^{\rm th}$ percentile values of the medians of all realizations. 
+    Shaded regions show the $1^{\rm st}$ and 99$^{\rm th}$ percentile spread of the medians of all realizations. 
     There are approximately 8 times as many dwarf primaries as massive primaries. 
@@
 Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$.
-The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.
-    \todo{(replace with 1000 realizations fig)}
+The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.}
       }
@@
     \centering
-    \includegraphics[width=\textwidth]{stellarmass_distribution.png}
-    \caption{\todo{caption, add z=4}
+    \includegraphics[width=\textwidth]{stellarmass_distribution_1000.png}
+    \caption{\todo{caption}
       }

### 2023-02-10 paper/pears.tex
edited captions 1-4

@@
 \usepackage{multirow}
+\usepackage{tikz}
+\usepackage{xcolor}
 
@@
 \newcommand{\kc}[1]{\textcolor{yellow}{\textbf{kc: #1}} }
-\newcommand{\gb}[1]{\textcolor{yellow}{\textbf{g: #1}} }
+\newcommand\shadetext[2][]{%
+  \setbox0=\hbox{{\special{pdf:literal 7 Tr }#2}}%
+  \tikz[baseline=0]\path [#1] \pgfextra{\rlap{\copy0}} (0,-\dp0) rectangle (\wd0,\ht0);% 
+  }
+\newcommand{\gb}[1]{\shadetext[left color=blue, right color=red, middle color=lime, shading angle=45]{\textbf{g: #1}} }
 % \newcommand{\ecite}[1]{\textcolor{pink}{\textbf{: #1}} }
@@
 \newcommand{\vrad}{\ensuremath{v_\textrm{rad}}}
+\newcommand{\ms}[1]{\ensuremath{M_{*{#1}}}}
 \newcommand{\mud}{\ensuremath{\mu_\delta}}
@@
 The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.}
-      }
     \label{fig:counts}
@@
     \includegraphics[width=\textwidth]{stellarmass_distribution_1000.png}
-    \caption{\todo{caption}
-      }
+    \caption{Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs.
+Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$.
+Overall, the stellar mass ratio distribution of major and minor pairs of dwarf and massive galaxies show little evolution from $z=4$ (right) to $z=0$ (left).
+    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.}
     \label{fig:massratio}
@@
   \centering
-  \includegraphics[width=\textwidth]{pairratio.png}
-  \caption{(Top) Median fraction (and 1-99 percentile shaded regions) of dwarf (green) or massive (pink) primaries with a major (left) or minor (right) companion.
-Shaded regions show the $$-$$ percentile range of the median pair fractions of each realization.
-  % 
-  (Bottom) The median subtracted difference between the massive pair frction and the dwarf pair fraction, with the $$-$$ percentile range shaded. 
-  The fraction of massive primaries with a major or minor companion remains approximately constant for $z>1$, and increases sharply  $z<\sim0.25$ the pair fraction increases sharply to $z=0$.
-However, the pair fraction for dwarf pairs evolves significantly differently to massive galaxy pairs.
-The fraction of dwarf primaries with a companion is approximately constant for $z>2$, but decreases monotonically from $z=2$ to $z=0$.
-\todo{finish caption, replace plot w 1000 reals vers., add 0 horizon}
-    }
+  \includegraphics[width=\textwidth]{pairratio_1000.png}
+  \caption{
+    % Top plots ~
+    (Top) Median fraction of dwarf or massive primaries with a major or minor companion by stellar mass. 
+    Shaded regions show the $1$-$99$ percentile range of the median pair fractions of each realization. 
+      % massive pairs
+    The fraction of massive primaries (pink) with a major (left) or minor (right) companion remains approximately constant for $z>1$, with an average pair fraction of 0.16-0.17 and 0.14-0.15 respectively.
+Between $z=0.25$ and $z=0$, the massive major pair fraction increases sharply from 0.165 to 0.207, a 25\% increase, while the minor pair fraction increases from 0.127 to 0.152, a 20\% increase.
+      % dwarf pairs
+    Dwarf pairs (green), on the other hand, have pair fractions that are approximately constant from $z=3-4$, but the fraction of major(minor) pairs declines monotonically from 0.126(0.111) at x=3 to just 0.041(0.034) at x=0, a 67(70)\% decrease.
+    % Bottom plots ~
+  (Bottom) The median subtracted difference between the massive pair fraction and the dwarf pair fraction, with the shaded $1$-$99$ percentile range of the difference of each realization.
+The difference between the massive pair fraction and dwarf pair fraction increases with decreasing redshift, peaking at $z=0$ with a difference of 0.166 for major pairs and 0.111 for minor pairs.
+This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly in the low redshift regime.}
   \label{fig:pairratio}
@@
   \includegraphics[width=\textwidth]{separation.png}
-  \caption{Median physical separation (in kpc) and 1-99 percentile shaded regions of 1000 abundance matching realizations as a function of redshift for dwarf pairs (left, green), and massive pairs (right, pink).
+  \caption{(Top) Median physical separation (in kpc) of dwarf pairs (left, green) and massive pairs (right, pink) as a function of redshift. 
+  Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
   Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
-Minor dwarf pairs tend to be $\sim10-20\kpc$ closer than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs.
-In general, as the redshift \textit{decreases} toward $z=0$, the average physical separation of a dwarf or massive pair \textit{increases}.
-The evolution of massive pair separations is approximately linear for $z>1$, increasing sharply for $z<0$, while the evolution of the dwarf pairs closely resembles a power law distrbution across the whole redshift range from $z=0-4$.
-\todo{finish caption, replace with 1000 reals plot}
+  In general, as the redshift decreases from $z=4$ to $z=0$, the average physical separation of a pair increases for both dwarf and massive pairs. 
+  % Dwarf pairs
+  The redshift evolution of the dwarf pairs closely resembles a power law distrbution across the whole redshift range from $z=0-4$.
+  At $z=4$, the typical separation between major (minor) dwarf pairs is XX(XX) kpc, and peaks at $z=0$ with a median separation of XX (xx).
+  % Massive Pairs
+  The separation between massive pairs, on the other hand, increases approximately linearly from $z=4$, where the median separations of major (minor) pairs is XX(XX), to $z=1$, where median separations are XX(XX).
+The median separation rises more steeply from z=1 to z=0, peaking at $z=0$ with median separations of XX and XX for major and minor massive pairs respectively.
+  % Difference plots
+  (Bottom) The median subtracted separation difference between major and minor pairs, and 1-99\% shaded region.
+  Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs.
+\todo{fill caption numberss, z=4, replace with 1000 reals plot}
     }
@@
   \includegraphics[width=\textwidth]{separation_distribution.png}
-  \caption{Normalized physical separation distribution for dwarf and massive pairs (top/green and bottom/pink, respectively) from $z=0$ (left) to $z=3$ (right).
-Major pairs are shown as solid lines, while minor pairs are dashed.
-  Both dwarf and massive pairs have narrow distributions about low separations at high redshifts, and a wider distribution of separations at lower redshift. 
-  \kc{would it be instructive to make this plot, unnormalized, with z=0-3 on same plot to see if low sep pop numbers change drastically}
-  Also note than many of the close pairs at high z may merge by $z=0$. \todo{change color of med lines, add z=4, replace with 1000 reals }
+  \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right).
+Major pairs are shown as solid lines, while minor pairs are dotted.
+The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines.
+  At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively).
+However, at low redshift, the separation distirbution tends to spread out more evenly across a large range of separations, thus increasing the median.
+  % \kc{would it be instructive to make this plot, unnormalized, with z=0-3 on same plot to see if low sep pop numbers change drastically}
+   \todo{change color of med lines, add z=4, replace with 1000 reals }
     }
@@
   \includegraphics[width=\textwidth]{velocity.png}
-  \caption{Median relative velocity (in \kms) and 1-99 percentile shaded regions of 1000 abundance matching realizations as a function of redshift for dwarf pairs (left, green) and massive pairs (right, pink).
+  \caption{
+    (Top) Median relative velocity (in \kms) between the primary and secondary halos of: dwarf pairs (left, green), and massive pairs (right, pink) as a function of redshift. 
+    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations.
 Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
-Major and minor pairs (in both the dwarf and massive regime) tend to have approximately the same median relative velocity.
-In addition, as the redshift \textit{decreases} toward $z=0$, the average relative velocity of a pair \textit{decreases} as well.
-The overall behavior of the redshift evolution is nearly identical for dwarf and massive pairs (though note that the massive pairs have \textit{much} higher relative velocities than the dwarf pairs at all redshifts.) \todo{reaplace with 1000 reals, finish caption, add 0 horizon line}
+    The overall behavior of the redshift evolution is nearly identical for dwarf and massive pairs.
+    As the redshift decreases from $z=4$ to $z=0$, the average relative velocity of a pair decreases as well for both dwarf and massive pairs.
+    % brief describe
+    The median relative velocity of a dwarf pair (major or minor) is $xx$ at $z=0$ and $xx$ at $z=4$, and of a massive pair is $xx$ at $z=0$ and $xx$ at $z=4$. 
+    % Difference plot
+    (Bottom) The median subtracted relative velocity difference between major and minor pairs, and 1-99\% shaded region.
+    The is little difference between major and minor dwarf pairs (bottom left), with minor pairs having a relative velocity of $0-5\kms$ higher than major pairs. 
+    Major and minor massive pairs also have very little median velocity difference at low redshift (bottom right), with minor pairs having a relative velocity between $1-20\kms$ faster than major pairs.
+    \todo{replace with 1000 reals, median "relative" velocity, finish caption, add 0 horizon line}
     }
@@
 The distribution of velocities for major and minor pairs is roughly equivalent.
-  \todo{finish caption, change color of med lines, add z=4, replace with 1000 reals }
+  \todo{finish caption, change color of med lines, add z=4, replace with 1000 reals } \kc{comment here like this} \gb{this is the one for gurtina}
     }
@@
 There is little to no mass dependence on the scaled velocity of dwarf or massive pairs.}
+Also note than many of the close pairs at high z may merge by $z=0$.
 

### 2023-02-10 paper/pears.tex
changes to all result captions

@@
   \caption{
-  Normalized velocity distribution for dwarf and massive pairs (top/green and bottom/pink, respectively) from $z=0$ (left) to $z=3$ (right).
-Major pairs are shown as solid lines, while minor pairs are dashed.
+  Normalized distribution of relative velocities between primary and secondary halos for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right).
+Major pairs are shown as solid lines, while minor pairs are dotted.
+The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines.
+  %
   The distribution of relative velocities for dwarf and massive pairs move to slightly lower velocities at lower redshifts.
 The distribution of velocities for major and minor pairs is roughly equivalent.
-  \todo{finish caption, change color of med lines, add z=4, replace with 1000 reals } \kc{comment here like this} \gb{this is the one for gurtina}
+  \todo{finish caption, change color of med lines, add z=4, replace with 1000 reals}
     }

### 2023-02-10 paper/pears.tex
results intro para, separations plot 1

@@
 %%%%%%%%%%%%%%%%%%%
+\kc{why did we stop at z=4? we didn't, explanation about low \# statistics }
 
@@
 \section{Results}
-\subsection{Pair ratios}
+We collect dwarf pairs and massive pairs at all snapshots from the TNG100-1 simulation and analyze the occurrence rate and kinematic behavior of the pairs across cosmic time. 
+At each snapshot, we generate 1000 different realizations of the pair catalog, where each realization represents one instance of the abundance matching technique to assign stellar masses to dark matter halos (see methods).
+In each of the following plots, the median and a percentile spread each value are calculated by finding the median from each of the 1000 AM realizations, and taking the median and spread of that set of median values.
+
+In Sec.~\ref{sec:results-frac}, we show the redshift evolution of the fraction of primaries with a major or minor companion/secondary, and compare the "pair fractions" of dwarf pairs and massive pairs.
+In Sec.~\ref{sec:results-kinematics}, we look at the redshift evolution of the median separations and relative velocities between primary and secondary halos on a snapshot-by-snapshot basis.
+
+\subsection{Pair fraction}\label{sec:results-frac}
 Thus, the rate of dwarf pairs and massive pairs \textit{per primary} will evolve distinctly in the dwarf and massive pair case.
@@
 
-\subsection{Kinematic evolution}
+\subsection{Kinematic evolution}\label{sec:results-kinematics}
+The primary and secondary halos of each pair at each individual snapshot/redshift is separated by some physical separation and has a relative velocity of
 
+We separate the population of dwarf and massive pairs into "major" and "minor" pairs (as defined in Sec.~\ref{sec:methods-crit-pairs}) to show how the stellar mass ratio between the primary and secondary may affect the kinematics.
+
+At each individual snapshot, we find the median separation
+
+\subsubsection{Physical Separations}
+The median separations of dwarf and massive pairs increases with lower redshift, regardless of pair type. 
+Fig.~\ref{fig:sep} shows the median and 1-99\% range of separations for dwarf pairs and massive pairs, as well as the subtracted difference between the median separation of major pairs and of minor pairs of both mass type.
+Both dwarf and massive pairs have smoothly evolving medians that increase with decreasing redshift. 
+There is a small offset in the median separations of major and minor dwarf pairs (between $10-25\,\kpc$ from  $z=0-1$ and approximately $5\,\kpc$ from $z=1-4$), and a larger median separation offset for major and minor massive pairs (between $25-100\,\kpc$ from  $z=0-1$ and approximately $10-40\,\kpc$ from $z=1-4$).
+Thus, apart from the overall scale of the separations between primary and secondary, dwarf and massive pairs exhibit similar trends as a function of time.
+
+Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$ for all 1000 AM realizations.
+
+\subsubsection{Relative Velocities}
+Fig.~\ref{fig:vel}
+Fig.~\ref{fig:vel-dist}
+
+%%% plots for kinematics
 \begin{figure*}[htb]
@@
 \end{figure*}
+%%%
 

### 2023-02-10 paper/pears.tex
some vel stuff

@@
 
-In Sec.~\ref{sec:results-frac}, we show the redshift evolution of the fraction of primaries with a major or minor companion/secondary, and compare the "pair fractions" of dwarf pairs and massive pairs.
+In Sec.~\ref{sec:results-frac}, we show the redshift evolution of the fraction of primaries with a major or minor companion and compare the "pair fractions" of dwarf pairs to massive pairs.
 In Sec.~\ref{sec:results-kinematics}, we look at the redshift evolution of the median separations and relative velocities between primary and secondary halos on a snapshot-by-snapshot basis.
@@
 
-At each individual snapshot, we find the median separation
+At each individual snapshot, we find the instantaneous median separation and relative velocity of every pair that was selected in that snapshot.
 
-\subsubsection{Physical Separations}
-The median separations of dwarf and massive pairs increases with lower redshift, regardless of pair type. 
+\subsubsection{Separations}
+% separation vs. redshift plot
+The median separations of dwarf pairs and massive pairs smoothly increases with lower redshift, regardless of pair type. 
 Fig.~\ref{fig:sep} shows the median and 1-99\% range of separations for dwarf pairs and massive pairs, as well as the subtracted difference between the median separation of major pairs and of minor pairs of both mass type.
-Both dwarf and massive pairs have smoothly evolving medians that increase with decreasing redshift. 
 There is a small offset in the median separations of major and minor dwarf pairs (between $10-25\,\kpc$ from  $z=0-1$ and approximately $5\,\kpc$ from $z=1-4$), and a larger median separation offset for major and minor massive pairs (between $25-100\,\kpc$ from  $z=0-1$ and approximately $10-40\,\kpc$ from $z=1-4$).
@@
 
-Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$ for all 1000 AM realizations.
+% separation distribution plot
+Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$, and includes all 1000 AM realizations. 
+For reference, the median at each corresponding redshift from Fig.~\ref{fig:sep} (that is, the median of the medians of each realization) are shown in light black vertical lines.
+Each plot is normalized such that the area under an individual curve is 1.
+    % the redshift evolution
+All pair types (dwarf and massive, major and minor) have narrow distributions that pile up around 0 $\kpc$ at $z=4$, but the distributions become more and more broad as $z\to0$ (note that only pairs with separations $>10\kpc$ are included in this analysis, see Sec.~\ref{sec:methods-crit-pairs}).
+
+The distribution profiles are similar when the scale of the x-axis for massive pair separations is twice that of the dwarf pairs. 
+Pair separations at $z=0$ tend to primarily fall between $10-\sim400\,\kpc$ for dwarf pairs and   between $10-\sim1000\,\kpc$ for massive pairs. 
+At $z=4$, these ranges decrease to $10-150\,\kpc$ for dwarf pairs and $10-300\,\kpc$ for massive pairs. 
+    % comparing major and minor
+Major and minor pairs (both dwarf pairs and massive pairs) have roughly equivalent distributions, though the distribution of minor pairs with low separations is slightly higher than the major pairs.
+Thus, secondary halo of minor pairs tend to live slightly closer to their primaries than the  major secondaries.
+
+\todo{here maybe include a table? what are some values?  z=0,1,2,3,4 and pair frac, sep, vel. ?}
 
 \subsubsection{Relative Velocities}
-Fig.~\ref{fig:vel}
+% velocity vs. redshift plot
+We also consider the snapshot-by-snapshot instantaneous relative velocity between each primary and secondary.
+We find that the median relative velocity of all pairs (dwarf and massive, major and minor) decreases with decreasing redshift, reaching a minimum at $z=0$ as seen in Fig.~\ref{fig:vel}. 
+Though the velocity scales are different, the bulk behavior of dwarf pairs and massive pairs is identical.
+
+The median velocity of a major dwarf pair decreases approximately linearly from $xx$ at $z=4$ to $xx$ at $z=0$. Likewise, the median velocity for major massive pairs decreases.
+Fig.~\ref{fig:vel} also includes a panel showing the subtracted median difference at each snapshot of the minor pair from the major pair.
+Since minor pairs typically have slightly higher velocities than their major pair counterparts, this difference is usually $<\sim0$.
+
+% velocity distribution plot
 Fig.~\ref{fig:vel-dist}
@@
   \centering
-  \includegraphics[width=\textwidth]{velocity.png}
+  \includegraphics[width=\textwidth]{velocity_1000.png}
   \caption{

### 2023-02-11 paper/pears.tex
Updates from Overleaf

@@
   \centering
-  \includegraphics[width=\textwidth]{separation.png}
+  \includegraphics[width=\textwidth]{separation_1000.png}
   \caption{(Top) Median physical separation (in kpc) of dwarf pairs (left, green) and massive pairs (right, pink) as a function of redshift. 
@@
   % Dwarf pairs
-  The redshift evolution of the dwarf pairs closely resembles a power law distrbution across the whole redshift range from $z=0-4$.
-  At $z=4$, the typical separation between major (minor) dwarf pairs is XX(XX) kpc, and peaks at $z=0$ with a median separation of XX (xx).
+  The redshift evolution of the dwarf pairs closely resembles a power law distribution across the whole redshift range from $z=0-4$.
+  At $z=4$, the typical separation between major (minor) dwarf pairs is $42(38)\,\kpc$, and peaks at $z=0$ with a median separation of $128(109)\,\kpc$.
   % Massive Pairs
-  The separation between massive pairs, on the other hand, increases approximately linearly from $z=4$, where the median separations of major (minor) pairs is XX(XX), to $z=1$, where median separations are XX(XX).
-The median separation rises more steeply from z=1 to z=0, peaking at $z=0$ with median separations of XX and XX for major and minor massive pairs respectively.
+  The separation between massive pairs, on the other hand, increases approximately linearly from $z=4$, where the median separations of major (minor) pairs is $81(71)\,\kpc$, to $z=1$, where median separations are $171(124)\,\kpc$.
+The median separation rises more steeply from z=1 to z=0, peaking around $z=\sim0$ at $288\,\kpc$ and $205\,\kpc$ for major and minor massive pairs respectively.
   % Difference plots
@@
   Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs. 
-\todo{fill caption numberss, z=4, replace with 1000 reals plot}
     }
@@
   At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively).
-However, at low redshift, the separation distirbution tends to spread out more evenly across a large range of separations, thus increasing the median.
+However, at low redshift, the separation distribution tends to spread out more evenly across a large range of separations, thus increasing the median.
   % \kc{would it be instructive to make this plot, unnormalized, with z=0-3 on same plot to see if low sep pop numbers change drastically}
@@
     % brief describe
-    The median relative velocity of a dwarf pair (major or minor) is $xx$ at $z=0$ and $xx$ at $z=4$, and of a massive pair is $xx$ at $z=0$ and $xx$ at $z=4$. 
+    The median relative velocity of a dwarf pair (major or minor) is $70\,\kms$ at $z=0$ and $133\,\kms$ at $z=4$, and of a massive pair is $170\,\kms$ at $z=0$ and $260\,\kms$ at $z=4$ ($295\,\kms$ for a minor pair).
     % Difference plot
     (Bottom) The median subtracted relative velocity difference between major and minor pairs, and 1-99\% shaded region.
-    The is little difference between major and minor dwarf pairs (bottom left), with minor pairs having a relative velocity of $0-5\kms$ higher than major pairs. 
-    Major and minor massive pairs also have very little median velocity difference at low redshift (bottom right), with minor pairs having a relative velocity between $1-20\kms$ faster than major pairs.
-    \todo{replace with 1000 reals, median "relative" velocity, finish caption, add 0 horizon line}
+    The is little difference between major and minor dwarf pairs (bottom left), with minor pairs having a relative velocity of $0-5\,\kms$ higher than major pairs. 
+    Major and minor massive pairs also have very little median velocity difference at low redshift (bottom right), with minor pairs having a relative velocity between $1-20\,\kms$ faster than major pairs.
     }

### 2023-02-11 paper/pears.tex
pulling to get new vel dist 1000 plot

@@
   \centering
-  \includegraphics[width=\textwidth]{separation_distribution.png}
+  \includegraphics[width=\textwidth]{separation_distribution_1000.png}
   \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right).
@@
 However, at low redshift, the separation distribution tends to spread out more evenly across a large range of separations, thus increasing the median.
-  % \kc{would it be instructive to make this plot, unnormalized, with z=0-3 on same plot to see if low sep pop numbers change drastically}
-   \todo{change color of med lines, add z=4, replace with 1000 reals }
     }
@@
   \centering
-  \includegraphics[width=\textwidth]{velocity_distribution.png}
+  \includegraphics[width=\textwidth]{velocity_distribution_1000.png}
   \caption{
@@
 Major pairs are shown as solid lines, while minor pairs are dotted.
-The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines.
+The median relative velocity of each pair type from Fig.~\ref{fig:vel} is shown in solid (major) and dotted (minor) vertical black lines.
   %
   The distribution of relative velocities for dwarf and massive pairs move to slightly lower velocities at lower redshifts. 
-The distribution of velocities for major and minor pairs is roughly equivalent.
-  \todo{finish caption, change color of med lines, add z=4, replace with 1000 reals}
+  At $z=0$, typical dwarf pair relative velocities are $0-200\,\kms$, while at $z=4$ they are $0-300\,\kms$. 
+  Massive pairs typically have relative velocities between $0-300\,\kms$ at z=0 and $0-400\,\kms$ at $z=4$.
+  The distribution of velocities for major and minor pairs is roughly equivalent within each mass range. 
     }

### 2023-02-11 paper/pears.tex
final edits for the day to the velocity results sec.

@@
 \section{Sample selection}\label{sec:methods}
+% methods plots
+  \begin{figure*}[htp]
+    \centering
+    \includegraphics[width=\textwidth]{counts_1000.png}
+    \caption{(Top) Median number of dwarf (left) and massive (right) primaries and pairs per abundance matching realization as a function of redshift.
+    Shaded regions show the $1^{\rm st}$ and 99$^{\rm th}$ percentile spread of the medians of all realizations. 
+    There are approximately 8 times as many dwarf primaries as massive primaries. 
+    % dwarf galaxies
+    The dwarf primary count (green solid line in top left panel) is at a minimum at $z=4$, rises to a maximum of $\sim15000$ halos per realization by $z=1$, then decreases by $\sim16\%$ to 12000 halos at $z=0$.
+The dwarf pair count (green dashed line), on the other hand, peaks at $z\sim2$ with 3000 pairs, and decreases to a minimum of about 1000 pairs at $z=0$.
+    % Massive galaxies (right)
+    The massive primary count (pink solid line in top right panel) behaves similarly to the dwarf primary count, with a minimum count at $z=4$ which rises to a maximum of $\sim2000$ halos per realization at $z\sim1$, then decreases slightly by $\sim5\%$ to $\sim$1800 halos by $z=0$.
+    Unlike dwarf pairs whose pair count peaks at $z=2$, pair count for massive galaxies (pink dashed line) follows similar behavior to the total massive primary count, with a minimum at $z=4$, and increasing to $z=\sim 1$ before leveling off.
+At very low redshift, the pair count and primary count have opposite behavior, with the pair count \textit{increasing} at very low redshifts of $z=0-0.25$ and \textit{peaking} at $z=0$.
+    (Bottom) Fraction of pairs per primary as a function of redshift (i.e., the ratio between dotted line and solid line in each column).
+Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$.
+The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.}
+    \label{fig:counts}
+  \end{figure*}
+
+  \begin{figure*}[htp]
+    \centering
+    \includegraphics[width=\textwidth]{stellarmass_distribution_1000.png}
+    \caption{Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs.
+Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$.
+Overall, the stellar mass ratio distribution of major and minor pairs of dwarf and massive galaxies show little evolution from $z=4$ (right) to $z=0$ (left).
+    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.}
+    \label{fig:massratio}
+  \end{figure*}
+
 Our sample data was obtained using a strict set of selection criteria, as outlined in this section.
@@
 Each of these simulations follows the dynamical evolution of $1820^3$ dark matter particles from $z=127$ to $z=0$ through a periodic volume of roughly $100^3$ Mpc$^3$. 
-The \ill{} simulations follow a cosmology consistent with \textit{WMAP-9}~\citep{hinshaw13}, while the \tng{} simulations are consistent with \textit{Planck2015}~\citep{Planck2015}.
-Specifically, we use the \textit{Illustris-1-Dark}, \textit{Illustris-1}, \textit{TNG100-1-Dark}, and \textit{TNG100-1} simulations (hereafter \illd, \illh, \tngd, and \tngh{} respectively, see Table~\ref{table:sim} for details).
+The \ill{} simulations follow a cosmology consistent with \textit{WMAP-9}~\citep{hinshaw2013}, while the \tng{} simulations are consistent with \textit{Planck2015}~\citep{Planck2015}.
+Specifically, we use the \textit{Illustris-1-Dark}, \textit{Illustris-1}, \textit{TNG100-1-Dark}, and \textit{TNG100-1} simulations (hereafter \illd, \illh, \tngd, and \tngh{} respectively, % see Table~\ref{table:sim} for details).
 
@@
 % subfind, sublink, and groups and subhalos
-We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm ~\citep{springel01,dolag09}. 
-These catalogs consist of halos (or "groups"), defined using the Friends-of-Friends (FoF) algorithm~\citep{davis85} to link nearby particles, and their associated subhalos, which are over-dense and gravitationally bound dark matter structures.
+We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm ~\citep{springel2001,dolag09}. 
+These catalogs consist of halos (or "groups"), defined using the Friends-of-Friends (FoF) algorithm~\citep{davis1985} to link nearby particles, and their associated subhalos, which are over-dense and gravitationally bound dark matter structures.
 We also use the merger trees provided by the \texttt{SUBLINK} algorithm \citep{gomez15}, which tracks subhalos between snapshots using their particle data, in order to trace the mass growth and merger histories of our subhalos.
 
-\begin{table*}[htb]
-\begin{tabular}{l|llll}
- & \illd & \illh & \tngd & \tngh\\\hline\hline
- L$_{\rm Box}$ [Mpc] & 106.5 & 106.5 & 110.7 & 110.7 \\
-m$_{\rm DM}$ [M$_\odot$] & 7.5$\times10^6$ & 6.3$\times10^6$ & 8.9$\times10^6$ & $7.5\times10^6$\\
-m$_{\rm gas}$ & -- & $1.3\times 10^{6}$ & -- & $1.4\times 10^{6}$ \\\hline
-\end{tabular}
-\caption{\label{table:sim}Parameters of the Illustris simulations used in this analysis.}
-\end{table*}
+% \begin{table*}[htb]
+% \begin{tabular}{l|llll}
+%  & \illd & \illh & \tngd & \tngh\\\hline\hline
+%  L$_{\rm Box}$ [Mpc] & 106.5 & 106.5 & 110.7 & 110.7 \\
+% m$_{\rm DM}$ [M$_\odot$] & 7.5$\times10^6$ & 6.3$\times10^6$ & 8.9$\times10^6$ & $7.5\times10^6$\\
+% m$_{\rm gas}$ & -- & $1.3\times 10^{6}$ & -- & $1.4\times 10^{6}$ \\\hline
+% \end{tabular}
+% \caption{\label{table:sim}Parameters of the Illustris simulations used in this analysis.}
+% \end{table*}
 
@@
 % How do we utilize it? 
-In particular, we use the abundance matching relationship presented in~\citet{moster13}, which provides an analytic recipe to paint stellar masses onto dark matter halos. 
-The~\citet{moster13} relationship is a redshift-evolving function of the halo mass, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.
+In particular, we use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic recipe to paint stellar masses onto dark matter halos. 
+The~\citet{Moster2013} relationship is a redshift-evolving function of the halo mass, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.
 \kc{why moster instead of another AM relationship? most closely represent data at lower mass? }
@@
 
-Thus, we treat each of the subhalos as centrals according to the~\citet{moster13} prescription, using the current snapshot redshift and the peak halo mass of the subhalo to calculate the stellar mass.
+Thus, we treat each of the subhalos as centrals according to the~\citet{Moster2013} prescription, using the current snapshot redshift and the peak halo mass of the subhalo to calculate the stellar mass.
 This additionally allows us remain robust to scenarios in which a secondary may have formed most of its stars, and then lost a significant portion of its dark matter content through tidal interactions with a primary, but will retain the bulk of its stellar content.
@@
 % equivalent snapshot table
-\begin{table*}[]
+\begin{table*}[tbp]
   \centering
@@
 
-  \begin{figure*}[htb]
-    \centering
-    \includegraphics[width=\textwidth]{counts_1000.png}
-    \caption{(Top) Median number of dwarf (left) and massive (right) primaries and pairs per abundance matching realization as a function of redshift.
-    Shaded regions show the $1^{\rm st}$ and 99$^{\rm th}$ percentile spread of the medians of all realizations. 
-    There are approximately 8 times as many dwarf primaries as massive primaries. 
-    % dwarf galaxies
-    The dwarf primary count (green solid line in top left panel) is at a minimum at $z=4$, rises to a maximum of $\sim15000$ halos per realization by $z=1$, then decreases by $\sim16\%$ to 12000 halos at $z=0$.
-The dwarf pair count (green dashed line), on the other hand, peaks at $z\sim2$ with 3000 pairs, and decreases to a minimum of about 1000 pairs at $z=0$.
-    % Massive galaxies (right)
-    The massive primary count (pink solid line in top right panel) behaves similarly to the dwarf primary count, with a minimum count at $z=4$ which rises to a maximum of $\sim2000$ halos per realization at $z\sim1$, then decreases slightly by $\sim5\%$ to $\sim$1800 halos by $z=0$.
-    Unlike dwarf pairs whose pair count peaks at $z=2$, pair count for massive galaxies (pink dashed line) follows similar behavior to the total massive primary count, with a minimum at $z=4$, and increasing to $z=\sim 1$ before leveling off.
-At very low redshift, the pair count and primary count have opposite behavior, with the pair count \textit{increasing} at very low redshifts of $z=0-0.25$ and \textit{peaking} at $z=0$.
-    (Bottom) Fraction of pairs per primary as a function of redshift (i.e., the ratio between dotted line and solid line in each column).
-Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$.
-The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.}
-    \label{fig:counts}
-  \end{figure*}
-
-  \begin{figure*}[htb]
-    \centering
-    \includegraphics[width=\textwidth]{stellarmass_distribution_1000.png}
-    \caption{Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs.
-Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$.
-Overall, the stellar mass ratio distribution of major and minor pairs of dwarf and massive galaxies show little evolution from $z=4$ (right) to $z=0$ (left).
-    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.}
-    \label{fig:massratio}
-  \end{figure*}
-
 %%%%%%%%%%%%%%%%%%%
@@
 \subsection{Pair fraction}\label{sec:results-frac}
-Thus, the rate of dwarf pairs and massive pairs \textit{per primary} will evolve distinctly in the dwarf and massive pair case.
+%% text on pair fraction plot
+\kc{WIP} Thus, the rate of dwarf pairs and massive pairs \textit{per primary} will evolve distinctly in the dwarf and massive pair case.
 
+%% pair fraction plot
 \label{sec:results}
-\begin{figure*}[htb]
+\begin{figure*}[htp]
   \centering
@@
 \subsection{Kinematic evolution}\label{sec:results-kinematics}
+\kc{WIP}
 The primary and secondary halos of each pair at each individual snapshot/redshift is separated by some physical separation and has a relative velocity of
@@
 \subsubsection{Separations}
-% separation vs. redshift plot
+%% text on separation vs. redshift plot
 The median separations of dwarf pairs and massive pairs smoothly increases with lower redshift, regardless of pair type. 
@@
 
-% separation distribution plot
+%% text on separation distribution plot
 Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$, and includes all 1000 AM realizations. 
@@
 All pair types (dwarf and massive, major and minor) have narrow distributions that pile up around 0 $\kpc$ at $z=4$, but the distributions become more and more broad as $z\to0$ (note that only pairs with separations $>10\kpc$ are included in this analysis, see Sec.~\ref{sec:methods-crit-pairs}).
-
+\linebreak
 The distribution profiles are similar when the scale of the x-axis for massive pair separations is twice that of the dwarf pairs. 
@@
 
-\todo{here maybe include a table? what are some values?  z=0,1,2,3,4 and pair frac, sep, vel. ?}
+\todo{quick final conclusions on separations}
 
-\subsubsection{Relative Velocities}
-% velocity vs. redshift plot
-We also consider the snapshot-by-snapshot instantaneous relative velocity between each primary and secondary.
-We find that the median relative velocity of all pairs (dwarf and massive, major and minor) decreases with decreasing redshift, reaching a minimum at $z=0$ as seen in Fig.~\ref{fig:vel}. 
-Though the velocity scales are different, the bulk behavior of dwarf pairs and massive pairs is identical.
+\kc{here maybe include a table? what are some values?  z=0,1,2,3,4 and pair frac, sep, vel. ?}
 
-The median velocity of a major dwarf pair decreases approximately linearly from $xx$ at $z=4$ to $xx$ at $z=0$. Likewise, the median velocity for major massive pairs decreases.
-Fig.~\ref{fig:vel} also includes a panel showing the subtracted median difference at each snapshot of the minor pair from the major pair.
-Since minor pairs typically have slightly higher velocities than their major pair counterparts, this difference is usually $<\sim0$.
-
-% velocity distribution plot
-Fig.~\ref{fig:vel-dist}
-
-%%% plots for kinematics
-\begin{figure*}[htb]
+%% separation plots
+\begin{figure*}[htp]
   \centering
@@
 
-\begin{figure*}[htb]
+\begin{figure*}[htp]
   \centering
@@
 
-\begin{figure*}[htb]
+\subsubsection{Relative Velocities}
+%% text on velocity vs. redshift plot
+We also consider the snapshot-by-snapshot instantaneous relative velocity between each primary and secondary.
+We find that the median relative velocity of all pairs (dwarf and massive, major and minor) decreases with decreasing redshift, reaching a minimum at $z=0$ as seen in Fig.~\ref{fig:vel}. 
+Though the velocity scales are different, the bulk behavior of dwarf pairs and massive pairs is identical. 
+\linebreak
+The median velocity of a major dwarf pair decreases approximately linearly from $130$ at $z=4$ to $70\,\kms$ at $z=0$.
+Likewise, the median velocity for major massive pairs decreases from $260$ at $z=4$ to $170\,\kms$ at $z=0$, albeit less smoothly.
+Fig.~\ref{fig:vel} also includes a panel showing the subtracted median difference at each snapshot of the minor pair from the major pair.
+Since minor pairs typically have slightly higher velocities than their major pair counterparts, this difference is usually $<\sim0$.
+The offsets between the relative velocities of dwarf major and minor pairs is between $0-5\,\kms$, and between $0-25\,\kms$ for massive major and minor pairs.
+
+%% text on velocity distribution plot
+\kc{left off here\~}
+Fig.~\ref{fig:vel-dist}
+
+%% velocity plots 
+\begin{figure*}[htp]
   \centering

### 2023-02-16 paper/pears.tex
slight updates to scaled plot captions
minor changes to scaled captions reflecting z>4 change
added text on pair frac plot

@@
 \usepackage{xcolor}
+\usepackage{soul}
 
@@
   \todo{REMEMBER TO USE 100-1000 REALS IN PLOTS}
+
   \todo{Include ticks on top and right axis as well}
+
+  \todo{Remove all instances of "we find" to "we compute" or "we calculate"}
 \end{abstract}
@@
     \includegraphics[width=\textwidth]{counts_1000.png}
-    \caption{(Top) Median number of dwarf (left) and massive (right) primaries and pairs per abundance matching realization as a function of redshift.
-    Shaded regions show the $1^{\rm st}$ and 99$^{\rm th}$ percentile spread of the medians of all realizations. 
+    \caption{(Top) \kc{correct wording: Median number of dwarf (left) and massive (right) primaries and pairs per abundance matching realization as a function of redshift.} 
+    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations, as described in Sec.~\ref{sec:methods-err}.
     There are approximately 8 times as many dwarf primaries as massive primaries. 
@@
 % Why do we need stellar masses?
-One of the goals of this study is to determine the impact of baryonic physics on the occurance rate and typical separations of galaxy \kc{subhalo?} pairs in cosmological simulations. 
+One of the goals of this study is to determine the impact of baryonic physics on the occurrence rate and typical separations of galaxy \kc{subhalo?} pairs in cosmological simulations. 
 However, selecting halo pairs by stellar mass ratio using the stellar masses provided by the simulations is not possible in the dark matter only runs. 
@@
 We report the mean of all realizations and error bars indicate the 1$\sigma$ dispersion across the realizations.
+
+\subsubsection{Error calculations}\label{sec:methods-err}
+
 %%%%%%%%%%%
@@
 %% text on pair fraction plot
-\kc{WIP} Thus, the rate of dwarf pairs and massive pairs \textit{per primary} will evolve distinctly in the dwarf and massive pair case.
+The pair fraction is defined here as the fraction of identified dwarf or massive primaries with a major or minor companion (see Sec.~\ref{sec:methods-crit} for more info on selection criteria for major and minor pairs).
+Fig.~\ref{fig:pairratio} shows the calculated pair fractions for massive and dwarf pairs (including both major and minor pairs separately) as a function of time for $z=0-4$.
+
+    % differences between major and minor pairs? 
+The minor pair fraction of both massive and dwarf pairs tends to be smaller than that of major pairs of the same mass range at all redshifts.
+This is likely because of the lower stellar mass ratio limit we put on our pairs.
+\kc{take away -- why?
+what does the difference between major and minor mean?
+check g's 2018 paper for discussion}
+
+    % differences between massive and dwarf pairs? 
+Additionally, dwarf and massive pair fractions evolve distinctly over this redshift range -- the mass pair fraction is roughly flat/constant, while the dwarf pair fraction declines from $z=\sim 2-3$ to a minimum at $z=0$.
+The subtracted difference between the pair fractions of massive and dwarf pairs (respectively) is low and flat at high z (z=$2-4$), but increases up to $\sim0.12-0.18$ by $z=0$. 
+Thus, our expectations for massive and dwarf pair counts should evolve very differently at low redshift, despite being roughly equivalent at higher z. 
+The implications of the difference in the evolution of pair fractions for dwarf and massive pairs across time is discussed in detail in Sec.~\ref{sec:discussion}.
 
@@
     (Top) Median fraction of dwarf or massive primaries with a major or minor companion by stellar mass. 
-    Shaded regions show the $1$-$99$ percentile range of the median pair fractions of each realization. 
+    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
       % massive pairs
@@
 The difference between the massive pair fraction and dwarf pair fraction increases with decreasing redshift, peaking at $z=0$ with a difference of 0.166 for major pairs and 0.111 for minor pairs.
-This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly in the low redshift regime.}
+This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly in the low redshift regime.\todo{remove "difference" label, explain in capt.
+what "diff" means}}
   \label{fig:pairratio}
@@
 
+\kc{key takeaways}
+\kc{what do I want to say about this figure?
+This makes sense because as the universe evolves, structures become bigger and you start increasing the material accreted in the outer regions of the halo, so it not surprising to see an increasing median separation towards lower redshifts.
+}
+\kc{halo mass sets the scale of the typical separations of objects.}
+\kc{We leave the discussion on the implications of the evolution of median separations on pair selection criteria for sec.~\ref{sec:discussion}}
+\kc{This begs the question: what does this mean for selection criteria for pairs at different mass scales and at different redshifts?}
+\kc{The general trend for pairs of all mass types is for higher seps at lower z.
+Also, minor pairs tend to live at closer separations than their major counterparts.
+This is likely because close major pairs are more likely to merge more quickly than minor pairs, so you aren't left with many close major pairs since they have merged at higher z.}
+
 %% text on separation distribution plot
@@
 
-\todo{quick final conclusions on separations}
-
-\kc{here maybe include a table? what are some values?  z=0,1,2,3,4 and pair frac, sep, vel. ?}
+\kc{table? z=0,1,2,3,4 and pair frac, sep, vel. ?}
 
@@
   % Dwarf pairs
-  The redshift evolution of the dwarf pairs closely resembles a power law distribution across the whole redshift range from $z=0-4$.
+  The redshift evolution of the dwarf pairs \remove{\st{closely resembles a power law distribution}} across the whole redshift range from $z=0-4$.
   At $z=4$, the typical separation between major (minor) dwarf pairs is $42(38)\,\kpc$, and peaks at $z=0$ with a median separation of $128(109)\,\kpc$.
@@
   Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs.
+\todo{remove "difference" legend, explain in capt.
+what "Maj-Min" means}
     }
@@
 
+\kc{key takeaways}
+
 %% text on velocity distribution plot
@@
     Major and minor massive pairs also have very little median velocity difference at low redshift (bottom right), with minor pairs having a relative velocity between $1-20\,\kms$ faster than major pairs.
+    \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
     }
@@
   \centering
-  \includegraphics[width=\textwidth]{scaledsep.png}
+  \includegraphics[width=\textwidth]{scaledsep_1000.png}
   \caption{Median scaled separation (separation of a pair divided by the virial radius of its group) as a function of redshift.
@@
 Massive minor pairs tend to have smaller scaled separations compared to dwarf pairs at all redshifts.
-  \todo{replace with 1000 reals fig, finish caption, add 0 horizon line}
+  \todo{finish caption} \todo{remove "difference" legend, explain in capt. what "Ma-Dw" means}
     }
@@
   \centering
-  \includegraphics[width=\textwidth]{scaledsep_distribution.png}
-  \caption{\todo{finish caption, 1000 reals, change median color, add z=4}}
+  \includegraphics[width=\textwidth]{scaledsep_distribution_1000.png}
+  \caption{\todo{finish caption}}
   \label{fig:sep-scaled-dist}
@@
   \centering
-  \includegraphics[width=\textwidth]{scaledvel.png}
+  \includegraphics[width=\textwidth]{scaledvel_1000.png}
   \caption{Median scaled velocity (relative velocity of a pair divided by the virial velocity), defined as the circular velocity at the virial radius of the group as a function of redshift. 
@@
   All sets of pairs show an increase in scaled velocity at lower redshifts.
-  \todo{finish caption, replace with 1000 reals, add 0 horizon line}
+  \todo{finish caption} \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
   }
@@
   \centering
-  \includegraphics[width=\textwidth]{scaledvel_distribution.png}
-  \caption{\todo{finish caption, 1000 reals, change median color, add z=4}}
+  \includegraphics[width=\textwidth]{scaledvel_distribution_1000.png}
+  \caption{\todo{finish caption}}
   \label{fig:vel-scaled-dist}
@@
 \subsection{Implications for observations}
+\subsection{Implications for observational pair selection criteria}
 
@@
 \label{sec:summary}
+Findings:
+\begin{itemize}
+    \item Pair fraction for dwarfs and massives does not proceed identically throughout cosmic time. Opposite behavior at low z. 
+    \item Median pair separations increase and relative velocities decrease from high to low redshift. 
+    \item Minor dwarf and massive pairs exhibit 
+\end{itemize}
 

### 2023-02-24 notebooks/makedata_slurm.py
updates to plotting routines and saving data

@@ -1,0 +1,253 @@
+import h5py
+import os.path
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gd
+from utils.paths import SetupPaths
+import matplotlib.patches as  mpatches
+from matplotlib.ticker import FormatStrFormatter
+from utils.get_summary_data import compile_summary
+from utils.vectorCorrection import vectorCorrection as vector
+
+
+paths = SetupPaths()
+
+# defining equivalent redshifts
+zs = {"z":np.array([0,1,2,3,4]), 
+#       "zill":np.array([135,85,68,60,56]), 
+      "ztng":np.array([99,50,33,25,21])}
+
+# make functions to get data at the requested snapshot
+def get_primmask(primstells, size):
+    if size == "dwarf":
+        mask = (primstells > 0.01) & (primstells < 0.5)
+    elif size == "massive":
+        mask = (primstells > 0.5) & (primstells < 10)
+    return mask
+
+def get_groupmask(groupmass, size):
+    if size == "dwarf":
+        mask = (groupmass > 8) & (groupmass < 50)
+    elif size == "massive":
+        mask = (groupmass > 100) & (groupmass < 650)
+    return mask
+
+class EmptyFile(Exception): pass
+class SkipRedshift(Exception): pass
+
+
+def get_sepvel(reals, key, scaled=False, errorprint=False, redshiftcutoff=True): 
+    snapshots = np.arange(0,100,1)
+    snapshots = np.delete(snapshots, np.where(snapshots==48)[0])
+    redcutoff = 4.2
+        
+    redshifts = []  
+    med_majdw, med_mindw, med_majma, med_minma = [], [], [], []
+    med_majdiff, med_mindiff, med_ddiff, med_mdiff = [], [], [], []
+    quart_majdw, quart_mindw, quart_majma, quart_minma = [], [], [], []
+    quart_majdiff, quart_mindiff, quart_ddiff, quart_mdiff  = [], [], [], []
+            
+    for snap in snapshots:  
+        try:
+            pair_path = f"TNG_{snap}_{reals}.hdf5"
+            pair_data = h5py.File(f"{paths.path_pairs}{pair_path}", "r")
+            
+            if np.size(pair_data) == 0:
+                raise EmptyFile
+                
+            redshift = pair_data['Header'].attrs['Redshift']
+            
+            if redshiftcutoff & ( redshift > redcutoff) :
+                raise SkipRedshift
+                
[…]

### 2023-02-24 pears/utils/PlotMaker1000.py

@@ -1,0 +1,946 @@
+'''
+ PlotMaker1000 makes your favorite plot! 
+ Just pick a plot name below ~                   
+'''
+
+Plot2Make = "counts"
+Plot2Make = "pairfrac"
+# Plot2Make = "sep"
+# Plot2Make = "vel"
+# Plot2Make = "sepdist"
+# Plot2Make = "veldist"
+# Plot2Make = "scaledsep"
+# Plot2Make = "scaledvel"
+
+maketype = "plot"
+maketype = "data"
+maketype = "both"
+
+numreals = 1000
+
+#%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+__author__ = "Katie Chamberlain"
+__status__ = "Beta - forever~"
+__date__   = "Feb 2023 - unedited "
+
+import os.path
+import h5py
+import numpy as np
+import seaborn as sns
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gd
+from utils.paths import SetupPaths
+import matplotlib.patches as  mpatches
+from matplotlib.ticker import FormatStrFormatter
+from utils.get_summary_data import compile_summary
+from utils.vectorCorrection import vectorCorrection as vector
+
+
+paths = SetupPaths()
+
+plt.show();
+plt.rcParams.update({'font.size':20,"xtick.direction":"in","ytick.direction":"in", 
+                     "xtick.top":True, "ytick.right":True,"text.usetex":False,
+                     "xtick.labelsize":18,"ytick.labelsize":18})
+
+# defining color palette for plotting
+palette = {"Illustris dark": "#009292", "Illustris hydro": "#B6DAFF",
+           "TNG dark": "#930200", "TNG hydro": "#FFB5DC",
+           "dwarf":"olive","massive":"salmon", "difference":"#2C1D11", "difference2":"#464646"}
+
+alphas = {"maj": 0.7, "min": 0.3}
+
+# defining equivalent redshifts
+zs = {"z":np.array([0,1,2,3,4]), 
+      "ztng":np.array([99,50,33,25,21])}
+
+# make functions to get data at the requested snapshot
+def get_primmask(primstells, size):
+    if size == "dwarf":
+        mask = (primstells > 0.01) & (primstells < 0.5)
+    elif size == "massive":
+        mask = (primstells > 0.5) & (primstells < 10)
+    return mask
+
+def get_groupmask(groupmass, size):
+    if size == "dwarf":
[…]

### 2023-02-24 pears/utils/paths.py

@@ -51,3 +51,8 @@ class SetupPaths:
         self.path_pairs = self.path_data + "pairs/"
         self.path_median = self.path_data + "median_realization/"
         self.path_simstars = self.path_data + "simulation_mstar/"
+        
+        # pears paper and plots
+        self.path_plots = self.path_pears + "plots/paper1/"
+        self.path_plotdata = self.path_plots + "plotdata/"
+        self.path_paper = self.path_pears + "pears/"

### 2023-02-24 paper/pears.tex

@@
 
+\kc{ to $z=1$, where median separations are $171(124)\,\kpc$}
+
+\kc{ ,. The median separation rises more steeply from z=1 to z=0, peaking around $z=\sim0$ at $288\,\kpc$ and $205\,\kpc$ for major and minor massive pairs respectively.}
+
 \kc{table? z=0,1,2,3,4 and pair frac, sep, vel. ?}
@@
   % Dwarf pairs
-  The redshift evolution of the dwarf pairs \remove{\st{closely resembles a power law distribution}} across the whole redshift range from $z=0-4$.
-  At $z=4$, the typical separation between major (minor) dwarf pairs is $42(38)\,\kpc$, and peaks at $z=0$ with a median separation of $128(109)\,\kpc$.
+  The typical separation between major (minor) dwarf pairs increases from $42(38)\,\kpc$ at $z=4$ to a peak of $128(109)\,\kpc$ at $z=0$.
   % Massive Pairs
-  The separation between massive pairs, on the other hand, increases approximately linearly from $z=4$, where the median separations of major (minor) pairs is $81(71)\,\kpc$, to $z=1$, where median separations are $171(124)\,\kpc$.
-The median separation rises more steeply from z=1 to z=0, peaking around $z=\sim0$ at $288\,\kpc$ and $205\,\kpc$ for major and minor massive pairs respectively.
+  The separation between major (minor) massive pairs, on the other hand, increases from $81(71)\,\kpc$ at $z=4$ to $288(205)\,\kpc$ at  $z=0$.
   % Difference plots
-  (Bottom) The median subtracted separation difference between major and minor pairs, and 1-99\% shaded region.
+  (Bottom) The median difference and 1-99\% range of the difference between major and minor pairs from 1000.
   Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs.

### 2023-02-24 paper/pears.tex
switched plots to newest vers and added combo plots for scaled sep and vel

@@
     \centering
-    \includegraphics[width=\textwidth]{stellarmass_distribution_1000.png}
+    \includegraphics[width=\textwidth]{smrdist_1000.png}
     \caption{Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs.
@@
   \centering
-  \includegraphics[width=\textwidth]{pairratio_1000.png}
+  \includegraphics[width=\textwidth]{pairfrac_1000.png}
   \caption{
@@
   \centering
-  \includegraphics[width=\textwidth]{separation_1000.png}
+  \includegraphics[width=\textwidth]{sep_1000.png}
   \caption{(Top) Median physical separation (in kpc) of dwarf pairs (left, green) and massive pairs (right, pink) as a function of redshift. 
@@
   \centering
-  \includegraphics[width=\textwidth]{separation_distribution_1000.png}
+  \includegraphics[width=\textwidth]{sepdist_1000.png}
   \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right).
@@
   \centering
-  \includegraphics[width=\textwidth]{velocity_1000.png}
+  \includegraphics[width=\textwidth]{vel_1000.png}
   \caption{
@@
   \centering
-  \includegraphics[width=\textwidth]{velocity_distribution_1000.png}
+  \includegraphics[width=\textwidth]{veldist_1000.png}
   \caption{
@@
   \centering
-  \includegraphics[width=\textwidth]{scaledsep_1000.png}
+  \includegraphics[width=\textwidth]{scaledcombo_1000.png}
   \caption{Median scaled separation (separation of a pair divided by the virial radius of its group) as a function of redshift.
@@
   \todo{finish caption} \todo{remove "difference" legend, explain in capt. what "Ma-Dw" means}
+  Median scaled velocity (relative velocity of a pair divided by the virial velocity), defined as the circular velocity at the virial radius of the group as a function of redshift. 
+  Major pairs are on the left (solid lines), minor pairs are on the right in dashed lines.
+  All sets of pairs show an increase in scaled velocity at lower redshifts.
+  \todo{finish caption} \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
     }
-  \label{fig:sep-scaled}
+  \label{fig:scaled}
 \end{figure*}
@@
   \centering
-  \includegraphics[width=\textwidth]{scaledsep_distribution_1000.png}
+  \includegraphics[width=\textwidth]{scaledcombodist_1000.png}
   \caption{\todo{finish caption}}
-  \label{fig:sep-scaled-dist}
-\end{figure*}
-
-\begin{figure*}[htp]
-  \centering
-  \includegraphics[width=\textwidth]{scaledvel_1000.png}
-  \caption{Median scaled velocity (relative velocity of a pair divided by the virial velocity), defined as the circular velocity at the virial radius of the group as a function of redshift. 
-  Major pairs are on the left (solid lines), minor pairs are on the right in dashed lines.
-  All sets of pairs show an increase in scaled velocity at lower redshifts.
-  \todo{finish caption} \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
-  }
-  \label{fig:vel-scaled}
-\end{figure*}
-
-\begin{figure*}[htp]
-  \centering
-  \includegraphics[width=\textwidth]{scaledvel_distribution_1000.png}
-  \caption{\todo{finish caption}}
-  \label{fig:vel-scaled-dist}
+  \label{fig:scaled-dist}
 \end{figure*}

### 2023-02-28 paper/pears.tex
reorganized results and discussion and pair frac text

@@
 \begin{abstract}
-  \todo{REMEMBER TO USE 100-1000 REALS IN PLOTS}
-
-  \todo{Include ticks on top and right axis as well}
 
@@
  \section{Sample selection}\label{sec:methods}
-% methods plots
-  \begin{figure*}[htp]
-    \centering
-    \includegraphics[width=\textwidth]{counts_1000.png}
-    \caption{(Top) \kc{correct wording: Median number of dwarf (left) and massive (right) primaries and pairs per abundance matching realization as a function of redshift.} 
-    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations, as described in Sec.~\ref{sec:methods-err}.
-    There are approximately 8 times as many dwarf primaries as massive primaries. 
-    % dwarf galaxies
-    The dwarf primary count (green solid line in top left panel) is at a minimum at $z=4$, rises to a maximum of $\sim15000$ halos per realization by $z=1$, then decreases by $\sim16\%$ to 12000 halos at $z=0$.
+% % methods plots
+%   \begin{figure*}[htp]
+%     \centering
+%     \includegraphics[width=\textwidth]{counts_1000.png}
+%     \caption{(Top) Median number of dwarf (left) and massive (right) primaries and pairs as a function of redshift.
+%     Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations, as described in Sec.~\ref{sec:methods-err}.
+%     There are approximately 8 times as many dwarf primaries as massive primaries. 
+%     % dwarf galaxies
+%     The dwarf primary count (green solid line in top left panel) is at a minimum at $z=4$, rises to a maximum of $\sim15000$ halos per realization by $z=1$, then decreases by $\sim16\%$ to 12000 halos at $z=0$.
 The dwarf pair count (green dashed line), on the other hand, peaks at $z\sim2$ with 3000 pairs, and decreases to a minimum of about 1000 pairs at $z=0$.
-    % Massive galaxies (right)
-    The massive primary count (pink solid line in top right panel) behaves similarly to the dwarf primary count, with a minimum count at $z=4$ which rises to a maximum of $\sim2000$ halos per realization at $z\sim1$, then decreases slightly by $\sim5\%$ to $\sim$1800 halos by $z=0$.
-    Unlike dwarf pairs whose pair count peaks at $z=2$, pair count for massive galaxies (pink dashed line) follows similar behavior to the total massive primary count, with a minimum at $z=4$, and increasing to $z=\sim 1$ before leveling off.
+%     % Massive galaxies (right)
+%     The massive primary count (pink solid line in top right panel) behaves similarly to the dwarf primary count, with a minimum count at $z=4$ which rises to a maximum of $\sim2000$ halos per realization at $z\sim1$, then decreases slightly by $\sim5\%$ to $\sim$1800 halos by $z=0$.
+%     Unlike dwarf pairs whose pair count peaks at $z=2$, pair count for massive galaxies (pink dashed line) follows similar behavior to the total massive primary count, with a minimum at $z=4$, and increasing to $z=\sim 1$ before leveling off.
 At very low redshift, the pair count and primary count have opposite behavior, with the pair count \textit{increasing} at very low redshifts of $z=0-0.25$ and \textit{peaking} at $z=0$.
-    (Bottom) Fraction of pairs per primary as a function of redshift (i.e., the ratio between dotted line and solid line in each column).
+%     (Bottom) Fraction of pairs per primary as a function of redshift (i.e., the ratio between dotted line and solid line in each column).
 Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$.
 The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.}
-    \label{fig:counts}
-  \end{figure*}
+%     \label{fig:counts}
+%   \end{figure*}
 
-  \begin{figure*}[htp]
-    \centering
-    \includegraphics[width=\textwidth]{smrdist_1000.png}
-    \caption{Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs.
+%   \begin{figure*}[htp]
+%     \centering
+%     \includegraphics[width=\textwidth]{smrdist_1000.png}
+%     \caption{Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs.
 Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$.
 Overall, the stellar mass ratio distribution of major and minor pairs of dwarf and massive galaxies show little evolution from $z=4$ (right) to $z=0$ (left).
-    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.}
-    \label{fig:massratio}
-  \end{figure*}
+%     Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.}
+%     \label{fig:massratio}
+%   \end{figure*}
 
-Our sample data was obtained using a strict set of selection criteria, as outlined in this section.
-In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulations utilized in this study.
-Sec.~\ref{sec:methods-am} explains the abudance matching prescription used to associate stellar masses with the dark matter subhalos.
-Sec.~\ref{sec:methods-crit} provides a detailed outline of our selection criteria and process for picking pairs.
-Finally, Sec.~\ref{sec:methods-counts} gives an overview of the properties of our sample.
+% Our sample data was obtained using a strict set of selection criteria, as outlined in this section.
+% In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulations utilized in this study.
+% Sec.~\ref{sec:methods-am} explains the abudance matching prescription used to associate stellar masses with the dark matter subhalos.
+% Sec.~\ref{sec:methods-crit} provides a detailed outline of our selection criteria and process for picking pairs.
+% Finally, Sec.~\ref{sec:methods-counts} gives an overview of the properties of our sample.
 
-%%%%%%%%%%%
-%%%%%%%%%%%
-\subsection{Simulation details}\label{sec:methods-sims}
-% what is it that we are trying to study? why use illustris?
-To understand the occurance rate and separations of typical galaxy pairs in a cosmological context, we require a simulation that provides a large statistical sample of pairs in both the dwarf and massive galaxy regime.
-Thus, we are limited in our simulation choice to large-volume cosmological simulations. 
-However, we also require high resolution simulations such that the dwarf subhalos are resolved well enough to ensure robust statistics at the low mass end, and so we are not limited by our inability to resolve objects down to halo masses of $M_{\rm halo}\approx1\times 10^9\, \Msun$.
+% %%%%%%%%%%%
+% %%%%%%%%%%%
+% \subsection{Simulation details}\label{sec:methods-sims}
+% % what is it that we are trying to study? why use illustris?
+% To understand the occurance rate and separations of typical galaxy pairs in a cosmological context, we require a simulation that provides a large statistical sample of pairs in both the dwarf and massive galaxy regime.
+% Thus, we are limited in our simulation choice to large-volume cosmological simulations. 
+% However, we also require high resolution simulations such that the dwarf subhalos are resolved well enough to ensure robust statistics at the low mass end, and so we are not limited by our inability to resolve objects down to halo masses of $M_{\rm halo}\approx1\times 10^9\, \Msun$.
 
-% Baryonic processes
-Baryonic process are known to affect the dark matter halo structure of low mass ($M_*<1\times10^9\Msun$) subhalos in simulations~\citep[see e.g.][and references therein]{Sales:2022}.
-Additionally, the shallow potential well of dwarf galaxies compared to their massive counterparts may lend themselves more easily to disruption from baryonic processes such as supernova feedback, which could change the occurance rate of low mass subhalos in hydrodynamic simulations \kc{check and see if they looked at this in the TNG100 galaxy paper}.
-To study the effect of baryonic processes on the rate and separation of pairs, we require cosmological simulations which have both dark matter only runs and to full hydrodynamics.
+% % Baryonic processes
+% Baryonic process are known to affect the dark matter halo structure of low mass ($M_*<1\times10^9\Msun$) subhalos in simulations~\citep[see e.g.][and references therein]{Sales:2022}.
+% Additionally, the shallow potential well of dwarf galaxies compared to their massive counterparts may lend themselves more easily to disruption from baryonic processes such as supernova feedback, which could change the occurance rate of low mass subhalos in hydrodynamic simulations \kc{check and see if they looked at this in the TNG100 galaxy paper}.
+% To study the effect of baryonic processes on the rate and separation of pairs, we require cosmological simulations which have both dark matter only runs and to full hydrodynamics.
 
-% details of Illustris and Illustris TNG
-The \textit{Illustris Project} ~\citep{vogelsberger14A,nelson15} and \textit{IllustrisTNG Project}~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} are a set of N-body and hydrodynamic cosmological simulations which are perfectly suited for such a study.
-We use the dark matter only and full hydrodynamic runs of both the \ill-1 and \tng100-1 simulations to explore the connection between pairs and baryonic processes. 
-Each of these simulations follows the dynamical evolution of $1820^3$ dark matter particles from $z=127$ to $z=0$ through a periodic volume of roughly $100^3$ Mpc$^3$. 
-The \ill{} simulations follow a cosmology consistent with \textit{WMAP-9}~\citep{hinshaw2013}, while the \tng{} simulations are consistent with \textit{Planck2015}~\citep{Planck2015}.
-Specifically, we use the \textit{Illustris-1-Dark}, \textit{Illustris-1}, \textit{TNG100-1-Dark}, and \textit{TNG100-1} simulations (hereafter \illd, \illh, \tngd, and \tngh{} respectively, % see Table~\ref{table:sim} for details).
+% % details of Illustris and Illustris TNG
+% The \textit{Illustris Project} ~\citep{vogelsberger14A,nelson15} and \textit{IllustrisTNG Project}~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} are a set of N-body and hydrodynamic cosmological simulations which are perfectly suited for such a study.
+% We use the dark matter only and full hydrodynamic runs of both the \ill-1 and \tng100-1 simulations to explore the connection between pairs and baryonic processes. 
+% Each of these simulations follows the dynamical evolution of $1820^3$ dark matter particles from $z=127$ to $z=0$ through a periodic volume of roughly $100^3$ Mpc$^3$. 
+% The \ill{} simulations follow a cosmology consistent with \textit{WMAP-9}~\citep{hinshaw2013}, while the \tng{} simulations are consistent with \textit{Planck2015}~\citep{Planck2015}.
+% Specifically, we use the \textit{Illustris-1-Dark}, \textit{Illustris-1}, \textit{TNG100-1-Dark}, and \textit{TNG100-1} simulations (hereafter \illd, \illh, \tngd, and \tngh{} respectively, % see Table~\ref{table:sim} for details).
 
-% deets on the hydrodynamics of 
-\kc{hydrodynamics details on the difference between the two hydro simulations. also include differences between the two dark simulations, if there are any besides the cosmology. }
+% % deets on the hydrodynamics of 
+% \kc{hydrodynamics details on the difference between the two hydro simulations. also include differences between the two dark simulations, if there are any besides the cosmology. }
 
-% subfind, sublink, and groups and subhalos
-We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm ~\citep{springel2001,dolag09}. 
-These catalogs consist of halos (or "groups"), defined using the Friends-of-Friends (FoF) algorithm~\citep{davis1985} to link nearby particles, and their associated subhalos, which are over-dense and gravitationally bound dark matter structures.
-We also use the merger trees provided by the \texttt{SUBLINK} algorithm \citep{gomez15}, which tracks subhalos between snapshots using their particle data, in order to trace the mass growth and merger histories of our subhalos.
+% % subfind, sublink, and groups and subhalos
+% We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm ~\citep{springel2001,dolag09}. 
+% These catalogs consist of halos (or "groups"), defined using the Friends-of-Friends (FoF) algorithm~\citep{davis1985} to link nearby particles, and their associated subhalos, which are over-dense and gravitationally bound dark matter structures.
+% We also use the merger trees provided by the \texttt{SUBLINK} algorithm \citep{gomez15}, which tracks subhalos between snapshots using their particle data, in order to trace the mass growth and merger histories of our subhalos.
 
-% \begin{table*}[htb]
-% \begin{tabular}{l|llll}
-%  & \illd & \illh & \tngd & \tngh\\\hline\hline
-%  L$_{\rm Box}$ [Mpc] & 106.5 & 106.5 & 110.7 & 110.7 \\
-% m$_{\rm DM}$ [M$_\odot$] & 7.5$\times10^6$ & 6.3$\times10^6$ & 8.9$\times10^6$ & $7.5\times10^6$\\
-% m$_{\rm gas}$ & -- & $1.3\times 10^{6}$ & -- & $1.4\times 10^{6}$ \\\hline
-% \end{tabular}
-% \caption{\label{table:sim}Parameters of the Illustris simulations used in this analysis.}
-% \end{table*}
+% % \begin{table*}[htb]
+% % \begin{tabular}{l|llll}
+% %  & \illd & \illh & \tngd & \tngh\\\hline\hline
+% %  L$_{\rm Box}$ [Mpc] & 106.5 & 106.5 & 110.7 & 110.7 \\
+% % m$_{\rm DM}$ [M$_\odot$] & 7.5$\times10^6$ & 6.3$\times10^6$ & 8.9$\times10^6$ & $7.5\times10^6$\\
+% % m$_{\rm gas}$ & -- & $1.3\times 10^{6}$ & -- & $1.4\times 10^{6}$ \\\hline
+% % \end{tabular}
+% % \caption{\label{table:sim}Parameters of the Illustris simulations used in this analysis.}
+% % \end{table*}
 
-%%%%%%%%%%%
-%%%%%%%%%%%
-\subsection{Abundance matching prescription}\label{sec:methods-am}
-% Why do we need stellar masses?
-One of the goals of this study is to determine the impact of baryonic physics on the occurrence rate and typical separations of galaxy \kc{subhalo?} pairs in cosmological simulations. 
-However, selecting halo pairs by stellar mass ratio using the stellar masses provided by the simulations is not possible in the dark matter only runs. 
-Thus, in order ensure the dark matter only and full hydrodynamic samples are self-consistent, we need to associate each of the selected subhalos with a realistic stellar mass.
+% %%%%%%%%%%%
+% %%%%%%%%%%%
+% \subsection{Abundance matching prescription}\label{sec:methods-am}
+% % Why do we need stellar masses?
+% One of the goals of this study is to determine the impact of baryonic physics on the occurrence rate and typical separations of galaxy \kc{subhalo?} pairs in cosmological simulations. 
+% However, selecting halo pairs by stellar mass ratio using the stellar masses provided by the simulations is not possible in the dark matter only runs. 
+% Thus, in order ensure the dark matter only and full hydrodynamic samples are self-consistent, we need to associate each of the selected subhalos with a realistic stellar mass.
 
-% What is abundance matching
-Abundance matching is one such method of associating a dark matter halo with a stellar mass, assuming a galaxy would form in a halo of that mass.
+% % What is abundance matching
+% Abundance matching is one such method of associating a dark matter halo with a stellar mass, assuming a galaxy would form in a halo of that mass.
 
-However, there is large scatter in the stellar-mass-halo-mass (SMHM) relationship, especially in the dwarf halo regime.
+% However, there is large scatter in the stellar-mass-halo-mass (SMHM) relationship, especially in the dwarf halo regime.
 
-% How do we utilize it? 
-In particular, we use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic recipe to paint stellar masses onto dark matter halos. 
-The~\citet{Moster2013} relationship is a redshift-evolving function of the halo mass, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.
-\kc{why moster instead of another AM relationship? most closely represent data at lower mass? }
+% % How do we utilize it? 
+% In particular, we use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic recipe to paint stellar masses onto dark matter halos. 
+% The~\citet{Moster2013} relationship is a redshift-evolving function of the halo mass, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.
+% \kc{why moster instead of another AM relationship? most closely represent data at lower mass? }
 
-To assign stellar masses to each of the dark matter halos, we assume that the stellar mass of both the primary and secondary halo can change as a function of redshift after the secondary has entered the primary's halo and do not immediately cease star formation.
-This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{geha13} which finds that isolated dwarfs ($>1\Mpc$ from a MW-type galaxy) are often star forming and rarely quenched.
-Additionally,~\citet{Munshi2021} found that the stellar mass of subhalos at $z=0$ in the XX simulations are more closely correlated with the peak halo mass than the $z=0$ halo mass for halos with peak halo mass $10^8<M_{\rm peak}<10^{11} \Msun$.
+% To assign stellar masses to each of the dark matter halos, we assume that the stellar mass of both the primary and secondary halo can change as a function of redshift after the secondary has entered the primary's halo and do not immediately cease star formation.
+% This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{geha13} which finds that isolated dwarfs ($>1\Mpc$ from a MW-type galaxy) are often star forming and rarely quenched.
+% Additionally,~\citet{Munshi2021} found that the stellar mass of subhalos at $z=0$ in the XX simulations are more closely correlated with the peak halo mass than the $z=0$ halo mass for halos with peak halo mass $10^8<M_{\rm peak}<10^{11} \Msun$.
 
-Thus, we treat each of the subhalos as centrals according to the~\citet{Moster2013} prescription, using the current snapshot redshift and the peak halo mass of the subhalo to calculate the stellar mass.
-This additionally allows us remain robust to scenarios in which a secondary may have formed most of its stars, and then lost a significant portion of its dark matter content through tidal interactions with a primary, but will retain the bulk of its stellar content.
+% Thus, we treat each of the subhalos as centrals according to the~\citet{Moster2013} prescription, using the current snapshot redshift and the peak halo mass of the subhalo to calculate the stellar mass.
+% This additionally allows us remain robust to scenarios in which a secondary may have formed most of its stars, and then lost a significant portion of its dark matter content through tidal interactions with a primary, but will retain the bulk of its stellar content.
 
-We create 1000 stellar mass realizations from the SMHM relationship, thus accounting for the systematic uncerntainy in subhalo stellar masses.
+% We create 1000 stellar mass realizations from the SMHM relationship, thus accounting for the systematic uncerntainy in subhalo stellar masses.
 Each realization is treated as an independent sample, such that computed properties (pair frequency, separations, etc) are given as the median each realization.
@@
 
-\subsubsection{Error calculations}\label{sec:methods-err}
+% \subsubsection{Error calculations}\label{sec:methods-err}
 
-%%%%%%%%%%%
-%%%%%%%%%%%
-\subsection{Selection criteria}\label{sec:methods-crit}
-In this section, we outline the selection criteria used to select dwarf and massive subhalo pairs. 
-The same selection criteria is utilized for all four simulations (\illd, \illh, \tngd, and \tngh)
-In short, blah. 
-Detailed steps are as follows.
+% %%%%%%%%%%%
+% %%%%%%%%%%%
+% \subsection{Selection criteria}\label{sec:methods-crit}
+% In this section, we outline the selection criteria used to select dwarf and massive subhalo pairs. 
+% The same selection criteria is utilized for all four simulations (\illd, \illh, \tngd, and \tngh)
+% In short, blah. 
+% Detailed steps are as follows.
 
-\subsubsection{Isolation}
-As we are interested in the frequency and separations of galaxy pairs that are undisturbed by nearby massive perturbers, we select subhalo pairs as the most massive subhalos of their group halos. 
-We have confirmed that nearly 100\% of the the most massive subhalos in each group are outside of the Hill radius of any nearby subhalo with greater mass, and are thus a rough isolation criteria is inherent in our selection.
+% \subsubsection{Isolation}
+% As we are interested in the frequency and separations of galaxy pairs that are undisturbed by nearby massive perturbers, we select subhalo pairs as the most massive subhalos of their group halos. 
+% We have confirmed that nearly 100\% of the the most massive subhalos in each group are outside of the Hill radius of any nearby subhalo with greater mass, and are thus a rough isolation criteria is inherent in our selection.
 
-\textbf{Definitions:} each of these defines the subhalo at a single snapshot and for a single realization.
-\begin{itemize}
-  \item Primary - Most massive subhalo in a group by stellar mass
-  \item Secondary - 
-  \item Major pair - A pair of subhalos consisting of a primary and secondary with stellar mass ratio $1/4 < \rm M_{*,sec}/M_{*, prim} < 1$
-  \item Minor pair - A pair of subhalos consisting of a primary and secondary with stellar mass ratio $1/10 < \rm M_{*,sec}/M_{*, prim} < 1/4$
-\end{itemize}
-Note that the subhalo that is assigned as primary or secondary may change between stellar mass realizations.
+% \textbf{Definitions:} each of these defines the subhalo at a single snapshot and for a single realization.
+% \begin{itemize}
+%   \item Primary - Most massive subhalo in a group by stellar mass
+%   \item Secondary - 
+%   \item Major pair - A pair of subhalos consisting of a primary and secondary with stellar mass ratio $1/4 < \rm M_{*,sec}/M_{*, prim} < 1$
+%   \item Minor pair - A pair of subhalos consisting of a primary and secondary with stellar mass ratio $1/10 < \rm M_{*,sec}/M_{*, prim} < 1/4$
+% \end{itemize}
+% Note that the subhalo that is assigned as primary or secondary may change between stellar mass realizations.
 Also note\kc{that this method may yield pairs where the secondary has a higher subhalo mass than the primary.
@@
 
-\begin{enumerate}
-  \item Select groups in some group range that encompasses MCs and MW-M31
-  \item For every subhalo in every group with halo mass >1e9Msun, use merger trees to get the maximum masses.
-  \item Generate 1000 stellar mass realization using abundance matching so we can account for the spread in the relationship
-  \item Generate catalog at each redshift containing: 
-  \begin{itemize}
-    \item For each realization, and in each group with a single subhalo, add the subhalo and it's properties to a catalog of single halos.
-    \item For each realization, and in each group with 2+ halos, find most massive halo by stellar mass, and the second most massive halo by stellar mass, then add to pair catalog. 
-    \item If a group has 3+ halos, check the stellar mass of the third most massive object, and see if it is a major/minor companion of the secondary. If not, teritary flag = 0. Otherwise =1.
-  \end{itemize}
-  \item Select dwarf primaries: for full catalog, most massive halo (in "pairs") or single halos with stellar mass $1\times10^{8} < \msam < 5\times10^{9} \Msun$. 
-  \item Select dwarf pairs: for full pair catalog, any pair with stellar mass ratio between 1-1/4 (major pairs) or between 1/4-1/10 (minor pairs).
+% \begin{enumerate}
+%   \item Select groups in some group range that encompasses MCs and MW-M31
+%   \item For every subhalo in every group with halo mass >1e9Msun, use merger trees to get the maximum masses.
+%   \item Generate 1000 stellar mass realization using abundance matching so we can account for the spread in the relationship
+%   \item Generate catalog at each redshift containing: 
+%   \begin{itemize}
+%     \item For each realization, and in each group with a single subhalo, add the subhalo and it's properties to a catalog of single halos.
+%     \item For each realization, and in each group with 2+ halos, find most massive halo by stellar mass, and the second most massive halo by stellar mass, then add to pair catalog. 
+%     \item If a group has 3+ halos, check the stellar mass of the third most massive object, and see if it is a major/minor companion of the secondary. If not, teritary flag = 0. Otherwise =1.
+%   \end{itemize}
+%   \item Select dwarf primaries: for full catalog, most massive halo (in "pairs") or single halos with stellar mass $1\times10^{8} < \msam < 5\times10^{9} \Msun$. 
+%   \item Select dwarf pairs: for full pair catalog, any pair with stellar mass ratio between 1-1/4 (major pairs) or between 1/4-1/10 (minor pairs).
 All pairs is the union of these two sets.
@@
 Note that unpaired can still have very minor companions.
-\end{enumerate}
+% \end{enumerate}
 
-The lower mass threshold for subhalos that constitute our dwarf pairs have a halo mass greater than $1\times10^9\Msun$, such that each of our halos are resolved into at least 100 particles in each simulation.
-\kc{why 100?}
+% The lower mass threshold for subhalos that constitute our dwarf pairs have a halo mass greater than $1\times10^9\Msun$, such that each of our halos are resolved into at least 100 particles in each simulation.
+% \kc{why 100?}
 
-\subsubsection{Primary subhalos}\label{sec:methods-crit-prims}
+% \subsubsection{Primary subhalos}\label{sec:methods-crit-prims}
 
-\subsubsection{Primary subhalos}\label{sec:methods-crit-pairs}
+% \subsubsection{Primary subhalos}\label{sec:methods-crit-pairs}
 
-\subsubsection{Stellar masses from the hydro sims}
+% \subsubsection{Stellar masses from the hydro sims}
 
-\subsection{Counts and distributions}\label{sec:methods-counts}
+% \subsection{Counts and distributions}\label{sec:methods-counts}
 
-\begin{itemize}
-  \item Introduce simulations
-  \item outline selection steps
-  \item dwarf pairs
-  \item massive pairs
-  \item include table with parameters used for pairs
-  \item plots
-    \begin{itemize}
-      \item distribution plots
-      \item counts plots
-    \end{itemize}
-\end{itemize}
+% \begin{itemize}
+%   \item Introduce simulations
+%   \item outline selection steps
+%   \item dwarf pairs
+%   \item massive pairs
+%   \item include table with parameters used for pairs
+%   \item plots
+%     \begin{itemize}
+%       \item distribution plots
+%       \item counts plots
+%     \end{itemize}
+% \end{itemize}
 
-% selection criterion
-\begin{table*}[htb]
-  \centering
-    \begin{tabular}{lcc}
-     & Dwarf Pairs & Massive Pairs \\\hline\hline
-    % Group Mass & $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ & $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$  \\
-    % Subhalo Max Mass &  &  \\
-    % Subhalo Current Mass & $>1\times10^{10} \Msun$ & $> 5\times10^{11} \Msun$ \\
-    Primary &$1\times10^{8} < \msam < 5\times10^{9} \Msun$ & $5\times10^{9} < \msam < 1\times10^{11} \Msun$\\\hline
-    \end{tabular}
-    \caption{\label{table:mass}Selection criteria for dwarf and massive pairs.}
-    \end{table*}
+% % selection criterion
+% \begin{table*}[htb]
+%   \centering
+%     \begin{tabular}{lcc}
+%      & Dwarf Pairs & Massive Pairs \\\hline\hline
+%     % Group Mass & $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ & $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$  \\
+%     % Subhalo Max Mass &  &  \\
+%     % Subhalo Current Mass & $>1\times10^{10} \Msun$ & $> 5\times10^{11} \Msun$ \\
+%     Primary &$1\times10^{8} < \msam < 5\times10^{9} \Msun$ & $5\times10^{9} < \msam < 1\times10^{11} \Msun$\\\hline
+%     \end{tabular}
+%     \caption{\label{table:mass}Selection criteria for dwarf and massive pairs.}
+%     \end{table*}
 
-% equivalent snapshot table
-\begin{table*}[tbp]
-  \centering
-  \begin{tabular}{l|cc|cccc} % increase this to 7 columns
-    \hline \hline
-   & \multicolumn{2}{c|}{Snapshot number} & \multicolumn{4}{c}{Number of primaries}\\
-   & \ill & \tng  & \illd & \illh & \tngd & \tngh \\ 
-  \hline
-  z = 0   &   135  &   99   & $11431.5_{-24.42}^{68.38}$ & $12650.0_{-25.84}^{46.84}$ & $13255.0_{-32.60}^{56.72}$ & $12035.0_{-69.24}^{20.36}$\\
-  z = 1   &   85   &   50   &  $14769.0_{-30.24}^{47.28}$ & $16568.0_{-32.20}^{69.60}$ & $17445.5_{-40.86}^{51.90}$ & $15946.5_{-59.38}^{39.22}$ \\
-  z = 2   &   68   &   33   &  $12602.5_{-31.98}^{45.94}$ & $14174.0_{-12.48}^{62.32}$ & $15413.5_{-34.62}^{28.86}$ & $14334.0_{-29.44}^{45.24}$ \\
-  z = 3   &   60   &   25   &     $8533.5_{-54.50}^{39.46}$ & $9390.0_{-63.40}^{41.32}$ & $10901.0_{-44.64}^{46.56}$ & $10106.5_{-47.90}^{39.74}$  \\
-  % z = 3.7   &   54   &   21   \\
-  \hline \hline
-  \end{tabular}
-  \caption{\label{tab:equiv-snapshot} The snapshot number of the original \ill\ and the \tng\ simulations at redshifts $z=0-3$, as well as the median number dwarf (massive) primaries that were selected with $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$ ($5\times 10^{9} < \msam < 1\times 10^{11} \rm M_\odot$) in XX abundance matching realizations.
+% % equivalent snapshot table
+% \begin{table*}[tbp]
+%   \centering
+%   \begin{tabular}{l|cc|cccc} % increase this to 7 columns
+%     \hline \hline
+%    & \multicolumn{2}{c|}{Snapshot number} & \multicolumn{4}{c}{Number of primaries}\\
+%    & \ill & \tng  & \illd & \illh & \tngd & \tngh \\ 
+%   \hline
+%   z = 0   &   135  &   99   & $11431.5_{-24.42}^{68.38}$ & $12650.0_{-25.84}^{46.84}$ & $13255.0_{-32.60}^{56.72}$ & $12035.0_{-69.24}^{20.36}$\\
+%   z = 1   &   85   &   50   &  $14769.0_{-30.24}^{47.28}$ & $16568.0_{-32.20}^{69.60}$ & $17445.5_{-40.86}^{51.90}$ & $15946.5_{-59.38}^{39.22}$ \\
+%   z = 2   &   68   &   33   &  $12602.5_{-31.98}^{45.94}$ & $14174.0_{-12.48}^{62.32}$ & $15413.5_{-34.62}^{28.86}$ & $14334.0_{-29.44}^{45.24}$ \\
+%   z = 3   &   60   &   25   &     $8533.5_{-54.50}^{39.46}$ & $9390.0_{-63.40}^{41.32}$ & $10901.0_{-44.64}^{46.56}$ & $10106.5_{-47.90}^{39.74}$  \\
+%   % z = 3.7   &   54   &   21   \\
+%   \hline \hline
+%   \end{tabular}
+%   \caption{\label{tab:equiv-snapshot} The snapshot number of the original \ill\ and the \tng\ simulations at redshifts $z=0-3$, as well as the median number dwarf (massive) primaries that were selected with $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$ ($5\times 10^{9} < \msam < 1\times 10^{11} \rm M_\odot$) in XX abundance matching realizations.
 \kc{fill in with numbers after doing more realizations} \kc{include takeaway}}
-  \end{table*}
+%   \end{table*}
 
-%%%%%%%%%%%%%%%%%%%
-%% dwarf figures %%
-%%%%%%%%%%%%%%%%%%%
-\kc{why did we stop at z=4? we didn't, explanation about low \# statistics }
+% %%%%%%%%%%%%%%%%%%%
+% %% dwarf figures %%
+% %%%%%%%%%%%%%%%%%%%
+% \kc{why did we stop at z=4? we didn't, explanation about low \# statistics }
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%
 
@@
 At each snapshot, we generate 1000 different realizations of the pair catalog, where each realization represents one instance of the abundance matching technique to assign stellar masses to dark matter halos (see methods).
-In each of the following plots, the median and a percentile spread each value are calculated by finding the median from each of the 1000 AM realizations, and taking the median and spread of that set of median values.
+In each of the following plots, the median and a percentile spread each value are calculated by finding the median from each of the 1000 AM realizations, and taking the median and spread of that set of median values (see Sec.~\ref{sec:methods-err} for more detail).
 
-In Sec.~\ref{sec:results-frac}, we show the redshift evolution of the fraction of primaries with a major or minor companion and compare the "pair fractions" of dwarf pairs to massive pairs.
-In Sec.~\ref{sec:results-kinematics}, we look at the redshift evolution of the median separations and relative velocities between primary and secondary halos on a snapshot-by-snapshot basis.
+In Sec.~\ref{sec:results-frac}, we show the redshift evolution of the fraction of primaries with a major or minor companion (the ``pair fraction") and compare dwarf pairs and massive pairs.
+In Sec.~\ref{sec:results-kinematics}, we look at the redshift evolution of the separations and relative velocities between primary and secondary halos of each pair.
+% need to specify this is snapshot by snapshot?
+In Sec.~\ref{sec:results-scaled}, we compare the ``scaled" separations and velocities of dwarf and massive pairs.
 
 \subsection{Pair fraction}\label{sec:results-frac}
-%% text on pair fraction plot
+    % intro to pair frac plot
 The pair fraction is defined here as the fraction of identified dwarf or massive primaries with a major or minor companion (see Sec.~\ref{sec:methods-crit} for more info on selection criteria for major and minor pairs).
-Fig.~\ref{fig:pairratio} shows the calculated pair fractions for massive and dwarf pairs (including both major and minor pairs separately) as a function of time for $z=0-4$.
+Fig.~\ref{fig:pairratio} shows the pair fractions calculated for massive and dwarf pairs (including both major and minor pairs separately) as a function of time for $z=0-4$.
+
+    % differences between massive and dwarf pairs? 
+The dwarf pair fraction evolves distinctly from that of massive pairs.
+Both major and minor dwarf pair fractions start at their minima at $z=0$, and increase by about 200\% by $z\sim2-2.5$, at which point the pair fractions level off and remain constant from $z=3-4$. 
+The major and minor pair fractions for massive pairs evolve similarly, starting at their maxima at $z=0$, then abruptly declining to $z\sim0.25$, before remaining approximately constant from $z=1-4$ %(see Table~\ref{table:vals} for more precise values of the pair fractions).
+
+    % difference panels
+The bottom panel of Fig.~\ref{fig:pairratio} shows the dwarf pair fraction subtracted from the massive pair fraction (labelled ``$\rm M-D$"). 
+The pair fraction difference reaches a maximum at $z=0$ for both major and minor pairs, and declines to $z\sim2-2.5$ at which point the difference levels out close to 0.
 
     % differences between major and minor pairs? 
-The minor pair fraction of both massive and dwarf pairs tends to be smaller than that of major pairs of the same mass range at all redshifts.
-This is likely because of the lower stellar mass ratio limit we put on our pairs.
-\kc{take away -- why?
-what does the difference between major and minor mean?
-check g's 2018 paper for discussion}
+The median pair fraction for minor pairs (for both dwarf and massive galaxies) is less than that of major pairs of the same mass range at all redshifts.
+This is due to the lower stellar mass ratio limit we put on our pairs.
+Expanding the mass ratio criteria of our minor pair sample to include stellar mass ratios between 1/10-1/100 in our minor pair sample increases the fraction of minor pairs by a factor of $>2$ for massive pairs and between $~1.5-2x$ for dwarf pairs.
+\kc{are there any additional takeaways from this?
+}
 
-    % differences between massive and dwarf pairs? 
-Additionally, dwarf and massive pair fractions evolve distinctly over this redshift range -- the mass pair fraction is roughly flat/constant, while the dwarf pair fraction declines from $z=\sim 2-3$ to a minimum at $z=0$.
-The subtracted difference between the pair fractions of massive and dwarf pairs (respectively) is low and flat at high z (z=$2-4$), but increases up to $\sim0.12-0.18$ by $z=0$. 
-Thus, our expectations for massive and dwarf pair counts should evolve very differently at low redshift, despite being roughly equivalent at higher z. 
-The implications of the difference in the evolution of pair fractions for dwarf and massive pairs across time is discussed in detail in Sec.~\ref{sec:discussion}.
+    % what do we learn from this? what are the takeaways? where do we discuss this in more detail?
+Overall, these results show that massive and dwarf pair counts evolve differently, particularly at very low redshift despite the pair fractions being roughly equal at higher z.
+These differences could be a result of the different formation mechanisms at play in the evolution of the systems at two different mass scales, or alternatively, from differences in satellite dynamics between dwarf and massive systems (see Sec.~\ref{sec:results-kinematics}).
+The implications for the difference in the evolution of pair fractions for dwarf and massive pairs across time is discussed in detail in Sec.~\ref{sec:discussion}.
 
-%% pair fraction plot
+    % pair fraction plot
 \label{sec:results}
@@
     % Top plots ~
-    (Top) Median fraction of dwarf or massive primaries with a major or minor companion by stellar mass. 
+    (Top) Median pair fraction, defined as the fraction of dwarf or massive primaries with a major (left) or minor (right) companion by stellar mass (see Sec.~\ref{sec:methods-crit}). 
     Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
       % massive pairs
-    The fraction of massive primaries (pink) with a major (left) or minor (right) companion remains approximately constant for $z>1$, with an average pair fraction of 0.16-0.17 and 0.14-0.15 respectively.
-Between $z=0.25$ and $z=0$, the massive major pair fraction increases sharply from 0.165 to 0.207, a 25\% increase, while the minor pair fraction increases from 0.127 to 0.152, a 20\% increase.
+    The massive pair fraction (pink) remains approximately constant for $z>1$, with an average pair fraction of 0.16-0.17 for major pairs and 0.14-0.15 for minor pairs.
+Between $z=0.25$ and $z=0$, the massive major pair fraction increases to 0.207, while the minor pair fraction increases to 0.152.
       % dwarf pairs
-    Dwarf pairs (green), on the other hand, have pair fractions that are approximately constant from $z=3-4$, but the fraction of major(minor) pairs declines monotonically from 0.126(0.111) at x=3 to just 0.041(0.034) at x=0, a 67(70)\% decrease.
+    Dwarf pair fractions, shown in green, are approximately constant from $z=3-4$, then declines monotonically to $z=0$.
+The major pair fraction is $0.041$ at $z=0$ and $0.126$ at $z=3$, while the minor pair fractions are $0.034$ and $0.111$ at $z=0$ and $z=3$, respectively.
     % Bottom plots ~
-  (Bottom) The median subtracted difference between the massive pair fraction and the dwarf pair fraction, with the shaded $1$-$99$ percentile range of the difference of each realization.
-The difference between the massive pair fraction and dwarf pair fraction increases with decreasing redshift, peaking at $z=0$ with a difference of 0.166 for major pairs and 0.111 for minor pairs.
-This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly in the low redshift regime.\todo{remove "difference" label, explain in capt.
-what "diff" means}}
+    (Bottom) The median subtracted (massive - dwarf) pair fraction difference, with the shaded $1$-$99$ percentile range from 1000 abundance matching realizations.
+The pair fraction difference increases with decreasing redshift, peaking at $z=0$ with a difference of 0.166 for major pairs and 0.111 for minor pairs.
+This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly in the low redshift regime.}
   \label{fig:pairratio}
@@
 
+%%
+% Kinematics section
 \subsection{Kinematic evolution}\label{sec:results-kinematics}
-\kc{WIP}
 The primary and secondary halos of each pair at each individual snapshot/redshift is separated by some physical separation and has a relative velocity of
@@
 \kc{halo mass sets the scale of the typical separations of objects.}
-\kc{We leave the discussion on the implications of the evolution of median separations on pair selection criteria for sec.~\ref{sec:discussion}}
+
 \kc{This begs the question: what does this mean for selection criteria for pairs at different mass scales and at different redshifts?}
@@
 This is likely because close major pairs are more likely to merge more quickly than minor pairs, so you aren't left with many close major pairs since they have merged at higher z.}
-
-%% text on separation distribution plot
-Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$, and includes all 1000 AM realizations. 
-For reference, the median at each corresponding redshift from Fig.~\ref{fig:sep} (that is, the median of the medians of each realization) are shown in light black vertical lines.
-Each plot is normalized such that the area under an individual curve is 1.
-    % the redshift evolution
-All pair types (dwarf and massive, major and minor) have narrow distributions that pile up around 0 $\kpc$ at $z=4$, but the distributions become more and more broad as $z\to0$ (note that only pairs with separations $>10\kpc$ are included in this analysis, see Sec.~\ref{sec:methods-crit-pairs}).
-\linebreak
-The distribution profiles are similar when the scale of the x-axis for massive pair separations is twice that of the dwarf pairs. 
-Pair separations at $z=0$ tend to primarily fall between $10-\sim400\,\kpc$ for dwarf pairs and   between $10-\sim1000\,\kpc$ for massive pairs. 
-At $z=4$, these ranges decrease to $10-150\,\kpc$ for dwarf pairs and $10-300\,\kpc$ for massive pairs. 
-    % comparing major and minor
-Major and minor pairs (both dwarf pairs and massive pairs) have roughly equivalent distributions, though the distribution of minor pairs with low separations is slightly higher than the major pairs.
-Thus, secondary halo of minor pairs tend to live slightly closer to their primaries than the  major secondaries.
 
@@
 \kc{table? z=0,1,2,3,4 and pair frac, sep, vel. ?}
+
+The increase in low redshift median separations suggests that low separation pairs undergo mergers that remove them from the sample at later snapshots, thus increasing the median separation over time.
+Alternatively, it's just cause the halos are getting bigger. This is explored in Sec.~\ref{sec:results-scaled}.
+
+We leave the discussion of the implications of the evolution of median separations on pair selection criteria for Sec.~\ref{sec:discussion}.
 
@@
   Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs.
-\todo{remove "difference" legend, explain in capt.
-what "Maj-Min" means}
     }
@@
 
-\begin{figure*}[htp]
-  \centering
-  \includegraphics[width=\textwidth]{sepdist_1000.png}
-  \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right).
-Major pairs are shown as solid lines, while minor pairs are dotted.
-The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines.
-  At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively).
-However, at low redshift, the separation distribution tends to spread out more evenly across a large range of separations, thus increasing the median.
-    }
-  \label{fig:sep-dist}
-\end{figure*}
-
 \subsubsection{Relative Velocities}
 %% text on velocity vs. redshift plot
-We also consider the snapshot-by-snapshot instantaneous relative velocity between each primary and secondary.
+\kc{revisit this section } We also consider the snapshot-by-snapshot instantaneous relative velocity between each primary and secondary.
 We find that the median relative velocity of all pairs (dwarf and massive, major and minor) decreases with decreasing redshift, reaching a minimum at $z=0$ as seen in Fig.~\ref{fig:vel}. 
@@
 The offsets between the relative velocities of dwarf major and minor pairs is between $0-5\,\kms$, and between $0-25\,\kms$ for massive major and minor pairs.
-
-\kc{key takeaways}
-
-%% text on velocity distribution plot
-\kc{left off here\~}
-Fig.~\ref{fig:vel-dist}
 
@@
 
+%%%
+
+\subsection{Scaled Kinematics}\label{sec:results-scaled}
+% introduction to section
+For brevity we sshow results for the major dwarf and massive pairs. Minor pairs show the same trends
+
+%text on scaled kins evlution
+basically talk about how we find that the scaled versions of dwarfs and massives behave very similarly.
+so, the scaled versins of all of these pairs behave VERY similarly in sc.
+velocity space, a bit different in sc.
+separation space but still kinda the same.
+also, can talk about how at z>2.5, dwarf pairs tend to live ooutside of their host's virial mass which is wildin -> maybe not bound at high z, though could become bound by low z by mass accretion ?
+
+% text on scaled kins distributions 
+dwarf and massive distributioons look very similar, and also do not show a ton of evolution with redshift.
+for scaled separation, and velocity both, this is due to the growth of halos, so while the separation increases, the halo radius also increases.
+Since v inversely proportional to $R^1/2$, the increasing virial radius leads to lower circular velocitries given same mass, and thus, the higher separation pairs will allso have lower velocities.
+
+Scaled vel fig.
+--   Despite the difference between dwarf and massive pairs in physical distribution as indicated by the plot of scaled separations (Figure~\ref{fig:sep-scaled}), the scaled velocity distribution of pairs indicates that dwarf and massive galaxy pairs operate similarly in velocity space.
+There is little to no mass dependence on the scaled velocity of dwarf or massive pairs., and is thus independent of the mass scale , meaning dwarf and massive scaled velocities evolve is nearly identically for $z=0-4$.
+
+% scaled evolution plot
+\begin{figure*}[htp]
+  \centering
+  \includegraphics[width=\textwidth]{scaledcombo_1000.png}
+  \caption{
+  %  Left
+  (Left) Median scaled separation as a function of redshift (see Sec.~\ref{sec:methods} for the definitions of scaled separation and velocity).
+All shaded regions show $X-XX\%$ percentile spread from 1000 abundance matching realizations.
+    % any overall trends?
+  At $z>2$, a majority of all pair types have separations greater than the group virial radius, while at $z<2$, a majority of pairs have smaller separations.  
+  Massive major pairs at low redshift tend to have slight smaller scaled separations than dwarfs at $z<\sim2$, but vary significantly at higher redshifts. 
+  % Right 
+  (Right) Median scaled velocity as a function of redshift.
+    % any overall trends?
+  All pairs show a peak in scaled velocity at $z=0$.
+From $z=0-0.5$, a majority of both dwarf and massive pairs have relative velocities larger than the circular velocity of their group at the virial radius.
+At $z>0.5$, however, the majority of pairs have $v_{rel}<v_{vir}$.
+The scaled velocity evolves nearly identically for dwarf and massive pairs.
+  % Bottom 
+  (Bottom) The scaled separation/velocity of dwarf major pairs subtracted from that of massive major pairs, indicated by ``M-D".
+  The scaled separation difference shows minor differences between the dwarf and massive population, with dwarf pairs having slightly higher scaled separation for $z<1$.
+The scaled velocity difference is $\sim0$ at all redshifts.
+  Minor pairs (not shown here) follow the same trends as major pairs in both the massive and dwarf regime.
+    }
+  \label{fig:scaled}
+\end{figure*}
+
+% scaled distribution plot
+\begin{figure*}[htp]
+  \centering
+  \includegraphics[width=\textwidth]{scaledcombodist_1000.png}
+  \caption{Scaled separation distribution (left) and scaled velocity distribution (right) at $z=0,1,2,3$, and $4$, normalized by the total number of pairs at the corresponding redshift. 
+  % the point? what am I trying to get across
+  There is little difference between the distributions for dwarf (top) and massive (bottom) pairs. There is also relatively little redshift evolution in the spread of each individual panel. 
+  }
+  \label{fig:scaled-dist}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
+\label{sec:discussion}
+
+Mean separation fig. --
+
+Separation dist fig. -- The number of widely separated pairs at low redshift is much greater than at high redshift, so these pairs either form late, or move apart from each other.
+
+Also note than many of the close pairs at high z may merge by $z=0$.
+
+\subsection{Massive pairs vs. Dwarf pairs}
+Pair ratio fig.
+-- The vast difference between the dwarf and massive pair fractions suggests \todo{XX - that pairs at different mass scales evolve differently ?
+Thus, can't just assume a massive pair fraction for a lower mass regime}
+
+\subsection{Dwarf and massive pair kinematic differences}
+
+\subsection{Comparison to literature}
+
+\subsection{Implications for observations}
+
+\subsection{Implications for observational pair selection criteria}
+%% text on separation distribution plot
+Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$, and includes all 1000 AM realizations. 
+For reference, the median at each corresponding redshift from Fig.~\ref{fig:sep} (that is, the median of the medians of each realization) are shown in light black vertical lines.
+Each plot is normalized such that the area under an individual curve is 1.
+    % the redshift evolution
+All pair types (dwarf and massive, major and minor) have narrow distributions that pile up around 0 $\kpc$ at $z=4$, but the distributions become more and more broad as $z\to0$ (note that only pairs with separations $>10\kpc$ are included in this analysis, see Sec.~\ref{sec:methods-crit-pairs}).
+\linebreak
+The distribution profiles are similar when the scale of the x-axis for massive pair separations is twice that of the dwarf pairs. 
+Pair separations at $z=0$ tend to primarily fall between $10-\sim400\,\kpc$ for dwarf pairs and   between $10-\sim1000\,\kpc$ for massive pairs. 
+At $z=4$, these ranges decrease to $10-150\,\kpc$ for dwarf pairs and $10-300\,\kpc$ for massive pairs. 
+    % comparing major and minor
+Major and minor pairs (both dwarf pairs and massive pairs) have roughly equivalent distributions, though the distribution of minor pairs with low separations is slightly higher than the major pairs.
+Thus, secondary halo of minor pairs tend to live slightly closer to their primaries than the  major secondaries.
+
+\begin{figure*}[htp]
+  \centering
+  \includegraphics[width=\textwidth]{sepdist_1000.png}
+  \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right).
+Major pairs are shown as solid lines, while minor pairs are dotted.
+The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines.
+  At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively).
+However, at low redshift, the separation distribution tends to spread out more evenly across a large range of separations, thus increasing the median.
+    }
+  \label{fig:sep-dist}
+\end{figure*}
+
 \begin{figure*}[htp]
@@
 \end{figure*}
-%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-\label{sec:discussion}
-
-Pair ratio fig.
--- The vast difference between the dwarf and massive pair fractions suggests \todo{XX - that pairs at different mass scales evolve differently ?
-Thus, can't just assume a massive pair fraction for a lower mass regime}
-
-Mean separation fig.
--- The increase in low redshift median separations suggests that low separation pairs undergo mergers that remove them from the sample at later snapshots, thus increasing the median separation over time.
-
-Separation dist fig. -- The number of widely separated pairs at low redshift is much greater than at high redshift, so these pairs either form late, or move apart from each other.
-
-Scaled sep fig.
--- \textbf{The difference between the scaled separations of dwarf and massive pairs highlights the mass dependence of the physical distribution of halo pairs, i.e., dwarf pairs are not simply a smaller scale version of massive pairs.}
-
-Scaled vel fig.
---   \textbf{Despite the difference between dwarf and massive pairs in physical distribution as indicated by the plot of scaled separations (Figure~\ref{fig:sep-scaled}), the scaled velocity distribution of pairs indicates that dwarf and massive galaxy pairs operate similarly in velocity space.
-There is little to no mass dependence on the scaled velocity of dwarf or massive pairs.}
-Also note than many of the close pairs at high z may merge by $z=0$.
-
-\begin{figure*}[htp]
-  \centering
-  \includegraphics[width=\textwidth]{scaledcombo_1000.png}
-  \caption{Median scaled separation (separation of a pair divided by the virial radius of its group) as a function of redshift.
-Dwarf pairs (major (solid) and minor (dashed)) tend to have smaller scaled separations at lower redshifts, leveling out between $z=0-1$.
-In particular, the secondaries of dwarf major pairs at $z>2$ tend to live more than one virial radius away from the primary.
-Massive major pairs at low redshift tend to have smaller scaled separations  at $z<\sim2$, but vary significantly at higher redshifts.
-  Minor pairs (right), both dwarf and massive, tend to have smaller separations, tending to live closer than one virial radius between the primary and secondary.
-Massive minor pairs tend to have smaller scaled separations compared to dwarf pairs at all redshifts.
-  \todo{finish caption} \todo{remove "difference" legend, explain in capt. what "Ma-Dw" means}
-  Median scaled velocity (relative velocity of a pair divided by the virial velocity), defined as the circular velocity at the virial radius of the group as a function of redshift. 
-  Major pairs are on the left (solid lines), minor pairs are on the right in dashed lines.
-  All sets of pairs show an increase in scaled velocity at lower redshifts.
-  \todo{finish caption} \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
-    }
-  \label{fig:scaled}
-\end{figure*}
-
-\begin{figure*}[htp]
-  \centering
-  \includegraphics[width=\textwidth]{scaledcombodist_1000.png}
-  \caption{\todo{finish caption}}
-  \label{fig:scaled-dist}
-\end{figure*}
-
-\kc{add discussion subsection titles}
-\subsection{Dwarf and massive pair kinematic differences}
-\subsection{Comparison to literature}
-\subsection{Implications for observations}
-\subsection{Implications for observational pair selection criteria}
+%% text on velocity distribution plot
+\kc{left off here\~}
+Fig.~\ref{fig:vel-dist}
 
@@
     \item Median pair separations increase and relative velocities decrease from high to low redshift. 
-    \item Minor dwarf and massive pairs exhibit 
 \end{itemize}

### 2023-03-02 paper/pears.tex
revised sep caption and first half of sep text

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
- \section{Sample selection}\label{sec:methods}
+ \section{Methodology}\label{sec:methods}
+% \subsection{Simulation details}
+% \subsection{Choosing dwarf and massive halos in TNG}
+% \subsection{Abundance matching}
+% \subsection{Pair selection}
+%     \subsubsection{Selecting primaries}
+%     \subsubsection{Selecting companions}
+% \subsection{Overview of pair properties}
+%     \subsubsection{Description of counts plot}
+%     \subsubsection{Description of stellar mass ratio plot}
+% \subsection{Table}
+% Table should include the median number of primaries and of pairs (major and minor) at a variety of redshifts.
+
 % % methods plots
@@
 
-% %%%%%%%%%%%%%%%%%%%
-% %% dwarf figures %%
-% %%%%%%%%%%%%%%%%%%%
-% \kc{why did we stop at z=4? we didn't, explanation about low \# statistics }
+% % %%%%%%%%%%%%%%%%%%%
+% % %% dwarf figures %%
+% % %%%%%%%%%%%%%%%%%%%
+% % \kc{why did we stop at z=4? we didn't, explanation about low \# statistics }
 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%
+% %
 
@@
 \subsection{Pair fraction}\label{sec:results-frac}
-    % intro to pair frac plot
-The pair fraction is defined here as the fraction of identified dwarf or massive primaries with a major or minor companion (see Sec.~\ref{sec:methods-crit} for more info on selection criteria for major and minor pairs).
-Fig.~\ref{fig:pairratio} shows the pair fractions calculated for massive and dwarf pairs (including both major and minor pairs separately) as a function of time for $z=0-4$.
+%     % intro to pair frac plot
+% The pair fraction is defined here as the fraction of identified dwarf or massive primaries with a major or minor companion (see Sec.~\ref{sec:methods-crit} for more info on selection criteria for major and minor pairs).
+% Fig.~\ref{fig:pairratio} shows the pair fractions calculated for massive and dwarf pairs (including both major and minor pairs separately) as a function of time for $z=0-4$.
 
-    % differences between massive and dwarf pairs? 
-The dwarf pair fraction evolves distinctly from that of massive pairs.
-Both major and minor dwarf pair fractions start at their minima at $z=0$, and increase by about 200\% by $z\sim2-2.5$, at which point the pair fractions level off and remain constant from $z=3-4$. 
-The major and minor pair fractions for massive pairs evolve similarly, starting at their maxima at $z=0$, then abruptly declining to $z\sim0.25$, before remaining approximately constant from $z=1-4$ %(see Table~\ref{table:vals} for more precise values of the pair fractions).
+%     % differences between massive and dwarf pairs? 
+% The dwarf pair fraction evolves distinctly from that of massive pairs.
+% Both major and minor dwarf pair fractions start at their minima at $z=0$, and increase by about 200\% by $z\sim2-2.5$, at which point the pair fractions level off and remain constant from $z=3-4$. 
+% The major and minor pair fractions for massive pairs evolve similarly, starting at their maxima at $z=0$, then abruptly declining to $z\sim0.25$, before remaining approximately constant from $z=1-4$ %(see Table~\ref{table:vals} for more precise values of the pair fractions).
 
-    % difference panels
-The bottom panel of Fig.~\ref{fig:pairratio} shows the dwarf pair fraction subtracted from the massive pair fraction (labelled ``$\rm M-D$"). 
-The pair fraction difference reaches a maximum at $z=0$ for both major and minor pairs, and declines to $z\sim2-2.5$ at which point the difference levels out close to 0.
+%     % difference panels
+% The bottom panel of Fig.~\ref{fig:pairratio} shows the dwarf pair fraction subtracted from the massive pair fraction (labelled ``$\rm M-D$"). 
+% The pair fraction difference reaches a maximum at $z=0$ for both major and minor pairs, and declines to $z\sim2-2.5$ at which point the difference levels out close to 0.
 
-    % differences between major and minor pairs? 
-The median pair fraction for minor pairs (for both dwarf and massive galaxies) is less than that of major pairs of the same mass range at all redshifts.
+%     % differences between major and minor pairs? 
+% The median pair fraction for minor pairs (for both dwarf and massive galaxies) is less than that of major pairs of the same mass range at all redshifts.
 This is due to the lower stellar mass ratio limit we put on our pairs.
-Expanding the mass ratio criteria of our minor pair sample to include stellar mass ratios between 1/10-1/100 in our minor pair sample increases the fraction of minor pairs by a factor of $>2$ for massive pairs and between $~1.5-2x$ for dwarf pairs.
+% Expanding the mass ratio criteria of our minor pair sample to include stellar mass ratios between 1/10-1/100 in our minor pair sample increases the fraction of minor pairs by a factor of $>2$ for massive pairs and between $~1.5-2x$ for dwarf pairs.
 \kc{are there any additional takeaways from this?
@@
 
-    % what do we learn from this? what are the takeaways? where do we discuss this in more detail?
-Overall, these results show that massive and dwarf pair counts evolve differently, particularly at very low redshift despite the pair fractions being roughly equal at higher z.
-These differences could be a result of the different formation mechanisms at play in the evolution of the systems at two different mass scales, or alternatively, from differences in satellite dynamics between dwarf and massive systems (see Sec.~\ref{sec:results-kinematics}).
-The implications for the difference in the evolution of pair fractions for dwarf and massive pairs across time is discussed in detail in Sec.~\ref{sec:discussion}.
+%     % what do we learn from this? what are the takeaways? where do we discuss this in more detail?
+% Overall, these results show that massive and dwarf pair counts evolve differently, particularly at very low redshift despite the pair fractions being roughly equal at higher z. 
+% These differences could be a result of the different formation mechanisms at play in the evolution of the systems at these two different mass scales, or alternatively, from differences in satellite dynamics between dwarf and massive systems (see Sec.~\ref{sec:results-kinematics}).
+% The implications for the difference in the evolution of pair fractions for dwarf and massive pairs across time is discussed in detail in Sec.~\ref{sec:discussion}.
 
-    % pair fraction plot
-\label{sec:results}
-\begin{figure*}[htp]
-  \centering
-  \includegraphics[width=\textwidth]{pairfrac_1000.png}
-  \caption{
-    % Top plots ~
-    (Top) Median pair fraction, defined as the fraction of dwarf or massive primaries with a major (left) or minor (right) companion by stellar mass (see Sec.~\ref{sec:methods-crit}). 
-    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
-      % massive pairs
-    The massive pair fraction (pink) remains approximately constant for $z>1$, with an average pair fraction of 0.16-0.17 for major pairs and 0.14-0.15 for minor pairs.
+%     % pair fraction plot
+% \label{sec:results}
+% \begin{figure*}[htp]
+%   \centering
+%   \includegraphics[width=\textwidth]{pairfrac_1000.png}
+%   \caption{
+%     % Top plots ~
+%     (Top) Median pair fraction, defined as the fraction of dwarf or massive primaries with a major (left) or minor (right) companion by stellar mass (see Sec.~\ref{sec:methods-crit}). 
+%     Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
+%       % massive pairs
+%     The massive pair fraction (pink) remains approximately constant for $z>1$, with an average pair fraction of 0.16-0.17 for major pairs and 0.14-0.15 for minor pairs.
 Between $z=0.25$ and $z=0$, the massive major pair fraction increases to 0.207, while the minor pair fraction increases to 0.152.
-      % dwarf pairs
-    Dwarf pair fractions, shown in green, are approximately constant from $z=3-4$, then declines monotonically to $z=0$.
+%       % dwarf pairs
+%     Dwarf pair fractions, shown in green, are approximately constant from $z=3-4$, then declines monotonically to $z=0$.
 The major pair fraction is $0.041$ at $z=0$ and $0.126$ at $z=3$, while the minor pair fractions are $0.034$ and $0.111$ at $z=0$ and $z=3$, respectively.
-    % Bottom plots ~
-    (Bottom) The median subtracted (massive - dwarf) pair fraction difference, with the shaded $1$-$99$ percentile range from 1000 abundance matching realizations.
+%     % Bottom plots ~
+%     (Bottom) The median subtracted (massive - dwarf) pair fraction difference, with the shaded $1$-$99$ percentile range from 1000 abundance matching realizations.
 The pair fraction difference increases with decreasing redshift, peaking at $z=0$ with a difference of 0.166 for major pairs and 0.111 for minor pairs.
 This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly in the low redshift regime.}
-  \label{fig:pairratio}
-\end{figure*}
+%   \label{fig:pairratio}
+% \end{figure*}
 
@@
     %% text on separation vs. redshift plot
-The median separations of dwarf pairs and massive pairs smoothly increases with lower redshift, regardless of pair type. 
-Fig.~\ref{fig:sep} shows the median and 1-99\% range of separations for dwarf pairs and massive pairs, as well as the subtracted difference between the median separation of major pairs and of minor pairs of both mass type.
-There is a small offset in the median separations of major and minor dwarf pairs (between $10-25\,\kpc$ from  $z=0-1$ and approximately $5\,\kpc$ from $z=1-4$), and a larger median separation offset for major and minor massive pairs (between $25-100\,\kpc$ from  $z=0-1$ and approximately $10-40\,\kpc$ from $z=1-4$).
+We calculate the median relative separations between the primary and secondary halos of the pairs identified in our dwarf pair sample and massive pair sample. 
+We split the results by the stellar mass ratio of each pair, dividing the sample into "major" pairs and minor pairs, which allows us to compare the behavior of different mass ratio systems individually in the dwarf and massive mass range (see details for pair collecting in Sec.~\ref{deets}).
+Our results are collected in Fig.~\ref{fig:sep}, which shows the redshift evolution of the median relative separations for dwarf pairs and massive pairs.
+
+We show that the median relative separations between the primary and secondary of both dwarf and massive pairs increases with decreasing redshift, regardless of pair type. 
+A combination of physical mechanisms is likely spurring the increase in median pair separations at low $z$. 
+For example, high $z$, low separation pairs may undergo mergers at earlier times, removing them from the sample at later snapshots, thus increasing the median separation over time. 
+Alternatively, mass accretion, from the cosmic web and/or from mergers, causes dark matter halos to become both more massive and more extended as $z\to0$. 
+Thus, the growth of structure that is expected in $\Lambda$CDM could naturally lead to an increase in typical pair separations at low $z$.
+We explore the connection between halo extent and relative pair separations in Sec.~\ref{sec:results-scaled}.
+
+Dwarf pairs and massive pairs have a relative separation difference of $\sim150\kpc$ at $z=0$, and a difference of $\sim40$ at $z=4$.   
+\kc{halo mass sets the scale of the typical separations of objects.}
+Since there is such a large difference between typical pair seps at high and low z, this may lead to unintended selection bias when identifying observation pairs as a result of redshift-independent separation criteria.
 Thus, apart from the overall scale of the separations between primary and secondary, dwarf and massive pairs exhibit similar trends as a function of time.
 
-\kc{key takeaways}
-\kc{what do I want to say about this figure?
-This makes sense because as the universe evolves, structures become bigger and you start increasing the material accreted in the outer regions of the halo, so it not surprising to see an increasing median separation towards lower redshifts.
-}
-\kc{halo mass sets the scale of the typical separations of objects.}
+This begs the question: what does this mean for selection criteria for pairs at different mass scales and at different redshifts?
+We leave the discussion of the implications of the evolution of median separations on pair selection criteria for Sec.~\ref{sec:discussion}.
 
-\kc{This begs the question: what does this mean for selection criteria for pairs at different mass scales and at different redshifts?}
-\kc{The general trend for pairs of all mass types is for higher seps at lower z.
-Also, minor pairs tend to live at closer separations than their major counterparts.
-This is likely because close major pairs are more likely to merge more quickly than minor pairs, so you aren't left with many close major pairs since they have merged at higher z.}
-
-\kc{ to $z=1$, where median separations are $171(124)\,\kpc$}
-
-\kc{ ,. The median separation rises more steeply from z=1 to z=0, peaking around $z=\sim0$ at $288\,\kpc$ and $205\,\kpc$ for major and minor massive pairs respectively.}
-
-\kc{table? z=0,1,2,3,4 and pair frac, sep, vel. ?}
-
-The increase in low redshift median separations suggests that low separation pairs undergo mergers that remove them from the sample at later snapshots, thus increasing the median separation over time.
-Alternatively, it's just cause the halos are getting bigger. This is explored in Sec.~\ref{sec:results-scaled}.
-
-We leave the discussion of the implications of the evolution of median separations on pair selection criteria for Sec.~\ref{sec:discussion}.
+In addition, Fig.~\ref{fig:sep} shows the median subtracted difference between the relative separations calculated for major pairs and minor pairs of both mass type. 
+There is a small offset in the median separations of major and minor dwarf pairs (between $10-25\,\kpc$ from  $z=0-1$ and approximately $5\,\kpc$ from $z=1-4$), and a larger median separation offset for major and minor massive pairs (between $25-100\,\kpc$ from  $z=0-1$ and approximately $10-40\,\kpc$ from $z=1-4$).
+The major-minor offset is likely a result of more major pairs merging more quickly (thus at earlier times and higher $z$) due to the increased impact of dynamical friction, thus leading to a population of low relative separation minor pairs that have yet to merge.
 
@@
   \includegraphics[width=\textwidth]{sep_1000.png}
-  \caption{(Top) Median physical separation (in kpc) of dwarf pairs (left, green) and massive pairs (right, pink) as a function of redshift. 
-  Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
-  Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
-  In general, as the redshift decreases from $z=4$ to $z=0$, the average physical separation of a pair increases for both dwarf and massive pairs. 
+  \caption{(Top) Median physical separation in kpc between the primary and secondary halos of dwarf pairs (left) and massive pairs (right) as a function of redshift. 
+  Shaded areas show the 1-99\% percentile range of the median from 1000 abundance matching realizations. 
+  Major pairs are shown in solid lines, and minor pairs are depicted with dashed lines.
+  In general, for both dwarf pairs and massive pairs, the average physical separation of the two halos in a pair increases for as the redshift decreases from $z=4\to0$. 
   % Dwarf pairs
@@
   % Massive Pairs
-  The separation between major (minor) massive pairs, on the other hand, increases from $81(71)\,\kpc$ at $z=4$ to $288(205)\,\kpc$ at  $z=0$.
+  The separation between major (minor) massive pairs likewise increases from $81(71)\,\kpc$ at $z=4$ to $288(205)\,\kpc$ at  $z=0$.
   % Difference plots
-  (Bottom) The median difference and 1-99\% range of the difference between major and minor pairs from 1000.
-  Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs.
+  (Bottom) The median difference and 1-99\% range (as above) between the median separation of major pairs and minor pairs.
+  At dwarf mass scales, minor companions tend to be $\sim10-20\kpc$ closer to their primary than major companions, while minor massive pairs have a relative separation that is $10-50\kpc$ less than major pairs.
     }
@@
   % the point? what am I trying to get across
-  There is little difference between the distributions for dwarf (top) and massive (bottom) pairs. There is also relatively little redshift evolution in the spread of each individual panel. 
+  The first thing to note is that there is relatively little redshift-dependent change in the overall shape and extent of each distribution, and thus the scaled quantities are only loosely independent of redshift.
+  Additionally, the shape and extent of the dwarf pair (top) and the massive pair (bottom) distributions are nearly identical, thus the scaled quantities are also independent of the halo mass scale.
+Thus, the kinematics of dwarf pairs and massive pairs evolve roughly equivalently when normalizing by the halo mass.
+  Unscaled versions of this plot are discussed in Sec.~\ref{sec:discussion}.
   }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-\label{sec:discussion}
+\section{Discussion}\label{sec:discussion}
 
-Mean separation fig. --
+% Mean separation fig. --
 
-Separation dist fig. -- The number of widely separated pairs at low redshift is much greater than at high redshift, so these pairs either form late, or move apart from each other.
+% Separation dist fig. -- The number of widely separated pairs at low redshift is much greater than at high redshift, so these pairs either form late, or move apart from each other.
 
-Also note than many of the close pairs at high z may merge by $z=0$.
+% Also note than many of the close pairs at high z may merge by $z=0$.
 
-\subsection{Massive pairs vs. Dwarf pairs}
-Pair ratio fig.
+% \subsection{Massive pairs vs. Dwarf pairs}
+% Pair ratio fig.
 -- The vast difference between the dwarf and massive pair fractions suggests \todo{XX - that pairs at different mass scales evolve differently ?
@@
 
-\subsection{Dwarf and massive pair kinematic differences}
+% \subsection{Dwarf and massive pair kinematic differences}
 
-\subsection{Comparison to literature}
+% \subsection{Comparison to literature}
 
-\subsection{Implications for observations}
+% \subsection{Implications for observations}
 
-\subsection{Implications for observational pair selection criteria}
-%% text on separation distribution plot
-Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$, and includes all 1000 AM realizations. 
-For reference, the median at each corresponding redshift from Fig.~\ref{fig:sep} (that is, the median of the medians of each realization) are shown in light black vertical lines.
-Each plot is normalized such that the area under an individual curve is 1.
-    % the redshift evolution
-All pair types (dwarf and massive, major and minor) have narrow distributions that pile up around 0 $\kpc$ at $z=4$, but the distributions become more and more broad as $z\to0$ (note that only pairs with separations $>10\kpc$ are included in this analysis, see Sec.~\ref{sec:methods-crit-pairs}).
-\linebreak
-The distribution profiles are similar when the scale of the x-axis for massive pair separations is twice that of the dwarf pairs. 
-Pair separations at $z=0$ tend to primarily fall between $10-\sim400\,\kpc$ for dwarf pairs and   between $10-\sim1000\,\kpc$ for massive pairs. 
-At $z=4$, these ranges decrease to $10-150\,\kpc$ for dwarf pairs and $10-300\,\kpc$ for massive pairs. 
-    % comparing major and minor
-Major and minor pairs (both dwarf pairs and massive pairs) have roughly equivalent distributions, though the distribution of minor pairs with low separations is slightly higher than the major pairs.
+% \subsection{Implications for observational pair selection criteria}
+% %% text on separation distribution plot
+% Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$, and includes all 1000 AM realizations. 
+% For reference, the median at each corresponding redshift from Fig.~\ref{fig:sep} (that is, the median of the medians of each realization) are shown in light black vertical lines.
+% Each plot is normalized such that the area under an individual curve is 1.
+%     % the redshift evolution
+% All pair types (dwarf and massive, major and minor) have narrow distributions that pile up around 0 $\kpc$ at $z=4$, but the distributions become more and more broad as $z\to0$ (note that only pairs with separations $>10\kpc$ are included in this analysis, see Sec.~\ref{sec:methods-crit-pairs}).
+% \linebreak
+% The distribution profiles are similar when the scale of the x-axis for massive pair separations is twice that of the dwarf pairs. 
+% Pair separations at $z=0$ tend to primarily fall between $10-\sim400\,\kpc$ for dwarf pairs and   between $10-\sim1000\,\kpc$ for massive pairs. 
+% At $z=4$, these ranges decrease to $10-150\,\kpc$ for dwarf pairs and $10-300\,\kpc$ for massive pairs. 
+%     % comparing major and minor
+% Major and minor pairs (both dwarf pairs and massive pairs) have roughly equivalent distributions, though the distribution of minor pairs with low separations is slightly higher than the major pairs.
 Thus, secondary halo of minor pairs tend to live slightly closer to their primaries than the  major secondaries.
 
-\begin{figure*}[htp]
-  \centering
-  \includegraphics[width=\textwidth]{sepdist_1000.png}
-  \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right).
+% \begin{figure*}[htp]
+%   \centering
+%   \includegraphics[width=\textwidth]{sepdist_1000.png}
+%   \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right).
 Major pairs are shown as solid lines, while minor pairs are dotted.
 The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines.
-  At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively).
+%   At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively).
 However, at low redshift, the separation distribution tends to spread out more evenly across a large range of separations, thus increasing the median.
-    }
-  \label{fig:sep-dist}
-\end{figure*}
+%     }
+%   \label{fig:sep-dist}
+% \end{figure*}
 
-\begin{figure*}[htp]
-  \centering
-  \includegraphics[width=\textwidth]{veldist_1000.png}
-  \caption{
-  Normalized distribution of relative velocities between primary and secondary halos for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right).
+% \begin{figure*}[htp]
+%   \centering
+%   \includegraphics[width=\textwidth]{veldist_1000.png}
+%   \caption{
+%   Normalized distribution of relative velocities between primary and secondary halos for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right).
 Major pairs are shown as solid lines, while minor pairs are dotted.
 The median relative velocity of each pair type from Fig.~\ref{fig:vel} is shown in solid (major) and dotted (minor) vertical black lines.
-  %
-  The distribution of relative velocities for dwarf and massive pairs move to slightly lower velocities at lower redshifts. 
-  At $z=0$, typical dwarf pair relative velocities are $0-200\,\kms$, while at $z=4$ they are $0-300\,\kms$. 
-  Massive pairs typically have relative velocities between $0-300\,\kms$ at z=0 and $0-400\,\kms$ at $z=4$.
-  The distribution of velocities for major and minor pairs is roughly equivalent within each mass range. 
-    }
-  \label{fig:vel-dist}
-\end{figure*}
+%   %
+%   The distribution of relative velocities for dwarf and massive pairs move to slightly lower velocities at lower redshifts. 
+%   At $z=0$, typical dwarf pair relative velocities are $0-200\,\kms$, while at $z=4$ they are $0-300\,\kms$. 
+%   Massive pairs typically have relative velocities between $0-300\,\kms$ at z=0 and $0-400\,\kms$ at $z=4$.
+%   The distribution of velocities for major and minor pairs is roughly equivalent within each mass range. 
+%     }
+%   \label{fig:vel-dist}
+% \end{figure*}
 
-%% text on velocity distribution plot
-\kc{left off here\~}
-Fig.~\ref{fig:vel-dist}
+% %% text on velocity distribution plot
+% \kc{left off here\~}
+% Fig.~\ref{fig:vel-dist}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary and Conclusions}
-\label{sec:summary}
-Findings:
-\begin{itemize}
-    \item Pair fraction for dwarfs and massives does not proceed identically throughout cosmic time. Opposite behavior at low z. 
-    \item Median pair separations increase and relative velocities decrease from high to low redshift. 
-\end{itemize}
+\section{Summary and Conclusions}\label{sec:summary}
+% Findings:
+% \begin{itemize}
+%     \item Pair fraction for dwarfs and massives does not proceed identically throughout cosmic time. Opposite behavior at low z. 
+%     \item Median pair separations increase and relative velocities decrease from high to low redshift. 
+% \end{itemize}
 

### 2023-03-02 paper/pears.tex
revised separations and velocity text + caps

@@
 
-% % %%%%%%%%%%%%%%%%%%%
-% % %% dwarf figures %%
-% % %%%%%%%%%%%%%%%%%%%
-% % \kc{why did we stop at z=4? we didn't, explanation about low \# statistics }
-
 % % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % %
-
 \section{Results}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%
+% Pair fraction section %
 \subsection{Pair fraction}\label{sec:results-frac}
-%     % intro to pair frac plot
-% The pair fraction is defined here as the fraction of identified dwarf or massive primaries with a major or minor companion (see Sec.~\ref{sec:methods-crit} for more info on selection criteria for major and minor pairs).
-% Fig.~\ref{fig:pairratio} shows the pair fractions calculated for massive and dwarf pairs (including both major and minor pairs separately) as a function of time for $z=0-4$.
+    % intro to pair frac plot
+The pair fraction is defined here as the fraction of identified dwarf or massive primaries with a major or minor companion (see Sec.~\ref{sec:methods-crit} for more info on selection criteria for major and minor pairs).
+Fig.~\ref{fig:pairratio} shows the pair fractions calculated for massive and dwarf pairs (including both major and minor pairs separately) as a function of time for $z=0-4$.
 
-%     % differences between massive and dwarf pairs? 
-% The dwarf pair fraction evolves distinctly from that of massive pairs.
-% Both major and minor dwarf pair fractions start at their minima at $z=0$, and increase by about 200\% by $z\sim2-2.5$, at which point the pair fractions level off and remain constant from $z=3-4$. 
-% The major and minor pair fractions for massive pairs evolve similarly, starting at their maxima at $z=0$, then abruptly declining to $z\sim0.25$, before remaining approximately constant from $z=1-4$ %(see Table~\ref{table:vals} for more precise values of the pair fractions).
+    % differences between massive and dwarf pairs? 
+The dwarf pair fraction evolves distinctly from that of massive pairs.
+Both major and minor dwarf pair fractions start at their minima at $z=0$, and increase by about 200\% by $z\sim2-2.5$, at which point the pair fractions level off and remain constant from $z=3-4$. 
+The major and minor pair fractions for massive pairs evolve similarly, starting at their maxima at $z=0$, then abruptly declining to $z\sim0.25$, before remaining approximately constant from $z=1-4$ %(see Table~\ref{table:vals} for more precise values of the pair fractions).
 
-%     % difference panels
-% The bottom panel of Fig.~\ref{fig:pairratio} shows the dwarf pair fraction subtracted from the massive pair fraction (labelled ``$\rm M-D$"). 
-% The pair fraction difference reaches a maximum at $z=0$ for both major and minor pairs, and declines to $z\sim2-2.5$ at which point the difference levels out close to 0.
+    % difference panels
+The bottom panel of Fig.~\ref{fig:pairratio} shows the dwarf pair fraction subtracted from the massive pair fraction (labelled ``$\rm M-D$"). 
+The pair fraction difference reaches a maximum at $z=0$ for both major and minor pairs, and declines to $z\sim2-2.5$ at which point the difference levels out close to 0.
 
-%     % differences between major and minor pairs? 
-% The median pair fraction for minor pairs (for both dwarf and massive galaxies) is less than that of major pairs of the same mass range at all redshifts.
+    % differences between major and minor pairs? 
+The median pair fraction for minor pairs (for both dwarf and massive galaxies) is less than that of major pairs of the same mass range at all redshifts.
 This is due to the lower stellar mass ratio limit we put on our pairs.
-% Expanding the mass ratio criteria of our minor pair sample to include stellar mass ratios between 1/10-1/100 in our minor pair sample increases the fraction of minor pairs by a factor of $>2$ for massive pairs and between $~1.5-2x$ for dwarf pairs.
+Expanding the mass ratio criteria of our minor pair sample to include stellar mass ratios between 1/10-1/100 in our minor pair sample increases the fraction of minor pairs by a factor of $>2$ for massive pairs and between $~1.5-2x$ for dwarf pairs.
 \kc{are there any additional takeaways from this?
@@
 
-%     % what do we learn from this? what are the takeaways? where do we discuss this in more detail?
-% Overall, these results show that massive and dwarf pair counts evolve differently, particularly at very low redshift despite the pair fractions being roughly equal at higher z. 
-% These differences could be a result of the different formation mechanisms at play in the evolution of the systems at these two different mass scales, or alternatively, from differences in satellite dynamics between dwarf and massive systems (see Sec.~\ref{sec:results-kinematics}).
-% The implications for the difference in the evolution of pair fractions for dwarf and massive pairs across time is discussed in detail in Sec.~\ref{sec:discussion}.
+    % what do we learn from this? what are the takeaways? where do we discuss this in more detail?
+Overall, these results show that massive and dwarf pair counts evolve differently, particularly at very low redshift despite the pair fractions being roughly equal at higher z. 
+These differences could be a result of the different formation mechanisms at play in the evolution of the systems at these two different mass scales, or alternatively, from differences in satellite dynamics between dwarf and massive systems (see Sec.~\ref{sec:results-kinematics}).
+The implications for the difference in the evolution of pair fractions for dwarf and massive pairs across time is discussed in detail in Sec.~\ref{sec:discussion}.
 
-%     % pair fraction plot
-% \label{sec:results}
-% \begin{figure*}[htp]
-%   \centering
-%   \includegraphics[width=\textwidth]{pairfrac_1000.png}
-%   \caption{
-%     % Top plots ~
-%     (Top) Median pair fraction, defined as the fraction of dwarf or massive primaries with a major (left) or minor (right) companion by stellar mass (see Sec.~\ref{sec:methods-crit}). 
-%     Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
-%       % massive pairs
-%     The massive pair fraction (pink) remains approximately constant for $z>1$, with an average pair fraction of 0.16-0.17 for major pairs and 0.14-0.15 for minor pairs.
+    % pair fraction plot
+\label{sec:results}
+\begin{figure*}[htp]
+  \centering
+  \includegraphics[width=\textwidth]{pairfrac_1000.png}
+  \caption{
+    % Top plots ~
+    (Top) Median pair fraction, defined as the fraction of dwarf or massive primaries with a major (left) or minor (right) companion by stellar mass (see Sec.~\ref{sec:methods-crit}). 
+    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
+      % massive pairs
+    The massive pair fraction (pink) remains approximately constant for $z>1$, with an average pair fraction of 0.16-0.17 for major pairs and 0.14-0.15 for minor pairs.
 Between $z=0.25$ and $z=0$, the massive major pair fraction increases to 0.207, while the minor pair fraction increases to 0.152.
-%       % dwarf pairs
-%     Dwarf pair fractions, shown in green, are approximately constant from $z=3-4$, then declines monotonically to $z=0$.
+      % dwarf pairs
+    Dwarf pair fractions, shown in green, are approximately constant from $z=3-4$, then declines monotonically to $z=0$.
 The major pair fraction is $0.041$ at $z=0$ and $0.126$ at $z=3$, while the minor pair fractions are $0.034$ and $0.111$ at $z=0$ and $z=3$, respectively.
-%     % Bottom plots ~
-%     (Bottom) The median subtracted (massive - dwarf) pair fraction difference, with the shaded $1$-$99$ percentile range from 1000 abundance matching realizations.
+    % Bottom plots ~
+    (Bottom) The median subtracted (massive - dwarf) pair fraction difference, with the shaded $1$-$99$ percentile range from 1000 abundance matching realizations.
 The pair fraction difference increases with decreasing redshift, peaking at $z=0$ with a difference of 0.166 for major pairs and 0.111 for minor pairs.
 This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly in the low redshift regime.}
-%   \label{fig:pairratio}
-% \end{figure*}
+  \label{fig:pairratio}
+\end{figure*}
+% end pair fraction 
+%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%
-% Kinematics section
+%%%%%%%%%%%%%%%%%%%%%%
+% Kinematics section %
 \subsection{Kinematic evolution}\label{sec:results-kinematics}
-The primary and secondary halos of each pair at each individual snapshot/redshift is separated by some physical separation and has a relative velocity of
+At each individual snapshot, we find the instantaneous separation and relative velocity of the primary and secondary halo of every pair that was selected in the snapshot. 
+This is done separately for all 1000 different abundance matching realizations at each snapshot, as described in Sec.~\ref{sec:methods-am}, then we explore the properties of the set of median separations and velocities for each realization.
+In this section, we compute the median relative separations and velocities of all 1000 realizations of dwarf and massive pairs, and show their behavior as a function of redshift.
+We separate the population of pairs into "major" and "minor" pairs (as defined in Sec.~\ref{sec:methods-crit-pairs}) to show how the stellar mass ratio between the primary and secondary may affect the kinematics.
 
-We separate the population of dwarf and massive pairs into "major" and "minor" pairs (as defined in Sec.~\ref{sec:methods-crit-pairs}) to show how the stellar mass ratio between the primary and secondary may affect the kinematics.
-
-At each individual snapshot, we find the instantaneous median separation and relative velocity of every pair that was selected in that snapshot.
-
+% separations %
     \subsubsection{Separations}
     %% text on separation vs. redshift plot
+    %% intro to separations & bulk results
     We calculate the median relative separations between the primary and secondary halos of the pairs identified in our dwarf pair sample and massive pair sample. 
@@
 
+    %% the behavior of massive and dwarf pairs
     We show that the median relative separations between the primary and secondary of both dwarf and massive pairs increases with decreasing redshift, regardless of pair type. 
@@
     Thus, the growth of structure that is expected in $\Lambda$CDM could naturally lead to an increase in typical pair separations at low $z$.
-We explore the connection between halo extent and relative pair separations in Sec.~\ref{sec:results-scaled}.
+    We explore the relationship between halo growth and relative pair separations in Sec.~\ref{sec:results-scaled}.
 
+    %% the DIFFERENCE between dwarf and massive pairs
+    Dwarf and massive pairs exhibit similar relative separation trends as a function of time, however, the scale of the typical relative separations of pairs in our sample is set by the mass halo of the primary.
     Dwarf pairs and massive pairs have a relative separation difference of $\sim150\kpc$ at $z=0$, and a difference of $\sim40$ at $z=4$.   
-\kc{halo mass sets the scale of the typical separations of objects.}
-Since there is such a large difference between typical pair seps at high and low z, this may lead to unintended selection bias when identifying observation pairs as a result of redshift-independent separation criteria.
-Thus, apart from the overall scale of the separations between primary and secondary, dwarf and massive pairs exhibit similar trends as a function of time.
+    This is expected, as more massive halos have larger spheres of influence and more substructure. 
+    \kc{maybe move this sentence to discussion:}But, the difference between dwarf and massive pair relative separation ranges, and their evolution over time begs the question: what does this mean for observational pair selection criteria at different mass scales and at different redshifts?
+    We leave the discussion of the implications our relative separation results on pair selection criteria for Sec.~\ref{sec:discussion}.
 
-This begs the question: what does this mean for selection criteria for pairs at different mass scales and at different redshifts?
-We leave the discussion of the implications of the evolution of median separations on pair selection criteria for Sec.~\ref{sec:discussion}.
-
+    %% the difference between major and minor pairs
     In addition, Fig.~\ref{fig:sep} shows the median subtracted difference between the relative separations calculated for major pairs and minor pairs of both mass type. 
     There is a small offset in the median separations of major and minor dwarf pairs (between $10-25\,\kpc$ from  $z=0-1$ and approximately $5\,\kpc$ from $z=1-4$), and a larger median separation offset for major and minor massive pairs (between $25-100\,\kpc$ from  $z=0-1$ and approximately $10-40\,\kpc$ from $z=1-4$).
-The major-minor offset is likely a result of more major pairs merging more quickly (thus at earlier times and higher $z$) due to the increased impact of dynamical friction, thus leading to a population of low relative separation minor pairs that have yet to merge.
+    The major-minor offset is likely a result of more major pairs merging more quickly (thus at earlier times and higher $z$) due to the increased effect of dynamical friction, thus leading to a population of low relative separation minor pairs that have yet to merge.
 
@@
 
+% velocities %
     \subsubsection{Relative Velocities}
     %% text on velocity vs. redshift plot
-\kc{revisit this section } We also consider the snapshot-by-snapshot instantaneous relative velocity between each primary and secondary.
-We find that the median relative velocity of all pairs (dwarf and massive, major and minor) decreases with decreasing redshift, reaching a minimum at $z=0$ as seen in Fig.~\ref{fig:vel}. 
-Though the velocity scales are different, the bulk behavior of dwarf pairs and massive pairs is identical. 
-\linebreak
-The median velocity of a major dwarf pair decreases approximately linearly from $130$ at $z=4$ to $70\,\kms$ at $z=0$.
-Likewise, the median velocity for major massive pairs decreases from $260$ at $z=4$ to $170\,\kms$ at $z=0$, albeit less smoothly.
+    %% intro to velocity & bulk results
+    In addition to the separations between the primary and secondary halos of our pair sample, we also calculate the median relative velocity between the halos of each pair.
+    Once again we split the results into "major" and "minor" pairs for both the dwarf and massive pair sample to get a better understanding of the impact of the mass of the secondary. 
+    In Fig.~\ref{fig:vel}, we show the median relative velocity between the primary and secondary halos of dwarf and massive pairs as a function of redshift. 
+    Note that these relative velocities are calculated from the instantaneous velocity of the halos at the snapshot the pair is in (see Sec.~\ref{sec:methods} for more details about our velocity calculations).
+
+    %% the behavior of massive and dwarf pairs
+    We find that the median relative velocity between a pair's primary and secondary halo decreases towards lower redshift, regardless of pair type.
+    The median velocity of a major dwarf pair decreases linearly from $130$ at $z=4$ to $70\,\kms$ at $z=0$.
+Likewise, the median velocity for major massive pairs decreases from $260$ at $z=4$ to $170\,\kms$ at $z=0$, though with more spread at high $z$.
+    As the circular velocity of a secondary object about the primary is inversely proportional to the radius, it is not surprising to find a decrease in the relative velocity for pairs at lower redshift due to the expansion of the universe/decrease in concentration/increase in the virial radius of the halo as $z\to0$.
+\kc{citation needed}
+    See Sec.~\ref{sec:results-scaled} for more details.
+
+    %% the DIFFERENCE between dwarf and massive pairs
+    As in the case of relative separations of pairs, dwarf and massive pairs show a similar evolutionary trend in relative velocity as a function of redshift, though at different scales determined by the mass of the primary.
+    Massive pairs have a median relative velocity $\sim100\kms$ larger than dwarf pairs at $z=0$, and $\sim140\kms$ at $z=4$. \kc{see comment}
+    %This is also not particularly surprising, since the circular velocity prop to $( M/r)^1/2,$, and massive primaries may be >10x as massive as dwarf primaries, while the separation between a massive primary and it's secondary will only be 2x further than a dwarf pair.
+
+    %% the difference between major and minor pairs
     Fig.~\ref{fig:vel} also includes a panel showing the subtracted median difference at each snapshot of the minor pair from the major pair.
-Since minor pairs typically have slightly higher velocities than their major pair counterparts, this difference is usually $<\sim0$.
+Unlike the relative separation, the relative velocities do not have a strong dependence on the secondary mass.
+    Since minor pairs typically have slightly higher velocities than their major pair counterparts, this difference is usually $<0$.
 The offsets between the relative velocities of dwarf major and minor pairs is between $0-5\,\kms$, and between $0-25\,\kms$ for massive major and minor pairs.
+\kc{see comment} %does it make sense that minor pairs are faster?
 
@@
       \caption{
-    (Top) Median relative velocity (in \kms) between the primary and secondary halos of: dwarf pairs (left, green), and massive pairs (right, pink) as a function of redshift. 
+        (Top) Median relative velocity (in \kms) between the primary and secondary halos of dwarf pairs (left) and massive pairs (right) as a function of redshift. 
         Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
-Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
-    The overall behavior of the redshift evolution is nearly identical for dwarf and massive pairs.
-    As the redshift decreases from $z=4$ to $z=0$, the average relative velocity of a pair decreases as well for both dwarf and massive pairs.
+        The overall behavior of the redshift evolution of pair relative velocities is nearly identical for dwarf and massive pairs.
+        As the redshift decreases from $z=4$ to $z=0$, the average relative velocity of a pair decreases for both dwarf and massive pairs.
         % brief describe
-    The median relative velocity of a dwarf pair (major or minor) is $70\,\kms$ at $z=0$ and $133\,\kms$ at $z=4$, and of a massive pair is $170\,\kms$ at $z=0$ and $260\,\kms$ at $z=4$ ($295\,\kms$ for a minor pair).
+        The median relative velocity of a dwarf pair (major or minor) is $70\,\kms$ at $z=0$ and $133\,\kms$ at $z=4$, and of a massive pair is $170\,\kms$ at $z=0$ and $260\,\kms$ at $z=4$ ($295\,\kms$ for a minor pair at $z=4$).
         % Difference plot
-    (Bottom) The median subtracted relative velocity difference between major and minor pairs, and 1-99\% shaded region.
-    The is little difference between major and minor dwarf pairs (bottom left), with minor pairs having a relative velocity of $0-5\,\kms$ higher than major pairs. 
-    Major and minor massive pairs also have very little median velocity difference at low redshift (bottom right), with minor pairs having a relative velocity between $1-20\,\kms$ faster than major pairs.
-    \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
+        (Bottom) The median relative velocity difference between major and minor pairs ("Maj - Min"), and 1-99\% shaded region.
+        There is little difference between the relative velocity of major and minor dwarf pairs (bottom left), with minor pairs having a relative velocity of $0-5\,\kms$ higher than major pairs. 
+        Massive pair types (bottom right) also have little velocity difference at low redshift, although minor pairs have a relative velocity between $1-20\,\kms$ faster than major pairs at higher redshift ($z>\sim 2.5$).
         }
@@
 
-%%%
+% scaled results %
+    \subsection{Scaled Kinematics}\label{sec:results-scaled}
+    %% introduction to section
+    For brevity we show results for the major dwarf and massive pairs. Minor pairs show the same trends
 
-\subsection{Scaled Kinematics}\label{sec:results-scaled}
-% introduction to section
-For brevity we sshow results for the major dwarf and massive pairs. Minor pairs show the same trends
-
-%text on scaled kins evlution
+    %% text on scaled kins evlution
     basically talk about how we find that the scaled versions of dwarfs and massives behave very similarly.
@@
 
-% text on scaled kins distributions 
+    %% text on scaled kins distributions 
     dwarf and massive distributioons look very similar, and also do not show a ton of evolution with redshift.
@@
 
-% scaled evolution plot
+    %% scaled evolution plot
     \begin{figure*}[htp]
@@
 
-% scaled distribution plot
+    %% scaled distribution plot
     \begin{figure*}[htp]
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% end kinematics
+%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%
+% Discussion section %
 \section{Discussion}\label{sec:discussion}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-03-06 paper/pears.tex
Updates from Overleaf

@@
 \newcommand{\reflabel}[1]{\ensuremath{^{\mbox{\scriptsize{#1}}}}}
+\newcommand{\scsep}{\ensuremath{\rm r_{sep}/r_{vir}}}
+\newcommand{\scvel}{\ensuremath{\rm v_{rel}/v_{vir}}}
 
@@
     \subsection{Scaled Kinematics}\label{sec:results-scaled}
-    %% introduction to section
-    For brevity we show results for the major dwarf and massive pairs. Minor pairs show the same trends
+    %% intro to scaled kin. evolution & bulk results
+    In Sec.~\ref{sec:results-kinematics}, we show that the separations and relative velocities of dwarf and massive pairs evolve similarly as a function of redshift. 
+    However, the magnitude of pair separations and velocities are set by the mass scale of the pair. 
+    For example, a dwarf pair at $z=0$ has a median relative velocity of $70\kms$, while a massive pair will have a median velocity of $175\kms$ at $z=0$.
 
-    %% text on scaled kins evlution
-    basically talk about how we find that the scaled versions of dwarfs and massives behave very similarly.
-    so, the scaled versins of all of these pairs behave VERY similarly in sc.
-velocity space, a bit different in sc.
-separation space but still kinda the same.
-also, can talk about how at z>2.5, dwarf pairs tend to live ooutside of their host's virial mass which is wildin -> maybe not bound at high z, though could become bound by low z by mass accretion ?
+    To explore the impact of halo growth and mass scale the kinematics pairs, we study the relative separation of a primary and secondary halo scaled by the virial radius of the FoF group (\scsep), and the relative velocity divided by the circular speed of the group at the virial radius (\scvel).
+    In Fig.~\ref{fig:scaled}, we show the median scaled separation and scaled velocity for dwarf and massive major pairs as a function of time. 
+    Minor pairs show the same trends, so we've omitted them here for brevity.
 
-    %% text on scaled kins distributions 
-    dwarf and massive distributioons look very similar, and also do not show a ton of evolution with redshift.
-for scaled separation, and velocity both, this is due to the growth of halos, so while the separation increases, the halo radius also increases.
-Since v inversely proportional to $R^1/2$, the increasing virial radius leads to lower circular velocitries given same mass, and thus, the higher separation pairs will allso have lower velocities.
+    %% the behavior of massive and dwarf pairs
+    Overall, the median scaled separation of dwarf pairs and massive pairs do not evolve significantly differently from $z=4\to0$.
+    In fact, the median separation of halos in a pair is smaller than the group virial radius for at $z<2.5$, but is larger than the virial radius at $z>2.5$.
+    %maybe not bound at high z, though could become bound by low z by mass accretion ? 
+    Dwarf pairs tend to have slightly larger separations relative to their virial radius than massive pairs at almost all redshifts, though the spread of median scaled separations is large for massive pairs at $z>2$.
 
-    Scaled vel fig.
---   Despite the difference between dwarf and massive pairs in physical distribution as indicated by the plot of scaled separations (Figure~\ref{fig:sep-scaled}), the scaled velocity distribution of pairs indicates that dwarf and massive galaxy pairs operate similarly in velocity space.
-There is little to no mass dependence on the scaled velocity of dwarf or massive pairs., and is thus independent of the mass scale , meaning dwarf and massive scaled velocities evolve is nearly identically for $z=0-4$.
+    The median scaled velocities of dwarf pairs and massive pairs increase at lower redshift (see right panel of Fig.~\ref{fig:scaled}).
+In fact, dwarf and massive pairs evolve almost identically for $z=0-4$, and thus, the redshift evolution of a pair at either of these mass scales is independent of the total mass of the system.
+    We also find that pairs at $z<0.5$ have relative velocities in excess of their virial velocity, but are smaller than the virial velocity for $z=0.5-4$.
+
+    %% distributions of scaled kinematics
+    In Fig.~\ref{fig:scaled-dist}, we show the distribution of scaled separations and velocities at redshifts $z=0,1,2,3,4$. 
+    The distributions show roughly equivalent shape and extent for both dwarf and massive scaled kinematics, and do not vary significantly with redshift. 
+    scaled separation, and velocity both, this is due to the growth of halos, so while the separation increases, the halo radius also increases.
+    % behavior of massive vs. dwarf 
+    Overall, our results imply that there is little to no mass dependence on the redshift evolution of pair velocities, though pair separations seem to have a weak dependence on the total system mass.
 
@@
       \includegraphics[width=\textwidth]{scaledcombo_1000.png}
-      \caption{
+      \caption{ \label{fig:scaled}
       %  Left
@@
         % any overall trends?
-      All pairs show a peak in scaled velocity at $z=0$.
+      All pairs show a peak in scaled velocity around $z=0$.
 From $z=0-0.5$, a majority of both dwarf and massive pairs have relative velocities larger than the circular velocity of their group at the virial radius.
@@
       (Bottom) The scaled separation/velocity of dwarf major pairs subtracted from that of massive major pairs, indicated by ``M-D".
-      The scaled separation difference shows minor differences between the dwarf and massive population, with dwarf pairs having slightly higher scaled separation for $z<1$.
+      The scaled separation difference shows small differences between the dwarf and massive population, with dwarf pairs having slightly higher scaled separation for $z<1$.
 The scaled velocity difference is $\sim0$ at all redshifts.
       Minor pairs (not shown here) follow the same trends as major pairs in both the massive and dwarf regime.
-        }
-      \label{fig:scaled}
+\kc{maybe it'd be helpful to add horizontal lines at 1 }        }
     \end{figure*}

### 2023-03-07 paper/pears.tex
wrote scaled kin. section, added methods and discussion outline

@@
  \section{Methodology}\label{sec:methods}
-% \subsection{Simulation details}
-% \subsection{Choosing dwarf and massive halos in TNG}
-% \subsection{Abundance matching}
-% \subsection{Pair selection}
-%     \subsubsection{Selecting primaries}
-%     \subsubsection{Selecting companions}
-% \subsection{Overview of pair properties}
-%     \subsubsection{Description of counts plot}
-%     \subsubsection{Description of stellar mass ratio plot}
-% \subsection{Table}
-% Table should include the median number of primaries and of pairs (major and minor) at a variety of redshifts.
-
-% % methods plots
-%   \begin{figure*}[htp]
-%     \centering
-%     \includegraphics[width=\textwidth]{counts_1000.png}
-%     \caption{(Top) Median number of dwarf (left) and massive (right) primaries and pairs as a function of redshift.
-%     Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations, as described in Sec.~\ref{sec:methods-err}.
-%     There are approximately 8 times as many dwarf primaries as massive primaries. 
-%     % dwarf galaxies
-%     The dwarf primary count (green solid line in top left panel) is at a minimum at $z=4$, rises to a maximum of $\sim15000$ halos per realization by $z=1$, then decreases by $\sim16\%$ to 12000 halos at $z=0$.
-The dwarf pair count (green dashed line), on the other hand, peaks at $z\sim2$ with 3000 pairs, and decreases to a minimum of about 1000 pairs at $z=0$.
-%     % Massive galaxies (right)
-%     The massive primary count (pink solid line in top right panel) behaves similarly to the dwarf primary count, with a minimum count at $z=4$ which rises to a maximum of $\sim2000$ halos per realization at $z\sim1$, then decreases slightly by $\sim5\%$ to $\sim$1800 halos by $z=0$.
-%     Unlike dwarf pairs whose pair count peaks at $z=2$, pair count for massive galaxies (pink dashed line) follows similar behavior to the total massive primary count, with a minimum at $z=4$, and increasing to $z=\sim 1$ before leveling off.
-At very low redshift, the pair count and primary count have opposite behavior, with the pair count \textit{increasing} at very low redshifts of $z=0-0.25$ and \textit{peaking} at $z=0$.
-%     (Bottom) Fraction of pairs per primary as a function of redshift (i.e., the ratio between dotted line and solid line in each column).
-Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$.
-The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.}
-%     \label{fig:counts}
-%   \end{figure*}
-
-%   \begin{figure*}[htp]
-%     \centering
-%     \includegraphics[width=\textwidth]{smrdist_1000.png}
-%     \caption{Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs.
-Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$.
-Overall, the stellar mass ratio distribution of major and minor pairs of dwarf and massive galaxies show little evolution from $z=4$ (right) to $z=0$ (left).
-%     Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.}
-%     \label{fig:massratio}
-%   \end{figure*}
-
 %  Our sample data was obtained using a strict set of selection criteria, as outlined in this section.
 % In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulations utilized in this study.
-% Sec.~\ref{sec:methods-am} explains the abudance matching prescription used to associate stellar masses with the dark matter subhalos.
+% Sec.~\ref{sec:methods-am} explains the abundance matching prescription used to associate stellar masses with the dark matter subhalos.
 % Sec.~\ref{sec:methods-crit} provides a detailed outline of our selection criteria and process for picking pairs.
@@
 
-% %%%%%%%%%%%
-% %%%%%%%%%%%
-% \subsection{Simulation details}\label{sec:methods-sims}
+\subsection{Simulation details} \label{sec:methods-sims}
+    \begin{itemize}
+        \item What do we require in a sim/why using TNG hydro?
+        \item Brief sim details \& and the data we use (group and merger cats)
+    \end{itemize}
+
+\subsection{Choosing dwarf and massive halos in TNG} \label{sec:methods-halos}
+
+\subsection{Abundance matching} \label{sec:methods-am}
+    \begin{itemize}
+        \item what is abudance matching
+        \item why are we using it?
+        \item what method and how do we use it? 
+    \end{itemize}
+
+\subsection{Pair selection}\label{sec:methods-pairs}
+    \begin{itemize}
+        \item what types of pairs are we looking for? 
+        \item why do we pick the mass range we are looking at?
+        \item how do we pick out the groups we'll use (group crit)
+    \end{itemize}
+    \subsubsection{Selecting primaries}
+            \begin{itemize}
+                \item definition of prims
+                \item how we use single-halo groups. 
+            \end{itemize}
+    \subsubsection{Selecting companions}
+            \begin{itemize}
+                \item companions selected by mass ratio
+                \item explain pairing method for each realization
+            \end{itemize}
+
+\subsection{Overview of pair properties} \label{sec:methods-props}
+    \begin{itemize}
+        \item what are properties of our sample?
+    \end{itemize}
+    \subsubsection{Description of counts plot}
+            \begin{itemize}
+                \item general behavior of dwarf primaries
+                \item general behavior of dwarf pairs
+                \item general behavior of massive prims
+                \item general behavior of massive pairs
+                \item brief explanation of bottom panel
+            \end{itemize}
+    \subsubsection{Description of stellar mass ratio plot}
+            \begin{itemize}
+                \item what is being shown?
+                \item what is the general behavior?
+                \item comparison: dwarfs vs. massive galaxies 
+                \item comparison: major vs. minor pairs
+            \end{itemize}
+
+\subsection{Analysis method/defs} \label{sec:methods-analysis}
+    \begin{itemize}
+        \item Pair fractions
+        \item separations
+        \item velocities
+        \item scaled units
+        \item data presented (median def and spread)
+    \end{itemize}
+
+\subsection{Table}
+Table should include the median number of primaries and of pairs (major and minor) at a variety of redshifts.
+
+%%%%%%%%%%%
+%%%%%%%%%%%
+% \subsection{Simulation details}
 % % what is it that we are trying to study? why use illustris?
@@
 
-% % \begin{table*}[htb]
-% % \begin{tabular}{l|llll}
-% %  & \illd & \illh & \tngd & \tngh\\\hline\hline
-% %  L$_{\rm Box}$ [Mpc] & 106.5 & 106.5 & 110.7 & 110.7 \\
-% % m$_{\rm DM}$ [M$_\odot$] & 7.5$\times10^6$ & 6.3$\times10^6$ & 8.9$\times10^6$ & $7.5\times10^6$\\
-% % m$_{\rm gas}$ & -- & $1.3\times 10^{6}$ & -- & $1.4\times 10^{6}$ \\\hline
-% % \end{tabular}
-% % \caption{\label{table:sim}Parameters of the Illustris simulations used in this analysis.}
-% % \end{table*}
-
 % %%%%%%%%%%%
-% %%%%%%%%%%%
-% \subsection{Abundance matching prescription}\label{sec:methods-am}
+%%%%%%%%%%%
+% \subsection{Abundance matching prescription}
 % % Why do we need stellar masses?
@@
 
-% %%%%%%%%%%%
-% %%%%%%%%%%%
-% \subsection{Selection criteria}\label{sec:methods-crit}
+%%%%%%%%%%%
+%%%%%%%%%%%
+% \subsection{Selection criteria}
 % In this section, we outline the selection criteria used to select dwarf and massive subhalo pairs. 
@@
 % \subsubsection{Isolation}
-% As we are interested in the frequency and separations of galaxy pairs that are undisturbed by nearby massive perturbers, we select subhalo pairs as the most massive subhalos of their group halos. 
+% As we are interested in the frequency and kinematics of galaxy pairs that are undisturbed by nearby massive perturbers, we select subhalo pairs as the most massive subhalos of their group halos. 
 % We have confirmed that nearly 100\% of the the most massive subhalos in each group are outside of the Hill radius of any nearby subhalo with greater mass, and are thus a rough isolation criteria is inherent in our selection.
@@
 
-% \subsubsection{Primary subhalos}\label{sec:methods-crit-prims}
+% methods plots
+  \begin{figure*}[htp]
+    \centering
+    \includegraphics[width=\textwidth]{counts_1000.png}
+    \caption{(Top) Median number of dwarf (left) and massive (right) primaries and pairs as a function of redshift.
+    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations, as described in Sec.~\ref{sec:methods-err}.
+    There are approximately 8 times as many dwarf primaries as massive primaries. 
+    % dwarf galaxies
+    The dwarf primary count (green solid line in top left panel) is at a minimum at $z=4$, rises to a maximum of $\sim15000$ halos per realization by $z=1$, then decreases by $\sim16\%$ to 12000 halos at $z=0$.
+The dwarf pair count (green dashed line), on the other hand, peaks at $z\sim2$ with 3000 pairs, and decreases to a minimum of about 1000 pairs at $z=0$.
+    % Massive galaxies (right)
+    The massive primary count (pink solid line in top right panel) behaves similarly to the dwarf primary count, with a minimum count at $z=4$ which rises to a maximum of $\sim2000$ halos per realization at $z\sim1$, then decreases slightly by $\sim5\%$ to $\sim$1800 halos by $z=0$.
+    Unlike dwarf pairs whose pair count peaks at $z=2$, pair count for massive galaxies (pink dashed line) follows similar behavior to the total massive primary count, with a minimum at $z=4$, and increasing to $z=\sim 1$ before leveling off.
+At very low redshift, the pair count and primary count have opposite behavior, with the pair count \textit{increasing} at very low redshifts of $z=0-0.25$ and \textit{peaking} at $z=0$.
+    (Bottom) Fraction of pairs per primary as a function of redshift (i.e., the ratio between dotted line and solid line in each column).
+Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$.
+The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.}
+    \label{fig:counts}
+  \end{figure*}
 
-% \subsubsection{Primary subhalos}\label{sec:methods-crit-pairs}
+  \begin{figure*}[htp]
+    \centering
+    \includegraphics[width=\textwidth]{smrdist_1000.png}
+    \caption{Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs.
+Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$.
+Overall, the stellar mass ratio distribution of major and minor pairs of dwarf and massive galaxies show little evolution from $z=4$ (right) to $z=0$ (left).
+    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.}
+    \label{fig:massratio}
+  \end{figure*}
 
-% \subsubsection{Stellar masses from the hydro sims}
+\begin{table*}[htb]
+  \centering
+    \begin{tabular}{lcc}
+     & Dwarf Pairs & Massive Pairs \\\hline\hline
+    % Group Mass & $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ & $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$  \\
+    % Subhalo Max Mass &  &  \\
+    % Subhalo Current Mass & $>1\times10^{10} \Msun$ & $> 5\times10^{11} \Msun$ \\
+    Primary &$1\times10^{8} < \msam < 5\times10^{9} \Msun$ & $5\times10^{9} < \msam < 1\times10^{11} \Msun$\\\hline
+    \end{tabular}
+    \caption{\label{table:mass}Selection criteria for dwarf and massive pairs.}
+    \end{table*}
 
-% \subsection{Counts and distributions}\label{sec:methods-counts}
-
-% \begin{itemize}
-%   \item Introduce simulations
-%   \item outline selection steps
-%   \item dwarf pairs
-%   \item massive pairs
-%   \item include table with parameters used for pairs
-%   \item plots
-%     \begin{itemize}
-%       \item distribution plots
-%       \item counts plots
-%     \end{itemize}
-% \end{itemize}
-
-% % selection criterion
-% \begin{table*}[htb]
-%   \centering
-%     \begin{tabular}{lcc}
-%      & Dwarf Pairs & Massive Pairs \\\hline\hline
-%     % Group Mass & $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ & $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$  \\
-%     % Subhalo Max Mass &  &  \\
-%     % Subhalo Current Mass & $>1\times10^{10} \Msun$ & $> 5\times10^{11} \Msun$ \\
-%     Primary &$1\times10^{8} < \msam < 5\times10^{9} \Msun$ & $5\times10^{9} < \msam < 1\times10^{11} \Msun$\\\hline
-%     \end{tabular}
-%     \caption{\label{table:mass}Selection criteria for dwarf and massive pairs.}
-%     \end{table*}
-
-% % equivalent snapshot table
-% \begin{table*}[tbp]
-%   \centering
-%   \begin{tabular}{l|cc|cccc} % increase this to 7 columns
-%     \hline \hline
-%    & \multicolumn{2}{c|}{Snapshot number} & \multicolumn{4}{c}{Number of primaries}\\
-%    & \ill & \tng  & \illd & \illh & \tngd & \tngh \\ 
-%   \hline
-%   z = 0   &   135  &   99   & $11431.5_{-24.42}^{68.38}$ & $12650.0_{-25.84}^{46.84}$ & $13255.0_{-32.60}^{56.72}$ & $12035.0_{-69.24}^{20.36}$\\
-%   z = 1   &   85   &   50   &  $14769.0_{-30.24}^{47.28}$ & $16568.0_{-32.20}^{69.60}$ & $17445.5_{-40.86}^{51.90}$ & $15946.5_{-59.38}^{39.22}$ \\
-%   z = 2   &   68   &   33   &  $12602.5_{-31.98}^{45.94}$ & $14174.0_{-12.48}^{62.32}$ & $15413.5_{-34.62}^{28.86}$ & $14334.0_{-29.44}^{45.24}$ \\
-%   z = 3   &   60   &   25   &     $8533.5_{-54.50}^{39.46}$ & $9390.0_{-63.40}^{41.32}$ & $10901.0_{-44.64}^{46.56}$ & $10106.5_{-47.90}^{39.74}$  \\
-%   % z = 3.7   &   54   &   21   \\
-%   \hline \hline
-%   \end{tabular}
-%   \caption{\label{tab:equiv-snapshot} The snapshot number of the original \ill\ and the \tng\ simulations at redshifts $z=0-3$, as well as the median number dwarf (massive) primaries that were selected with $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$ ($5\times 10^{9} < \msam < 1\times 10^{11} \rm M_\odot$) in XX abundance matching realizations.
+% equivalent snapshot table
+\begin{table*}[tbp]
+  \centering
+  \begin{tabular}{l|cc|cccc} % increase this to 7 columns
+    \hline \hline
+   & \multicolumn{2}{c|}{Snapshot number} & \multicolumn{4}{c}{Number of primaries}\\
+   & \ill & \tng  & \illd & \illh & \tngd & \tngh \\ 
+  \hline
+  z = 0   &   135  &   99   & $11431.5_{-24.42}^{68.38}$ & $12650.0_{-25.84}^{46.84}$ & $13255.0_{-32.60}^{56.72}$ & $12035.0_{-69.24}^{20.36}$\\
+  z = 1   &   85   &   50   &  $14769.0_{-30.24}^{47.28}$ & $16568.0_{-32.20}^{69.60}$ & $17445.5_{-40.86}^{51.90}$ & $15946.5_{-59.38}^{39.22}$ \\
+  z = 2   &   68   &   33   &  $12602.5_{-31.98}^{45.94}$ & $14174.0_{-12.48}^{62.32}$ & $15413.5_{-34.62}^{28.86}$ & $14334.0_{-29.44}^{45.24}$ \\
+  z = 3   &   60   &   25   &     $8533.5_{-54.50}^{39.46}$ & $9390.0_{-63.40}^{41.32}$ & $10901.0_{-44.64}^{46.56}$ & $10106.5_{-47.90}^{39.74}$  \\
+  % z = 3.7   &   54   &   21   \\
+  \hline \hline
+  \end{tabular}
+  \caption{\label{tab:equiv-snapshot} The snapshot number of the original \ill\ and the \tng\ simulations at redshifts $z=0-3$, as well as the median number dwarf (massive) primaries that were selected with $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$ ($5\times 10^{9} < \msam < 1\times 10^{11} \rm M_\odot$) in XX abundance matching realizations.
 \kc{fill in with numbers after doing more realizations} \kc{include takeaway}}
-%   \end{table*}
+  \end{table*}
 
@@
 The scaled velocity difference is $\sim0$ at all redshifts.
-      Minor pairs (not shown here) follow the same trends as major pairs in both the massive and dwarf regime.
-\kc{maybe it'd be helpful to add horizontal lines at 1 }        }
+      Minor pairs (not shown here) follow the same trends as major pairs in both the massive and dwarf regime.}
 \end{figure*}
@@
   \includegraphics[width=\textwidth]{scaledcombodist_1000.png}
-      \caption{Scaled separation distribution (left) and scaled velocity distribution (right) at $z=0,1,2,3$, and $4$, normalized by the total number of pairs at the corresponding redshift. 
+  \caption{
+      Scaled separation distribution (left) and scaled velocity distribution (right) at $z=0,1,2,3$, and $4$, normalized by the total number of pairs at the corresponding redshift. 
       % the point? what am I trying to get across
@@
 % Discussion section %
+\pagebreak
 \section{Discussion}\label{sec:discussion}
 
+\subsection{Comparison to previous works/literature}
+\begin{itemize}
+    \item our pairs are not projected dist, so represent set of maximum seps/vels possible
+    \item compare to Synder 2022+
+    \item compare to Lotz and Rodriguez Gomez 
+\end{itemize}
+
+\subsection{Implications for differences in massive and dwarf pair evolution?}
+
+\subsection{Implications for observational pair definitions}
+    \begin{itemize}
+        \item examples of typical pair selection criteria
+        \item Sep distribution explanation
+        \item Vel. distribution ex.
+        \item quantify \% of pairs > current cuts
+
+    \end{itemize}
+
+\subsection{Low separation implications for JWST and other wide and deep surveys}
+
+\subsection{Limitations of our methods}
+\pagebreak
 % Mean separation fig. --
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\pagebreak
 \section{Summary and Conclusions}\label{sec:summary}
+\begin{itemize}
+    \item What we did 
+    \item Main findings:
+        \begin{itemize}
+            \item pair fractions
+            \item separations
+            \item velocities
+            \item scaled values
+        \end{itemize}
+    \item Main takeaways: (maybe include these within main findings bullets~)
+        \begin{itemize}
+            \item lit comp.
+            \item dwarfs not equal massives 
+            \item JWST imps.
+        \end{itemize}
+    \item Future work
+\end{itemize}
+
 % Findings:

### 2023-03-09 paper/pears.tex
intro and 1st sec of methods

@@
  \section{Methodology}\label{sec:methods}
-%  Our sample data was obtained using a strict set of selection criteria, as outlined in this section.
-% In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulations utilized in this study.
-% Sec.~\ref{sec:methods-am} explains the abundance matching prescription used to associate stellar masses with the dark matter subhalos.
-% Sec.~\ref{sec:methods-crit} provides a detailed outline of our selection criteria and process for picking pairs.
-% Finally, Sec.~\ref{sec:methods-counts} gives an overview of the properties of our sample.
+We use a run of the \tngh\ simulation to select halo pairs according to a strict set of selection criteria as outlined in this section. 
+In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulation utilized in this study.
+Sec.~\ref{sec:methods-halos} outlines the initial mass cuts used to define our full sample of primary halos about which we will search for secondary companions.
+Sec.~\ref{sec:methods-am} outlines the abundance matching prescription we used to associate dark matter subhalos with stellar masses.
+Sec.~\ref{sec:methods-pairs} describes the second set of selection criteria we apply to obtain the full sample of dwarf and massive pairs.
+In Sec.~\ref{sec:methods-props}, we show some of the properties of our entire pair sample, including the total number of pairs and stellar mass ratios.
+Finally, Sec.~\ref{sec:methods-analysis} gives an overview of our analysis methods and a description of the parameters of interest in this study.
 
     \subsection{Simulation details} \label{sec:methods-sims}
-    \begin{itemize}
-        \item What do we require in a sim/why using TNG hydro?
-        \item Brief sim details \& and the data we use (group and merger cats)
-    \end{itemize}
+        % Brief description of TNG hydro and which run we use.
+    The \tng\ project ~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} consists of a suite of dark-matter-only $N$-body as well as full physics cosmological simulations consistent with the \textit{Planck2015} \lcdm/  cosmology~\citep{Planck2015}.
+    In this study we utilize data from the main high resolution full physics run of the (110.7\Mpc)$^3$ volume simulation, \textsl{TNG100-1}, which includes dark matter and baryonic particles and follows the evolution of $1820^3$ dark matter particles from $z=127$ to $z=0$.
+
+      % subfind, sublink, and groups and subhalos
+    We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm~\citep{springel2001,dolag09}. 
+    These catalogs consist of halos , defined using the Friends-of-Friends (FoF) algorithm~\citep{davis1985} to link nearby particles, and their associated subhalos, which are over-dense and gravitationally bound dark matter structures compared to the background.
+(From here, we will refer to FoF halos as "groups" and their subhalos as )
+      % We also use merger catalogs generated by XX for YY purpose. 
+    We also use merger trees provided by the \texttt{SUBLINK} algorithm~\citep{RG2015}, which tracks subhalos between snapshots using their DM particle data, in order to trace subhalo mass growth and merger histories.
+
+    The large volume of this simulation offers a large statistical sample of halos to study in a cosmological context, but is also high enough resolution ($m_{\rm DM} = 7.5\times10^6\Msun$, $m_{\rm gas} = 1.4\times10^6\Msun$) that dwarf halos ($\sim1\times10^{9-10.5}\Msun$) halos are resolved into roughly hundreds or more particles, well above the resolution limit of 32 DM particles for halos identified with \texttt{SUBFIND}, and 20 gas and star particles used to construct baryonic merger trees.
+
+        %  this MIGHT go in a different section? am I talking about this because I want to show why we use hydro instead of dark? 
+    Baryonic process are known to affect the structure and formation of dark matter halos of low mass ($M_*\lesssim 1\times10^9\Msun$) subhalos in simulations~\citep[see e.g.][and references therein]{Sales:2022}.
+    Additionally, the shallow potential well of dwarf galaxies compared to their massive counterparts may lend themselves more easily to disruption from baryonic processes such as supernova feedback and reionization~\citep{}, resulting in fewer low mass halos ($\lesssim 5\times10^{10}$) in hydrodynamic simulations~\citep{vogelsberger14B}.
+    % Thus, the number of primaries  we expect that our choice of simulation will result in
 
@@
                 \item explain pairing method for each realization
+                \item minimum separation of 15kpc so that we can be more confident about the mass associated with each halo (at smaller seps, more mass will be attributed to the central, also though why we use the stellar mass associated with the max mass isntead of the current mass)
             \end{itemize}
@@
 % However, we also require high resolution simulations such that the dwarf subhalos are resolved well enough to ensure robust statistics at the low mass end, and so we are not limited by our inability to resolve objects down to halo masses of $M_{\rm halo}\approx1\times 10^9\, \Msun$.
-
-% % Baryonic processes
-% Baryonic process are known to affect the dark matter halo structure of low mass ($M_*<1\times10^9\Msun$) subhalos in simulations~\citep[see e.g.][and references therein]{Sales:2022}.
-% Additionally, the shallow potential well of dwarf galaxies compared to their massive counterparts may lend themselves more easily to disruption from baryonic processes such as supernova feedback, which could change the occurance rate of low mass subhalos in hydrodynamic simulations \kc{check and see if they looked at this in the TNG100 galaxy paper}.
-% To study the effect of baryonic processes on the rate and separation of pairs, we require cosmological simulations which have both dark matter only runs and to full hydrodynamics.
-
-% % details of Illustris and Illustris TNG
-% The \textit{Illustris Project} ~\citep{vogelsberger14A,nelson15} and \textit{IllustrisTNG Project}~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} are a set of N-body and hydrodynamic cosmological simulations which are perfectly suited for such a study.
-% We use the dark matter only and full hydrodynamic runs of both the \ill-1 and \tng100-1 simulations to explore the connection between pairs and baryonic processes. 
-% Each of these simulations follows the dynamical evolution of $1820^3$ dark matter particles from $z=127$ to $z=0$ through a periodic volume of roughly $100^3$ Mpc$^3$. 
-% The \ill{} simulations follow a cosmology consistent with \textit{WMAP-9}~\citep{hinshaw2013}, while the \tng{} simulations are consistent with \textit{Planck2015}~\citep{Planck2015}.
-% Specifically, we use the \textit{Illustris-1-Dark}, \textit{Illustris-1}, \textit{TNG100-1-Dark}, and \textit{TNG100-1} simulations (hereafter \illd, \illh, \tngd, and \tngh{} respectively, % see Table~\ref{table:sim} for details).
-
-% % deets on the hydrodynamics of 
-% \kc{hydrodynamics details on the difference between the two hydro simulations. also include differences between the two dark simulations, if there are any besides the cosmology. }
-
-% % subfind, sublink, and groups and subhalos
-% We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm ~\citep{springel2001,dolag09}. 
-% These catalogs consist of halos (or "groups"), defined using the Friends-of-Friends (FoF) algorithm~\citep{davis1985} to link nearby particles, and their associated subhalos, which are over-dense and gravitationally bound dark matter structures.
-% We also use the merger trees provided by the \texttt{SUBLINK} algorithm \citep{gomez15}, which tracks subhalos between snapshots using their particle data, in order to trace the mass growth and merger histories of our subhalos.
 

### 2023-03-13 paper/pears.tex
finished with halo selection and AM sec

@@
  \section{Methodology}\label{sec:methods}
-We use a run of the \tngh\ simulation to select halo pairs according to a strict set of selection criteria as outlined in this section. 
+We aim to quantify and characterize the frequency (or occurrence rate) and bulk kinematic properties of galaxy pairs in a cosmologically consistent way a function of cosmic time. 
+In particular, we study dwarf galaxy pairs and massive galaxy pairs that are of similar stellar and halo mass to a variety of pairs in the Local Group. 
+We categorize these pairs into one of four pair types: massive major pairs, such as the MW+M31; massive minor pairs, such as M31+M33 or MW+LMC; dwarf major pairs, such as M33+LMC; and finally, dwarf minor pairs, such as the LMC+SMC.
+
+To this end, we use a run of the \tngh\ simulation to select halo pairs at each snapshot according to a strict set of selection criteria as outlined in the remainder of this section. 
 In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulation utilized in this study.
-Sec.~\ref{sec:methods-halos} outlines the initial mass cuts used to define our full sample of primary halos about which we will search for secondary companions.
+Sec.~\ref{sec:methods-halos} outlines the initial mass cuts used to define our full sample of halos, from which we will select pairs.
 Sec.~\ref{sec:methods-am} outlines the abundance matching prescription we used to associate dark matter subhalos with stellar masses.
-Sec.~\ref{sec:methods-pairs} describes the second set of selection criteria we apply to obtain the full sample of dwarf and massive pairs.
+Sec.~\ref{sec:methods-pairs} describes the second set of selection criteria we apply to obtain the full sample of pairs.
 In Sec.~\ref{sec:methods-props}, we show some of the properties of our entire pair sample, including the total number of pairs and stellar mass ratios.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%
+% Sim details section %
     \subsection{Simulation details} \label{sec:methods-sims}
@@
     The \tng\ project ~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} consists of a suite of dark-matter-only $N$-body as well as full physics cosmological simulations consistent with the \textit{Planck2015} \lcdm/  cosmology~\citep{Planck2015}.
-    In this study we utilize data from the main high resolution full physics run of the (110.7\Mpc)$^3$ volume simulation, \textsl{TNG100-1}, which includes dark matter and baryonic particles and follows the evolution of $1820^3$ dark matter particles from $z=127$ to $z=0$.
+    In this study we utilize data from the main high resolution full physics run of the (110.7\Mpc)$^3$ volume simulation, \textsl{TNG100-1}, which includes dark matter and baryonic particles and follows the evolution of $1820^3$ dark matter particles in 100 snapshots from $z=127$ to $z=0$.
 
@@
     % Thus, the number of primaries  we expect that our choice of simulation will result in 
+% End sim details     %
+%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%    
+% Choosing halos section %
     \subsection{Choosing dwarf and massive halos in TNG} \label{sec:methods-halos}
+    % start off with group selection 
+        % brief explanation of FoF groups in sim
+    Each snapshot from the TNG100 group catalogs consist of FoF groups, large halos of closely associated DM particles, and the subhalos they contain, which are smaller bound structures of DM and the gas and star particles nearest to them.
+    We will refer to these two structures as "groups" and either "halos" or "subhalos" respectively, from here on. 
+    Galaxies form in these subhalos, so our pair sample will consist of pairs of subhalos within these larger group structures.
 
+    We are interested in the inherent dynamics and properties of pairs of halos in the field.
+    Thus, we want our pairs to consist of some of the most massive halos in each group, and ensure that the pair is not dynamically influenced by nearby massive groups. 
+    By selecting pairs from the most massive halos of a group, a rough isolation criteria is inherent in our selection due to the nature of the FoF algorithm, which groups together nearby particles. 
+    To confirm that our sample , we have confirmed that nearly 100\% of the the most massive subhalos in each group are outside of the Hill radius of any nearby group or subhalo with greater mass.
+
+    The first selection criteria that we invoke is a cut on the total group mass, $M_{G}$ (i.e., a mass cut on the FoF group mass, given by \texttt{Group\_M\_TopHat200} in the \tng\ group catalogs). 
+    We define the group mass range for dwarf groups as $8\times 10^{10} < M_{G,d} < 5\times 10^{11}\Msun$, which will host mass analogs of the LMC+SMC and LMC+M33 pairs. 
+    Massive group a massive group mass range from $1\times10^{12} < M_{G,m} < 6.5\times10^{12}$, which at the lower mass end will host MW+LMC pairs, and MW+M31 pairs at the higher mass end. 
+    The group mass criteria is fixed for all redshifts, so at high z, the dwarf pairs we select may be the progenitors of higher mass systems at $z=0$.
+    Note that all masses used in this analysis are physical units, such that masses from the group catalogs are divided by $h$ to get units of \Msun.
+
+    Selecting dwarf pairs from the dwarf group mass range also ensures that we are not selecting satellite systems in the halos of more massive systems. 
+    The LMC+SMC, for example, are highly perturbed by the influence of the MW, and thus we do not pick dwarf pairs from high mass groups that may contain large nearby MW-mass analogs.
+
+        % explain what halos we will move forward with. 
+    For each group that passes the group mass cut, we create a catalog of all subhalos that pass a ``current mass" criteria: current (same snapshot) halo mass must be $M_h > 1\times10^{9}\Msun$ (the \texttt{SubhaloMass} field in the group catalogs).\footnote{Note that for the TNG100 hydro run, the halo mass is the total sum of all bound dark matter \textit{and} baryonic particles.}
+    This lower mass threshold ensures that our halos are resolved into $>100$ particles, and thus should be robust to the SUBFIND and SUBLINK algorithms even at the lowest mass end.
+
+    We then utilize the merger tree catalogs to determine the maximum halo mass ever achieved by each halo. 
+    The set of all subhalos at each snapshot that pass the group mass and current mass cuts constitutes our entire subhalo sample. 
+    From here, we will use further selection criteria to narrow our sample down to pairs.
+
+% End choosing halos     %
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%    
+% Choosing halos section %
     \subsection{Abundance matching} \label{sec:methods-am}
-    \begin{itemize}
-        \item what is abudance matching
-        \item why are we using it?
-        \item what method and how do we use it? 
-    \end{itemize}
+        % what is abundance matching
+    Abundance matching is a technique used to associate dark matter halo mass with specific galaxy properties.
+    This allows us to associate dark matter halos from the \tng\ simulation with observationally motivated galaxy properties. % maybe observationally constrained, instead? 
+    In particular, we will be utilizing a stellar mass to halo mass (SMHM) relationship to assign stellar masses to each of the subhalos in our sample.
 
+    % few details about the msoter relationship. how was it determined?
+        % why are we using abundance matching 
+    The \tng100-1 subhalo catalogs do already contain a stellar mass field as computed in the simulation by simulating star formation and  AGN feedback, stellar feedback, galactic winds, etc.    
+    However, there are a couple reasons we opt to assign stellar masses to our halos, rather than use those from the simulation.
+
+    Primarily, applying an abundance matching prescription to assign stellar masses to each of the dark matter halos allows us to account for the observed spread in the stellar mass-halo mass relationship.
+    This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the spread in the SMHM function is large. 
+    In addition, using stellar masses as calculated from abundance matching allows us to side step any simulation-dependent stellar mass effects.
+    In the case of \tng100 specifically, it is known that the stellar masses of low mass galaxies are often overestimated compared to the galaxy luminosity function at the low mass end\cite{}. 
+    Using an observationally-calibrated abundance matching prescription will thus lead to a more robust result for comparison with and predictions for observations. 
+    Finally, utilizing an abundance matching prescription allows us to directly compare results between dark matter only and hydro simulations, since the stellar masses are assigned the same way. 
+    We make brief note of results from dark matter only simulations in Sec.~\ref{sec:results}.
+
+        % what am prescription are we using? 
+    We use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic recipe to assign stellar masses to dark matter halos. 
+    The~\citet{Moster2013} relationship is a function of the halo mass, evolves with redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.
+    Additionally, stellar mass is defined separately for central halos (``hosts") and for infalling satellites (``subhalos"), where the first is a function of the virial mass of the halo and its redshift, $M_{vir}$ and $z$, and the second is a function of the mass and redshift at the time of infall, $M_{inf}$ and $z_{inf}$.
+    This assumes that the satellite halos are at the peak of their stellar mass before infall, and neglects the affect of star formation or stellar stripping within the host halo.
+
+        % what do we use for the mass ~ 
+    In this work, we will use the peak halo mass \Mpeak\ from the \sublink\ merger trees to calculate subhalo stellar masses. 
+    \citet{Munshi2021} found that the stellar mass of subhalos at $z=0$ in the ``Marvel-ous Dwarfs" and ``DC Justice League" zoom simulations are more closely correlated with the peak halo mass ($M_{peak}$) than the $z=0$ halo mass for halos with peak halo mass $10^8<M_{\rm peak}<10^{11} \Msun$.
+    % separate citation for peak halo mass and stellar mass relatiosnhip for M > 1e11Msun 
+    Using the peak halo mass additionally allows us to remain robust to scenarios in which a secondary has formed most of its stars, then loses a significant portion of its dark matter content through tidal interactions with a primary, but retains the bulk of its stellar content.
+
+        % regarding the redshift dependence ~
+    We additionally assume that the stellar mass of both the primary and secondary halo can change as a function of redshift after the secondary has entered the primary's halo and do not immediately cease star formation.
+    This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{geha13} which finds that dwarfs $>1\Mpc$ from a MW-type galaxy are often star forming and rarely quenched.
+    Additionally, the SAGA survey has found that large satellites of MW-type galaxies are often very blue, with infall into the halo spurring high rates of star formation due to the large gas fraction in dwarfs~\citep{saga}.
+    Thus, we calculate stellar masses for our subhalos using $M_{\rm peak}$ and the redshift of the current snapshot to calculate the stellar mass of each subhalo, to account for the additional stellar mass that can form after infall.
+
+    As mentioned in a footnote in Sec.~\ref{sec:methods-halos}, the total halo mass of subhalos in the hydro simulation includes the mass of both dark matter and baryonic particles. 
+    In TNG100-1, the DM particle mass is decreased XX\% compared to the DM particle mass in \tng100-1 Dark to account for the additional mass of baryons, such that the total mass of the halo will remain roughly the same between the dark matter only and hydro simulations.
+    Since the~\citet{Moster2013} AM relation was calibrated using DM subhalos from the \texttt{MilleniumII} dark matter only simulation, we will use the total subhalo mass from the TNG100-1 hydro simulation as a proxy for the corresponding DM halo mass in the TNG100-1 Dark run.
+
+        % realizations? 
+    For each subhalo at each snapshot in our full subhalo sample (see Sec.~\ref{sec:methods-halos}), we create a set of 1000 stellar mass values from the SMHM relationship to account for the systematic uncertainty in subhalo stellar masses.
+    Each realization is treated as an independent sample of galaxy stellar masses, which allows us to report realistic spreads of pair properties.
+    Thus, we create 1000 separate pair catalogs, and compute pair properties (pair frequency, separations, etc) for each individual abundance matching realization.
+
+% End choosing halos     %
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%    
+% Pair selection section %
 \subsection{Pair selection}\label{sec:methods-pairs}
+(Note that the LMC+SMC pair would not be selected by our selection criteria since they are a system of satellites in a halo containing much more massive galaxies that would instead by selected as the primary and secondary galaxies of a pair.)
+
+% \begin{enumerate}
+%   \item Select groups in some group range that encompasses MCs and MW-M31
+%   \item For every subhalo in every group with halo mass >1e9Msun, use merger trees to get the maximum masses.
+%   \item Generate 1000 stellar mass realization using abundance matching so we can account for the spread in the relationship
+%   \item Generate catalog at each redshift containing: 
+%   \begin{itemize}
+%     \item For each realization, and in each group with a single subhalo, add the subhalo and it's properties to a catalog of single halos.
+%     \item For each realization, and in each group with 2+ halos, find most massive halo by stellar mass, and the second most massive halo by stellar mass, then add to pair catalog. 
+%     \item If a group has 3+ halos, check the stellar mass of the third most massive object, and see if it is a major/minor companion of the secondary. If not, teritary flag = 0. Otherwise =1.
+%   \end{itemize}
+%   \item Select dwarf primaries: for full catalog, most massive halo (in "pairs") or single halos with stellar mass $1\times10^{8} < \msam < 5\times10^{9} \Msun$. 
+%   \item Select dwarf pairs: for full pair catalog, any pair with stellar mass ratio between 1-1/4 (major pairs) or between 1/4-1/10 (minor pairs).
+All pairs is the union of these two sets.
+Any pair or single halo that is outside of these two sets is an "unpaired" halo.
+Note that unpaired can still have very minor companions.
+% \end{enumerate}
+
     \begin{itemize}
@@
             \end{itemize}
+
+% Pair selection end %
+%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-% %%%%%%%%%%%
-%%%%%%%%%%%
-% \subsection{Abundance matching prescription}
-% % Why do we need stellar masses?
-% One of the goals of this study is to determine the impact of baryonic physics on the occurrence rate and typical separations of galaxy \kc{subhalo?} pairs in cosmological simulations. 
-% However, selecting halo pairs by stellar mass ratio using the stellar masses provided by the simulations is not possible in the dark matter only runs. 
-% Thus, in order ensure the dark matter only and full hydrodynamic samples are self-consistent, we need to associate each of the selected subhalos with a realistic stellar mass.
-
-% % What is abundance matching
-% Abundance matching is one such method of associating a dark matter halo with a stellar mass, assuming a galaxy would form in a halo of that mass.
-
-% However, there is large scatter in the stellar-mass-halo-mass (SMHM) relationship, especially in the dwarf halo regime.
-
-% % How do we utilize it? 
-% In particular, we use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic recipe to paint stellar masses onto dark matter halos. 
-% The~\citet{Moster2013} relationship is a redshift-evolving function of the halo mass, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.
-% \kc{why moster instead of another AM relationship? most closely represent data at lower mass? }
-
-% To assign stellar masses to each of the dark matter halos, we assume that the stellar mass of both the primary and secondary halo can change as a function of redshift after the secondary has entered the primary's halo and do not immediately cease star formation.
-% This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{geha13} which finds that isolated dwarfs ($>1\Mpc$ from a MW-type galaxy) are often star forming and rarely quenched.
-% Additionally,~\citet{Munshi2021} found that the stellar mass of subhalos at $z=0$ in the XX simulations are more closely correlated with the peak halo mass than the $z=0$ halo mass for halos with peak halo mass $10^8<M_{\rm peak}<10^{11} \Msun$.
-
-% Thus, we treat each of the subhalos as centrals according to the~\citet{Moster2013} prescription, using the current snapshot redshift and the peak halo mass of the subhalo to calculate the stellar mass.
-% This additionally allows us remain robust to scenarios in which a secondary may have formed most of its stars, and then lost a significant portion of its dark matter content through tidal interactions with a primary, but will retain the bulk of its stellar content.
-
-% We create 1000 stellar mass realizations from the SMHM relationship, thus accounting for the systematic uncerntainy in subhalo stellar masses.
-Each realization is treated as an independent sample, such that computed properties (pair frequency, separations, etc) are given as the median each realization.
-We report the mean of all realizations and error bars indicate the 1$\sigma$ dispersion across the realizations.
-
 % \subsubsection{Error calculations}\label{sec:methods-err}
@@
 This one happens ~XX\% of the time.}
-
-% \begin{enumerate}
-%   \item Select groups in some group range that encompasses MCs and MW-M31
-%   \item For every subhalo in every group with halo mass >1e9Msun, use merger trees to get the maximum masses.
-%   \item Generate 1000 stellar mass realization using abundance matching so we can account for the spread in the relationship
-%   \item Generate catalog at each redshift containing: 
-%   \begin{itemize}
-%     \item For each realization, and in each group with a single subhalo, add the subhalo and it's properties to a catalog of single halos.
-%     \item For each realization, and in each group with 2+ halos, find most massive halo by stellar mass, and the second most massive halo by stellar mass, then add to pair catalog. 
-%     \item If a group has 3+ halos, check the stellar mass of the third most massive object, and see if it is a major/minor companion of the secondary. If not, teritary flag = 0. Otherwise =1.
-%   \end{itemize}
-%   \item Select dwarf primaries: for full catalog, most massive halo (in "pairs") or single halos with stellar mass $1\times10^{8} < \msam < 5\times10^{9} \Msun$. 
-%   \item Select dwarf pairs: for full pair catalog, any pair with stellar mass ratio between 1-1/4 (major pairs) or between 1/4-1/10 (minor pairs).
-All pairs is the union of these two sets.
-Any pair or single halo that is outside of these two sets is an "unpaired" halo.
-Note that unpaired can still have very minor companions.
-% \end{enumerate}
-
-% The lower mass threshold for subhalos that constitute our dwarf pairs have a halo mass greater than $1\times10^9\Msun$, such that each of our halos are resolved into at least 100 particles in each simulation.
-% \kc{why 100?}
 

### 2023-03-17 paper/pears.tex
added text to pair selection-primaries

@@
     \subsection{Pair selection}\label{sec:methods-pairs}
-(Note that the LMC+SMC pair would not be selected by our selection criteria since they are a system of satellites in a halo containing much more massive galaxies that would instead by selected as the primary and secondary galaxies of a pair.)
+    The full pair sample is constructed from the set of all subhalos and their abundance matching realizations.
+Each pair will consist of a ``primary," the more massive object, and a ``secondary," which is the less massive companion.
+
+    % justify why we want to use stellar mass to define things
+    A majority of the literature uses the definition of "major" and "minor" pairs based on the stellar mass of the objects.
+This is true as well for observational pair samples, such as Lotz 2011, wherein the halo mass of the objects is unknown, and thus the stellar mass is used to define the mass ratio of the pair.
+In order to reproduce statistics that can be meaningfully compared to observations/can be used to inform observations, we opt to define our pair sample via the stellar masses from the abundance matching prescription given in Sec.~\ref{sec:methods-am}.
+
+    \begin{itemize}
+    \item what types of pairs are we looking for? 
+    \item why do we pick the mass range we are looking at?
+    \end{itemize}
 
 % \begin{enumerate}
-%   \item Select groups in some group range that encompasses MCs and MW-M31
-%   \item For every subhalo in every group with halo mass >1e9Msun, use merger trees to get the maximum masses.
-%   \item Generate 1000 stellar mass realization using abundance matching so we can account for the spread in the relationship
-%   \item Generate catalog at each redshift containing: 
-%   \begin{itemize}
-%     \item For each realization, and in each group with a single subhalo, add the subhalo and it's properties to a catalog of single halos.
-%     \item For each realization, and in each group with 2+ halos, find most massive halo by stellar mass, and the second most massive halo by stellar mass, then add to pair catalog. 
-%     \item If a group has 3+ halos, check the stellar mass of the third most massive object, and see if it is a major/minor companion of the secondary. If not, teritary flag = 0. Otherwise =1.
-%   \end{itemize}
 %   \item Select dwarf primaries: for full catalog, most massive halo (in "pairs") or single halos with stellar mass $1\times10^{8} < \msam < 5\times10^{9} \Msun$. 
@@
 
+    \subsubsection{Selecting primaries}
+    Primary galaxies (equivalently, ``primary subhalos") are the most massive galaxy of their group, i.e., each group can have at most one primary galaxy.  
+    We perform mass cuts on the stellar mass of the primary to define our sample of dwarf primaries and massive primaries.
+Each stellar mass realization is treated independently, such that the primary of a group may change between stellar mass realizations.
+Additionally, some groups may not have a ``primary" in one realization, but will in others.
+
+    For each stellar mass realization, we rank order the subhalos of each group by stellar mass, then perform a mass cut specific to the type of group: dwarf primaries from dwarf mass groups, and massive primaries from massive mass groups (see Sec.~\ref{sec:methods-halos} for group mass criteria).
+    We define the stellar mass range for dwarf primaries and massive primaries as:
+    \begin{align*} 
+    \mbox{\textbf{dwarf primaries:}}&\, 1\times 10^{8}< \rm M_{*} < 5\times10^{9}\Msun \\ 
+    \mbox{\textbf{massive primaries:}}&\, 5\times 10^{9}< \rm M_{*} < 1\times 10^{11}\Msun
+    \end{align*}
+    The stellar mass criteria is fixed, and does not change as a function of redshift. 
+    The median number of primaries in a single stellar mass realization at $z=0$ is XX dwarf primaries and XX massive primaries (see Sec.~\ref{sec:methods-props} for more info). 
+    This range was chosen to replicate a set of pairs with masses similar to LMC+SMC and MW-M31 mass pairs.
+The abundance matching prescription has a spread of $\sim 1$dex at $M_{h}\sim 10^{10}\Msun$, thus the set of selected primaries in each realization is unique.
+
+    A subhalo will not be selected as a primary if it is not the first most massive halo in the group, i.e., there is no more massive subhalo (by stellar mass) in the group.
+However, since our selection is based on stellar mass, and there is a large spread in the SMHM relation, the most massive object by stellar mass may not be the most massive subhalo in terms of subhalo mass.
+    This is by design, since our selection criteria are meant to roughly align with observational pair selection criteria which use the stellar mass ratio between the primary and companion to define a major or minor pair, rather than the DM halo mass.
+
+    Additional cases:
     \begin{itemize}
-        \item what types of pairs are we looking for? 
-        \item why do we pick the mass range we are looking at?
-        \item how do we pick out the groups we'll use (group crit)
+        \item In the case that a group hosts no galaxy in this stellar mass range in any realization, the group is removed from the sample. 
+        \item If a subhalo passes the stellar mass cut for a primary, but does not have an associated companion from the selection criteria for a secondary (see next subsection), the subhalo will still be considered a primary.
+We refer to all primaries without companions as ``isolated primaries."
+        \item If the most massive object by stellar mass is more or less massive than our 
     \end{itemize}
-    \subsubsection{Selecting primaries}
-            \begin{itemize}
-                \item definition of prims
-                \item how we use single-halo groups. 
-            \end{itemize}
-    \subsubsection{Selecting companions}
+
+    \subsubsection{Selecting secondary companions}
+    The secondary companion galaxies are selected via their stellar mass ratio
+    The second most massive galaxy by stellar mass in each group is then used
+
+    \begin{align*} 
+    \mbox{\textbf{major pair:}}&\, \frac{1}{4}\leq \frac{\rm M_{*,2}}{\rm M_{*,1}}< 1 \\ 
+    \mbox{\textbf{minor pair:}}&\, \frac{1}{10}\leq \frac{\rm M_{*,2}}{\rm M_{*,1}} < \frac{1}{4}\Msun
+    \end{align*}
+
+    Note that in this selection routine, the LMC+SMC pair would not be selected, as they are a system of satellites in a massive group.
+Rather, the MW-M31 pair would be selected and identified as a ``massive major pair."
+
             \begin{itemize}

### 2023-03-22 paper/pears.tex
finished draft of end of methods and started definitions section

@@
     The full pair sample is constructed from the set of all subhalos and their abundance matching realizations.
-Each pair will consist of a ``primary," the more massive object, and a ``secondary," which is the less massive companion.
+Each pair will consist of a ``primary" more massive object, and a ``secondary" less massive companion.
 
@@
 
-    \begin{itemize}
-    \item what types of pairs are we looking for? 
-    \item why do we pick the mass range we are looking at?
-    \end{itemize}
+    %%% 
+    % begin subsubsection
+    \subsubsection{Selecting primaries}
+    Primary galaxies (equivalently, ``primary subhalos") are the most massive galaxy of their group by stellar mass. Thus, each group can have at most one primary galaxy.
 
-% \begin{enumerate}
-%   \item Select dwarf primaries: for full catalog, most massive halo (in "pairs") or single halos with stellar mass $1\times10^{8} < \msam < 5\times10^{9} \Msun$. 
-%   \item Select dwarf pairs: for full pair catalog, any pair with stellar mass ratio between 1-1/4 (major pairs) or between 1/4-1/10 (minor pairs).
-All pairs is the union of these two sets.
-Any pair or single halo that is outside of these two sets is an "unpaired" halo.
-Note that unpaired can still have very minor companions.
-% \end{enumerate}
-
-    \subsubsection{Selecting primaries}
-    Primary galaxies (equivalently, ``primary subhalos") are the most massive galaxy of their group, i.e., each group can have at most one primary galaxy.  
     We perform mass cuts on the stellar mass of the primary to define our sample of dwarf primaries and massive primaries.
@@
     \mbox{\textbf{dwarf primaries:}}&\, 1\times 10^{8}< \rm M_{*} < 5\times10^{9}\Msun \\ 
-    \mbox{\textbf{massive primaries:}}&\, 5\times 10^{9}< \rm M_{*} < 1\times 10^{11}\Msun
+    \mbox{\textbf{massive primaries:}}&\, 5\times 10^{9}< \rm M_{*} < 1\times 10^{11}\Msun.
     \end{align*}
+
     The stellar mass criteria is fixed, and does not change as a function of redshift. 
     The median number of primaries in a single stellar mass realization at $z=0$ is XX dwarf primaries and XX massive primaries (see Sec.~\ref{sec:methods-props} for more info). 
-    This range was chosen to replicate a set of pairs with masses similar to LMC+SMC and MW-M31 mass pairs.
-The abundance matching prescription has a spread of $\sim 1$dex at $M_{h}\sim 10^{10}\Msun$, thus the set of selected primaries in each realization is unique.
+    The primary stellar mass range is chosen to replicate a set of pairs with masses similar to LMC+SMC and MW-M31.
 
-    A subhalo will not be selected as a primary if it is not the first most massive halo in the group, i.e., there is no more massive subhalo (by stellar mass) in the group.
+    The abundance matching prescription has a spread of $\sim 1$dex at $M_{h}\sim 10^{10}\Msun$~\citep{Moster2013}, thus the set of selected primaries in each realization is typically unique.
+
+    % explain special cases that people might wonder about.
+    A subhalo will not be selected as a primary if it is not the first most massive halo in the group, i.e., there are no subhalos in the group that are more massive than the primary (by stellar mass).
 However, since our selection is based on stellar mass, and there is a large spread in the SMHM relation, the most massive object by stellar mass may not be the most massive subhalo in terms of subhalo mass.
-    This is by design, since our selection criteria are meant to roughly align with observational pair selection criteria which use the stellar mass ratio between the primary and companion to define a major or minor pair, rather than the DM halo mass.
+    This is by design, since our selection criteria are meant to more closely replicate observational pair selection criteria which use the stellar mass ratio between the primary and companion to define a major or minor pair, rather than the DM halo mass.
 
-    Additional cases:
-    \begin{itemize}
-        \item In the case that a group hosts no galaxy in this stellar mass range in any realization, the group is removed from the sample. 
-        \item If a subhalo passes the stellar mass cut for a primary, but does not have an associated companion from the selection criteria for a secondary (see next subsection), the subhalo will still be considered a primary.
+    If a subhalo passes the stellar mass cut for a primary, but does not have an associated companion from the selection criteria for a secondary (see next subsection), the subhalo will still be considered a primary.
 We refer to all primaries without companions as ``isolated primaries."
-        \item If the most massive object by stellar mass is more or less massive than our 
-    \end{itemize}
+    The total set of primaries includes both paired primaries and isolated primaries.
+    % end  primary subsubsection
+    %%%
 
+    %%% 
+    % begin secondary subsubsection
     \subsubsection{Selecting secondary companions}
-    The secondary companion galaxies are selected via their stellar mass ratio
-    The second most massive galaxy by stellar mass in each group is then used
+    The second most massive galaxy by stellar mass in each group is then used to define the secondary companions for each primary. 
+    As before, the selection of secondary companions occurs independently for each stellar mass realization, and for each snapshot, such that we collect 1000 different sets of pairs for each redshift.
 
+    We create two categories of pairs: 
+    major pairs and minor pairs, such that the secondary companion galaxies are selected via the stellar mass ratio between the secondary and primary.     
+    Since we have already rank ordered the halos in each stellar mass realization by their stellar mass, the stellar mass ratio will never exceed 1.   
+    The stellar mass ratio criteria for major and minor pairs are:
     \begin{align*} 
-    \mbox{\textbf{major pair:}}&\, \frac{1}{4}\leq \frac{\rm M_{*,2}}{\rm M_{*,1}}< 1 \\ 
-    \mbox{\textbf{minor pair:}}&\, \frac{1}{10}\leq \frac{\rm M_{*,2}}{\rm M_{*,1}} < \frac{1}{4}\Msun
+    \mbox{\textbf{major pair:}}&\, \frac{1}{4}\leq \frac{\rm M_{*2}}{\rm M_{*1}}< 1 \\ 
+    \mbox{\textbf{minor pair:}}&\, \frac{1}{10}\leq \frac{\rm M_{*2}}{\rm M_{*1}} < \frac{1}{4}
     \end{align*}
+    In addition, we require that each pair have a minimum separation of $15\kpc$ between the primary and secondary, which is XX times the smoothing length of the simulation. 
+    At smaller separations, more and more mass will be attributed to the central subhalo, which can lead to confusion in the merger tree histories. \kc{fix the wording here}.
+
+    If a primary subhalo does not have a companion that meets the stellar mass ratio criteria, separation criteria, or lower subhalo mass criteria (see Sec.~\ref{sec:methods-halos}), the subhalo will still be considered a primary.
+    We refer to all primaries without companions as ``isolated primaries."
 
@@
 Rather, the MW-M31 pair would be selected and identified as a ``massive major pair."
-
-            \begin{itemize}
-                \item companions selected by mass ratio
-                \item explain pairing method for each realization
-                \item minimum separation of 15kpc so that we can be more confident about the mass associated with each halo (at smaller seps, more mass will be attributed to the central, also though why we use the stellar mass associated with the max mass isntead of the current mass)
-            \end{itemize}
+    % end secondary subsubsection
+    %%%
 
@@
 
-\subsection{Overview of pair properties} \label{sec:methods-props}
-    \begin{itemize}
-        \item what are properties of our sample?
-    \end{itemize}
-    \subsubsection{Description of counts plot}
-            \begin{itemize}
-                \item general behavior of dwarf primaries
-                \item general behavior of dwarf pairs
-                \item general behavior of massive prims
-                \item general behavior of massive pairs
-                \item brief explanation of bottom panel
-            \end{itemize}
-    \subsubsection{Description of stellar mass ratio plot}
-            \begin{itemize}
-                \item what is being shown?
-                \item what is the general behavior?
-                \item comparison: dwarfs vs. massive galaxies 
-                \item comparison: major vs. minor pairs
-            \end{itemize}
+%%%%%%%%%%%%%%%%%%%%
+% Pair prop. start %
+    \subsection{Overview of selected pair sample} \label{sec:methods-props}
+        The full pair sample contains 1000 individual sets of pairs at each snapshot, for all 100 snapshots of the \tng100-1 simulation. 
+        For each snapshot, we calculate the median number of primaries and pairs in each of the 1000 stellar mass realizations. 
+        The data shown is the median and 1-99\% range of the set of medians from the realizations.
 
-\subsection{Analysis method/defs} \label{sec:methods-analysis}
-    \begin{itemize}
-        \item Pair fractions
-        \item separations
-        \item velocities
-        \item scaled units
-        \item data presented (median def and spread)
-    \end{itemize}
+        Fig.~\ref{fig:counts} shows the redshift evolution of the number of dwarf and massive primaries and pairs we identify over the redshift range $z=0-4$. 
+        The number of identified primaries is smallest at $z=4$, and rises to a maximum around $z=1$ for both dwarf and massive primaries.        
+        There are approximately 8 times as many dwarf primaries as massive primaries.
 
-\subsection{Table}
-Table should include the median number of primaries and of pairs (major and minor) at a variety of redshifts.
+        The dwarf primary count (green solid line in top left panel) reaches a maximum median of $\sim15000$ halos (in one realization) at $z\sim0.6$, then decreases by $\sim16\%$ to 12000 halos at $z=0$.
+        The dwarf pair count (green dashed line) peaks much earlier at $z\sim2$ with $\sim3000$ pairs, and decreases to $\sim1000$ pairs at $z=0$.
+        The massive primary count (pink solid line in top right panel) reaches a maximum median of $\sim2000$ halos (in one realization) at $z\sim1$, then remains approximately constant to $z=0$. 
+        The pair count for massive galaxies (pink dashed line) behaves similarly to the primary count, increasing from $z=4$ to $z\sim1$, then leveling off to $z=0$.
 
-%%%%%%%%%%%
-%%%%%%%%%%%
-% \subsection{Simulation details}
-% % what is it that we are trying to study? why use illustris?
-% To understand the occurance rate and separations of typical galaxy pairs in a cosmological context, we require a simulation that provides a large statistical sample of pairs in both the dwarf and massive galaxy regime.
-% Thus, we are limited in our simulation choice to large-volume cosmological simulations. 
-% However, we also require high resolution simulations such that the dwarf subhalos are resolved well enough to ensure robust statistics at the low mass end, and so we are not limited by our inability to resolve objects down to halo masses of $M_{\rm halo}\approx1\times 10^9\, \Msun$.
+        The bottom panel of Fig.~\ref{fig:counts} shows the number of pairs divided by the number of primaries, or the fraction of pairs per primary as a function of redshift. 
+        Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$.
+The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.
 
-% \subsubsection{Error calculations}\label{sec:methods-err}
+        We show the distribution of stellar mass ratios between the secondary and primary of each dwarf and massive pair in Fig.~\ref{fig:massratio}.
+        % Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.
+        In general, the shape of the distribution remains constant from $z=0-4$ for both dwarfs and massive pairs, and between the dwarf and massive pairs at each redshift. 
+        Thus, the typical stellar mass ratio of pairs in our sample is independent of mass scale and of redshift.
 
-%%%%%%%%%%%
-%%%%%%%%%%%
-% \subsection{Selection criteria}
-% In this section, we outline the selection criteria used to select dwarf and massive subhalo pairs. 
-% The same selection criteria is utilized for all four simulations (\illd, \illh, \tngd, and \tngh)
-% In short, blah. 
-% Detailed steps are as follows.
+% Pair prop. end %
+%%%%%%%%%%%%%%%%%%
 
-% \subsubsection{Isolation}
-% As we are interested in the frequency and kinematics of galaxy pairs that are undisturbed by nearby massive perturbers, we select subhalo pairs as the most massive subhalos of their group halos. 
-% We have confirmed that nearly 100\% of the the most massive subhalos in each group are outside of the Hill radius of any nearby subhalo with greater mass, and are thus a rough isolation criteria is inherent in our selection.
-
-% \textbf{Definitions:} each of these defines the subhalo at a single snapshot and for a single realization.
-% \begin{itemize}
-%   \item Primary - Most massive subhalo in a group by stellar mass
-%   \item Secondary - 
-%   \item Major pair - A pair of subhalos consisting of a primary and secondary with stellar mass ratio $1/4 < \rm M_{*,sec}/M_{*, prim} < 1$
-%   \item Minor pair - A pair of subhalos consisting of a primary and secondary with stellar mass ratio $1/10 < \rm M_{*,sec}/M_{*, prim} < 1/4$
-% \end{itemize}
-% Note that the subhalo that is assigned as primary or secondary may change between stellar mass realizations.
-Also note\kc{that this method may yield pairs where the secondary has a higher subhalo mass than the primary.
-This one happens ~XX\% of the time.}
-
-% methods plots
+%%%%%%%%%%%%%%%%%%%%%%
+% begin method plots %
   \begin{figure*}[htp]
@@
     % dwarf galaxies
-    The dwarf primary count (green solid line in top left panel) is at a minimum at $z=4$, rises to a maximum of $\sim15000$ halos per realization by $z=1$, then decreases by $\sim16\%$ to 12000 halos at $z=0$.
-The dwarf pair count (green dashed line), on the other hand, peaks at $z\sim2$ with 3000 pairs, and decreases to a minimum of about 1000 pairs at $z=0$.
+    The dwarf primary count (solid) is at a minimum at $z=4$, rises to a maximum by $z\sim1$, then decreases from $z=1\to0$. 
+    The dwarf pair count (dashed) peaks at $z\sim2$.
     % Massive galaxies (right)
@@
 
-\begin{table*}[htb]
-  \centering
-    \begin{tabular}{lcc}
-     & Dwarf Pairs & Massive Pairs \\\hline\hline
-    % Group Mass & $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ & $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$  \\
-    % Subhalo Max Mass &  &  \\
-    % Subhalo Current Mass & $>1\times10^{10} \Msun$ & $> 5\times10^{11} \Msun$ \\
-    Primary &$1\times10^{8} < \msam < 5\times10^{9} \Msun$ & $5\times10^{9} < \msam < 1\times10^{11} \Msun$\\\hline
-    \end{tabular}
-    \caption{\label{table:mass}Selection criteria for dwarf and massive pairs.}
-    \end{table*}
+% end method plots %  
+%%%%%%%%%%%%%%%%%%%%%%
+
+% \begin{table*}[htb]
+%   \centering
+%     \begin{tabular}{lcc}
+%      & Dwarf Pairs & Massive Pairs \\\hline\hline
+%     % Group Mass & $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ & $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$  \\
+%     % Subhalo Max Mass &  &  \\
+%     % Subhalo Current Mass & $>1\times10^{10} \Msun$ & $> 5\times10^{11} \Msun$ \\
+%     Primary &$1\times10^{8} < \msam < 5\times10^{9} \Msun$ & $5\times10^{9} < \msam < 1\times10^{11} \Msun$\\\hline
+%     \end{tabular}
+%     \caption{\label{table:mass}Selection criteria for dwarf and massive pairs.}
+%     \end{table*}
 
 % equivalent snapshot table
-\begin{table*}[tbp]
-  \centering
-  \begin{tabular}{l|cc|cccc} % increase this to 7 columns
-    \hline \hline
-   & \multicolumn{2}{c|}{Snapshot number} & \multicolumn{4}{c}{Number of primaries}\\
-   & \ill & \tng  & \illd & \illh & \tngd & \tngh \\ 
-  \hline
-  z = 0   &   135  &   99   & $11431.5_{-24.42}^{68.38}$ & $12650.0_{-25.84}^{46.84}$ & $13255.0_{-32.60}^{56.72}$ & $12035.0_{-69.24}^{20.36}$\\
-  z = 1   &   85   &   50   &  $14769.0_{-30.24}^{47.28}$ & $16568.0_{-32.20}^{69.60}$ & $17445.5_{-40.86}^{51.90}$ & $15946.5_{-59.38}^{39.22}$ \\
-  z = 2   &   68   &   33   &  $12602.5_{-31.98}^{45.94}$ & $14174.0_{-12.48}^{62.32}$ & $15413.5_{-34.62}^{28.86}$ & $14334.0_{-29.44}^{45.24}$ \\
-  z = 3   &   60   &   25   &     $8533.5_{-54.50}^{39.46}$ & $9390.0_{-63.40}^{41.32}$ & $10901.0_{-44.64}^{46.56}$ & $10106.5_{-47.90}^{39.74}$  \\
-  % z = 3.7   &   54   &   21   \\
-  \hline \hline
-  \end{tabular}
-  \caption{\label{tab:equiv-snapshot} The snapshot number of the original \ill\ and the \tng\ simulations at redshifts $z=0-3$, as well as the median number dwarf (massive) primaries that were selected with $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$ ($5\times 10^{9} < \msam < 1\times 10^{11} \rm M_\odot$) in XX abundance matching realizations.
+% \begin{table*}[tbp]
+%   \centering
+%   \begin{tabular}{l|cc|cccc} % increase this to 7 columns
+%     \hline \hline
+%    & {Snapshot} & {Number of primaries} & {Number of pairs}\\
+%    & \ill & \tng  & \illd & \illh & \tngd & \tngh \\ 
+%   \hline
+%   z = 0   &   135  &   99   & $11431.5_{-24.42}^{68.38}$ & $12650.0_{-25.84}^{46.84}$ & $13255.0_{-32.60}^{56.72}$ & $12035.0_{-69.24}^{20.36}$\\
+%   z = 1   &   85   &   50   &  $14769.0_{-30.24}^{47.28}$ & $16568.0_{-32.20}^{69.60}$ & $17445.5_{-40.86}^{51.90}$ & $15946.5_{-59.38}^{39.22}$ \\
+%   z = 2   &   68   &   33   &  $12602.5_{-31.98}^{45.94}$ & $14174.0_{-12.48}^{62.32}$ & $15413.5_{-34.62}^{28.86}$ & $14334.0_{-29.44}^{45.24}$ \\
+%   z = 3   &   60   &   25   &     $8533.5_{-54.50}^{39.46}$ & $9390.0_{-63.40}^{41.32}$ & $10901.0_{-44.64}^{46.56}$ & $10106.5_{-47.90}^{39.74}$  \\
+%   % z = 3.7   &   54   &   21   \\
+%   \hline \hline
+%   \end{tabular}
+%   \caption{\label{tab:equiv-snapshot} The snapshot number of the original \ill\ and the \tng\ simulations at redshifts $z=0-3$, as well as the median number dwarf (massive) primaries that were selected with $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$ ($5\times 10^{9} < \msam < 1\times 10^{11} \rm M_\odot$) in XX abundance matching realizations.
 \kc{fill in with numbers after doing more realizations} \kc{include takeaway}}
-  \end{table*}
+%   \end{table*}
 
@@
 \section{Results}
-We collect dwarf pairs and massive pairs at all snapshots from the TNG100-1 simulation and analyze the occurrence rate and kinematic behavior of the pairs across cosmic time. 
-At each snapshot, we generate 1000 different realizations of the pair catalog, where each realization represents one instance of the abundance matching technique to assign stellar masses to dark matter halos (see methods).
-In each of the following plots, the median and a percentile spread each value are calculated by finding the median from each of the 1000 AM realizations, and taking the median and spread of that set of median values (see Sec.~\ref{sec:methods-err} for more detail).
+We collect dwarf pairs and massive pairs at all snapshots from the TNG100-1 simulation. 
+We analyze the occurrence rate and kinematic behavior of the pairs across cosmic time, and ....
 
+In Sec.~\ref{sec:results-defs}, we define each of the parameters we will be considering and provide a brief explanation of how we calculate the data we show \kc{oof help}.
 In Sec.~\ref{sec:results-frac}, we show the redshift evolution of the fraction of primaries with a major or minor companion (the ``pair fraction") and compare dwarf pairs and massive pairs.
@@
 In Sec.~\ref{sec:results-scaled}, we compare the ``scaled" separations and velocities of dwarf and massive pairs.
+
+%%%%%%%%%%%%%%%%%%%%%   
+% Definitions start %
+\subsection{Definitions} \label{sec:results-defs}
+    The pair sample consists of 1000 sets of pairs at each snapshot, each set representing a different realization of the abundance matching prescription. 
+    In each of the following plots, the median and a percentile spread each value are calculated by finding the median from each of the 1000 AM realizations, and taking the median and spread of that set of median values.
+
+    \begin{itemize}
+        \item[-] \textbf{Pair fractions:} the major pair fraction is the ratio of the number of major pairs to the total number of primaries (isolated + paired). 
+        The minor pair fraction is defined in a similar way.
+
+        \item[-] \textbf{Separations:} pair separations are defined as the relative separation between the primary and secondary of each pair. 
+        Pair separations are computed in physical units, not comoving.
+
+        \item[-] \textbf{Velocities:} relative velocities are defined as the relative velocity difference between the primary and secondary of each pair. 
+        This can be interpreted as the velocity of a secondary with respect to a stationary primary. 
+        Relative velocities are computed in physical $\kms$.
+
+        \item[-] \textbf{Scaled velocities and separations:} scaled
+
+        \item data presented (median def and spread)
+
+    \end{itemize}
+
+% Definitions end %
+%%%%%%%%%%%%%%%%%%%
 
@@
     % Top plots ~
-    (Top) Median pair fraction, defined as the fraction of dwarf or massive primaries with a major (left) or minor (right) companion by stellar mass (see Sec.~\ref{sec:methods-crit}). 
+    (Top) Median pair fraction, defined as the fraction of dwarf or massive primaries with a major (left) or minor (right) companion by stellar mass (see Sec.~\ref{sec:methods-pairs}). 
     Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
@@
 In this section, we compute the median relative separations and velocities of all 1000 realizations of dwarf and massive pairs, and show their behavior as a function of redshift.
-We separate the population of pairs into "major" and "minor" pairs (as defined in Sec.~\ref{sec:methods-crit-pairs}) to show how the stellar mass ratio between the primary and secondary may affect the kinematics.
+We separate the population of pairs into "major" and "minor" pairs (as defined in Sec.~\ref{sec:methods-pairs}) to show how the stellar mass ratio between the primary and secondary may affect the kinematics.
 
@@
     We calculate the median relative separations between the primary and secondary halos of the pairs identified in our dwarf pair sample and massive pair sample. 
-    We split the results by the stellar mass ratio of each pair, dividing the sample into "major" pairs and minor pairs, which allows us to compare the behavior of different mass ratio systems individually in the dwarf and massive mass range (see details for pair collecting in Sec.~\ref{deets}).
+    We split the results by the stellar mass ratio of each pair, dividing the sample into "major" pairs and minor pairs, which allows us to compare the behavior of different mass ratio systems individually in the dwarf and massive mass range.
     Our results are collected in Fig.~\ref{fig:sep}, which shows the redshift evolution of the median relative separations for dwarf pairs and massive pairs.

### 2023-05-15 paper/pears.tex

@@
  \section{Methodology}\label{sec:methods}
-We aim to quantify and characterize the frequency (or occurrence rate) and bulk kinematic properties of galaxy pairs in a cosmologically consistent way a function of cosmic time. 
-In particular, we study dwarf galaxy pairs and massive galaxy pairs that are of similar stellar and halo mass to a variety of pairs in the Local Group. 
+We aim to quantify and characterize the frequency (or occurrence rate) and bulk kinematic properties of galaxy pairs in a cosmologically consistent way as a function of cosmic time. 
+In particular, we study dwarf galaxy pairs and massive galaxy pairs that are of similar stellar and halo mass to a variety of galaxy pairs in the Local Group. 
 We categorize these pairs into one of four pair types: massive major pairs, such as the MW+M31; massive minor pairs, such as M31+M33 or MW+LMC; dwarf major pairs, such as M33+LMC; and finally, dwarf minor pairs, such as the LMC+SMC.
@@
 Sec.~\ref{sec:methods-pairs} describes the second set of selection criteria we apply to obtain the full sample of pairs.
-In Sec.~\ref{sec:methods-props}, we show some of the properties of our entire pair sample, including the total number of pairs and stellar mass ratios.
-Finally, Sec.~\ref{sec:methods-analysis} gives an overview of our analysis methods and a description of the parameters of interest in this study.
+Finally, Sec.~\ref{sec:pairprops} details some of the properties of our entire pair sample, including the total number of pairs and stellar mass ratios.
 
@@
         % Brief description of TNG hydro and which run we use.
-    The \tng\ project ~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} consists of a suite of dark-matter-only $N$-body as well as full physics cosmological simulations consistent with the \textit{Planck2015} \lcdm/  cosmology~\citep{Planck2015}.
+    The \tng\ project ~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} consists of a suite of dark-matter-only $N$-body as well as full physics cosmological simulations consistent with the \textit{Planck2015} \lcdm\  cosmology~\citep{Planck2015}.
     In this study we utilize data from the main high resolution full physics run of the (110.7\Mpc)$^3$ volume simulation, \textsl{TNG100-1}, which includes dark matter and baryonic particles and follows the evolution of $1820^3$ dark matter particles in 100 snapshots from $z=127$ to $z=0$.
@@
     We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm~\citep{springel2001,dolag09}. 
-    These catalogs consist of halos , defined using the Friends-of-Friends (FoF) algorithm~\citep{davis1985} to link nearby particles, and their associated subhalos, which are over-dense and gravitationally bound dark matter structures compared to the background.
+    These catalogs consist of halos, defined using the Friends-of-Friends (FoF) algorithm~\citep{davis1985} to link nearby particles, and their associated subhalos, which are over-dense and gravitationally bound dark matter structures compared to the background.
 (From here, we will refer to FoF halos as "groups" and their subhalos as )
@@
     We define the group mass range for dwarf groups as $8\times 10^{10} < M_{G,d} < 5\times 10^{11}\Msun$, which will host mass analogs of the LMC+SMC and LMC+M33 pairs. 
-    Massive group a massive group mass range from $1\times10^{12} < M_{G,m} < 6.5\times10^{12}$, which at the lower mass end will host MW+LMC pairs, and MW+M31 pairs at the higher mass end. 
+    Massive groups range from $1\times10^{12} < M_{G,m} < 6.5\times10^{12}$, which at the lower mass end will host MW+LMC pairs, and MW+M31 pairs at the higher mass end. 
     The group mass criteria is fixed for all redshifts, so at high z, the dwarf pairs we select may be the progenitors of higher mass systems at $z=0$.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%    
-% Choosing halos section %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    
+% Abundance matching section %
     \subsection{Abundance matching} \label{sec:methods-am}
@@
     Additionally, the SAGA survey has found that large satellites of MW-type galaxies are often very blue, with infall into the halo spurring high rates of star formation due to the large gas fraction in dwarfs~\citep{saga}.
-    Thus, we calculate stellar masses for our subhalos using $M_{\rm peak}$ and the redshift of the current snapshot to calculate the stellar mass of each subhalo, to account for the additional stellar mass that can form after infall.
+    Thus, we calculate stellar masses for our subhalos using $M_{\rm peak}$ and the redshift of the current snapshot to calculate the stellar mass of each subhalo, and to account for the additional stellar mass that can form after infall.
 
@@
     In TNG100-1, the DM particle mass is decreased XX\% compared to the DM particle mass in \tng100-1 Dark to account for the additional mass of baryons, such that the total mass of the halo will remain roughly the same between the dark matter only and hydro simulations.
-    Since the~\citet{Moster2013} AM relation was calibrated using DM subhalos from the \texttt{MilleniumII} dark matter only simulation, we will use the total subhalo mass from the TNG100-1 hydro simulation as a proxy for the corresponding DM halo mass in the TNG100-1 Dark run.
+    Since the~\citet{Moster2013} AM relation was calibrated using DM subhalos from the \texttt{MilleniumII} dark matter only simulation, we will use the total subhalo mass from the TNG100-1 hydro simulation as a proxy for the corresponding DM halo mass in the TNG100-1 Dark run, \texttt{SubhaloMass}.
 
@@
 
-% End choosing halos     %
+% End Abundance matching %
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-    We perform mass cuts on the stellar mass of the primary to define our sample of dwarf primaries and massive primaries.
+        We apply mass cuts on the stellar mass of the primary to define our sample of dwarf primaries and massive primaries.
 Each stellar mass realization is treated independently, such that the primary of a group may change between stellar mass realizations.
@@
         The stellar mass criteria is fixed, and does not change as a function of redshift. 
-    The median number of primaries in a single stellar mass realization at $z=0$ is XX dwarf primaries and XX massive primaries (see Sec.~\ref{sec:methods-props} for more info). 
+        The median number of primaries in a single stellar mass realization at $z=0$ is XX dwarf primaries and XX massive primaries (see Sec.~\ref{sec:pairprops} for more info). 
         The primary stellar mass range is chosen to replicate a set of pairs with masses similar to LMC+SMC and MW-M31.
@@
     %%%     
-
 % Pair selection end %
@@
 
-%%%%%%%%%%%%%%%%%%%%
-% Pair prop. start %
-    \subsection{Overview of selected pair sample} \label{sec:methods-props}
-        The full pair sample contains 1000 individual sets of pairs at each snapshot, for all 100 snapshots of the \tng100-1 simulation. 
-        For each snapshot, we calculate the median number of primaries and pairs in each of the 1000 stellar mass realizations. 
-        The data shown is the median and 1-99\% range of the set of medians from the realizations.
+% Methods end %
+%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%
 
-        Fig.~\ref{fig:counts} shows the redshift evolution of the number of dwarf and massive primaries and pairs we identify over the redshift range $z=0-4$. 
-        The number of identified primaries is smallest at $z=4$, and rises to a maximum around $z=1$ for both dwarf and massive primaries.        
-        There are approximately 8 times as many dwarf primaries as massive primaries.
-
-        The dwarf primary count (green solid line in top left panel) reaches a maximum median of $\sim15000$ halos (in one realization) at $z\sim0.6$, then decreases by $\sim16\%$ to 12000 halos at $z=0$.
-        The dwarf pair count (green dashed line) peaks much earlier at $z\sim2$ with $\sim3000$ pairs, and decreases to $\sim1000$ pairs at $z=0$.
-        The massive primary count (pink solid line in top right panel) reaches a maximum median of $\sim2000$ halos (in one realization) at $z\sim1$, then remains approximately constant to $z=0$. 
-        The pair count for massive galaxies (pink dashed line) behaves similarly to the primary count, increasing from $z=4$ to $z\sim1$, then leveling off to $z=0$.
-
-        The bottom panel of Fig.~\ref{fig:counts} shows the number of pairs divided by the number of primaries, or the fraction of pairs per primary as a function of redshift. 
-        Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$.
-The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.
-
-        We show the distribution of stellar mass ratios between the secondary and primary of each dwarf and massive pair in Fig.~\ref{fig:massratio}.
-        % Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.
-        In general, the shape of the distribution remains constant from $z=0-4$ for both dwarfs and massive pairs, and between the dwarf and massive pairs at each redshift. 
-        Thus, the typical stellar mass ratio of pairs in our sample is independent of mass scale and of redshift.
-
-% Pair prop. end %
-%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%
-% begin method plots %
-  \begin{figure*}[htp]
+%%%%%%%%%%%%%%%%%%%%%%%%%
+% begin pair prop plots %  
+\begin{figure*}[htb]
     \centering
@@
 
-  \begin{figure*}[htp]
+\begin{figure*}[htb]
     \centering
@@
 \end{figure*}
+% end pair prop plots %  
+%%%%%%%%%%%%%%%%%%%%%%%
 
-% end method plots %  
-%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%
+% Pair prop. start %
+\section{Sample: Overview of pair properties} \label{sec:pairprops}
+    The full pair sample contains 1000 individual sets of pairs at each snapshot, for all 100 snapshots of the \tng100-1 simulation. 
+    For each snapshot, we calculate the median number of primaries and pairs in each of the 1000 stellar mass realizations. 
+    The data shown is the median and 1-99\% range of the set of medians from the realizations.
+
+    Fig.~\ref{fig:counts} shows the redshift evolution of the number of dwarf and massive primaries and pairs we identify over the redshift range $z=0-4$. 
+    The number of identified primaries is smallest at $z=4$, and rises to a maximum around $z=1$ for both dwarf and massive primaries.        
+    There are approximately 8 times as many dwarf primaries as massive primaries.
+
+    The dwarf primary count (green solid line in top left panel) reaches a maximum median of $\sim15000$ halos (in one realization) at $z\sim0.6$, then decreases by $\sim16\%$ to 12000 halos at $z=0$.
+    The dwarf pair count (green dashed line) peaks much earlier at $z\sim2$ with $\sim3000$ pairs, and decreases to $\sim1000$ pairs at $z=0$.
+    From $z=4$ to $z=2$, the number of dwarf primaries doubles, as does the number of pairs due to the growth of structures over cosmic time.
+    The massive primary count (pink solid line in top right panel) reaches a maximum median of $\sim2000$ halos (in one realization) at $z\sim1$, then remains approximately constant to $z=0$. 
+    The pair count for massive galaxies (pink dashed line) behaves similarly to the primary count, increasing from $z=4$ to $z\sim1$, then leveling off to $z=0$.
+
+    The bottom panel of Fig.~\ref{fig:counts} shows the number of pairs divided by the number of primaries, or the fraction of pairs per primary as a function of redshift. 
+    Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$.
+The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.
+
+    We show the distribution of stellar mass ratios between the secondary and primary of each dwarf and massive pair in Fig.~\ref{fig:massratio}.
+    % Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.
+    In general, the shape of the distribution remains constant from $z=0-4$ for both dwarfs and massive pairs, and between the dwarf and massive pairs at each redshift. 
+    Thus, the typical stellar mass ratio of pairs in our sample is independent of mass scale and of redshift.
+
+% Pair prop. end %
+%%%%%%%%%%%%%%%%%%
 
@@
 
-% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %
-\section{Results}
-We collect dwarf pairs and massive pairs at all snapshots from the TNG100-1 simulation. 
-We analyze the occurrence rate and kinematic behavior of the pairs across cosmic time, and ....
+%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%
+% Begin Results section %
 
-In Sec.~\ref{sec:results-defs}, we define each of the parameters we will be considering and provide a brief explanation of how we calculate the data we show \kc{oof help}.
+\section{Results: The frequency and kinematics of dwarf and massive pairs}
+We collect dwarf pairs and massive pairs at all snapshots from the TNG100-1 simulation and analyze the occurrence rate for major and minor pair types across cosmic time.
+We also analyze the kinematic behavior of pairs on a snapshot by snapshot basis, and determine how the bulk kinematics of the different pair populations differ, as well as how they change over time.
+
+The pair sample consists of 1000 sets of pairs at each snapshot, each set representing a different realization of the abundance matching prescription. 
+At each snapshot, we calculate the median occurrence rate and kinematic values for each of the 1000 realizations. 
+Each of the following plots shows the parameter's median and percentile spread calculated from the set of 1000 medians from each realization.
+
 In Sec.~\ref{sec:results-frac}, we show the redshift evolution of the fraction of primaries with a major or minor companion (the ``pair fraction") and compare dwarf pairs and massive pairs.
@@
 % Definitions start %
-\subsection{Definitions} \label{sec:results-defs}
-    The pair sample consists of 1000 sets of pairs at each snapshot, each set representing a different realization of the abundance matching prescription. 
-    In each of the following plots, the median and a percentile spread each value are calculated by finding the median from each of the 1000 AM realizations, and taking the median and spread of that set of median values.
-
-    \begin{itemize}
-        \item[-] \textbf{Pair fractions:} the major pair fraction is the ratio of the number of major pairs to the total number of primaries (isolated + paired). 
-        The minor pair fraction is defined in a similar way.
-
-        \item[-] \textbf{Separations:} pair separations are defined as the relative separation between the primary and secondary of each pair. 
-        Pair separations are computed in physical units, not comoving.
-
-        \item[-] \textbf{Velocities:} relative velocities are defined as the relative velocity difference between the primary and secondary of each pair. 
-        This can be interpreted as the velocity of a secondary with respect to a stationary primary. 
-        Relative velocities are computed in physical $\kms$.
-
-        \item[-] \textbf{Scaled velocities and separations:} scaled
-
-        \item data presented (median def and spread)
-
-    \end{itemize}
+% \subsection{Definitions} \label{sec:results-defs}
 
@@
     \subsection{Pair fraction}\label{sec:results-frac}
-    % intro to pair frac plot
-The pair fraction is defined here as the fraction of identified dwarf or massive primaries with a major or minor companion (see Sec.~\ref{sec:methods-crit} for more info on selection criteria for major and minor pairs).
+    We determine the occurrence rate of a pair type by calculating the pair fraction. 
+    The pair fraction is defined here as the ratio of the number of pairs to the total number of primaries (isolated + paired):
+    $$\rm \frac{N_{pair-type}}{N_{primaries}}.$$
+    For example, the dwarf major pair fraction is calculated as the number of dwarf major pairs divided by the number of dwarf primaries. 
+    Dwarf minor pair fractions, and massive major and minor pair fractions are defined in the same way. 
+    The pair fraction of dwarf or massive pairs with a major or minor companion gives the likelihood of finding a companion of a certain mass type about a primary identified in the field.
+
     Fig.~\ref{fig:pairratio} shows the pair fractions calculated for massive and dwarf pairs (including both major and minor pairs separately) as a function of time for $z=0-4$. 
-
         % differences between massive and dwarf pairs? 
     The dwarf pair fraction evolves distinctly from that of massive pairs.
-Both major and minor dwarf pair fractions start at their minima at $z=0$, and increase by about 200\% by $z\sim2-2.5$, at which point the pair fractions level off and remain constant from $z=3-4$. 
-The major and minor pair fractions for massive pairs evolve similarly, starting at their maxima at $z=0$, then abruptly declining to $z\sim0.25$, before remaining approximately constant from $z=1-4$ %(see Table~\ref{table:vals} for more precise values of the pair fractions).
+    Dwarf pair fractions (both major and minor) start at their minima at $z=0$, and increase by about 200\% by $z\sim2-2.5$, at which point the pair fractions level off and remain constant from $z=3-4$.
+    On the other hand, massive pair fractions reach their maxima at $z=0$, then abruptly declining to $z\sim0.25$, before remaining approximately constant from $z=1-4$.
 
         % difference panels
-The bottom panel of Fig.~\ref{fig:pairratio} shows the dwarf pair fraction subtracted from the massive pair fraction (labelled ``$\rm M-D$"). 
-The pair fraction difference reaches a maximum at $z=0$ for both major and minor pairs, and declines to $z\sim2-2.5$ at which point the difference levels out close to 0.
+    The bottom panels of Fig.~\ref{fig:pairratio} shows the dwarf pair fraction subtracted from the massive pair fraction (labelled ``$\rm M-D$"). 
+    The pair fraction difference reaches a maximum at $z=0$ for both major and minor pairs, and declines to $z\sim2-2.5$ at which point the difference levels out close to 0, where major dwarf and massive pairs, as well as minor dwarf and massive, are equivalently common.
 
         % differences between major and minor pairs? 
-The median pair fraction for minor pairs (for both dwarf and massive galaxies) is less than that of major pairs of the same mass range at all redshifts.
+    The median pair fraction of minor pairs is less than that of major pairs of the same mass range at all redshifts. 
     This is due to the lower stellar mass ratio limit we put on our pairs. 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%
-% Kinematics section %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% beging Kinematics results %
     \subsection{Kinematic evolution}\label{sec:results-kinematics}
-At each individual snapshot, we find the instantaneous separation and relative velocity of the primary and secondary halo of every pair that was selected in the snapshot. 
-This is done separately for all 1000 different abundance matching realizations at each snapshot, as described in Sec.~\ref{sec:methods-am}, then we explore the properties of the set of median separations and velocities for each realization.
-In this section, we compute the median relative separations and velocities of all 1000 realizations of dwarf and massive pairs, and show their behavior as a function of redshift.
-We separate the population of pairs into "major" and "minor" pairs (as defined in Sec.~\ref{sec:methods-pairs}) to show how the stellar mass ratio between the primary and secondary may affect the kinematics.
+    We also analyze the kinematic behavior of our pair sample as a function of time. 
+    Instantaneous pair separations are defined as the relative separation between the primary and secondary of each pair in the snapshot, and are computed in physical $\kpc$, and \textit{not} in comoving $\kpc/h$.
+    Similarly, relative velocities are defined as the relative velocity difference in the same snapshot between the primary and secondary of each pair, and are computed in physical $\kms$.
+
+    In this section, we compute the median relative separations and velocities of all pairs in each snapshot, each of which includes the set of pairs from 1000 stellar mass realizations.
+    We separate the population of dwarf and massive pairs further into major and minor pairs to show how the stellar mass ratio between the primary and secondary may affect the kinematics.
 
@@
         %% intro to separations & bulk results
-    We calculate the median relative separations between the primary and secondary halos of the pairs identified in our dwarf pair sample and massive pair sample. 
-    We split the results by the stellar mass ratio of each pair, dividing the sample into "major" pairs and minor pairs, which allows us to compare the behavior of different mass ratio systems individually in the dwarf and massive mass range.
-    Our results are collected in Fig.~\ref{fig:sep}, which shows the redshift evolution of the median relative separations for dwarf pairs and massive pairs.
-
+        % We calculate the median relative separations between the primary and secondary halos of the pairs identified in our dwarf pair sample and massive pair sample. 
+        % We split the results by the stellar mass ratio of each pair, dividing the sample into "major" pairs and minor pairs, which allows us to compare the behavior of different mass ratio systems individually in the dwarf and massive mass range.
+        Our results are 
+        illustrated in Fig.~\ref{fig:sep}, which shows the redshift evolution of the median relative separations for dwarf pairs and massive pairs. 
         %% the behavior of massive and dwarf pairs
@@
         %% intro to velocity & bulk results
-    In addition to the separations between the primary and secondary halos of our pair sample, we also calculate the median relative velocity between the halos of each pair.
-    Once again we split the results into "major" and "minor" pairs for both the dwarf and massive pair sample to get a better understanding of the impact of the mass of the secondary. 
+        % In addition to the separations between the primary and secondary halos of our pair sample, we also calculate the median relative velocity between the halos of each pair.
+        % Once again we split the results into "major" and "minor" pairs for both the dwarf and massive pair sample to get a better understanding of the impact of the mass of the secondary. 
         In Fig.~\ref{fig:vel}, we show the median relative velocity between the primary and secondary halos of dwarf and massive pairs as a function of redshift. 
-    Note that these relative velocities are calculated from the instantaneous velocity of the halos at the snapshot the pair is in (see Sec.~\ref{sec:methods} for more details about our velocity calculations).
-
         %% the behavior of massive and dwarf pairs
-    We find that the median relative velocity between a pair's primary and secondary halo decreases towards lower redshift, regardless of pair type.
+        We find that the median relative velocity of a pair decreases towards lower redshift, regardless of pair type.
         The median velocity of a major dwarf pair decreases linearly from $130$ at $z=4$ to $70\,\kms$ at $z=0$.
@@
         \end{figure*}
+% end kinematic results %        
+%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% scaled results %
+%%%%%%%%%%%%%%%%%%%%%%%%
+% begin scaled results %
     \subsection{Scaled Kinematics}\label{sec:results-scaled}
     %% intro to scaled kin. evolution & bulk results
-In Sec.~\ref{sec:results-kinematics}, we show that the separations and relative velocities of dwarf and massive pairs evolve similarly as a function of redshift. 
+    In the previous section, Sec.~\ref{sec:results-kinematics}, we show that the separations and relative velocities of dwarf and massive pairs evolve similarly as a function of redshift. 
     However, the magnitude of pair separations and velocities are set by the mass scale of the pair. 
@@
 
-To explore the impact of halo growth and mass scale the kinematics pairs, we study the relative separation of a primary and secondary halo scaled by the virial radius of the FoF group (\scsep), and the relative velocity divided by the circular speed of the group at the virial radius (\scvel).
+    To explore the impact of halo growth and mass scale the kinematics pairs, we study the relative separation of a primary and secondary halo scaled by the virial radius of the FoF group, and the relative velocity divided by the circular speed of the group at the virial radius.
+    That is, 
+    $$\rm r_{scaled}=\scsep$$
+    $$\rm v_{scaled}=\scvel$$
+    $$\rm v_{vir}=\sqrt{G M_{vir}/r_{vir}},$$
+    where $\rm r_{vir}$ is the group radius \texttt{Group\_R\_TopHat200} in physical $\kpc$ from the group catalogs, and $\rm M_{vir}$ the total group mass \texttt{Group\_M\_TopHat200} in $\Msun$.
+
     In Fig.~\ref{fig:scaled}, we show the median scaled separation and scaled velocity for dwarf and massive major pairs as a function of time. 
@@
     \end{figure*} 
-
-% end kinematics
+% end scaled results %
 %%%%%%%%%%%%%%%%%%%%%%
 
+% end kinematics %
+%%%%%%%%%%%%%%%%%%
+
+% end Results section%
 %%%%%%%%%%%%%%%%%%%%%%
-% Discussion section %
-\pagebreak
+%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Begin Discussion section %
 \section{Discussion}\label{sec:discussion}
+\subsection{Implications for the differences in pair fractions of dwarf and massive pairs}
+In Sec.~\ref{sec:results-frac}, we presented the pair fraction of massive and dwarf galaxy pairs and found that the relative frequency of the two populations evolve distinctly from $z=0-4$. 
+While the frequency of massive pairs compared to the number of massive primaries is roughly constant and become more common at low redshift, dwarf major and minor pairs become more than 50\% less common at $z=0$ compared to $z=2$.
+Since scaled separations and velocities do not change drastically between dwarf and massive pairs, the difference in the evolution of the pair fractions indicates that the merger processes of each population may proceed differently.
 
-\subsection{Comparison to previous works/literature}
+% One scenario that could explain this behavior is a very rapid merger timescale for dwarf pairs, and a slower merger timescale for massive pairs. 
+% In this case, dwarf pairs will merge quickly after formation, thus depleting the number of dwarf pairs at later times. 
+% Simultaneously, the merged remnant of a dwarf pair is likely to join the population of isolated primaries until star formation finally pushes the stellar mass up into the massive primary regime.
+% The likelihood of a dwarf pair becoming a massive primary with a minor companion is very small, since only XX\% of dwarf pairs have a major tertiary companion. \kc{calculate the number of }
+
+% Alternatively, if the dark matter halo and stellar mass of a dwarf galaxy pair increase enough through cosmic accretion or very minor mergers from $z=4$ to $z=2$, the pair will be reclassified as a massive pair at later times.
+
+For example, dwarf galaxy merger timescales may be significantly shorter than massive galaxy merger timescales, which would deplete the population of dwarf galaxy pairs by low redshift. 
+Additionally, early dwarf galaxy mergers may result in systems that are identified as massive pairs at late times, and massive pairs may grow such that they exceed our mass criteria, thus leading to an apparent overall decrease in the number of pairs.
+The drop in the absolute number of dwarf and massive primaries at low z as shown in Fig.~\ref{fig:counts} indicates that indeed many of these systems leave the mass range specified by our selection criteria between $z=0-1$.
+However, since the number of dwarf primaries is roughly constant between $z=0.5-1.5$, but the number of pairs is still decreasing during this time, this indicates that mergers are occurring during this time, and not yet leaving the mass regime specified.
+In fact, the number of dwarf pairs that are removed from the sample from $z=0$ to $z=2$ is 10 times greater than the total number of massive pairs, indicating that these pairs are not simply accreting matter and moving into the higher mass bin.
+
+\subsection{Comparison to previous pair fraction studies}
+We performed a pair fraction analysis for dwarf and massive galaxy pairs in the TNG100 simulation, utilizing the full 6D position and velocity information that simulations enable. 
+However this means that direct comparison to pair fractions reported from observations is not straight-forward, as observationally selected pairs uniquely suffer from contamination, due to projected pairs, and restrictive separation criteria, that exclude more widely separated pairs.
+Fortunately, a number of previous studies of pair fractions in the Illustris simulations have used lightcones to create mock images of observationally-motivated fields, from which they select pairs in the same fashion that is typically done with observational data.
+These studies select simulated galaxies based on stellar mass, and then use cuts on the projected separation and line of sight velocity difference to select pairs, which permits direct comparison between simulations and observations.
+
+At the low mass end, \citet{Besla2018} quantified dwarf galaxy pair fractions in Illustris-1, both projected and physical pairs, which enabled a direct comparison of the cosmologically-derived pair fractions with an equivalently selected dwarf pair fraction from SDSS.
+The pair selection criteria for dwarf galaxies, here defined as stellar masses\footnote{The stellar masses of galaxies from the Illustris simulations used in \citet{Besla2018} are from the median of the \citet{Moster2013} abundance matching prescription, the same as used in this work, rather than the stellar mass values from the simulations.} from $2\times10^{8} < M_{*} < 5\times10^{9}\,\Msun$, include a projected separation criteria of $r_{p} < 150\,\kpc$ and a relative line-of-sight velocity difference $\Delta v_{\rm los} < 150\,\kms$.
+
+By searching for pairs in a projected space while having access to the true 3D positions and velocities of the galaxies, they quantified the contamination fraction and found that up to $\sim40$\% of identified companions were unrelated but appeared to be close due to projection effects.
+In Illustris, they found that the projected major pair fraction of dwarf galaxies at $z\sim0$ is $f_{p,proj.}\sim0.005-0.012$, while the . \kc{where tf are these numbers from??? }
+The total pair fraction (including all stellar mass ratios) is $0.032\pm0.005$ for the projected mock catalogs, which are consistent with SDSS equivalently-selected pairs, which find a total pair fraction of $0.035\pm0.3$.
+
+However, using the full physical catalogs, they find a lower pair fraction of $0.02\pm0.004$.
+\kc{I *THINK* this is the fraction of TOTAL pairs (N\_1 from the tables)?
+not just major pairs?
+otherwise I don't know how it's different.}
+For comparison, when we modify our pair selection criteria to match those of \citet{Besla2018}, and require a physical separation $r_{\rm sep}< 150\,\kms$ and a 3D relative velocity $\Delta v_{\rm los} < 150\,\kms$, we find a dwarf major pair fraction of XX at $z=0$, which is slightly SKZ than the \citet{Besla2018} results.
+This is/is not surprising because SKZ.
+
+As the behavior of the major pair fraction as a function of primary stellar mass is consistent between the projected mock catalogs and the SDSS catalogs, they conclude that cosmological simulations can be used to reliably constrain observational pair fractions of dwarf mergers across time.
+\kc{across time...
+is this true?}
+Additionally, which projected and physical pair catalogs yield different absolute values of pair fractions, their behavioral trends as a function of mass are nearly identical such that, in terms of trends, projected and physical pair fractions will yield similar results.
+
+% While the study uses projected separations and line of sight velocities, we can assume that the same \textit{trends} are valid for full-6D selected pairs, such that our pair fraction trends can be reasonably compared to those in observations.
+
+Separate studies have analyzed the pair fractions of higher mass galaxies in Illustris simulation. 
+In particular, \citet{snyder2017} created mock catalogs using lightcones in the Illustris-1 simulation to pick pairs in the same fashion as done in observations. 
+Specifically, they consider only major pairs with: $1\times 10^{11}>M_{*,1} >1\times 10^{10.5}Msun$, projected distances between $14\kpc-71\kpc$, and a redshift separation of $\Delta z<0.02(1+z_{pri}$, which corresponds to a velocity separation of $<1.8\time10^4\kms$.
+They find that the major pair fraction for primaries with stellar mass $1\times 10^{10.5-11}Msun$ is constant or decreasing for $z>1$. 
+Additionally, they compared to observational studies \kc{what studies} that selected pairs with stellar mass $(M* > 10^{10.8}\Msun)$, $(10 <d/(kpc h-1) < 30)$, and $(Msec/Mpri > 0.1)$, and found good agreement between the measured pair fractions as a function of redshift.
+Thus, projected pair fractions in the Illustris simulation are likely representative of those found in observations for massive galaxy pairs.
+
+\citet{snyder2023} extended this work to utilize the TNG simulation, and created mock images of extragalactic survey fields mimicking future planned surveys like JADES.
+From the mock images, they calculated the pair fraction for major pairs with projected separations between $5-70 \kpc$ and with redshift separations of $\Delta z< 0.02(1+z)$, and also found flat or decreasing major pair fractions.
+This is in agreement with our work, as our major pair fraction for massive galaxies is approximately constant or decreasing with higher redshift for $z>1$. 
+While we cannot directly compare the values of the pair fractions themselves, as the projected and physical pair separations will yield very different pair fractions as shown in \citet{Besla2018}, we can say that the behavioral trends are the same.
+Pair fractions computed using physical separations do not have to account for contamination due to projection effects, which would increase the inferred pair fraction, however our separation criteria is much less stringent, which would also increase the pair fraction.
+
+% Alejandro's paper connection: studies are finding good agreement between simulations and TNG, as evidenced by this paper.
+They found that TNG simulated images well approximated the morphologies of galaxies in the KIDS survey, although they were a bit more compact and lumpy.
+But this means that there is precedent for using TNG in these kinds of comparisons.
+
+% ? maybe to do: plot with comparison values 
+\subsection{Implications for observational pair selection criteria}
+    %figures
+    %%%%%%%%%%%%%%%%%%%%
+    \begin{figure*}[htp]
+      \centering
+      \includegraphics[width=\textwidth]{sepdist_1000.png}
+      \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right).
+Major pairs are shown as solid lines, while minor pairs are dotted.
+The median separation of each pair type (from Fig.~\ref{fig:sep}) is shown in solid (major) and dotted (minor) vertical black lines.
+      At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively).
+However, at low redshift, the separation distribution tends to spread out more evenly across a large range of separations, thus increasing the median.
+        }
+      \label{fig:sep-dist}
+    \end{figure*}
+    %%%%%%%%%%%%%%%%%%%%
+    %%%%%%%%%%%%%%%%%%%%
+    \begin{figure*}[htp]
+      \centering
+      \includegraphics[width=\textwidth]{frac_selected.png}
+      \caption{ The fraction of total pairs selected with additional separation selection criteria as a function of redshift. 
+        }
+      \label{fig:frac-select}
+    \end{figure*}
+    %%%%%%%%%%%%%%%%%%%%
+
+    % outline
     \begin{itemize}
-    \item our pairs are not projected dist, so represent set of maximum seps/vels possible
-    \item compare to Synder 2022+
-    \item compare to Lotz and Rodriguez Gomez 
+        \item examples of typical pair selection criteria (i.e. <75 kpc, velocity crit, etc.)
+        \item Show how low separation cuts affect pair fractions      
+        \item Sep distribution plot and explanation (text below) 
+        \item Plot of \% of total pairs selected as function of z for different separation criteria (or maybe better is to do total as function of separation, for different redshifts?) 
+        \item What does this mean for JWST and future surveys?
     \end{itemize}
 
-\subsection{Implications for differences in massive and dwarf pair evolution?}
+% text on the separation distribution plot
+Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$, and includes all 1000 AM realizations. 
+For reference, the median at each corresponding redshift from Fig.~\ref{fig:sep} (that is, the median of the medians of each realization) are shown in light black vertical lines.
+Each plot is normalized such that the area under an individual curve is 1.
+    % the redshift evolution
+At $z=4$, all pair types (dwarf and massive, major and minor) have narrow distributions that pile up around 0 $\kpc$\footnote{Note that only pairs with separations $>10\kpc$ are included in this analysis, see Sec.~\ref{sec:methods-crit-pairs}.}, with ranges between $10-150\,\kpc$ for dwarf pairs and $10-300\,\kpc$ for massive pairs.
+The distributions become more and more broad as $z\to0$, where separations range between $\sim10-400\,\kpc$ for dwarf pairs and $\sim10-1000\,\kpc$ for massive pairs.
 
-\subsection{Implications for observational pair definitions}
-    \begin{itemize}
-        \item examples of typical pair selection criteria
-        \item Sep distribution explanation
-        \item Vel. distribution ex.
-        \item quantify \% of pairs > current cuts
+Since the distribution of separations changes dramatically from $z=4$ to $z=0$, the population of low separation pairs that are selected at $z=4$ includes the majority of true pairs, but this is not the case at low z.
+At low z, separation criteria must be very broad to encompass the majority of pairs. 
+Figure~\ref{fig:frac-select} shows the fraction of pairs that have separations less than $\{50, 75, 100, 150\}\kpc$.
+At high redshift ($z\sim2-4$) a majority of pairs are included in the selection, however at lower redshift ($z\sim0-1$), the pair completeness decreases substantially, with fewer than XX\% of the total number pairs for XX separation criteria.
 
-    \end{itemize}
-
-\subsection{Low separation implications for JWST and other wide and deep surveys}
-
-\subsection{Limitations of our methods}
-\pagebreak
-% Mean separation fig. --
-
-% Separation dist fig. -- The number of widely separated pairs at low redshift is much greater than at high redshift, so these pairs either form late, or move apart from each other.
-
-% Also note than many of the close pairs at high z may merge by $z=0$.
-
-% \subsection{Massive pairs vs. Dwarf pairs}
-% Pair ratio fig.
--- The vast difference between the dwarf and massive pair fractions suggests \todo{XX - that pairs at different mass scales evolve differently ?
-Thus, can't just assume a massive pair fraction for a lower mass regime}
-
-% \subsection{Dwarf and massive pair kinematic differences}
-
-% \subsection{Comparison to literature}
-
-% \subsection{Implications for observations}
-
-% \subsection{Implications for observational pair selection criteria}
-% %% text on separation distribution plot
-% Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$, and includes all 1000 AM realizations. 
-% For reference, the median at each corresponding redshift from Fig.~\ref{fig:sep} (that is, the median of the medians of each realization) are shown in light black vertical lines.
-% Each plot is normalized such that the area under an individual curve is 1.
-%     % the redshift evolution
-% All pair types (dwarf and massive, major and minor) have narrow distributions that pile up around 0 $\kpc$ at $z=4$, but the distributions become more and more broad as $z\to0$ (note that only pairs with separations $>10\kpc$ are included in this analysis, see Sec.~\ref{sec:methods-crit-pairs}).
-% \linebreak
-% The distribution profiles are similar when the scale of the x-axis for massive pair separations is twice that of the dwarf pairs. 
-% Pair separations at $z=0$ tend to primarily fall between $10-\sim400\,\kpc$ for dwarf pairs and   between $10-\sim1000\,\kpc$ for massive pairs. 
-% At $z=4$, these ranges decrease to $10-150\,\kpc$ for dwarf pairs and $10-300\,\kpc$ for massive pairs. 
-%     % comparing major and minor
-% Major and minor pairs (both dwarf pairs and massive pairs) have roughly equivalent distributions, though the distribution of minor pairs with low separations is slightly higher than the major pairs.
-Thus, secondary halo of minor pairs tend to live slightly closer to their primaries than the  major secondaries.
-
-% \begin{figure*}[htp]
-%   \centering
-%   \includegraphics[width=\textwidth]{sepdist_1000.png}
-%   \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right).
-Major pairs are shown as solid lines, while minor pairs are dotted.
-The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines.
-%   At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively).
-However, at low redshift, the separation distribution tends to spread out more evenly across a large range of separations, thus increasing the median.
-%     }
-%   \label{fig:sep-dist}
-% \end{figure*}
-
-% \begin{figure*}[htp]
-%   \centering
-%   \includegraphics[width=\textwidth]{veldist_1000.png}
-%   \caption{
-%   Normalized distribution of relative velocities between primary and secondary halos for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right).
-Major pairs are shown as solid lines, while minor pairs are dotted.
-The median relative velocity of each pair type from Fig.~\ref{fig:vel} is shown in solid (major) and dotted (minor) vertical black lines.
-%   %
-%   The distribution of relative velocities for dwarf and massive pairs move to slightly lower velocities at lower redshifts. 
-%   At $z=0$, typical dwarf pair relative velocities are $0-200\,\kms$, while at $z=4$ they are $0-300\,\kms$. 
-%   Massive pairs typically have relative velocities between $0-300\,\kms$ at z=0 and $0-400\,\kms$ at $z=4$.
-%   The distribution of velocities for major and minor pairs is roughly equivalent within each mass range. 
-%     }
-%   \label{fig:vel-dist}
-% \end{figure*}
-
-% %% text on velocity distribution plot
-% \kc{left off here\~}
-% Fig.~\ref{fig:vel-dist}
+As JWST is expected to image dwarfs (give stellar mass range) out to z=XX in XX survey, the selection criteria for dwarf pairs that are applied will affect the inferred pair fractions greatly.
 
@@
 \section{Summary and Conclusions}\label{sec:summary}
+In this paper, we collect a large set of dwarf and massive subhalo pairs from the Illustris TNG100-1 simulation. 
+Pairs are selected from the full volume over all 100 snapshots of the simulation, though the sample size of pairs in the first 20 snapshots ($z>4.2$) is extremely small. 
+Major and minor pairs are determined using the stellar mass ratio between the primary and secondary halo using stellar masses from 1000 random realizations of the abundance matching prescription. 
+From this pair sample, we calculate the pair fractions and snapshot by snapshot kinematics of 4 different pair types: dwarf major pairs, dwarf minor pairs, massive major pairs, and massive minor pairs.
+
+Our main findings are as follows:
 \begin{itemize}
-    \item What we did 
-    \item Main findings:
+    \item The pair fraction for dwarf and massive pairs does not proceed identically throughout cosmic time.
+In fact, the two mass scales have opposite behavior at low z.
+The number of dwarf pairs per dwarf primary decreases from $z=2\to0$, while the number of massive pairs per massive primary is approximately constant from $z=4\to0.25$, with an abrupt increase at lower redshift.
+    \item The median physical separation between the primary and secondary subhalo of a pair increases with decreasing redshift.
+The typical separation of a dwarf (massive) pair is $120\,\kpc$ ($240\,\kpc$) at $z=0$ and $40\,\kpc$ ($80\,\kpc$) at $z=4$.
+    \item The median relative velocity between the primary and secondary subhalo of a pair decreases towards lower redshift.
+The typical relative velocity of a dwarf (massive) pair is $70\,\kms$ ($175\,\kms$) at $z=0$ and $132\,\kms$ ($290\,\kms$) at $z=4$.
+    \item The separation scaled by the total virial radius of the group is similar for dwarf and massive pairs, though massive pairs tend to have lower scaled separations for redshifts between $z=0-2$.
+The relative velocity scaled by the circular velocity at the virial radius evolves identically for both dwarf and massive pairs, indicating that the relative velocities are self-similar at different mass scales.
+    \item All of the above trends hold true for both major and minor pairs of the same mass range (i.e., the conclusions for the dwarf major pairs hold too for the dwarf minor pairs). 
+\end{itemize}
+
+Our results are consistent with prior works that have studied the pair fractions of massive and dwarf galaxies in the Illustris simulations in a projected sense. 
+The agreement between the pair fraction trends from projected and from physical pair selection criteria points to the IllustrisTNG simulation's robust ability to reproduce the characteristics of galaxy pairs from observations.
+
+Additionally, we conclude that:
 \begin{itemize}
-            \item pair fractions
-            \item separations
-            \item velocities
-            \item scaled values
+    \item Dwarf galaxy pairs and massive galaxy pairs likely have different evolutionary and merger processes which result in the opposing behavior of dwarf and massive pair fractions as a function of redshift.
+    \item The separation criteria used to observationally identify pairs likely results in an incompleteness of at least XX\% by $z=0$, though is less problematic for high redshift pairs where pairs tend to have smaller separations.
 \end{itemize}
-    \item Main takeaways: (maybe include these within main findings bullets~)
+
+Our conclusions point to the importance of time-evolving pair selection criteria that account for the natural separation increase of pairs at the universe expands.
+
+\kc{other main takeaways?}
+
+\begin{itemize}
+    \item otherMain takeaways: (maybe include these within main findings bullets~)
         \begin{itemize}
@@
 % \begin{itemize}
-%     \item Pair fraction for dwarfs and massives does not proceed identically throughout cosmic time. Opposite behavior at low z. 
+%     \item 
 %     \item Median pair separations increase and relative velocities decrease from high to low redshift. 

### 2023-05-15 paper/pears.tex
Updates from Overleaf

@@
       % We also use merger catalogs generated by XX for YY purpose. 
-    We also use merger trees provided by the \texttt{SUBLINK} algorithm~\citep{RG2015}, which tracks subhalos between snapshots using their DM particle data, in order to trace subhalo mass growth and merger histories.
+    We also use merger trees provided by the \texttt{SUBLINK} algorithm~\citep{rg15}, which tracks subhalos between snapshots using their DM particle data, in order to trace subhalo mass growth and merger histories.
 
@@
     \caption{(Top) Median number of dwarf (left) and massive (right) primaries and pairs as a function of redshift.
-    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations, as described in Sec.~\ref{sec:methods-err}.
+    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations, as described in Sec.~\ref{sec:results}.
     There are approximately 8 times as many dwarf primaries as massive primaries. 
@@
     % the redshift evolution
-At $z=4$, all pair types (dwarf and massive, major and minor) have narrow distributions that pile up around 0 $\kpc$\footnote{Note that only pairs with separations $>10\kpc$ are included in this analysis, see Sec.~\ref{sec:methods-crit-pairs}.}, with ranges between $10-150\,\kpc$ for dwarf pairs and $10-300\,\kpc$ for massive pairs.
+At $z=4$, all pair types (dwarf and massive, major and minor) have narrow distributions that pile up around 0 $\kpc$\footnote{Note that only pairs with separations $>10\kpc$ are included in this analysis, see Sec.~\ref{sec:methods-pairs}.}, with ranges between $10-150\,\kpc$ for dwarf pairs and $10-300\,\kpc$ for massive pairs.
 The distributions become more and more broad as $z\to0$, where separations range between $\sim10-400\,\kpc$ for dwarf pairs and $\sim10-1000\,\kpc$ for massive pairs.

### 2023-06-07 paper/pears.tex
finished 2.1 comments

@@
 \newcommand{\ms}[1]{\ensuremath{M_{*{#1}}}}
-\newcommand{\mud}{\ensuremath{\mu_\delta}}
-\newcommand{\mua}{\ensuremath{\mu_\alpha^*}}
-\newcommand{\bov}{\ensuremath{\boldsymbol{v}}}
-\newcommand{\boldx}{\ensuremath{\boldsymbol{x}}}
-\newcommand{\vtrav}{\ensuremath{\bov_{\rm travel}}}
-\newcommand{\xtrav}{\ensuremath{\boldx_{\rm travel}}}
-\newcommand{\pos}[2]{\ensuremath{\boldx_{\rm #1 \to #2}}}
-\newcommand{\vel}[2]{\ensuremath{\bov_{\rm #1 \to #2}}}
-\newcommand{\mwbary}{\ensuremath{\textrm{MW}_\textrm{bary}}}
-\newcommand{\mwouter}{\ensuremath{\textrm{MW}_\textrm{halo}}}
-\newcommand{\mwdisk}{\ensuremath{\textrm{MW}_\textrm{disk}}}
 \newcommand{\reflabel}[1]{\ensuremath{^{\mbox{\scriptsize{#1}}}}}
@@
 \newcommand{\scvel}{\ensuremath{\rm v_{rel}/v_{vir}}}
+\newcommand{\subcat}{\textit{Subhalo Catalog}}
+\newcommand{\starcat}{\textit{Subhalo + Stellar Mass Catalog}}
+\newcommand{\paircat}{\textit{Full Pair Catalog}}
 
@@
 \title{
-  Frequency of dwarf and massive galaxy pairs in the IllustrisTNG cosmological simulation
+  Frequency of low and high mass galaxy pairs in the IllustrisTNG cosmological simulation
 }
@@
 
-  \todo{Remove all instances of "we find" to "we compute" or "we calculate"}
+  \todo{Name data sets and refer to their names }
 \end{abstract}
@@
 
+\begin{itemize}
+    \item Galaxy mergers are a feature of LCDM and support the growth of galaxies across cosmic time.
+    \item The frequency of finding pairs tells us about how often we might expect: starbursts, SMBH mergers, the importance/role of mergers in building stellar mass/morphologies of galaxies today, SFHs, etc.
+    \item pair fraction at high masses has been well studied both obs and theoretically.
+There are studies of high mass (Mstar = 5e9-1e11Msun) pairs.
+These studies are typically done in projection for comparison to observational campaigns.
+    \item There are studies of low mass pairs (define what you mean by this), but only at low z, or as satellites of more massive systems (analogs of LG). 
+    \item in the era of jwst, these studies will be pushed to lower masses and high z, however, from a theory perspective, pair fractions at low masses have been under-studied (first 2 ish paragraphs ~ )
+    \item There are reasons to believe that high and low mass (Mstar = 1e8-5e9Msun) pairs might evolve differently, so it's important to study the low mass end too.
+
+    \item Also, major and minor mergers are important for different reasons, so studying them as separate systems is well motivated.
+        - is major high mass vs major low mass different, etc since these two types of mass ratios lead to different things 
+        - importance of mergers in high vs low mass galaxies (major mergers may be less important to SFH of Universe etc - look at sabrina's papers)
+    \item Systematically understanding the underlying difference between low and high mass pairs, Projected vs.
+physical 3D separations/pairs Two routes of studying galaxy pairs are through observations and simulations, but simulations allow us to fully understand the 3D position and velocity of objects.
+    \item in this study, we'll be quantifying the pair fraction of low mass pairs, and self consistently comparing to the pair fraction of high mass systems
+    \item In this work, we aim to characterize the pair fraction of both high and low mass galaxies, major and minor pairs, consistently as a function of time. 
+\end{itemize}
+cite Stierwalt for low mass pairs 4485/4490 (iso vs non iso pairs) 
+Pearson Besla 2016 
+Pearson Besla 2018 4485/4490
+Luber Pearson Besla 
+Nevin
+
+Discussion section: 
+what does this mean for our understanding of the LG (isolated mass analogs) 
+ngc 4490/4485 as another low z example (minor dwarf pair)
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
  \section{Methodology}\label{sec:methods}
-We aim to quantify and characterize the frequency (or occurrence rate) and bulk kinematic properties of galaxy pairs in a cosmologically consistent way as a function of cosmic time. 
-In particular, we study dwarf galaxy pairs and massive galaxy pairs that are of similar stellar and halo mass to a variety of galaxy pairs in the Local Group. 
-We categorize these pairs into one of four pair types: massive major pairs, such as the MW+M31; massive minor pairs, such as M31+M33 or MW+LMC; dwarf major pairs, such as M33+LMC; and finally, dwarf minor pairs, such as the LMC+SMC.
-
-To this end, we use a run of the \tngh\ simulation to select halo pairs at each snapshot according to a strict set of selection criteria as outlined in the remainder of this section. 
+We aim to quantify and characterize the frequency, or occurrence rate, of low mass ($\rm\ms{}=10^{9}-5\times 10^{10}\Msun$) and high mass ($\rm\ms{}=5\times10^{10}-10^{12}\Msun$) galaxy pairs in cosmological simulations as a function of cosmic time.
+To this end, we utilize the IllustrisTNG simulation to select halo pairs at each snapshot according to a strict set of selection criteria as outlined in the remainder of this section. 
 In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulation utilized in this study.
-Sec.~\ref{sec:methods-halos} outlines the initial mass cuts used to define our full sample of halos, from which we will select pairs.
-Sec.~\ref{sec:methods-am} outlines the abundance matching prescription we used to associate dark matter subhalos with stellar masses.
-Sec.~\ref{sec:methods-pairs} describes the second set of selection criteria we apply to obtain the full sample of pairs.
-Finally, Sec.~\ref{sec:pairprops} details some of the properties of our entire pair sample, including the total number of pairs and stellar mass ratios.
+Sec.~\ref{sec:methods-halos} outlines the initial mass cuts used to define our \subcat, to which we will 
+add stellar mass information. %consist of the set of subhalos from which we will select pairs.
+Sec.~\ref{sec:methods-am} outlines the abundance matching prescription used to associate dark matter subhalos with stellar masses, and the creation of the \starcat, from which we will select pairs.
+Sec.~\ref{sec:methods-pairs} describes the second set of selection criteria that we use to finally construct the \paircat. 
+% Finally, Sec.~\ref{sec:pairprops} details some of the properties of our entire pair sample, including the total number of pairs and stellar mass ratios. -- Note: created new section
 
@@
         % Brief description of TNG hydro and which run we use.
-    The \tng\ project ~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} consists of a suite of dark-matter-only $N$-body as well as full physics cosmological simulations consistent with the \textit{Planck2015} \lcdm\  cosmology~\citep{Planck2015}.
-    In this study we utilize data from the main high resolution full physics run of the (110.7\Mpc)$^3$ volume simulation, \textsl{TNG100-1}, which includes dark matter and baryonic particles and follows the evolution of $1820^3$ dark matter particles in 100 snapshots from $z=127$ to $z=0$.
+    The \tng\ project~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} consists of a suite of dark-matter-only $N$-body as well as full physics cosmological simulations consistent with the \textit{Planck2015} \lcdm\  cosmology~\citep{Planck2015}.
+    In this study we utilize data from the main high resolution, full physics run of the (110.7\Mpc)$^3$ volume simulation, \textsl{TNG100-1}, which follows the evolution of baryons and $1820^3$ dark matter particles from $z=127$ to $z=0$.
 
@@
     We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm~\citep{springel2001,dolag09}. 
-    These catalogs consist of halos, defined using the Friends-of-Friends (FoF) algorithm~\citep{davis1985} to link nearby particles, and their associated subhalos, which are over-dense and gravitationally bound dark matter structures compared to the background.
-(From here, we will refer to FoF halos as "groups" and their subhalos as )
-      % We also use merger catalogs generated by XX for YY purpose. 
-    We also use merger trees provided by the \texttt{SUBLINK} algorithm~\citep{rg15}, which tracks subhalos between snapshots using their DM particle data, in order to trace subhalo mass growth and merger histories.
+    This catalog was created using the Friends-of-Friends (FoF) algorithm~\citep{davis1985}, which links nearby particles to define large halos of associated particles, from which subhalos are identified as over-dense and gravitationally bound dark matter structures.
+    In addition, we utilize the merger trees provided by the \texttt{SUBLINK} algorithm~\citep{rg15}, which tracks subhalos between snapshots using their DM particle data in order to trace mass growth and merger histories of subhalos between snapshots.
 
-    The large volume of this simulation offers a large statistical sample of halos to study in a cosmological context, but is also high enough resolution ($m_{\rm DM} = 7.5\times10^6\Msun$, $m_{\rm gas} = 1.4\times10^6\Msun$) that dwarf halos ($\sim1\times10^{9-10.5}\Msun$) halos are resolved into roughly hundreds or more particles, well above the resolution limit of 32 DM particles for halos identified with \texttt{SUBFIND}, and 20 gas and star particles used to construct baryonic merger trees.
+    The high resolution of the TNG100-1 simulation permits a direct comparison of low mass and high mass galaxy pair fractions without concern for incompleteness at the low mass end from unresolved low mass pairs (details in~\ref{sec:methods-halos}).
+    Additionally, the volume of this simulation provides a large enough sample of massive halo pairs to allow for a statistically significant comparison.
 
-        %  this MIGHT go in a different section? am I talking about this because I want to show why we use hydro instead of dark? 
-    Baryonic process are known to affect the structure and formation of dark matter halos of low mass ($M_*\lesssim 1\times10^9\Msun$) subhalos in simulations~\citep[see e.g.][and references therein]{Sales:2022}.
-    Additionally, the shallow potential well of dwarf galaxies compared to their massive counterparts may lend themselves more easily to disruption from baryonic processes such as supernova feedback and reionization~\citep{}, resulting in fewer low mass halos ($\lesssim 5\times10^{10}$) in hydrodynamic simulations~\citep{vogelsberger14B}.
-    % Thus, the number of primaries  we expect that our choice of simulation will result in 
+    % Baryonic process are known to affect the structure and formation of dark matter halos of low mass ($M_*\lesssim 1\times10^9\Msun$) subhalos in simulations~\citep[see e.g.][and references therein]{Sales:2022}.
+    % Additionally, the shallow potential well of dwarf galaxies compared to their massive counterparts may lend themselves more easily to disruption from baryonic processes such as supernova feedback and reionization~\citep{}, resulting in fewer low mass halos ($\lesssim 5\times10^{10}$) in hydrodynamic simulations~\citep{vogelsberger14B}.
 % End sim details     %
@@
 % Choosing halos section %
-    \subsection{Choosing dwarf and massive halos in TNG} \label{sec:methods-halos}
-    % start off with group selection 
-        % brief explanation of FoF groups in sim
-    Each snapshot from the TNG100 group catalogs consist of FoF groups, large halos of closely associated DM particles, and the subhalos they contain, which are smaller bound structures of DM and the gas and star particles nearest to them.
-    We will refer to these two structures as "groups" and either "halos" or "subhalos" respectively, from here on. 
-    Galaxies form in these subhalos, so our pair sample will consist of pairs of subhalos within these larger group structures.
+    \subsection{Choosing dwarf and massive subhalos in TNG} \label{sec:methods-halos}
+    Galaxies form in dark matter subhalos, so our pair sample will consist of pairs of subhalos within these larger group structures.
+    In this section, we've outlined the steps to create the \subcat, which we will utilize to assign stellar masses to each of the dark matter subhalos.
 
-    We are interested in the inherent dynamics and properties of pairs of halos in the field.
-    Thus, we want our pairs to consist of some of the most massive halos in each group, and ensure that the pair is not dynamically influenced by nearby massive groups. 
-    By selecting pairs from the most massive halos of a group, a rough isolation criteria is inherent in our selection due to the nature of the FoF algorithm, which groups together nearby particles. 
-    To confirm that our sample , we have confirmed that nearly 100\% of the the most massive subhalos in each group are outside of the Hill radius of any nearby group or subhalo with greater mass.
+    We are interested in the inherent frequency of galaxy pairs in the field. 
+    The largest perturbers of a subhalo are typically part of the same group, as a consequence of the FoF algorithm. 
+    Thus, selecting from the most massive subhalos of a group ensures that the pairs are roughly isolated. 
+    In addition, we have confirmed that over 99\% of subhalos are isolated from large perturbers within 1 \Mpc.
+    This isolation criteria, which is a feature of our selection process, ensures that the final selected pairs are not dynamically influenced by nearby massive groups.
 
-    The first selection criteria that we invoke is a cut on the total group mass, $M_{G}$ (i.e., a mass cut on the FoF group mass, given by \texttt{Group\_M\_TopHat200} in the \tng\ group catalogs). 
-    We define the group mass range for dwarf groups as $8\times 10^{10} < M_{G,d} < 5\times 10^{11}\Msun$, which will host mass analogs of the LMC+SMC and LMC+M33 pairs. 
-    Massive groups range from $1\times10^{12} < M_{G,m} < 6.5\times10^{12}$, which at the lower mass end will host MW+LMC pairs, and MW+M31 pairs at the higher mass end. 
-    The group mass criteria is fixed for all redshifts, so at high z, the dwarf pairs we select may be the progenitors of higher mass systems at $z=0$.
+    The following selection process is repeated for each snapshot of the simulation over a redshift range of $z=0-\sim4$, at which point the population of massive subhalo pairs falls off rapidly (see Sec.~\ref{sec:pairprops} for more details).
+
+    First, at each snapshot, we invoke a cut on the total FoF group mass, \MG{}, given by \texttt{Group\_M\_TopHat200} in the TNG100 group catalogs. 
+    We define the group mass range for low mass and high mass groups as 
+    \begin{align*}
+        \mbox{\textbf{low mass:}}&\,\rm M_{G} = 8\times 10^{10}- 5\times 10^{11}\,\Msun \\ 
+        \mbox{\textbf{high mass:}}&\, \rm M_{G}=10^{12}- 6.5\times10^{12}\,\Msun.
+    \end{align*}
+    The group mass criteria is fixed for all redshifts, which means that some low mass groups at high $z$ may be the progenitors of high mass systems at $z=0$.
     Note that all masses used in this analysis are physical units, such that masses from the group catalogs are divided by $h$ to get units of \Msun.
 
-    Selecting dwarf pairs from the dwarf group mass range also ensures that we are not selecting satellite systems in the halos of more massive systems. 
-    The LMC+SMC, for example, are highly perturbed by the influence of the MW, and thus we do not pick dwarf pairs from high mass groups that may contain large nearby MW-mass analogs.
+    Selecting low mass pairs from the low group mass range ensures that we are not selecting satellite systems in the halos of more massive systems, nor low mass pairs in a large group. 
+    Additionally, $z\sim0$ groups of high mass will host isolated mass analogs of the MW--M31 and MW--LMC systems, while the low mass groups will host isolated mass analogs of an LMC--LMC or LMC--SMC pair.
 
         % explain what halos we will move forward with. 
-    For each group that passes the group mass cut, we create a catalog of all subhalos that pass a ``current mass" criteria: current (same snapshot) halo mass must be $M_h > 1\times10^{9}\Msun$ (the \texttt{SubhaloMass} field in the group catalogs).\footnote{Note that for the TNG100 hydro run, the halo mass is the total sum of all bound dark matter \textit{and} baryonic particles.}
-    This lower mass threshold ensures that our halos are resolved into $>100$ particles, and thus should be robust to the SUBFIND and SUBLINK algorithms even at the lowest mass end.
+    From the set of groups that pass the group mass cut, we create a catalog of all subhalos within each group that pass a ``current mass" threshold: the subhalo mass at the given snapshot, given by \texttt{SubhaloMass} field in the group catalogs, must be $M_h > 1\times10^{9}\Msun$.\footnote{Note that for the TNG100 hydro run, the subhalo mass is the total sum of all bound dark \textit{and} baryonic matter.}
+    This lower mass threshold ensures that our halos are resolved into $>100$ particles, and thus should be robust to the SUBFIND and SUBLINK algorithms, even at the low mass end.
 
-    We then utilize the merger tree catalogs to determine the maximum halo mass ever achieved by each halo. 
-    The set of all subhalos at each snapshot that pass the group mass and current mass cuts constitutes our entire subhalo sample. 
-    From here, we will use further selection criteria to narrow our sample down to pairs.
-
+    The set of all subhalos at each snapshot that pass the group mass and current mass cuts constitutes our entire subhalo sample, which we call the \subcat. 
+    At this stage, the \subcat{} consists of all subhalos which pass the
+    group mass and current mass criteria, and contains the subhalo ID and associated FoF group number of each subhalo.
+    From here, we will use further selection criteria to narrow down this large sample and to match pairs of subhalos in each group.
 % End choosing halos     %
@@
     \subsection{Abundance matching} \label{sec:methods-am}
-        % what is abundance matching
-    Abundance matching is a technique used to associate dark matter halo mass with specific galaxy properties.
-    This allows us to associate dark matter halos from the \tng\ simulation with observationally motivated galaxy properties. % maybe observationally constrained, instead? 
-    In particular, we will be utilizing a stellar mass to halo mass (SMHM) relationship to assign stellar masses to each of the subhalos in our sample.
+    We will be utilizing a stellar mass to halo mass (SMHM) relationship to assign stellar masses to each of the subhalos in our \subcat.  
+    There are a few reasons we opt to assign stellar masses to our subhalos, rather than use those computed by the simulation.
 
-    % few details about the msoter relationship. how was it determined?
-        % why are we using abundance matching 
-    The \tng100-1 subhalo catalogs do already contain a stellar mass field as computed in the simulation by simulating star formation and  AGN feedback, stellar feedback, galactic winds, etc.    
-    However, there are a couple reasons we opt to assign stellar masses to our halos, rather than use those from the simulation.
-
-    Primarily, applying an abundance matching prescription to assign stellar masses to each of the dark matter halos allows us to account for the observed spread in the stellar mass-halo mass relationship.
-    This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the spread in the SMHM function is large. 
+    Primarily, applying an abundance matching prescription to assign stellar masses to each of the dark matter halos allows us to account for the observed spread in the SMHM relationship. 
+    This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large. 
     In addition, using stellar masses as calculated from abundance matching allows us to side step any simulation-dependent stellar mass effects.
-    In the case of \tng100 specifically, it is known that the stellar masses of low mass galaxies are often overestimated compared to the galaxy luminosity function at the low mass end\cite{}. 
+    In the case of TNG100 specifically, it is known that the stellar masses of low mass galaxies are often overestimated compared to the galaxy luminosity function at the low mass end\cite{}. 
     Using an observationally-calibrated abundance matching prescription will thus lead to a more robust result for comparison with and predictions for observations. 
     Finally, utilizing an abundance matching prescription allows us to directly compare results between dark matter only and hydro simulations, since the stellar masses are assigned the same way. 
-    We make brief note of results from dark matter only simulations in Sec.~\ref{sec:results}.
+    We make brief note of results for our equivalent analysis using the dark matter only, TNG100-Dark simulation as well in Sec.~\ref{sec:discussion}.\kc{need to specify section once written}
 
         % what am prescription are we using? 
-    We use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic recipe to assign stellar masses to dark matter halos. 
+    In particular, we use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic prescription to assign stellar masses to dark matter halos. 
     The~\citet{Moster2013} relationship is a function of the halo mass, evolves with redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.
@@
         % realizations? 
-    For each subhalo at each snapshot in our full subhalo sample (see Sec.~\ref{sec:methods-halos}), we create a set of 1000 stellar mass values from the SMHM relationship to account for the systematic uncertainty in subhalo stellar masses.
+    For each subhalo at each snapshot in our full subhalo sample (see Sec.~\ref{sec:methods-halos}), we create a "realization" of the catalog for , 1000 stellar mass values from the SMHM relationship to account for the systematic uncertainty in subhalo stellar masses.
     Each realization is treated as an independent sample of galaxy stellar masses, which allows us to report realistic spreads of pair properties.
     Thus, we create 1000 separate pair catalogs, and compute pair properties (pair frequency, separations, etc) for each individual abundance matching realization.
+    \kc{what is the name of this catalog? (Isolated Group cats + 1000 Stellar Mass) }
 
@@
 Each pair will consist of a ``primary" more massive object, and a ``secondary" less massive companion.
+    \kc{We are starting with XX catalog, we'll sprinkle on some selection criteria, then store YY and ZZ. }
 
     % justify why we want to use stellar mass to define things
-    A majority of the literature uses the definition of "major" and "minor" pairs based on the stellar mass of the objects.
+    %A majority of the literature uses the definition of "major" and "minor" pairs based on the stellar mass of the objects.
 This is true as well for observational pair samples, such as Lotz 2011, wherein the halo mass of the objects is unknown, and thus the stellar mass is used to define the mass ratio of the pair.
@@
 Additionally, some groups may not have a ``primary" in one realization, but will in others.
+\kc{}
 
@@
         \end{align*}
+        \kc{justification for this stellar mass range? LG relation to put into context these ranges }
+        The primary stellar mass range is chosen to replicate a set of pairs with masses similar to LMC--SMC and MW--M31. \kc{remove "pairs"}
 
@@
         The median number of primaries in a single stellar mass realization at $z=0$ is XX dwarf primaries and XX massive primaries (see Sec.~\ref{sec:pairprops} for more info).
-        The primary stellar mass range is chosen to replicate a set of pairs with masses similar to LMC+SMC and MW-M31.
 
-        The abundance matching prescription has a spread of $\sim 1$dex at $M_{h}\sim 10^{10}\Msun$~\citep{Moster2013}, thus the set of selected primaries in each realization is typically unique.
+        The abundance matching prescription has a spread of $\sim 1$dex at $M_{h}\sim 10^{10}\Msun$~\citep{Moster2013},
+        \kc{move to AM section}%thus the set of selected primaries in each realization is typically unique.
 
         % explain special cases that people might wonder about.
-        A subhalo will not be selected as a primary if it is not the first most massive halo in the group, i.e., there are no subhalos in the group that are more massive than the primary (by stellar mass).
-However, since our selection is based on stellar mass, and there is a large spread in the SMHM relation, the most massive object by stellar mass may not be the most massive subhalo in terms of subhalo mass.
-        This is by design, since our selection criteria are meant to more closely replicate observational pair selection criteria which use the stellar mass ratio between the primary and companion to define a major or minor pair, rather than the DM halo mass.
+        %A subhalo will not be selected as a primary if it is not the first most massive halo in the group, i.e., there are no subhalos in the group that are more massive than the primary (by stellar mass).
+However, s
+        Since our selection is based on stellar mass, and there is a large spread in the SMHM relation, the primary for any realization of the catalog may not be the most massive subhalo in terms of total subhalo mass.
+        %This is by design, since our selection criteria are meant to more closely replicate observational pair selection criteria which use the stellar mass ratio between the primary and companion to define a major or minor pair, rather than the DM halo mass.
 
-        If a subhalo passes the stellar mass cut for a primary, but does not have an associated companion from the selection criteria for a secondary (see next subsection), the subhalo will still be considered a primary.
-We refer to all primaries without companions as ``isolated primaries."
-        The total set of primaries includes both paired primaries and isolated primaries.
     % end  primary subsubsection
@@
     \subsubsection{Selecting secondary companions}
-        The second most massive galaxy by stellar mass in each group is then used to define the secondary companions for each primary. 
-        As before, the selection of secondary companions occurs independently for each stellar mass realization, and for each snapshot, such that we collect 1000 different sets of pairs for each redshift.
+        The second most massive galaxy by stellar mass in each group is then used to define the secondary companion for each primary. 
+        As before, the selection of secondary companions occurs independently for each stellar mass realization, and for each snapshot, such that the population of secondaries in each realization will have a different stellar mass distribution.
+        %we collect 1000 different sets of pairs for each redshift.
 
+    \subsubsection{To create the pair catalog,}
         We create two categories of pairs: 
         major pairs and minor pairs, such that the secondary companion galaxies are selected via the stellar mass ratio between the secondary and primary.     
-        Since we have already rank ordered the halos in each stellar mass realization by their stellar mass, the stellar mass ratio will never exceed 1.   
+        % Since we have already rank ordered the halos in each stellar mass realization by their stellar mass, the stellar mass ratio will never exceed 1.   
         The stellar mass ratio criteria for major and minor pairs are:
@@
         \end{align*}
-        In addition, we require that each pair have a minimum separation of $15\kpc$ between the primary and secondary, which is XX times the smoothing length of the simulation. 
-        At smaller separations, more and more mass will be attributed to the central subhalo, which can lead to confusion in the merger tree histories. \kc{fix the wording here}.
+        \kc{give the reason for this look at z0.png}
+
+        \kc{For each pair we store the pair separation in physical units and relative velocity.
+We require that each pair have a minimum separation of $15 \kpc$ between the primary and secondary, which is XX times the smoothing length of the simulation.
+}
+        \kc{need to explain how the separations and velocities are computed from the catalog etc. }
+        At smaller separations, more and more mass will be attributed to the central subhalo, which can lead to confusion in the SUBFIND catalogs. %the merger tree histories. \kc{the }.
 
@@
         We refer to all primaries without companions as ``isolated primaries."
+        \kc{move this down to the secondary section}
+        If a subhalo passes the stellar mass cut for a primary, but does not have an associated companion from the selection criteria for a secondary (see next subsection), the subhalo will still be considered a primary.
+We refer to all primaries without companions as ``isolated primaries."
+        The total set of primaries includes both paired primaries and isolated primaries.
 
-        Note that in this selection routine, the LMC+SMC pair would not be selected, as they are a system of satellites in a massive group.
-Rather, the MW-M31 pair would be selected and identified as a ``massive major pair."
+        The pair catalog contains blah blah blah. 
+        1000 sets of pairs at each snapshot blah blah
+
+        The pair sample consists of 1000 sets of pairs at each snapshot, each set representing a different realization of the abundance matching prescription. 
+        At each snapshot, we calculate the median occurrence rate and kinematic values for each of the 1000 realizations. 
+        Each of the following plots shows the parameter's median and percentile spread calculated from the set of 1000 medians from each realization.
+
+        how do we use these catalogs? Interested in the aggregate properties of the full sample, and so we will treat blah blah
+
     % end secondary subsubsection
@@
 At very low redshift, the pair count and primary count have opposite behavior, with the pair count \textit{increasing} at very low redshifts of $z=0-0.25$ and \textit{peaking} at $z=0$.
+    \kc{where does it peak and what is }
     (Bottom) Fraction of pairs per primary as a function of redshift (i.e., the ratio between dotted line and solid line in each column).
@@
     \includegraphics[width=\textwidth]{smrdist_1000.png}
-    \caption{Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs.
+    \caption{\kc{using all 1000 realizations - combined sample of XX catalog} Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs.
 Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$.
@@
 \section{Sample: Overview of pair properties} \label{sec:pairprops}
+    Utilizing the pair catalog, We compute the \# of prims in each realization of the 
     The full pair sample contains 1000 individual sets of pairs at each snapshot, for all 100 snapshots of the \tng100-1 simulation.
-    For each snapshot, we calculate the median number of primaries and pairs in each of the 1000 stellar mass realizations. 
-    The data shown is the median and 1-99\% range of the set of medians from the realizations.
 
-    Fig.~\ref{fig:counts} shows the redshift evolution of the number of dwarf and massive primaries and pairs we identify over the redshift range $z=0-4$. 
+    Fig.~\ref{fig:counts} shows the redshift evolution of the median number of dwarf and massive primaries and pairs we identify over the redshift range $z=0-4$.   
+    For each snapshot, we calculate the median number of primaries and of pairs in each realization within the Pair Catalog, yielding a set of 1000 medians. 
+    The solid line and dashed lines are the median of this set of 1000 medians, and the shaded regions show the 1-99\% spread of the set.
+
     The number of identified primaries is smallest at $z=4$, and rises to a maximum around $z=1$ for both dwarf and massive primaries.        
@@
 
-    The dwarf primary count (green solid line in top left panel) reaches a maximum median of $\sim15000$ halos (in one realization) at $z\sim0.6$, then decreases by $\sim16\%$ to 12000 halos at $z=0$.
+    The median dwarf primary count (green solid line in top left panel) reaches a maximum of $\sim15000$ halos at $z\sim0.6$, then decreases by $\sim16\%$ to 12000 halos at $z=0$. 
     The dwarf pair count (green dashed line) peaks much earlier at $z\sim2$ with $\sim3000$ pairs, and decreases to $\sim1000$ pairs at $z=0$.
@@
 
-    We show the distribution of stellar mass ratios between the secondary and primary of each dwarf and massive pair in Fig.~\ref{fig:massratio}.
+    include all 1000 realizations as a single "Combined Sample"
+    We show the distribution of stellar mass ratios between the secondary and primary of each dwarf and massive pair in Fig.~\ref{fig:massratio} from the Pair Catalog, com 
+    \kc{explain how we compute this}
+    all realizations.
     % Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.
     In general, the shape of the distribution remains constant from $z=0-4$ for both dwarfs and massive pairs, and between the dwarf and massive pairs at each redshift. 
-    Thus, the typical stellar mass ratio of pairs in our sample is independent of mass scale and of redshift.
+    Thus, the typical stellar mass ratio of pairs in our sample is independent of mass scale and of redshift. \kc{how much more likely are you to find 1/4 than 1:1 things? what about 1:10 to 1:4?}
 
@@
 \section{Results: The frequency and kinematics of dwarf and massive pairs}
-We collect dwarf pairs and massive pairs at all snapshots from the TNG100-1 simulation and analyze the occurrence rate for major and minor pair types across cosmic time.
-We also analyze the kinematic behavior of pairs on a snapshot by snapshot basis, and determine how the bulk kinematics of the different pair populations differ, as well as how they change over time.
+We have created catalogs of isolated low and high mass galaxy pairs from $z=0-4$ in the TNG100-1 simulation. 
+In this section, we will analyze the occurrence rate and kinematic properties (physical separations and relative velocities) for major and minor pair types across cosmic time.
 
-The pair sample consists of 1000 sets of pairs at each snapshot, each set representing a different realization of the abundance matching prescription. 
-At each snapshot, we calculate the median occurrence rate and kinematic values for each of the 1000 realizations. 
-Each of the following plots shows the parameter's median and percentile spread calculated from the set of 1000 medians from each realization.
-
-In Sec.~\ref{sec:results-frac}, we show the redshift evolution of the fraction of primaries with a major or minor companion (the ``pair fraction") and compare dwarf pairs and massive pairs.
+In Sec.~\ref{sec:results-frac}, we show the redshift evolution of the fraction of primaries with a major or minor companion (the ``pair fraction") and compare the results for dwarf pairs and massive pairs.
 In Sec.~\ref{sec:results-kinematics}, we look at the redshift evolution of the separations and relative velocities between primary and secondary halos of each pair.
 % need to specify this is snapshot by snapshot?
-In Sec.~\ref{sec:results-scaled}, we compare the ``scaled" separations and velocities of dwarf and massive pairs.
+In Sec.~\ref{sec:results-scaled}, we compare the separations and velocities scaled by the FoF group's virial properties. 
+Finally, in Sec.~\ref{sec:results-virialcut}, we take subsets of the Pair Catalog, selecting only pairs within some fraction of the virial radius, and illustrate the impact on the recovered low and high mass pair fractions.
 
@@
     For example, the dwarf major pair fraction is calculated as the number of dwarf major pairs divided by the number of dwarf primaries. 
-    Dwarf minor pair fractions, and massive major and minor pair fractions are defined in the same way. 
     The pair fraction of dwarf or massive pairs with a major or minor companion gives the likelihood of finding a companion of a certain mass type about a primary identified in the field.
@@
         % what do we learn from this? what are the takeaways? where do we discuss this in more detail?
-    Overall, these results show that massive and dwarf pair counts evolve differently, particularly at very low redshift despite the pair fractions being roughly equal at higher z. 
+    Overall, these results show that massive and dwarf pair counts evolve differently over time, particularly at very low redshift, despite the pair fractions being roughly equal at higher z. 
     These differences could be a result of the different formation mechanisms at play in the evolution of the systems at these two different mass scales, or alternatively, from differences in satellite dynamics between dwarf and massive systems (see Sec.~\ref{sec:results-kinematics}).
@@
         % Top plots ~
-        (Top) Median pair fraction, defined as the fraction of dwarf or massive primaries with a major (left) or minor (right) companion by stellar mass (see Sec.~\ref{sec:methods-pairs}). 
+        (Top) Median pair fraction, defined as the fraction of dwarf or massive primaries with a major (solid) or minor (dashed) companion by stellar mass (see Sec.~\ref{sec:methods-pairs}). 
         Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
@@
           % dwarf pairs
-        Dwarf pair fractions, shown in green, are approximately constant from $z=3-4$, then declines monotonically to $z=0$.
+        Dwarf pair fractions, shown in green, are approximately constant from $z=3-4$, then decline monotonically to $z=0$.
 The major pair fraction is $0.041$ at $z=0$ and $0.126$ at $z=3$, while the minor pair fractions are $0.034$ and $0.111$ at $z=0$ and $z=3$, respectively.
@@
 The pair fraction difference increases with decreasing redshift, peaking at $z=0$ with a difference of 0.166 for major pairs and 0.111 for minor pairs.
-This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly in the low redshift regime.}
+This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly at low redshift.}
       \label{fig:pairratio}
@@
         %% the difference between major and minor pairs
-        In addition, Fig.~\ref{fig:sep} shows the median subtracted difference between the relative separations calculated for major pairs and minor pairs of both mass type. 
-        There is a small offset in the median separations of major and minor dwarf pairs (between $10-25\,\kpc$ from  $z=0-1$ and approximately $5\,\kpc$ from $z=1-4$), and a larger median separation offset for major and minor massive pairs (between $25-100\,\kpc$ from  $z=0-1$ and approximately $10-40\,\kpc$ from $z=1-4$).
+        In addition, the bottom panels of Fig.~\ref{fig:sep} shows the median subtracted difference between the relative separations calculated for major pairs and minor pairs of both mass types. 
+        There is a small offset in the median separations of major and minor dwarf pairs (between $10-25\,\kpc$ from  $z=0-1$ and approximately $5\,\kpc$ from $z=1-4$), and a larger offset for major and minor massive pairs (between $25-100\,\kpc$ from  $z=0-1$ and approximately $10-40\,\kpc$ from $z=1-4$).
         The major-minor offset is likely a result of more major pairs merging more quickly (thus at earlier times and higher $z$) due to the increased effect of dynamical friction, thus leading to a population of low relative separation minor pairs that have yet to merge.
@@
 Likewise, the median velocity for major massive pairs decreases from $260$ at $z=4$ to $170\,\kms$ at $z=0$, though with more spread at high $z$.
-        As the circular velocity of a secondary object about the primary is inversely proportional to the radius, it is not surprising to find a decrease in the relative velocity for pairs at lower redshift due to the expansion of the universe/decrease in concentration/increase in the virial radius of the halo as $z\to0$.
+        \todo{} As the circular velocity of a secondary object about the primary is inversely proportional to the radius, it is not surprising to find a decrease in the relative velocity for pairs at lower redshift due to the decrease in concentration/increase in the virial radius of the halo as $z\to0$.
 \kc{citation needed}
@@
         Fig.~\ref{fig:vel} also includes a panel showing the subtracted median difference at each snapshot of the minor pair from the major pair.
-Unlike the relative separation, the relative velocities do not have a strong dependence on the secondary mass.
-        Since minor pairs typically have slightly higher velocities than their major pair counterparts, this difference is usually $<0$.
+Unlike the relative separation, the relative velocities do not have a strong dependence on mass ratio of the pairs.
         The offsets between the relative velocities of dwarf major and minor pairs is between $0-5\,\kms$, and between $0-25\,\kms$ for massive major and minor pairs.
@@
 
-    To explore the impact of halo growth and mass scale the kinematics pairs, we study the relative separation of a primary and secondary halo scaled by the virial radius of the FoF group, and the relative velocity divided by the circular speed of the group at the virial radius.
+    To explore the impact of halo growth and mass scale the kinematics pairs, we study the relative separation of a primary and secondary halo scaled by the virial radius ($r_{vir}$) of the FoF group, and the relative velocity ($v_{vir}$) divided by the circular speed of the FoF group at the virial radius.
     That is, 
@@
     In Fig.~\ref{fig:scaled}, we show the median scaled separation and scaled velocity for dwarf and massive major pairs as a function of time. 
-    Minor pairs show the same trends, so we've omitted them here for brevity.
+    Minor pairs show the same trends, and so we have omitted them here for brevity.
 
@@
     Overall, the median scaled separation of dwarf pairs and massive pairs do not evolve significantly differently from $z=4\to0$.
-    In fact, the median separation of halos in a pair is smaller than the group virial radius for at $z<2.5$, but is larger than the virial radius at $z>2.5$.
+    In fact, the median separation of halos in a pair is smaller than the group virial radius at $z<2.5$, but is larger than the virial radius at $z>2.5$.
     %maybe not bound at high z, though could become bound by low z by mass accretion ? 
-    Dwarf pairs tend to have slightly larger separations relative to their virial radius than massive pairs at almost all redshifts, though the spread of median scaled separations is large for massive pairs at $z>2$.
+    Dwarf pairs tend to have slightly larger separations relative to the group virial radius than massive pairs at almost all redshifts, though the spread of median scaled separations is large for massive pairs at $z>2$.
 
@@
     The distributions show roughly equivalent shape and extent for both dwarf and massive scaled kinematics, and do not vary significantly with redshift.
-    scaled separation, and velocity both, this is due to the growth of halos, so while the separation increases, the halo radius also increases.
+
     % behavior of massive vs. dwarf 
-    Overall, our results imply that there is little to no mass dependence on the redshift evolution of pair velocities, though pair separations seem to have a weak dependence on the total system mass.
+    Overall, our results imply that there is little difference between high mass and low mass pairs in the redshift evolution of pair velocities, though pair separations seem to have a weak dependence at low redshift on the type of pair.
+Inner regions of the halo , high mass pairs tend to be even closer, likely due to
+    This appears opposite to the physical separations, but when you scale to the total mass of the system, the 
+    Fof groups are increasng in size . \todo{}
 
@@
 
+\subsection{Separation cuts as fxn of virial radius}
+put in plots~ 
 % end Results section%
@@
 \section{Discussion}\label{sec:discussion}
+
+% In particular, we study dwarf galaxy pairs and massive galaxy pairs that are of similar stellar and halo mass to a variety of galaxy pairs in the Local Group. 
+% We categorize these pairs into one of four pair types: massive major pairs, such as the MW+M31; massive minor pairs, such as M31+M33 or MW+LMC; dwarf major pairs, such as M33+LMC; and finally, dwarf minor pairs, such as the LMC+SMC.
+% \kc{can maybe move these two sentences to a discussion section}
+
+    \kc{ make a subsection about the equivalence of our findings with the dark matter simulation) We make brief note of results for our equivalent analysis using the dark matter only TNG100-Dark simulation as well in Sec.~\ref{sec:results}.}
+
 \subsection{Implications for the differences in pair fractions of dwarf and massive pairs}

### 2023-06-28 paper/pears.tex
added sepcut and vircut plots, sepcut text, edited fig 3 caption

@@
 \newcommand{\paircat}{\textit{Full Pair Catalog}}
+\newcommand{\Rvir}{\ensuremath{\rm R_{vir}}}
 
@@
 
-  \todo{Name data sets and refer to their names }
 \end{abstract}
@@
     \item Systematically understanding the underlying difference between low and high mass pairs, Projected vs.
-physical 3D separations/pairs Two routes of studying galaxy pairs are through observations and simulations, but simulations allow us to fully understand the 3D position and velocity of objects.
+3D separations/pairs Two routes of studying galaxy pairs are through observations and simulations, but simulations allow us to fully understand the 3D position and velocity of objects.
     \item in this study, we'll be quantifying the pair fraction of low mass pairs, and self consistently comparing to the pair fraction of high mass systems
@@
  \section{Methodology}\label{sec:methods}
-We aim to quantify and characterize the frequency, or occurrence rate, of low mass ($\rm\ms{}=10^{9}-5\times 10^{10}\Msun$) and high mass ($\rm\ms{}=5\times10^{10}-10^{12}\Msun$) galaxy pairs in cosmological simulations as a function of cosmic time.
+We aim to quantify and characterize the frequency, or occurrence rate, of low mass ($\rm\ms{}=10^{8}-5\times 10^{9}\Msun$) and high mass ($\rm\ms{}=5\times10^{9}-10^{11}\Msun$) galaxy pairs in cosmological simulations as a function of cosmic time.
 To this end, we utilize the IllustrisTNG simulation to select halo pairs at each snapshot according to a strict set of selection criteria as outlined in the remainder of this section. 
@@
         % explain what halos we will move forward with. 
-    From the set of groups that pass the group mass cut, we create a catalog of all subhalos within each group that pass a ``current mass" threshold: the subhalo mass at the given snapshot, given by \texttt{SubhaloMass} field in the group catalogs, must be $M_h > 1\times10^{9}\Msun$.\footnote{Note that for the TNG100 hydro run, the subhalo mass is the total sum of all bound dark \textit{and} baryonic matter.}
-    This lower mass threshold ensures that our halos are resolved into $>100$ particles, and thus should be robust to the SUBFIND and SUBLINK algorithms, even at the low mass end.
+    From the set of groups that pass the group mass cut, we create a catalog of all subhalos within each group that pass a ``current mass" threshold, such that the subhalo mass at the given snapshot, given by \texttt{SubhaloMass} field in the group catalogs, is
+    \begin{equation*}
+    \mbox{\textbf{min. subhalo mass:}}\,
+    \Mhalo > 1\times10^{9}\Msun.\footnote{Note that for the TNG100 hydro run, the subhalo mass is the total sum of all bound dark \textit{and} baryonic matter.}
+    \end{equation*}
+    This lower mass threshold ensures that our halos are resolved into $>100$ particles, and thus should be robust to the \subfind\ and \sublink\ algorithms, even at the low mass end.  
+    For each subhalo that passes both of the above criteria, we use the \sublink\ merger trees to identify the maximum subhalo mass achieved by the subhalo, \Mpeak. 
+    We consider only the given snapshot and all previous snapshots in the determination of \Mpeak.
 
-    The set of all subhalos at each snapshot that pass the group mass and current mass cuts constitutes our entire subhalo sample, which we call the \subcat. 
-    At this stage, the \subcat{} consists of all subhalos which pass the
-    group mass and current mass criteria, and contains the subhalo ID and associated FoF group number of each subhalo.
+    All subhalos in a given snapshot that pass both the group and current mass selection criteria will be added to our full sample of subhalos, which we call the \subcat. 
+    The catalog contains subhalos at each snapshot from $z=0-\sim4.2$ (snapshot numbers 20-99) and their associated properties, namely: Subhalo ID, FoF Group Number, current subhalo mass \Mhalo, and peak halo mass \Mpeak.
     From here, we will use further selection criteria to narrow down this large sample and to match pairs of subhalos in each group.
@@
     Primarily, applying an abundance matching prescription to assign stellar masses to each of the dark matter halos allows us to account for the observed spread in the SMHM relationship. 
-    This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large. 
+    This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large, $\sim 1$dex at $M_{h}\sim 10^{10}\Msun$. 
     In addition, using stellar masses as calculated from abundance matching allows us to side step any simulation-dependent stellar mass effects.
-    In the case of TNG100 specifically, it is known that the stellar masses of low mass galaxies are often overestimated compared to the galaxy luminosity function at the low mass end\cite{}. 
+    In the case of TNG100 specifically, stellar masses of low mass galaxies are often overestimated compared to the galaxy luminosity function at the low mass end\cite{}. 
     Using an observationally-calibrated abundance matching prescription will thus lead to a more robust result for comparison with and predictions for observations. 
@@
         % what am prescription are we using? 
-    In particular, we use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic prescription to assign stellar masses to dark matter halos. 
-    The~\citet{Moster2013} relationship is a function of the halo mass, evolves with redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.
-    Additionally, stellar mass is defined separately for central halos (``hosts") and for infalling satellites (``subhalos"), where the first is a function of the virial mass of the halo and its redshift, $M_{vir}$ and $z$, and the second is a function of the mass and redshift at the time of infall, $M_{inf}$ and $z_{inf}$.
-    This assumes that the satellite halos are at the peak of their stellar mass before infall, and neglects the affect of star formation or stellar stripping within the host halo.
-
-        % what do we use for the mass ~ 
-    In this work, we will use the peak halo mass \Mpeak\ from the \sublink\ merger trees to calculate subhalo stellar masses. 
-    \citet{Munshi2021} found that the stellar mass of subhalos at $z=0$ in the ``Marvel-ous Dwarfs" and ``DC Justice League" zoom simulations are more closely correlated with the peak halo mass ($M_{peak}$) than the $z=0$ halo mass for halos with peak halo mass $10^8<M_{\rm peak}<10^{11} \Msun$.
-    % separate citation for peak halo mass and stellar mass relatiosnhip for M > 1e11Msun 
-    Using the peak halo mass additionally allows us to remain robust to scenarios in which a secondary has formed most of its stars, then loses a significant portion of its dark matter content through tidal interactions with a primary, but retains the bulk of its stellar content.
-
-        % regarding the redshift dependence ~
-    We additionally assume that the stellar mass of both the primary and secondary halo can change as a function of redshift after the secondary has entered the primary's halo and do not immediately cease star formation.
-    This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{geha13} which finds that dwarfs $>1\Mpc$ from a MW-type galaxy are often star forming and rarely quenched.
-    Additionally, the SAGA survey has found that large satellites of MW-type galaxies are often very blue, with infall into the halo spurring high rates of star formation due to the large gas fraction in dwarfs~\citep{saga}.
-    Thus, we calculate stellar masses for our subhalos using $M_{\rm peak}$ and the redshift of the current snapshot to calculate the stellar mass of each subhalo, and to account for the additional stellar mass that can form after infall.
-
-    As mentioned in a footnote in Sec.~\ref{sec:methods-halos}, the total halo mass of subhalos in the hydro simulation includes the mass of both dark matter and baryonic particles. 
-    In TNG100-1, the DM particle mass is decreased XX\% compared to the DM particle mass in \tng100-1 Dark to account for the additional mass of baryons, such that the total mass of the halo will remain roughly the same between the dark matter only and hydro simulations.
-    Since the~\citet{Moster2013} AM relation was calibrated using DM subhalos from the \texttt{MilleniumII} dark matter only simulation, we will use the total subhalo mass from the TNG100-1 hydro simulation as a proxy for the corresponding DM halo mass in the TNG100-1 Dark run, \texttt{SubhaloMass}.
+    We use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic prescription to assign stellar masses to dark matter halos. 
+    The~\citet{Moster2013} relationship is a function of subhalo mass, redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.
 
         % realizations? 
-    For each subhalo at each snapshot in our full subhalo sample (see Sec.~\ref{sec:methods-halos}), we create a "realization" of the catalog for , 1000 stellar mass values from the SMHM relationship to account for the systematic uncertainty in subhalo stellar masses.
-    Each realization is treated as an independent sample of galaxy stellar masses, which allows us to report realistic spreads of pair properties.
-    Thus, we create 1000 separate pair catalogs, and compute pair properties (pair frequency, separations, etc) for each individual abundance matching realization.
-    \kc{what is the name of this catalog? (Isolated Group cats + 1000 Stellar Mass) }
+    We elect to use the maximum subhalo mass \Mpeak\ in the stellar mass calculation, rather than the subhalo mass at the given snapshot.
+    We also use the current redshift of the given snapshot, $z_{snap}$, of each subhalo in the stellar mass calculation. 
+    Thus, $\ms{}=f(\Mpeak,z_{snap})$.
+
+    Using \Mpeak\ mass allows us to remain robust to scenarios in which a secondary has formed most of its stars, then loses a significant portion of its dark matter content through tidal interactions with a primary, but retains the bulk of its stellar content.
+    In fact, \citet{Munshi2021} found that the stellar mass of subhalos at $z=0$ in the ``Marvel-ous Dwarfs" and ``DC Justice League" zoom simulations are more closely correlated with $M_{peak}$ than the $z=0$ halo mass for halos with peak halo mass $10^8<M_{\rm peak}<10^{11} \Msun$.
+
+    Using $z_{snap}$ means that we allow the stellar mass of both the primary and secondary halo to change as a function of redshift, even after the secondary has entered the primary's halo.
+%and do not immediately cease star formation.
+    This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{geha13} which finds that dwarfs $>1\Mpc$ from a MW-type galaxy are often star forming and rarely quenched.
+    Additionally, the SAGA survey has found that large satellites of MW-type galaxies are often very blue, with infall into the halo spurring high rates of star formation due to the large gas fraction in dwarfs~\citep{Mao2021}.
+    % maybe need a note here on whether this is fair to extend to higher mass system?
+
+    We then calculate the stellar mass for a given subhalo by gaussian sampling each of the fitting parameters of the analytic framework from~\cite{Moster2013}, in order to account for the spread in the SMHM relationship.
+    We generate a single stellar mass ``realization" of the full \subcat\ by calculating a stellar mass for each subhalo, using an independent draw the SMHM distribution for each subhalo. 
+    For each snapshot, we repeat this process 1000 times to generate 1000 realizations of stellar masses for the \subcat.
+    The resulting catalog is called the \starcat, and consists of the set of all subhalos from the \subcat, as well as the 1000 stellar mass realizations. 
+    Each realization is treated as an independent sample of galaxy stellar masses, which will allow us to report realistic spreads of pair properties.
+
+    % As mentioned in a footnote in Sec.~\ref{sec:methods-halos}, the total halo mass of subhalos in the hydro simulation includes the mass of both dark matter and baryonic particles. 
+    % In TNG100-1, the DM particle mass is decreased XX\% compared to the DM particle mass in \tng100-1 Dark to account for the additional mass of baryons, such that the total mass of the halo will remain roughly the same between the dark matter only and hydro simulations.
+    % Since the~\citet{Moster2013} AM relation was calibrated using DM subhalos from the \texttt{MilleniumII} dark matter only simulation, we will use the total subhalo mass from the TNG100 hydro simulation as a proxy for the corresponding DM halo mass in the TNG100-1 Dark run, \texttt{SubhaloMass}.
 
@@
     \subsection{Pair selection}\label{sec:methods-pairs}
-    The full pair sample is constructed from the set of all subhalos and their abundance matching realizations.
-Each pair will consist of a ``primary" more massive object, and a ``secondary" less massive companion.
-    \kc{We are starting with XX catalog, we'll sprinkle on some selection criteria, then store YY and ZZ. }
+    Starting from the \starcat, here we outline the pair matching process through which we generate the \paircat. 
+    At each redshift, and for each stellar mass realization, we will identify subhalo pairs consisting of a "primary" and a "secondary", where primaries are the more massive of the pair by stellar mass.
 
@@
     \subsubsection{Selecting primaries}
-        Primary galaxies (equivalently, ``primary subhalos") are the most massive galaxy of their group by stellar mass. Thus, each group can have at most one primary galaxy.
+        Primary galaxies (equivalently, ``primary subhalos") are the most massive galaxy of their FoF group by stellar mass, such that each group can have at most one primary galaxy.  
+        Each stellar mass realization is treated independently, such that the subhalo identified as the primary of a group may change between stellar mass realizations.
 
-        We apply mass cuts on the stellar mass of the primary to define our sample of dwarf primaries and massive primaries.
-Each stellar mass realization is treated independently, such that the primary of a group may change between stellar mass realizations.
-Additionally, some groups may not have a ``primary" in one realization, but will in others.
-\kc{}
+        At a given snapshot, and for each stellar mass realization, we rank order the subhalos of each group by stellar mass. 
+        Primaries must be the most massive subhalo in their group, and pass the following stellar mass criteria:         
+        \begin{align*} 
+        \mbox{\textbf{low mass primaries:}}&\, 10^{8}< \rm M_{*1} < 5\times10^{9}\Msun \\ 
+        \mbox{\textbf{high mass primaries:}}&\, 5\times 10^{9}< \rm M_{*1} < 10^{11}\Msun.
+        \end{align*}
+        The stellar mass criteria is fixed, and does not change as a function of redshift. 
+        At $z=0$, the stellar mass range for low mass primaries corresponds to isolated analogs of the LMC or M33, while the high mass primaries represent isolated analogs of the MW or M31.
 
-        For each stellar mass realization, we rank order the subhalos of each group by stellar mass, then perform a mass cut specific to the type of group: dwarf primaries from dwarf mass groups, and massive primaries from massive mass groups (see Sec.~\ref{sec:methods-halos} for group mass criteria).
-        We define the stellar mass range for dwarf primaries and massive primaries as:
-        \begin{align*} 
-        \mbox{\textbf{dwarf primaries:}}&\, 1\times 10^{8}< \rm M_{*} < 5\times10^{9}\Msun \\ 
-        \mbox{\textbf{massive primaries:}}&\, 5\times 10^{9}< \rm M_{*} < 1\times 10^{11}\Msun.
-        \end{align*}
-        \kc{justification for this stellar mass range? LG relation to put into context these ranges }
-        The primary stellar mass range is chosen to replicate a set of pairs with masses similar to LMC--SMC and MW--M31. \kc{remove "pairs"}
-
-        The stellar mass criteria is fixed, and does not change as a function of redshift. 
-        The median number of primaries in a single stellar mass realization at $z=0$ is XX dwarf primaries and XX massive primaries (see Sec.~\ref{sec:pairprops} for more info).
-
-        The abundance matching prescription has a spread of $\sim 1$dex at $M_{h}\sim 10^{10}\Msun$~\citep{Moster2013},
-        \kc{move to AM section}%thus the set of selected primaries in each realization is typically unique.
-
-        % explain special cases that people might wonder about.
-        %A subhalo will not be selected as a primary if it is not the first most massive halo in the group, i.e., there are no subhalos in the group that are more massive than the primary (by stellar mass).
-However, s
-        Since our selection is based on stellar mass, and there is a large spread in the SMHM relation, the primary for any realization of the catalog may not be the most massive subhalo in terms of total subhalo mass.
-        %This is by design, since our selection criteria are meant to more closely replicate observational pair selection criteria which use the stellar mass ratio between the primary and companion to define a major or minor pair, rather than the DM halo mass.
+        % The median number of primaries in a single stellar mass realization at $z=0$ is XX dwarf primaries and XX massive primaries (see Sec.~\ref{sec:pairprops} for more info). 
+        Since our selection is based on stellar mass, and there is a large spread in the SMHM relation, a primary subhalo may not be the most massive subhalo in terms of total subhalo mass.
 
@@
     \subsubsection{Selecting secondary companions}
-        The second most massive galaxy by stellar mass in each group is then used to define the secondary companion for each primary. 
-        As before, the selection of secondary companions occurs independently for each stellar mass realization, and for each snapshot, such that the population of secondaries in each realization will have a different stellar mass distribution.
-        %we collect 1000 different sets of pairs for each redshift.
+        As before, the selection of secondary companions occurs independently for each stellar mass realization, and for each snapshot. 
+        Secondary subhalos are defined as the second most massive subhalo in a FoF group by stellar mass. 
+        Secondary subhalos with stellar mass $M_{*2}$ must have a stellar mass ratio:
+        \begin{align*}
+            &\mbox{\textbf{stellar mass ratio:}}\,      
+            M_{*2}/M_{*1} > 1/10.
+        \end{align*} 
+        We do not include companions with a stellar mass ratio $M_{*2}/M_{*1} <1/10$ due to the lower bound subhalo mass criteria of $\Mhalo=10^9$, which has at least a the corresponding stellar mass of $10^6\Msun$ at $z=0$.
+        The stellar mass ratio criterion ensures completeness of the sample, even at the lowest stellar masses considered.
 
-    \subsubsection{To create the pair catalog,}
-        We create two categories of pairs: 
-        major pairs and minor pairs, such that the secondary companion galaxies are selected via the stellar mass ratio between the secondary and primary.     
-        % Since we have already rank ordered the halos in each stellar mass realization by their stellar mass, the stellar mass ratio will never exceed 1.   
+    \subsubsection{Creating the pair catalog}
+        Pairs consist of a single primary and secondary in a FoF group as selected via the criteria above. 
+        Each pair is categorized as either a major or minor pair based on the stellar mass ratio between the primary and secondary. 
         The stellar mass ratio criteria for major and minor pairs are:
@@
         \mbox{\textbf{major pair:}}&\, \frac{1}{4}\leq \frac{\rm M_{*2}}{\rm M_{*1}}< 1 \\ 
-        \mbox{\textbf{minor pair:}}&\, \frac{1}{10}\leq \frac{\rm M_{*2}}{\rm M_{*1}} < \frac{1}{4}
+        \mbox{\textbf{minor pair:}}&\, \frac{1}{10}\leq \frac{\rm M_{*2}}{\rm M_{*1}} < \frac{1}{4}.
         \end{align*}
-        \kc{give the reason for this look at z0.png}
 
-        \kc{For each pair we store the pair separation in physical units and relative velocity.
-We require that each pair have a minimum separation of $15 \kpc$ between the primary and secondary, which is XX times the smoothing length of the simulation.
-}
-        \kc{need to explain how the separations and velocities are computed from the catalog etc. }
-        At smaller separations, more and more mass will be attributed to the central subhalo, which can lead to confusion in the SUBFIND catalogs. %the merger tree histories. \kc{the }.
+        For each pair, we calculate the physical separation (\kpc, not comoving \kpc) between the two subhalos using the \texttt{SubhaloPos} field from the group catalogs, and we require that each pair have a minimum separation of $15 \kpc$ between the primary and secondary.
+        The minimum separation cut is 20 times the smoothing length of the simulation at $z=0$ which ensures that \subfind can identify the subhalos as distinct objects.
 
-        If a primary subhalo does not have a companion that meets the stellar mass ratio criteria, separation criteria, or lower subhalo mass criteria (see Sec.~\ref{sec:methods-halos}), the subhalo will still be considered a primary.
+        If a primary subhalo does not have a companion that meets the stellar mass ratio criteria and separation criteria, the subhalo will still be considered a primary. 
         We refer to all primaries without companions as ``isolated primaries."
-        \kc{move this down to the secondary section}
-        If a subhalo passes the stellar mass cut for a primary, but does not have an associated companion from the selection criteria for a secondary (see next subsection), the subhalo will still be considered a primary.
-We refer to all primaries without companions as ``isolated primaries."
-        The total set of primaries includes both paired primaries and isolated primaries.
+        The total number of primaries includes both isolated primaries and those with companions, and is larger than or equal to the total number of pairs.
 
-        The pair catalog contains blah blah blah. 
-        1000 sets of pairs at each snapshot blah blah
-
-        The pair sample consists of 1000 sets of pairs at each snapshot, each set representing a different realization of the abundance matching prescription. 
-        At each snapshot, we calculate the median occurrence rate and kinematic values for each of the 1000 realizations. 
-        Each of the following plots shows the parameter's median and percentile spread calculated from the set of 1000 medians from each realization.
-
-        how do we use these catalogs? Interested in the aggregate properties of the full sample, and so we will treat blah blah
+        For each snapshot and each of the 1000 realizations of the abundance matching prescription, we create a set of isolated primaries and pairs. 
+        The final \paircat is the collection of all isolated primaries and pairs at each snapshot, and includes the following information: for each isolated primary, we store the subhalo mass and stellar mass from the given realization; from each pair we store the primary and secondary subhalo masses, stellar masses, group radius, and separation.
 
@@
     \includegraphics[width=\textwidth]{counts_1000.png}
-    \caption{(Top) Median number of dwarf (left) and massive (right) primaries and pairs as a function of redshift.
-    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations, as described in Sec.~\ref{sec:results}.
-    There are approximately 8 times as many dwarf primaries as massive primaries. 
+    \caption{(Top) Number of isolated low mass (left) and high mass (right) primaries and pairs as a function of redshift.
+    The solid and dashed lines represent the median of the set of total counts from each of the 1000 stellar mass realizations in the \paircat, while the shaded regions depict the 1-99 percentile spread of the median.
+    There are approximately 8 times as many low mass primaries as high mass primaries. 
     % dwarf galaxies
-    The dwarf primary count (solid) is at a minimum at $z=4$, rises to a maximum by $z\sim1$, then decreases from $z=1\to0$. 
-    The dwarf pair count (dashed) peaks at $z\sim2$.
+    The low mass primary count (left) peaks at $z=1$ (with $\sim 15000$ primary subhalos per realization), while the low mass pair count peaks at $z=2$ (with $\sim 3000$ pairs per realization). 
     % Massive galaxies (right)
-    The massive primary count (pink solid line in top right panel) behaves similarly to the dwarf primary count, with a minimum count at $z=4$ which rises to a maximum of $\sim2000$ halos per realization at $z\sim1$, then decreases slightly by $\sim5\%$ to $\sim$1800 halos by $z=0$.
-    Unlike dwarf pairs whose pair count peaks at $z=2$, pair count for massive galaxies (pink dashed line) follows similar behavior to the total massive primary count, with a minimum at $z=4$, and increasing to $z=\sim 1$ before leveling off.
-At very low redshift, the pair count and primary count have opposite behavior, with the pair count \textit{increasing} at very low redshifts of $z=0-0.25$ and \textit{peaking} at $z=0$.
-    \kc{where does it peak and what is }
-    (Bottom) Fraction of pairs per primary as a function of redshift (i.e., the ratio between dotted line and solid line in each column).
-Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$.
-The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.}
+    The high mass primary count (right) peaks at $z\sim1$ (with $\sim 1900$ primary subhalos per realization), while the high mass pair count peaks at $z=0$ (with $\sim 700$ pairs per realization). 
+    (Bottom) Total pair fraction (fraction of primaries with a companion secondary) as a function of redshift (see Sec.~\ref{sec:pairprops} for calculation details).
+    Low mass pair fraction is approximately flat between $z=2.5-4$, and decreases from $z=2.5$ to $z=0$. 
+    The high mass total pair fraction is flat or decreasing from $z=1$ to $z=4$, but spikes sharply between $z=0-0.25$.}
     \label{fig:counts}
@@
     \includegraphics[width=\textwidth]{smrdist_1000.png}
-    \caption{\kc{using all 1000 realizations - combined sample of XX catalog} Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs.
+    \caption{Stellar mass ratio distribution of all low mass (top) and high mass (bottom) pairs for all 1000 stellar mass realizations combined.
 Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$.
-Overall, the stellar mass ratio distribution of major and minor pairs of dwarf and massive galaxies show little evolution from $z=4$ (right) to $z=0$ (left).
-    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.}
+Overall, the stellar mass ratio distribution of major and minor pairs of low and high mass galaxies show little evolution from $z=4$ (right) to $z=0$ (left).
+    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both low and high mass pairs.}
     \label{fig:massratio}
@@
 \section{Sample: Overview of pair properties} \label{sec:pairprops}
-    Utilizing the pair catalog, We compute the \# of prims in each realization of the 
-    The full pair sample contains 1000 individual sets of pairs at each snapshot, for all 100 snapshots of the \tng100-1 simulation.
+    Utilizing the \paircat, for each snapshot, we compute the total number of primaries (isolated and paired) and pairs in each of the 1000 realizations, then take the median and 1 and 99 percentile spread on the median over all realizations.
+    Additionally, we compute the low and high mass total pair fraction (the total number of pairs, $\rm N_{pair}$, divided by the total number of primaries $\rm N_{prim}$) for each individual realization, then find the median and spread over all 1000 realizations.
 
-    Fig.~\ref{fig:counts} shows the redshift evolution of the median number of dwarf and massive primaries and pairs we identify over the redshift range $z=0-4$.   
-    For each snapshot, we calculate the median number of primaries and of pairs in each realization within the Pair Catalog, yielding a set of 1000 medians. 
-    The solid line and dashed lines are the median of this set of 1000 medians, and the shaded regions show the 1-99\% spread of the set.
+    Fig.~\ref{fig:counts} shows the median number (solid and dashed lines) of identified low and high mass primaries and pairs over the redshift range $z=0-4$.   
+    The shaded regions show the 1-99\% spread of the set, though the spread is hard to distinguish in the low mass case.
 
-    The number of identified primaries is smallest at $z=4$, and rises to a maximum around $z=1$ for both dwarf and massive primaries.        
-    There are approximately 8 times as many dwarf primaries as massive primaries.
+    The number of identified primaries is lowest at $z=4$, and rises to a maximum around $z=1$ for both low and high mass primaries.
+    The median count of low mass primaries (green solid line in top left panel) reaches a maximum of $\sim15000$ halos at $z\sim0.6$, then decreases by $\sim16\%$ to 12000 halos at $z=0$. 
+    The count of high mass primaries (pink solid line in top right panel) reaches a maximum of $\sim2000$ at $z\sim1$, then remains approximately constant to $z=0$. 
+    There are roughly 8 times as many low mass primaries as high mass primaries.
 
-    The median dwarf primary count (green solid line in top left panel) reaches a maximum of $\sim15000$ halos at $z\sim0.6$, then decreases by $\sim16\%$ to 12000 halos at $z=0$. 
-    The dwarf pair count (green dashed line) peaks much earlier at $z\sim2$ with $\sim3000$ pairs, and decreases to $\sim1000$ pairs at $z=0$.
-    From $z=4$ to $z=2$, the number of dwarf primaries doubles, as does the number of pairs due to the growth of structures over cosmic time.
-    The massive primary count (pink solid line in top right panel) reaches a maximum median of $\sim2000$ halos (in one realization) at $z\sim1$, then remains approximately constant to $z=0$. 
-    The pair count for massive galaxies (pink dashed line) behaves similarly to the primary count, increasing from $z=4$ to $z\sim1$, then leveling off to $z=0$.
+    Unlike the primary count, the pair counts for low and high mass pairs peak at very different redshifts. 
+    The count of low mass pairs (green dashed line) peaks much earlier at $z\sim2$ with $\sim3000$ pairs, and decreases to $\sim1000$ pairs at $z=0$.
+    % From $z=4$ to $z=2$, the number of dwarf primaries doubles, as does the number of pairs due to the growth of structures over cosmic time.
+    The pair count for high mass galaxies (pink dashed line), on the other hand, behaves more similarly to the primary count, increasing from $z=4$ to a peak at $z\sim1$, then leveling off through $z=0$.
 
-    The bottom panel of Fig.~\ref{fig:counts} shows the number of pairs divided by the number of primaries, or the fraction of pairs per primary as a function of redshift. 
-    Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$.
-The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.
+    The bottom panel of Fig.~\ref{fig:counts} shows the total pair fraction for low mass and high mass pairs, or equivalently, the fraction of primaries with a companion.
+    The total pair fractions for both low and high mass pairs are roughly flat for $z=2.5-4$, and display opposite behavior for low redshifts between $z=0-2.5$. 
+    The low mass pair fraction decreases from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the high mass pair fraction remains flat between $z=1-2.5$.
+    At very low redshifts, from $z=0-0.25$, the high mass pair fraction spikes sharply from $\sim 0.29$ to $\sim 0.36$, an increase of $25\%$.
 
-    include all 1000 realizations as a single "Combined Sample"
-    We show the distribution of stellar mass ratios between the secondary and primary of each dwarf and massive pair in Fig.~\ref{fig:massratio} from the Pair Catalog, com 
-    \kc{explain how we compute this}
-    all realizations.
-    % Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.
-    In general, the shape of the distribution remains constant from $z=0-4$ for both dwarfs and massive pairs, and between the dwarf and massive pairs at each redshift. 
-    Thus, the typical stellar mass ratio of pairs in our sample is independent of mass scale and of redshift. \kc{how much more likely are you to find 1/4 than 1:1 things? what about 1:10 to 1:4?}
-
-% Pair prop. end %
-%%%%%%%%%%%%%%%%%%
-
-% \begin{table*}[htb]
-%   \centering
-%     \begin{tabular}{lcc}
-%      & Dwarf Pairs & Massive Pairs \\\hline\hline
-%     % Group Mass & $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ & $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$  \\
-%     % Subhalo Max Mass &  &  \\
-%     % Subhalo Current Mass & $>1\times10^{10} \Msun$ & $> 5\times10^{11} \Msun$ \\
-%     Primary &$1\times10^{8} < \msam < 5\times10^{9} \Msun$ & $5\times10^{9} < \msam < 1\times10^{11} \Msun$\\\hline
-%     \end{tabular}
-%     \caption{\label{table:mass}Selection criteria for dwarf and massive pairs.}
-%     \end{table*}
-
-% equivalent snapshot table
-% \begin{table*}[tbp]
-%   \centering
-%   \begin{tabular}{l|cc|cccc} % increase this to 7 columns
-%     \hline \hline
-%    & {Snapshot} & {Number of primaries} & {Number of pairs}\\
-%    & \ill & \tng  & \illd & \illh & \tngd & \tngh \\ 
-%   \hline
-%   z = 0   &   135  &   99   & $11431.5_{-24.42}^{68.38}$ & $12650.0_{-25.84}^{46.84}$ & $13255.0_{-32.60}^{56.72}$ & $12035.0_{-69.24}^{20.36}$\\
-%   z = 1   &   85   &   50   &  $14769.0_{-30.24}^{47.28}$ & $16568.0_{-32.20}^{69.60}$ & $17445.5_{-40.86}^{51.90}$ & $15946.5_{-59.38}^{39.22}$ \\
-%   z = 2   &   68   &   33   &  $12602.5_{-31.98}^{45.94}$ & $14174.0_{-12.48}^{62.32}$ & $15413.5_{-34.62}^{28.86}$ & $14334.0_{-29.44}^{45.24}$ \\
-%   z = 3   &   60   &   25   &     $8533.5_{-54.50}^{39.46}$ & $9390.0_{-63.40}^{41.32}$ & $10901.0_{-44.64}^{46.56}$ & $10106.5_{-47.90}^{39.74}$  \\
-%   % z = 3.7   &   54   &   21   \\
-%   \hline \hline
-%   \end{tabular}
-%   \caption{\label{tab:equiv-snapshot} The snapshot number of the original \ill\ and the \tng\ simulations at redshifts $z=0-3$, as well as the median number dwarf (massive) primaries that were selected with $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$ ($5\times 10^{9} < \msam < 1\times 10^{11} \rm M_\odot$) in XX abundance matching realizations.
-\kc{fill in with numbers after doing more realizations} \kc{include takeaway}}
-%   \end{table*}
+    In Fig.~\ref{fig:massratio}, we show the combined distribution of stellar mass ratios of every pair from all 1000 realizations in the \paircat.
+    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both low and high mass pairs.
+    In general, the shape of the distribution remains constant from $z=0$ (left) to $z=4$ (right) for both low and high mass pairs, and is thus independent of mass scale and of redshift.
 
@@
 
-\section{Results: The frequency and kinematics of dwarf and massive pairs}
-We have created catalogs of isolated low and high mass galaxy pairs from $z=0-4$ in the TNG100-1 simulation. 
-In this section, we will analyze the occurrence rate and kinematic properties (physical separations and relative velocities) for major and minor pair types across cosmic time.
+\section{Results: The frequency of low mass and high mass pairs}
+We have created catalogs of isolated low and high mass galaxy pairs from $z=0-4$ in the TNG100 simulation. 
+In this section, we will analyze the occurrence rate of major and minor pair types across cosmic time.
 
-In Sec.~\ref{sec:results-frac}, we show the redshift evolution of the fraction of primaries with a major or minor companion (the ``pair fraction") and compare the results for dwarf pairs and massive pairs.
-In Sec.~\ref{sec:results-kinematics}, we look at the redshift evolution of the separations and relative velocities between primary and secondary halos of each pair.
-% need to specify this is snapshot by snapshot?
-In Sec.~\ref{sec:results-scaled}, we compare the separations and velocities scaled by the FoF group's virial properties. 
-Finally, in Sec.~\ref{sec:results-virialcut}, we take subsets of the Pair Catalog, selecting only pairs within some fraction of the virial radius, and illustrate the impact on the recovered low and high mass pair fractions.
+We are interested in the aggregate properties of the full sample, and so we will treat each stellar mass realization in the \paircat\ as an independent sample. 
+At each snapshot, we calculate the median occurrence rate of each of the 1000 realizations. 
+From this set of 1000 medians, we calculate the median and percentile spread which is shown in the following plots at the solid or dashed line, and the shaded region, respectively.
 
-%%%%%%%%%%%%%%%%%%%%%   
-% Definitions start %
-% \subsection{Definitions} \label{sec:results-defs}
-
-% Definitions end %
-%%%%%%%%%%%%%%%%%%%
+In Sec.~\ref{sec:results-frac}, we show the redshift evolution of the fraction of primaries with a major or minor companion (the ``pair fraction") and compare the results for low mass and high mass pairs.
+In Sec.~\ref{sec:results-frac-sepcut}, we look at the redshift evolution of pair fraction as a function of pair separation. 
+% In Sec.~\ref{sec:results-scaled}, we compare the separations and velocities scaled by the FoF group's virial properties. 
+% Finally, in Sec.~\ref{sec:results-virialcut}, we take subsets of the Pair Catalog, selecting only pairs within some fraction of the virial radius, and illustrate the impact on the recovered low and high mass pair fractions.
 
@@
 % Pair fraction section %
-    \subsection{Pair fraction}\label{sec:results-frac}
-    We determine the occurrence rate of a pair type by calculating the pair fraction. 
-    The pair fraction is defined here as the ratio of the number of pairs to the total number of primaries (isolated + paired):
-    $$\rm \frac{N_{pair-type}}{N_{primaries}}.$$
-    For example, the dwarf major pair fraction is calculated as the number of dwarf major pairs divided by the number of dwarf primaries. 
-    The pair fraction of dwarf or massive pairs with a major or minor companion gives the likelihood of finding a companion of a certain mass type about a primary identified in the field.
+    \subsection{Major and minor pair fractions}\label{sec:results-frac}
+    We determine the occurrence rate of a major or minor pair by calculating the pair fraction. 
+    The pair fraction is defined here as the ratio of the number of pairs to the total number of isolated \textit{and} paired primaries:
+    $$f_{p}=\rm \frac{N_{pairs}}{N_{primaries}}.$$
+    For example, the pair fraction of low mass major pairs is the number of low mass major pairs divided by the number of low mass primaries. 
+    The pair fraction can be understood as a measure of the likelihood of finding a companion of a certain mass type about a primary identified in the field.
 
-    Fig.~\ref{fig:pairratio} shows the pair fractions calculated for massive and dwarf pairs (including both major and minor pairs separately) as a function of time for $z=0-4$. 
-        % differences between massive and dwarf pairs? 
-    The dwarf pair fraction evolves distinctly from that of massive pairs.
-    Dwarf pair fractions (both major and minor) start at their minima at $z=0$, and increase by about 200\% by $z\sim2-2.5$, at which point the pair fractions level off and remain constant from $z=3-4$.
-    On the other hand, massive pair fractions reach their maxima at $z=0$, then abruptly declining to $z\sim0.25$, before remaining approximately constant from $z=1-4$.
-
-        % difference panels
-    The bottom panels of Fig.~\ref{fig:pairratio} shows the dwarf pair fraction subtracted from the massive pair fraction (labelled ``$\rm M-D$"). 
-    The pair fraction difference reaches a maximum at $z=0$ for both major and minor pairs, and declines to $z\sim2-2.5$ at which point the difference levels out close to 0, where major dwarf and massive pairs, as well as minor dwarf and massive, are equivalently common.
-
+    Fig.~\ref{fig:pairfrac} shows the pair fractions calculated for low and high mass pairs (including both major and minor pairs separately) as a function of time for $z=0-4$. 
         % differences between major and minor pairs? 
-    The median pair fraction of minor pairs is less than that of major pairs of the same mass range at all redshifts. 
-    This is due to the lower stellar mass ratio limit we put on our pairs. 
-    Expanding the mass ratio criteria of our minor pair sample to include stellar mass ratios between 1/10-1/100 in our minor pair sample increases the fraction of minor pairs by a factor of $>2$ for massive pairs and between $~1.5-2x$ for dwarf pairs.
+    The pair fraction of minor pairs is less than that of major pairs for both low and high mass pairs at all redshifts, due to the lower stellar mass ratio limit we put on our pairs.
+    If we lower the stellar mass ratio floor for minor pairs, the minor pairs would outnumber the major pairs.
+    % Expanding the mass ratio criteria of our minor pair sample to include stellar mass ratios between 1/10-1/100 in our minor pair sample increases the fraction of minor pairs by a factor of $>2$ for massive pairs and between $~1.5-2x$ for dwarf pairs.
 \kc{are there any additional takeaways from this?
@@
 
-        % what do we learn from this? what are the takeaways? where do we discuss this in more detail?
-    Overall, these results show that massive and dwarf pair counts evolve differently over time, particularly at very low redshift, despite the pair fractions being roughly equal at higher z. 
-    These differences could be a result of the different formation mechanisms at play in the evolution of the systems at these two different mass scales, or alternatively, from differences in satellite dynamics between dwarf and massive systems (see Sec.~\ref{sec:results-kinematics}).
-    The implications for the difference in the evolution of pair fractions for dwarf and massive pairs across time is discussed in detail in Sec.~\ref{sec:discussion}.
+        % differences between massive and dwarf pairs? 
+    The low mass pair fraction evolves distinctly from that of high mass pairs.
+    Low mass major and minor pair fractions start at their minima at $z=0$, and increase by about 200\% by $z\sim2-2.5$, at which point they level off and remain constant from $z=3-4$. 
+    On the other hand, high mass pair fractions reach their maxima at $z=0$, then abruptly declining to $z\sim0.25$, before remaining approximately constant from $z=1-4$.
+
+        % difference panels
+    The bottom panels of Fig.~\ref{fig:pairfrac} shows the low mass pair fraction subtracted from the high mass pair fraction (labelled ``$\rm High-Low$").
+    The pair fraction difference reaches a maximum at $z=0$ for both major and minor pairs, and declines to $z\sim2-2.5$. 
+    From $z=2.5-4$, the difference is approximately 0, and thus both major and minor pairs of high and low mass are equivalently common.
+
+        % takeaways 
+    Overall, these results show that low mass and high mass pair counts evolve differently over time, particularly at very low redshift, despite the pair fractions being roughly equal at higher redshift.
+    The implications for the difference in the evolution of pair fractions for low mass and high mass pairs across time is discussed in detail in Sec.~\ref{sec:discussion}.
 
@@
       \includegraphics[width=\textwidth]{pairfrac_1000.png}
-      \caption{
-        % Top plots ~
-        (Top) Median pair fraction, defined as the fraction of dwarf or massive primaries with a major (solid) or minor (dashed) companion by stellar mass (see Sec.~\ref{sec:methods-pairs}). 
-        Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
+      \caption{% Top plots ~
+        (Top) Median pair fraction, defined as the fraction of low mass or high mass primaries with a major (solid) or minor (dashed) companion by stellar mass (see Sec.~\ref{sec:methods-pairs}). 
+        Shaded areas show the 1-99 percentile range on the median (solid and dashed lines) from 1000 stellar mass realizations. 
           % massive pairs
-        The massive pair fraction (pink) remains approximately constant for $z>1$, with an average pair fraction of 0.16-0.17 for major pairs and 0.14-0.15 for minor pairs.
-Between $z=0.25$ and $z=0$, the massive major pair fraction increases to 0.207, while the minor pair fraction increases to 0.152.
+        The high mass pair fraction (pink) remains approximately constant for $z>1$, for both major and minor pairs. 
+        Between $z=0.3$ and $z=0$, the major pair fraction increases from $0.163^{+0.011}_{-0.010}$ to $0.207^{+0.012}_{-0.014}$, while the minor pair fraction increases from $0.125^{+0.017}_{-0.014}$ to $0.152^{+0.016}_{-0.017}$.
           % dwarf pairs
-        Dwarf pair fractions, shown in green, are approximately constant from $z=3-4$, then decline monotonically to $z=0$.
-The major pair fraction is $0.041$ at $z=0$ and $0.126$ at $z=3$, while the minor pair fractions are $0.034$ and $0.111$ at $z=0$ and $z=3$, respectively.
+        Low mass pair fractions, shown in green, are approximately constant from $z=3-4$, then decline monotonically to $z=0$.
+The major pair fraction is $0.041^{+0.003}_{-0.004}$ at $z=0$ and $0.126^{+0.008}_{-0.007}$ at $z=3$, while the minor pair fractions are $0.034\pm0.004$ and $0.111\pm0.008$ at $z=0$ and $z=3$, respectively.
         % Bottom plots ~
-        (Bottom) The median subtracted (massive - dwarf) pair fraction difference, with the shaded $1$-$99$ percentile range from 1000 abundance matching realizations.
-The pair fraction difference increases with decreasing redshift, peaking at $z=0$ with a difference of 0.166 for major pairs and 0.111 for minor pairs.
-This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly at low redshift.}
-      \label{fig:pairratio}
+        (Bottom) The median subtracted difference between high and low mass pair fractions, with the shaded $1$-$99$ percentile range from 1000 abundance matching realizations.
+The pair fraction difference increases with decreasing redshift, peaking at $z=0$ with a difference of $0.166\pm0.013$ for major pairs and $0.111\pm0.017$ for minor pairs.
+This shows that the redshift evolution of the pair fractions of low and high mass pairs proceeds differently, particularly at low redshift.}
+      \label{fig:pairfrac}
     \end{figure*}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% beging Kinematics results %
-    \subsection{Kinematic evolution}\label{sec:results-kinematics}
-    We also analyze the kinematic behavior of our pair sample as a function of time. 
-    Instantaneous pair separations are defined as the relative separation between the primary and secondary of each pair in the snapshot, and are computed in physical $\kpc$, and \textit{not} in comoving $\kpc/h$.
-    Similarly, relative velocities are defined as the relative velocity difference in the same snapshot between the primary and secondary of each pair, and are computed in physical $\kms$.
+% begining separation cut-pair fraction results %
 
-    In this section, we compute the median relative separations and velocities of all pairs in each snapshot, each of which includes the set of pairs from 1000 stellar mass realizations.
-    We separate the population of dwarf and massive pairs further into major and minor pairs to show how the stellar mass ratio between the primary and secondary may affect the kinematics.
+\subsection{Major pair fractions as a function of maximum separation}\label{sec:results-frac-cuts}
+    We also analyze subsets of the low and high mass major pairs that pass additional separation criteria. 
+    Here, we study two different sets of separation criteria to compare the resulting pair fractions of subsets of the low and high mass major pairs to the full sample shown in Fig.~\ref{fig:pairfrac}.
+    The first separation criteria that we employ selects pairs of different separations as a function of the size of the group's halo, as discussed in Sec.~\ref{sec:results-frac-vircut}. 
+    In Sec.~\ref{sec:results-frac-sepcut}, we use physical 3D separation cuts to compare the population of low separation major pairs of low and high mass.
 
-    % separations %
-        \subsubsection{Separations}
-        %% text on separation vs. redshift plot
-        %% intro to separations & bulk results
-        % We calculate the median relative separations between the primary and secondary halos of the pairs identified in our dwarf pair sample and massive pair sample. 
-        % We split the results by the stellar mass ratio of each pair, dividing the sample into "major" pairs and minor pairs, which allows us to compare the behavior of different mass ratio systems individually in the dwarf and massive mass range.
-        Our results are 
-        illustrated in Fig.~\ref{fig:sep}, which shows the redshift evolution of the median relative separations for dwarf pairs and massive pairs. 
-        %% the behavior of massive and dwarf pairs
-        We show that the median relative separations between the primary and secondary of both dwarf and massive pairs increases with decreasing redshift, regardless of pair type. 
-        A combination of physical mechanisms is likely spurring the increase in median pair separations at low $z$. 
-        For example, high $z$, low separation pairs may undergo mergers at earlier times, removing them from the sample at later snapshots, thus increasing the median separation over time. 
-        Alternatively, mass accretion, from the cosmic web and/or from mergers, causes dark matter halos to become both more massive and more extended as $z\to0$. 
-        Thus, the growth of structure that is expected in $\Lambda$CDM could naturally lead to an increase in typical pair separations at low $z$.
-        We explore the relationship between halo growth and relative pair separations in Sec.~\ref{sec:results-scaled}.
+\subsubsection{Separation cut - fraction of the virial radius}\label{sec:results-frac-vircut}
+    \todo{here! }
+              Interestingly, the recovered fraction of the full sample at <0.5rvir is <50\% but still closely resembles the full pair frac at z<2!
+thus, at low z, the behavior of the pair fractions is dominated by halos within 0.5 Rvir ~~
 
-        %% the DIFFERENCE between dwarf and massive pairs
-        Dwarf and massive pairs exhibit similar relative separation trends as a function of time, however, the scale of the typical relative separations of pairs in our sample is set by the mass halo of the primary.
-        Dwarf pairs and massive pairs have a relative separation difference of $\sim150\kpc$ at $z=0$, and a difference of $\sim40$ at $z=4$.   
-        This is expected, as more massive halos have larger spheres of influence and more substructure. 
-        \kc{maybe move this sentence to discussion:}But, the difference between dwarf and massive pair relative separation ranges, and their evolution over time begs the question: what does this mean for observational pair selection criteria at different mass scales and at different redshifts?
-        We leave the discussion of the implications our relative separation results on pair selection criteria for Sec.~\ref{sec:discussion}.
-
-        %% the difference between major and minor pairs
-        In addition, the bottom panels of Fig.~\ref{fig:sep} shows the median subtracted difference between the relative separations calculated for major pairs and minor pairs of both mass types. 
-        There is a small offset in the median separations of major and minor dwarf pairs (between $10-25\,\kpc$ from  $z=0-1$ and approximately $5\,\kpc$ from $z=1-4$), and a larger offset for major and minor massive pairs (between $25-100\,\kpc$ from  $z=0-1$ and approximately $10-40\,\kpc$ from $z=1-4$).
-        The major-minor offset is likely a result of more major pairs merging more quickly (thus at earlier times and higher $z$) due to the increased effect of dynamical friction, thus leading to a population of low relative separation minor pairs that have yet to merge.
-
-        %% separation plots
+    %figures
+    %%%%%%%%%%%%%%%%%%%%
     \begin{figure*}[htp]
         \centering
-          \includegraphics[width=\textwidth]{sep_1000.png}
-          \caption{(Top) Median physical separation in kpc between the primary and secondary halos of dwarf pairs (left) and massive pairs (right) as a function of redshift. 
-          Shaded areas show the 1-99\% percentile range of the median from 1000 abundance matching realizations. 
-          Major pairs are shown in solid lines, and minor pairs are depicted with dashed lines.
-          In general, for both dwarf pairs and massive pairs, the average physical separation of the two halos in a pair increases for as the redshift decreases from $z=4\to0$. 
-          % Dwarf pairs
-          The typical separation between major (minor) dwarf pairs increases from $42(38)\,\kpc$ at $z=4$ to a peak of $128(109)\,\kpc$ at $z=0$.
-          % Massive Pairs
-          The separation between major (minor) massive pairs likewise increases from $81(71)\,\kpc$ at $z=4$ to $288(205)\,\kpc$ at  $z=0$.
-          % Difference plots
-          (Bottom) The median difference and 1-99\% range (as above) between the median separation of major pairs and minor pairs.
-          At dwarf mass scales, minor companions tend to be $\sim10-20\kpc$ closer to their primary than major companions, while minor massive pairs have a relative separation that is $10-50\kpc$ less than major pairs.
+        \includegraphics[width=\textwidth]{pairfrac_vircut.png}
+        \caption{ The pair fraction of the subset of high mass (pink) and low mass (green) pairs with 3D separations within a fraction of the group's virial radius (see Sec.~\ref{sec:results-frac-sepcut} for details of calculations).
+        The median and 1-99 percentile spread are shown by the solid lines and shaded regions, respectively.
+        Pair fractions for the subsample of low and high mass pairs with separations less that 0.25\Rvir are constant or declining with increasing redshift, and do not resemble the pair fractions for the full pair sample.
+        However, increasing the maximum separation of a pair to $0.5\Rvir$ leads to low and high mass major pair fractions that take on the same behavior as the full sample for $z<2$, where the low mass pair fraction decreases, and the high mass pair fraction (on average) increases.
+        The pair fraction trends for the low and high mass subsamples become similar to those of the true pair fractions (as seen in Fig.~\ref{fig:pairfrac}) when all pairs within $1.5\Rvir$ are included in the subsample.
+      % bottom plot
+        (Bottom) The fraction of the total collection of pairs in the subset of pairs that passes each separation cut.
+        More than 50\% of low and high mass pairs have separations $<1.5\Rvir$ at all redshifts. 
+        When the maximum separation is increased to $2.5\Rvir$, the recovery rate at all redshifts is $>90\%$ for low mass pairs, and $>80\%$ for high mass pairs. 
         }
-          \label{fig:sep}
+      \label{fig:vircut}
     \end{figure*}
+    %%%%%%%%%%%%%%%%%%%%
 
-    % velocities %
-        \subsubsection{Relative Velocities}
-        %% text on velocity vs. redshift plot
-        %% intro to velocity & bulk results
-        % In addition to the separations between the primary and secondary halos of our pair sample, we also calculate the median relative velocity between the halos of each pair.
-        % Once again we split the results into "major" and "minor" pairs for both the dwarf and massive pair sample to get a better understanding of the impact of the mass of the secondary. 
-        In Fig.~\ref{fig:vel}, we show the median relative velocity between the primary and secondary halos of dwarf and massive pairs as a function of redshift. 
-        %% the behavior of massive and dwarf pairs
-        We find that the median relative velocity of a pair decreases towards lower redshift, regardless of pair type.
-        The median velocity of a major dwarf pair decreases linearly from $130$ at $z=4$ to $70\,\kms$ at $z=0$.
-Likewise, the median velocity for major massive pairs decreases from $260$ at $z=4$ to $170\,\kms$ at $z=0$, though with more spread at high $z$.
-        \todo{} As the circular velocity of a secondary object about the primary is inversely proportional to the radius, it is not surprising to find a decrease in the relative velocity for pairs at lower redshift due to the decrease in concentration/increase in the virial radius of the halo as $z\to0$.
-\kc{citation needed}
-        See Sec.~\ref{sec:results-scaled} for more details.
+\subsubsection{Separation cut - physical separations}\label{sec:results-frac-sepcut}
+    We calculate the pair fraction for all major low mass and high mass pairs, excluding pairs that exceed separations of $(50,70,100,150,200,300)\kpc$. 
+    This additional separation criterion creates subsamples of the \paircat, and contains low and high mass pairs with separations between $15-50\kpc$, $15-70\kpc$, and so on\footnote{See Sec.~\ref{sec:methods-pairs} for a description of the $15\kpc$ lower separation cutoff.}.
 
-        %% the DIFFERENCE between dwarf and massive pairs
-        As in the case of relative separations of pairs, dwarf and massive pairs show a similar evolutionary trend in relative velocity as a function of redshift, though at different scales determined by the mass of the primary.
-        Massive pairs have a median relative velocity $\sim100\kms$ larger than dwarf pairs at $z=0$, and $\sim140\kms$ at $z=4$. \kc{see comment}
-        %This is also not particularly surprising, since the circular velocity prop to $( M/r)^1/2,$, and massive primaries may be >10x as massive as dwarf primaries, while the separation between a massive primary and it's secondary will only be 2x further than a dwarf pair.
+    Fig.~\ref{fig:sepcut} shows the pair fractions for the subsamples of pairs with separations lower than the physical separation listed at the top of each column. 
+    Similarly to the previous pair fraction plots, the top row presents the total median (solid line) of the collection of 1000 individual medians from each realization, and the shaded regions show the 1-99\%ile spread on the same collection of individual medians.
+    The bottom row of the plot shows the "recovery fraction", or the number of pairs in each subsample compared to the full sample of major pairs.
 
-        %% the difference between major and minor pairs
-        Fig.~\ref{fig:vel} also includes a panel showing the subtracted median difference at each snapshot of the minor pair from the major pair.
-Unlike the relative separation, the relative velocities do not have a strong dependence on mass ratio of the pairs.
-        The offsets between the relative velocities of dwarf major and minor pairs is between $0-5\,\kms$, and between $0-25\,\kms$ for massive major and minor pairs.
-\kc{see comment} %does it make sense that minor pairs are faster?
+    As the maximum separation increases (left to right), so too does the pair fraction, as you begin to include more and more of the distantly separated pairs, as well as the recovery fraction. 
+    The low mass major pair fraction (green) maintains roughly the same behavior (decreasing with decreasing redshift) for each separation cut, and closely resembles the pair fraction of the full sample (in Fig.~\ref{fig:pairfrac}) for maximum separation cuts higher than $150\kpc$.
+    The low mass pair fraction does not change significantly by excluding pairs with separations $>150\kpc$, thus the pair fraction profile is dominated by the closest 50\% of low mass pairs.
 
-        %% velocity plots 
+    On the other hand, none of the subsamples of the high mass pairs display similar behavior to the full sample. 
+    In particular, for smaller separation cuts (50\kpc or 70\kpc), the redshift evolution of the pair fraction more closely resembles the low mass pairs.
+    For $r_{sep}<300\kpc$, the trends in the high mass major pair fraction is only similar at $z>1.5$, where it levels off, rather than continues to increase at higher $z$.
+
+    The recovery rate for low mass pairs is universally higher than for high mass pairs.
+    By increasing the allowed separations $300\kpc$, virtually all low mass pairs are included in the subsample, with $>90\%$ of the total sample at $z=0$, and $\sim100\%$ for $z>1$.
+    However, high mass pairs have a median separation of $\sim300\kpc$ at $z=0$, which means the recovery rate for low separation high mass pairs is very low. 
+    In order to get a recovery fraction of at least 50\% at all redshifts from $z=0-4$, the subset of high mass pairs must include pairs with separations at least up to $300\kpc$.
+
+    %figures
+    %%%%%%%%%%%%%%%%%%%%
     \begin{figure*}[htp]
         \centering
-          \includegraphics[width=\textwidth]{vel_1000.png}
-          \caption{
-            (Top) Median relative velocity (in \kms) between the primary and secondary halos of dwarf pairs (left) and massive pairs (right) as a function of redshift. 
-            Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
-            The overall behavior of the redshift evolution of pair relative velocities is nearly identical for dwarf and massive pairs.
-            As the redshift decreases from $z=4$ to $z=0$, the average relative velocity of a pair decreases for both dwarf and massive pairs.
-            % brief describe
-            The median relative velocity of a dwarf pair (major or minor) is $70\,\kms$ at $z=0$ and $133\,\kms$ at $z=4$, and of a massive pair is $170\,\kms$ at $z=0$ and $260\,\kms$ at $z=4$ ($295\,\kms$ for a minor pair at $z=4$).
-            % Difference plot
-            (Bottom) The median relative velocity difference between major and minor pairs ("Maj - Min"), and 1-99\% shaded region.
-            There is little difference between the relative velocity of major and minor dwarf pairs (bottom left), with minor pairs having a relative velocity of $0-5\,\kms$ higher than major pairs. 
-            Massive pair types (bottom right) also have little velocity difference at low redshift, although minor pairs have a relative velocity between $1-20\,\kms$ faster than major pairs at higher redshift ($z>\sim 2.5$).
+        \includegraphics[width=\textwidth]{pairfrac_sepcut.png}
+        \caption{      % top plot
+        (Top) The major pair fraction of the subset of high mass (pink) and low mass (green) pairs with 3D separations less than the value given at the top of each column. 
+        The median and 1-99 percentile spread are shown by the solid lines and shaded regions, respectively. 
+        % what do we notice
+        The behavior of the redshift evolution of major pair fractions for low and high mass pairs is strongly dependent on the maximum separation included in the subset.
+        Pair fractions of low mass and high mass pairs are nearly indistinguishable for the lowest separation pairs $r_{sep}<50\kpc$ at every redshift. 
+        For $z<2$, the true pair fraction behaviour (as seen in Fig.~\ref{fig:pairfrac}) becomes distinguishable when the maximum separation is $300\kpc$.
+      % bottom plot
+        (Bottom) The fraction of the total collection of pairs in the subset of pairs that passes each separation cut.
+        Less than 50\% of massive pairs have separations $r_{sep}<50\kpc$, and 50-100\% have separations $r_{sep}<300\kpc$. 
+        Between 20-60\% of low mass pairs have separations $r_{sep}<50\kpc$, while a separation cut of $r_{sep}<300\kpc$ captures roughly 100\% of the low mass pair population at all redshifts. 
         }
-          \label{fig:vel}
+      \label{fig:sepcut}
     \end{figure*}
-% end kinematic results %        
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-% begin scaled results %
-    \subsection{Scaled Kinematics}\label{sec:results-scaled}
-    %% intro to scaled kin. evolution & bulk results
-    In the previous section, Sec.~\ref{sec:results-kinematics}, we show that the separations and relative velocities of dwarf and massive pairs evolve similarly as a function of redshift. 
-    However, the magnitude of pair separations and velocities are set by the mass scale of the pair. 
-    For example, a dwarf pair at $z=0$ has a median relative velocity of $70\kms$, while a massive pair will have a median velocity of $175\kms$ at $z=0$.
-
-    To explore the impact of halo growth and mass scale the kinematics pairs, we study the relative separation of a primary and secondary halo scaled by the virial radius ($r_{vir}$) of the FoF group, and the relative velocity ($v_{vir}$) divided by the circular speed of the FoF group at the virial radius.
-    That is, 
-    $$\rm r_{scaled}=\scsep$$
-    $$\rm v_{scaled}=\scvel$$
-    $$\rm v_{vir}=\sqrt{G M_{vir}/r_{vir}},$$
-    where $\rm r_{vir}$ is the group radius \texttt{Group\_R\_TopHat200} in physical $\kpc$ from the group catalogs, and $\rm M_{vir}$ the total group mass \texttt{Group\_M\_TopHat200} in $\Msun$.
-
-    In Fig.~\ref{fig:scaled}, we show the median scaled separation and scaled velocity for dwarf and massive major pairs as a function of time. 
-    Minor pairs show the same trends, and so we have omitted them here for brevity.
-
-    %% the behavior of massive and dwarf pairs
-    Overall, the median scaled separation of dwarf pairs and massive pairs do not evolve significantly differently from $z=4\to0$.
-    In fact, the median separation of halos in a pair is smaller than the group virial radius at $z<2.5$, but is larger than the virial radius at $z>2.5$.
-    %maybe not bound at high z, though could become bound by low z by mass accretion ? 
-    Dwarf pairs tend to have slightly larger separations relative to the group virial radius than massive pairs at almost all redshifts, though the spread of median scaled separations is large for massive pairs at $z>2$.
-
-    The median scaled velocities of dwarf pairs and massive pairs increase at lower redshift (see right panel of Fig.~\ref{fig:scaled}).
-In fact, dwarf and massive pairs evolve almost identically for $z=0-4$, and thus, the redshift evolution of a pair at either of these mass scales is independent of the total mass of the system.
-    We also find that pairs at $z<0.5$ have relative velocities in excess of their virial velocity, but are smaller than the virial velocity for $z=0.5-4$.
-
-    %% distributions of scaled kinematics
-    In Fig.~\ref{fig:scaled-dist}, we show the distribution of scaled separations and velocities at redshifts $z=0,1,2,3,4$. 
-    The distributions show roughly equivalent shape and extent for both dwarf and massive scaled kinematics, and do not vary significantly with redshift.
-
-    % behavior of massive vs. dwarf 
-    Overall, our results imply that there is little difference between high mass and low mass pairs in the redshift evolution of pair velocities, though pair separations seem to have a weak dependence at low redshift on the type of pair.
-Inner regions of the halo , high mass pairs tend to be even closer, likely due to
-    This appears opposite to the physical separations, but when you scale to the total mass of the system, the 
-    Fof groups are increasng in size . \todo{}
-
-    %% scaled evolution plot
-    \begin{figure*}[htp]
-      \centering
-      \includegraphics[width=\textwidth]{scaledcombo_1000.png}
-      \caption{ \label{fig:scaled}
-          %  Left
-          (Left) Median scaled separation as a function of redshift (see Sec.~\ref{sec:methods} for the definitions of scaled separation and velocity).
-All shaded regions show $X-XX\%$ percentile spread from 1000 abundance matching realizations.
-          % any overall trends?
-          At $z>2$, a majority of all pair types have separations greater than the group virial radius, while at $z<2$, a majority of pairs have smaller separations.  
-          Massive major pairs at low redshift tend to have slight smaller scaled separations than dwarfs at $z<\sim2$, but vary significantly at higher redshifts. 
-          % Right 
-          (Right) Median scaled velocity as a function of redshift.
-          % any overall trends?
-          All pairs show a peak in scaled velocity around $z=0$.
-From $z=0-0.5$, a majority of both dwarf and massive pairs have relative velocities larger than the circular velocity of their group at the virial radius.
-At $z>0.5$, however, the majority of pairs have $v_{rel}<v_{vir}$.
-The scaled velocity evolves nearly identically for dwarf and massive pairs.
-          % Bottom 
-          (Bottom) The scaled separation/velocity of dwarf major pairs subtracted from that of massive major pairs, indicated by ``M-D".
-          The scaled separation difference shows small differences between the dwarf and massive population, with dwarf pairs having slightly higher scaled separation for $z<1$.
-The scaled velocity difference is $\sim0$ at all redshifts.
-          Minor pairs (not shown here) follow the same trends as major pairs in both the massive and dwarf regime.}
-    \end{figure*}
-
-    %% scaled distribution plot
-    \begin{figure*}[htp]
-      \centering
-      \includegraphics[width=\textwidth]{scaledcombodist_1000.png}
-      \caption{
-          Scaled separation distribution (left) and scaled velocity distribution (right) at $z=0,1,2,3$, and $4$, normalized by the total number of pairs at the corresponding redshift. 
-          % the point? what am I trying to get across
-          The first thing to note is that there is relatively little redshift-dependent change in the overall shape and extent of each distribution, and thus the scaled quantities are only loosely independent of redshift.
-          Additionally, the shape and extent of the dwarf pair (top) and the massive pair (bottom) distributions are nearly identical, thus the scaled quantities are also independent of the halo mass scale.
-Thus, the kinematics of dwarf pairs and massive pairs evolve roughly equivalently when normalizing by the halo mass.
-          Unscaled versions of this plot are discussed in Sec.~\ref{sec:discussion}.
-      }
-      \label{fig:scaled-dist}
-    \end{figure*} 
-% end scaled results %
-%%%%%%%%%%%%%%%%%%%%%%
-
-% end kinematics %
-%%%%%%%%%%%%%%%%%%
-
-\subsection{Separation cuts as fxn of virial radius}
-put in plots~ 
+    %%%%%%%%%%%%%%%%%%%%
 % end Results section%
-%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%
@@
 
-    \kc{ make a subsection about the equivalence of our findings with the dark matter simulation) We make brief note of results for our equivalent analysis using the dark matter only TNG100-Dark simulation as well in Sec.~\ref{sec:results}.}
+%     \kc{ make a subsection about the equivalence of our findings with the dark matter simulation) We make brief note of results for our equivalent analysis using the dark matter only TNG100-Dark simulation as well in Sec.~\ref{sec:results}.}
 
-\subsection{Implications for the differences in pair fractions of dwarf and massive pairs}
-In Sec.~\ref{sec:results-frac}, we presented the pair fraction of massive and dwarf galaxy pairs and found that the relative frequency of the two populations evolve distinctly from $z=0-4$. 
-While the frequency of massive pairs compared to the number of massive primaries is roughly constant and become more common at low redshift, dwarf major and minor pairs become more than 50\% less common at $z=0$ compared to $z=2$.
-Since scaled separations and velocities do not change drastically between dwarf and massive pairs, the difference in the evolution of the pair fractions indicates that the merger processes of each population may proceed differently.
+% \subsection{Implications for the differences in pair fractions of dwarf and massive pairs}
+% In Sec.~\ref{sec:results-frac}, we presented the pair fraction of massive and dwarf galaxy pairs and found that the relative frequency of the two populations evolve distinctly from $z=0-4$. 
+% While the frequency of massive pairs compared to the number of massive primaries is roughly constant and become more common at low redshift, dwarf major and minor pairs become more than 50\% less common at $z=0$ compared to $z=2$.
+% Since scaled separations and velocities do not change drastically between dwarf and massive pairs, the difference in the evolution of the pair fractions indicates that the merger processes of each population may proceed differently.
 
-% One scenario that could explain this behavior is a very rapid merger timescale for dwarf pairs, and a slower merger timescale for massive pairs. 
-% In this case, dwarf pairs will merge quickly after formation, thus depleting the number of dwarf pairs at later times. 
-% Simultaneously, the merged remnant of a dwarf pair is likely to join the population of isolated primaries until star formation finally pushes the stellar mass up into the massive primary regime.
-% The likelihood of a dwarf pair becoming a massive primary with a minor companion is very small, since only XX\% of dwarf pairs have a major tertiary companion. \kc{calculate the number of }
+% % One scenario that could explain this behavior is a very rapid merger timescale for dwarf pairs, and a slower merger timescale for massive pairs. 
+% % In this case, dwarf pairs will merge quickly after formation, thus depleting the number of dwarf pairs at later times. 
+% % Simultaneously, the merged remnant of a dwarf pair is likely to join the population of isolated primaries until star formation finally pushes the stellar mass up into the massive primary regime.
+% % The likelihood of a dwarf pair becoming a massive primary with a minor companion is very small, since only XX\% of dwarf pairs have a major tertiary companion. \kc{calculate the number of }
 
-% Alternatively, if the dark matter halo and stellar mass of a dwarf galaxy pair increase enough through cosmic accretion or very minor mergers from $z=4$ to $z=2$, the pair will be reclassified as a massive pair at later times.
+% % Alternatively, if the dark matter halo and stellar mass of a dwarf galaxy pair increase enough through cosmic accretion or very minor mergers from $z=4$ to $z=2$, the pair will be reclassified as a massive pair at later times.
 
-For example, dwarf galaxy merger timescales may be significantly shorter than massive galaxy merger timescales, which would deplete the population of dwarf galaxy pairs by low redshift. 
-Additionally, early dwarf galaxy mergers may result in systems that are identified as massive pairs at late times, and massive pairs may grow such that they exceed our mass criteria, thus leading to an apparent overall decrease in the number of pairs.
-The drop in the absolute number of dwarf and massive primaries at low z as shown in Fig.~\ref{fig:counts} indicates that indeed many of these systems leave the mass range specified by our selection criteria between $z=0-1$.
-However, since the number of dwarf primaries is roughly constant between $z=0.5-1.5$, but the number of pairs is still decreasing during this time, this indicates that mergers are occurring during this time, and not yet leaving the mass regime specified.
-In fact, the number of dwarf pairs that are removed from the sample from $z=0$ to $z=2$ is 10 times greater than the total number of massive pairs, indicating that these pairs are not simply accreting matter and moving into the higher mass bin.
+% For example, dwarf galaxy merger timescales may be significantly shorter than massive galaxy merger timescales, which would deplete the population of dwarf galaxy pairs by low redshift. 
+% Additionally, early dwarf galaxy mergers may result in systems that are identified as massive pairs at late times, and massive pairs may grow such that they exceed our mass criteria, thus leading to an apparent overall decrease in the number of pairs.
+% The drop in the absolute number of dwarf and massive primaries at low z as shown in Fig.~\ref{fig:counts} indicates that indeed many of these systems leave the mass range specified by our selection criteria between $z=0-1$.
+% However, since the number of dwarf primaries is roughly constant between $z=0.5-1.5$, but the number of pairs is still decreasing during this time, this indicates that mergers are occurring during this time, and not yet leaving the mass regime specified.
+% In fact, the number of dwarf pairs that are removed from the sample from $z=0$ to $z=2$ is 10 times greater than the total number of massive pairs, indicating that these pairs are not simply accreting matter and moving into the higher mass bin.
 
-\subsection{Comparison to previous pair fraction studies}
-We performed a pair fraction analysis for dwarf and massive galaxy pairs in the TNG100 simulation, utilizing the full 6D position and velocity information that simulations enable. 
-However this means that direct comparison to pair fractions reported from observations is not straight-forward, as observationally selected pairs uniquely suffer from contamination, due to projected pairs, and restrictive separation criteria, that exclude more widely separated pairs.
-Fortunately, a number of previous studies of pair fractions in the Illustris simulations have used lightcones to create mock images of observationally-motivated fields, from which they select pairs in the same fashion that is typically done with observational data.
-These studies select simulated galaxies based on stellar mass, and then use cuts on the projected separation and line of sight velocity difference to select pairs, which permits direct comparison between simulations and observations.
+% \subsection{Comparison to previous pair fraction studies}
+% We performed a pair fraction analysis for dwarf and massive galaxy pairs in the TNG100 simulation, utilizing the full 6D position and velocity information that simulations enable. 
+% However this means that direct comparison to pair fractions reported from observations is not straight-forward, as observationally selected pairs uniquely suffer from contamination, due to projected pairs, and restrictive separation criteria, that exclude more widely separated pairs.
+% Fortunately, a number of previous studies of pair fractions in the Illustris simulations have used lightcones to create mock images of observationally-motivated fields, from which they select pairs in the same fashion that is typically done with observational data.
+% These studies select simulated galaxies based on stellar mass, and then use cuts on the projected separation and line of sight velocity difference to select pairs, which permits direct comparison between simulations and observations.
 
-At the low mass end, \citet{Besla2018} quantified dwarf galaxy pair fractions in Illustris-1, both projected and physical pairs, which enabled a direct comparison of the cosmologically-derived pair fractions with an equivalently selected dwarf pair fraction from SDSS.
-The pair selection criteria for dwarf galaxies, here defined as stellar masses\footnote{The stellar masses of galaxies from the Illustris simulations used in \citet{Besla2018} are from the median of the \citet{Moster2013} abundance matching prescription, the same as used in this work, rather than the stellar mass values from the simulations.} from $2\times10^{8} < M_{*} < 5\times10^{9}\,\Msun$, include a projected separation criteria of $r_{p} < 150\,\kpc$ and a relative line-of-sight velocity difference $\Delta v_{\rm los} < 150\,\kms$.
+% At the low mass end, \citet{Besla2018} quantified dwarf galaxy pair fractions in Illustris-1, both projected and 3D pairs, which enabled a direct comparison of the cosmologically-derived pair fractions with an equivalently selected dwarf pair fraction from SDSS.
+% The pair selection criteria for dwarf galaxies, here defined as stellar masses\footnote{The stellar masses of galaxies from the Illustris simulations used in \citet{Besla2018} are from the median of the \citet{Moster2013} abundance matching prescription, the same as used in this work, rather than the stellar mass values from the simulations.} from $2\times10^{8} < M_{*} < 5\times10^{9}\,\Msun$, include a projected separation criteria of $r_{p} < 150\,\kpc$ and a relative line-of-sight velocity difference $\Delta v_{\rm los} < 150\,\kms$.
 
-By searching for pairs in a projected space while having access to the true 3D positions and velocities of the galaxies, they quantified the contamination fraction and found that up to $\sim40$\% of identified companions were unrelated but appeared to be close due to projection effects.
-In Illustris, they found that the projected major pair fraction of dwarf galaxies at $z\sim0$ is $f_{p,proj.}\sim0.005-0.012$, while the . \kc{where tf are these numbers from??? }
-The total pair fraction (including all stellar mass ratios) is $0.032\pm0.005$ for the projected mock catalogs, which are consistent with SDSS equivalently-selected pairs, which find a total pair fraction of $0.035\pm0.3$.
+% By searching for pairs in a projected space while having access to the true 3D positions and velocities of the galaxies, they quantified the contamination fraction and found that up to $\sim40$\% of identified companions were unrelated but appeared to be close due to projection effects.
+% In Illustris, they found that the projected major pair fraction of dwarf galaxies at $z\sim0$ is $f_{p,proj.}\sim0.005-0.012$, while the . \kc{where tf are these numbers from??? }
+% The total pair fraction (including all stellar mass ratios) is $0.032\pm0.005$ for the projected mock catalogs, which are consistent with SDSS equivalently-selected pairs, which find a total pair fraction of $0.035\pm0.3$.
 
-However, using the full physical catalogs, they find a lower pair fraction of $0.02\pm0.004$.
+% However, using the full physical catalogs, they find a lower pair fraction of $0.02\pm0.004$.
 \kc{I *THINK* this is the fraction of TOTAL pairs (N\_1 from the tables)?
@@
 otherwise I don't know how it's different.}
-For comparison, when we modify our pair selection criteria to match those of \citet{Besla2018}, and require a physical separation $r_{\rm sep}< 150\,\kms$ and a 3D relative velocity $\Delta v_{\rm los} < 150\,\kms$, we find a dwarf major pair fraction of XX at $z=0$, which is slightly SKZ than the \citet{Besla2018} results.
-This is/is not surprising because SKZ.
+% For comparison, when we modify our pair selection criteria to match those of \citet{Besla2018}, and require a 3D separation $r_{\rm sep}< 150\,\kms$ and a 3D relative velocity $\Delta v_{\rm los} < 150\,\kms$, we find a dwarf major pair fraction of XX at $z=0$, which is slightly SKZ than the \citet{Besla2018} results.
+% This is/is not surprising because SKZ.
 
-As the behavior of the major pair fraction as a function of primary stellar mass is consistent between the projected mock catalogs and the SDSS catalogs, they conclude that cosmological simulations can be used to reliably constrain observational pair fractions of dwarf mergers across time.
+% As the behavior of the major pair fraction as a function of primary stellar mass is consistent between the projected mock catalogs and the SDSS catalogs, they conclude that cosmological simulations can be used to reliably constrain observational pair fractions of dwarf mergers across time.
 \kc{across time...
 is this true?}
-Additionally, which projected and physical pair catalogs yield different absolute values of pair fractions, their behavioral trends as a function of mass are nearly identical such that, in terms of trends, projected and physical pair fractions will yield similar results.
+% Additionally, which projected and 3D pair catalogs yield different absolute values of pair fractions, their behavioral trends as a function of mass are nearly identical such that, in terms of trends, projected and 3D pair fractions will yield similar results.
 
-% While the study uses projected separations and line of sight velocities, we can assume that the same \textit{trends} are valid for full-6D selected pairs, such that our pair fraction trends can be reasonably compared to those in observations.
+% % While the study uses projected separations and line of sight velocities, we can assume that the same \textit{trends} are valid for full-6D selected pairs, such that our pair fraction trends can be reasonably compared to those in observations.
 
-Separate studies have analyzed the pair fractions of higher mass galaxies in Illustris simulation. 
-In particular, \citet{snyder2017} created mock catalogs using lightcones in the Illustris-1 simulation to pick pairs in the same fashion as done in observations. 
-Specifically, they consider only major pairs with: $1\times 10^{11}>M_{*,1} >1\times 10^{10.5}Msun$, projected distances between $14\kpc-71\kpc$, and a redshift separation of $\Delta z<0.02(1+z_{pri}$, which corresponds to a velocity separation of $<1.8\time10^4\kms$.
-They find that the major pair fraction for primaries with stellar mass $1\times 10^{10.5-11}Msun$ is constant or decreasing for $z>1$. 
-Additionally, they compared to observational studies \kc{what studies} that selected pairs with stellar mass $(M* > 10^{10.8}\Msun)$, $(10 <d/(kpc h-1) < 30)$, and $(Msec/Mpri > 0.1)$, and found good agreement between the measured pair fractions as a function of redshift.
-Thus, projected pair fractions in the Illustris simulation are likely representative of those found in observations for massive galaxy pairs.
+% Separate studies have analyzed the pair fractions of higher mass galaxies in Illustris simulation. 
+% In particular, \citet{snyder2017} created mock catalogs using lightcones in the Illustris-1 simulation to pick pairs in the same fashion as done in observations. 
+% Specifically, they consider only major pairs with: $1\times 10^{11}>M_{*,1} >1\times 10^{10.5}Msun$, projected distances between $14\kpc-71\kpc$, and a redshift separation of $\Delta z<0.02(1+z_{pri}$, which corresponds to a velocity separation of $<1.8\time10^4\kms$.
+% They find that the major pair fraction for primaries with stellar mass $1\times 10^{10.5-11}Msun$ is constant or decreasing for $z>1$. 
+% Additionally, they compared to observational studies \kc{what studies} that selected pairs with stellar mass $(M* > 10^{10.8}\Msun)$, $(10 <d/(kpc h-1) < 30)$, and $(Msec/Mpri > 0.1)$, and found good agreement between the measured pair fractions as a function of redshift.
+% Thus, projected pair fractions in the Illustris simulation are likely representative of those found in observations for massive galaxy pairs.
 
-\citet{snyder2023} extended this work to utilize the TNG simulation, and created mock images of extragalactic survey fields mimicking future planned surveys like JADES.
-From the mock images, they calculated the pair fraction for major pairs with projected separations between $5-70 \kpc$ and with redshift separations of $\Delta z< 0.02(1+z)$, and also found flat or decreasing major pair fractions.
-This is in agreement with our work, as our major pair fraction for massive galaxies is approximately constant or decreasing with higher redshift for $z>1$. 
-While we cannot directly compare the values of the pair fractions themselves, as the projected and physical pair separations will yield very different pair fractions as shown in \citet{Besla2018}, we can say that the behavioral trends are the same.
-Pair fractions computed using physical separations do not have to account for contamination due to projection effects, which would increase the inferred pair fraction, however our separation criteria is much less stringent, which would also increase the pair fraction.
+% \citet{snyder2023} extended this work to utilize the TNG simulation, and created mock images of extragalactic survey fields mimicking future planned surveys like JADES.
+% From the mock images, they calculated the pair fraction for major pairs with projected separations between $5-70 \kpc$ and with redshift separations of $\Delta z< 0.02(1+z)$, and also found flat or decreasing major pair fractions.
+% This is in agreement with our work, as our major pair fraction for massive galaxies is approximately constant or decreasing with higher redshift for $z>1$. 
+% While we cannot directly compare the values of the pair fractions themselves, as the projected and 3D pair separations will yield very different pair fractions as shown in \citet{Besla2018}, we can say that the behavioral trends are the same.
+% Pair fractions computed using 3D separations do not have to account for contamination due to projection effects, which would increase the inferred pair fraction, however our separation criteria is much less stringent, which would also increase the pair fraction.
 
-% Alejandro's paper connection: studies are finding good agreement between simulations and TNG, as evidenced by this paper.
+% % Alejandro's paper connection: studies are finding good agreement between simulations and TNG, as evidenced by this paper.
 They found that TNG simulated images well approximated the morphologies of galaxies in the KIDS survey, although they were a bit more compact and lumpy.
@@
 
-% ? maybe to do: plot with comparison values 
-\subsection{Implications for observational pair selection criteria}
-    %figures
-    %%%%%%%%%%%%%%%%%%%%
-    \begin{figure*}[htp]
-      \centering
-      \includegraphics[width=\textwidth]{sepdist_1000.png}
-      \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right).
-Major pairs are shown as solid lines, while minor pairs are dotted.
-The median separation of each pair type (from Fig.~\ref{fig:sep}) is shown in solid (major) and dotted (minor) vertical black lines.
-      At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively).
-However, at low redshift, the separation distribution tends to spread out more evenly across a large range of separations, thus increasing the median.
-        }
-      \label{fig:sep-dist}
-    \end{figure*}
-    %%%%%%%%%%%%%%%%%%%%
-    %%%%%%%%%%%%%%%%%%%%
-    \begin{figure*}[htp]
-      \centering
-      \includegraphics[width=\textwidth]{frac_selected.png}
-      \caption{ The fraction of total pairs selected with additional separation selection criteria as a function of redshift. 
-        }
-      \label{fig:frac-select}
-    \end{figure*}
-    %%%%%%%%%%%%%%%%%%%%
+% % ? maybe to do: plot with comparison values 
+% \subsection{Implications for observational pair selection criteria}
+%     %figures
+%     %%%%%%%%%%%%%%%%%%%%
+%     \begin{figure*}[htp]
+%       \centering
+%       \includegraphics[width=\textwidth]{frac_selected.png}
+%       \caption{ The fraction of total pairs selected with additional separation selection criteria as a function of redshift. 
+%         }
+%       \label{fig:frac-select}
+%     \end{figure*}
+%     %%%%%%%%%%%%%%%%%%%%
 
-    % outline
-    \begin{itemize}
-        \item examples of typical pair selection criteria (i.e. <75 kpc, velocity crit, etc.)
-        \item Show how low separation cuts affect pair fractions      
-        \item Sep distribution plot and explanation (text below) 
-        \item Plot of \% of total pairs selected as function of z for different separation criteria (or maybe better is to do total as function of separation, for different redshifts?) 
-        \item What does this mean for JWST and future surveys?
-    \end{itemize}
+%     % outline
+%     \begin{itemize}
+%         \item examples of typical pair selection criteria (i.e. <75 kpc, velocity crit, etc.)
+%         \item Show how low separation cuts affect pair fractions      
+%         \item Sep distribution plot and explanation (text below) 
+%         \item Plot of \% of total pairs selected as function of z for different separation criteria (or maybe better is to do total as function of separation, for different redshifts?) 
+%         \item What does this mean for JWST and future surveys?
+%     \end{itemize}
 
-% text on the separation distribution plot
-Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$, and includes all 1000 AM realizations. 
-For reference, the median at each corresponding redshift from Fig.~\ref{fig:sep} (that is, the median of the medians of each realization) are shown in light black vertical lines.
-Each plot is normalized such that the area under an individual curve is 1.
-    % the redshift evolution
-At $z=4$, all pair types (dwarf and massive, major and minor) have narrow distributions that pile up around 0 $\kpc$\footnote{Note that only pairs with separations $>10\kpc$ are included in this analysis, see Sec.~\ref{sec:methods-pairs}.}, with ranges between $10-150\,\kpc$ for dwarf pairs and $10-300\,\kpc$ for massive pairs.
-The distributions become more and more broad as $z\to0$, where separations range between $\sim10-400\,\kpc$ for dwarf pairs and $\sim10-1000\,\kpc$ for massive pairs.
+% % text on the separation distribution plot
+% % Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$, and includes all 1000 AM realizations. 
+% % For reference, the median at each corresponding redshift from Fig.~\ref{fig:sep} (that is, the median of the medians of each realization) are shown in light black vertical lines.
+% % Each plot is normalized such that the area under an individual curve is 1.
+%     % the redshift evolution
+% % At $z=4$, all pair types (dwarf and massive, major and minor) have narrow distributions that pile up around 0 $\kpc$\footnote{Note that only pairs with separations $>10\kpc$ are included in this analysis, see Sec.~\ref{sec:methods-pairs}.}, with ranges between $10-150\,\kpc$ for dwarf pairs and $10-300\,\kpc$ for massive pairs.
+% % The distributions become more and more broad as $z\to0$, where separations range between $\sim10-400\,\kpc$ for dwarf pairs and $\sim10-1000\,\kpc$ for massive pairs.
 
-Since the distribution of separations changes dramatically from $z=4$ to $z=0$, the population of low separation pairs that are selected at $z=4$ includes the majority of true pairs, but this is not the case at low z.
-At low z, separation criteria must be very broad to encompass the majority of pairs. 
-Figure~\ref{fig:frac-select} shows the fraction of pairs that have separations less than $\{50, 75, 100, 150\}\kpc$.
-At high redshift ($z\sim2-4$) a majority of pairs are included in the selection, however at lower redshift ($z\sim0-1$), the pair completeness decreases substantially, with fewer than XX\% of the total number pairs for XX separation criteria.
+% % Since the distribution of separations changes dramatically from $z=4$ to $z=0$, the population of low separation pairs that are selected at $z=4$ includes the majority of true pairs, but this is not the case at low z.
+% % At low z, separation criteria must be very broad to encompass the majority of pairs. 
+% % Figure~\ref{fig:frac-select} shows the fraction of pairs that have separations less than $\{50, 75, 100, 150\}\kpc$.
+% % At high redshift ($z\sim2-4$) a majority of pairs are included in the selection, however at lower redshift ($z\sim0-1$), the pair completeness decreases substantially, with fewer than XX\% of the total number pairs for XX separation criteria.
 
-As JWST is expected to image dwarfs (give stellar mass range) out to z=XX in XX survey, the selection criteria for dwarf pairs that are applied will affect the inferred pair fractions greatly.
+% As JWST is expected to image dwarfs (give stellar mass range) out to z=XX in XX survey, the selection criteria for dwarf pairs that are applied will affect the inferred pair fractions greatly.
 
-%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\pagebreak
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \pagebreak
+
 \section{Summary and Conclusions}\label{sec:summary}
-In this paper, we collect a large set of dwarf and massive subhalo pairs from the Illustris TNG100-1 simulation. 
-Pairs are selected from the full volume over all 100 snapshots of the simulation, though the sample size of pairs in the first 20 snapshots ($z>4.2$) is extremely small. 
-Major and minor pairs are determined using the stellar mass ratio between the primary and secondary halo using stellar masses from 1000 random realizations of the abundance matching prescription. 
-From this pair sample, we calculate the pair fractions and snapshot by snapshot kinematics of 4 different pair types: dwarf major pairs, dwarf minor pairs, massive major pairs, and massive minor pairs.
+% In this paper, we collect a large set of dwarf and massive subhalo pairs from the Illustris TNG100-1 simulation. 
+% Pairs are selected from the full volume over all 100 snapshots of the simulation, though the sample size of pairs in the first 20 snapshots ($z>4.2$) is extremely small. 
+% Major and minor pairs are determined using the stellar mass ratio between the primary and secondary halo using stellar masses from 1000 random realizations of the abundance matching prescription. 
+% From this pair sample, we calculate the pair fractions and snapshot by snapshot kinematics of 4 different pair types: dwarf major pairs, dwarf minor pairs, massive major pairs, and massive minor pairs.
 
-Our main findings are as follows:
-\begin{itemize}
-    \item The pair fraction for dwarf and massive pairs does not proceed identically throughout cosmic time.
+% Our main findings are as follows:
+% \begin{itemize}
+%     \item The pair fraction for dwarf and massive pairs does not proceed identically throughout cosmic time.
 In fact, the two mass scales have opposite behavior at low z.
 The number of dwarf pairs per dwarf primary decreases from $z=2\to0$, while the number of massive pairs per massive primary is approximately constant from $z=4\to0.25$, with an abrupt increase at lower redshift.
-    \item The median physical separation between the primary and secondary subhalo of a pair increases with decreasing redshift.
+%     \item The median 3D separation between the primary and secondary subhalo of a pair increases with decreasing redshift.
 The typical separation of a dwarf (massive) pair is $120\,\kpc$ ($240\,\kpc$) at $z=0$ and $40\,\kpc$ ($80\,\kpc$) at $z=4$.
-    \item The median relative velocity between the primary and secondary subhalo of a pair decreases towards lower redshift.
+%     \item The median relative velocity between the primary and secondary subhalo of a pair decreases towards lower redshift.
 The typical relative velocity of a dwarf (massive) pair is $70\,\kms$ ($175\,\kms$) at $z=0$ and $132\,\kms$ ($290\,\kms$) at $z=4$.
-    \item The separation scaled by the total virial radius of the group is similar for dwarf and massive pairs, though massive pairs tend to have lower scaled separations for redshifts between $z=0-2$.
+%     \item The separation scaled by the total virial radius of the group is similar for dwarf and massive pairs, though massive pairs tend to have lower scaled separations for redshifts between $z=0-2$.
 The relative velocity scaled by the circular velocity at the virial radius evolves identically for both dwarf and massive pairs, indicating that the relative velocities are self-similar at different mass scales.
-    \item All of the above trends hold true for both major and minor pairs of the same mass range (i.e., the conclusions for the dwarf major pairs hold too for the dwarf minor pairs). 
-\end{itemize}
+%     \item All of the above trends hold true for both major and minor pairs of the same mass range (i.e., the conclusions for the dwarf major pairs hold too for the dwarf minor pairs). 
+% \end{itemize}
 
-Our results are consistent with prior works that have studied the pair fractions of massive and dwarf galaxies in the Illustris simulations in a projected sense. 
-The agreement between the pair fraction trends from projected and from physical pair selection criteria points to the IllustrisTNG simulation's robust ability to reproduce the characteristics of galaxy pairs from observations.
+% Our results are consistent with prior works that have studied the pair fractions of massive and dwarf galaxies in the Illustris simulations in a projected sense. 
+% The agreement between the pair fraction trends from projected and from 3D pair selection criteria points to the IllustrisTNG simulation's robust ability to reproduce the characteristics of galaxy pairs from observations.
 
-Additionally, we conclude that:
-\begin{itemize}
-    \item Dwarf galaxy pairs and massive galaxy pairs likely have different evolutionary and merger processes which result in the opposing behavior of dwarf and massive pair fractions as a function of redshift.
-    \item The separation criteria used to observationally identify pairs likely results in an incompleteness of at least XX\% by $z=0$, though is less problematic for high redshift pairs where pairs tend to have smaller separations.
-\end{itemize}
+% Additionally, we conclude that:
+% \begin{itemize}
+%     \item Dwarf galaxy pairs and massive galaxy pairs likely have different evolutionary and merger processes which result in the opposing behavior of dwarf and massive pair fractions as a function of redshift.
+%     \item The separation criteria used to observationally identify pairs likely results in an incompleteness of at least XX\% by $z=0$, though is less problematic for high redshift pairs where pairs tend to have smaller separations.
+% \end{itemize}
 
-Our conclusions point to the importance of time-evolving pair selection criteria that account for the natural separation increase of pairs at the universe expands.
+% Our conclusions point to the importance of time-evolving pair selection criteria that account for the natural separation increase of pairs at the universe expands.
 
-\kc{other main takeaways?}
+% \kc{other main takeaways?}
 
-\begin{itemize}
-    \item otherMain takeaways: (maybe include these within main findings bullets~)
-        \begin{itemize}
-            \item lit comp.
-            \item dwarfs not equal massives 
-            \item JWST imps.
-        \end{itemize}
-    \item Future work
-\end{itemize}
+% \begin{itemize}
+%     \item otherMain takeaways: (maybe include these within main findings bullets~)
+%         \begin{itemize}
+%             \item lit comp.
+%             \item dwarfs not equal massives 
+%             \item JWST imps.
+%         \end{itemize}
+%     \item Future work
+% \end{itemize}
 

### 2023-07-14 paper/pears.tex
done with my intro!! *party*

@@
 \newcommand{\subcat}{\textit{Subhalo Catalog}}
+%\newcommand{\lsubcat}{\textit{Low Mass Subhalo Catalog}}
+%\newcommand{\hsubcat}{\textit{High Mass Subhalo Catalog}}
 \newcommand{\starcat}{\textit{Subhalo + Stellar Mass Catalog}}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\shorttitle{Frequency of galaxy pairs}
+\shorttitle{Pair fractions in TNG100}
 \shortauthors{Chamberlain et al.}
@@
 \title{
-  Frequency of low and high mass galaxy pairs in the IllustrisTNG cosmological simulation
-}
+  % Pair fractions of low mass and high mass galaxy pairs in the TNG100 cosmological simulation
+  % low mass and high mass galaxy pairs evolve differently as a function of redshift
+  A new framework for recovering the mass and redshift dependence\\ of galaxy pair fractions across cosmic time }
+% Differences in the redshift evolution of low mass and high mass galaxy pairs in the TNG100 cosmological simulation
 
@@
 
+\author{others}
+
 \begin{abstract}
-
+  Galaxy pair fractions for low mass galaxies (DEFINE) are understudied across cosmic time.
+In particular, it is unclear whether low mass galaxy pair fractions are expected to evolve similarly to that of high mass galaxies (DEFINE high mass) in CDM theory.
+There has been no systematic study to ensure that any differences in CDM simulation can be captured in observational surveys.
+  In this study we *** Illustris, quick methods
+    define pair fractions self-consistently, WE find BLAH
+    we also a conduct a study to assess the impact of pair selection criteria based on separation cuts on the resulting pair fractions . We find BLAH. 
+    If you apply the same separation, you wash out these effects, but we know that they exist in merger fracs, so how do we observe this ?    
+    This sample is also used to place our Local Group of galaxy pairs in cosmological context across cosmic time for the first time --> high level 
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
+% galaxy mergers 
+    Galaxy mergers have been studied in detail as a mechanism for driving galaxy evolution, and have been identified as a trigger of, for example, 
+    active galactic nuclei (AGN)~\citep[e.g.][]{Hopkins2008,comerford15,Blecha2018,ellison19}, 
+    star formation~\citep[e.g.][]{Mihos1996, DiMatteo2008,Patton2013, hopkins13,patton20,hani20}, 
+    and changes in morphology~\citep[e.g.][]{Conselice2003,lotz08,casteels14,rg17,Guzman-Ortega2023}. 
+    Constraining the merger rate for galaxies is critical for quantifying the importance of mergers for galaxy evolution and hierarchical assembly.
 
-\begin{itemize}
-    \item Galaxy mergers are a feature of LCDM and support the growth of galaxies across cosmic time.
-    \item The frequency of finding pairs tells us about how often we might expect: starbursts, SMBH mergers, the importance/role of mergers in building stellar mass/morphologies of galaxies today, SFHs, etc.
-    \item pair fraction at high masses has been well studied both obs and theoretically.
-There are studies of high mass (Mstar = 5e9-1e11Msun) pairs.
-These studies are typically done in projection for comparison to observational campaigns.
-    \item There are studies of low mass pairs (define what you mean by this), but only at low z, or as satellites of more massive systems (analogs of LG). 
-    \item in the era of jwst, these studies will be pushed to lower masses and high z, however, from a theory perspective, pair fractions at low masses have been under-studied (first 2 ish paragraphs ~ )
-    \item There are reasons to believe that high and low mass (Mstar = 1e8-5e9Msun) pairs might evolve differently, so it's important to study the low mass end too.
+    In practice, merger rates cannot be measured straightforwardly from observations and, rather, are calculated by converting the observed frequency of a galaxy merger signature (i.e., asymmetry, concentration, pair fraction, etc.) to a merger rate using an observability timescale~\citep[e.g.][]{lotz11}.
+    Low mass galaxies are most often morphologically disturbed by fly-bys and non-merger interactions~\citep{Martin2021}, and star forming galaxies at high redshift tend to be clumpy and asymmetric, even in isolation~\citep{Wuyts2013}, thus pair fractions offer likely the most robust method of observationally quantifying merger rates.
 
-    \item Also, major and minor mergers are important for different reasons, so studying them as separate systems is well motivated.
-        - is major high mass vs major low mass different, etc since these two types of mass ratios lead to different things 
-        - importance of mergers in high vs low mass galaxies (major mergers may be less important to SFH of Universe etc - look at sabrina's papers)
-    \item Systematically understanding the underlying difference between low and high mass pairs, Projected vs.
-3D separations/pairs Two routes of studying galaxy pairs are through observations and simulations, but simulations allow us to fully understand the 3D position and velocity of objects.
-    \item in this study, we'll be quantifying the pair fraction of low mass pairs, and self consistently comparing to the pair fraction of high mass systems
-    \item In this work, we aim to characterize the pair fraction of both high and low mass galaxies, major and minor pairs, consistently as a function of time. 
-\end{itemize}
-cite Stierwalt for low mass pairs 4485/4490 (iso vs non iso pairs) 
-Pearson Besla 2016 
-Pearson Besla 2018 4485/4490
-Luber Pearson Besla 
-Nevin
+    Pair fractions of high mass ($M_*\gtrsim10^{10}\Msun$) galaxies have been well studied across cosmic time both observationally~\citep[e.g.][]{Patton2000,lotz11,Ferreras2014, Man2016,Duncan2019}, and theoretically~\citep[e.g.][]{rg15,snyder2017,snyder2023}, with theoretical studies typically done in projection for comparison to observational campaigns.
+    Low mass galaxy pairs ($10^8<M_*<5\times10^9\Msun$) have been studied at low redshift~\citep[e.g.][]{stierwalt15,pearson16,Besla2018,Paudel2018,Luber2022},
+    but are less well understood across cosmic time owing to the difficulty in observing faint systems outside of the Local Volume. 
+    However, JWST will significantly revolutionize our ability to find such systems at higher redshift~\citep{Behroozi2020}.
 
-Discussion section: 
-what does this mean for our understanding of the LG (isolated mass analogs) 
-ngc 4490/4485 as another low z example (minor dwarf pair)
+    There are reasons to believe that low mass and high mass pairs evolve differently as a function of time.
+    For example, semi-empirical and cosmological studies find that galaxy merger rates vary both with redshift and the mass of the most massive galaxy of the pair~\citep[see e.g.][]{Stewart2009,Hopkins2010,rg15}.
+    % Such differences are likely to give rise to differences in the pair fractions of low and high mass pairs.
+    It is thus reasonable to assume that the pair fractions of these two mass scales reflect these evolutionary differences as well.
+
+    The redshift evolution of low and high mass pair fractions has not yet been studied in simulations in a self-consistent way, where high mass and low mass pairs are selected from simulations using otherwise equivalent selection criteria.
+    We aim to characterize the redshift behavior of pair fractions of low mass and high mass pairs, independent of environmental and projection effects, and to create a robust framework by which to fairly compare pair fractions of different mass scales across cosmic time.
+
+    In this study, we take the approach of self-consistently selecting physically associated pairs of low mass ($10^8<M_*<5\times10^9\Msun$) and high mass $(5\times10^9<M_*<10^{11}\,\Msun)$ galaxies. 
+    Specifically, we identify major ($1-1/4$) and minor $(1/10-1/4)$ pairs from $z=0-4.2$ in the IllustrisTNG cosmological simulation, TNG100. 
+    We require that pairs are part of the same FoF group and that no other more massive perturbers are nearby, which allows us to ensure that the recovered pair fractions are inherent to the population of selected pairs rather than a function of environment.
+
+    Typically, observational studies of pair fractions apply projected separation cuts that are constant over time and do not vary with the mass of the target system. 
+    To fairly test for differences in the evolutionary behavior of pair fractions, especially in observational studies, it is necessary to determine whether this is an appropriate technique for faithfully recovering true pair fraction behavior.
+    % it will be necessary to apply the proper theoretical framework for interpretting and analyzing low mass and high mass systems equivalently. 
+    In this study we identify how the application of a fixed separation criteria affects inferred pair fractions, and make recommendations for a time and mass evolving separation cut to permit equitable pair fraction comparisons between different mass regimes.
+    % We identify how the application of To this end, we apply one set of fixed separation cuts, and a second set of separation cuts that varies as a function of mass and redshift, and identify how these two methods
+
+    Finally, there are a number of galaxy pairs in the Local Group that are mass analogs of the isolated pairs in our sample.
+    For example: the MW--M31 system is a high mass major pair, the MW--LMC and M31--M33 systems are high mass minor pairs, and the LMC--SMC are a low mass minor pair.
+    Studies have examined the frequency of such configurations, particularly at low redshift or in the form of progenitor systems of the Local Group in cosmological simulations~\citep{Bk2011,Fattahi2013,Patel2017a-Orbits,Geha2017,Mao2021}, but the prevalence of such pairs in isolation has not yet been quantified as a function of redshift.
+    We utilize our pair dataset to quantify the likelihood of finding isolated mass-analogs of Local Group pairs as a function of redshift, particularly when the present day separations of these systems are folded in.
+
+    This paper is structured as follows. 
+    In Section~\ref{sec:methods}, we outline our methodology for selecting physically associated high mass and low mass pairs from the TNG simulation. 
+    In Section~\ref{sec:pairprops}, we provide an overview of properties of the selected sample, including the number of primaries, pairs, and their stellar mass ratios as a function of time. 
+    We present the time evolving pair fraction of high mass and low mass pairs in Section~\ref{sec:results}, and show how they change for different separation criteria. 
+    In Section~\ref{sec:discussion}, we discuss the implications of the differences between low and high mass pair fractions for observational campaigns and give context to our results by drawing comparisons to Local Group pairs.
+    Finally, we summarize our results and conclusions in Section~\ref{sec:summary}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Methodology}\label{sec:methods}
-We aim to quantify and characterize the frequency, or occurrence rate, of low mass ($\rm\ms{}=10^{8}-5\times 10^{9}\Msun$) and high mass ($\rm\ms{}=5\times10^{9}-10^{11}\Msun$) galaxy pairs in cosmological simulations as a function of cosmic time.
-To this end, we utilize the IllustrisTNG simulation to select halo pairs at each snapshot according to a strict set of selection criteria as outlined in the remainder of this section. 
+We aim to quantify and characterize the frequency, or pair fraction, of low mass ($\rm\ms{}=10^{8}-5\times 10^{9}\Msun$) and high mass ($\rm\ms{}=5\times10^{9}-10^{11}\Msun$) galaxy pairs in cosmological simulations as a function of cosmic time.
+To this end, we utilize the \tng\ simulation to select subhalo pairs as a function of redshift, according to the selection criteria outlined in the remainder of this section.
+
 In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulation utilized in this study.
-Sec.~\ref{sec:methods-halos} outlines the initial mass cuts used to define our \subcat, to which we will 
-add stellar mass information. %consist of the set of subhalos from which we will select pairs.
+Sec.~\ref{sec:methods-halos} outlines the initial mass cuts used to define our \subcat, to which we will add stellar mass information. 
 Sec.~\ref{sec:methods-am} outlines the abundance matching prescription used to associate dark matter subhalos with stellar masses, and the creation of the \starcat, from which we will select pairs.
 Sec.~\ref{sec:methods-pairs} describes the second set of selection criteria that we use to finally construct the \paircat.
-% Finally, Sec.~\ref{sec:pairprops} details some of the properties of our entire pair sample, including the total number of pairs and stellar mass ratios. -- Note: created new section
 
@@
         % Brief description of TNG hydro and which run we use.
-    The \tng\ project~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} consists of a suite of dark-matter-only $N$-body as well as full physics cosmological simulations consistent with the \textit{Planck2015} \lcdm\  cosmology~\citep{Planck2015}.
-    In this study we utilize data from the main high resolution, full physics run of the (110.7\Mpc)$^3$ volume simulation, \textsl{TNG100-1}, which follows the evolution of baryons and $1820^3$ dark matter particles from $z=127$ to $z=0$.
+    The IllustrisTNG project~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} consists of a suite of dark-matter-only $N$-body and full physics cosmological simulations that adopt the \textit{Planck2015} \lcdm\  cosmology~\citep{Planck2015}.
+    % GB edited below 
+    In this study we utilize data from TNG100-1, the main high resolution, full physics simulation of a (110.7\Mpc)$^3$ volume (hereafter TNG100). 
+    This simulation follows the evolution of baryons and $1820^3$ dark matter particles from $z=127$ to $z=0$.  
+    The volume of this simulation is sufficiently large, and resolution is sufficiently high, to conduct a simultaneous analysis of the statistics of both low mass and high mass galaxy pairs, as shown by studies of pair statistics in similarly sized volumes~\citep{Sales2013,Patel2017a-Orbits,Patel2017b-Masses,Besla2018}.
+% more?
 
@@
     This catalog was created using the Friends-of-Friends (FoF) algorithm~\citep{davis1985}, which links nearby particles to define large halos of associated particles, from which subhalos are identified as over-dense and gravitationally bound dark matter structures.
-    In addition, we utilize the merger trees provided by the \texttt{SUBLINK} algorithm~\citep{rg15}, which tracks subhalos between snapshots using their DM particle data in order to trace mass growth and merger histories of subhalos between snapshots.
-
-    The high resolution of the TNG100-1 simulation permits a direct comparison of low mass and high mass galaxy pair fractions without concern for incompleteness at the low mass end from unresolved low mass pairs (details in~\ref{sec:methods-halos}).
-    Additionally, the volume of this simulation provides a large enough sample of massive halo pairs to allow for a statistically significant comparison.
+    In addition, we utilize the merger trees provided by the \texttt{SUBLINK} algorithm~\citep{rg15}, which tracks subhalos between snapshots, enabling us to trace the mass evolution of our selected subhalos.
 
@@
 % Choosing halos section %
-    \subsection{Choosing dwarf and massive subhalos in TNG} \label{sec:methods-halos}
-    Galaxies form in dark matter subhalos, so our pair sample will consist of pairs of subhalos within these larger group structures.
-    In this section, we've outlined the steps to create the \subcat, which we will utilize to assign stellar masses to each of the dark matter subhalos.
+    \subsection{Choosing low and high mass subhalos in TNG100} \label{sec:methods-halos}
 
-    We are interested in the inherent frequency of galaxy pairs in the field. 
-    The largest perturbers of a subhalo are typically part of the same group, as a consequence of the FoF algorithm. 
-    Thus, selecting from the most massive subhalos of a group ensures that the pairs are roughly isolated. 
-    In addition, we have confirmed that over 99\% of subhalos are isolated from large perturbers within 1 \Mpc.
-    This isolation criteria, which is a feature of our selection process, ensures that the final selected pairs are not dynamically influenced by nearby massive groups.
+    In this section, we outline the steps to create the \subcat, which we will utilize to assign stellar masses to each of the dark matter subhalos to create our low mass and high mass galaxy catalogs.
 
-    The following selection process is repeated for each snapshot of the simulation over a redshift range of $z=0-\sim4$, at which point the population of massive subhalo pairs falls off rapidly (see Sec.~\ref{sec:pairprops} for more details).
+    % GB edited 
+    We are interested in the inherent frequency of low and high mass galaxy pairs in the field, rather than in over dense environments. 
+    This will allow us to assess whether there are fundamental differences in the frequency of pairs as a function of mass scale that are independent of environmental factors. 
+    As such, we must ensure that our target subhalos are sufficiently isolated.  
+    We do this by placing limits on the total mass of the FoF group to which our low mass or high mass samples belong.
 
-    First, at each snapshot, we invoke a cut on the total FoF group mass, \MG{}, given by \texttt{Group\_M\_TopHat200} in the TNG100 group catalogs. 
-    We define the group mass range for low mass and high mass groups as 
+    The following selection process is repeated for each snapshot of the simulation over a redshift range of$z=0-\sim4$.  
+    We stop our analysis at $z=4.2$ since the population of massive subhalo pairs falls off rapidly at larger redshifts, where the sample size of high mass primaries falls well below 100 subhalos per realization.
+
+    First, at each snapshot, we apply a cut on the total FoF group mass, \MG{}, given by \texttt{Group\_M\_TopHat200} in the TNG100 group catalogs. 
+    We define the group mass range for low mass and high mass groups as: 
     \begin{align*}
@@
     \end{align*}
-    The group mass criteria is fixed for all redshifts, which means that some low mass groups at high $z$ may be the progenitors of high mass systems at $z=0$.
-    Note that all masses used in this analysis are physical units, such that masses from the group catalogs are divided by $h$ to get units of \Msun.
+    The FoF group mass criteria is fixed for all redshifts, which means that some low mass groups at high $z$ may be the progenitors of high mass systems at $z=0$.
+    Note that all masses used in this analysis are physical units, meaning that masses from the group catalogs are divided by $h$ to get units of \Msun.
 
-    Selecting low mass pairs from the low group mass range ensures that we are not selecting satellite systems in the halos of more massive systems, nor low mass pairs in a large group. 
-    Additionally, $z\sim0$ groups of high mass will host isolated mass analogs of the MW--M31 and MW--LMC systems, while the low mass groups will host isolated mass analogs of an LMC--LMC or LMC--SMC pair.
+    By requiring that the total FoF group mass does not exceed the above limits, we ensure that there are no subhalos more massive than these limits that will perturb the dynamical state of identified pairs.
+    For example, selecting low mass pairs from the low mass FoF groups ensures that the selected pairs are not satellite systems of high mass subhalos. 
+    We have confirmed that over 99\% of subhalos selected from FoF groups that obey the listed mass limits are isolated; meaning, they are not within $1.5\,\Mpc$ of perturbers more massive than the given FoF group.
+
+    % GB removed
+  %  Selecting low mass pairs from the low group mass range ensures that we are not selecting satellite systems in the halos of more massive systems, nor low mass pairs in a large group. 
+  %  Additionally, $z\sim0$ groups of high mass will host isolated mass analogs of the MW--M31 and MW--LMC systems, while the low mass groups will host isolated mass analogs of an LMC--LMC or LMC--SMC pair.
 
         % explain what halos we will move forward with. 
-    From the set of groups that pass the group mass cut, we create a catalog of all subhalos within each group that pass a ``current mass" threshold, such that the subhalo mass at the given snapshot, given by \texttt{SubhaloMass} field in the group catalogs, is
+    From the set of FoF groups that pass the group mass cut, we create a catalog of all subhalos within each FoF group that pass a current ``minimum mass" threshold.  
+    We require that the subhalo mass (\Mhalo\footnote{Note that for the TNG100 hydro run, the subhalo mass is the total sum of all bound dark \textit{and} baryonic matter.}) at the given snapshot, defined by the \texttt{SubhaloMass} field in the group catalogs, is:
     \begin{equation*}
-    \mbox{\textbf{min. subhalo mass:}}\,
-    \Mhalo > 1\times10^{9}\Msun.\footnote{Note that for the TNG100 hydro run, the subhalo mass is the total sum of all bound dark \textit{and} baryonic matter.}
+    \mbox{\textbf{minimum subhalo mass:}}\,
+    \Mhalo > 1\times10^{9}\Msun.
     \end{equation*}
-    This lower mass threshold ensures that our halos are resolved into $>100$ particles, and thus should be robust to the \subfind\ and \sublink\ algorithms, even at the low mass end.  
-    For each subhalo that passes both of the above criteria, we use the \sublink\ merger trees to identify the maximum subhalo mass achieved by the subhalo, \Mpeak. 
+    This ``minimum mass" threshold ensures that subhalos are resolved into $>100$ particles, and thus should be robustly identifiable using the \subfind\ and \sublink\ algorithms \citep{rg15}.
+
+    % GB edited
+    For each subhalo that passes both criteria, i.e.
+the subhalo belongs to either a high mass or low mass FoF group and also passes the ``minimum mass" threshold, we use the \sublink\ merger trees to identify the maximum subhalo mass achieved by the subhalo, \Mpeak.
     We consider only the given snapshot and all previous snapshots in the determination of \Mpeak.
 
-    All subhalos in a given snapshot that pass both the group and current mass selection criteria will be added to our full sample of subhalos, which we call the \subcat. 
+    All subhalos in a given snapshot that pass both the FoF group and ``minimum mass" selection criteria form our full sample of subhalos, which we call the \subcat. 
     The catalog contains subhalos at each snapshot from $z=0-\sim4.2$ (snapshot numbers 20-99) and their associated properties, namely: Subhalo ID, FoF Group Number, current subhalo mass \Mhalo, and peak halo mass \Mpeak.
-    From here, we will use further selection criteria to narrow down this large sample and to match pairs of subhalos in each group.
+    At z=0, this selection process results in 44656 subhalos in low mass groups and 38350 subhalos in high mass groups.
+
+    From here, we will use further selection criteria to narrow down this large sample and to identify pairs of subhalos in each group.
 % End choosing halos     %
@@
     \subsection{Abundance matching} \label{sec:methods-am}
-    We will be utilizing a stellar mass to halo mass (SMHM) relationship to assign stellar masses to each of the subhalos in our \subcat.  
-    There are a few reasons we opt to assign stellar masses to our subhalos, rather than use those computed by the simulation.
+    We utilize a stellar mass to halo mass (SMHM) relationship to assign stellar masses to each of the subhalos in our \subcat.  
+    There are a few reasons we opt to assign stellar masses to our subhalos, rather than use those computed directly from the stellar particles in TNG100.
 
-    Primarily, applying an abundance matching prescription to assign stellar masses to each of the dark matter halos allows us to account for the observed spread in the SMHM relationship. 
-    This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large, $\sim 1$dex at $M_{h}\sim 10^{10}\Msun$. 
-    In addition, using stellar masses as calculated from abundance matching allows us to side step any simulation-dependent stellar mass effects.
-    In the case of TNG100 specifically, stellar masses of low mass galaxies are often overestimated compared to the galaxy luminosity function at the low mass end\cite{}. 
-    Using an observationally-calibrated abundance matching prescription will thus lead to a more robust result for comparison with and predictions for observations. 
-    Finally, utilizing an abundance matching prescription allows us to directly compare results between dark matter only and hydro simulations, since the stellar masses are assigned the same way. 
-    We make brief note of results for our equivalent analysis using the dark matter only, TNG100-Dark simulation as well in Sec.~\ref{sec:discussion}.\kc{need to specify section once written}
+    Primarily, applying an abundance matching prescription to assign stellar masses allows us to account for the observed spread in the SMHM relationship. 
+    This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large, between $\sim 0.3$ for $M_{h}\sim 10^{10}\Msun$ up to $\sim 1$dex for $M_{h}\sim10^{8}\Msun$~\citep{Munshi2021}.
+    While the SMHM function of \tng{} at $z=0$ closely reproduces the profile of the SMHM relation from various abundance matching and semi-empirical models~\citep{TNG5}, using stellar masses as calculated from abundance matching allows us to side step any simulation-dependent stellar mass effects.
+    Finally, utilizing an abundance matching prescription enables direct comparisons of results between dark matter only and full hydrodynamics simulations, since the stellar masses are assigned in an identical way.
+    We make a brief note of results for our equivalent analysis using the dark matter only, TNG100-Dark simulation, in Sec.~\ref{sec:disc-dark}.
 
-        % what am prescription are we using? 
     We use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic prescription to assign stellar masses to dark matter halos. 
@@
 
-        % realizations? 
-    We elect to use the maximum subhalo mass \Mpeak\ in the stellar mass calculation, rather than the subhalo mass at the given snapshot.
+    Because the abundance matching prescription is calibrated for centrals of FoF groups, we elect to use the maximum subhalo mass \Mpeak\ in the stellar mass calculation, rather than the subhalo mass at the given snapshot \citep[see][]{Besla2018}.
     We also use the current redshift of the given snapshot, $z_{snap}$, of each subhalo in the stellar mass calculation. 
@@
     Using $z_{snap}$ means that we allow the stellar mass of both the primary and secondary halo to change as a function of redshift, even after the secondary has entered the primary's halo. 
-%and do not immediately cease star formation.
-    This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{geha13} which finds that dwarfs $>1\Mpc$ from a MW-type galaxy are often star forming and rarely quenched.
+    This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{geha13}, which found that dwarfs $>1.5\Mpc$ from a MW-type galaxy are often star forming and rarely quenched.
     Additionally, the SAGA survey has found that large satellites of MW-type galaxies are often very blue, with infall into the halo spurring high rates of star formation due to the large gas fraction in dwarfs~\citep{Mao2021}.
-    % maybe need a note here on whether this is fair to extend to higher mass system?
 
@@
     Each realization is treated as an independent sample of galaxy stellar masses, which will allow us to report realistic spreads of pair properties.
-
-    % As mentioned in a footnote in Sec.~\ref{sec:methods-halos}, the total halo mass of subhalos in the hydro simulation includes the mass of both dark matter and baryonic particles. 
-    % In TNG100-1, the DM particle mass is decreased XX\% compared to the DM particle mass in \tng100-1 Dark to account for the additional mass of baryons, such that the total mass of the halo will remain roughly the same between the dark matter only and hydro simulations.
-    % Since the~\citet{Moster2013} AM relation was calibrated using DM subhalos from the \texttt{MilleniumII} dark matter only simulation, we will use the total subhalo mass from the TNG100 hydro simulation as a proxy for the corresponding DM halo mass in the TNG100-1 Dark run, \texttt{SubhaloMass}.
 
@@
     Starting from the \starcat, here we outline the pair matching process through which we generate the \paircat. 
-    At each redshift, and for each stellar mass realization, we will identify subhalo pairs consisting of a "primary" and a "secondary", where primaries are the more massive of the pair by stellar mass.
+    At each redshift, and for each stellar mass realization, we will identify subhalo pairs consisting of a ``primary" and a ``secondary", where primaries are the more massive of the pair by stellar mass.
 
@@
         Primary galaxies (equivalently, ``primary subhalos") are the most massive galaxy of their FoF group by stellar mass, such that each group can have at most one primary galaxy.  
-        Each stellar mass realization is treated independently, such that the subhalo identified as the primary of a group may change between stellar mass realizations.
+        Each stellar mass realization is treated independently, and so the subhalo identified as the primary of a group may change between stellar mass realizations.
 
-        At a given snapshot, and for each stellar mass realization, we rank order the subhalos of each group by stellar mass. 
-        Primaries must be the most massive subhalo in their group, and pass the following stellar mass criteria:         
+        At a given snapshot, and for each stellar mass realization, we rank order the subhalos of each FoF group by stellar mass. 
+        Primaries are defined as the subhalo with the highest stellar mass ($M_{*1}$) in their FoF group that passes the following criteria:         
         \begin{align*} 
-        \mbox{\textbf{low mass primaries:}}&\, 10^{8}< \rm M_{*1} < 5\times10^{9}\Msun \\ 
-        \mbox{\textbf{high mass primaries:}}&\, 5\times 10^{9}< \rm M_{*1} < 10^{11}\Msun.
+        \mbox{\textbf{low mass primaries:}}&\, 10^{8}< \rm M_{*1} < 5\times10^{9} \Msun \\ 
+        \mbox{\textbf{high mass primaries:}}&\, 5\times 10^{9}< \rm M_{*1} < 10^{11} \Msun.
         \end{align*}
-        The stellar mass criteria is fixed, and does not change as a function of redshift. 
+        The stellar mass criteria is fixed, and \textit{does not change} as a function of redshift. 
         At $z=0$, the stellar mass range for low mass primaries corresponds to isolated analogs of the LMC or M33, while the high mass primaries represent isolated analogs of the MW or M31.
@@
         As before, the selection of secondary companions occurs independently for each stellar mass realization, and for each snapshot. 
-        Secondary subhalos are defined as the second most massive subhalo in a FoF group by stellar mass. 
-        Secondary subhalos with stellar mass $M_{*2}$ must have a stellar mass ratio:
+        Secondary subhalos are defined as the second most massive subhalo in a FoF group by stellar mass ($M_{*2}$). 
+        Secondary subhalos must also have a stellar mass ratio with respect to primaries of:
         \begin{align*}
@@
         \end{align*}
-        We do not include companions with a stellar mass ratio $M_{*2}/M_{*1} <1/10$ due to the lower bound subhalo mass criteria of $\Mhalo=10^9$, which has at least a the corresponding stellar mass of $10^6\Msun$ at $z=0$.
-        The stellar mass ratio criterion ensures completeness of the sample, even at the lowest stellar masses considered.
+
+        We do not include companions with a stellar mass ratio $M_{*2}/M_{*1} <1/10$ as we will be limiting our pair sample to traditional definitions of major and minor pairs, 
+        which are typically defined to have stellar mass ratios $M_{*2}/M_{*1} > 1/10$~\citep[i.e.][]{lotz11, rg15, snyder2017, duncan19, Wang2020, Guzman-Ortega2023}.
+        % where minor pairs are typically defined as having mass ratios between $1/4 > M_{*2}/M_{*1} > 1/10$ \citep{lotz11, rg15, Guzman-Ortega2023}.
+        Our subhalo ``minimum mass" threshold of $\Mhalo=10^9$ (described in Sec.~\ref{sec:methods-halos}) corresponds to a mean stellar mass of $10^6\Msun$ at $z=0$. 
+        This stellar mass is well below the 1/10 criteria for the lowest stellar mass primary considered ($M_{*1} > 10^8 \Msun$), ensuring that our pair sample will be complete even at the lowest stellar masses considered.
 
     \subsubsection{Creating the pair catalog}
-        Pairs consist of a single primary and secondary in a FoF group as selected via the criteria above. 
-        Each pair is categorized as either a major or minor pair based on the stellar mass ratio between the primary and secondary. 
-        The stellar mass ratio criteria for major and minor pairs are:
+        Pairs consist of a single primary and secondary in a FoF group as defined via the criteria above. 
+        Each pair is categorized as either a major or minor pair based on the stellar mass ratio between the primary and secondary. Following, e.g. \cite{lotz11, rg15}, 
+        the stellar mass ratio criteria for major and minor pairs are:
         \begin{align*} 
@@
 
-        For each pair, we calculate the physical separation (\kpc, not comoving \kpc) between the two subhalos using the \texttt{SubhaloPos} field from the group catalogs, and we require that each pair have a minimum separation of $15 \kpc$ between the primary and secondary.
-        The minimum separation cut is 20 times the smoothing length of the simulation at $z=0$ which ensures that \subfind can identify the subhalos as distinct objects.
+    % Katie add citation 
+        For each pair, we calculate the physical separation (\kpc, not comoving \kpc) between the two subhalos using the \texttt{SubhaloPos} field from the group catalogs.
+We require that each pair have a minimum separation of $10 \kpc$ between primary and secondary to limit the impact of very close subhalos becoming indistinguishable in \subfind~\citep{rg17}.
+        % The minimum separation cut is more than 10 times the smoothing length of the simulation at $z=0$, which ensures that  can identify the subhalos as distinct objects XXXXX ADD CITATION HERE - vicente?
+subfind paper?.
+%\citep{Besla2018}.
 
@@
 
-        For each snapshot and each of the 1000 realizations of the abundance matching prescription, we create a set of isolated primaries and pairs. 
-        The final \paircat is the collection of all isolated primaries and pairs at each snapshot, and includes the following information: for each isolated primary, we store the subhalo mass and stellar mass from the given realization; from each pair we store the primary and secondary subhalo masses, stellar masses, group radius, and separation.
+        For each snapshot and each of the 1000 realizations of the stellar mass in \starcat, we identify a set of isolated primaries and pairs. 
+        The final \paircat\ is the collection of all isolated primaries and pairs at each snapshot, and includes the following information. 
+        For each isolated primary, we store the current subhalo mass (\Mhalo) and stellar mass from the given realization. 
+        For each pair, we store the primary and secondary subhalo masses (\Mhalo) and stellar masses, the pair separation, and the virial radius of the FoF group (given by the  the \texttt{Group\_R\_TopHat200} field in the group catalogs).
 
-    % end secondary subsubsection
-    %%%     
 % Pair selection end %
@@
     The high mass primary count (right) peaks at $z\sim1$ (with $\sim 1900$ primary subhalos per realization), while the high mass pair count peaks at $z=0$ (with $\sim 700$ pairs per realization). 
-    (Bottom) Total pair fraction (fraction of primaries with a companion secondary) as a function of redshift (see Sec.~\ref{sec:pairprops} for calculation details).
-    Low mass pair fraction is approximately flat between $z=2.5-4$, and decreases from $z=2.5$ to $z=0$. 
+    (Bottom) Total pair fraction (fraction of primaries with a major or minor secondary) as a function of redshift (see Sec.~\ref{sec:pairprops} for calculation details).
+    The low mass total pair fraction is approximately flat between $z=2.5-4$, and decreases from $z=2.5$ to $z=0$. 
     The high mass total pair fraction is flat or decreasing from $z=1$ to $z=4$, but spikes sharply between $z=0-0.25$.}
@@
     \includegraphics[width=\textwidth]{smrdist_1000.png}
-    \caption{Stellar mass ratio distribution of all low mass (top) and high mass (bottom) pairs for all 1000 stellar mass realizations combined.
+    \caption{Stellar mass ratio distribution of all low mass (top) and high mass (bottom) pairs for all 1000 stellar mass realizations combined at each redshift.
 Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$.
 Overall, the stellar mass ratio distribution of major and minor pairs of low and high mass galaxies show little evolution from $z=4$ (right) to $z=0$ (left).
-    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both low and high mass pairs.}
+    Major pairs make up $51-55\%$ of the total sample of pairs at every redshift for both low and high mass pairs.}
     \label{fig:massratio}
@@
 \section{Sample: Overview of pair properties} \label{sec:pairprops}
-    Utilizing the \paircat, for each snapshot, we compute the total number of primaries (isolated and paired) and pairs in each of the 1000 realizations, then take the median and 1 and 99 percentile spread on the median over all realizations.
-    Additionally, we compute the low and high mass total pair fraction (the total number of pairs, $\rm N_{pair}$, divided by the total number of primaries $\rm N_{prim}$) for each individual realization, then find the median and spread over all 1000 realizations.
+    Utilizing the \paircat, for each snapshot, we compute the total number of primaries (isolated and paired) and pairs (both major and minor) in each of the 1000 realizations.
+We then compute the median and 1 and 99 percentile spread on the median over all realizations.
+    Additionally, we compute the low and high mass total pair fraction (the total number of major and minor pairs, $\rm N_{pair}$, divided by the total number of primaries $\rm N_{prim}$) for each individual realization.
+We again compute the median and spread over all 1000 realizations.
 
     Fig.~\ref{fig:counts} shows the median number (solid and dashed lines) of identified low and high mass primaries and pairs over the redshift range $z=0-4$.   
-    The shaded regions show the 1-99\% spread of the set, though the spread is hard to distinguish in the low mass case.
+    The shaded regions show the 1-99\% spread of the set.
 
     The number of identified primaries is lowest at $z=4$, and rises to a maximum around $z=1$ for both low and high mass primaries.
-    The median count of low mass primaries (green solid line in top left panel) reaches a maximum of $\sim15000$ halos at $z\sim0.6$, then decreases by $\sim16\%$ to 12000 halos at $z=0$. 
-    The count of high mass primaries (pink solid line in top right panel) reaches a maximum of $\sim2000$ at $z\sim1$, then remains approximately constant to $z=0$. 
+    The median count of low mass primaries (green solid line in top left panel) reaches a maximum of $15545^{+89}_{-88}$ halos at $z\sim0.6$, then decreases by $\sim22\%$ to $12002^{+85}_{-86}$ halos at $z=0$.
+    The count of high mass primaries (pink solid line in top right panel) reaches a maximum of $1901^{+16}_{-19}$ at $z=0.5$, and slightly declines to $z=0$. 
     There are roughly 8 times as many low mass primaries as high mass primaries.
@@
     Unlike the primary count, the pair counts for low and high mass pairs peak at very different redshifts. 
-    The count of low mass pairs (green dashed line) peaks much earlier at $z\sim2$ with $\sim3000$ pairs, and decreases to $\sim1000$ pairs at $z=0$.
-    % From $z=4$ to $z=2$, the number of dwarf primaries doubles, as does the number of pairs due to the growth of structures over cosmic time.
-    The pair count for high mass galaxies (pink dashed line), on the other hand, behaves more similarly to the primary count, increasing from $z=4$ to a peak at $z\sim1$, then leveling off through $z=0$.
+    The count of low mass pairs (green dashed line) peaks much earlier, at $z=1.9$ with $2956^{+99}_{-95}$ pairs, and decreases to $896^{+51}_{-50}$ pairs at $z=0$.
+    The pair count for high mass galaxies (pink dashed line), on the other hand, behaves more similarly to the primary count, increasing from $z=4$ to $z\sim1$, then decreasing to $z=0.25$ before peaking with $647\pm27$ pairs at $z=0$.
 
-    The bottom panel of Fig.~\ref{fig:counts} shows the total pair fraction for low mass and high mass pairs, or equivalently, the fraction of primaries with a companion.
+    % Katie to fix XXXX
+    The bottom panel of Fig.~\ref{fig:counts} shows the total pair fraction for low mass and high mass pairs, or equivalently, the fraction of primaries with a major or minor companion.
     The total pair fractions for both low and high mass pairs are roughly flat for $z=2.5-4$, and display opposite behavior for low redshifts between $z=0-2.5$. 
-    The low mass pair fraction decreases from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the high mass pair fraction remains flat between $z=1-2.5$.
-    At very low redshifts, from $z=0-0.25$, the high mass pair fraction spikes sharply from $\sim 0.29$ to $\sim 0.36$, an increase of $25\%$.
+    The low mass total pair fraction decreases from $0.233^{+0.008}_{-0.009}$ to $0.075\pm 0.004$, a decrease of roughly $68\%$, while the high mass total pair fraction remains flat between $z=1-2.5$, ranging between $0.275$ and $0.351$.
+    At very low redshifts, from $z=0-0.25$, the high mass total pair fraction spikes sharply from $0.288^{+0.016}_{-0.013}$ to $0.359^{+0.015}_{-0.014}$, an increase of $37\%$.
 
@@
     Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both low and high mass pairs.
-    In general, the shape of the distribution remains constant from $z=0$ (left) to $z=4$ (right) for both low and high mass pairs, and is thus independent of mass scale and of redshift.
+    In general, the shape of the distribution remains constant from $z=0$ (left) to $z=4$ (right) for both low and high mass pairs, and changes weakly as a function of mass scale and of redshift. 
+    There are between $\sim3.3-4.8$ times more pairs with mass ratios $\sim1/4$ than $\sim1/1$, and about $1.8-2.2$ times more pairs have $1/10$ than $1/4$. 
+    Roughly 2\% of the total pair population is a 1:1 mass ratio encounter; this is true for low and high mass galaxies and across all redshifts considered.
 
@@
 % Begin Results section %
+\section{Results: The frequency of low mass and high mass pairs}
+\label{sec:results}
 
-\section{Results: The frequency of low mass and high mass pairs}
-We have created catalogs of isolated low and high mass galaxy pairs from $z=0-4$ in the TNG100 simulation. 
-In this section, we will analyze the occurrence rate of major and minor pair types across cosmic time.
+We have created catalogs of isolated low and high mass galaxy pairs from $z=0-4.2$ in the TNG100 simulation. 
+In this section, we will analyze the frequency of major and minor pair types across cosmic time, with the goal of identifying potential differences between high and low mass galaxies.
 
-We are interested in the aggregate properties of the full sample, and so we will treat each stellar mass realization in the \paircat\ as an independent sample. 
-At each snapshot, we calculate the median occurrence rate of each of the 1000 realizations. 
-From this set of 1000 medians, we calculate the median and percentile spread which is shown in the following plots at the solid or dashed line, and the shaded region, respectively.
+In Sec.~\ref{sec:results-frac}, we examine the redshift evolution of the fraction of primaries with a major or minor companion (the ``pair fraction") and compare the results for low mass and high mass pairs.
+In Sec.~\ref{sec:results-frac-sepcut}, we examine the redshift evolution of the pair fraction as a function of pair separation.
 
-In Sec.~\ref{sec:results-frac}, we show the redshift evolution of the fraction of primaries with a major or minor companion (the ``pair fraction") and compare the results for low mass and high mass pairs.
-In Sec.~\ref{sec:results-frac-sepcut}, we look at the redshift evolution of pair fraction as a function of pair separation. 
-% In Sec.~\ref{sec:results-scaled}, we compare the separations and velocities scaled by the FoF group's virial properties. 
-% Finally, in Sec.~\ref{sec:results-virialcut}, we take subsets of the Pair Catalog, selecting only pairs within some fraction of the virial radius, and illustrate the impact on the recovered low and high mass pair fractions.
+In the following analysis we will treat each stellar mass realization in the \paircat\ as an independent sample. 
+At each snapshot, we create a set ``S" of 1000 median pair fractions, which are computed utilizing each of the 1000 realizations of the target pair sample, independently.
+We then calculate the median of the set ``S" (the median of medians) and the percentile spread. 
+It is this median that is shown in each of the following plots as the solid or dashed line, and the shaded regions correspond to the spread.
 
@@
     \subsection{Major and minor pair fractions}\label{sec:results-frac}
-    We determine the occurrence rate of a major or minor pair by calculating the pair fraction. 
-    The pair fraction is defined here as the ratio of the number of pairs to the total number of isolated \textit{and} paired primaries:
+    The pair fraction is defined here as the ratio of the number of pairs ($N_{pairs}$) to the total number of isolated \textit{and} paired primaries ($N_{primaries}$):
     $$f_{p}=\rm \frac{N_{pairs}}{N_{primaries}}.$$
-    For example, the pair fraction of low mass major pairs is the number of low mass major pairs divided by the number of low mass primaries. 
-    The pair fraction can be understood as a measure of the likelihood of finding a companion of a certain mass type about a primary identified in the field.
+    For example, the low mass major pair fraction is the number of low mass major pairs divided by the number of low mass primaries, which can also interpreted as the likelihood of finding a major companion of an isolated low mass primary.
 
     Fig.~\ref{fig:pairfrac} shows the pair fractions calculated for low and high mass pairs (including both major and minor pairs separately) as a function of time for $z=0-4$. 
-        % differences between major and minor pairs? 
-    The pair fraction of minor pairs is less than that of major pairs for both low and high mass pairs at all redshifts, due to the lower stellar mass ratio limit we put on our pairs.
-    If we lower the stellar mass ratio floor for minor pairs, the minor pairs would outnumber the major pairs.
-    % Expanding the mass ratio criteria of our minor pair sample to include stellar mass ratios between 1/10-1/100 in our minor pair sample increases the fraction of minor pairs by a factor of $>2$ for massive pairs and between $~1.5-2x$ for dwarf pairs.
-\kc{are there any additional takeaways from this?
-}
+    Note that, as discussed in Sec.~\ref{sec:methods-pairs}, we adopt a lower stellar mass ratio floor of $1/10$, and consequently the total pair sample is dominated by major pairs.
 
@@
     The low mass pair fraction evolves distinctly from that of high mass pairs.
-    Low mass major and minor pair fractions start at their minima at $z=0$, and increase by about 200\% by $z\sim2-2.5$, at which point they level off and remain constant from $z=3-4$. 
-    On the other hand, high mass pair fractions reach their maxima at $z=0$, then abruptly declining to $z\sim0.25$, before remaining approximately constant from $z=1-4$.
+    Low mass pair fraction for both major and minor pairs (green) are approximately constant from $z=3-4$, then decline monotonically to $z=0$.
+At $z=0$, the major pair fraction is $0.041^{+0.003}_{-0.004}$, while the minor pair fraction is $0.034\pm0.004$.
+    At $z=3$, the pair fractions have increased by $207\%$ to $0.126^{+0.008}_{-0.007}$ for major pairs and $0.111\pm0.008$ for minor pairs.
+
+    High mass pair fractions (pink) remain approximately constant for $z>1$, where the median of the major pair fraction fluctuates between 0.150-0.179, and the median for minor pairs fluctuates between 0.135-0.151.
+    Between $z=0.3$ and $z=0$, the major pair fraction increases from $0.163^{+0.011}_{-0.010}$ to $0.207^{+0.012}_{-0.014}$, while the minor pair fraction increases from $0.125^{+0.017}_{-0.014}$ to $0.152^{+0.016}_{-0.017}$.
 
         % difference panels
-    The bottom panels of Fig.~\ref{fig:pairfrac} shows the low mass pair fraction subtracted from the high mass pair fraction (labelled ``$\rm High-Low$").
-    The pair fraction difference reaches a maximum at $z=0$ for both major and minor pairs, and declines to $z\sim2-2.5$. 
-    From $z=2.5-4$, the difference is approximately 0, and thus both major and minor pairs of high and low mass are equivalently common.
+    The bottom panels of Fig.~\ref{fig:pairfrac} shows the low mass pair fraction subtracted from the high mass pair fraction (labeled ``$\rm High-Low$").
+    The difference between high and low mass pair fractions increases with decreasing redshift, peaking at $z=0$ with a difference of $0.166\pm0.013$ for major pairs and $0.111\pm0.017$ for minor pairs.
+    Thus, at low redshift, we expect both major and minor pairs to be more common in high mass galaxies than in low mass galaxies. 
+    From $z=2.5-4$, the difference is approximately 0, and thus both major and minor pairs of high and low mass galaxies are equivalently common at high redshift.
 
@@
     Overall, these results show that low mass and high mass pair counts evolve differently over time, particularly at very low redshift, despite the pair fractions being roughly equal at higher redshift.
-    The implications for the difference in the evolution of pair fractions for low mass and high mass pairs across time is discussed in detail in Sec.~\ref{sec:discussion}.
+    The implications for the difference in the evolution of pair fractions for low mass and high mass pairs across time is discussed in detail in Sec.~\ref{sec:disc-obs}.
 
         % pair fraction plot
-    \label{sec:results}
     \begin{figure*}[htp]
@@
       \caption{% Top plots ~
-        (Top) Median pair fraction, defined as the fraction of low mass or high mass primaries with a major (solid) or minor (dashed) companion by stellar mass (see Sec.~\ref{sec:methods-pairs}). 
-        Shaded areas show the 1-99 percentile range on the median (solid and dashed lines) from 1000 stellar mass realizations. 
-          % massive pairs
-        The high mass pair fraction (pink) remains approximately constant for $z>1$, for both major and minor pairs. 
-        Between $z=0.3$ and $z=0$, the major pair fraction increases from $0.163^{+0.011}_{-0.010}$ to $0.207^{+0.012}_{-0.014}$, while the minor pair fraction increases from $0.125^{+0.017}_{-0.014}$ to $0.152^{+0.016}_{-0.017}$.
-          % dwarf pairs
-        Low mass pair fractions, shown in green, are approximately constant from $z=3-4$, then decline monotonically to $z=0$.
-The major pair fraction is $0.041^{+0.003}_{-0.004}$ at $z=0$ and $0.126^{+0.008}_{-0.007}$ at $z=3$, while the minor pair fractions are $0.034\pm0.004$ and $0.111\pm0.008$ at $z=0$ and $z=3$, respectively.
+        (Top) Median pair fraction as a function of redshift, defined as the fraction of low mass or high mass primaries with a major (solid) or minor (dashed) companion  (see Sec.~\ref{sec:methods-pairs}).
+        Shaded areas show the 1-99 percentile range on the median (solid and dashed lines) from 1000 stellar mass realizations, as discussed at the beginning of Sec.~\ref{sec:results}. 
+            % low mass
+        Low mass major and minor pair fractions (green) are both at their minima at $z=0$, and increase by about 200\% by $z\sim2-2.5$, at which point they level off and remain constant from $z=3-4$. 
+            % high mass
+        On the other hand, high mass major and minor pair fractions reach their maxima at $z=0$, then abruptly decline until $z\sim0.25$ before remaining approximately constant from $z=1-4$. 
         % Bottom plots ~
-        (Bottom) The median subtracted difference between high and low mass pair fractions, with the shaded $1$-$99$ percentile range from 1000 abundance matching realizations.
-The pair fraction difference increases with decreasing redshift, peaking at $z=0$ with a difference of $0.166\pm0.013$ for major pairs and $0.111\pm0.017$ for minor pairs.
-This shows that the redshift evolution of the pair fractions of low and high mass pairs proceeds differently, particularly at low redshift.}
+        (Bottom) The median and $1$-$99$ percentile range of the subtracted difference between high and low mass pair fractions. 
+        The difference peaks at $z=0$ for both major and minor pairs, and declines with increasing redshift.
+        This panel shows that the redshift evolution of the pair fractions of low and high mass pairs proceeds differently, particularly at low redshift where pairs are more common for high mass galaxies than low mass galaxies.}
       \label{fig:pairfrac}
@@
 
-\subsection{Major pair fractions as a function of maximum separation}\label{sec:results-frac-cuts}
-    We also analyze subsets of the low and high mass major pairs that pass additional separation criteria. 
-    Here, we study two different sets of separation criteria to compare the resulting pair fractions of subsets of the low and high mass major pairs to the full sample shown in Fig.~\ref{fig:pairfrac}.
-    The first separation criteria that we employ selects pairs of different separations as a function of the size of the group's halo, as discussed in Sec.~\ref{sec:results-frac-vircut}. 
-    In Sec.~\ref{sec:results-frac-sepcut}, we use physical 3D separation cuts to compare the population of low separation major pairs of low and high mass.
+\subsection{Major pair fractions as a function of separation}\label{sec:results-frac-cuts}
+    In this section we analyze subsets of the low and high mass major pairs from the previous section that pass additional separation criteria. 
+    We study two different sets of separation criteria to compare the resulting pair fractions to the full sample shown in Fig.~\ref{fig:pairfrac}.
+    In  Sec.~\ref{sec:results-frac-vircut} we apply a separation criteria that requires secondaries to be within a given factor of the virial radius of the FoF group, which is a reasonable proxy for the virial radius of the primary.
+    In Sec.~\ref{sec:results-frac-sepcut}, we use a range of limits on the 3D pair separation, where limits are consistent with values adopted in the literature.
 
-\subsubsection{Separation cut - fraction of the virial radius}\label{sec:results-frac-vircut}
-    \todo{here! }
-              Interestingly, the recovered fraction of the full sample at <0.5rvir is <50\% but still closely resembles the full pair frac at z<2!
-thus, at low z, the behavior of the pair fractions is dominated by halos within 0.5 Rvir ~~
+    In all cases, solid lines correspond to the median pair fraction and shaded regions to the 1st--99th percentile, as explained at the beginning of Sec.~\ref{sec:results}.
+
+\subsubsection{Pair separation limits as a function of the virial radius of the FoF group}\label{sec:results-frac-vircut}
+    We calculate the pair fraction for subsamples of low mass and high mass major pairs by selecting only pairs that have separations less than some factor of the virial radius of its FoF group. 
+    Note that a minimum separation limit of $10\kpc$ is always applied to all of our pairs (see Sec.~\ref{sec:methods-pairs}). 
+    The virial radius is taken from the \texttt{Group\_R\_TopHat200} field in the group catalogs.
+
+    % GB added the caveat below - might need to edit 
+    Major pairs typically correspond to the two most massive subhalos in their FoF group. 
+    The virial mass of their FoF group is reasonably approximated by the combined subhalo mass of both pairs.
+    The combined mass of major low mass galaxy pairs recovers 98\% of the FoF group mass and the combined mass of major high mass galaxy pairs recovers 93\%. 
+    For example, the total mass of the Local Group is dominated by that of the MW and M31 \citep[e.g., ][]{Chamberlain2023}. 
+    The virial radius of the FoF group is thus reasonably approximated by the virial radius of a halo with a virial mass equal to the combined subhalo mass of the two major pair members.
+% note the subhalo mass of the two major pair members could be approximated using abundance matching
+
+    By basing our separation criteria on the FoF group virial radius, the separation cut will vary both as a function of redshift and as a function of the combined mass of the pair.
+    For the high mass FoF groups, the median virial radius at $z=[0,1,2,3,4]$ is $\sim(348, 206, 134, 97, 76)\kpc$. 
+    For the low mass FoF groups, the median virial radius at $z=[0,1,2,3,4]$ is $\sim[134, 85, 59, 43, 33]\kpc$.
+
+    We choose 6 subsamples, consisting of pairs with separations less than $0.25, 0.5, 1.0, 1.5, 2.0,$ and $2.5\Rvir$. 
+    The top row of Fig.~\ref{fig:vircut} shows the median pair fraction (solid lines), calculated as described at the beginning of section~\ref{sec:results}, 
+    for high mass (pink) and low mass (green) pairs in each of the 6 subsamples. 
+    In the bottom row, we show the completeness\kc{change name}, which is the fraction of the total pair sample that is recovered in each subsample, i.e.
+the number of pairs that pass each separation criterion divided by the total number of pairs in the full sample presented in Sec.~\ref{sec:results-frac}.
+
+    As the pair separation limits increase (left to right), the completeness increases, as does the pair fraction, as expected because each consecutive selection cut is less restrictive and will contain more of the full sample.
+    More than 75\% of the full pair sample is recovered at all redshifts with separation criteria up to $2\Rvir$.
+
+    All subsamples of high mass pairs display broadly the same pair fraction redshift evolution as the full high mass sample (pink line in left panel of Figure~\ref{fig:pairfrac}): each of the subsampled high mass pair fractions peak at $z=0$ and remain roughly constant or decrease at higher redshift.
+    The finer detail trends from the full sample, particularly the upturn at low z, are reasonably captured if $r_{sep} < 0.5 \Rvir$, despite the completeness being $\sim$40\%. 
+    % The magnitude of the pair fraction as a function of redshift for the full sample is best captured if $r_{sep} < 2.0\Rvir$.
+
+    The subsamples of low mass pairs, however, show a different trend from the full sample (green line in left panel of Figure~\ref{fig:pairfrac}) if the separation cut is too small. 
+    For $r_{sep} < 0.25\Rvir$, the pair fraction is flat or decreasing as a function of redshift (especially for $z>1$), similar to the behavior for high mass pairs. 
+    For $r_{sep} < 0.5\Rvir$ and $r_{sep} < 1.0\Rvir$, the pair fraction rises to a peak at $z\sim2$ and then decreases. 
+    %edited 
+    When the separation is limited to $r_{sep} < 1.5\Rvir$, the trends with redshift for the full low mass sample are recovered, particularly the roughly flat behavior from $z\sim2-4$, despite a sample completeness of $<75\%$.
+    % The magnitude of the full low mass pair fraction is recovered for $r_{sep} < 2.0$\Rvir. 
+    We also find that differences between the redshift evolution of high mass pairs vs. low mass pairs (particularly at $z<2$) become apparent if $r_{sep} < 0.5\Rvir$ for both galaxy types. 
+    Overall we find that recovering the redshift evolution of the pair fractions of all galaxy pairs requires a separation cut such that the number of close pairs constitutes $\sim40-50\%$ or more of the full sample at all redshifts.
 
@@
         \includegraphics[width=\textwidth]{pairfrac_vircut.png}
-        \caption{ The pair fraction of the subset of high mass (pink) and low mass (green) pairs with 3D separations within a fraction of the group's virial radius (see Sec.~\ref{sec:results-frac-sepcut} for details of calculations).
-        The median and 1-99 percentile spread are shown by the solid lines and shaded regions, respectively.
-        Pair fractions for the subsample of low and high mass pairs with separations less that 0.25\Rvir are constant or declining with increasing redshift, and do not resemble the pair fractions for the full pair sample.
-        However, increasing the maximum separation of a pair to $0.5\Rvir$ leads to low and high mass major pair fractions that take on the same behavior as the full sample for $z<2$, where the low mass pair fraction decreases, and the high mass pair fraction (on average) increases.
-        The pair fraction trends for the low and high mass subsamples become similar to those of the true pair fractions (as seen in Fig.~\ref{fig:pairfrac}) when all pairs within $1.5\Rvir$ are included in the subsample.
-      % bottom plot
-        (Bottom) The fraction of the total collection of pairs in the subset of pairs that passes each separation cut.
-        More than 50\% of low and high mass pairs have separations $<1.5\Rvir$ at all redshifts. 
-        When the maximum separation is increased to $2.5\Rvir$, the recovery rate at all redshifts is $>90\%$ for low mass pairs, and $>80\%$ for high mass pairs. 
+        \caption{\label{fig:vircut}The median and 1-99 percentile spread are shown by the solid lines and shaded regions, respectively. 
+        (Top) The median pair fraction of the subset of high mass (pink) and low mass (green) pairs with 3D separations within a given factor of the pair's FoF group virial radius.
+        Such a separation criteria will vary as a function of both the mass of the pair and the redshift. 
+        Recovering the redshift evolution seen for the total sample (left panel of Figure~\ref{fig:pairfrac}) requires separation cuts of $r_{sep} < 1.5\Rvir$ for low mass pairs and $r_{sep} < 0.5\Rvir$ for high mass pairs.
+        Recovering the differences between high and low mass pair fraction trends seen for the total sample at $z>2$, requires $r_{sep} < 0.5\Rvir$ for both galaxy types. 
+        (Bottom) The completeness, calculated as the fraction of the total collection of pairs recovered by the subset of pairs at the given separation cut. 
+        We find that recovering the redshift evolution of the pair fractions of all galaxy pairs requires a separation cut such that the number of close pairs constitutes $\sim50-70\%$ of the full sample at all redshifts.
     }
-      \label{fig:vircut}
     \end{figure*}
@@
 
-\subsubsection{Separation cut - physical separations}\label{sec:results-frac-sepcut}
-    We calculate the pair fraction for all major low mass and high mass pairs, excluding pairs that exceed separations of $(50,70,100,150,200,300)\kpc$. 
-    This additional separation criterion creates subsamples of the \paircat, and contains low and high mass pairs with separations between $15-50\kpc$, $15-70\kpc$, and so on\footnote{See Sec.~\ref{sec:methods-pairs} for a description of the $15\kpc$ lower separation cutoff.}.
+\subsubsection{Pair separation limits based on static 3D physical separation} \label{sec:results-frac-sepcut}
+    We calculate the pair fraction for subsamples of major low mass and high mass pairs by including only pairs with separations less than $[50,70,100,150,200,\mathrm{and\, }300]\kpc$.  
+    Note that this separation criteria does not vary as a function of redshift or mass of the pair, and that a minimum separation limit of $10\kpc$ is always applied (see Sec.~\ref{sec:methods-pairs}).
+    This separation criterion creates subsamples of the \paircat\ containing low and high mass pairs with separations between $10-50\kpc$, $10-70\kpc$, and so on.
 
-    Fig.~\ref{fig:sepcut} shows the pair fractions for the subsamples of pairs with separations lower than the physical separation listed at the top of each column. 
-    Similarly to the previous pair fraction plots, the top row presents the total median (solid line) of the collection of 1000 individual medians from each realization, and the shaded regions show the 1-99\%ile spread on the same collection of individual medians.
-    The bottom row of the plot shows the "recovery fraction", or the number of pairs in each subsample compared to the full sample of major pairs.
+    Fig.~\ref{fig:sepcut} shows the median pair fractions for the subsamples of pairs with separations lower than the physical separation listed at the top of each column. 
+    The bottom row of the plot shows the completeness, or the number of pairs in each subsample compared to the full sample of major pairs. 
+    Again, as the maximum separation increases (left to right), so too does the pair fraction and completeness of the subsample.
 
-    As the maximum separation increases (left to right), so too does the pair fraction, as you begin to include more and more of the distantly separated pairs, as well as the recovery fraction. 
-    The low mass major pair fraction (green) maintains roughly the same behavior (decreasing with decreasing redshift) for each separation cut, and closely resembles the pair fraction of the full sample (in Fig.~\ref{fig:pairfrac}) for maximum separation cuts higher than $150\kpc$.
-    The low mass pair fraction does not change significantly by excluding pairs with separations $>150\kpc$, thus the pair fraction profile is dominated by the closest 50\% of low mass pairs.
+    The low mass major pair fraction (green) maintains roughly the same behavior (decreasing with decreasing redshift) for each separation cut, and first recovers the redshift evolution and magnitude of the pair fraction of the full sample (left panel of Fig.~\ref{fig:pairfrac}) for a separation cut of $r_{sep} < 150\kpc$.
+    This is not surprising based on our results from the previous section as this separation is larger than the median virial radius of the sample and the completeness is larger than 50\% at all redshifts (reaching nearly 100\% at $z\sim3$).
+    The low mass pair fraction does not change significantly by excluding pairs with separations $>150\kpc$.
 
-    On the other hand, none of the subsamples of the high mass pairs display similar behavior to the full sample. 
-    In particular, for smaller separation cuts (50\kpc or 70\kpc), the redshift evolution of the pair fraction more closely resembles the low mass pairs.
-    For $r_{sep}<300\kpc$, the trends in the high mass major pair fraction is only similar at $z>1.5$, where it levels off, rather than continues to increase at higher $z$.
+    On the other hand, none of the subsamples of the high mass pairs accurately recover the behavior of the full high mass sample. 
+    In particular, the redshift evolution of the pair fraction between $z=0.25-2.5$ is not readily distinguishable from that of low mass pairs for any subsample from a physical separation cut.
+    At higher redshifts, the median pair fraction increases rather than leveling off or decreasing as in the full sample.
+    Even for $r_{sep}<300\kpc$, the high mass pair fraction peaks at $z=4$, at odds with results using the full pair sample or any of the virial radius cuts in the previous section.
 
-    The recovery rate for low mass pairs is universally higher than for high mass pairs.
-    By increasing the allowed separations $300\kpc$, virtually all low mass pairs are included in the subsample, with $>90\%$ of the total sample at $z=0$, and $\sim100\%$ for $z>1$.
-    However, high mass pairs have a median separation of $\sim300\kpc$ at $z=0$, which means the recovery rate for low separation high mass pairs is very low. 
-    In order to get a recovery fraction of at least 50\% at all redshifts from $z=0-4$, the subset of high mass pairs must include pairs with separations at least up to $300\kpc$.
+    By applying a separation cut that is constant as a function of redshift and mass of the system, the recovery fraction of the total sample varies markedly as a function of redshift.  
+    This is in stark contrast to results from the previous section where the recovery fraction was roughly constant as a function of redshift.
+    Because the same separation cut is applied to low and high mass pairs, the completeness for low mass pairs is universally higher than for high mass pairs at each separation cut, which wipes out any redshift evolution differences between the two galaxy types.
+
+% Phyiscally motivated framework for the selection criteria.
 
@@
         \includegraphics[width=\textwidth]{pairfrac_sepcut.png}
-        \caption{      % top plot
+        \caption{% top plot
         (Top) The major pair fraction of the subset of high mass (pink) and low mass (green) pairs with 3D separations less than the value given at the top of each column. 
         The median and 1-99 percentile spread are shown by the solid lines and shaded regions, respectively. 
-        % what do we notice
-        The behavior of the redshift evolution of major pair fractions for low and high mass pairs is strongly dependent on the maximum separation included in the subset.
-        Pair fractions of low mass and high mass pairs are nearly indistinguishable for the lowest separation pairs $r_{sep}<50\kpc$ at every redshift. 
-        For $z<2$, the true pair fraction behaviour (as seen in Fig.~\ref{fig:pairfrac}) becomes distinguishable when the maximum separation is $300\kpc$.
+        The 3D separation cut does not vary as a function of redshift or mass of the system. 
+        The general redshift evolution of the full high mass pair sample (decreasing with redshift for $z>1$) is not recovered for any physical separation cut, while the behavior of low mass pair fractions are well recovered by the $r_{sep}<150\kpc$ subsample.
+        The pair fractions for low mass and high mass pairs are virtually indistinguishable for separation cuts less than $70\kpc$. 
         % bottom plot
-        (Bottom) The fraction of the total collection of pairs in the subset of pairs that passes each separation cut.
-        Less than 50\% of massive pairs have separations $r_{sep}<50\kpc$, and 50-100\% have separations $r_{sep}<300\kpc$. 
-        Between 20-60\% of low mass pairs have separations $r_{sep}<50\kpc$, while a separation cut of $r_{sep}<300\kpc$ captures roughly 100\% of the low mass pair population at all redshifts. 
+        (Bottom) The fraction of the total collection of pairs in the subset that passes each separation cut. 
+        The recovered fraction varies as a function of redshift because a constant separation is chosen. 
+        A higher fraction of low mass pairs are recovered than high mass pairs at all separation cuts. 
+        Less than 50\% of all high mass pairs have separations $r_{sep}<70\kpc$ at all redshifts, and $>50\%$ of the full high mass sample is recovered at all redshifts only for $r_{sep}<300\kpc$. 
+        Between 20-60\% of low mass pairs have separations $r_{sep}<50\kpc$ at all redshifts, while a separation cut of $r_{sep}<150\kpc$ captures roughly 50-100\% of the low mass pair population at all redshifts.
         }
@@
     %%%%%%%%%%%%%%%%%%%%
+
+    \subsection{Comparison between TNG100-1 and TNG100-Dark}\label{sec:disc-dark}
+    We repeated the entirety of our analysis using data from the TNG100-Dark simulation.
+    Each step in our selection criteria was repeated identically, including our selection of group halos, abundance matching process, and selection of primary and secondary halos.
+    We created an equivalent catalog to the \paircat\ containing only subhalo properties from the TNG100-Dark simulation, and calculated the low and high mass pair fractions for $z=0-4.2$.
+
+    We found that the redshift evolution of low mass and high mass pair fractions in the TNG100-Dark simulation mimic those of the TNG100 simulation. 
+    In particular, low mass pair fractions remain flat between $z\sim2-4$, and decline from $z=2$ to a minimum at $z=0$. 
+    High mass pair fractions likewise decrease with higher redshift for $z>1$, and peak at $z=0$.
+    The numerical value of the pair fraction at all redshifts is $\sim10\%$ larger in TNG100-Dark for both low and high mass pairs, and for major and minor pairs.
+
+    % As mentioned in a footnote in Sec.~\ref{sec:methods-halos}, the total halo mass of subhalos in the hydro simulation includes the mass of both dark matter and baryonic particles. 
+    % In TNG100-1, the DM particle mass is decreased XX\% compared to the DM particle mass in \tng100-1 Dark to account for the additional mass of baryons, such that the total mass of the halo will remain roughly the same between the dark matter only and hydro simulations.
+    % Since the~\citet{Moster2013} AM relation was calibrated using DM subhalos from the \texttt{MilleniumII} dark matter only simulation, we will use the total subhalo mass from the TNG100 hydro simulation as a proxy for the corresponding DM halo mass in the TNG100-1 Dark run, \texttt{SubhaloMass}.
+
 % end Results section%
@@
 \section{Discussion}\label{sec:discussion}
+We performed a pair fraction analysis for low mass and high mass pairs in the TNG100 simulation from $z=0-4.2$, utilizing the full spatial information that simulations enable to ensure that the pairs are physically co-located as part of the same FoF Group.
+In this section, we discuss the broader impacts and implications of the behavior of high and low mass pair fractions over time.
 
-% In particular, we study dwarf galaxy pairs and massive galaxy pairs that are of similar stellar and halo mass to a variety of galaxy pairs in the Local Group. 
-% We categorize these pairs into one of four pair types: massive major pairs, such as the MW+M31; massive minor pairs, such as M31+M33 or MW+LMC; dwarf major pairs, such as M33+LMC; and finally, dwarf minor pairs, such as the LMC+SMC.
-% \kc{can maybe move these two sentences to a discussion section}
+\todo{redo ordering when finalized~}
+In Sec.~\ref{sec:disc-dark}, we briefly describe how our equivalent pair fraction analysis utilizing the TNG100-Dark simulation compares to the TNG100 results presented in Sec.~\ref{sec:results}. 
+In Sec.~\ref{sec:disc-comp}, we compare our results to previous studies of pair fractions that utilize simulations. 
+% implications of difference and detectability 
+We discuss the implications of the pair fraction behavior of low mass pairs and high mass pairs as a function of redshift and how we might be able to detect these differences in Sec.~\ref{sec:disc-obs}.
+% local group
+Finally in Sec.~\ref{sec:disc-LG}, we draw comparisons between our pair sample and various Local Group pairs to quantify the likelihood of finding isolated analogs of such pairs at higher $z$.
 
-%     \kc{ make a subsection about the equivalence of our findings with the dark matter simulation) We make brief note of results for our equivalent analysis using the dark matter only TNG100-Dark simulation as well in Sec.~\ref{sec:results}.}
+\subsection{Comparison to existing pair fraction studies}\label{sec:disc-comp}
+    A direct comparison to pair fractions reported from observations is not straight-forward, as observationally selected pairs suffer from contamination due to projected pairs and restrictive separation criteria that exclude more widely separated pairs.
+    Here, we compare our results to pair fractions and merger rates reported by other studies of the Illustris cosmological simulations to establish the reliability of our findings.
 
-% \subsection{Implications for the differences in pair fractions of dwarf and massive pairs}
-% In Sec.~\ref{sec:results-frac}, we presented the pair fraction of massive and dwarf galaxy pairs and found that the relative frequency of the two populations evolve distinctly from $z=0-4$. 
-% While the frequency of massive pairs compared to the number of massive primaries is roughly constant and become more common at low redshift, dwarf major and minor pairs become more than 50\% less common at $z=0$ compared to $z=2$.
-% Since scaled separations and velocities do not change drastically between dwarf and massive pairs, the difference in the evolution of the pair fractions indicates that the merger processes of each population may proceed differently.
+    % low mass comparison
+        \citet{Besla2018} quantified low mass galaxy ($2\times10^{8} < M_{*} < 5\times10^{9}\,\Msun$) pair fractions at $z\sim0$ in the Illustris-1 hydrodynamic cosmological simulation, utilizing both projected and 3D pairs.
+        The selection criteria for projected pairs include a projected separation cut, $r_{p} < 150\,\kpc$, and a relative line-of-sight velocity difference $\Delta v_{\rm los} < 150\,\kms$.
 
-% % One scenario that could explain this behavior is a very rapid merger timescale for dwarf pairs, and a slower merger timescale for massive pairs. 
-% % In this case, dwarf pairs will merge quickly after formation, thus depleting the number of dwarf pairs at later times. 
-% % Simultaneously, the merged remnant of a dwarf pair is likely to join the population of isolated primaries until star formation finally pushes the stellar mass up into the massive primary regime.
-% % The likelihood of a dwarf pair becoming a massive primary with a minor companion is very small, since only XX\% of dwarf pairs have a major tertiary companion. \kc{calculate the number of }
+        Searching for pairs in a projected space while having access to the true 3D positions and velocities of the galaxies allowed \cite{Besla2018} to quantify the contamination fraction of false pairs due to projection effect.
+        They found that up to $\sim40$\% of identified companions were unrelated but appeared to be close due to projection effects. 
+        The projected pair sample also enabled a direct comparison of the cosmologically-derived pair fractions with an equivalently selected low mass galaxy pair fraction from SDSS.
+        They found that the low mass major pair fraction from SDSS sample was in good agreement with the simulations.
+The~\citet{Besla2018} study points to the Illustris simulation's ability to robustly constrain pair fractions of low mass galaxies, specifically at low $z$.
 
-% % Alternatively, if the dark matter halo and stellar mass of a dwarf galaxy pair increase enough through cosmic accretion or very minor mergers from $z=4$ to $z=2$, the pair will be reclassified as a massive pair at later times.
+        We find reasonable agreement with the sample of physical pairs in \cite{Besla2018}, which found a major pair fraction between 0.003-0.018 over a mass range of $2\times 10^8 < M_* < 5 \times 10^9$ $M\odot$.
+        % used fig. 15 for these vals.
+        Our roughly equivalent low mass major pair sample, when adopting a separation cut of $r_{sep}<150\kpc$, results in a major pair fraction of $0.022^{+0.002}_{-0.003}$ at $z=0$.
+We expect our results to be somewhat higher than in \cite{Besla2018} as our stellar mass range for primaries extends to a lower value of $10^8\Msun$.
+As such, we are confident that our results for low mass pairs are reasonable.
 
-% For example, dwarf galaxy merger timescales may be significantly shorter than massive galaxy merger timescales, which would deplete the population of dwarf galaxy pairs by low redshift. 
-% Additionally, early dwarf galaxy mergers may result in systems that are identified as massive pairs at late times, and massive pairs may grow such that they exceed our mass criteria, thus leading to an apparent overall decrease in the number of pairs.
-% The drop in the absolute number of dwarf and massive primaries at low z as shown in Fig.~\ref{fig:counts} indicates that indeed many of these systems leave the mass range specified by our selection criteria between $z=0-1$.
-% However, since the number of dwarf primaries is roughly constant between $z=0.5-1.5$, but the number of pairs is still decreasing during this time, this indicates that mergers are occurring during this time, and not yet leaving the mass regime specified.
-% In fact, the number of dwarf pairs that are removed from the sample from $z=0$ to $z=2$ is 10 times greater than the total number of massive pairs, indicating that these pairs are not simply accreting matter and moving into the higher mass bin.
+    % high mass comparison
+        For high mass pairs, \citet{snyder2017} created mock catalogs using lightcones in the Illustris-1 simulation to select pairs in the same fashion as done in observations. 
+        They consider major pairs (stellar mass ratio $>1/4$) with: $1\times 10^{11}>M_{*,1} >1\times 10^{10.5}\Msun$, projected distances between $14\kpc-71\kpc$, and a redshift separation of $\Delta z<0.02(1+z_{pri})$, corresponding to a velocity separation of $<1.8\times10^4\kms$ at $z=2$.
+        They find that the major pair fraction is constant or decreasing for $z>1$, which is in good agreement with observational studies.
 
-% \subsection{Comparison to previous pair fraction studies}
-% We performed a pair fraction analysis for dwarf and massive galaxy pairs in the TNG100 simulation, utilizing the full 6D position and velocity information that simulations enable. 
-% However this means that direct comparison to pair fractions reported from observations is not straight-forward, as observationally selected pairs uniquely suffer from contamination, due to projected pairs, and restrictive separation criteria, that exclude more widely separated pairs.
-% Fortunately, a number of previous studies of pair fractions in the Illustris simulations have used lightcones to create mock images of observationally-motivated fields, from which they select pairs in the same fashion that is typically done with observational data.
-% These studies select simulated galaxies based on stellar mass, and then use cuts on the projected separation and line of sight velocity difference to select pairs, which permits direct comparison between simulations and observations.
+        \citet{snyder2023} extended this work, utilizing the TNG simulation to create mock images of extragalactic survey fields mimicking future planned surveys like JADES.
+        From the mock images, they calculated the pair fraction for major pairs with projected separations between $5-70 \kpc$ and with redshift separations of $\Delta z< 0.02(1+z)$. 
+        Again, they found a flat or decreasing major pair fraction with increasing redshift above $z=1$.
 
-% At the low mass end, \citet{Besla2018} quantified dwarf galaxy pair fractions in Illustris-1, both projected and 3D pairs, which enabled a direct comparison of the cosmologically-derived pair fractions with an equivalently selected dwarf pair fraction from SDSS.
-% The pair selection criteria for dwarf galaxies, here defined as stellar masses\footnote{The stellar masses of galaxies from the Illustris simulations used in \citet{Besla2018} are from the median of the \citet{Moster2013} abundance matching prescription, the same as used in this work, rather than the stellar mass values from the simulations.} from $2\times10^{8} < M_{*} < 5\times10^{9}\,\Msun$, include a projected separation criteria of $r_{p} < 150\,\kpc$ and a relative line-of-sight velocity difference $\Delta v_{\rm los} < 150\,\kms$.
+        While we cannot directly compare the values of the pair fractions themselves, since the Snyder et al. work is done in projected space, we can compare the trends as a function of redshift. 
+        Our study finds that the high mass major pair sample has a pair fraction that decreases with redshift above $z=1$, which is in agreement with \cite{snyder2023}.
 
-% By searching for pairs in a projected space while having access to the true 3D positions and velocities of the galaxies, they quantified the contamination fraction and found that up to $\sim40$\% of identified companions were unrelated but appeared to be close due to projection effects.
-% In Illustris, they found that the projected major pair fraction of dwarf galaxies at $z\sim0$ is $f_{p,proj.}\sim0.005-0.012$, while the . \kc{where tf are these numbers from??? }
-% The total pair fraction (including all stellar mass ratios) is $0.032\pm0.005$ for the projected mock catalogs, which are consistent with SDSS equivalently-selected pairs, which find a total pair fraction of $0.035\pm0.3$.
+    % merger rates
+        In addition, \cite{rg15} examine the merger rates of galaxies in the Illustris-1 simulation at $z=0$. 
+        From their Figure~10, there is roughly a factor of 4 difference in the major merger rate for high mass ($M_* \sim 10^{11} \Msun$) vs. low mass ($M_* \sim 10^8 \Msun$) galaxies. 
+        % 1e8 -- 0.005-0.001 -- 5e9
+        % 5e9 -- 0.001 - 0.02 -- 1e11
+        This is also seen in figure 12 of \cite{Guzman-Ortega2023}, who conducted a similar study of galaxy merger rates in the TNG50 simulation. 
+        These studies conclude that the galaxy merger rate has a strong dependence on the mass of the primary galaxy. 
+        Semi-empirical studies also find similar results \citep{Stewart2009, Hopkins2010}. 
+        From our Figure~\ref{fig:pairfrac}, at $z=0$, there is also a factor of 4 difference in the pair fraction for high and low mass galaxies. 
+        The good agreement between our results at $z=0$ and the merger rate calculations suggests that our finding of different pair fractions between low and high mass galaxies is reliable.
 
-% However, using the full physical catalogs, they find a lower pair fraction of $0.02\pm0.004$.
-\kc{I *THINK* this is the fraction of TOTAL pairs (N\_1 from the tables)?
-not just major pairs?
-otherwise I don't know how it's different.}
-% For comparison, when we modify our pair selection criteria to match those of \citet{Besla2018}, and require a 3D separation $r_{\rm sep}< 150\,\kms$ and a 3D relative velocity $\Delta v_{\rm los} < 150\,\kms$, we find a dwarf major pair fraction of XX at $z=0$, which is slightly SKZ than the \citet{Besla2018} results.
-% This is/is not surprising because SKZ.
+            % THis puts more faith into pair fractions as being tracer -- conversion to merger rates would be more straightforward if use cut that scales with 
+            % If pair fraction separation is FIXED then the difference washes out - which is inconsistent with teh merger rate results from massive galaxies.  (the translation to major merger rates )
 
-% As the behavior of the major pair fraction as a function of primary stellar mass is consistent between the projected mock catalogs and the SDSS catalogs, they conclude that cosmological simulations can be used to reliably constrain observational pair fractions of dwarf mergers across time.
-\kc{across time...
-is this true?}
-% Additionally, which projected and 3D pair catalogs yield different absolute values of pair fractions, their behavioral trends as a function of mass are nearly identical such that, in terms of trends, projected and 3D pair fractions will yield similar results.
+   \subsection{Implications for Local Group Galaxies}\label{sec:disc-LG}
+% providing context from well studied galaxies 
+    Our study encompasses the stellar mass range and stellar mass ratios of a few well studied pairs within the Local Group and Local Volume.
+    Thus, we can make predictions for the frequency of finding isolated mass analogs of these systems at higher $z$. 
+    For example, isolated mass analogs of the following pairs are included in each specified sample:
+    the LMC--SMC and NGC4490-4485\footnote{NGC4490-4485 is a low mass ($M_* = 7.2 \mbox{ and } 0.82 \times 10^9\Msun$, respectively) galaxy binary that is $\sim7\Mpc$ away from the MW~\citep{Theureau2007,pearson18}.} (low mass minor pair), the MW--LMC and M31--M33 (high mass minor pair), and the MW--M31 (high mass major pair).
+    Note that both the NGC4490-4485 and MW--M31 pair pass all of our pair selection criteria, while the LMC--SMC,  MW--LMC, and M31--M33 are non-isolated pairs within a more massive group environment.
 
-% % While the study uses projected separations and line of sight velocities, we can assume that the same \textit{trends} are valid for full-6D selected pairs, such that our pair fraction trends can be reasonably compared to those in observations.
+    Mass analogs of the MW--M31 pair are most common today (pink solid line in the left panel of Fig.~\ref{fig:pairfrac}). 
+    Given their large separation of $\sim$760 kpc, they would only be included in the $<2.5$\Rvir panel of Figure~\ref{fig:vircut}.
 
-% Separate studies have analyzed the pair fractions of higher mass galaxies in Illustris simulation. 
-% In particular, \citet{snyder2017} created mock catalogs using lightcones in the Illustris-1 simulation to pick pairs in the same fashion as done in observations. 
-% Specifically, they consider only major pairs with: $1\times 10^{11}>M_{*,1} >1\times 10^{10.5}Msun$, projected distances between $14\kpc-71\kpc$, and a redshift separation of $\Delta z<0.02(1+z_{pri}$, which corresponds to a velocity separation of $<1.8\time10^4\kms$.
-% They find that the major pair fraction for primaries with stellar mass $1\times 10^{10.5-11}Msun$ is constant or decreasing for $z>1$. 
-% Additionally, they compared to observational studies \kc{what studies} that selected pairs with stellar mass $(M* > 10^{10.8}\Msun)$, $(10 <d/(kpc h-1) < 30)$, and $(Msec/Mpri > 0.1)$, and found good agreement between the measured pair fractions as a function of redshift.
-% Thus, projected pair fractions in the Illustris simulation are likely representative of those found in observations for massive galaxy pairs.
+    We find that isolated mass analogs of the LMC--SMC and NGC4490-4485 are roughly three times as common at $z>3$ (green dotted line in the right panel of Fig.~\ref{fig:pairfrac}). 
+    These high $z$ pairs may enter a more massive group halo to become satellites of a larger galaxy~\citep[like the LMC--SMC, ][]{Besla2007,Patel2017a-Orbits}, or if they remain isolated, may continue to merge in a manner similar to NGC4490-4485~\citep{pearson18}.
 
-% \citet{snyder2023} extended this work to utilize the TNG simulation, and created mock images of extragalactic survey fields mimicking future planned surveys like JADES.
-% From the mock images, they calculated the pair fraction for major pairs with projected separations between $5-70 \kpc$ and with redshift separations of $\Delta z< 0.02(1+z)$, and also found flat or decreasing major pair fractions.
-% This is in agreement with our work, as our major pair fraction for massive galaxies is approximately constant or decreasing with higher redshift for $z>1$. 
-% While we cannot directly compare the values of the pair fractions themselves, as the projected and 3D pair separations will yield very different pair fractions as shown in \citet{Besla2018}, we can say that the behavioral trends are the same.
-% Pair fractions computed using 3D separations do not have to account for contamination due to projection effects, which would increase the inferred pair fraction, however our separation criteria is much less stringent, which would also increase the pair fraction.
+    Isolated mass analogs of the MW--LMC and M31--M33 systems are equally likely at $z>1$ as they are at present (right panel of Figure~\ref{fig:pairfrac}). 
+    If we fold in the present-day separation of the MW--LMC system ($\sim50 \kpc$), this high mass minor pair becomes rare at low~$z$\footnote{Fig.~\ref{fig:sepcut} displays pair fraction trends for major pairs.
+The equivalent plot for minor pairs, which we did not include here, shows the same trends as the major pairs, particularly in the $<50\kpc$ panel where the pair fraction for high mass minor pairs is $<0.02$ at $z=0$.}.
+Specifically, we find that 2\% of MW's would host such a close LMC at $z=0$, which is consistent with other cosmological studies, such as \citet{Patel2017a-Orbits}, which finds that 3.8\% of MW-mass halos host an LMC-mass analog within 50 kpc at $z=0$.
+    We also find that such systems (high mass minor pairs with a low separation) are 2-3 times more common at high~$z$.
+M31--M33 analogs, which have higher separations $(\sim200\kpc)$, are more common than MW--LMC analogs at all redshifts.
 
-% % Alejandro's paper connection: studies are finding good agreement between simulations and TNG, as evidenced by this paper.
-They found that TNG simulated images well approximated the morphologies of galaxies in the KIDS survey, although they were a bit more compact and lumpy.
-But this means that there is precedent for using TNG in these kinds of comparisons.
+\subsection{Implications for observational pair fraction studies}\label{sec:disc-obs}
 
-% % ? maybe to do: plot with comparison values 
-% \subsection{Implications for observational pair selection criteria}
-%     %figures
-%     %%%%%%%%%%%%%%%%%%%%
-%     \begin{figure*}[htp]
-%       \centering
-%       \includegraphics[width=\textwidth]{frac_selected.png}
-%       \caption{ The fraction of total pairs selected with additional separation selection criteria as a function of redshift. 
-%         }
-%       \label{fig:frac-select}
-%     \end{figure*}
-%     %%%%%%%%%%%%%%%%%%%%
+    In Sec.~\ref{sec:results-frac}, we presented the pair fraction of high mass and low mass galaxy pairs and found that the relative frequency of the two populations evolve distinctly from $z=0-4.2$.
+    High mass pair fractions peak at $z=0$, decrease from $z=0-0.3$, after which they are roughly constant or mildly decreasing with increasing redshift. 
+    In contrast, low mass pair fractions increase with increasing redshift until $z=2.5$, after which the frequency is roughly constant with increasing redshift. 
+    This behavior is seen for both major and minor pairs.
 
-%     % outline
-%     \begin{itemize}
-%         \item examples of typical pair selection criteria (i.e. <75 kpc, velocity crit, etc.)
-%         \item Show how low separation cuts affect pair fractions      
-%         \item Sep distribution plot and explanation (text below) 
-%         \item Plot of \% of total pairs selected as function of z for different separation criteria (or maybe better is to do total as function of separation, for different redshifts?) 
-%         \item What does this mean for JWST and future surveys?
-%     \end{itemize}
+% Making separation cuts based on physical separations is not the right way to go, and instead we need something that evolves as a function of mass and redshift. 
+    In the previous section we also found that our finding of different pair fractions for high and low mass galaxies are consistent with expectations of a mass dependence in the galaxy merger rate~\citep{rg15, Guzman-Ortega2023}.
 
-% % text on the separation distribution plot
-% % Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$, and includes all 1000 AM realizations. 
-% % For reference, the median at each corresponding redshift from Fig.~\ref{fig:sep} (that is, the median of the medians of each realization) are shown in light black vertical lines.
-% % Each plot is normalized such that the area under an individual curve is 1.
-%     % the redshift evolution
-% % At $z=4$, all pair types (dwarf and massive, major and minor) have narrow distributions that pile up around 0 $\kpc$\footnote{Note that only pairs with separations $>10\kpc$ are included in this analysis, see Sec.~\ref{sec:methods-pairs}.}, with ranges between $10-150\,\kpc$ for dwarf pairs and $10-300\,\kpc$ for massive pairs.
-% % The distributions become more and more broad as $z\to0$, where separations range between $\sim10-400\,\kpc$ for dwarf pairs and $\sim10-1000\,\kpc$ for massive pairs.
+    In Sec.~\ref{sec:results-frac-cuts}, we characterized the behavior of pair fractions for subsamples of the full pair catalog that pass additional separation cuts.
+    We found that physical separation cuts that do not vary as a function of time and mass eliminate the ability to distinguish the different redshift evolution of high and low mass pair fractions, thus unable to capture trends from studies which find that the merger rate varies as a function of galaxy mass~\citep{Stewart2009, Hopkins2010}.
+    Instead, by adopting a separation cut based on the virial radius of the group halo, we can accurately recover the different redshift evolution of low mass vs.
+high mass pair fractions, particularly at $z<2.5$.
 
-% % Since the distribution of separations changes dramatically from $z=4$ to $z=0$, the population of low separation pairs that are selected at $z=4$ includes the majority of true pairs, but this is not the case at low z.
-% % At low z, separation criteria must be very broad to encompass the majority of pairs. 
-% % Figure~\ref{fig:frac-select} shows the fraction of pairs that have separations less than $\{50, 75, 100, 150\}\kpc$.
-% % At high redshift ($z\sim2-4$) a majority of pairs are included in the selection, however at lower redshift ($z\sim0-1$), the pair completeness decreases substantially, with fewer than XX\% of the total number pairs for XX separation criteria.
+    Pair fractions are typically translated to galaxy merger rates using an observability window~\citep{lotz11}.
+    The good agreement between the difference in the low mass and high mass pair fractions and the mass-dependent galaxy merger rates from \cite{rg15} suggests that applying separation cuts that can recover this mass dependency are critical to reliably translate pair fractions to galaxy merger rates.
 
-% As JWST is expected to image dwarfs (give stellar mass range) out to z=XX in XX survey, the selection criteria for dwarf pairs that are applied will affect the inferred pair fractions greatly.
+% Our results indicate that limits on pair separations to study pair fractions should vary as a function of total mass of the pair and redshift. 
+    To study the redshift evolution of low mass pairs and recover differences in the behavior vs.
+high mass pairs, we advocate for a pair separation cut of  $r_{sep} < 1.0\Rvir$, where $\Rvir$ can be inferred using an estimate of the combined dark matter mass of the pair.
+    Taking the observed stellar mass of each pair member, the halo mass for each pair can be estimated using the SMHM relation \citep[e.g.,][]{Moster2013}. 
+    The combined halo mass of the pair can then be used as a proxy for the virial mass of the FoF group ($\rm M_{vir}$) to compute the virial radius, e.g. 
+    \begin{equation}
+    \Rvir = \sqrt[3]{\frac{3\rm M_{vir}}{4\pi \Delta_{c}\rho_{c}}},
+    \end{equation}
+    where $\rho_c$ is the critical density of the universe, and $\Delta_{c}$ is the overdensity constant~\citep[see][]{BinneyTremaine}. 
+    Both $\rho_c$ and $\Delta_{c}$ are functions of redshift, such that $\Rvir$ changes as a function of both the mass of the pair and redshift.
+
+    Given that chance projections will artificially boost the pair fraction as the pair separation is increased, recovering the general evolution of the pair fraction as a function of redshift may be more realistic than recovering the magnitude of the pair fraction itself, since the former requires smaller separation limits.
+    The requirement of $r_{sep} < 1.0\Rvir$ for low mass pairs translates to median separation limits that are less than $\sim 60(30)\kpc$ at $z \sim2(4)$, which are sufficiently small as to avoid major projection effects.
+
+    JWST is expected to identify low mass galaxies ($M_* > 10^8\Msun$) out to at least $z=10$~\citep{Behroozi2020}. 
+    We argue that the adopted pair separation criteria, particular for low mass pairs, will greatly affect the measured pair fractions and consequently the inferred merger rates.
+
+    Understanding in detail the origin of the discrepancy in the redshift evolution of low mass vs.
+high mass pairs requires tracking the specific pairs across simulation snapshots to trace their orbits and study changes in the mass and environment of the pairs across cosmic time.
+    We leave this as the focus of future work.
 
 % %%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary and Conclusions}\label{sec:summary}
+In this paper, we construct a sample of isolated low mass and high mass pairs from the Illustris TNG100 simulation from $z=0-4.2$.
+% GB: define low mass and high mass.
+Also make it clear that pairs are chosen to belong in the same FoF group initially, ensuring they are isolated and not contaminated by projection effects.
+Major and minor pairs are determined using the stellar mass ratio between the primary and secondary halo, % GB : define major and minor
+where stellar masses are assigned using an abundance matching prescription (Cite Moster) to generate 1000 separate realizations of all pairs at each redshift.
+% GB clarify that you sampled the error space.
+From this pair sample, we calculate the pair fraction as a function of redshift for 4 different pair types: low mass major pairs, low mass minor pairs, high mass major pairs, and high mass minor pairs.
+We additionally employ separation cuts to explore the impact of separation selection criteria on the resulting pair fractions.
+% GB: state goal -- our goal is to quantify the evolution of galaxy pairs across cosmic time and identify any differences in this evolution as a function of primary mass (high mass vs.
+low mass galaxies).
 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \pagebreak
+Our main findings are as follows:
+\begin{itemize}
+    \item The pair fraction for low mass and high mass pairs does not proceed identically throughout cosmic time. 
+    In fact, the two mass scales have opposite behavior at $z<2.5$ (see Figure XXX). 
+    The pair fraction of low mass pairs decreases from $z=2\to0$, while the pair fraction of high mass pairs peaks at $z=0$.
+    \item At z=0, we find a low mass major (minor) pair fraction of $0.041^{+0.003}_{-0.004}$ ($0.034\pm0.004$), and a high mass major (minor) pair fraction of $0.207^{+0.012}_{-0.014}$ ($0.152^{+0.016}_{-0.017}$).
+    These results are consistent with studies that find that the merger rate for high mass pairs is $\sim4\times$ higher than for low mass galaxies. 
+    \item Low mass minor pairs evolve similarly to low mass major pairs as a function of redshift.
+    % GB edited
+    The redshift evolution of 
+    high mass minor pair fractions 
+    %have much 
+    is flatter %pair fractions 
+    at $z>1$ than for high mass major pairs, which are constant or decreasing with redshift.
+    \item The true pair fraction behavior of high and low mass pairs is recovered well using a subsample of pairs with a maximum separation cut of $r_{sep}<1\Rvir$, where $\Rvir$ is the 
+    virial radius of the FoF group (see Eqn). % GB: where teh virial radius can be estimated from the combined halo mass of the pair using SMHM relation. 
+    %radius of the group halo.
+    In particular, this separation cut selects between $\sim40-60\%$ of the full population of pairs at all redshifts, and recovers the differences in the redshift evolution of low mass vs.
+high mass pair fractions from $z=0-2.5$.
+% GB: add here what Rvir corresponds to in kpc at specific redshift.
+    %the behavioral trend differences between low mass and high mass pairs from $z=0-2.5$ are distinct.
+    \item The pair fractions of high and low mass pairs are 
+    %somewhat i
+    indistinguishable when a static physical separation cut is employed; i.e.
+a separation that does not evolve with redshift (e.g.
+$r_{sep}<50\kpc$), and is identical for low mass and high mass pairs.
+% GB: explain why this happens - with a fixed separation you are capturing more of the low mass pair sample than the high mass pair sample  \\
+    \item  XXXX conclusion about local group analogs 
+    % \item In order to recover 
+\end{itemize}
+    This means you're recovering different fractions of each population and you aren't actually doing to recover. 
+Thus, in order for the true pair fraction behavior as a function of time to be quantified observationally, we argue that pair selection criteria must be a function of both mass and redshift. 
+Otherwise, selecting the same volume of two different mass scales will incorrectly bias inferred pair fractions, and wash out any differences between low and high mass pairs.
+% GB: connect the importance of recovering the differences between low and high mass pair fractions to efforts to translate pair fractions to merger rates using e.g.
+observability time scales that are fixed.
+Stress importance of avoiding static separation cuts in era of JWST where more low mass galaxies will be discovered.
 
-\section{Summary and Conclusions}\label{sec:summary}
-% In this paper, we collect a large set of dwarf and massive subhalo pairs from the Illustris TNG100-1 simulation. 
-% Pairs are selected from the full volume over all 100 snapshots of the simulation, though the sample size of pairs in the first 20 snapshots ($z>4.2$) is extremely small. 
-% Major and minor pairs are determined using the stellar mass ratio between the primary and secondary halo using stellar masses from 1000 random realizations of the abundance matching prescription. 
-% From this pair sample, we calculate the pair fractions and snapshot by snapshot kinematics of 4 different pair types: dwarf major pairs, dwarf minor pairs, massive major pairs, and massive minor pairs.
+% GB i don't think you need much else beyond the above
 
-% Our main findings are as follows:
-% \begin{itemize}
-%     \item The pair fraction for dwarf and massive pairs does not proceed identically throughout cosmic time.
-In fact, the two mass scales have opposite behavior at low z.
-The number of dwarf pairs per dwarf primary decreases from $z=2\to0$, while the number of massive pairs per massive primary is approximately constant from $z=4\to0.25$, with an abrupt increase at lower redshift.
-%     \item The median 3D separation between the primary and secondary subhalo of a pair increases with decreasing redshift.
-The typical separation of a dwarf (massive) pair is $120\,\kpc$ ($240\,\kpc$) at $z=0$ and $40\,\kpc$ ($80\,\kpc$) at $z=4$.
-%     \item The median relative velocity between the primary and secondary subhalo of a pair decreases towards lower redshift.
-The typical relative velocity of a dwarf (massive) pair is $70\,\kms$ ($175\,\kms$) at $z=0$ and $132\,\kms$ ($290\,\kms$) at $z=4$.
-%     \item The separation scaled by the total virial radius of the group is similar for dwarf and massive pairs, though massive pairs tend to have lower scaled separations for redshifts between $z=0-2$.
-The relative velocity scaled by the circular velocity at the virial radius evolves identically for both dwarf and massive pairs, indicating that the relative velocities are self-similar at different mass scales.
-%     \item All of the above trends hold true for both major and minor pairs of the same mass range (i.e., the conclusions for the dwarf major pairs hold too for the dwarf minor pairs). 
-% \end{itemize}
+% Translating between pair fractions and merger rates for observationally defined samples requires an observability timescale. 
+Since the pair fraction behavior of low and high mass pairs is well recovered using only pairs with $r_{sep}<1.0\Rvir$, we expect that observations that use redshift and mass-dependent selection criteria for high and low mass pairs separately, will likely be able to dis
 
-% Our results are consistent with prior works that have studied the pair fractions of massive and dwarf galaxies in the Illustris simulations in a projected sense. 
-% The agreement between the pair fraction trends from projected and from 3D pair selection criteria points to the IllustrisTNG simulation's robust ability to reproduce the characteristics of galaxy pairs from observations.
+% Our results are consistent with prior works that have studied the pair fractions of low mass, physical galaxy pairs in the Illustris simulations, as well as those that adopt projected separation and velocity criteria over a similar stellar mass range as ours.
+% The agreement between the pair fraction trends from these projected studies, which have found good agreement with observations, and from our physical pair fraction study   to TNG's robust ability to reproduce the frequency of galaxy pairs from observations.
 
-% Additionally, we conclude that:
+% Talk about what we've missed and hinted at, and what our next project will kinda do to resolve this.
+
+Quantifying the observability timescale of low mass and high mass systems separately will be necessary to properly
+
 % \begin{itemize}
@@
 % Our conclusions point to the importance of time-evolving pair selection criteria that account for the natural separation increase of pairs at the universe expands.
-
-% \kc{other main takeaways?}
-
-% \begin{itemize}
-%     \item otherMain takeaways: (maybe include these within main findings bullets~)
-%         \begin{itemize}
-%             \item lit comp.
-%             \item dwarfs not equal massives 
-%             \item JWST imps.
-%         \end{itemize}
-%     \item Future work
-% \end{itemize}
-
-% Findings:
-% \begin{itemize}
-%     \item 
-%     \item Median pair separations increase and relative velocities decrease from high to low redshift. 
-% \end{itemize}
 

### 2023-07-24 paper/pears.tex
sending to G P and V!

@@
 \begin{abstract}
-  Galaxy pair fractions for low mass galaxies (DEFINE) are understudied across cosmic time.
-In particular, it is unclear whether low mass galaxy pair fractions are expected to evolve similarly to that of high mass galaxies (DEFINE high mass) in CDM theory.
-There has been no systematic study to ensure that any differences in CDM simulation can be captured in observational surveys.
-  In this study we *** Illustris, quick methods
-    define pair fractions self-consistently, WE find BLAH
-    we also a conduct a study to assess the impact of pair selection criteria based on separation cuts on the resulting pair fractions . We find BLAH. 
-    If you apply the same separation, you wash out these effects, but we know that they exist in merger fracs, so how do we observe this ?    
-    This sample is also used to place our Local Group of galaxy pairs in cosmological context across cosmic time for the first time --> high level 
+Low mass galaxy pair fractions are understudied across cosmic time. 
+In the era of JWST, a self-consistent framework is needed to select both low and high mass galaxy pairs in order to connect observed pair fractions to cosmological merger rates across all mass scales and redshifts.
+Here, we construct a sample of low mass ($\rm 10^8<M_*<5\times10^9\,\Msun$) and high mass ($\rm 5\times10^9<M_*<10^{11}\,\Msun$) subhalo pairs from the TNG100 simulation from $z=0-4.2$. 
+Pairs belong to the same FoF group, meaning they are isolated, physically associated, and not contaminated by projection effects. 
+Stellar masses are assigned using abundance matching. 
+We find that the low mass pair fraction increases from $z=0-2.5$, while the high mass pair fraction peaks at $z=0$ and is constant or slightly decreasing at $z>1$. 
+At z=0 the low mass major pair fraction is four times lower than that of high mass pairs, consistent with findings for cosmological merger rates. 
+Our results indicate that pair fractions can faithfully reproduce trends in merger rates if galaxy pairs are selected appropriately. 
+Specifically, static pair separation limits applied equivalently to all galaxy pairs do not recover the evolution of low and high mass pair fractions. 
+Instead, we advocate for separation limits that vary with the mass and redshift of the system, such as separation limits scaled by the estimated virial radius of the pair ($r_{sep}< 1 R_{vir}$). 
+Finally, we place isolated mass-analogs of Local Group galaxy pairs (MW--M31, MW--LMC, M31--M33, LMC--SMC) in a cosmological context, quantifying for the first time the frequency of finding isolated analogs of such pairs as a function of redshift.
+
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
-% galaxy mergers 
     Galaxy mergers have been studied in detail as a mechanism for driving galaxy evolution, and have been identified as a trigger of, for example, 
-    active galactic nuclei (AGN)~\citep[e.g.][]{Hopkins2008,comerford15,Blecha2018,ellison19}, 
-    star formation~\citep[e.g.][]{Mihos1996, DiMatteo2008,Patton2013, hopkins13,patton20,hani20}, 
-    and changes in morphology~\citep[e.g.][]{Conselice2003,lotz08,casteels14,rg17,Guzman-Ortega2023}. 
-    Constraining the merger rate for galaxies is critical for quantifying the importance of mergers for galaxy evolution and hierarchical assembly.
+    active galactic nuclei (AGN)~\citep[e.g.][]{Hopkins2008,Comerford2015,Blecha2018,Ellison2019}, 
+    star formation~\citep[e.g.][]{Mihos1996, DiMatteo2008,Patton2013, Hopkins2013,Patton2020,Hani2020}, 
+    and changes in morphology~\citep[e.g.][]{Conselice2003,Lotz2008,Casteels2014,RG2017,Guzman-Ortega2023}. 
+    Constraining the merger rate for galaxies is critical for quantifying the importance of mergers for galaxy evolution and testing predictions for hierarchical assembly in cold dark matter theory \citep[e.g.][]{Stewart2009,Hopkins2010,RG2015}.
 
-    In practice, merger rates cannot be measured straightforwardly from observations and, rather, are calculated by converting the observed frequency of a galaxy merger signature (i.e., asymmetry, concentration, pair fraction, etc.) to a merger rate using an observability timescale~\citep[e.g.][]{lotz11}.
-    Low mass galaxies are most often morphologically disturbed by fly-bys and non-merger interactions~\citep{Martin2021}, and star forming galaxies at high redshift tend to be clumpy and asymmetric, even in isolation~\citep{Wuyts2013}, thus pair fractions offer likely the most robust method of observationally quantifying merger rates.
+    In practice, merger rates cannot be measured straightforwardly from observations and, rather, are calculated by converting the observed frequency of a galaxy merger signature (i.e., asymmetry, concentration, pair fraction, etc.) to a merger rate using an observability timescale~\citep[e.g.][]{Lotz2011}.
+    Low mass galaxies are most often morphologically disturbed by fly-bys and non-merger interactions~\citep{Martin2021}, and star forming galaxies at high redshift tend to be clumpy and asymmetric, even in isolation~\citep{Wuyts2013}, thus pair fractions offer the most robust method of observationally quantifying merger rates across cosmic time.
 
-    Pair fractions of high mass ($M_*\gtrsim10^{10}\Msun$) galaxies have been well studied across cosmic time both observationally~\citep[e.g.][]{Patton2000,lotz11,Ferreras2014, Man2016,Duncan2019}, and theoretically~\citep[e.g.][]{rg15,snyder2017,snyder2023}, with theoretical studies typically done in projection for comparison to observational campaigns.
-    Low mass galaxy pairs ($10^8<M_*<5\times10^9\Msun$) have been studied at low redshift~\citep[e.g.][]{stierwalt15,pearson16,Besla2018,Paudel2018,Luber2022},
+    Pair fractions of high mass ($M_*\gtrsim10^{10}\Msun$) galaxies have been well studied across cosmic time both observationally~\citep[e.g.][]{Patton2000,Lotz2011,Ferreras2014, Man2016,Duncan2019}, and theoretically~\citep[e.g.][]{RG2015,Snyder2017,Snyder2023}, with theoretical studies typically done in projection for comparison to observational campaigns.
+    Low mass galaxy pairs ($10^8<M_*<5\times10^9\Msun$) have been studied at low redshift~\citep[e.g.][]{Stierwalt2015,Pearson2016,Besla2018,Paudel2018,Luber2022},
     but are less well understood across cosmic time owing to the difficulty in observing faint systems outside of the Local Volume. 
@@
     There are reasons to believe that low mass and high mass pairs evolve differently as a function of time.
-    For example, semi-empirical and cosmological studies find that galaxy merger rates vary both with redshift and the mass of the most massive galaxy of the pair~\citep[see e.g.][]{Stewart2009,Hopkins2010,rg15}.
+    For example, semi-empirical and cosmological studies find that galaxy merger rates vary both with redshift and the mass of the most massive galaxy of the pair~\citep[see e.g.][]{Stewart2009,Hopkins2010,RG2015}.
     % Such differences are likely to give rise to differences in the pair fractions of low and high mass pairs.
@@
     The redshift evolution of low and high mass pair fractions has not yet been studied in simulations in a self-consistent way, where high mass and low mass pairs are selected from simulations using otherwise equivalent selection criteria.
-    We aim to characterize the redshift behavior of pair fractions of low mass and high mass pairs, independent of environmental and projection effects, and to create a robust framework by which to fairly compare pair fractions of different mass scales across cosmic time.
+    We aim to characterize the redshift behavior of pair fractions of low mass and high mass pairs, independent of environmental and projection effects, and to create a robust framework in which to fairly compare pair fractions of different mass scales across cosmic time.
 
@@
     To fairly test for differences in the evolutionary behavior of pair fractions, especially in observational studies, it is necessary to determine whether this is an appropriate technique for faithfully recovering true pair fraction behavior.
-    % it will be necessary to apply the proper theoretical framework for interpretting and analyzing low mass and high mass systems equivalently. 
     In this study we identify how the application of a fixed separation criteria affects inferred pair fractions, and make recommendations for a time and mass evolving separation cut to permit equitable pair fraction comparisons between different mass regimes.
-    % We identify how the application of To this end, we apply one set of fixed separation cuts, and a second set of separation cuts that varies as a function of mass and redshift, and identify how these two methods
 
@@
       % subfind, sublink, and groups and subhalos
-    We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm~\citep{springel2001,dolag09}. 
-    This catalog was created using the Friends-of-Friends (FoF) algorithm~\citep{davis1985}, which links nearby particles to define large halos of associated particles, from which subhalos are identified as over-dense and gravitationally bound dark matter structures.
-    In addition, we utilize the merger trees provided by the \texttt{SUBLINK} algorithm~\citep{rg15}, which tracks subhalos between snapshots, enabling us to trace the mass evolution of our selected subhalos.
+    We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm~\citep{Springel2001,Dolag2009}. 
+    This catalog was created using the Friends-of-Friends (FoF) algorithm~\citep{Davis1985}, which links nearby particles to define large halos of associated particles, from which subhalos are identified as over-dense and gravitationally bound dark matter structures.
+    In addition, we utilize the merger trees provided by the \texttt{SUBLINK} algorithm~\citep{RG2015}, which tracks subhalos between snapshots, enabling us to trace the mass evolution of our selected subhalos.
 
@@
 
-    First, at each snapshot, we apply a cut on the total FoF group mass, \MG{}, given by \texttt{Group\_M\_TopHat200} in the TNG100 group catalogs. 
+    First, at each snapshot, we apply a cut on the total FoF group mass, \MG{}, given by \texttt{Group\_M\_TopHat200}\footnote{The mass \texttt{Group\_M\_TopHat200} is the total mass enclosed by a sphere with mean density $\Delta_c *\rho_c$, where $\Delta_c$ is the overdensity constant from~\citet{Brynorman1998} and $\rho_c$ is the critical density of the universe at the time calculated.} in the TNG100 group catalogs.
     We define the group mass range for low mass and high mass groups as: 
@@
     \end{equation*}
-    This ``minimum mass" threshold ensures that subhalos are resolved into $>100$ particles, and thus should be robustly identifiable using the \subfind\ and \sublink\ algorithms \citep{rg15}.
+    This ``minimum mass" threshold ensures that subhalos are resolved into $>100$ particles, and thus should be robustly identifiable using the \subfind\ and \sublink\ algorithms \citep{RG2015}.
 
@@
     Using $z_{snap}$ means that we allow the stellar mass of both the primary and secondary halo to change as a function of redshift, even after the secondary has entered the primary's halo. 
-    This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{geha13}, which found that dwarfs $>1.5\Mpc$ from a MW-type galaxy are often star forming and rarely quenched.
+    This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{Geha2013}, which found that dwarfs $>1.5\Mpc$ from a MW-type galaxy are often star forming and rarely quenched.
     Additionally, the SAGA survey has found that large satellites of MW-type galaxies are often very blue, with infall into the halo spurring high rates of star formation due to the large gas fraction in dwarfs~\citep{Mao2021}.
@@
         We do not include companions with a stellar mass ratio $M_{*2}/M_{*1} <1/10$ as we will be limiting our pair sample to traditional definitions of major and minor pairs, 
-        which are typically defined to have stellar mass ratios $M_{*2}/M_{*1} > 1/10$~\citep[i.e.][]{lotz11, rg15, snyder2017, duncan19, Wang2020, Guzman-Ortega2023}.
-        % where minor pairs are typically defined as having mass ratios between $1/4 > M_{*2}/M_{*1} > 1/10$ \citep{lotz11, rg15, Guzman-Ortega2023}.
+        which are typically defined to have stellar mass ratios $M_{*2}/M_{*1} > 1/10$~\citep[i.e.][]{Lotz2011, RG2015, Snyder2017, Duncan2019, Wang2020, Guzman-Ortega2023}.
+        % where minor pairs are typically defined as having mass ratios between $1/4 > M_{*2}/M_{*1} > 1/10$ \citep{Lotz2011, RG2015, Guzman-Ortega2023}.
         Our subhalo ``minimum mass" threshold of $\Mhalo=10^9$ (described in Sec.~\ref{sec:methods-halos}) corresponds to a mean stellar mass of $10^6\Msun$ at $z=0$. 
@@
         Pairs consist of a single primary and secondary in a FoF group as defined via the criteria above. 
-        Each pair is categorized as either a major or minor pair based on the stellar mass ratio between the primary and secondary. Following, e.g. \cite{lotz11, rg15}, 
+        Each pair is categorized as either a major or minor pair based on the stellar mass ratio between the primary and secondary. Following, e.g. \cite{Lotz2011, RG2015}, 
         the stellar mass ratio criteria for major and minor pairs are:
@@
         For each pair, we calculate the physical separation (\kpc, not comoving \kpc) between the two subhalos using the \texttt{SubhaloPos} field from the group catalogs.
-We require that each pair have a minimum separation of $10 \kpc$ between primary and secondary to limit the impact of very close subhalos becoming indistinguishable in \subfind~\citep{rg17}.
+We require that each pair have a minimum separation of $10 \kpc$ between primary and secondary to limit the impact of very close subhalos becoming indistinguishable in \subfind~\citep{RG2017}.
         % The minimum separation cut is more than 10 times the smoothing length of the simulation at $z=0$, which ensures that  can identify the subhalos as distinct objects XXXXX ADD CITATION HERE - vicente?
@@
         For each isolated primary, we store the current subhalo mass (\Mhalo) and stellar mass from the given realization. 
-        For each pair, we store the primary and secondary subhalo masses (\Mhalo) and stellar masses, the pair separation, and the virial radius of the FoF group (given by the  the \texttt{Group\_R\_TopHat200} field in the group catalogs).
+        For each pair, we store the primary and secondary subhalo masses (\Mhalo) and stellar masses, the pair separation, and the virial radius of the FoF group (given by the \texttt{Group\_R\_TopHat200} field in the group catalogs\footnote{The radius of the sphere which encloses the virial mass \texttt{Group\_M\_TopHat200}.
+See Sec.~\ref{sec:methods} for details.}).
 
@@
 In Sec.~\ref{sec:results-frac}, we examine the redshift evolution of the fraction of primaries with a major or minor companion (the ``pair fraction") and compare the results for low mass and high mass pairs.
-In Sec.~\ref{sec:results-frac-sepcut}, we examine the redshift evolution of the pair fraction as a function of pair separation.
+In Sec.~\ref{sec:results-frac-cuts}, we examine the redshift evolution of the pair fraction as a function of pair separation. 
+In Sec.~\ref{sec:disc-dark}, we briefly describe how our equivalent pair fraction analysis utilizing the TNG100-Dark simulation compares to the TNG100 results presented in the previous two sections.
 
@@
     for high mass (pink) and low mass (green) pairs in each of the 6 subsamples. 
-    In the bottom row, we show the completeness\kc{change name}, which is the fraction of the total pair sample that is recovered in each subsample, i.e.
+    In the bottom row, we show the recovery fraction, which is the fraction of the total pair sample that is recovered by each subsample, i.e.
 the number of pairs that pass each separation criterion divided by the total number of pairs in the full sample presented in Sec.~\ref{sec:results-frac}.
 
-    As the pair separation limits increase (left to right), the completeness increases, as does the pair fraction, as expected because each consecutive selection cut is less restrictive and will contain more of the full sample.
+    As the pair separation limits increase (left to right), the recovery fraction increases, as does the pair fraction, as expected because each consecutive selection cut is less restrictive and will contain more of the full sample.
     More than 75\% of the full pair sample is recovered at all redshifts with separation criteria up to $2\Rvir$.
@@
     All subsamples of high mass pairs display broadly the same pair fraction redshift evolution as the full high mass sample (pink line in left panel of Figure~\ref{fig:pairfrac}): each of the subsampled high mass pair fractions peak at $z=0$ and remain roughly constant or decrease at higher redshift.
-    The finer detail trends from the full sample, particularly the upturn at low z, are reasonably captured if $r_{sep} < 0.5 \Rvir$, despite the completeness being $\sim$40\%. 
+    The finer detail trends from the full sample, particularly the upturn at low z, are reasonably captured if $r_{sep} < 0.5 \Rvir$, despite the recovery being $\sim$40\%. 
     % The magnitude of the pair fraction as a function of redshift for the full sample is best captured if $r_{sep} < 2.0\Rvir$.
@@
     %edited 
-    When the separation is limited to $r_{sep} < 1.5\Rvir$, the trends with redshift for the full low mass sample are recovered, particularly the roughly flat behavior from $z\sim2-4$, despite a sample completeness of $<75\%$.
+    When the separation is limited to $r_{sep} < 1.5\Rvir$, the trends with redshift for the full low mass sample are recovered, particularly the roughly flat behavior from $z\sim2-4$, despite a sample recovery of $<75\%$.
     % The magnitude of the full low mass pair fraction is recovered for $r_{sep} < 2.0$\Rvir. 
@@
         Recovering the differences between high and low mass pair fraction trends seen for the total sample at $z>2$, requires $r_{sep} < 0.5\Rvir$ for both galaxy types. 
-        (Bottom) The completeness, calculated as the fraction of the total collection of pairs recovered by the subset of pairs at the given separation cut. 
+        (Bottom) The recovery fraction, calculated as the fraction of the total collection of pairs recovered by the subset of pairs at the given separation cut. 
         We find that recovering the redshift evolution of the pair fractions of all galaxy pairs requires a separation cut such that the number of close pairs constitutes $\sim50-70\%$ of the full sample at all redshifts.
@@
     Fig.~\ref{fig:sepcut} shows the median pair fractions for the subsamples of pairs with separations lower than the physical separation listed at the top of each column. 
-    The bottom row of the plot shows the completeness, or the number of pairs in each subsample compared to the full sample of major pairs. 
-    Again, as the maximum separation increases (left to right), so too does the pair fraction and completeness of the subsample.
+    The bottom row of the plot shows the recovery fraction, or the number of pairs in each subsample compared to the full sample of major pairs. 
+    Again, as the maximum separation increases (left to right), so too does the pair fraction and recovered fraction of the subsample.
 
     The low mass major pair fraction (green) maintains roughly the same behavior (decreasing with decreasing redshift) for each separation cut, and first recovers the redshift evolution and magnitude of the pair fraction of the full sample (left panel of Fig.~\ref{fig:pairfrac}) for a separation cut of $r_{sep} < 150\kpc$.
-    This is not surprising based on our results from the previous section as this separation is larger than the median virial radius of the sample and the completeness is larger than 50\% at all redshifts (reaching nearly 100\% at $z\sim3$).
+    This is not surprising based on our results from the previous section as this separation is larger than the median virial radius of the sample and the recovery fraction is larger than 0.50 at all redshifts (reaching nearly 100\% at $z\sim3$).
     The low mass pair fraction does not change significantly by excluding pairs with separations $>150\kpc$.
@@
     This is in stark contrast to results from the previous section where the recovery fraction was roughly constant as a function of redshift.
-    Because the same separation cut is applied to low and high mass pairs, the completeness for low mass pairs is universally higher than for high mass pairs at each separation cut, which wipes out any redshift evolution differences between the two galaxy types.
+    Because the same separation cut is applied to low and high mass pairs, the recovery fraction for low mass pairs is universally higher than for high mass pairs at each separation cut, which wipes out any redshift evolution differences between the two galaxy types.
 
@@
     % Since the~\citet{Moster2013} AM relation was calibrated using DM subhalos from the \texttt{MilleniumII} dark matter only simulation, we will use the total subhalo mass from the TNG100 hydro simulation as a proxy for the corresponding DM halo mass in the TNG100-1 Dark run, \texttt{SubhaloMass}.
-
-% end Results section%
+% end results
 %%%%%%%%%%%%%%%%%%%%%%
@@
 
-\todo{redo ordering when finalized~}
-In Sec.~\ref{sec:disc-dark}, we briefly describe how our equivalent pair fraction analysis utilizing the TNG100-Dark simulation compares to the TNG100 results presented in Sec.~\ref{sec:results}. 
+In Sec.~\ref{sec:disc-LG}, we draw comparisons between our pair sample and various Local Group pairs to quantify the likelihood of finding isolated analogs of such pairs at higher $z$.
 In Sec.~\ref{sec:disc-comp}, we compare our results to previous studies of pair fractions that utilize simulations. 
-% implications of difference and detectability 
-We discuss the implications of the pair fraction behavior of low mass pairs and high mass pairs as a function of redshift and how we might be able to detect these differences in Sec.~\ref{sec:disc-obs}.
-% local group
-Finally in Sec.~\ref{sec:disc-LG}, we draw comparisons between our pair sample and various Local Group pairs to quantify the likelihood of finding isolated analogs of such pairs at higher $z$.
+Finally, we discuss the implications of the pair fraction behavior of low mass pairs and high mass pairs as a function of redshift for observations and how we might be able to detect these differences in Sec.~\ref{sec:disc-obs}.
+
+   \subsection{Implications for Local Group Galaxies}\label{sec:disc-LG}
+% providing context from well studied galaxies 
+    Our study encompasses the stellar mass range and stellar mass ratios of a few well studied pairs within the Local Group and Local Volume.
+    Thus, we can make predictions for the frequency of finding isolated mass analogs of these systems at higher $z$. 
+    For example, isolated mass analogs of the following pairs are included in each specified sample:
+    the LMC--SMC and NGC4490-4485\footnote{NGC4490-4485 is a low mass ($M_* = 7.2 \mbox{ and } 0.82 \times 10^9\Msun$, respectively) galaxy binary that is $\sim7\Mpc$ away from the MW~\citep{Theureau2007,Pearson2018}.} (low mass minor pair), the MW--LMC and M31--M33 (high mass minor pair), and the MW--M31 (high mass major pair).
+    Note that both the NGC4490-4485 and MW--M31 pair pass all of our pair selection criteria, while the LMC--SMC,  MW--LMC, and M31--M33 are non-isolated pairs within a more massive group environment.
+
+    Mass analogs of the MW--M31 pair are most common today (pink solid line in the left panel of Fig.~\ref{fig:pairfrac}). 
+    Given their large separation of $\sim$760 kpc, they would only be included in the $<2.5\Rvir$ panel of Figure~\ref{fig:vircut}.
+
+    We find that isolated mass analogs of the LMC--SMC and NGC4490-4485 are roughly three times as common at $z>3$ (green dotted line in the right panel of Fig.~\ref{fig:pairfrac}). 
+    These high $z$ pairs may enter a more massive group halo to become satellites of a larger galaxy~\citep[like the LMC--SMC, ][]{Besla2007,Patel2017a-Orbits}, or if they remain isolated, may continue to merge in a manner similar to NGC4490-4485~\citep{Pearson2018}.
+
+    Isolated mass analogs of the MW--LMC and M31--M33 systems are equally likely at $z>1$ as they are at present (right panel of Figure~\ref{fig:pairfrac}). 
+    If we fold in the present-day separation of the MW--LMC system ($\sim50 \kpc$), this high mass minor pair becomes rare at low~$z$\footnote{Fig.~\ref{fig:sepcut} displays pair fraction trends for major pairs.
+The equivalent plot for minor pairs, which we did not include here, shows the same trends as the major pairs, particularly in the $<50\kpc$ panel where the pair fraction for high mass minor pairs is $<0.02$ at $z=0$.}.
+Specifically, we find that 2\% of MW's would host such a close LMC at $z=0$, which is consistent with other cosmological studies, such as \citet{Patel2017a-Orbits}, which finds that 3.8\% of MW-mass halos host an LMC-mass analog within 50 kpc at $z=0$.
+    We also find that such systems (high mass minor pairs with a low separation) are 2-3 times more common at high~$z$.
+M31--M33 analogs, which have higher separations $(\sim200\kpc)$, are more common than MW--LMC analogs at all redshifts.
 
@@
     % high mass comparison
-        For high mass pairs, \citet{snyder2017} created mock catalogs using lightcones in the Illustris-1 simulation to select pairs in the same fashion as done in observations. 
+        For high mass pairs, \citet{Snyder2017} created mock catalogs using lightcones in the Illustris-1 simulation to select pairs in the same fashion as done in observations. 
         They consider major pairs (stellar mass ratio $>1/4$) with: $1\times 10^{11}>M_{*,1} >1\times 10^{10.5}\Msun$, projected distances between $14\kpc-71\kpc$, and a redshift separation of $\Delta z<0.02(1+z_{pri})$, corresponding to a velocity separation of $<1.8\times10^4\kms$ at $z=2$.
@@
 
-        \citet{snyder2023} extended this work, utilizing the TNG simulation to create mock images of extragalactic survey fields mimicking future planned surveys like JADES.
+        \citet{Snyder2023} extended this work, utilizing the TNG simulation to create mock images of extragalactic survey fields mimicking future planned surveys like JADES.
         From the mock images, they calculated the pair fraction for major pairs with projected separations between $5-70 \kpc$ and with redshift separations of $\Delta z< 0.02(1+z)$. 
@@
         While we cannot directly compare the values of the pair fractions themselves, since the Snyder et al. work is done in projected space, we can compare the trends as a function of redshift. 
-        Our study finds that the high mass major pair sample has a pair fraction that decreases with redshift above $z=1$, which is in agreement with \cite{snyder2023}.
+        Our study finds that the high mass major pair sample has a pair fraction that decreases with redshift above $z=1$, which is in agreement with \cite{Snyder2023}.
 
     % merger rates
-        In addition, \cite{rg15} examine the merger rates of galaxies in the Illustris-1 simulation at $z=0$. 
+        In addition, \cite{RG2015} examine the merger rates of galaxies in the Illustris-1 simulation at $z=0$. 
         From their Figure~10, there is roughly a factor of 4 difference in the major merger rate for high mass ($M_* \sim 10^{11} \Msun$) vs. low mass ($M_* \sim 10^8 \Msun$) galaxies. 
@@
 
-   \subsection{Implications for Local Group Galaxies}\label{sec:disc-LG}
-% providing context from well studied galaxies 
-    Our study encompasses the stellar mass range and stellar mass ratios of a few well studied pairs within the Local Group and Local Volume.
-    Thus, we can make predictions for the frequency of finding isolated mass analogs of these systems at higher $z$. 
-    For example, isolated mass analogs of the following pairs are included in each specified sample:
-    the LMC--SMC and NGC4490-4485\footnote{NGC4490-4485 is a low mass ($M_* = 7.2 \mbox{ and } 0.82 \times 10^9\Msun$, respectively) galaxy binary that is $\sim7\Mpc$ away from the MW~\citep{Theureau2007,pearson18}.} (low mass minor pair), the MW--LMC and M31--M33 (high mass minor pair), and the MW--M31 (high mass major pair).
-    Note that both the NGC4490-4485 and MW--M31 pair pass all of our pair selection criteria, while the LMC--SMC,  MW--LMC, and M31--M33 are non-isolated pairs within a more massive group environment.
-
-    Mass analogs of the MW--M31 pair are most common today (pink solid line in the left panel of Fig.~\ref{fig:pairfrac}). 
-    Given their large separation of $\sim$760 kpc, they would only be included in the $<2.5$\Rvir panel of Figure~\ref{fig:vircut}.
-
-    We find that isolated mass analogs of the LMC--SMC and NGC4490-4485 are roughly three times as common at $z>3$ (green dotted line in the right panel of Fig.~\ref{fig:pairfrac}). 
-    These high $z$ pairs may enter a more massive group halo to become satellites of a larger galaxy~\citep[like the LMC--SMC, ][]{Besla2007,Patel2017a-Orbits}, or if they remain isolated, may continue to merge in a manner similar to NGC4490-4485~\citep{pearson18}.
-
-    Isolated mass analogs of the MW--LMC and M31--M33 systems are equally likely at $z>1$ as they are at present (right panel of Figure~\ref{fig:pairfrac}). 
-    If we fold in the present-day separation of the MW--LMC system ($\sim50 \kpc$), this high mass minor pair becomes rare at low~$z$\footnote{Fig.~\ref{fig:sepcut} displays pair fraction trends for major pairs.
-The equivalent plot for minor pairs, which we did not include here, shows the same trends as the major pairs, particularly in the $<50\kpc$ panel where the pair fraction for high mass minor pairs is $<0.02$ at $z=0$.}.
-Specifically, we find that 2\% of MW's would host such a close LMC at $z=0$, which is consistent with other cosmological studies, such as \citet{Patel2017a-Orbits}, which finds that 3.8\% of MW-mass halos host an LMC-mass analog within 50 kpc at $z=0$.
-    We also find that such systems (high mass minor pairs with a low separation) are 2-3 times more common at high~$z$.
-M31--M33 analogs, which have higher separations $(\sim200\kpc)$, are more common than MW--LMC analogs at all redshifts.
-
 \subsection{Implications for observational pair fraction studies}\label{sec:disc-obs}
@@
 % Making separation cuts based on physical separations is not the right way to go, and instead we need something that evolves as a function of mass and redshift. 
-    In the previous section we also found that our finding of different pair fractions for high and low mass galaxies are consistent with expectations of a mass dependence in the galaxy merger rate~\citep{rg15, Guzman-Ortega2023}.
+    In the previous section we also found that our finding of different pair fractions for high and low mass galaxies are consistent with expectations of a mass dependence in the galaxy merger rate~\citep{RG2015, Guzman-Ortega2023}.
 
@@
 
-    Pair fractions are typically translated to galaxy merger rates using an observability window~\citep{lotz11}.
-    The good agreement between the difference in the low mass and high mass pair fractions and the mass-dependent galaxy merger rates from \cite{rg15} suggests that applying separation cuts that can recover this mass dependency are critical to reliably translate pair fractions to galaxy merger rates.
+    Pair fractions are typically translated to galaxy merger rates using an observability window~\citep{Lotz2011}.
+    The good agreement between the difference in the low mass and high mass pair fractions and the mass-dependent galaxy merger rates from \cite{RG2015} suggests that applying separation cuts that can recover this mass dependency are critical to reliably translate pair fractions to galaxy merger rates.
 
@@
     The combined halo mass of the pair can then be used as a proxy for the virial mass of the FoF group ($\rm M_{vir}$) to compute the virial radius, e.g. 
-    \begin{equation}
+    \begin{equation}\label{eq}
     \Rvir = \sqrt[3]{\frac{3\rm M_{vir}}{4\pi \Delta_{c}\rho_{c}}},
     \end{equation}
-    where $\rho_c$ is the critical density of the universe, and $\Delta_{c}$ is the overdensity constant~\citep[see][]{BinneyTremaine}. 
+    where $\rho_c$ is the critical density of the universe, and $\Delta_{c}$ is the overdensity constant~\citep[see][]{BinneyTremaine2008}. 
     Both $\rho_c$ and $\Delta_{c}$ are functions of redshift, such that $\Rvir$ changes as a function of both the mass of the pair and redshift.
@@
     We leave this as the focus of future work.
+% end discussion
+% %%%%%%%%%%%%%%%%%%%%%%
 
-% %%%%%%%%%%%%%%%%%%%%%%
 % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Summary and Conclusions}\label{sec:summary}
-In this paper, we construct a sample of isolated low mass and high mass pairs from the Illustris TNG100 simulation from $z=0-4.2$.
-% GB: define low mass and high mass.
-Also make it clear that pairs are chosen to belong in the same FoF group initially, ensuring they are isolated and not contaminated by projection effects.
-Major and minor pairs are determined using the stellar mass ratio between the primary and secondary halo, % GB : define major and minor
-where stellar masses are assigned using an abundance matching prescription (Cite Moster) to generate 1000 separate realizations of all pairs at each redshift.
-% GB clarify that you sampled the error space.
+In this paper, we construct a sample of low mass ($\rm 10^8<M_*<5\times10^9\,\Msun$) and high mass ($\rm 5\times10^9<M_*<10^{11}\,\Msun$) pairs from the TNG100 simulation from $z=0-4.2$.
+Pairs are selected as belonging to the same FoF group such that they are isolated and physically associated, and not contaminated by projection effects.
+Major and minor pairs are determined using the stellar mass ratio (1--1/4 and 1/4--1/10, respectively) between the primary and secondary halo, where stellar masses are assigned using an abundance matching prescription from~\cite{Moster2013} to generate 1000 separate realizations of selected pairs at each redshift in order to sample the error space of the SMHM relation.
+
 From this pair sample, we calculate the pair fraction as a function of redshift for 4 different pair types: low mass major pairs, low mass minor pairs, high mass major pairs, and high mass minor pairs.
-We additionally employ separation cuts to explore the impact of separation selection criteria on the resulting pair fractions.
-% GB: state goal -- our goal is to quantify the evolution of galaxy pairs across cosmic time and identify any differences in this evolution as a function of primary mass (high mass vs.
-low mass galaxies).
+Our goal is to quantify the evolution of low mass and high mass galaxy pairs across cosmic time and to identify any differences in the redshift evolution of pair fractions of low mass and high mass pairs.
+We also aim to determine whether the redshift evolution of the pair fraction can be well recovered from observationally selected pairs. 
+To this end, we additionally employ both static and time+mass evolving separation cuts to explore the resulting impact on the pair fractions.
 
@@
 \begin{itemize}
-    \item The pair fraction for low mass and high mass pairs does not proceed identically throughout cosmic time. 
-    In fact, the two mass scales have opposite behavior at $z<2.5$ (see Figure XXX). 
-    The pair fraction of low mass pairs decreases from $z=2\to0$, while the pair fraction of high mass pairs peaks at $z=0$.
+  % overall low vs high mass
+    \item \textbf{The pair fraction for low mass and high mass pairs does not proceed identically throughout cosmic time.}
+    In fact, the two mass scales have opposite behavior at $z<2.5$ (see Figure~\ref{fig:pairfrac}).
+    The pair fraction of low mass pairs increases from $z=0$ to $z\sim2.5$, while the pair fraction of high mass pairs peaks at $z=0$ and is constant or slightly decreasing at $z>1$.
+  % present values
     \item At z=0, we find a low mass major (minor) pair fraction of $0.041^{+0.003}_{-0.004}$ ($0.034\pm0.004$), and a high mass major (minor) pair fraction of $0.207^{+0.012}_{-0.014}$ ($0.152^{+0.016}_{-0.017}$).
-    These results are consistent with studies that find that the merger rate for high mass pairs is $\sim4\times$ higher than for low mass galaxies. 
+    These results are consistent with studies that find that the merger rate for high mass pairs is $\sim4\times$ higher than for low mass galaxies \citep[e.g.][]{RG2015}. 
+  % major vs. minor pairs 
     \item Low mass minor pairs evolve similarly to low mass major pairs as a function of redshift.
-    % GB edited
-    The redshift evolution of 
-    high mass minor pair fractions 
-    %have much 
-    is flatter %pair fractions 
-    at $z>1$ than for high mass major pairs, which are constant or decreasing with redshift.
-    \item The true pair fraction behavior of high and low mass pairs is recovered well using a subsample of pairs with a maximum separation cut of $r_{sep}<1\Rvir$, where $\Rvir$ is the 
-    virial radius of the FoF group (see Eqn). % GB: where teh virial radius can be estimated from the combined halo mass of the pair using SMHM relation. 
-    %radius of the group halo.
-    In particular, this separation cut selects between $\sim40-60\%$ of the full population of pairs at all redshifts, and recovers the differences in the redshift evolution of low mass vs.
+    % The redshift evolution of high mass minor pair fractions is flatter at $z>1$ than for high mass major pairs, which are constant or decreasing with redshift.
+  % virial radius results
+    \item The different redshift evolution of the pair fraction of high and low mass pairs is well recovered using a subsample of pairs with a maximum separation cut of $r_{sep}<1\Rvir$, where $\Rvir$ is the virial radius of the FoF group (see Eq.~\ref{eq}, where the virial radius can be estimated in observations from the combined halo mass of the pair using the SHMH relation).
+    This separation cut corresponds to separations less than [134(348), 59(134), 33(76)]$\kpc$ at z=[0,2,4] for low mass (high mass) pairs.
+    In particular, a maximum separation cut of $r_{sep}<1\Rvir$ encompasses between $\sim40-60\%$ of the full population of pairs at all redshifts, and recovers the distinct differences in the redshift evolution of low mass vs.
 high mass pair fractions from $z=0-2.5$.
-% GB: add here what Rvir corresponds to in kpc at specific redshift.
-    %the behavioral trend differences between low mass and high mass pairs from $z=0-2.5$ are distinct.
-    \item The pair fractions of high and low mass pairs are 
-    %somewhat i
-    indistinguishable when a static physical separation cut is employed; i.e.
-a separation that does not evolve with redshift (e.g.
-$r_{sep}<50\kpc$), and is identical for low mass and high mass pairs.
-% GB: explain why this happens - with a fixed separation you are capturing more of the low mass pair sample than the high mass pair sample  \\
-    \item  XXXX conclusion about local group analogs 
-    % \item In order to recover 
+  % physical separation results
+    \item The identified differences in the redshift evolution of high and low mass pairs are erased when a static physical separation cut is employed; i.e.
+a separation that does not evolve with redshift or with mass (e.g.
+$r_{sep}<50\kpc$).
+    This occurs because fixed separation cuts capture roughly 10-50\% more pairs in the low mass pair sample than the high mass sample at all redshifts.  
+    Consequently, selecting the same volume to study the pair fractions for low and high mass galaxies via a static separation cut will bias inferred pair fractions. 
+  % local group results
+    \item Isolated mass-analogs of the MW--M31 are most common at $z=0$, while analogs of the MW--LMC and M31--M33 are equally common at $z=0$ as at $z>1$. 
+    However, MW--LMC-type systems with very low separations ($\lesssim50\kpc$) are 2-3 times more common at higher $z\sim$2. 
+    Isolated analogs of the LMC--SMC and  NGC4490-4485 are 3 times more common for $z>3$. 
 \end{itemize}
-    This means you're recovering different fractions of each population and you aren't actually doing to recover. 
-Thus, in order for the true pair fraction behavior as a function of time to be quantified observationally, we argue that pair selection criteria must be a function of both mass and redshift. 
-Otherwise, selecting the same volume of two different mass scales will incorrectly bias inferred pair fractions, and wash out any differences between low and high mass pairs.
-% GB: connect the importance of recovering the differences between low and high mass pair fractions to efforts to translate pair fractions to merger rates using e.g.
-observability time scales that are fixed.
-Stress importance of avoiding static separation cuts in era of JWST where more low mass galaxies will be discovered.
 
-% GB i don't think you need much else beyond the above
+    A number of studies have identified a mass and redshift dependence in the galaxy merger rate as a function of time, particularly in cosmological simulations and semi-empirical models~\cite[see e.g.][]{Stewart2009,Hopkins2010,RG2015}.
+    Our results show that galaxy pair fractions for physically associated, isolated pairs, likewise evolve as a function of mass and redshift. 
+    However, we also find that the recovered pair fractions are sensitive to the separation criteria that is used to define pairs.
+    The redshift evolution of pair fractions for physically associated low mass and high mass galaxy pairs can only be distinguished when the separation criteria is a function of both mass and redshift.
 
-% Translating between pair fractions and merger rates for observationally defined samples requires an observability timescale. 
-Since the pair fraction behavior of low and high mass pairs is well recovered using only pairs with $r_{sep}<1.0\Rvir$, we expect that observations that use redshift and mass-dependent selection criteria for high and low mass pairs separately, will likely be able to dis
+    Many observational pair fraction studies use static definitions of the maximum projected separation to determine close pairs, then translate between pair fractions and merger rates via an observability timescale.
+    The observability timescale, however, is not typically calibrated as a function of both mass and redshift, meaning that identical measured pair fractions of high and low mass pairs will yield indistinguishable merger rates.
 
-% Our results are consistent with prior works that have studied the pair fractions of low mass, physical galaxy pairs in the Illustris simulations, as well as those that adopt projected separation and velocity criteria over a similar stellar mass range as ours.
-% The agreement between the pair fraction trends from these projected studies, which have found good agreement with observations, and from our physical pair fraction study   to TNG's robust ability to reproduce the frequency of galaxy pairs from observations.
+    In order to observationally recover the cosmologically expected difference between the merger rates of high and low mass galaxies, it is crucial to ensure that differences in the redshift evolution of the pair fraction for these galaxy populations can be adequately captured.
+    This will of particular importance in the era of JWST, where more low mass ($M_*\sim10^8 \Msun$) galaxies and galaxy pairs will be discovered at higher redshift (up to $z>10$). 
+    Thus, we argue that pair selection criteria must be a function of both mass and redshift, rather than selecting a universal, static pair separation criterion.
 
-% Talk about what we've missed and hinted at, and what our next project will kinda do to resolve this.
-
-Quantifying the observability timescale of low mass and high mass systems separately will be necessary to properly
-
-% \begin{itemize}
-    % \item Dwarf galaxy pairs and massive galaxy pairs likely have different evolutionary and merger processes which result in the opposing behavior of dwarf and massive pair fractions as a function of redshift.
-    % \item The separation criteria used to observationally identify pairs likely results in an incompleteness of at least XX\% by $z=0$, though is less problematic for high redshift pairs where pairs tend to have smaller separations.
-% \end{itemize}
-
-% Our conclusions point to the importance of time-evolving pair selection criteria that account for the natural separation increase of pairs at the universe expands.
-
+% fin
 %%%%%%%%%%%%%%%%%%%%%%%%

### 2023-09-22 paper/pears.tex
submitting to arxiv!

@@
 \usepackage{soul}
+\usepackage{hyperref}
 
@@
 % Affiliations
-\newcommand{\affuofa}{University of Arizona, 933 N. Cherry Ave,
-    Tucson, AZ 85721, USA}
+\newcommand{\affuofa}{University of Arizona, 933 N. Cherry Ave, Tucson, AZ 85721, USA}
+\newcommand{\affunam}{Instituto de Radioastronom\'ia y Astrof\'isica, Universidad Nacional Aut\'onoma de M\'exico, Apdo. Postal 72-3, 58089 Morelia, Mexico}
+\newcommand{\affuoff}{Department of Astronomy, University of Florida, P.O. Box 112055, Gainesville, FL 32611, USA}
+\newcommand{\affberk}{Department of Astronomy, University of California, Berkeley, 501 Campbell Hall, Berkeley, CA, 94720, USA}
+\newcommand{\affuofu}{Department of Physics and Astronomy, University of Utah, 115 South 1400 East, Salt Lake City, Utah 84112, USA}
+\newcommand{\affnyu}{The Center for Cosmology and Particle Physics, New York University, 726 Broadway, New York, NY 10003}
+\newcommand{\affnrao}{National Radio Astronomy Observatory, 520 Edgemont Road,
+Charlottesville, VA 22903, USA}
+\newcommand{\affuva}{Department of Astronomy, University of Virginia, 530 McCormick Road, Charlottesville, VA 22904, USA}
+\newcommand{\affempty}{Empty}
+\newcommand{\affnottingham}{School of Physics and Astronomy, University of Nottingham, University Park, Nottingham NG7 2RD, UK}
+\newcommand{\affkorea}{Korea Astronomy and Space Science Institute, 776 Daedeokdae-ro, Yuseong-gu, Daejeon 34055, Korea}
+\newcommand{\afftrent}{Department of Physics and Astronomy, Trent University, 1600 West Bank Drive, Peterborough, ON K9L 0G2, Canada}
+\newcommand{\affoccidental}{Occidental College, Physics Department, 1600 Campus Road, Los Angeles, CA 90041, USA}
 
-%% This is the end of the preamble.  Indicate the beginning of the
-%% manuscript itself with \begin{document}.
+%% This is the end of the preamble.
 
@@
   % low mass and high mass galaxy pairs evolve differently as a function of redshift
-  A new framework for recovering the mass and redshift dependence\\ of galaxy pair fractions across cosmic time }
+  A physically motivated framework for measuring\\ the mass and redshift dependence of galaxy pair fractions across cosmic time 
+  % A physically motivated framework for measuring galaxy pair fractions across cosmic time
+   % for measuring galaxy pair fractions across cosmic time
+   % measuring or recovering?
+  }
 % Differences in the redshift evolution of low mass and high mass galaxy pairs in the TNG100 cosmological simulation
@@
 \author[0000-0001-8765-8670]{Katie~Chamberlain}
-\affiliation{\affuofa}
+\thanks{E-mail: katiechambe@arizona.edu}\affiliation{\affuofa}
 
@@
 
-\author{others}
+\author[0000-0002-9820-1219]{Ekta~Patel}
+\thanks{Hubble Fellow}\affiliation{\affberk} \affiliation{\affuofu}
+
+\author[0000-0002-9495-0079]{Vicente Rodriguez-Gomez}
+\affiliation{\affunam}
+
+\author[0000-0002-5653-0786]{Paul Torrey}
+\affiliation{\affuoff}
+
+\author[0000-0003-2939-8668]{Garreth Martin}
+\affiliation{\affnottingham}\affiliation{\affkorea}\affiliation{\affuofa}
+
+\author[0000-0001-8348-2671]{Kelsey Johnson}
+\affiliation{\affuva}
+
+\author[0000-0002-1871-4154]{Dave Patton}
+\affiliation{\afftrent}
+
+\author[0000-0003-0256-5446]{Sarah Pearson}
+\thanks{Hubble Fellow}\affiliation{\affnyu}
+
+\author[0000-0003-3474-1125]{George Privon}
+\affiliation{\affnrao}\affiliation{\affuoff}\affiliation{\affuva}
+
+\author[0000-0002-2596-8531]{Sabrina Stierwalt}
+\affiliation{\affoccidental}
 
 \begin{abstract} 
-Low mass galaxy pair fractions are understudied across cosmic time. 
-In the era of JWST, a self-consistent framework is needed to select both low and high mass galaxy pairs in order to connect observed pair fractions to cosmological merger rates across all mass scales and redshifts.
-Here, we construct a sample of low mass ($\rm 10^8<M_*<5\times10^9\,\Msun$) and high mass ($\rm 5\times10^9<M_*<10^{11}\,\Msun$) subhalo pairs from the TNG100 simulation from $z=0-4.2$. 
-Pairs belong to the same FoF group, meaning they are isolated, physically associated, and not contaminated by projection effects. 
-Stellar masses are assigned using abundance matching. 
-We find that the low mass pair fraction increases from $z=0-2.5$, while the high mass pair fraction peaks at $z=0$ and is constant or slightly decreasing at $z>1$. 
-At z=0 the low mass major pair fraction is four times lower than that of high mass pairs, consistent with findings for cosmological merger rates. 
+Low mass galaxy pair fractions are under-studied across cosmic time. 
+In the era of JWST, Roman, and Rubin, a self-consistent framework is needed to select both low and high mass galaxy pairs to connect observed pair fractions to cosmological merger rates across all mass scales and redshifts.
+We use the Illustris TNG100 simulation to identify pairs between $z=0-4.2$ that are physically associated, free from contamination owing to projection effects.
+We construct a sample of low mass ($\rm 10^8<M_*<5\times10^9\,\Msun$) and high mass ($\rm 5\times10^9<M_*<10^{11}\,\Msun$) isolated subhalo pairs, using abundance matching to assign stellar masses. 
+The low mass pair fraction, i.e. the fraction of galaxies in pairs, increases from $z=0-2.5$, while the high mass pair fraction peaks at $z=0$ and is constant or slightly decreasing at $z>1$. 
+At $z=0$ the low mass major (1:4 mass ratio) pair fraction is 4$\times$ lower than that of high mass pairs, consistent with findings for cosmological merger rates. 
 Our results indicate that pair fractions can faithfully reproduce trends in merger rates if galaxy pairs are selected appropriately. 
 Specifically, static pair separation limits applied equivalently to all galaxy pairs do not recover the evolution of low and high mass pair fractions. 
-Instead, we advocate for separation limits that vary with the mass and redshift of the system, such as separation limits scaled by the estimated virial radius of the pair ($r_{sep}< 1 R_{vir}$). 
-Finally, we place isolated mass-analogs of Local Group galaxy pairs (MW--M31, MW--LMC, M31--M33, LMC--SMC) in a cosmological context, quantifying for the first time the frequency of finding isolated analogs of such pairs as a function of redshift.
+Instead, we advocate for separation limits that vary with the mass and redshift of the system, such as separation limits scaled by the virial radius of the host halo ($r_{\mathrm{sep}}< 1 R_{\rm vir}$).
+Finally, we place isolated mass-analogs of Local Group galaxy pairs (i.e., MW--M31, MW--LMC, LMC--SMC) in a cosmological context,
+
+%  changed by rec. of garreth
+and show that isolated analogs of LMC--SMC-mass pairs, as well as MW--LMC-mass pairs with low separation ($<50\kpc$), are $2-3\times$ more common at $z\gtrsim2-3$.
+%quantifying for the first time the frequency of finding isolated analogs of such pairs as a function of redshift.
 
@@
     Galaxy mergers have been studied in detail as a mechanism for driving galaxy evolution, and have been identified as a trigger of, for example, 
-    active galactic nuclei (AGN)~\citep[e.g.][]{Hopkins2008,Comerford2015,Blecha2018,Ellison2019}, 
-    star formation~\citep[e.g.][]{Mihos1996, DiMatteo2008,Patton2013, Hopkins2013,Patton2020,Hani2020}, 
-    and changes in morphology~\citep[e.g.][]{Conselice2003,Lotz2008,Casteels2014,RG2017,Guzman-Ortega2023}. 
+    active galactic nuclei (AGN)~\citep[e.g.][]{Hopkins2008,Treister2010,Ramos2011,Satyapal2014,Comerford2015,Glikman2015,Blecha2018,Ellison2019}, 
+    star formation~\citep[e.g.][]{Mihos1996, DiMatteo2008,Ellison2011,Patton2013, Hopkins2013,Martin2017,Patton2020,Hani2020,Martin2021}, 
+    and changes in morphology~\citep[e.g.][]{Conselice2003,Lotz2008,Casteels2014,Patton2016,Bignone2017,RG2017,Martin2018,Jackson2019,Snyder2019,Jackson2022,Guzman-Ortega2023}. 
     Constraining the merger rate for galaxies is critical for quantifying the importance of mergers for galaxy evolution and testing predictions for hierarchical assembly in cold dark matter theory \citep[e.g.][]{Stewart2009,Hopkins2010,RG2015}.
@@
     In practice, merger rates cannot be measured straightforwardly from observations and, rather, are calculated by converting the observed frequency of a galaxy merger signature (i.e., asymmetry, concentration, pair fraction, etc.) to a merger rate using an observability timescale~\citep[e.g.][]{Lotz2011}.
-    Low mass galaxies are most often morphologically disturbed by fly-bys and non-merger interactions~\citep{Martin2021}, and star forming galaxies at high redshift tend to be clumpy and asymmetric, even in isolation~\citep{Wuyts2013}, thus pair fractions offer the most robust method of observationally quantifying merger rates across cosmic time.
+However, morphological signatures of mergers are often caused by non-merger phenomena.
+    For example, low mass galaxies are more commonly morphologically disturbed by fly-bys and non-merger interactions than by mergers~\citep{Martin2021}, 
+    and star-forming galaxies at high redshift tend to be clumpy and asymmetric even in isolation~\citep{Wuyts2013}.
+    Additionally, detection of these signatures can be strongly dependent on image depth or galaxy stellar mass, and identifying tidal features that rely on human classifications may be unreliable~\citep{Martin2022}.
 
-    Pair fractions of high mass ($M_*\gtrsim10^{10}\Msun$) galaxies have been well studied across cosmic time both observationally~\citep[e.g.][]{Patton2000,Lotz2011,Ferreras2014, Man2016,Duncan2019}, and theoretically~\citep[e.g.][]{RG2015,Snyder2017,Snyder2023}, with theoretical studies typically done in projection for comparison to observational campaigns.
+    Pair fractions, on the other hand, can be calculated independently of morphological information, and thus offer a more robust method of observationally quantifying merger rates across cosmic time.
+    Pair fractions of high mass ($M_*\gtrsim10^{10}\Msun$) galaxies have been well studied across cosmic time both observationally~\citep[e.g.][]{Patton2002,Lin2004,Lin2008,Lotz2011,Ferreras2014, Man2016,Duncan2019}, and theoretically~\citep[e.g.][]{RG2015,Snyder2017,Snyder2023}, with theoretical studies typically done in projection for comparison to observational campaigns\footnote{The studies cited here have limits on the projected separation of their sample, such that the projected separations range between $5\,\kpc$ and $\sim140\,\kpc$.}.
     Low mass galaxy pairs ($10^8<M_*<5\times10^9\Msun$) have been studied at low redshift~\citep[e.g.][]{Stierwalt2015,Pearson2016,Besla2018,Paudel2018,Luber2022},
     but are less well understood across cosmic time owing to the difficulty in observing faint systems outside of the Local Volume. 
-    However, JWST will significantly revolutionize our ability to find such systems at higher redshift~\citep{Behroozi2020}.
+    However, JWST~\citep{Gardner2006}, as well as the next generation of deep and wide-field surveys from Rubin Observatory\footnote{ \href{https://rubinobservatory.org/}{https://rubinobservatory.org}}~\citep{RUBIN2019} and Roman Space Telescope\footnote{\href{https://roman.gsfc.nasa.gov/}{https://roman.gsfc.nasa.gov}}~\citep{Spergel2015}, will significantly revolutionize our ability to identify such systems at high redshift $(z\gtrsim10)$~\citep{Behroozi2020} and in abundance at lower redshift ($z\lesssim6$)~\citep{Robertson2019a,Robertson2019b-LSST}.
 
     There are reasons to believe that low mass and high mass pairs evolve differently as a function of time.
-    For example, semi-empirical and cosmological studies find that galaxy merger rates vary both with redshift and the mass of the most massive galaxy of the pair~\citep[see e.g.][]{Stewart2009,Hopkins2010,RG2015}.
+    For example, semi-empirical and cosmological studies find that galaxy merger rates vary both with redshift and the mass of the most massive galaxy of the pair~\citep[see e.g.][]{Guo2008,Stewart2009,Hopkins2010,RG2015,Martin2021}.
     % Such differences are likely to give rise to differences in the pair fractions of low and high mass pairs.
@@
 
-    In this study, we take the approach of self-consistently selecting physically associated pairs of low mass ($10^8<M_*<5\times10^9\Msun$) and high mass $(5\times10^9<M_*<10^{11}\,\Msun)$ galaxies. 
-    Specifically, we identify major ($1-1/4$) and minor $(1/10-1/4)$ pairs from $z=0-4.2$ in the IllustrisTNG cosmological simulation, TNG100. 
-    We require that pairs are part of the same FoF group and that no other more massive perturbers are nearby, which allows us to ensure that the recovered pair fractions are inherent to the population of selected pairs rather than a function of environment.
+    Typically, observational studies of pair fractions apply projected separation cuts that are constant over time and do not vary with the mass of the target system. 
+    To fairly test for differences in the evolutionary behavior of pair fractions, especially in observational studies, it is necessary to determine whether this is an appropriate technique for accurately recovering true pair fraction behavior.
+    In this study we identify how the application of a fixed separation criteria affects inferred pair fractions, and make recommendations for a time and mass evolving separation cut to permit equitable pair fraction comparisons between different mass regimes.
 
-    Typically, observational studies of pair fractions apply projected separation cuts that are constant over time and do not vary with the mass of the target system. 
-    To fairly test for differences in the evolutionary behavior of pair fractions, especially in observational studies, it is necessary to determine whether this is an appropriate technique for faithfully recovering true pair fraction behavior.
-    In this study we identify how the application of a fixed separation criteria affects inferred pair fractions, and make recommendations for a time and mass evolving separation cut to permit equitable pair fraction comparisons between different mass regimes.
+    In particular, we take the approach of consistently selecting physically associated pairs of low mass ($10^8<M_*<5\times10^9\Msun$) and high mass $(5\times10^9<M_*<10^{11}\,\Msun)$ galaxies. 
+    Specifically, we identify major ($1-1/4$) and minor $(1/10-1/4)$ stellar mass ratio pairs from $z=0-4.2$ in the IllustrisTNG cosmological simulation, TNG100. 
+    We require that pairs are part of the same Friends of Friends (FoF) group and that no other more massive perturbers are nearby, which allows us to ensure that the recovered pair fractions are inherent to the population of selected pairs rather than a function of environment.
 
@@
     In Section~\ref{sec:methods}, we outline our methodology for selecting physically associated high mass and low mass pairs from the TNG simulation. 
-    In Section~\ref{sec:pairprops}, we provide an overview of properties of the selected sample, including the number of primaries, pairs, and their stellar mass ratios as a function of time. 
-    We present the time evolving pair fraction of high mass and low mass pairs in Section~\ref{sec:results}, and show how they change for different separation criteria. 
+    In Section~\ref{sec:pairprops}, we provide an overview of the properties of the selected sample, including the number of primaries, pairs, and their stellar mass ratios as a function of time. 
+    We present the time-evolving pair fraction of high mass and low mass pairs in Section~\ref{sec:results}, and show how they change for different separation criteria. 
     In Section~\ref{sec:discussion}, we discuss the implications of the differences between low and high mass pair fractions for observational campaigns and give context to our results by drawing comparisons to Local Group pairs.
@@
 We aim to quantify and characterize the frequency, or pair fraction, of low mass ($\rm\ms{}=10^{8}-5\times 10^{9}\Msun$) and high mass ($\rm\ms{}=5\times10^{9}-10^{11}\Msun$) galaxy pairs in cosmological simulations as a function of cosmic time.
-To this end, we utilize the \tng\ simulation to select subhalo pairs as a function of redshift, according to the selection criteria outlined in the remainder of this section.
+To this end, we utilize the \tng\ suite of simulations to select subhalo pairs as a function of redshift, according to the selection criteria outlined in the remainder of this section.
 
@@
     The IllustrisTNG project~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} consists of a suite of dark-matter-only $N$-body and full physics cosmological simulations that adopt the \textit{Planck2015} \lcdm\  cosmology~\citep{Planck2015}.
-    % GB edited below 
-    In this study we utilize data from TNG100-1, the main high resolution, full physics simulation of a (110.7\Mpc)$^3$ volume (hereafter TNG100). 
+
+    In this study, we utilize data from TNG100-1, the main high resolution, full physics simulation of a $(110.7\,\Mpc)^3$ volume (hereafter TNG100)\footnote{We will also use data from TNG100-1-Dark, the main high resolution dark-matter-only run (hereafter TNG100-Dark), as presented in Sec.~\ref{sec:disc-dark}.}
     This simulation follows the evolution of baryons and $1820^3$ dark matter particles from $z=127$ to $z=0$.  
-    The volume of this simulation is sufficiently large, and resolution is sufficiently high, to conduct a simultaneous analysis of the statistics of both low mass and high mass galaxy pairs, as shown by studies of pair statistics in similarly sized volumes~\citep{Sales2013,Patel2017a-Orbits,Patel2017b-Masses,Besla2018}.
-% more?
+    The volume of this simulation is sufficiently large, and the resolution is sufficiently high, to conduct a simultaneous analysis of the statistics of both low mass and high mass galaxy pairs, as shown by studies of pair statistics in similarly sized volumes~\citep{Sales2013,Patel2017a-Orbits,Patel2017b-Masses,Besla2018}.
 
@@
     We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm~\citep{Springel2001,Dolag2009}. 
-    This catalog was created using the Friends-of-Friends (FoF) algorithm~\citep{Davis1985}, which links nearby particles to define large halos of associated particles, from which subhalos are identified as over-dense and gravitationally bound dark matter structures.
+    This catalog was created using the Friends-of-Friends (FoF) algorithm~\citep{Davis1985}, which links nearby dark matter particles to define large halos of associated particles, from which subhalos are identified as over-dense and gravitationally bound dark matter structures.
     In addition, we utilize the merger trees provided by the \texttt{SUBLINK} algorithm~\citep{RG2015}, which tracks subhalos between snapshots, enabling us to trace the mass evolution of our selected subhalos.
 
-    % Baryonic process are known to affect the structure and formation of dark matter halos of low mass ($M_*\lesssim 1\times10^9\Msun$) subhalos in simulations~\citep[see e.g.][and references therein]{Sales:2022}.
-    % Additionally, the shallow potential well of dwarf galaxies compared to their massive counterparts may lend themselves more easily to disruption from baryonic processes such as supernova feedback and reionization~\citep{}, resulting in fewer low mass halos ($\lesssim 5\times10^{10}$) in hydrodynamic simulations~\citep{vogelsberger14B}.
 % End sim details     %
@@
 
-    In this section, we outline the steps to create the \subcat, which we will utilize to assign stellar masses to each of the dark matter subhalos to create our low mass and high mass galaxy catalogs.
+    In this section, we outline the steps to create the \subcat, which we will utilize to assign stellar masses to each of the dark matter subhalos.
 
-    % GB edited 
-    We are interested in the inherent frequency of low and high mass galaxy pairs in the field, rather than in over dense environments. 
-    This will allow us to assess whether there are fundamental differences in the frequency of pairs as a function of mass scale that are independent of environmental factors. 
+    We are interested in the intrinsic frequency of low and high mass galaxy pairs in the field, rather than in over dense environments. 
+    This allows us to assess whether there are fundamental differences in the frequency of pairs as a function of mass scale that are independent of environmental factors\footnote{Note that our pair fraction calculations are thus specifically for isolated systems, and the global pair fraction (including both isolated and non-isolated pairs) will be different.}.
     As such, we must ensure that our target subhalos are sufficiently isolated.  
-    We do this by placing limits on the total mass of the FoF group to which our low mass or high mass samples belong.
+    We do this by placing limits on the virial mass of the FoF group to which our low mass or high mass samples belong.
 
-    The following selection process is repeated for each snapshot of the simulation over a redshift range of$z=0-\sim4$.  
-    We stop our analysis at $z=4.2$ since the population of massive subhalo pairs falls off rapidly at larger redshifts, where the sample size of high mass primaries falls well below 100 subhalos per realization.
+    The following selection process is repeated for each snapshot of the simulation over a redshift range of $z=0-4.2$.  
+    We stop our analysis at $z=4.2$ since the population of massive subhalo pairs falls off rapidly at larger redshifts, where the sample size of high mass primaries falls well below 100 subhalos per snapshot.
 
-    First, at each snapshot, we apply a cut on the total FoF group mass, \MG{}, given by \texttt{Group\_M\_TopHat200}\footnote{The mass \texttt{Group\_M\_TopHat200} is the total mass enclosed by a sphere with mean density $\Delta_c *\rho_c$, where $\Delta_c$ is the overdensity constant from~\citet{Brynorman1998} and $\rho_c$ is the critical density of the universe at the time calculated.} in the TNG100 group catalogs.
+    First, at each snapshot, we apply a cut on the FoF group virial mass, $M_{\rm vir}$, given by \texttt{Group\_M\_TopHat200}\footnote{The mass \texttt{Group\_M\_TopHat200} is the mass enclosed by a sphere with mean density $\Delta_c *\rho_c$, where $\Delta_c$ is the overdensity constant from~\citet{Brynorman1998} and $\rho_c$ is the critical density of the universe at the time calculated.
+The corresponding virial radius in TNG100 is given by \texttt{Group\_R\_TopHat200}.} in the TNG100 group catalogs.
     We define the group mass range for low mass and high mass groups as: 
@@
     The FoF group mass criteria is fixed for all redshifts, which means that some low mass groups at high $z$ may be the progenitors of high mass systems at $z=0$.
-    Note that all masses used in this analysis are physical units, meaning that masses from the group catalogs are divided by $h$ to get units of \Msun.
+    % Note that all masses used in this analysis are physical units, meaning that masses from the group catalogs are divided by $h$ to get units of \Msun.
 
-    By requiring that the total FoF group mass does not exceed the above limits, we ensure that there are no subhalos more massive than these limits that will perturb the dynamical state of identified pairs.
+    By requiring that the FoF group virial mass does not exceed the above limits, we ensure that there are no subhalos more massive than these limits that will perturb the dynamical state of identified pairs.
     For example, selecting low mass pairs from the low mass FoF groups ensures that the selected pairs are not satellite systems of high mass subhalos. 
-    We have confirmed that over 99\% of subhalos selected from FoF groups that obey the listed mass limits are isolated; meaning, they are not within $1.5\,\Mpc$ of perturbers more massive than the given FoF group.
+    We have confirmed that over 99\% of subhalos selected from FoF groups that obey the listed mass limits are isolated; meaning, they are not within $1.5\,\Mpc$ of perturbers more massive than the mass of the pair.
 
-    % GB removed
-  %  Selecting low mass pairs from the low group mass range ensures that we are not selecting satellite systems in the halos of more massive systems, nor low mass pairs in a large group. 
-  %  Additionally, $z\sim0$ groups of high mass will host isolated mass analogs of the MW--M31 and MW--LMC systems, while the low mass groups will host isolated mass analogs of an LMC--LMC or LMC--SMC pair.
-
-        % explain what halos we will move forward with. 
     From the set of FoF groups that pass the group mass cut, we create a catalog of all subhalos within each FoF group that pass a current ``minimum mass" threshold.  
-    We require that the subhalo mass (\Mhalo\footnote{Note that for the TNG100 hydro run, the subhalo mass is the total sum of all bound dark \textit{and} baryonic matter.}) at the given snapshot, defined by the \texttt{SubhaloMass} field in the group catalogs, is:
+    At the given snapshot, we require a minimum subhalo mass \Mhalo\ to be:
     \begin{equation*}
@@
     \end{equation*}
-    This ``minimum mass" threshold ensures that subhalos are resolved into $>100$ particles, and thus should be robustly identifiable using the \subfind\ and \sublink\ algorithms \citep{RG2015}.
+    \Mhalo\ is given by the \texttt{SubhaloMass} field in the group catalogs, and is the total combined mass of all bound dark \textit{and} baryonic matter.
+    This ``minimum mass" threshold ensures that subhalos are resolved into $>100$ dark matter particles, and thus should be robustly identifiable using the \subfind\ and \sublink\ algorithms~\citep{RG2015}.
 
-    % GB edited
     For each subhalo that passes both criteria, i.e.
@@
     All subhalos in a given snapshot that pass both the FoF group and ``minimum mass" selection criteria form our full sample of subhalos, which we call the \subcat. 
-    The catalog contains subhalos at each snapshot from $z=0-\sim4.2$ (snapshot numbers 20-99) and their associated properties, namely: Subhalo ID, FoF Group Number, current subhalo mass \Mhalo, and peak halo mass \Mpeak.
+    The catalog contains subhalos at each snapshot from $z=0-\sim4.2$ (snapshot numbers 20-99) and their associated properties, namely: Subhalo ID, FoF Group Number, current subhalo mass \Mhalo, and peak subhalo mass \Mpeak.
     At z=0, this selection process results in 44656 subhalos in low mass groups and 38350 subhalos in high mass groups.
 
-    From here, we will use further selection criteria to narrow down this large sample and to identify pairs of subhalos in each group.
+    From here, we will use additional selection criteria to identify pairs of subhalos in each group.
 % End choosing halos     %
@@
     This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large, between $\sim 0.3$ for $M_{h}\sim 10^{10}\Msun$ up to $\sim 1$dex for $M_{h}\sim10^{8}\Msun$~\citep{Munshi2021}.
-    While the SMHM function of \tng{} at $z=0$ closely reproduces the profile of the SMHM relation from various abundance matching and semi-empirical models~\citep{TNG5}, using stellar masses as calculated from abundance matching allows us to side step any simulation-dependent stellar mass effects.
+    While the SMHM function of \tng{} at $z=0$ closely reproduces the profile of the SMHM relation from various abundance matching and semi-empirical models~\citep{TNG5,Nelson2019}, using stellar masses as calculated from abundance matching allows us to avoid any simulation-dependent stellar mass effects.
     Finally, utilizing an abundance matching prescription enables direct comparisons of results between dark matter only and full hydrodynamics simulations, since the stellar masses are assigned in an identical way.
@@
     We use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic prescription to assign stellar masses to dark matter halos. 
-    The~\citet{Moster2013} relationship is a function of subhalo mass, redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.
+    The~\citet{Moster2013} relationship is a function of subhalo mass, redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with a larger scatter at lower halo masses.
 
     Because the abundance matching prescription is calibrated for centrals of FoF groups, we elect to use the maximum subhalo mass \Mpeak\ in the stellar mass calculation, rather than the subhalo mass at the given snapshot \citep[see][]{Besla2018}.
-    We also use the current redshift of the given snapshot, $z_{snap}$, of each subhalo in the stellar mass calculation. 
-    Thus, $\ms{}=f(\Mpeak,z_{snap})$.
+    We also use the current redshift of the given snapshot, $z_{\mathrm{snap}}$, of each subhalo in the stellar mass calculation. 
+    Thus, $\ms{}=f(\Mpeak,z_{\mathrm{snap}})$.
 
     Using \Mpeak\ mass allows us to remain robust to scenarios in which a secondary has formed most of its stars, then loses a significant portion of its dark matter content through tidal interactions with a primary, but retains the bulk of its stellar content.
-    In fact, \citet{Munshi2021} found that the stellar mass of subhalos at $z=0$ in the ``Marvel-ous Dwarfs" and ``DC Justice League" zoom simulations are more closely correlated with $M_{peak}$ than the $z=0$ halo mass for halos with peak halo mass $10^8<M_{\rm peak}<10^{11} \Msun$.
+    In fact, \citet{Munshi2021} found that the stellar mass of subhalos at $z=0$ in the ``Marvel-ous Dwarfs" and ``DC Justice League" zoom simulations are more closely correlated with $M_{\mathrm{peak}}$ than the $z=0$ halo mass for halos with peak halo mass $10^8<M_{\rm peak}<10^{11} \Msun$.
 
-    Using $z_{snap}$ means that we allow the stellar mass of both the primary and secondary halo to change as a function of redshift, even after the secondary has entered the primary's halo. 
-    This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{Geha2013}, which found that dwarfs $>1.5\Mpc$ from a MW-type galaxy are often star forming and rarely quenched.
+    Using $z_{\mathrm{snap}}$ means that we account for changes in the stellar mass of both the primary and secondary halo, even after the secondary has entered the primary's halo. 
+    This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{Geha2013}, which found that dwarfs $>1.5\,\Mpc$ from a MW-type galaxy are often star forming and rarely quenched.
     Additionally, the SAGA survey has found that large satellites of MW-type galaxies are often very blue, with infall into the halo spurring high rates of star formation due to the large gas fraction in dwarfs~\citep{Mao2021}.
 
-    We then calculate the stellar mass for a given subhalo by gaussian sampling each of the fitting parameters of the analytic framework from~\cite{Moster2013}, in order to account for the spread in the SMHM relationship.
-    We generate a single stellar mass ``realization" of the full \subcat\ by calculating a stellar mass for each subhalo, using an independent draw the SMHM distribution for each subhalo. 
+    We then calculate the stellar mass for a given subhalo by Gaussian sampling each of the fitting parameters of the analytic framework from~\cite{Moster2013}, in order to account for the spread in the SMHM relationship.
+    We generate a single stellar mass ``realization" of the full \subcat\ by calculating a stellar mass for each subhalo, using an independent draw from the SMHM distribution for each subhalo. 
     For each snapshot, we repeat this process 1000 times to generate 1000 realizations of stellar masses for the \subcat.
@@
     Each realization is treated as an independent sample of galaxy stellar masses, which will allow us to report realistic spreads of pair properties.
+In addition, our pair stellar mass selection criteria will result in different collections of subhalos being selected in each realization, since the stellar masses van
 
@@
 
-    % justify why we want to use stellar mass to define things
-    %A majority of the literature uses the definition of "major" and "minor" pairs based on the stellar mass of the objects.
-This is true as well for observational pair samples, such as Lotz 2011, wherein the halo mass of the objects is unknown, and thus the stellar mass is used to define the mass ratio of the pair.
-In order to reproduce statistics that can be meaningfully compared to observations/can be used to inform observations, we opt to define our pair sample via the stellar masses from the abundance matching prescription given in Sec.~\ref{sec:methods-am}.
-
-    %%% 
-    % begin subsubsection
     \subsubsection{Selecting primaries}
@@
 
-        % The median number of primaries in a single stellar mass realization at $z=0$ is XX dwarf primaries and XX massive primaries (see Sec.~\ref{sec:pairprops} for more info). 
         Since our selection is based on stellar mass, and there is a large spread in the SMHM relation, a primary subhalo may not be the most massive subhalo in terms of total subhalo mass.
 
-    % end  primary subsubsection
-    %%%
-
-    %%% 
-    % begin secondary subsubsection
     \subsubsection{Selecting secondary companions}
@@
         which are typically defined to have stellar mass ratios $M_{*2}/M_{*1} > 1/10$~\citep[i.e.][]{Lotz2011, RG2015, Snyder2017, Duncan2019, Wang2020, Guzman-Ortega2023}.
-        % where minor pairs are typically defined as having mass ratios between $1/4 > M_{*2}/M_{*1} > 1/10$ \citep{Lotz2011, RG2015, Guzman-Ortega2023}.
-        Our subhalo ``minimum mass" threshold of $\Mhalo=10^9$ (described in Sec.~\ref{sec:methods-halos}) corresponds to a mean stellar mass of $10^6\Msun$ at $z=0$. 
-        This stellar mass is well below the 1/10 criteria for the lowest stellar mass primary considered ($M_{*1} > 10^8 \Msun$), ensuring that our pair sample will be complete even at the lowest stellar masses considered.
+
+        Our subhalo ``minimum mass" threshold of $\Mhalo=10^9\, \Msun$ (described in Sec.~\ref{sec:methods-halos}) corresponds to a mean stellar mass of approximately $10^6\,\Msun$ at $z=0$. 
+        This stellar mass is well below the 1/10 criteria for the lowest stellar mass primary considered ($M_{*1} > 10^8 \, \Msun$), ensuring that our pair sample will be complete even at the lowest stellar masses considered.
 
     \subsubsection{Creating the pair catalog}
-        Pairs consist of a single primary and secondary in a FoF group as defined via the criteria above. 
+        Pairs consist of a single primary and secondary in a FoF group as defined via the criteria above, such that only one pair is identified in a single FoF group. 
         Each pair is categorized as either a major or minor pair based on the stellar mass ratio between the primary and secondary. Following, e.g. \cite{Lotz2011, RG2015}, 
@@
 
-    % Katie add citation 
-        For each pair, we calculate the physical separation (\kpc, not comoving \kpc) between the two subhalos using the \texttt{SubhaloPos} field from the group catalogs.
-We require that each pair have a minimum separation of $10 \kpc$ between primary and secondary to limit the impact of very close subhalos becoming indistinguishable in \subfind~\citep{RG2017}.
+        For each pair, we calculate the physical separation (proper \kpc, not comoving \kpc) between the two subhalos using the \texttt{SubhaloPos} field from the subhalo catalogs.
+We require that each pair have a minimum separation of $10 \, \kpc$ between primary and secondary to limit the impact of very close subhalos becoming indistinguishable in \subfind as a result of the resolution limit due to the softening length.
         % The minimum separation cut is more than 10 times the smoothing length of the simulation at $z=0$, which ensures that  can identify the subhalos as distinct objects XXXXX ADD CITATION HERE - vicente?
@@
         If a primary subhalo does not have a companion that meets the stellar mass ratio criteria and separation criteria, the subhalo will still be considered a primary. 
-        We refer to all primaries without companions as ``isolated primaries."
-        The total number of primaries includes both isolated primaries and those with companions, and is larger than or equal to the total number of pairs.
+        We refer to all primaries that do not have a companion that passes these criteria as ``isolated primaries," including primaries that may have a companion that meets the stellar mass ratio criteria but has a separation $<10\,\kpc$.
+        The total number of primaries includes both isolated primaries and those with selected companions and is larger than the total number of pairs.
 
         For each snapshot and each of the 1000 realizations of the stellar mass in \starcat, we identify a set of isolated primaries and pairs. 
-        The final \paircat\ is the collection of all isolated primaries and pairs at each snapshot, and includes the following information. 
+        Additionally, within each realization, no single subhalo can be a part of two separate pairs, such that the primary and secondary of every pair are unique to the pair.
+        The final \paircat\ is the collection of all isolated primaries and pairs at each snapshot and includes the following information. 
         For each isolated primary, we store the current subhalo mass (\Mhalo) and stellar mass from the given realization. 
-        For each pair, we store the primary and secondary subhalo masses (\Mhalo) and stellar masses, the pair separation, and the virial radius of the FoF group (given by the \texttt{Group\_R\_TopHat200} field in the group catalogs\footnote{The radius of the sphere which encloses the virial mass \texttt{Group\_M\_TopHat200}.
-See Sec.~\ref{sec:methods} for details.}).
-
-% Pair selection end %
-%%%%%%%%%%%%%%%%%%%%%%
-
-% Methods end %
-%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%
+        For each pair, we store the primary and secondary subhalo masses (\Mhalo) and stellar masses, the pair separation, and the virial radius of the FoF group (see Sec.~\ref{sec:methods} for virial definitions).
 
@@
     The low mass total pair fraction is approximately flat between $z=2.5-4$, and decreases from $z=2.5$ to $z=0$. 
-    The high mass total pair fraction is flat or decreasing from $z=1$ to $z=4$, but spikes sharply between $z=0-0.25$.}
+    The high mass total pair fraction is flat or decreasing from $z=1$ to $z=4$, but peaks sharply between $z=0-0.25$.}
     \label{fig:counts}
@@
 \section{Sample: Overview of pair properties} \label{sec:pairprops}
-    Utilizing the \paircat, for each snapshot, we compute the total number of primaries (isolated and paired) and pairs (both major and minor) in each of the 1000 realizations.
-We then compute the median and 1 and 99 percentile spread on the median over all realizations.
-    Additionally, we compute the low and high mass total pair fraction (the total number of major and minor pairs, $\rm N_{pair}$, divided by the total number of primaries $\rm N_{prim}$) for each individual realization.
+    Utilizing the \paircat, for each snapshot, we compute the total number of primaries (isolated and paired) and pairs (including major and minor) in each of the 1000 realizations.
+We then compute the median and 1st and 99th percentile spread on the median over all realizations\footnote{The spread on the median of each realization is very small.
+Thus, we opt to show the 1st and 99th percentile spread rather than those which align with traditional definitions of 1$\sigma$ or 2$\sigma$ measurements}.
+    Additionally, we compute the low and high mass total pair fraction for each individual realization, defined here as the ratio of the total number of pairs ($N_{\mathrm{pairs}}$) to the total number of isolated \textit{and} paired primaries ($N_{\mathrm{primaries}}$):
+    $$f_{p}=\rm \frac{N_{\mathrm{pairs}}}{N_{\mathrm{primaries}}}.$$
     We again compute the median and spread over all 1000 realizations.
@@
     The number of identified primaries is lowest at $z=4$, and rises to a maximum around $z=1$ for both low and high mass primaries.
-    The median count of low mass primaries (green solid line in top left panel) reaches a maximum of $15545^{+89}_{-88}$ halos at $z\sim0.6$, then decreases by $\sim22\%$ to $12002^{+85}_{-86}$ halos at $z=0$.
+    The median count of low mass primaries (green solid line in top left panel) reaches a maximum of $15,545^{+89}_{-88}$ halos at $z\sim0.6$, then decreases by $\sim22\%$ to $12,002^{+85}_{-86}$ halos at $z=0$.
     The count of high mass primaries (pink solid line in top right panel) reaches a maximum of $1901^{+16}_{-19}$ at $z=0.5$, and slightly declines to $z=0$. 
+    Our sample of high mass primaries represents approximately 20\% of all subhalos in TNG100 with the same range of stellar masses at $z=0$.
     There are roughly 8 times as many low mass primaries as high mass primaries.
@@
 
-    % Katie to fix XXXX
     The bottom panel of Fig.~\ref{fig:counts} shows the total pair fraction for low mass and high mass pairs, or equivalently, the fraction of primaries with a major or minor companion.
@@
 
-In the following analysis we will treat each stellar mass realization in the \paircat\ as an independent sample. 
-At each snapshot, we create a set ``S" of 1000 median pair fractions, which are computed utilizing each of the 1000 realizations of the target pair sample, independently.
-We then calculate the median of the set ``S" (the median of medians) and the percentile spread. 
-It is this median that is shown in each of the following plots as the solid or dashed line, and the shaded regions correspond to the spread.
+In the following analysis, we will treat each stellar mass realization in the \paircat\ as an independent sample. 
+At each snapshot, we calculate the median and 1st and 99th percentile spread on the median of the pair fractions in each of the 1000 realizations of the target pair sample.
+Each of the following figures shows the median as the solid or dashed lines, and the shaded regions correspond to the spread on the median.
 
@@
     \subsection{Major and minor pair fractions}\label{sec:results-frac}
-    The pair fraction is defined here as the ratio of the number of pairs ($N_{pairs}$) to the total number of isolated \textit{and} paired primaries ($N_{primaries}$):
-    $$f_{p}=\rm \frac{N_{pairs}}{N_{primaries}}.$$
+    The major and minor pair fractions are computed in the way as defined in Sec.~\ref{sec:pairprops} Eq.~\ref{eq}, where $N_{\rm pairs}$ is the total number of major \textit{or} minor pairs in the sample.
     For example, the low mass major pair fraction is the number of low mass major pairs divided by the number of low mass primaries, which can also interpreted as the likelihood of finding a major companion of an isolated low mass primary.
@@
 
-        % differences between massive and dwarf pairs? 
     The low mass pair fraction evolves distinctly from that of high mass pairs.
-    Low mass pair fraction for both major and minor pairs (green) are approximately constant from $z=3-4$, then decline monotonically to $z=0$.
+    Low mass pair fractions for both major and minor pairs (green) are approximately constant from $z=3-4$, then decline monotonically to $z=0$.
 At $z=0$, the major pair fraction is $0.041^{+0.003}_{-0.004}$, while the minor pair fraction is $0.034\pm0.004$.
@@
 
-        % difference panels
     The bottom panels of Fig.~\ref{fig:pairfrac} shows the low mass pair fraction subtracted from the high mass pair fraction (labeled ``$\rm High-Low$").
@@
 
-        % takeaways 
     Overall, these results show that low mass and high mass pair counts evolve differently over time, particularly at very low redshift, despite the pair fractions being roughly equal at higher redshift.
-    The implications for the difference in the evolution of pair fractions for low mass and high mass pairs across time is discussed in detail in Sec.~\ref{sec:disc-obs}.
+    The implications for the difference in the evolution of pair fractions for low mass and high mass pairs across time are discussed in detail in Sec.~\ref{sec:disc-obs}.
 
@@
 \subsection{Major pair fractions as a function of separation}\label{sec:results-frac-cuts}
-    In this section we analyze subsets of the low and high mass major pairs from the previous section that pass additional separation criteria. 
+    In this section, we analyze subsets of the low and high mass major pairs from the previous section that pass additional separation criteria. 
     We study two different sets of separation criteria to compare the resulting pair fractions to the full sample shown in Fig.~\ref{fig:pairfrac}.
-    In  Sec.~\ref{sec:results-frac-vircut} we apply a separation criteria that requires secondaries to be within a given factor of the virial radius of the FoF group, which is a reasonable proxy for the virial radius of the primary.
+    In  Sec.~\ref{sec:results-frac-vircut} we apply a separation criterion that requires secondaries to be within a given factor of the virial radius of the FoF group, which is a reasonable proxy for the virial radius of the primary.
     In Sec.~\ref{sec:results-frac-sepcut}, we use a range of limits on the 3D pair separation, where limits are consistent with values adopted in the literature.
@@
     Major pairs typically correspond to the two most massive subhalos in their FoF group. 
-    The virial mass of their FoF group is reasonably approximated by the combined subhalo mass of both pairs.
-    The combined mass of major low mass galaxy pairs recovers 98\% of the FoF group mass and the combined mass of major high mass galaxy pairs recovers 93\%. 
-    For example, the total mass of the Local Group is dominated by that of the MW and M31 \citep[e.g., ][]{Chamberlain2023}. 
+    The virial mass of their FoF group is reasonably approximated by the combined subhalo mass of both galaxies in the pair.
+    The combined mass of major low mass galaxy pairs recovers on average 98\% of the FoF group mass, and the combined mass of major high mass galaxy pairs recovers an average of 93\%. 
+    For example, the mass of the Local Group is dominated by that of the MW and M31 \citep[e.g., ][]{Chamberlain2023}. 
     The virial radius of the FoF group is thus reasonably approximated by the virial radius of a halo with a virial mass equal to the combined subhalo mass of the two major pair members.
@@
 
-    By basing our separation criteria on the FoF group virial radius, the separation cut will vary both as a function of redshift and as a function of the combined mass of the pair.
+    By focusing our separation criteria on the FoF group virial radius, the separation cut will vary both as a function of redshift and as a function of the combined mass of the pair consistently.
     For the high mass FoF groups, the median virial radius at $z=[0,1,2,3,4]$ is $\sim(348, 206, 134, 97, 76)\kpc$. 
@@
     All subsamples of high mass pairs display broadly the same pair fraction redshift evolution as the full high mass sample (pink line in left panel of Figure~\ref{fig:pairfrac}): each of the subsampled high mass pair fractions peak at $z=0$ and remain roughly constant or decrease at higher redshift.
-    The finer detail trends from the full sample, particularly the upturn at low z, are reasonably captured if $r_{sep} < 0.5 \Rvir$, despite the recovery being $\sim$40\%. 
-    % The magnitude of the pair fraction as a function of redshift for the full sample is best captured if $r_{sep} < 2.0\Rvir$.
+    The finer detail trends from the full sample, particularly the upturn at low z, are reasonably captured if $r_{\mathrm{sep}} < 0.5 \Rvir$, despite the recovery being $\sim$40\%. 
+    % The magnitude of the pair fraction as a function of redshift for the full sample is best captured if $r_{\mathrm{sep}} < 2.0\Rvir$.
 
     The subsamples of low mass pairs, however, show a different trend from the full sample (green line in left panel of Figure~\ref{fig:pairfrac}) if the separation cut is too small. 
-    For $r_{sep} < 0.25\Rvir$, the pair fraction is flat or decreasing as a function of redshift (especially for $z>1$), similar to the behavior for high mass pairs. 
-    For $r_{sep} < 0.5\Rvir$ and $r_{sep} < 1.0\Rvir$, the pair fraction rises to a peak at $z\sim2$ and then decreases. 
+    For $r_{\mathrm{sep}} < 0.25\Rvir$, the pair fraction is flat or decreasing as a function of redshift (especially for $z>1$), similar to the behavior for high mass pairs. 
+    For $r_{\mathrm{sep}} < 0.5\Rvir$ and $r_{\mathrm{sep}} < 1.0\Rvir$, the pair fraction rises to a peak at $z\sim2$ and then decreases. 
     %edited 
-    When the separation is limited to $r_{sep} < 1.5\Rvir$, the trends with redshift for the full low mass sample are recovered, particularly the roughly flat behavior from $z\sim2-4$, despite a sample recovery of $<75\%$.
-    % The magnitude of the full low mass pair fraction is recovered for $r_{sep} < 2.0$\Rvir. 
-    We also find that differences between the redshift evolution of high mass pairs vs. low mass pairs (particularly at $z<2$) become apparent if $r_{sep} < 0.5\Rvir$ for both galaxy types. 
+    When the separation is limited to $r_{\mathrm{sep}} < 1.5\Rvir$, the trends with redshift for the full low mass sample are recovered, particularly the roughly flat behavior from $z\sim2-4$, despite a sample recovery of $<75\%$.
+    % The magnitude of the full low mass pair fraction is recovered for $r_{\mathrm{sep}} < 2.0$\Rvir. 
+    We also find that differences between the redshift evolution of high mass pairs vs. low mass pairs (particularly at $z<2$) become apparent if $r_{\mathrm{sep}} < 0.5\Rvir$ for both galaxy types. 
     Overall we find that recovering the redshift evolution of the pair fractions of all galaxy pairs requires a separation cut such that the number of close pairs constitutes $\sim40-50\%$ or more of the full sample at all redshifts.
@@
         Such a separation criteria will vary as a function of both the mass of the pair and the redshift. 
-        Recovering the redshift evolution seen for the total sample (left panel of Figure~\ref{fig:pairfrac}) requires separation cuts of $r_{sep} < 1.5\Rvir$ for low mass pairs and $r_{sep} < 0.5\Rvir$ for high mass pairs.
-        Recovering the differences between high and low mass pair fraction trends seen for the total sample at $z>2$, requires $r_{sep} < 0.5\Rvir$ for both galaxy types. 
+        Recovering the redshift evolution seen for the total sample (left panel of Figure~\ref{fig:pairfrac}) requires separation cuts of $r_{\mathrm{sep}} < 1.5\Rvir$ for low mass pairs and $r_{\mathrm{sep}} < 0.5\Rvir$ for high mass pairs.
+        Recovering the differences between high and low mass pair fraction trends seen for the total sample at $z>2$, requires $r_{\mathrm{sep}} < 0.5\Rvir$ for both galaxy types. 
         (Bottom) The recovery fraction, calculated as the fraction of the total collection of pairs recovered by the subset of pairs at the given separation cut. 
@@
 
-    The low mass major pair fraction (green) maintains roughly the same behavior (decreasing with decreasing redshift) for each separation cut, and first recovers the redshift evolution and magnitude of the pair fraction of the full sample (left panel of Fig.~\ref{fig:pairfrac}) for a separation cut of $r_{sep} < 150\kpc$.
+    The low mass major pair fraction (green) maintains roughly the same behavior (decreasing with decreasing redshift) for each separation cut, and first recovers the redshift evolution and magnitude of the pair fraction of the full sample (left panel of Fig.~\ref{fig:pairfrac}) for a separation cut of $r_{\mathrm{sep}} < 150\kpc$.
     This is not surprising based on our results from the previous section as this separation is larger than the median virial radius of the sample and the recovery fraction is larger than 0.50 at all redshifts (reaching nearly 100\% at $z\sim3$).
@@
     At higher redshifts, the median pair fraction increases rather than leveling off or decreasing as in the full sample.
-    Even for $r_{sep}<300\kpc$, the high mass pair fraction peaks at $z=4$, at odds with results using the full pair sample or any of the virial radius cuts in the previous section.
+    Even for $r_{\mathrm{sep}}<300\kpc$, the high mass pair fraction peaks at $z=4$, at odds with results using the full pair sample or any of the virial radius cuts in the previous section.
 
@@
     This is in stark contrast to results from the previous section where the recovery fraction was roughly constant as a function of redshift.
-    Because the same separation cut is applied to low and high mass pairs, the recovery fraction for low mass pairs is universally higher than for high mass pairs at each separation cut, which wipes out any redshift evolution differences between the two galaxy types.
+    Because the same separation cut is applied to low and high mass pairs, the recovery fraction for low mass pairs is universally higher than for high mass pairs at each separation cut, which erases any differences in redshift evolution between the two galaxy types.
 
@@
         The 3D separation cut does not vary as a function of redshift or mass of the system. 
-        The general redshift evolution of the full high mass pair sample (decreasing with redshift for $z>1$) is not recovered for any physical separation cut, while the behavior of low mass pair fractions are well recovered by the $r_{sep}<150\kpc$ subsample.
+        The general redshift evolution of the full high mass pair sample (decreasing with redshift for $z>1$) is not recovered for any physical separation cut, while the behavior of low mass pair fractions are well recovered by the $r_{\mathrm{sep}}<150\kpc$ subsample.
         The pair fractions for low mass and high mass pairs are virtually indistinguishable for separation cuts less than $70\kpc$. 
@@
         A higher fraction of low mass pairs are recovered than high mass pairs at all separation cuts. 
-        Less than 50\% of all high mass pairs have separations $r_{sep}<70\kpc$ at all redshifts, and $>50\%$ of the full high mass sample is recovered at all redshifts only for $r_{sep}<300\kpc$. 
-        Between 20-60\% of low mass pairs have separations $r_{sep}<50\kpc$ at all redshifts, while a separation cut of $r_{sep}<150\kpc$ captures roughly 50-100\% of the low mass pair population at all redshifts.
+        Less than 50\% of all high mass pairs have separations $r_{\mathrm{sep}}<70\kpc$ at all redshifts, and $>50\%$ of the full high mass sample is recovered at all redshifts only for $r_{\mathrm{sep}}<300\kpc$.
+        Between 20-60\% of low mass pairs have separations $r_{\mathrm{sep}}<50\kpc$ at all redshifts, while a separation cut of $r_{\mathrm{sep}}<150\kpc$ captures roughly 50-100\% of the low mass pair population at all redshifts.
         }
@@
     High mass pair fractions likewise decrease with higher redshift for $z>1$, and peak at $z=0$.
-    The numerical value of the pair fraction at all redshifts is $\sim10\%$ larger in TNG100-Dark for both low and high mass pairs, and for major and minor pairs.
+    The numerical value of the pair fraction at all redshifts is $\sim10\%$ larger in TNG100-Dark for both low and high mass pairs, and for major and minor pairs, which is likely a result of the suppressed abundance of low mass halos due to baryonic physics~\citep{chua17}.
 
@@
 In Sec.~\ref{sec:disc-comp}, we compare our results to previous studies of pair fractions that utilize simulations. 
-Finally, we discuss the implications of the pair fraction behavior of low mass pairs and high mass pairs as a function of redshift for observations and how we might be able to detect these differences in Sec.~\ref{sec:disc-obs}.
+Finally, we discuss the implications of the pair fraction behavior of low mass pairs and high mass pairs as a function of redshift for observations and our suggestions for appropriate separation cuts in observational pairs in Sec.~\ref{sec:disc-obs}.
 
    \subsection{Implications for Local Group Galaxies}\label{sec:disc-LG}
-% providing context from well studied galaxies 
     Our study encompasses the stellar mass range and stellar mass ratios of a few well studied pairs within the Local Group and Local Volume.
-    Thus, we can make predictions for the frequency of finding isolated mass analogs of these systems at higher $z$. 
+    Thus, we can make predictions for the frequency of finding isolated mass analogs of these systems at $z>0$ for the first time. 
     For example, isolated mass analogs of the following pairs are included in each specified sample:
@@
 
-    We find that isolated mass analogs of the LMC--SMC and NGC4490-4485 are roughly three times as common at $z>3$ (green dotted line in the right panel of Fig.~\ref{fig:pairfrac}). 
+    We find that isolated mass analogs of the LMC--SMC and NGC4490-4485 are roughly three times as common at $z>3$ than at $z=0$ (green dotted line in the right panel of Fig.~\ref{fig:pairfrac}). 
     These high $z$ pairs may enter a more massive group halo to become satellites of a larger galaxy~\citep[like the LMC--SMC, ][]{Besla2007,Patel2017a-Orbits}, or if they remain isolated, may continue to merge in a manner similar to NGC4490-4485~\citep{Pearson2018}.
@@
 
-        We find reasonable agreement with the sample of physical pairs in \cite{Besla2018}, which found a major pair fraction between 0.003-0.018 over a mass range of $2\times 10^8 < M_* < 5 \times 10^9$ $M\odot$.
+        We find reasonable agreement with the sample of physical pairs in \cite{Besla2018}, which found a major pair fraction between 0.003-0.018 over a mass range of $2\times 10^8 < M_* < 5 \times 10^9$ $M_\odot$.
         % used fig. 15 for these vals.
-        Our roughly equivalent low mass major pair sample, when adopting a separation cut of $r_{sep}<150\kpc$, results in a major pair fraction of $0.022^{+0.002}_{-0.003}$ at $z=0$.
-We expect our results to be somewhat higher than in \cite{Besla2018} as our stellar mass range for primaries extends to a lower value of $10^8\Msun$.
-As such, we are confident that our results for low mass pairs are reasonable.
+        Our roughly equivalent low mass major pair sample, when adopting a separation cut of $r_{\mathrm{sep}}<150\kpc$, results in a major pair fraction of $0.022^{+0.002}_{-0.003}$ at $z=0$.
+We believe our pair fractions are somewhat higher than in \cite{Besla2018} as our stellar mass range for primaries extends to a lower value of $10^8\Msun$.
+As such,  our results for low mass pairs are robust.
 
@@
 
-        While we cannot directly compare the values of the pair fractions themselves, since the Snyder et al. work is done in projected space, we can compare the trends as a function of redshift. 
-        Our study finds that the high mass major pair sample has a pair fraction that decreases with redshift above $z=1$, which is in agreement with \cite{Snyder2023}.
+        We cannot directly compare the values of the pair fractions in this work and \citet{Snyder2023}, since their work is done in projected space, but we can compare the trends as a function of redshift.
+        We find that the high mass major pair sample has a pair fraction that decreases with redshift above $z=1$, in agreement with \cite{Snyder2023}.
 
-    % merger rates
-        In addition, \cite{RG2015} examine the merger rates of galaxies in the Illustris-1 simulation at $z=0$. 
-        From their Figure~10, there is roughly a factor of 4 difference in the major merger rate for high mass ($M_* \sim 10^{11} \Msun$) vs. low mass ($M_* \sim 10^8 \Msun$) galaxies. 
+        In addition, \cite{RG2015} examine the merger rates of galaxies in the Illustris simulations as a function of stellar mass and redshift.
+        From their Figures~7 and 10, there is roughly a factor of 4 difference in the major merger rate for high mass ($M_* \sim 10^{11} \Msun$) vs.
+low mass ($M_* \sim 10^8 \Msun$) galaxies at $z=0$, and the difference becomes smaller at higher redshift.
         % 1e8 -- 0.005-0.001 -- 5e9
         % 5e9 -- 0.001 - 0.02 -- 1e11
-        This is also seen in figure 12 of \cite{Guzman-Ortega2023}, who conducted a similar study of galaxy merger rates in the TNG50 simulation. 
-        These studies conclude that the galaxy merger rate has a strong dependence on the mass of the primary galaxy. 
-        Semi-empirical studies also find similar results \citep{Stewart2009, Hopkins2010}. 
-        From our Figure~\ref{fig:pairfrac}, at $z=0$, there is also a factor of 4 difference in the pair fraction for high and low mass galaxies. 
-        The good agreement between our results at $z=0$ and the merger rate calculations suggests that our finding of different pair fractions between low and high mass galaxies is reliable.
-
-            % THis puts more faith into pair fractions as being tracer -- conversion to merger rates would be more straightforward if use cut that scales with 
-            % If pair fraction separation is FIXED then the difference washes out - which is inconsistent with teh merger rate results from massive galaxies.  (the translation to major merger rates )
+        A strong mass dependence of the galaxy merger rate at $z=0$ is also seen in Figure~12 of \cite{Guzman-Ortega2023}, as well as in results from semi-empirical models \citep{Stewart2009, Hopkins2010}.
+        From our Figure~\ref{fig:pairfrac}, there is also a factor of 4 difference in the pair fraction for high and low mass galaxies at $z=0$, which becomes smaller at higher redshift.
+        The consistency between our results and the variation with stellar mass and redshift of the galaxy merger rate suggests that our finding of different pair fractions between low and high mass galaxies at $z=0$, as well as their different redshift evolution trends, is indeed reliable.
 
@@
 
-    In Sec.~\ref{sec:results-frac}, we presented the pair fraction of high mass and low mass galaxy pairs and found that the relative frequency of the two populations evolve distinctly from $z=0-4.2$.
+    In Sec.~\ref{sec:results-frac}, we presented the pair fraction of high mass and low mass galaxy pairs and found that the relative frequency of the two populations evolves distinctly from $z=0-4.2$.
     High mass pair fractions peak at $z=0$, decrease from $z=0-0.3$, after which they are roughly constant or mildly decreasing with increasing redshift. 
@@
 
-% Making separation cuts based on physical separations is not the right way to go, and instead we need something that evolves as a function of mass and redshift. 
-    In the previous section we also found that our finding of different pair fractions for high and low mass galaxies are consistent with expectations of a mass dependence in the galaxy merger rate~\citep{RG2015, Guzman-Ortega2023}.
-
     In Sec.~\ref{sec:results-frac-cuts}, we characterized the behavior of pair fractions for subsamples of the full pair catalog that pass additional separation cuts.
-    We found that physical separation cuts that do not vary as a function of time and mass eliminate the ability to distinguish the different redshift evolution of high and low mass pair fractions, thus unable to capture trends from studies which find that the merger rate varies as a function of galaxy mass~\citep{Stewart2009, Hopkins2010}.
+    We found that physical separation cuts that do not vary as a function of time and mass eliminate the ability to distinguish the different redshift evolution of high and low mass pair fractions.
+These rigid criteria are unable to capture trends from studies that find that the merger rate varies as a function of galaxy mass~\citep{Stewart2009, Hopkins2010}.
     Instead, by adopting a separation cut based on the virial radius of the group halo, we can accurately recover the different redshift evolution of low mass vs.
@@
     Pair fractions are typically translated to galaxy merger rates using an observability window~\citep{Lotz2011}.
-    The good agreement between the difference in the low mass and high mass pair fractions and the mass-dependent galaxy merger rates from \cite{RG2015} suggests that applying separation cuts that can recover this mass dependency are critical to reliably translate pair fractions to galaxy merger rates.
+    The good agreement between the difference in the low mass and high mass pair fractions and the mass-dependent galaxy merger rates from \cite{RG2015} suggests that applying separation cuts that can recover this mass dependency are critical to reliably translating pair fractions to galaxy merger rates.
 
-% Our results indicate that limits on pair separations to study pair fractions should vary as a function of total mass of the pair and redshift. 
     To study the redshift evolution of low mass pairs and recover differences in the behavior vs.
-high mass pairs, we advocate for a pair separation cut of  $r_{sep} < 1.0\Rvir$, where $\Rvir$ can be inferred using an estimate of the combined dark matter mass of the pair.
+high mass pairs, we advocate for a pair separation cut of  $r_{\mathrm{sep}} < 1.0\Rvir$, where $\Rvir$ can be inferred using an estimate of the combined dark matter mass of the pair.
     Taking the observed stellar mass of each pair member, the halo mass for each pair can be estimated using the SMHM relation \citep[e.g.,][]{Moster2013}. 
@@
     Given that chance projections will artificially boost the pair fraction as the pair separation is increased, recovering the general evolution of the pair fraction as a function of redshift may be more realistic than recovering the magnitude of the pair fraction itself, since the former requires smaller separation limits.
-    The requirement of $r_{sep} < 1.0\Rvir$ for low mass pairs translates to median separation limits that are less than $\sim 60(30)\kpc$ at $z \sim2(4)$, which are sufficiently small as to avoid major projection effects.
+    The requirement of $r_{\mathrm{sep}} < 1.0\,\Rvir$ for low mass pairs translates to median separation limits that are less than $\sim 60(30)\kpc$ at $z \sim2(4)$, which are sufficiently small as to avoid major projection effects.
+    For high mass pairs, this translates to separations less than $\sim135(75)$ at $z\sim2(4)$.
 
-    JWST is expected to identify low mass galaxies ($M_* > 10^8\Msun$) out to at least $z=10$~\citep{Behroozi2020}. 
-    We argue that the adopted pair separation criteria, particular for low mass pairs, will greatly affect the measured pair fractions and consequently the inferred merger rates.
+    JWST is expected to identify low mass galaxies ($M_* > 10^8\Msun$) out to at least $z=10$~\citep{Cowley2018,Williams2018,Behroozi2020}. 
+    We argue that the adopted pair separation criteria, particularly for low mass pairs, will greatly affect the measured pair fractions and consequently the inferred merger rates.
 
@@
   % overall low vs high mass
-    \item \textbf{The pair fraction for low mass and high mass pairs does not proceed identically throughout cosmic time.}
-    In fact, the two mass scales have opposite behavior at $z<2.5$ (see Figure~\ref{fig:pairfrac}).
+    \item The pair fraction for low mass and high mass pairs does not proceed identically throughout cosmic time.
+    In fact, the two mass scales have opposite behaviors at $z<2.5$ (see Figure~\ref{fig:pairfrac}).
     The pair fraction of low mass pairs increases from $z=0$ to $z\sim2.5$, while the pair fraction of high mass pairs peaks at $z=0$ and is constant or slightly decreasing at $z>1$.
@@
     \item At z=0, we find a low mass major (minor) pair fraction of $0.041^{+0.003}_{-0.004}$ ($0.034\pm0.004$), and a high mass major (minor) pair fraction of $0.207^{+0.012}_{-0.014}$ ($0.152^{+0.016}_{-0.017}$).
-    These results are consistent with studies that find that the merger rate for high mass pairs is $\sim4\times$ higher than for low mass galaxies \citep[e.g.][]{RG2015}. 
+    These results are consistent with other simulation-based studies that find that the merger rate for high mass pairs is $\sim4\times$ higher than for low mass galaxies \citep[e.g.][]{RG2015}. 
   % major vs. minor pairs 
     \item Low mass minor pairs evolve similarly to low mass major pairs as a function of redshift.
-    % The redshift evolution of high mass minor pair fractions is flatter at $z>1$ than for high mass major pairs, which are constant or decreasing with redshift.
   % virial radius results
-    \item The different redshift evolution of the pair fraction of high and low mass pairs is well recovered using a subsample of pairs with a maximum separation cut of $r_{sep}<1\Rvir$, where $\Rvir$ is the virial radius of the FoF group (see Eq.~\ref{eq}, where the virial radius can be estimated in observations from the combined halo mass of the pair using the SHMH relation).
+    \item The differences in redshift evolution of pair fractions for high and low mass pairs is well recovered using a subsample of pairs with a maximum separation cut of $r_{\mathrm{sep}}<1\Rvir$, where $\Rvir$ is the virial radius of the FoF group (see Eq.~\ref{eq}, where the virial radius can be estimated in observations from the combined halo mass of the pair using the SHMH relation).
     This separation cut corresponds to separations less than [134(348), 59(134), 33(76)]$\kpc$ at z=[0,2,4] for low mass (high mass) pairs.
-    In particular, a maximum separation cut of $r_{sep}<1\Rvir$ encompasses between $\sim40-60\%$ of the full population of pairs at all redshifts, and recovers the distinct differences in the redshift evolution of low mass vs.
+    In particular, a maximum separation cut of $r_{\mathrm{sep}}<1\Rvir$ encompasses between $\sim40-60\%$ of the full population of pairs at all redshifts, and recovers the distinct differences in the redshift evolution of low mass vs.
 high mass pair fractions from $z=0-2.5$.
@@
 a separation that does not evolve with redshift or with mass (e.g.
-$r_{sep}<50\kpc$).
+$r_{\mathrm{sep}}<50\kpc$).
     This occurs because fixed separation cuts capture roughly 10-50\% more pairs in the low mass pair sample than the high mass sample at all redshifts.  
@@
     \item Isolated mass-analogs of the MW--M31 are most common at $z=0$, while analogs of the MW--LMC and M31--M33 are equally common at $z=0$ as at $z>1$. 
-    However, MW--LMC-type systems with very low separations ($\lesssim50\kpc$) are 2-3 times more common at higher $z\sim$2. 
+    However, MW--LMC-type systems with very low separations ($\lesssim50\kpc$) are 2-3 times more common at higher redshift ($z\sim$2). 
     Isolated analogs of the LMC--SMC and  NGC4490-4485 are 3 times more common for $z>3$. 
@@
     In order to observationally recover the cosmologically expected difference between the merger rates of high and low mass galaxies, it is crucial to ensure that differences in the redshift evolution of the pair fraction for these galaxy populations can be adequately captured.
-    This will of particular importance in the era of JWST, where more low mass ($M_*\sim10^8 \Msun$) galaxies and galaxy pairs will be discovered at higher redshift (up to $z>10$). 
+    This will be of particular importance in the era of JWST, where more low mass ($M_*\sim10^8 \Msun$) galaxies and galaxy pairs will be discovered at higher redshift (up to $z>10$), and for future wide-field galaxy surveys enabled by the Roman Space Telescope and Rubin Observatory.
     Thus, we argue that pair selection criteria must be a function of both mass and redshift, rather than selecting a universal, static pair separation criterion.
@@
 
+\section*{Acknowledgements}
+KC would like to thank Greg Snyder for fruitful early conversations during this work. 
+KC and GB are supported by NSF CAREER award AST-1941096. 
+EP acknowledges financial support provided by NASA through grant number HST-GO-16628. 
+Support for this work was also provided by NASA through the NASA Hubble Fellowship grant \# HST-HF2-51540.001-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Incorporated, under NASA contract NAS5-26555.
+Support for SP was provided by NASA through the NASA Hubble Fellowship grant \#HST-HF2-51466.001-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Incorporated, under NASA contract NAS5-26555.
+The work of S. Stierwalt is supported by the National Science Foundation Astronomy \& Astrophysics Research Grant No 1911107.
+
+The \textsc{IllustrisTNG} simulations were undertaken with compute time awarded by the Gauss Centre for Supercomputing (GCS) under GCS Large-Scale Projects GCS-ILLU and GCS-DWAR on the GCS share of the supercomputer Hazel Hen at the High Performance Computing Center Stuttgart (HLRS), as well as on the machines of the Max Planck Computing and Data Facility (MPCDF) in Garching, Germany.
+
+The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.
+
+This work is based upon High Performance Computing (HPC) resources supported by the University of Arizona TRIF, UITS, and Research, Innovation, and Impact (RII) and maintained by the UArizona Research Technologies department.
+
+We respectfully acknowledge the University of Arizona is on the land and territories of Indigenous peoples.
+Today, Arizona is home to 22 federally recognized tribes, with Tucson being home to the O’odham and the Yaqui.
+Committed to diversity and inclusion, the University strives to build sustainable relationships with sovereign Native Nations and Indigenous communities through education offerings, partnerships, and community service
+
 \bibliography{refs}{}

### 2024-01-04 paper/apj_sub/resubmission-Dec2023/response.txt
adding files from resubmission

We thank the reviewer for the thorough, thoughtful comments on our manuscript, which prompted us to reexamine the language used to discuss observations throughout the paper.

All additions/edits to the paper are marked in bold red text (with the \add{} command).

Please find a more detailed description of each of the changes below, as well as responses to individual comments in the order that they appeared. Also, please note that we have added an additional coauthor, Nitya Kallivayalil, who was mistakenly not included in the author list during the first submission.

Best,
Katie

Begin reviewer comments:
------------------------

The manuscript entitled " A physically motivated framework for measuring the mass and redshift dependence of galaxy pair fractions across cosmic time" by Chamberlain et al. contributes to the analysis of galaxy growth via mergers using numerical simulations to determine the fraction of close pairs and its dependence on mass and redshift. The separation with respect to stellar mass is especially interesting as the differences in the pair fraction predicted by the simulations could be tested with deep survey data (at least out to intermediate redshifts).

On a practical note, I find that the "dynamic" definition of the pair separation with respect to the virial radius of the host halo would be rather complicated to implement in observational data, as the way this virial radius is selected (from the unobservable DM) would unavoidably introduce systematics that would induce artificial trends hard to disentangle. This will be especially harder if photometric redshifts are used (note that this type of study requires a large number of sources with a high completeness down to relatively small apparent distances, something that many spectroscopic surveys struggle with). While less optimal, a fixed separation criterion allows for a robust selection in both simulations and observations. Perhaps this is the reason why this paper lacks a comprehensive comparison with observational data.
–
>> We thank the reviewer for this comment. In this study we have selected pairs using a standard pair separation cut, as is done in observations (<50 kpc, 100 kpc, 150 kpc, etc). We illustrated that such a fixed separation will result in completeness issues, which will limit the effectiveness of comparison against simulations. This will be particularly true for efforts to tease out physical differences in the pair fractions of massive vs low mass galaxies over time.

To address this shortcoming, we have introduced a “dynamic” definition that involves the virial radius of the host.  The referee is correct that this is a well defined quantity in the simulations, but not in the observations. However we disagree that such an approach is unfeasible for observational studies. A dynamic definition can be introduced in an observational study using the halo-to-stellar mass relation (abundance matching). This is the same relationship we have used in our theoretical study to infer stellar masses from halo mass. As such, the errors introduced would be similar to those of the theoretical study. No comparison between theory and observations is devoid of assumptions. Applying a “dynamic” definition for pair separation is simply an example method where the introduced errors would be similar for both theory and observational samples. 
–

There is also a concern I have regarding the sample selection. On page 2, col 2, line 132, the authors state that "... no other more massive perturbers are nearby", admittedly with the intention of focusing on the pairs and somehow removing the effect of the environment over larger scales. However, this will cause a systematic in the selection towards isolated pairs. In general, the distribution of pairs will be heavily dependent on the environment. 
–
>>We thank the reviewer for their response, and have clarified in the draft that these results are true of isolated environments only.

In this study, our primary goal is to identify whether physical differences between the fraction of low mass galaxy pairs and high mass galaxy pairs exist as a function of time. We recognize that an isolation criteria can be challenging to implement in observations at high z. However, an isolation criterion is necessary in our study to remove environmental factors that can impact pair counts, such as the disruption of pairs by a more massive host. This isolation criteria enables the low mass and high mass pairs to be compared directly, as lower mass pairs are more susceptible to environmental effects. Furthermore, isolation criteria are standardly applied in studies of galaxies at low z (see Geha+ 2012, which studies isolated quenched vs. star forming galaxies at 1.5Mpc from other galaxies, or Besla+ 2018 which applies isolation criteria to the SDSS sample in their paper). We have added language to make it clear that requiring isolation may be challenging at high z. 
–

The imposed selection will target close pairs in lower density regions, affecting in several ways the analysis:

1) Observational samples need estimates of the stellar mass of the galaxies, which requires a derivation of the stellar M/L, itself dependent on the star formation history of the galaxies. A sample targeting isolated galaxies may produce different M/L than a more standard field distribution, on samples defined in groups/clusters. This is even more relevant when a large range of cosmological time is invoked (in this case out to z~4). The trends could be (partly) caused by this: the M/L of z~4 galaxies can be very different with respect to the M/L of z~0 galaxies (say at fixed mass, morphology, velocity dispersion, etc).
–
>> We agree with the reviewer that the M/L ratio of z~4 galaxies may be different that of z~0 galaxies. The trends reported in our study rely on stellar masses derived from abundance matching, which is calibrated for central halos (i.e. isolated galaxies; Moster+2023). The M/L ratio does not factor into the analysis of the simulation data and cannot explain our reported trends.  We agree that observational studies comparing galaxies selected from stellar mass cuts at high and low z galaxies should account for such differences in their errors.  We stress that the goal of this study is to identify whether any physical differences should be expected in the pair fractions of low and high mass galaxies in an ideal LCDM theoretical study.
–

2) On figure 3, for instance, the decreasing trend consistently found in low mass pairs (minor and major), could be produced by the selection of isolated pairs. Statistically, there are far more low mass galaxies in any cosmological volume, but there is also the assembly of lower mass halos into more massive structures, so the decreasing trend towards low z may just be caused by the details of the selection that progressively eliminates more pairs as they will be found in groups. This should be clarified, as an observational comparison will not only need an assumption of virial radius (as mentioned above) but also the selection of isolated pairs as in the adopted methodology.
–
>>We thank the reviewer for this comment. We have added additional text to make it clear that our reported trends are unique to our selection criteria, and may well be different for non-isolated low mass halos.

The primary goal for this study is to set the theoretical foundation for isolated pair fraction studies that seek to understand/quantify the differences between low mass and high mass pairs. Specifically, our goal is to identify if any differences in pair fractions are expected to exist in LCDM theory - the idea pointed out by the referee, that lower mass halos may assemble into more massive structures, would indeed be a prediction from LCDM theory that a such a study of pair fractions could in fact illustrate. We have added a section 5.4 to make this point and thank the referee for this comment.

Because  our selection methodology identifies halo pairs independently at each snapshot, it is true that some low mass galaxies may not be identified in our sample at one redshift but do enter the sample at another. The exact physical processes responsible for the trends we identify in this paper require tracking the individual halos across cosmic time and will be addressed in our next study.
–

I would like to see a better explanation as to why abundance matching(AM) is used instead of directly taking the stellar mass of the galaxies in TNG. The authors give a not too convincing explanation in 2.3, and the worry is that the predictions will inherit potential systematics from AM.
–
>> We thank the referee for raising this issue and have adjusted section 2.3 accordingly. The intention behind using abundance matching is threefold:
First, abundance matching allows us a prescriptive way to perform equivalent analyses for fair comparison in both the TNG Hydro and TNG Dark simulations (mentioned in section 2.3 paragraph 2).
Second, abundance matching allows us to remain independent of the specific subgrid physics that is implemented in the TNG Hydro simulation (mentioned in section 2.3 paragraph 3). Different hydrodynamical simulations use alternative subgrid physics, therefore it is likely that applying our analysis to another simulation suite using simulation stellar masses would yield different results. The abundance matching technique voids such uncertainties.
Third, abundance matching permits many realizations of stellar masses to account for the observed spread of stellar masses at a fixed halo mass, or uncertainties in the M/L ratio in the determination of stellar mass. Otherwise, we would only be able to perform this analysis for a singular given realization from the simulation. 	
We have improved some of the language in this section to make it more clear that there are a variety of reasons to use abundance matching, and added a mention of the third point above more explicitly in section 2.3 paragraph 4. Fortunately, the abundance matching method of Moster+2013 already includes ~1 dex spread in the stellar mass associated with a halo of mass ~1e11Msun. The uncertainty in the AM relationship is built into our analysis as we sample the abundance matching relation many times within this error space.
–

The authors should include a more extended comparison of their work with observationally motivated studies that assessed the growth of galaxy mass in groups of close pairs (see, e.g., Ferreras et al. 2013, Man et al. 2016, Conselice et al. 2022). Section 5.2 discusses some recent work on pair fractions, such as Besla et al. 2018, that compares low mass close pairs in SDSS with Illustris. Note the notorious low completeness at very close separation of SDSS, which would make the proposed separations presented here very challenging for actual survey data. The Snyder et al. (2017) reference focuses on more massive galaxies in the Illustris simulation, and compares with Man et al. (2016). No figure in the manuscript shows any results from observational constraints. The crux of the methodology proposed here is how one can implement a separation selection based on the virial radius in observational data. I think the connection with observations is fundamental if this paper is to make a substantial step forward.
–
>> We thank the reviewer for this comment. The intention of this paper is to show systematically that: 1) pair fractions evolve as a function of redshift; and 2) the behavior of low mass pairs and high mass pairs differs in a theoretical setting. We have edited text in the discussion section to make this clearer, and to highlight that this work is not a mock survey study. As pointed out by the referee, our pair selection choices differ markedly from that utilized by most observational studies.  As such, we do not attempt to compare our results with those of observational pair fraction studies. We have also adjusted the title of this paper to better reflect our intention.

Instead, we do compare with other simulation based pair fraction studies (some of which have their own comparisons to observational data) to ensure that our results are consistent. While these papers all use mock catalogs to compute pair fractions, they use much of the same methodology for selection that we do.

However, we do want to emphasize that, while our methodology may be challenging to adapt observationally, we have identified important selection considerations for performing observational pair fraction studies of different galaxy masses at different redshifts. The observational community should be made aware of these issues if comparisons to cosmological simulations is desired.  
–

Moreover, regarding the implementation with real data, note, for instance, that the quoted minimum separation (10 kpc) in page 6, col 1, line 399, would be at the resolution limit in most ground-based surveys at intermediate redshift. I think the actual apparent separation criterion should be led by the observational limits, and not the resolution limits of the simulation.
–
>> The minimum separation of 10 kpc is necessary to avoid incompleteness issues in the simulations. 10 kpc corresponds to a few times the simulation softening length.  It is not in the scope of this present work to include the effect of observational limits on the recovery of the pair fractions.
–

Figure 3: The fiducial separation to define a pair should be quoted in the caption, as the next figure extends on this choice of separation.
–
>> We thank the reviewer for this comment, and have added this in the caption of Figure 3. 
–

Overall, while this is a matter of taste, I would remove the brief paragraphs introduced in each section that describe what will be done in that section. I find it acceptable to do this type of brief description at the end of the introduction, regarding the whole paper. Doing this in each section seems like a page filler, and rather kills the flow of the text.
–
>> We thank the reviewer for this comment, and have decided to leave the introductory paragraphs of each section for ease of navigation for the reader.
–

In section 3, page 6, col 2, line 450, the number of pairs would be better understood if quoted as a fraction, or at least emphasize that the sample is defined within a fixed comoving volume at those two redshifts.
–
>> We thank the reviewer for this comment. We have added a line in the text to specify that this sample is defined with a fixed comoving volume in section 3.
–

### 2024-06-06 apj_sub/resubmission-Dec2023/pears.tex
deploy: 25aee7d523218253c42225dd158be0e25da52704

--- 2023-09-22 paper/pears.tex
@@
-\documentclass[twocolumn]{aastex631}
+\documentclass[linenumbers,twocolumn]{aastex631}
 
@@
 
-\newcommand{\remove}[1]{\textcolor{red}{#1}}
-\newcommand{\add}[1]{\textcolor{green}{#1}}
+\newcommand{\add}[1]{\textcolor{red}{\textbf{#1}}}
 
@@
 %% This is the end of the preamble.
-
 \begin{document}
@@
   % low mass and high mass galaxy pairs evolve differently as a function of redshift
-  A physically motivated framework for measuring\\ the mass and redshift dependence of galaxy pair fractions across cosmic time 
-  % A physically motivated framework for measuring galaxy pair fractions across cosmic time
+  %A physically motivated framework for measuring\\ the mass and redshift dependence of galaxy pair fractions across cosmic time 
+  \add{A physically motivated framework to compare pair fractions\\ of isolated low and high mass galaxies across cosmic time }
+
    % for measuring galaxy pair fractions across cosmic time
@@
 
-\author[0000-0002-1871-4154]{Dave Patton}
+\author[0000-0002-3204-1742]{Nitya Kallivayalil}
+\affiliation{\affuva}
+
+\author[0000-0002-1871-4154]{David Patton}
 \affiliation{\afftrent}
@@
 \begin{abstract} 
-Low mass galaxy pair fractions are under-studied across cosmic time. 
-In the era of JWST, Roman, and Rubin, a self-consistent framework is needed to select both low and high mass galaxy pairs to connect observed pair fractions to cosmological merger rates across all mass scales and redshifts.
-We use the Illustris TNG100 simulation to identify pairs between $z=0-4.2$ that are physically associated, free from contamination owing to projection effects.
-We construct a sample of low mass ($\rm 10^8<M_*<5\times10^9\,\Msun$) and high mass ($\rm 5\times10^9<M_*<10^{11}\,\Msun$) isolated subhalo pairs, using abundance matching to assign stellar masses. 
-The low mass pair fraction, i.e. the fraction of galaxies in pairs, increases from $z=0-2.5$, while the high mass pair fraction peaks at $z=0$ and is constant or slightly decreasing at $z>1$. 
-At $z=0$ the low mass major (1:4 mass ratio) pair fraction is 4$\times$ lower than that of high mass pairs, consistent with findings for cosmological merger rates. 
-Our results indicate that pair fractions can faithfully reproduce trends in merger rates if galaxy pairs are selected appropriately. 
-Specifically, static pair separation limits applied equivalently to all galaxy pairs do not recover the evolution of low and high mass pair fractions. 
-Instead, we advocate for separation limits that vary with the mass and redshift of the system, such as separation limits scaled by the virial radius of the host halo ($r_{\mathrm{sep}}< 1 R_{\rm vir}$).
-Finally, we place isolated mass-analogs of Local Group galaxy pairs (i.e., MW--M31, MW--LMC, LMC--SMC) in a cosmological context,
+    Low mass galaxy pair fractions are under-studied, 
+    \add{and it is unclear whether low mass pair fractions evolve in the same way as more massive systems over cosmic time.} 
+    \add{In the era of JWST, Roman, and Rubin, selecting galaxy pairs in a self-consistent way will be critical to connect observed pair fractions to cosmological merger rates across all mass scales and redshifts.}
+    \add{Utilizing the Illustris TNG100 simulation, we create a sample of physically associated low mass ($\rm 10^8<M_*<5\times10^9\,\Msun$) and high mass ($\rm 5\times10^9<M_*<10^{11}\,\Msun$) pairs between $z=0-4.2$.}
+    The low mass pair fraction increases from $z=0-2.5$, while the high mass pair fraction peaks at $z=0$ and is constant or slightly decreasing at $z>1$.
+At $z=0$ the low mass major (1:4 mass ratio) pair fraction is 4$\times$ lower than high mass pairs, consistent with findings for cosmological merger rates.
+    \add{We show that separation limits that vary with the mass and redshift of the system, such as scaling by the virial radius of the host halo ($r_{\mathrm{sep}}< 1 R_{\rm vir}$), are critical for recovering pair fraction differences between low mass and high mass systems.}
+    \add{Alternatively, static physical separation limits applied equivalently to all galaxy pairs do not recover the differences between low and high mass pair fractions, even up to separations of $300\,\kpc$.}
+    Finally, we place isolated mass-analogs of Local Group galaxy pairs (i.e., MW--M31, MW--LMC, LMC--SMC) in a cosmological context, showing that isolated analogs of LMC--SMC-mass pairs, and low separation ($<50\kpc$) MW--LMC-mass pairs, are $2-3\times$ more common at $z\gtrsim2-3$.
 
-%  changed by rec. of garreth
-and show that isolated analogs of LMC--SMC-mass pairs, as well as MW--LMC-mass pairs with low separation ($<50\kpc$), are $2-3\times$ more common at $z\gtrsim2-3$.
-%quantifying for the first time the frequency of finding isolated analogs of such pairs as a function of redshift.
-
+    % old abstract:
+    % Low mass galaxy pair fractions are under-studied across cosmic time. 
+    % In the era of JWST, Roman, and Rubin, a self-consistent framework is needed to select both low and high mass galaxy pairs to connect observed pair fractions to cosmological merger rates across all mass scales and redshifts.
+We use the Illustris TNG100 simulation to identify physically associated pairs between $z=0-4.2$.
+    % Our sample includes low mass ($\rm 10^8<M_*<5\times10^9\,\Msun$) and high mass ($\rm 5\times10^9<M_*<10^{11}\,\Msun$) isolated subhalo pairs, with stellar masses from abundance matching. 
+    % The low mass pair fraction, i.e. the fraction of galaxies in pairs, increases from $z=0-2.5$, while the high mass pair fraction peaks at $z=0$ and is constant or slightly decreasing at $z>1$. 
+    % At $z=0$ the low mass major (1:4 mass ratio) pair fraction is 4$\times$ lower than high mass pairs, consistent with findings for cosmological merger rates. 
+    % Our results indicate that pair fractions can faithfully reproduce trends in merger rates if galaxy pairs are selected appropriately. 
+    % Specifically, static pair separation limits applied equivalently to all galaxy pairs do not recover the evolution of low and high mass pair fractions. 
+    % Instead, we advocate for separation limits that vary with the mass and redshift of the system, such as separation limits scaled by the virial radius of the host halo ($r_{\mathrm{sep}}< 1 R_{\rm vir}$).
+    % Finally, we place isolated mass-analogs of Local Group galaxy pairs (i.e., MW--M31, MW--LMC, LMC--SMC) in a cosmological context, showing that isolated analogs of LMC--SMC-mass pairs, and low separation ($<50\kpc$) MW--LMC-mass pairs, are $2-3\times$ more common at $z\gtrsim2-3$.
 \end{abstract}
@@
 
-    Typically, observational studies of pair fractions apply projected separation cuts that are constant over time and do not vary with the mass of the target system. 
-    To fairly test for differences in the evolutionary behavior of pair fractions, especially in observational studies, it is necessary to determine whether this is an appropriate technique for accurately recovering true pair fraction behavior.
-    In this study we identify how the application of a fixed separation criteria affects inferred pair fractions, and make recommendations for a time and mass evolving separation cut to permit equitable pair fraction comparisons between different mass regimes.
-
     In particular, we take the approach of consistently selecting physically associated pairs of low mass ($10^8<M_*<5\times10^9\Msun$) and high mass $(5\times10^9<M_*<10^{11}\,\Msun)$ galaxies. 
@@
     We require that pairs are part of the same Friends of Friends (FoF) group and that no other more massive perturbers are nearby, which allows us to ensure that the recovered pair fractions are inherent to the population of selected pairs rather than a function of environment.
+
+    Typically, 
+    \add{pair fraction studies via simulations and observations}
+    apply physical projected separation cuts that are constant over time and do not vary with the mass of the target system. 
+    \add{In this study we identify how the application of a fixed separation criteria affects inferred pair fractions, and show that a time and mass evolving separation cut is necessary to permit equitable pair fraction comparisons across different mass regimes.}
+    \add{Although implementing alternative selection criteria in future observational pair fraction studies may not always be strictly necessary, we recommend that pair selection criteria be reevaluated for observational studies that seek to compare pair fractions as a function of mass or redshift.}
+    % In this study we identify how the application of a fixed separation criteria affects inferred pair fractions, and make recommendations for a time and mass evolving separation cut to permit equitable pair fraction comparisons between different mass regimes.
+    % To fairly test for differences in the evolutionary behavior of pair fractions, especially in observational studies, it is necessary to determine whether this is an appropriate technique for accurately recovering true pair fraction behavior.
 
@@
     We present the time-evolving pair fraction of high mass and low mass pairs in Section~\ref{sec:results}, and show how they change for different separation criteria. 
-    In Section~\ref{sec:discussion}, we discuss the implications of the differences between low and high mass pair fractions for observational campaigns and give context to our results by drawing comparisons to Local Group pairs.
+    \add{In Section~\ref{sec:discussion}, we give context to our results by drawing comparisons to Local Group pairs and other Illustris-based pair fraction studies, and discuss implications for observational campaigns.}
+        % In Section~\ref{sec:discussion}, we discuss the implications of the differences between low and high mass pair fractions for observational campaigns and give context to our results by drawing comparisons to Local Group pairs.
     Finally, we summarize our results and conclusions in Section~\ref{sec:summary}.
@@
 
-    We are interested in the intrinsic frequency of low and high mass galaxy pairs in the field, rather than in over dense environments. 
+    % reworded for clarity
+    % We are interested in the intrinsic frequency of low and high mass galaxy pairs in the field, rather than in over dense environments.
 This allows us to assess whether there are fundamental differences in the frequency of pairs as a function of mass scale that are independent of environmental factors\footnote{Note that our pair fraction calculations are thus specifically for isolated systems, and the global pair fraction (including both isolated and non-isolated pairs) will be different.}.
@@
 We do this by placing limits on the virial mass of the FoF group to which our low mass or high mass samples belong.
+    \add{To assess whether the pair fractions of low mass and high mass pairs evolve in fundamentally different ways as a function of redshift, rather than as a product of their environmental conditions, we will focus on galaxy pairs in low density environments only\footnote{Note that our pair fraction calculations are thus specifically for isolated systems, and the global pair fraction (including both isolated and non-isolated pairs) will be different.}.
+    As such, we ensure that our target subhalos are sufficiently isolated by placing limits on the virial mass of the FoF group to which our low mass or high mass samples belong.}
 
@@
 
-    First, at each snapshot, we apply a cut on the FoF group virial mass, $M_{\rm vir}$, given by \texttt{Group\_M\_TopHat200}\footnote{The mass \texttt{Group\_M\_TopHat200} is the mass enclosed by a sphere with mean density $\Delta_c *\rho_c$, where $\Delta_c$ is the overdensity constant from~\citet{Brynorman1998} and $\rho_c$ is the critical density of the universe at the time calculated.
+    At each snapshot, we first apply a cut on the FoF group virial mass, $M_{\rm vir}$, given by \texttt{Group\_M\_TopHat200}\footnote{The mass \texttt{Group\_M\_TopHat200} is the mass enclosed by a sphere with mean density $\Delta_c *\rho_c$, where $\Delta_c$ is the overdensity constant from~\citet{Brynorman1998} and $\rho_c$ is the critical density of the universe at the time calculated.
 The corresponding virial radius in TNG100 is given by \texttt{Group\_R\_TopHat200}.} in the TNG100 group catalogs.
@@
     The FoF group mass criteria is fixed for all redshifts, which means that some low mass groups at high $z$ may be the progenitors of high mass systems at $z=0$.
-    % Note that all masses used in this analysis are physical units, meaning that masses from the group catalogs are divided by $h$ to get units of \Msun.
 
@@
     For example, selecting low mass pairs from the low mass FoF groups ensures that the selected pairs are not satellite systems of high mass subhalos. 
-    We have confirmed that over 99\% of subhalos selected from FoF groups that obey the listed mass limits are isolated; meaning, they are not within $1.5\,\Mpc$ of perturbers more massive than the mass of the pair.
+    % reworded for clarity
+    %We have confirmed that over 99\% of subhalos selected from FoF groups that obey the listed mass limits are isolated; meaning, they are not within $1.5\,\Mpc$ of perturbers more massive than the mass of the pair.
+    \add{Over 99\% of subhalos selected from FoF groups in these mass limits are not within $1.5\,\Mpc$ of a more massive perturber at $z=0$.}
 
@@
 
-    Primarily, applying an abundance matching prescription to assign stellar masses allows us to account for the observed spread in the SMHM relationship. 
+    \add{First, and primarily, utilizing an abundance matching prescription enables the direct comparison of results between dark matter only and full hydrodynamics simulations, since the stellar masses are assigned in an identical and prescriptive way.
+    We make a brief note of results for our equivalent analysis using the dark matter only, TNG100-Dark simulation, in Sec.~\ref{sec:disc-dark}.}
+
+    \add{Second, while the SMHM function of \tng{} at $z=0$ closely reproduces the profile of the SMHM relation from various abundance matching and semi-empirical models~\citep{TNG5,Nelson2019}, using stellar masses as calculated from abundance matching allows us to avoid any simulation-dependent stellar mass effects.
+    In particular, we would like to avoid a dependence between our results and the particular subgrid physics model implemented in \tng{}.}
+
+    \add{Third, abundance matching allows us to account for the observed spread in the SMHM relationship, as we can sample the relation many times to get a distribution of stellar masses for each subhalo in the simulation.
+Otherwise, we would only be able to perform this analysis once given the set of stellar masses from the simulation.
     This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large, between $\sim 0.3$ for $M_{h}\sim 10^{10}\Msun$ up to $\sim 1$dex for $M_{h}\sim10^{8}\Msun$~\citep{Munshi2021}.
-    While the SMHM function of \tng{} at $z=0$ closely reproduces the profile of the SMHM relation from various abundance matching and semi-empirical models~\citep{TNG5,Nelson2019}, using stellar masses as calculated from abundance matching allows us to avoid any simulation-dependent stellar mass effects.
-    Finally, utilizing an abundance matching prescription enables direct comparisons of results between dark matter only and full hydrodynamics simulations, since the stellar masses are assigned in an identical way.
-    We make a brief note of results for our equivalent analysis using the dark matter only, TNG100-Dark simulation, in Sec.~\ref{sec:disc-dark}.
+}
 
-    We use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic prescription to assign stellar masses to dark matter halos. 
-    The~\citet{Moster2013} relationship is a function of subhalo mass, redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with a larger scatter at lower halo masses.
+    %Primarily, applying an abundance matching prescription to assign stellar masses allows us to account for the observed spread in the SMHM relationship. 
+    %This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large, between $\sim 0.3$ for $M_{h}\sim 10^{10}\Msun$ up to $\sim 1$dex for $M_{h}\sim10^{8}\Msun$~\citep{Munshi2021}.
+    %While the SMHM function of \tng{} at $z=0$ closely reproduces the profile of the SMHM relation from various abundance matching and semi-empirical models~\citep{TNG5,Nelson2019}, using stellar masses as calculated from abundance matching allows us to avoid any simulation-dependent stellar mass effects.
+    %Finally, utilizing an abundance matching prescription enables direct comparisons of results between dark matter only and full hydrodynamics simulations, since the stellar masses are assigned in an identical way.
+    %We make a brief note of results for our equivalent analysis using the dark matter only, TNG100-Dark simulation, in Sec.~\ref{sec:disc-dark}.
 
-    Because the abundance matching prescription is calibrated for centrals of FoF groups, we elect to use the maximum subhalo mass \Mpeak\ in the stellar mass calculation, rather than the subhalo mass at the given snapshot \citep[see][]{Besla2018}.
-    We also use the current redshift of the given snapshot, $z_{\mathrm{snap}}$, of each subhalo in the stellar mass calculation. 
-    Thus, $\ms{}=f(\Mpeak,z_{\mathrm{snap}})$.
+    We use the abundance matching relationship presented in~\citet{Moster2013}.
+    %which provides an analytic prescription to assign stellar masses to dark matter halos. 
+    \add{The SMHM relationship therein provides an analytic prescription to assign stellar masses to dark matter halos as a function of subhalo mass and redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with a larger scatter at lower halo masses.
+    We were careful to choose the input subhalo mass and redshift that would assign the most accurate stellar masses to each halo given their individual histories.}
+    %The~\citet{Moster2013} relationship is a function of subhalo mass, redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with a larger scatter at lower halo masses.
+    %incomplete thought: The subhalo mass and redshift that are used to calculate the stellar mass impacts the stellar mass that is assigned to a given halo.
+For example, a satellite subhalo may have some of its associated dark matter stripped away by its host, while the stellar mass remains roughly the same throughout the loss of a significant portion of
 
+    The abundance matching prescription is calibrated for centrals of FoF groups, thus we elect to use the maximum subhalo mass \Mpeak\ in the stellar mass calculation, rather than the subhalo mass at the given snapshot \citep[see][]{Besla2018}.
     Using \Mpeak\ mass allows us to remain robust to scenarios in which a secondary has formed most of its stars, then loses a significant portion of its dark matter content through tidal interactions with a primary, but retains the bulk of its stellar content.
@@
 
+    We also use the current redshift of the given snapshot, $z_{\mathrm{snap}}$, of each subhalo in the stellar mass calculation. 
     Using $z_{\mathrm{snap}}$ means that we account for changes in the stellar mass of both the primary and secondary halo, even after the secondary has entered the primary's halo. 
@@
     Additionally, the SAGA survey has found that large satellites of MW-type galaxies are often very blue, with infall into the halo spurring high rates of star formation due to the large gas fraction in dwarfs~\citep{Mao2021}.
+    Thus, our abundance matching prescription is of the form $\ms{}=f(\Mpeak,z_{\mathrm{snap}})$.
 
-    We then calculate the stellar mass for a given subhalo by Gaussian sampling each of the fitting parameters of the analytic framework from~\cite{Moster2013}, in order to account for the spread in the SMHM relationship.
-    We generate a single stellar mass ``realization" of the full \subcat\ by calculating a stellar mass for each subhalo, using an independent draw from the SMHM distribution for each subhalo. 
-    For each snapshot, we repeat this process 1000 times to generate 1000 realizations of stellar masses for the \subcat.
+    We calculate the stellar mass for a given subhalo by Gaussian sampling each of the fitting parameters of the analytic framework from~\cite{Moster2013}, in order to account for the spread in the SMHM relationship.
+    %We generate a single stellar mass ``realization" of the full \subcat\ by calculating a stellar mass for each subhalo, using an independent draw from the SMHM distribution for each subhalo. 
+    \add{We generate a single stellar mass ``realization" using an independent draw from the SMHM distribution to calculate a stellar mass for each subhalo of the full \subcat.}
+    For each snapshot, we repeat this process 1000 times to generate 1000 separate realizations of assigned stellar masses for the \subcat.
     The resulting catalog is called the \starcat, and consists of the set of all subhalos from the \subcat, as well as the 1000 stellar mass realizations. 
     Each realization is treated as an independent sample of galaxy stellar masses, which will allow us to report realistic spreads of pair properties.
-In addition, our pair stellar mass selection criteria will result in different collections of subhalos being selected in each realization, since the stellar masses van
 
@@
     \subsection{Pair selection}\label{sec:methods-pairs}
-    Starting from the \starcat, here we outline the pair matching process through which we generate the \paircat. 
+    Starting from the \starcat, we outline the pair matching process used to generate the \paircat below. 
     At each redshift, and for each stellar mass realization, we will identify subhalo pairs consisting of a ``primary" and a ``secondary", where primaries are the more massive of the pair by stellar mass.
@@
     \subsubsection{Selecting primaries}
-        Primary galaxies (equivalently, ``primary subhalos") are the most massive galaxy of their FoF group by stellar mass, such that each group can have at most one primary galaxy.  
+        Primary galaxies (equivalently, ``primary subhalos") are the most massive galaxy of their FoF group by stellar mass, such that each group will have a singular primary galaxy.  
         Each stellar mass realization is treated independently, and so the subhalo identified as the primary of a group may change between stellar mass realizations.
@@
         For each pair, we calculate the physical separation (proper \kpc, not comoving \kpc) between the two subhalos using the \texttt{SubhaloPos} field from the subhalo catalogs.
-We require that each pair have a minimum separation of $10 \, \kpc$ between primary and secondary to limit the impact of very close subhalos becoming indistinguishable in \subfind as a result of the resolution limit due to the softening length.
+We require that each pair have a minimum separation of $10 \, \kpc$ between primary and secondary to limit the impact of very close subhalos becoming indistinguishable in \subfind\ as a result of the resolution limit due to the softening length.
         % The minimum separation cut is more than 10 times the smoothing length of the simulation at $z=0$, which ensures that  can identify the subhalos as distinct objects XXXXX ADD CITATION HERE - vicente?
@@
         If a primary subhalo does not have a companion that meets the stellar mass ratio criteria and separation criteria, the subhalo will still be considered a primary. 
-        We refer to all primaries that do not have a companion that passes these criteria as ``isolated primaries," including primaries that may have a companion that meets the stellar mass ratio criteria but has a separation $<10\,\kpc$.
+        We refer to all primaries that do not have a companion with these criteria as ``isolated primaries," including primaries with a companion that meets the stellar mass ratio criteria but has a separation $<10\,\kpc$.
         The total number of primaries includes both isolated primaries and those with selected companions and is larger than the total number of pairs.
@@
     Our sample of high mass primaries represents approximately 20\% of all subhalos in TNG100 with the same range of stellar masses at $z=0$.
-    There are roughly 8 times as many low mass primaries as high mass primaries.
+    There are roughly 8 times as many low mass primaries as high mass primaries. \add{Note that the comoving volume of \tng{} is the same at all redshifts.}
 
@@
 In this section, we will analyze the frequency of major and minor pair types across cosmic time, with the goal of identifying potential differences between high and low mass galaxies. 
-
 In Sec.~\ref{sec:results-frac}, we examine the redshift evolution of the fraction of primaries with a major or minor companion (the ``pair fraction") and compare the results for low mass and high mass pairs.
@@
     Overall, these results show that low mass and high mass pair counts evolve differently over time, particularly at very low redshift, despite the pair fractions being roughly equal at higher redshift.
-    The implications for the difference in the evolution of pair fractions for low mass and high mass pairs across time are discussed in detail in Sec.~\ref{sec:disc-obs}.
+    The implications for the difference in the evolution of pair fractions for low mass and high mass pairs across time are discussed in detail in Sec.~\ref{sec:discussion}.
 
@@
         (Top) Median pair fraction as a function of redshift, defined as the fraction of low mass or high mass primaries with a major (solid) or minor (dashed) companion  (see Sec.~\ref{sec:methods-pairs}).
+\add{All pairs in the \paircat\ must have a minimum separation of at least $>10\kpc$, with no constraint on the maximum separation.}
         Shaded areas show the 1-99 percentile range on the median (solid and dashed lines) from 1000 stellar mass realizations, as discussed at the beginning of Sec.~\ref{sec:results}. 
@@
     We choose 6 subsamples, consisting of pairs with separations less than $0.25, 0.5, 1.0, 1.5, 2.0,$ and $2.5\Rvir$. 
-    The top row of Fig.~\ref{fig:vircut} shows the median pair fraction (solid lines), calculated as described at the beginning of section~\ref{sec:results}, 
-    for high mass (pink) and low mass (green) pairs in each of the 6 subsamples. 
+    The top row of Fig.~\ref{fig:vircut} shows the median pair fraction (solid lines) for high mass (pink) and low mass (green) pairs in each of the 6 subsamples. 
     In the bottom row, we show the recovery fraction, which is the fraction of the total pair sample that is recovered by each subsample, i.e.
@@
 
-    As the pair separation limits increase (left to right), the recovery fraction increases, as does the pair fraction, as expected because each consecutive selection cut is less restrictive and will contain more of the full sample.
-    More than 75\% of the full pair sample is recovered at all redshifts with separation criteria up to $2\Rvir$.
+    As the pair separation limits increase (left to right), the recovery fraction increases, so too does the pair fraction as expected since each consecutive selection cut is less restrictive and will contain more of the full sample.
+    More than 75\% of the full pair sample is recovered at all redshifts when the sample contains all pairs within $2\Rvir$ (the two rightmost panels of Fig.~\ref{fig:vircut}).
 
-    All subsamples of high mass pairs display broadly the same pair fraction redshift evolution as the full high mass sample (pink line in left panel of Figure~\ref{fig:pairfrac}): each of the subsampled high mass pair fractions peak at $z=0$ and remain roughly constant or decrease at higher redshift.
+    All subsamples of high mass pairs display broadly the same pair fraction redshift evolution as the full high mass sample (pink line in left panel of Figure~\ref{fig:pairfrac}): each of the sub-sampled high mass pair fractions peak at $z=0$ and remain roughly constant or decrease at higher redshift.
     The finer detail trends from the full sample, particularly the upturn at low z, are reasonably captured if $r_{\mathrm{sep}} < 0.5 \Rvir$, despite the recovery being $\sim$40\%. 
@@
     We also find that differences between the redshift evolution of high mass pairs vs. low mass pairs (particularly at $z<2$) become apparent if $r_{\mathrm{sep}} < 0.5\Rvir$ for both galaxy types. 
-    Overall we find that recovering the redshift evolution of the pair fractions of all galaxy pairs requires a separation cut such that the number of close pairs constitutes $\sim40-50\%$ or more of the full sample at all redshifts.
+    Overall we find that recovering the redshift evolution of the pair fractions of all galaxy pairs requires a separation cut that contains at least the closest $\sim40-50\%$ of pairs from the full sample at all redshifts.
 
@@
         (Bottom) The recovery fraction, calculated as the fraction of the total collection of pairs recovered by the subset of pairs at the given separation cut. 
-        We find that recovering the redshift evolution of the pair fractions of all galaxy pairs requires a separation cut such that the number of close pairs constitutes $\sim50-70\%$ of the full sample at all redshifts.
+        We find that recovering the redshift evolution of the pair fractions of all galaxy pairs requires a separation cut such that the number of close pairs constitutes more than $\sim50\%$ of the full sample at all redshifts.
     }
@@
 In Sec.~\ref{sec:disc-comp}, we compare our results to previous studies of pair fractions that utilize simulations. 
-Finally, we discuss the implications of the pair fraction behavior of low mass pairs and high mass pairs as a function of redshift for observations and our suggestions for appropriate separation cuts in observational pairs in Sec.~\ref{sec:disc-obs}.
+We discuss the observational implications of the pair fraction behavior of low mass pairs and high mass pairs as a function of redshift
+%and our suggestions for appropriate separation cuts in observational pairs 
+in Sec.~\ref{sec:disc-obs}.
+\add{We conclude by discussing some possibilities for the pair fraction difference between low and high mass pairs in Sec.~\ref{sec:disc-diff}}
 
@@
     A direct comparison to pair fractions reported from observations is not straight-forward, as observationally selected pairs suffer from contamination due to projected pairs and restrictive separation criteria that exclude more widely separated pairs.
-    Here, we compare our results to pair fractions and merger rates reported by other studies of the Illustris cosmological simulations to establish the reliability of our findings.
+    Instead, we compare our results to pair fractions and merger rates reported by other studies of the Illustris cosmological simulations to establish the reliability of our findings.
 
@@
 
-        We find reasonable agreement with the sample of physical pairs in \cite{Besla2018}, which found a major pair fraction between 0.003-0.018 over a mass range of $2\times 10^8 < M_* < 5 \times 10^9$ $M_\odot$.
+        We find reasonable agreement with the sample of physical 3D pairs in \cite{Besla2018}, which found a major pair fraction between 0.003-0.018 over a mass range of $2\times 10^8 < M_* < 5 \times 10^9$ $M_\odot$.
         % used fig. 15 for these vals.
@@
     We found that physical separation cuts that do not vary as a function of time and mass eliminate the ability to distinguish the different redshift evolution of high and low mass pair fractions. 
-These rigid criteria are unable to capture trends from studies that find that the merger rate varies as a function of galaxy mass~\citep{Stewart2009, Hopkins2010}.
+    %These rigid criteria are unable to capture trends from studies that find that the merger rate varies as a function of galaxy mass~\citep{Stewart2009, Hopkins2010}. 
     Instead, by adopting a separation cut based on the virial radius of the group halo, we can accurately recover the different redshift evolution of low mass vs.
@@
 
-    Pair fractions are typically translated to galaxy merger rates using an observability window~\citep{Lotz2011}.
-    The good agreement between the difference in the low mass and high mass pair fractions and the mass-dependent galaxy merger rates from \cite{RG2015} suggests that applying separation cuts that can recover this mass dependency are critical to reliably translating pair fractions to galaxy merger rates.
+    % rewrote this, became the paragraphs below 
+    %To study the redshift evolution of galaxy pairs and recover differences in the behavior of low mass vs.
+high mass pairs, we advocate for a pair separation cut of  $r_{\mathrm{sep}} < 1.0\Rvir$, where $\Rvir$ can be inferred using an estimate of the combined dark matter mass of the pair.
+    % Taking the observed stellar mass of each pair member, the halo mass for each pair can be estimated using the SMHM relation \citep[e.g.,][]{Moster2013}. 
+    % The combined halo mass of the pair can then be used as a proxy for the virial mass of the FoF group ($\rm M_{vir}$) to compute the virial radius, e.g. 
+    % \begin{equation}\label{eq}
+    % \Rvir = \sqrt[3]{\frac{3\rm M_{vir}}{4\pi \Delta_{c}\rho_{c}}},
+    % \end{equation}
+    % where $\rho_c$ is the critical density of the universe, and $\Delta_{c}$ is the overdensity constant~\citep[see][]{BinneyTremaine2008}. 
+    % Both $\rho_c$ and $\Delta_{c}$ are functions of redshift, such that $\Rvir$ changes as a function of both the mass of the pair and redshift.
 
-    To study the redshift evolution of low mass pairs and recover differences in the behavior vs.
-high mass pairs, we advocate for a pair separation cut of  $r_{\mathrm{sep}} < 1.0\Rvir$, where $\Rvir$ can be inferred using an estimate of the combined dark matter mass of the pair.
-    Taking the observed stellar mass of each pair member, the halo mass for each pair can be estimated using the SMHM relation \citep[e.g.,][]{Moster2013}. 
+    \add{These results indicate that future observational studies that seek to compare low mass and high mass pair fractions, particularly as a function of time, must take care when determining their pair selection criteria.}
+    \add{We advocate for separation criteria that varies as both a function of mass and redshift, such as our choice of $r_{\mathrm{sep}} < 1.0\Rvir$, where $\Rvir$ can be inferred using an estimate of the combined dark matter mass of the pair.}\footnote{Taking the observed stellar mass of each pair member, the halo mass for each pair can be estimated using the SMHM relation \citep[e.g.,][]{Moster2013}.
     The combined halo mass of the pair can then be used as a proxy for the virial mass of the FoF group ($\rm M_{vir}$) to compute the virial radius, e.g. 
@@
     where $\rho_c$ is the critical density of the universe, and $\Delta_{c}$ is the overdensity constant~\citep[see][]{BinneyTremaine2008}. 
-    Both $\rho_c$ and $\Delta_{c}$ are functions of redshift, such that $\Rvir$ changes as a function of both the mass of the pair and redshift.
+    Both $\rho_c$ and $\Delta_{c}$ are functions of redshift, such that $\Rvir$ changes as a function of both the mass of the pair and redshift.}
+    \add{We have shown that utilizing fixed physical separation cuts can lead to significant deviation in the behavior of galaxy pair fractions for different galaxy masses and between $z=0-4$, and thus it is imperative to carefully consider the selection criteria used in future observational pair fraction studies of low and high mass pairs over time.}
+
+    \add{In addition, our findings are specific to systems in isolated environments, and thus may not be representative of the pair fractions of a more "standard" observational field that contains pairs in isolated and high density environments.}
+    \add{Mitigating this issue in observations would require making certain isolation cuts, such as those employed in \citet{Geha2013} to identify low mass pairs in isolated ($>1.5\,\Mpc$ away from an $\rm L^{*}$ galaxy) and non-isolated (within $1.5\,\Mpc$ of an $\rm L^{*}$ galaxy) environments.}
 
@@
 
-    JWST is expected to identify low mass galaxies ($M_* > 10^8\Msun$) out to at least $z=10$~\citep{Cowley2018,Williams2018,Behroozi2020}. 
+    % moved this paragraph and combined with another
+    Pair fractions are typically translated to galaxy merger rates using an observability window~\citep{Lotz2011}.
+    The good agreement between the difference in the low mass and high mass pair fractions and the mass-dependent galaxy merger rates from \cite{RG2015} suggests that applying separation cuts that can recover this mass dependency are critical to reliably translating pair fractions to galaxy merger rates.
+    In fact, JWST is expected to identify low mass galaxies ($M_* > 10^8\Msun$) out to at least $z=10$~\citep{Cowley2018,Williams2018,Behroozi2020}. 
     We argue that the adopted pair separation criteria, particularly for low mass pairs, will greatly affect the measured pair fractions and consequently the inferred merger rates.
 
-    Understanding in detail the origin of the discrepancy in the redshift evolution of low mass vs.
+\subsection{Underlying physical behavior of galaxy pairs}\label{sec:disc-diff}
+    \add{Though we find a distinct difference in the redshift evolution of low mass and high mass pair fractions, our study does not explicitly identify the specific driver of these differences.}
+    \add{In a \lcdm\ universe, the build-up of structure proceeds hierarchically, with smaller structures merging to form larger and larger structures at later times.}
+    \add{This may explain the significant decrease in the pair fraction of isolated low mass galaxies from $z=2$ to $z=0$, since more and more low mass systems would be accreted into larger group structures and would thus be removed from our isolated pair sample.}
+
+    \add{On the other hand, the inherent dynamics of the pairs themselves may dictate the redshift evolution of their respective pair fractions.}
+    \add{For example, if low mass pairs tend to have very short merger timescales, the total number of low mass pairs would decrease much more rapidly than massive pairs with a very long timescale.}
+
+    Understanding in further detail the origin of the discrepancy in the redshift evolution of low mass vs.
 high mass pairs requires tracking the specific pairs across simulation snapshots to trace their orbits and study changes in the mass and environment of the pairs across cosmic time.
@@
 Our goal is to quantify the evolution of low mass and high mass galaxy pairs across cosmic time and to identify any differences in the redshift evolution of pair fractions of low mass and high mass pairs.
-We also aim to determine whether the redshift evolution of the pair fraction can be well recovered from observationally selected pairs. 
+\add{We also aim to determine how separation criteria for pair selection can affect the pair fraction evolution of high and low mass pairs.}
+% We also aim to determine whether the redshift evolution of the pair fraction can be well recovered from observationally selected pairs. 
 To this end, we additionally employ both static and time+mass evolving separation cuts to explore the resulting impact on the pair fractions.
@@
   % virial radius results
-    \item The differences in redshift evolution of pair fractions for high and low mass pairs is well recovered using a subsample of pairs with a maximum separation cut of $r_{\mathrm{sep}}<1\Rvir$, where $\Rvir$ is the virial radius of the FoF group (see Eq.~\ref{eq}, where the virial radius can be estimated in observations from the combined halo mass of the pair using the SHMH relation).
+    \item The differences in redshift evolution of pair fractions for high and low mass pairs is well recovered using a subsample of pairs with a maximum separation cut that varies with mass and redshift, specifically for $r_{\mathrm{sep}}<1\Rvir$, where $\Rvir$ is the virial radius of the FoF group
+    % (see Eq.~\ref{eq}, where the virial radius can be estimated in observations from the combined halo mass of the pair using the SHMH relation).
+    .
     This separation cut corresponds to separations less than [134(348), 59(134), 33(76)]$\kpc$ at z=[0,2,4] for low mass (high mass) pairs.
@@
 
+    \add{Observational campaigns that seek to recover low mass and high mass pair fractions should consider using mass and redshift evolving separation criteria to select pairs.}
     Many observational pair fraction studies use static definitions of the maximum projected separation to determine close pairs, then translate between pair fractions and merger rates via an observability timescale.
@@
     This will be of particular importance in the era of JWST, where more low mass ($M_*\sim10^8 \Msun$) galaxies and galaxy pairs will be discovered at higher redshift (up to $z>10$), and for future wide-field galaxy surveys enabled by the Roman Space Telescope and Rubin Observatory.
-    Thus, we argue that pair selection criteria must be a function of both mass and redshift, rather than selecting a universal, static pair separation criterion.
+    %Thus, we argue that pair selection criteria must be a function of both mass and redshift, rather than selecting a universal, static pair separation criterion.
 

### 2024-06-06 gb_placeholder.tex
deploy: 25aee7d523218253c42225dd158be0e25da52704

Low mass galaxy pair fractions are understudied across cosmic time. Needed is a self-consistent framework to select both low and high mass galaxy pairs in order to connect observed pair fractions to cosmological merger rates across all mass scales and redshifts. Here, we construct a sample of low mass ($\rm 10^8<M_*<5\times10^9\,\Msun$) and high mass ($\rm 5\times10^9<M_*<10^{11}\,\Msun$) subhalo pairs from the TNG100 simulation from $z=0-4.2$. Pairs belong to the same FoF group, meaning they are isolated, physically associated, and not contaminated by projection effects. Stellar masses are assigned using abundance matching. We find that the low mass pair fraction increases from $z=0-2.5$, while the high mass pair fraction peaks at $z=0$ and is constant or slightly decreasing at $z>1$. At z=0 the low mass major pair fraction is four times lower than that of high mass pairs, consistent with findings for cosmological merger rates. Our results indicate that pair fractions can faithfully reproduce trends in merger rates if galaxy pairs are selected appropriately. Specifically, static pair separation limits applied equivalently to all galaxy pairs do not recover the  evolution of low and high mass pair fractions. Instead, we advocate for separation limits that vary with the mass and redshift of the system, such as separation limits scaled by the  estimated virial radius of the primary ($r_{sep}< 1 R_{vir}$). Finally, we place isolated mass-analogs of Local Group galaxy pairs (MW-M31, MW-LMC, M31-M33, LMC-SMC) in a cosmological context, quantifying for the first time the frequency of finding isolated analogs of such pairs as a function of redshift.

In particular galaxy pairs like the MW-M31 system are

However, applying a separation cut that is a function of mass and redshift recovers the difference in the behavior of low and high mass pairs at all redshifts.

  There has been no systematic study to ensure that any differences in \lcdm\ simulations can be captured in observational surveys. 
  In this study we utilize the TNG100 simulation to select isolated low mass and high mass pairs self-consistently to quantify pair fractions from $z=0-4.2$.
  We find that the pair fraction of high mass pairs peaks at $z=0$ and is constant or slightly decreasing with increasing redshift for $z>1$, while low mass pair fractions increase from $z=0$ to $z\sim2.5$ before leveling out from $z=2.5-4.2$.
  We also assess the impact of separation-based pair selection criteria on the resulting pair fractions, and find that physical separation cuts applied equivalently to all pairs eliminates the ability to distinguish the behavior of low and high mass pair fractions across all redshifts. 
  However, applying a separation cut that is a function of mass and redshift recovers the difference in the behavior of low and high mass pairs at all redshifts. 
  Our analysis is consistent with previous findings of a redshift and mass dependence of the merger fraction and merger rate of galaxy pairs in simulations. 
  We argue that in order for observational pair fraction campaigns to recover the true pair fractions, and thus the true merger rates, of galaxy pairs, separation criteria must evolve as a function of redshift and mass of each pair.
  Finally, we study the frequency of isolated mass-analogs of galaxy pairs in the Local Group in a cosmological context, and quantify for the first time the frequency of finding such isolated pairs as a function of redshift and separation.

### 2024-06-06 paper_incl_kinematics/paper.tex
deploy: 25aee7d523218253c42225dd158be0e25da52704

\documentclass[twocolumn]{aastex631}

% Packages
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{soul}

\definecolor{pink}{RGB}{232,132,161}
\definecolor{yellow}{RGB}{255,213,0}

\newcommand{\kc}[1]{\textcolor{yellow}{\textbf{kc: #1}} }
\newcommand\shadetext[2][]{%
  \setbox0=\hbox{{\special{pdf:literal 7 Tr }#2}}%
  \tikz[baseline=0]\path [#1] \pgfextra{\rlap{\copy0}} (0,-\dp0) rectangle (\wd0,\ht0);% 
  }
\newcommand{\gb}[1]{\shadetext[left color=blue, right color=red, middle color=lime, shading angle=45]{\textbf{g: #1}} }
% \newcommand{\ecite}[1]{\textcolor{pink}{\textbf{: #1}} }
% \newcommand{\e}[1]{\textcolor{yellow}{\textbf{: #1}} }

\newcommand{\remove}[1]{\textcolor{red}{#1}}
\newcommand{\add}[1]{\textcolor{green}{#1}}

\newcommand{\mlg}{\ensuremath{M_{\rm LG}}}
\newcommand{\mmto}{\ensuremath{M_{\rm M31}}}
\newcommand{\mmw}{\ensuremath{M_{\rm MW}}}
\newcommand{\vtan}{\ensuremath{v_\textrm{tan}}}
\newcommand{\vrad}{\ensuremath{v_\textrm{rad}}}
\newcommand{\ms}[1]{\ensuremath{M_{*{#1}}}}
\newcommand{\mud}{\ensuremath{\mu_\delta}}
\newcommand{\mua}{\ensuremath{\mu_\alpha^*}}
\newcommand{\bov}{\ensuremath{\boldsymbol{v}}}
\newcommand{\boldx}{\ensuremath{\boldsymbol{x}}}
\newcommand{\vtrav}{\ensuremath{\bov_{\rm travel}}}
\newcommand{\xtrav}{\ensuremath{\boldx_{\rm travel}}}
\newcommand{\pos}[2]{\ensuremath{\boldx_{\rm #1 \to #2}}}
\newcommand{\vel}[2]{\ensuremath{\bov_{\rm #1 \to #2}}}
\newcommand{\mwbary}{\ensuremath{\textrm{MW}_\textrm{bary}}}
\newcommand{\mwouter}{\ensuremath{\textrm{MW}_\textrm{halo}}}
\newcommand{\mwdisk}{\ensuremath{\textrm{MW}_\textrm{disk}}}
\newcommand{\reflabel}[1]{\ensuremath{^{\mbox{\scriptsize{#1}}}}}
\newcommand{\scsep}{\ensuremath{\rm r_{sep}/r_{vir}}}
\newcommand{\scvel}{\ensuremath{\rm v_{rel}/v_{vir}}}

% Style tweaks
% \renewcommand{\twocolumngrid}{\onecolumngrid}
% \setlength{\parindent}{1.1\baselineskip}
% \sloppy\sloppypar\raggedbottom\frenchspacing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\shorttitle{Frequency of galaxy pairs}
\shortauthors{Chamberlain et al.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{{./}{../plots/paper1/}}
\input{math_definitions.tex}

% Affiliations
\newcommand{\affuofa}{University of Arizona, 933 N. Cherry Ave,
    Tucson, AZ 85721, USA}

%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{
  Frequency of low and high mass galaxy pairs in the IllustrisTNG cosmological simulation
}

\author[0000-0001-8765-8670]{Katie~Chamberlain}
\affiliation{\affuofa}

\author[0000-0003-0715-2173]{Gurtina Besla}
\affiliation{\affuofa}

\begin{abstract}

  \todo{Name data sets and refer to their names }
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} \label{sec:intro}

\begin{itemize}
    \item Galaxy mergers are a feature of LCDM and support the growth of galaxies across cosmic time.
    \item The frequency of finding pairs tells us about how often we might expect: starbursts, SMBH mergers, the importance/role of mergers in building stellar mass/morphologies of galaxies today, SFHs, etc. 
    \item pair fraction at high masses has been well studied both obs and theoretically.
    \item in the era of jwst, these studies will be pushed to lower masses and high z, however, from a theory persp[ective, pair fractions at low masses have been under-studied (first 2 ish paragraphs ~ )
    \item in this study, we'll be quantifying the pair fraction of low mass pairs, and self consistently comparing to the pair fraction of high mass systems
    \item There are reasons to believe that high and low mass (Mstar = 1e8-5e9Msun) pairs might evolve differently, so it's important to study the low mass end too. 
    \item Also, major and minor mergers are important for different reasons, so studying them as separate systems is well motivated.
        - is major high mass vs major low mass different, etc since these two types of mass ratios lead to different things 
        - importance of mergers in high vs low mass galaxies (major mergers may be less important to SFH of Universe etc - look at sabrina's papers)
    \item Systematically understanding the underlying difference between low and high mass pairs, Projected vs. physical 3D separations/pairs Two routes of studying galaxy pairs are through observations and simulations, but simulations allow us to fully understand the 3D position and velocity of objects. 
    \item There are studies of high mass (Mstar = 5e9-1e11Msun) pairs. These studies are typically done in projection for comparison to observational campaigns.
    \item There are studies of low mass pairs, but only at low z, or as satellites of more massive systems (analogs of LG). 
    \item In this work, we aim to characterize the pair fraction of both high and low mass galaxies, major and minor pairs, consistently as a function of time. 
\end{itemize}
cite Stierwalt for low mass pairs 4485/4490 (iso vs non iso pairs) 
Pearson Besla 2016 
Pearson Besla 2018 4485/4490
Luber Pearson Besla 
Nevin

Discussion section: 
what does this mean for our understanding of the LG (isolated mass analogs) 
ngc 4490/4485 as another low z example (minor dwarf pair)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Methodology}\label{sec:methods}
We aim to quantify and characterize the frequency (or occurrence rate) and bulk kinematic properties of galaxy pairs in cosmological simulations as a function of cosmic time. 
In particular, we study dwarf galaxy pairs and massive galaxy pairs that are of similar stellar and halo mass to a variety of galaxy pairs in the Local Group. 
We categorize these pairs into one of four pair types: massive major pairs, such as the MW+M31; massive minor pairs, such as M31+M33 or MW+LMC; dwarf major pairs, such as M33+LMC; and finally, dwarf minor pairs, such as the LMC+SMC.
\kc{can maybe move these two sentences to a discussion section}

To this end, we utilize the IllustrisTNG simulations to select halo pairs at each snapshot according to a strict set of selection criteria as outlined in the remainder of this section. 
In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulation utilized in this study.
Sec.~\ref{sec:methods-halos} outlines the initial mass cuts used to define our full sample of halos, from which we will select pairs.
Sec.~\ref{sec:methods-am} outlines the abundance matching prescription we used to associate dark matter subhalos with stellar masses.
Sec.~\ref{sec:methods-pairs} describes the second set of selection criteria we apply to obtain the full sample of pairs.
Finally, Sec.~\ref{sec:pairprops} details some of the properties of our entire pair sample, including the total number of pairs and stellar mass ratios.

%%%%%%%%%%%%%%%%%%%%%%%
% Sim details section %
    \subsection{Simulation details} \label{sec:methods-sims}
        % Brief description of TNG hydro and which run we use.
    The \tng\ project ~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} consists of a suite of dark-matter-only $N$-body as well as full physics cosmological simulations consistent with the \textit{Planck2015} \lcdm\  cosmology~\citep{Planck2015}.
    In this study we utilize data from the main high resolution, full physics run of the (110.7\Mpc)$^3$ volume simulation, \textsl{TNG100-1}, which includes dark matter and baryons and follows the evolution of $1820^3$ dark matter particles in 100 snapshots from $z=127$ to $z=0$.

      % subfind, sublink, and groups and subhalos
    We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm~\citep{springel2001,dolag09}. 
    These catalogs consist of halos, defined using the Friends-of-Friends (FoF) algorithm~\citep{davis1985} to link nearby particles, and their associated subhalos, which are over-dense and gravitationally bound dark matter structures compared to the background. (From here, we will refer to FoF halos as "groups" and their subhalos as )
      % We also use merger catalogs generated by XX for YY purpose. 
    We also use merger trees provided by the \texttt{SUBLINK} algorithm~\citep{rg15}, which tracks subhalos between snapshots using their DM particle data, in order to trace subhalo mass growth and merger histories.

    The large volume of this simulation offers a large statistical sample of halos to study in a cosmological context, but is also high enough resolution ($m_{\rm DM} = 7.5\times10^6\Msun$, $m_{\rm gas} = 1.4\times10^6\Msun$) that dwarf halos ($\sim1\times10^{9-10.5}\Msun$) halos are resolved into roughly hundreds or more particles, well above the resolution limit of 32 DM particles for halos identified with \texttt{SUBFIND} \kc{fix this} 20 gas and star particles used to construct baryonic merger trees.

        %  this MIGHT go in a different section? am I talking about this because I want to show why we use hydro instead of dark? 
    Baryonic process are known to affect the structure and formation of dark matter halos of low mass ($M_*\lesssim 1\times10^9\Msun$) subhalos in simulations~\citep[see e.g.][and references therein]{Sales:2022}.
    Additionally, the shallow potential well of dwarf galaxies compared to their massive counterparts may lend themselves more easily to disruption from baryonic processes such as supernova feedback and reionization~\citep{}, resulting in fewer low mass halos ($\lesssim 5\times10^{10}$) in hydrodynamic simulations~\citep{vogelsberger14B}.
    % Thus, the number of primaries  we expect that our choice of simulation will result in 
% End sim details     %
%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%    
% Choosing halos section %
    \subsection{Choosing dwarf and massive halos in TNG} \label{sec:methods-halos}
    % start off with group selection 
        % brief explanation of FoF groups in sim
    Each snapshot from the TNG100 group catalogs consist of FoF groups, large halos of closely associated DM particles, and the subhalos they contain, which are smaller bound structures of DM and the gas and star particles nearest to them. 
    We will refer to these two structures as "groups" and either "halos" or "subhalos" respectively, from here on. 
    Galaxies form in these subhalos, so our pair sample will consist of pairs of subhalos within these larger group structures.

    \kc{be more prescriptive. }
    We are interested in the inherent dynamics and frequency of pairs of halos in the field.
    Thus, we want our pairs to consist of some of the most massive halos in each group, and ensure that the pair is not dynamically influenced by nearby massive groups. 
    By selecting pairs from the most massive halos of a group, a rough isolation criteria is inherent in our selection due to the nature of the FoF algorithm, which groups together nearby particles. 
    To confirm that our sample , we have confirmed that nearly 100\% of the most massive subhalos in each group are outside of the Hill radius of any nearby group or subhalo with greater mass.

    The first selection criteria that we invoke is a cut on the total group mass, $M_{G}$ (i.e., a mass cut on the FoF group mass, given by \texttt{Group\_M\_TopHat200} in the \tng\ group catalogs). 
    We define the group mass range for dwarf groups as $8\times 10^{10} < M_{G,d} < 5\times 10^{11}\Msun$
    %, which will host mass analogs of the LMC+SMC and LMC+M33 pairs. 
    Massive groups range from $1\times10^{12} < M_{G,m} < 6.5\times10^{12}$, which at the lower mass end will host MW+LMC pairs, and MW+M31 pairs at the higher mass end. 
    The group mass criteria is fixed for all redshifts, so at high z, the dwarf pairs we select may be the progenitors of higher mass systems at $z=0$.
    Note that all masses used in this analysis are physical units, such that masses from the group catalogs are divided by $h$ to get units of \Msun.

    Selecting dwarf pairs from the dwarf group mass range also ensures that we are not selecting satellite systems in the halos of more massive systems. 
    The LMC+SMC, for example, are highly perturbed by the influence of the MW, and thus we do not pick dwarf pairs from high mass groups that may contain large nearby MW-mass analogs.

        % explain what halos we will move forward with. 
    For each group that passes the group mass cut, we create a catalog of all subhalos that pass a ``current mass" criteria: the subhalo mass at the given snapshot (same snapshot) halo mass must be $M_h > 1\times10^{9}\Msun$ (the \texttt{SubhaloMass} field in the group catalogs).\footnote{Note that for the TNG100 hydro run, the halo mass is the total sum of all bound dark matter \textit{and} baryonic particles.}
    This lower mass threshold ensures that our halos are resolved into $>100$ particles, and thus should be robust to the SUBFIND and SUBLINK algorithms even at the lowest mass end.

    We then utilize the merger tree catalogs to determine the maximum halo mass ever achieved by each halo. 
    The set of all subhalos at each snapshot that pass the group mass and current mass cuts constitutes our entire subhalo sample. 
    From here, we will use further selection criteria to narrow our sample down to pairs.
    \kc{at this stage, this "Isolated Group" catalog contains XX }

% End choosing halos     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    
% Abundance matching section %
    \subsection{Abundance matching} \label{sec:methods-am}
        % what is abundance matching
    Abundance matching is a technique used to associate dark matter halo mass with specific galaxy properties.
    This allows us to associate dark matter halos from the \tng\ simulation with observationally motivated galaxy properties. % maybe observationally constrained, instead? 
    In particular, we will be utilizing a stellar mass to halo mass (SMHM) relationship to assign stellar masses to each of the subhalos in our sample.

    % few details about the msoter relationship. how was it determined?
        % why are we using abundance matching 
    The \tng100-1 subhalo catalogs do already contain a stellar mass field as computed in the simulation by simulating star formation and  AGN feedback, stellar feedback, galactic winds, etc.    
    However, there are a couple reasons we opt to assign stellar masses to our halos, rather than use those from the simulation.

    Primarily, applying an abundance matching prescription to assign stellar masses to each of the dark matter halos allows us to account for the observed spread in the stellar mass-halo mass relationship. 
    This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the spread in the SMHM function is large. 
    In addition, using stellar masses as calculated from abundance matching allows us to side step any simulation-dependent stellar mass effects.
    In the case of \tng100 specifically, it is known that the stellar masses of low mass galaxies are often overestimated compared to the galaxy luminosity function at the low mass end\cite{}. 
    Using an observationally-calibrated abundance matching prescription will thus lead to a more robust result for comparison with and predictions for observations. 
    Finally, utilizing an abundance matching prescription allows us to directly compare results between dark matter only and hydro simulations, since the stellar masses are assigned the same way. 
    We make brief note of results for our equivalent analysis using the dark matter only TNG100-1-Dark simulation as well in Sec.~\ref{sec:results}.

        % what am prescription are we using? 
    We use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic prescription to assign stellar masses to dark matter halos. 
    The~\citet{Moster2013} relationship is a function of the halo mass, evolves with redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.
    Additionally, stellar mass is defined separately for central halos (``hosts") and for infalling satellites (``subhalos"), where the first is a function of the virial mass of the halo and its redshift, $M_{vir}$ and $z$, and the second is a function of the mass and redshift at the time of infall, $M_{inf}$ and $z_{inf}$. 
    This assumes that the satellite halos are at the peak of their stellar mass before infall, and neglects the affect of star formation or stellar stripping within the host halo.

        % what do we use for the mass ~ 
    In this work, we will use the peak halo mass \Mpeak\ from the \sublink\ merger trees to calculate subhalo stellar masses. 
    \citet{Munshi2021} found that the stellar mass of subhalos at $z=0$ in the ``Marvel-ous Dwarfs" and ``DC Justice League" zoom simulations are more closely correlated with the peak halo mass ($M_{peak}$) than the $z=0$ halo mass for halos with peak halo mass $10^8<M_{\rm peak}<10^{11} \Msun$. 
    % separate citation for peak halo mass and stellar mass relatiosnhip for M > 1e11Msun 
    Using the peak halo mass additionally allows us to remain robust to scenarios in which a secondary has formed most of its stars, then loses a significant portion of its dark matter content through tidal interactions with a primary, but retains the bulk of its stellar content.

        % regarding the redshift dependence ~
    We additionally assume that the stellar mass of both the primary and secondary halo can change as a function of redshift after the secondary has entered the primary's halo and do not immediately cease star formation. 
    This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{geha13} which finds that dwarfs $>1\Mpc$ from a MW-type galaxy are often star forming and rarely quenched.
    Additionally, the SAGA survey has found that large satellites of MW-type galaxies are often very blue, with infall into the halo spurring high rates of star formation due to the large gas fraction in dwarfs~\citep{saga}. 
    Thus, we calculate stellar masses for our subhalos using $M_{\rm peak}$ and the redshift of the current snapshot to calculate the stellar mass of each subhalo, and to account for the additional stellar mass that can form after infall.

    As mentioned in a footnote in Sec.~\ref{sec:methods-halos}, the total halo mass of subhalos in the hydro simulation includes the mass of both dark matter and baryonic particles. 
    In TNG100-1, the DM particle mass is decreased XX\% compared to the DM particle mass in \tng100-1 Dark to account for the additional mass of baryons, such that the total mass of the halo will remain roughly the same between the dark matter only and hydro simulations. 
    Since the~\citet{Moster2013} AM relation was calibrated using DM subhalos from the \texttt{MilleniumII} dark matter only simulation, we will use the total subhalo mass from the TNG100-1 hydro simulation as a proxy for the corresponding DM halo mass in the TNG100-1 Dark run, \texttt{SubhaloMass}.

        % realizations? 
    For each subhalo at each snapshot in our full subhalo sample (see Sec.~\ref{sec:methods-halos}), we create a "realization" of the catalog for , 1000 stellar mass values from the SMHM relationship to account for the systematic uncertainty in subhalo stellar masses.
    Each realization is treated as an independent sample of galaxy stellar masses, which allows us to report realistic spreads of pair properties.
    Thus, we create 1000 separate pair catalogs, and compute pair properties (pair frequency, separations, etc) for each individual abundance matching realization.
    \kc{what is the name of this catalog? (Isolated Group cats + 1000 Stellar Mass) }

% End Abundance matching %
%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%    
% Pair selection section %
    \subsection{Pair selection}\label{sec:methods-pairs}
    The full pair sample is constructed from the set of all subhalos and their abundance matching realizations. Each pair will consist of a ``primary" more massive object, and a ``secondary" less massive companion. 
    \kc{We are starting with XX catalog, we'll sprinkle on some selection criteria, then store YY and ZZ. }

    % justify why we want to use stellar mass to define things
    %A majority of the literature uses the definition of "major" and "minor" pairs based on the stellar mass of the objects. This is true as well for observational pair samples, such as Lotz 2011, wherein the halo mass of the objects is unknown, and thus the stellar mass is used to define the mass ratio of the pair. In order to reproduce statistics that can be meaningfully compared to observations/can be used to inform observations, we opt to define our pair sample via the stellar masses from the abundance matching prescription given in Sec.~\ref{sec:methods-am}.

    %%% 
    % begin subsubsection
    \subsubsection{Selecting primaries}
        Primary galaxies (equivalently, ``primary subhalos") are the most massive galaxy of their group by stellar mass. Thus, each group can have at most one primary galaxy.

        We apply mass cuts on the stellar mass of the primary to define our sample of dwarf primaries and massive primaries. Each stellar mass realization is treated independently, such that the primary of a group may change between stellar mass realizations. Additionally, some groups may not have a ``primary" in one realization, but will in others. \kc{}

        For each stellar mass realization, we rank order the subhalos of each group by stellar mass, then perform a mass cut specific to the type of group: dwarf primaries from dwarf mass groups, and massive primaries from massive mass groups (see Sec.~\ref{sec:methods-halos} for group mass criteria). 
        We define the stellar mass range for dwarf primaries and massive primaries as:
        \begin{align*} 
        \mbox{\textbf{dwarf primaries:}}&\, 1\times 10^{8}< \rm M_{*} < 5\times10^{9}\Msun \\ 
        \mbox{\textbf{massive primaries:}}&\, 5\times 10^{9}< \rm M_{*} < 1\times 10^{11}\Msun.
        \end{align*}
        \kc{justification for this stellar mass range? LG relation to put into context these ranges }
        The primary stellar mass range is chosen to replicate a set of pairs with masses similar to LMC--SMC and MW--M31. \kc{remove "pairs"}

        The stellar mass criteria is fixed, and does not change as a function of redshift. 
        The median number of primaries in a single stellar mass realization at $z=0$ is XX dwarf primaries and XX massive primaries (see Sec.~\ref{sec:pairprops} for more info).

        The abundance matching prescription has a spread of $\sim 1$dex at $M_{h}\sim 10^{10}\Msun$~\citep{Moster2013},
        \kc{move to AM section}%thus the set of selected primaries in each realization is typically unique.

        % explain special cases that people might wonder about.
        %A subhalo will not be selected as a primary if it is not the first most massive halo in the group, i.e., there are no subhalos in the group that are more massive than the primary (by stellar mass). However, s
        Since our selection is based on stellar mass, and there is a large spread in the SMHM relation, the primary for any realization of the catalog may not be the most massive subhalo in terms of total subhalo mass. 
        %This is by design, since our selection criteria are meant to more closely replicate observational pair selection criteria which use the stellar mass ratio between the primary and companion to define a major or minor pair, rather than the DM halo mass.

    % end  primary subsubsection
    %%%

    %%% 
    % begin secondary subsubsection
    \subsubsection{Selecting secondary companions}
        The second most massive galaxy by stellar mass in each group is then used to define the secondary companion for each primary. 
        As before, the selection of secondary companions occurs independently for each stellar mass realization, and for each snapshot, such that the population of secondaries in each realization will have a different stellar mass distribution.
        %we collect 1000 different sets of pairs for each redshift.

    \subsubsection{To create the pair catalog,}
        We create two categories of pairs: 
        major pairs and minor pairs, such that the secondary companion galaxies are selected via the stellar mass ratio between the secondary and primary.     
        % Since we have already rank ordered the halos in each stellar mass realization by their stellar mass, the stellar mass ratio will never exceed 1.   
        The stellar mass ratio criteria for major and minor pairs are:
        \begin{align*} 
        \mbox{\textbf{major pair:}}&\, \frac{1}{4}\leq \frac{\rm M_{*2}}{\rm M_{*1}}< 1 \\ 
        \mbox{\textbf{minor pair:}}&\, \frac{1}{10}\leq \frac{\rm M_{*2}}{\rm M_{*1}} < \frac{1}{4}
        \end{align*}
        \kc{give the reason for this look at z0.png}

        \kc{For each pair we store the pair separation in physical units and relative velocity. We require that each pair have a minimum separation of $15 \kpc$ between the primary and secondary, which is XX times the smoothing length of the simulation. }
        \kc{need to explain how the separations and velocities are computed from the catalog etc. }
        At smaller separations, more and more mass will be attributed to the central subhalo, which can lead to confusion in the SUBFIND catalogs. %the merger tree histories. \kc{the }.

        If a primary subhalo does not have a companion that meets the stellar mass ratio criteria, separation criteria, or lower subhalo mass criteria (see Sec.~\ref{sec:methods-halos}), the subhalo will still be considered a primary. 
        We refer to all primaries without companions as ``isolated primaries."
        \kc{move this down to the secondary section}
        If a subhalo passes the stellar mass cut for a primary, but does not have an associated companion from the selection criteria for a secondary (see next subsection), the subhalo will still be considered a primary. We refer to all primaries without companions as ``isolated primaries."
        The total set of primaries includes both paired primaries and isolated primaries.

        The pair catalog contains blah blah blah. 
        1000 sets of pairs at each snapshot blah blah

        The pair sample consists of 1000 sets of pairs at each snapshot, each set representing a different realization of the abundance matching prescription. 
        At each snapshot, we calculate the median occurrence rate and kinematic values for each of the 1000 realizations. 
        Each of the following plots shows the parameter's median and percentile spread calculated from the set of 1000 medians from each realization.

        how do we use these catalogs? Interested in the aggregate properties of the full sample, and so we will treat blah blah

    % end secondary subsubsection
    %%%     
% Pair selection end %
%%%%%%%%%%%%%%%%%%%%%%

% Methods end %
%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
% begin pair prop plots %  
\begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{counts_1000.png}
    \caption{(Top) Median number of dwarf (left) and massive (right) primaries and pairs as a function of redshift.
    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations, as described in Sec.~\ref{sec:results}.
    There are approximately 8 times as many dwarf primaries as massive primaries. 
    % dwarf galaxies
    The dwarf primary count (solid) is at a minimum at $z=4$, rises to a maximum by $z\sim1$, then decreases from $z=1\to0$. 
    The dwarf pair count (dashed) peaks at $z\sim2$.
    % Massive galaxies (right)
    The massive primary count (pink solid line in top right panel) behaves similarly to the dwarf primary count, with a minimum count at $z=4$ which rises to a maximum of $\sim2000$ halos per realization at $z\sim1$, then decreases slightly by $\sim5\%$ to $\sim$1800 halos by $z=0$. 
    Unlike dwarf pairs whose pair count peaks at $z=2$, pair count for massive galaxies (pink dashed line) follows similar behavior to the total massive primary count, with a minimum at $z=4$, and increasing to $z=\sim 1$ before leveling off. At very low redshift, the pair count and primary count have opposite behavior, with the pair count \textit{increasing} at very low redshifts of $z=0-0.25$ and \textit{peaking} at $z=0$.
    \kc{where does it peak and what is }
    (Bottom) Fraction of pairs per primary as a function of redshift (i.e., the ratio between dotted line and solid line in each column). Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$. The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.}
    \label{fig:counts}
\end{figure*}

\begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{smrdist_1000.png}
    \caption{\kc{using all 1000 realizations - combined sample of XX catalog} Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs. Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$. Overall, the stellar mass ratio distribution of major and minor pairs of dwarf and massive galaxies show little evolution from $z=4$ (right) to $z=0$ (left). 
    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.}
    \label{fig:massratio}
\end{figure*}
% end pair prop plots %  
%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
% Pair prop. start %
\section{Sample: Overview of pair properties} \label{sec:pairprops}
    Utilizing the pair catalog, We compute the # of prims in each realization of the 
    The full pair sample contains 1000 individual sets of pairs at each snapshot, for all 100 snapshots of the \tng100-1 simulation.

    Fig.~\ref{fig:counts} shows the redshift evolution of the median number of dwarf and massive primaries and pairs we identify over the redshift range $z=0-4$.   
    For each snapshot, we calculate the median number of primaries and of pairs in each realization within the Pair Catalog, yielding a set of 1000 medians. 
    The solid line and dashed lines are the median of this set of 1000 medians, and the shaded regions show the 1-99\% spread of the set.

    The number of identified primaries is smallest at $z=4$, and rises to a maximum around $z=1$ for both dwarf and massive primaries.        
    There are approximately 8 times as many dwarf primaries as massive primaries.

    The median dwarf primary count (green solid line in top left panel) reaches a maximum of $\sim15000$ halos at $z\sim0.6$, then decreases by $\sim16\%$ to 12000 halos at $z=0$. 
    The dwarf pair count (green dashed line) peaks much earlier at $z\sim2$ with $\sim3000$ pairs, and decreases to $\sim1000$ pairs at $z=0$.
    From $z=4$ to $z=2$, the number of dwarf primaries doubles, as does the number of pairs due to the growth of structures over cosmic time.
    The massive primary count (pink solid line in top right panel) reaches a maximum median of $\sim2000$ halos (in one realization) at $z\sim1$, then remains approximately constant to $z=0$. 
    The pair count for massive galaxies (pink dashed line) behaves similarly to the primary count, increasing from $z=4$ to $z\sim1$, then leveling off to $z=0$.

    The bottom panel of Fig.~\ref{fig:counts} shows the number of pairs divided by the number of primaries, or the fraction of pairs per primary as a function of redshift. 
    Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$. The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.

    include all 1000 realizations as a single "Combined Sample"
    We show the distribution of stellar mass ratios between the secondary and primary of each dwarf and massive pair in Fig.~\ref{fig:massratio} from the Pair Catalog, com 
    \kc{explain how we compute this}
    all realizations.
    % Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.
    In general, the shape of the distribution remains constant from $z=0-4$ for both dwarfs and massive pairs, and between the dwarf and massive pairs at each redshift. 
    Thus, the typical stellar mass ratio of pairs in our sample is independent of mass scale and of redshift. \kc{how much more likely are you to find 1/4 than 1:1 things? what about 1:10 to 1:4?}

% Pair prop. end %
%%%%%%%%%%%%%%%%%%

% \begin{table*}[htb]
%   \centering
%     \begin{tabular}{lcc}
%      & Dwarf Pairs & Massive Pairs \\\hline\hline
%     % Group Mass & $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ & $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$  \\
%     % Subhalo Max Mass &  &  \\
%     % Subhalo Current Mass & $>1\times10^{10} \Msun$ & $> 5\times10^{11} \Msun$ \\
%     Primary &$1\times10^{8} < \msam < 5\times10^{9} \Msun$ & $5\times10^{9} < \msam < 1\times10^{11} \Msun$\\\hline
%     \end{tabular}
%     \caption{\label{table:mass}Selection criteria for dwarf and massive pairs.}
%     \end{table*}

% equivalent snapshot table
% \begin{table*}[tbp]
%   \centering
%   \begin{tabular}{l|cc|cccc} % increase this to 7 columns
%     \hline \hline
%    & {Snapshot} & {Number of primaries} & {Number of pairs}\\
%    & \ill & \tng  & \illd & \illh & \tngd & \tngh \\ 
%   \hline
%   z = 0   &   135  &   99   & $11431.5_{-24.42}^{68.38}$ & $12650.0_{-25.84}^{46.84}$ & $13255.0_{-32.60}^{56.72}$ & $12035.0_{-69.24}^{20.36}$\\
%   z = 1   &   85   &   50   &  $14769.0_{-30.24}^{47.28}$ & $16568.0_{-32.20}^{69.60}$ & $17445.5_{-40.86}^{51.90}$ & $15946.5_{-59.38}^{39.22}$ \\
%   z = 2   &   68   &   33   &  $12602.5_{-31.98}^{45.94}$ & $14174.0_{-12.48}^{62.32}$ & $15413.5_{-34.62}^{28.86}$ & $14334.0_{-29.44}^{45.24}$ \\
%   z = 3   &   60   &   25   &     $8533.5_{-54.50}^{39.46}$ & $9390.0_{-63.40}^{41.32}$ & $10901.0_{-44.64}^{46.56}$ & $10106.5_{-47.90}^{39.74}$  \\
%   % z = 3.7   &   54   &   21   \\
%   \hline \hline
%   \end{tabular}
%   \caption{\label{tab:equiv-snapshot} The snapshot number of the original \ill\ and the \tng\ simulations at redshifts $z=0-3$, as well as the median number dwarf (massive) primaries that were selected with $1\times 10^{8} < \msam < 5\times 10^{9} \rm M_\odot$ ($5\times 10^{9} < \msam < 1\times 10^{11} \rm M_\odot$) in XX abundance matching realizations. \kc{fill in with numbers after doing more realizations} \kc{include takeaway}}
%   \end{table*}

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
% Begin Results section %

\section{Results: The frequency and kinematics of dwarf and massive pairs}
We have created catalogs of isolated low and high mass galaxy pairs from $z=0-4$ in the TNG100-1 simulation. 
In this section, we will analyze the occurrence rate and kinematic properties (physical separations and relative velocities) for major and minor pair types across cosmic time.

In Sec.~\ref{sec:results-frac}, we show the redshift evolution of the fraction of primaries with a major or minor companion (the ``pair fraction") and compare the results for dwarf pairs and massive pairs.
In Sec.~\ref{sec:results-kinematics}, we look at the redshift evolution of the separations and relative velocities between primary and secondary halos of each pair. % need to specify this is snapshot by snapshot?
In Sec.~\ref{sec:results-scaled}, we compare the separations and velocities scaled by the FoF group's virial properties. 
Finally, in Sec.~\ref{sec:results-virialcut}, we take subsets of the Pair Catalog, selecting only pairs within some fraction of the virial radius, and illustrate the impact on the recovered low and high mass pair fractions.

%%%%%%%%%%%%%%%%%%%%%   
% Definitions start %
% \subsection{Definitions} \label{sec:results-defs}

% Definitions end %
%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
% Pair fraction section %
    \subsection{Pair fraction}\label{sec:results-frac}
    We determine the occurrence rate of a pair type by calculating the pair fraction. 
    The pair fraction is defined here as the ratio of the number of pairs to the total number of primaries (isolated + paired):
    $$\rm \frac{N_{pair-type}}{N_{primaries}}.$$
    For example, the dwarf major pair fraction is calculated as the number of dwarf major pairs divided by the number of dwarf primaries. 
    The pair fraction of dwarf or massive pairs with a major or minor companion gives the likelihood of finding a companion of a certain mass type about a primary identified in the field.

    Fig.~\ref{fig:pairratio} shows the pair fractions calculated for massive and dwarf pairs (including both major and minor pairs separately) as a function of time for $z=0-4$. 
        % differences between massive and dwarf pairs? 
    The dwarf pair fraction evolves distinctly from that of massive pairs.
    Dwarf pair fractions (both major and minor) start at their minima at $z=0$, and increase by about 200\% by $z\sim2-2.5$, at which point the pair fractions level off and remain constant from $z=3-4$. 
    On the other hand, massive pair fractions reach their maxima at $z=0$, then abruptly declining to $z\sim0.25$, before remaining approximately constant from $z=1-4$.

        % difference panels
    The bottom panels of Fig.~\ref{fig:pairratio} shows the dwarf pair fraction subtracted from the massive pair fraction (labelled ``$\rm M-D$"). 
    The pair fraction difference reaches a maximum at $z=0$ for both major and minor pairs, and declines to $z\sim2-2.5$ at which point the difference levels out close to 0, where major dwarf and massive pairs, as well as minor dwarf and massive, are equivalently common.

        % differences between major and minor pairs? 
    The median pair fraction of minor pairs is less than that of major pairs of the same mass range at all redshifts. 
    This is due to the lower stellar mass ratio limit we put on our pairs. 
    Expanding the mass ratio criteria of our minor pair sample to include stellar mass ratios between 1/10-1/100 in our minor pair sample increases the fraction of minor pairs by a factor of $>2$ for massive pairs and between $~1.5-2x$ for dwarf pairs. \kc{are there any additional takeaways from this? }

        % what do we learn from this? what are the takeaways? where do we discuss this in more detail?
    Overall, these results show that massive and dwarf pair counts evolve differently over time, particularly at very low redshift, despite the pair fractions being roughly equal at higher z. 
    These differences could be a result of the different formation mechanisms at play in the evolution of the systems at these two different mass scales, or alternatively, from differences in satellite dynamics between dwarf and massive systems (see Sec.~\ref{sec:results-kinematics}). 
    The implications for the difference in the evolution of pair fractions for dwarf and massive pairs across time is discussed in detail in Sec.~\ref{sec:discussion}.

        % pair fraction plot
    \label{sec:results}
    \begin{figure*}[htp]
      \centering
      \includegraphics[width=\textwidth]{pairfrac_1000.png}
      \caption{
        % Top plots ~
        (Top) Median pair fraction, defined as the fraction of dwarf or massive primaries with a major (solid) or minor (dashed) companion by stellar mass (see Sec.~\ref{sec:methods-pairs}). 
        Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
          % massive pairs
        The massive pair fraction (pink) remains approximately constant for $z>1$, with an average pair fraction of 0.16-0.17 for major pairs and 0.14-0.15 for minor pairs. Between $z=0.25$ and $z=0$, the massive major pair fraction increases to 0.207, while the minor pair fraction increases to 0.152.
          % dwarf pairs
        Dwarf pair fractions, shown in green, are approximately constant from $z=3-4$, then decline monotonically to $z=0$. The major pair fraction is $0.041$ at $z=0$ and $0.126$ at $z=3$, while the minor pair fractions are $0.034$ and $0.111$ at $z=0$ and $z=3$, respectively. 
        % Bottom plots ~
        (Bottom) The median subtracted (massive - dwarf) pair fraction difference, with the shaded $1$-$99$ percentile range from 1000 abundance matching realizations. The pair fraction difference increases with decreasing redshift, peaking at $z=0$ with a difference of 0.166 for major pairs and 0.111 for minor pairs. This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly at low redshift.}
      \label{fig:pairratio}
    \end{figure*}
% end pair fraction 
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% beging Kinematics results %
    \subsection{Kinematic evolution}\label{sec:results-kinematics}
    We also analyze the kinematic behavior of our pair sample as a function of time. 
    Instantaneous pair separations are defined as the relative separation between the primary and secondary of each pair in the snapshot, and are computed in physical $\kpc$, and \textit{not} in comoving $\kpc/h$. 
    Similarly, relative velocities are defined as the relative velocity difference in the same snapshot between the primary and secondary of each pair, and are computed in physical $\kms$.

    In this section, we compute the median relative separations and velocities of all pairs in each snapshot, each of which includes the set of pairs from 1000 stellar mass realizations.
    We separate the population of dwarf and massive pairs further into major and minor pairs to show how the stellar mass ratio between the primary and secondary may affect the kinematics.

    % separations %
        \subsubsection{Separations}
        %% text on separation vs. redshift plot
        %% intro to separations & bulk results
        % We calculate the median relative separations between the primary and secondary halos of the pairs identified in our dwarf pair sample and massive pair sample. 
        % We split the results by the stellar mass ratio of each pair, dividing the sample into "major" pairs and minor pairs, which allows us to compare the behavior of different mass ratio systems individually in the dwarf and massive mass range.
        Our results are 
        illustrated in Fig.~\ref{fig:sep}, which shows the redshift evolution of the median relative separations for dwarf pairs and massive pairs. 
        %% the behavior of massive and dwarf pairs
        We show that the median relative separations between the primary and secondary of both dwarf and massive pairs increases with decreasing redshift, regardless of pair type. 
        A combination of physical mechanisms is likely spurring the increase in median pair separations at low $z$. 
        For example, high $z$, low separation pairs may undergo mergers at earlier times, removing them from the sample at later snapshots, thus increasing the median separation over time. 
        Alternatively, mass accretion, from the cosmic web and/or from mergers, causes dark matter halos to become both more massive and more extended as $z\to0$. 
        Thus, the growth of structure that is expected in $\Lambda$CDM could naturally lead to an increase in typical pair separations at low $z$.
        We explore the relationship between halo growth and relative pair separations in Sec.~\ref{sec:results-scaled}.

        %% the DIFFERENCE between dwarf and massive pairs
        Dwarf and massive pairs exhibit similar relative separation trends as a function of time, however, the scale of the typical relative separations of pairs in our sample is set by the mass halo of the primary.
        Dwarf pairs and massive pairs have a relative separation difference of $\sim150\kpc$ at $z=0$, and a difference of $\sim40$ at $z=4$.   
        This is expected, as more massive halos have larger spheres of influence and more substructure. 
        \kc{maybe move this sentence to discussion:}But, the difference between dwarf and massive pair relative separation ranges, and their evolution over time begs the question: what does this mean for observational pair selection criteria at different mass scales and at different redshifts? 
        We leave the discussion of the implications our relative separation results on pair selection criteria for Sec.~\ref{sec:discussion}.

        %% the difference between major and minor pairs
        In addition, the bottom panels of Fig.~\ref{fig:sep} shows the median subtracted difference between the relative separations calculated for major pairs and minor pairs of both mass types. 
        There is a small offset in the median separations of major and minor dwarf pairs (between $10-25\,\kpc$ from  $z=0-1$ and approximately $5\,\kpc$ from $z=1-4$), and a larger offset for major and minor massive pairs (between $25-100\,\kpc$ from  $z=0-1$ and approximately $10-40\,\kpc$ from $z=1-4$). 
        The major-minor offset is likely a result of more major pairs merging more quickly (thus at earlier times and higher $z$) due to the increased effect of dynamical friction, thus leading to a population of low relative separation minor pairs that have yet to merge.

        %% separation plots
        \begin{figure*}[htp]
          \centering
          \includegraphics[width=\textwidth]{sep_1000.png}
          \caption{(Top) Median physical separation in kpc between the primary and secondary halos of dwarf pairs (left) and massive pairs (right) as a function of redshift. 
          Shaded areas show the 1-99\% percentile range of the median from 1000 abundance matching realizations. 
          Major pairs are shown in solid lines, and minor pairs are depicted with dashed lines.
          In general, for both dwarf pairs and massive pairs, the average physical separation of the two halos in a pair increases for as the redshift decreases from $z=4\to0$. 
          % Dwarf pairs
          The typical separation between major (minor) dwarf pairs increases from $42(38)\,\kpc$ at $z=4$ to a peak of $128(109)\,\kpc$ at $z=0$.
          % Massive Pairs
          The separation between major (minor) massive pairs likewise increases from $81(71)\,\kpc$ at $z=4$ to $288(205)\,\kpc$ at  $z=0$.
          % Difference plots
          (Bottom) The median difference and 1-99\% range (as above) between the median separation of major pairs and minor pairs.
          At dwarf mass scales, minor companions tend to be $\sim10-20\kpc$ closer to their primary than major companions, while minor massive pairs have a relative separation that is $10-50\kpc$ less than major pairs.
            }
          \label{fig:sep}
        \end{figure*}

    % velocities %
        \subsubsection{Relative Velocities}
        %% text on velocity vs. redshift plot
        %% intro to velocity & bulk results
        % In addition to the separations between the primary and secondary halos of our pair sample, we also calculate the median relative velocity between the halos of each pair.
        % Once again we split the results into "major" and "minor" pairs for both the dwarf and massive pair sample to get a better understanding of the impact of the mass of the secondary. 
        In Fig.~\ref{fig:vel}, we show the median relative velocity between the primary and secondary halos of dwarf and massive pairs as a function of redshift. 
        %% the behavior of massive and dwarf pairs
        We find that the median relative velocity of a pair decreases towards lower redshift, regardless of pair type.
        The median velocity of a major dwarf pair decreases linearly from $130$ at $z=4$ to $70\,\kms$ at $z=0$. Likewise, the median velocity for major massive pairs decreases from $260$ at $z=4$ to $170\,\kms$ at $z=0$, though with more spread at high $z$.
        \todo{} As the circular velocity of a secondary object about the primary is inversely proportional to the radius, it is not surprising to find a decrease in the relative velocity for pairs at lower redshift due to the decrease in concentration/increase in the virial radius of the halo as $z\to0$. \kc{citation needed}
        See Sec.~\ref{sec:results-scaled} for more details.

        %% the DIFFERENCE between dwarf and massive pairs
        As in the case of relative separations of pairs, dwarf and massive pairs show a similar evolutionary trend in relative velocity as a function of redshift, though at different scales determined by the mass of the primary.
        Massive pairs have a median relative velocity $\sim100\kms$ larger than dwarf pairs at $z=0$, and $\sim140\kms$ at $z=4$. \kc{see comment}
        %This is also not particularly surprising, since the circular velocity prop to $( M/r)^1/2,$, and massive primaries may be >10x as massive as dwarf primaries, while the separation between a massive primary and it's secondary will only be 2x further than a dwarf pair.

        %% the difference between major and minor pairs
        Fig.~\ref{fig:vel} also includes a panel showing the subtracted median difference at each snapshot of the minor pair from the major pair. Unlike the relative separation, the relative velocities do not have a strong dependence on mass ratio of the pairs. 
        The offsets between the relative velocities of dwarf major and minor pairs is between $0-5\,\kms$, and between $0-25\,\kms$ for massive major and minor pairs. \kc{see comment} %does it make sense that minor pairs are faster?

        %% velocity plots 
        \begin{figure*}[htp]
          \centering
          \includegraphics[width=\textwidth]{vel_1000.png}
          \caption{
            (Top) Median relative velocity (in \kms) between the primary and secondary halos of dwarf pairs (left) and massive pairs (right) as a function of redshift. 
            Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
            The overall behavior of the redshift evolution of pair relative velocities is nearly identical for dwarf and massive pairs.
            As the redshift decreases from $z=4$ to $z=0$, the average relative velocity of a pair decreases for both dwarf and massive pairs.
            % brief describe
            The median relative velocity of a dwarf pair (major or minor) is $70\,\kms$ at $z=0$ and $133\,\kms$ at $z=4$, and of a massive pair is $170\,\kms$ at $z=0$ and $260\,\kms$ at $z=4$ ($295\,\kms$ for a minor pair at $z=4$). 
            % Difference plot
            (Bottom) The median relative velocity difference between major and minor pairs ("Maj - Min"), and 1-99\% shaded region.
            There is little difference between the relative velocity of major and minor dwarf pairs (bottom left), with minor pairs having a relative velocity of $0-5\,\kms$ higher than major pairs. 
            Massive pair types (bottom right) also have little velocity difference at low redshift, although minor pairs have a relative velocity between $1-20\,\kms$ faster than major pairs at higher redshift ($z>\sim 2.5$).
            }
          \label{fig:vel}
        \end{figure*}
% end kinematic results %        
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%
% begin scaled results %
    \subsection{Scaled Kinematics}\label{sec:results-scaled}
    %% intro to scaled kin. evolution & bulk results
    In the previous section, Sec.~\ref{sec:results-kinematics}, we show that the separations and relative velocities of dwarf and massive pairs evolve similarly as a function of redshift. 
    However, the magnitude of pair separations and velocities are set by the mass scale of the pair. 
    For example, a dwarf pair at $z=0$ has a median relative velocity of $70\kms$, while a massive pair will have a median velocity of $175\kms$ at $z=0$.

    To explore the impact of halo growth and mass scale the kinematics pairs, we study the relative separation of a primary and secondary halo scaled by the virial radius ($r_{vir}$) of the FoF group, and the relative velocity ($v_{vir}$) divided by the circular speed of the FoF group at the virial radius. 
    That is, 
    $$\rm r_{scaled}=\scsep$$
    $$\rm v_{scaled}=\scvel$$
    $$\rm v_{vir}=\sqrt{G M_{vir}/r_{vir}},$$
    where $\rm r_{vir}$ is the group radius \texttt{Group\_R\_TopHat200} in physical $\kpc$ from the group catalogs, and $\rm M_{vir}$ the total group mass \texttt{Group\_M\_TopHat200} in $\Msun$.

    In Fig.~\ref{fig:scaled}, we show the median scaled separation and scaled velocity for dwarf and massive major pairs as a function of time. 
    Minor pairs show the same trends, and so we have omitted them here for brevity.

    %% the behavior of massive and dwarf pairs
    Overall, the median scaled separation of dwarf pairs and massive pairs do not evolve significantly differently from $z=4\to0$.
    In fact, the median separation of halos in a pair is smaller than the group virial radius at $z<2.5$, but is larger than the virial radius at $z>2.5$.
    %maybe not bound at high z, though could become bound by low z by mass accretion ? 
    Dwarf pairs tend to have slightly larger separations relative to the group virial radius than massive pairs at almost all redshifts, though the spread of median scaled separations is large for massive pairs at $z>2$.

    The median scaled velocities of dwarf pairs and massive pairs increase at lower redshift (see right panel of Fig.~\ref{fig:scaled}). In fact, dwarf and massive pairs evolve almost identically for $z=0-4$, and thus, the redshift evolution of a pair at either of these mass scales is independent of the total mass of the system. 
    We also find that pairs at $z<0.5$ have relative velocities in excess of their virial velocity, but are smaller than the virial velocity for $z=0.5-4$.

    %% distributions of scaled kinematics
    In Fig.~\ref{fig:scaled-dist}, we show the distribution of scaled separations and velocities at redshifts $z=0,1,2,3,4$. 
    The distributions show roughly equivalent shape and extent for both dwarf and massive scaled kinematics, and do not vary significantly with redshift.

    % behavior of massive vs. dwarf 
    Overall, our results imply that there is little difference between high mass and low mass pairs in the redshift evolution of pair velocities, though pair separations seem to have a weak dependence at low redshift on the type of pair. Inner regions of the halo , high mass pairs tend to be even closer, likely due to 
    This appears opposite to the physical separations, but when you scale to the total mass of the system, the 
    Fof groups are increasng in size . \todo{}

    %% scaled evolution plot
    \begin{figure*}[htp]
      \centering
      \includegraphics[width=\textwidth]{scaledcombo_1000.png}
      \caption{ \label{fig:scaled}
          %  Left
          (Left) Median scaled separation as a function of redshift (see Sec.~\ref{sec:methods} for the definitions of scaled separation and velocity). All shaded regions show $X-XX\%$ percentile spread from 1000 abundance matching realizations. 
          % any overall trends?
          At $z>2$, a majority of all pair types have separations greater than the group virial radius, while at $z<2$, a majority of pairs have smaller separations.  
          Massive major pairs at low redshift tend to have slight smaller scaled separations than dwarfs at $z<\sim2$, but vary significantly at higher redshifts. 
          % Right 
          (Right) Median scaled velocity as a function of redshift.
          % any overall trends?
          All pairs show a peak in scaled velocity around $z=0$. From $z=0-0.5$, a majority of both dwarf and massive pairs have relative velocities larger than the circular velocity of their group at the virial radius. At $z>0.5$, however, the majority of pairs have $v_{rel}<v_{vir}$. The scaled velocity evolves nearly identically for dwarf and massive pairs.
          % Bottom 
          (Bottom) The scaled separation/velocity of dwarf major pairs subtracted from that of massive major pairs, indicated by ``M-D".
          The scaled separation difference shows small differences between the dwarf and massive population, with dwarf pairs having slightly higher scaled separation for $z<1$. The scaled velocity difference is $\sim0$ at all redshifts.
          Minor pairs (not shown here) follow the same trends as major pairs in both the massive and dwarf regime.}
    \end{figure*}

    %% scaled distribution plot
    \begin{figure*}[htp]
      \centering
      \includegraphics[width=\textwidth]{scaledcombodist_1000.png}
      \caption{
          Scaled separation distribution (left) and scaled velocity distribution (right) at $z=0,1,2,3$, and $4$, normalized by the total number of pairs at the corresponding redshift. 
          % the point? what am I trying to get across
          The first thing to note is that there is relatively little redshift-dependent change in the overall shape and extent of each distribution, and thus the scaled quantities are only loosely independent of redshift. 
          Additionally, the shape and extent of the dwarf pair (top) and the massive pair (bottom) distributions are nearly identical, thus the scaled quantities are also independent of the halo mass scale. Thus, the kinematics of dwarf pairs and massive pairs evolve roughly equivalently when normalizing by the halo mass.
          Unscaled versions of this plot are discussed in Sec.~\ref{sec:discussion}.
      }
      \label{fig:scaled-dist}
    \end{figure*} 
% end scaled results %
%%%%%%%%%%%%%%%%%%%%%%

% end kinematics %
%%%%%%%%%%%%%%%%%%

\subsection{Separation cuts as fxn of virial radius}
put in plots~ 
% end Results section%
%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Begin Discussion section %
\section{Discussion}\label{sec:discussion}
\subsection{Implications for the differences in pair fractions of dwarf and massive pairs}
In Sec.~\ref{sec:results-frac}, we presented the pair fraction of massive and dwarf galaxy pairs and found that the relative frequency of the two populations evolve distinctly from $z=0-4$. 
While the frequency of massive pairs compared to the number of massive primaries is roughly constant and become more common at low redshift, dwarf major and minor pairs become more than 50\% less common at $z=0$ compared to $z=2$. 
Since scaled separations and velocities do not change drastically between dwarf and massive pairs, the difference in the evolution of the pair fractions indicates that the merger processes of each population may proceed differently.

% One scenario that could explain this behavior is a very rapid merger timescale for dwarf pairs, and a slower merger timescale for massive pairs. 
% In this case, dwarf pairs will merge quickly after formation, thus depleting the number of dwarf pairs at later times. 
% Simultaneously, the merged remnant of a dwarf pair is likely to join the population of isolated primaries until star formation finally pushes the stellar mass up into the massive primary regime.
% The likelihood of a dwarf pair becoming a massive primary with a minor companion is very small, since only XX\% of dwarf pairs have a major tertiary companion. \kc{calculate the number of }

% Alternatively, if the dark matter halo and stellar mass of a dwarf galaxy pair increase enough through cosmic accretion or very minor mergers from $z=4$ to $z=2$, the pair will be reclassified as a massive pair at later times.

For example, dwarf galaxy merger timescales may be significantly shorter than massive galaxy merger timescales, which would deplete the population of dwarf galaxy pairs by low redshift. 
Additionally, early dwarf galaxy mergers may result in systems that are identified as massive pairs at late times, and massive pairs may grow such that they exceed our mass criteria, thus leading to an apparent overall decrease in the number of pairs. 
The drop in the absolute number of dwarf and massive primaries at low z as shown in Fig.~\ref{fig:counts} indicates that indeed many of these systems leave the mass range specified by our selection criteria between $z=0-1$. 
However, since the number of dwarf primaries is roughly constant between $z=0.5-1.5$, but the number of pairs is still decreasing during this time, this indicates that mergers are occurring during this time, and not yet leaving the mass regime specified. 
In fact, the number of dwarf pairs that are removed from the sample from $z=0$ to $z=2$ is 10 times greater than the total number of massive pairs, indicating that these pairs are not simply accreting matter and moving into the higher mass bin.

\subsection{Comparison to previous pair fraction studies}
We performed a pair fraction analysis for dwarf and massive galaxy pairs in the TNG100 simulation, utilizing the full 6D position and velocity information that simulations enable. 
However this means that direct comparison to pair fractions reported from observations is not straight-forward, as observationally selected pairs uniquely suffer from contamination, due to projected pairs, and restrictive separation criteria, that exclude more widely separated pairs. 
Fortunately, a number of previous studies of pair fractions in the Illustris simulations have used lightcones to create mock images of observationally-motivated fields, from which they select pairs in the same fashion that is typically done with observational data.
These studies select simulated galaxies based on stellar mass, and then use cuts on the projected separation and line of sight velocity difference to select pairs, which permits direct comparison between simulations and observations.

At the low mass end, \citet{Besla2018} quantified dwarf galaxy pair fractions in Illustris-1, both projected and physical pairs, which enabled a direct comparison of the cosmologically-derived pair fractions with an equivalently selected dwarf pair fraction from SDSS.  
The pair selection criteria for dwarf galaxies, here defined as stellar masses\footnote{The stellar masses of galaxies from the Illustris simulations used in \citet{Besla2018} are from the median of the \citet{Moster2013} abundance matching prescription, the same as used in this work, rather than the stellar mass values from the simulations.} from $2\times10^{8} < M_{*} < 5\times10^{9}\,\Msun$, include a projected separation criteria of $r_{p} < 150\,\kpc$ and a relative line-of-sight velocity difference $\Delta v_{\rm los} < 150\,\kms$.

By searching for pairs in a projected space while having access to the true 3D positions and velocities of the galaxies, they quantified the contamination fraction and found that up to $\sim40$\% of identified companions were unrelated but appeared to be close due to projection effects. 
In Illustris, they found that the projected major pair fraction of dwarf galaxies at $z\sim0$ is $f_{p,proj.}\sim0.005-0.012$, while the . \kc{where tf are these numbers from??? }
The total pair fraction (including all stellar mass ratios) is $0.032\pm0.005$ for the projected mock catalogs, which are consistent with SDSS equivalently-selected pairs, which find a total pair fraction of $0.035\pm0.3$.

However, using the full physical catalogs, they find a lower pair fraction of $0.02\pm0.004$. \kc{I *THINK* this is the fraction of TOTAL pairs (N\_1 from the tables)? not just major pairs? otherwise I don't know how it's different.}
For comparison, when we modify our pair selection criteria to match those of \citet{Besla2018}, and require a physical separation $r_{\rm sep}< 150\,\kms$ and a 3D relative velocity $\Delta v_{\rm los} < 150\,\kms$, we find a dwarf major pair fraction of XX at $z=0$, which is slightly SKZ than the \citet{Besla2018} results.
This is/is not surprising because SKZ.

As the behavior of the major pair fraction as a function of primary stellar mass is consistent between the projected mock catalogs and the SDSS catalogs, they conclude that cosmological simulations can be used to reliably constrain observational pair fractions of dwarf mergers across time. \kc{across time... is this true?} 
Additionally, which projected and physical pair catalogs yield different absolute values of pair fractions, their behavioral trends as a function of mass are nearly identical such that, in terms of trends, projected and physical pair fractions will yield similar results.

% While the study uses projected separations and line of sight velocities, we can assume that the same \textit{trends} are valid for full-6D selected pairs, such that our pair fraction trends can be reasonably compared to those in observations.

Separate studies have analyzed the pair fractions of higher mass galaxies in Illustris simulation. 
In particular, \citet{snyder2017} created mock catalogs using lightcones in the Illustris-1 simulation to pick pairs in the same fashion as done in observations. 
Specifically, they consider only major pairs with: $1\times 10^{11}>M_{*,1} >1\times 10^{10.5}Msun$, projected distances between $14\kpc-71\kpc$, and a redshift separation of $\Delta z<0.02(1+z_{pri}$, which corresponds to a velocity separation of $<1.8\time10^4\kms$. 
They find that the major pair fraction for primaries with stellar mass $1\times 10^{10.5-11}Msun$ is constant or decreasing for $z>1$. 
Additionally, they compared to observational studies \kc{what studies} that selected pairs with stellar mass $(M* > 10^{10.8}\Msun)$, $(10 <d/(kpc h-1) < 30)$, and $(Msec/Mpri > 0.1)$, and found good agreement between the measured pair fractions as a function of redshift.
Thus, projected pair fractions in the Illustris simulation are likely representative of those found in observations for massive galaxy pairs.

\citet{snyder2023} extended this work to utilize the TNG simulation, and created mock images of extragalactic survey fields mimicking future planned surveys like JADES.
From the mock images, they calculated the pair fraction for major pairs with projected separations between $5-70 \kpc$ and with redshift separations of $\Delta z< 0.02(1+z)$, and also found flat or decreasing major pair fractions. 
This is in agreement with our work, as our major pair fraction for massive galaxies is approximately constant or decreasing with higher redshift for $z>1$. 
While we cannot directly compare the values of the pair fractions themselves, as the projected and physical pair separations will yield very different pair fractions as shown in \citet{Besla2018}, we can say that the behavioral trends are the same. 
Pair fractions computed using physical separations do not have to account for contamination due to projection effects, which would increase the inferred pair fraction, however our separation criteria is much less stringent, which would also increase the pair fraction.

% Alejandro's paper connection: studies are finding good agreement between simulations and TNG, as evidenced by this paper. They found that TNG simulated images well approximated the morphologies of galaxies in the KIDS survey, although they were a bit more compact and lumpy. But this means that there is precedent for using TNG in these kinds of comparisons.

% ? maybe to do: plot with comparison values 
\subsection{Implications for observational pair selection criteria}
    %figures
    %%%%%%%%%%%%%%%%%%%%
    \begin{figure*}[htp]
      \centering
      \includegraphics[width=\textwidth]{sepdist_1000.png}
      \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right). Major pairs are shown as solid lines, while minor pairs are dotted. The median separation of each pair type (from Fig.~\ref{fig:sep}) is shown in solid (major) and dotted (minor) vertical black lines. 
      At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively). However, at low redshift, the separation distribution tends to spread out more evenly across a large range of separations, thus increasing the median.
        }
      \label{fig:sep-dist}
    \end{figure*}
    %%%%%%%%%%%%%%%%%%%%
    %%%%%%%%%%%%%%%%%%%%
    \begin{figure*}[htp]
      \centering
      \includegraphics[width=\textwidth]{frac_selected.png}
      \caption{ The fraction of total pairs selected with additional separation selection criteria as a function of redshift. 
        }
      \label{fig:frac-select}
    \end{figure*}
    %%%%%%%%%%%%%%%%%%%%

    % outline
    \begin{itemize}
        \item examples of typical pair selection criteria (i.e. <75 kpc, velocity crit, etc.)
        \item Show how low separation cuts affect pair fractions      
        \item Sep distribution plot and explanation (text below) 
        \item Plot of \% of total pairs selected as function of z for different separation criteria (or maybe better is to do total as function of separation, for different redshifts?) 
        \item What does this mean for JWST and future surveys?
    \end{itemize}

% text on the separation distribution plot
Fig.~\ref{fig:sep-dist} shows the full distribution of separations for major and minor dwarf and massive pairs at $z=\{0,1,2,3,4\}$, and includes all 1000 AM realizations. 
For reference, the median at each corresponding redshift from Fig.~\ref{fig:sep} (that is, the median of the medians of each realization) are shown in light black vertical lines.
Each plot is normalized such that the area under an individual curve is 1.
    % the redshift evolution
At $z=4$, all pair types (dwarf and massive, major and minor) have narrow distributions that pile up around 0 $\kpc$\footnote{Note that only pairs with separations $>10\kpc$ are included in this analysis, see Sec.~\ref{sec:methods-pairs}.}, with ranges between $10-150\,\kpc$ for dwarf pairs and $10-300\,\kpc$ for massive pairs. 
The distributions become more and more broad as $z\to0$, where separations range between $\sim10-400\,\kpc$ for dwarf pairs and $\sim10-1000\,\kpc$ for massive pairs.

Since the distribution of separations changes dramatically from $z=4$ to $z=0$, the population of low separation pairs that are selected at $z=4$ includes the majority of true pairs, but this is not the case at low z. 
At low z, separation criteria must be very broad to encompass the majority of pairs. 
Figure~\ref{fig:frac-select} shows the fraction of pairs that have separations less than $\{50, 75, 100, 150\}\kpc$.
At high redshift ($z\sim2-4$) a majority of pairs are included in the selection, however at lower redshift ($z\sim0-1$), the pair completeness decreases substantially, with fewer than XX\% of the total number pairs for XX separation criteria.

As JWST is expected to image dwarfs (give stellar mass range) out to z=XX in XX survey, the selection criteria for dwarf pairs that are applied will affect the inferred pair fractions greatly.

%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
\section{Summary and Conclusions}\label{sec:summary}
In this paper, we collect a large set of dwarf and massive subhalo pairs from the Illustris TNG100-1 simulation. 
Pairs are selected from the full volume over all 100 snapshots of the simulation, though the sample size of pairs in the first 20 snapshots ($z>4.2$) is extremely small. 
Major and minor pairs are determined using the stellar mass ratio between the primary and secondary halo using stellar masses from 1000 random realizations of the abundance matching prescription. 
From this pair sample, we calculate the pair fractions and snapshot by snapshot kinematics of 4 different pair types: dwarf major pairs, dwarf minor pairs, massive major pairs, and massive minor pairs.

Our main findings are as follows:
\begin{itemize}
    \item The pair fraction for dwarf and massive pairs does not proceed identically throughout cosmic time. In fact, the two mass scales have opposite behavior at low z. The number of dwarf pairs per dwarf primary decreases from $z=2\to0$, while the number of massive pairs per massive primary is approximately constant from $z=4\to0.25$, with an abrupt increase at lower redshift. 
    \item The median physical separation between the primary and secondary subhalo of a pair increases with decreasing redshift. The typical separation of a dwarf (massive) pair is $120\,\kpc$ ($240\,\kpc$) at $z=0$ and $40\,\kpc$ ($80\,\kpc$) at $z=4$.
    \item The median relative velocity between the primary and secondary subhalo of a pair decreases towards lower redshift. The typical relative velocity of a dwarf (massive) pair is $70\,\kms$ ($175\,\kms$) at $z=0$ and $132\,\kms$ ($290\,\kms$) at $z=4$.
    \item The separation scaled by the total virial radius of the group is similar for dwarf and massive pairs, though massive pairs tend to have lower scaled separations for redshifts between $z=0-2$. The relative velocity scaled by the circular velocity at the virial radius evolves identically for both dwarf and massive pairs, indicating that the relative velocities are self-similar at different mass scales. 
    \item All of the above trends hold true for both major and minor pairs of the same mass range (i.e., the conclusions for the dwarf major pairs hold too for the dwarf minor pairs). 
\end{itemize}

Our results are consistent with prior works that have studied the pair fractions of massive and dwarf galaxies in the Illustris simulations in a projected sense. 
The agreement between the pair fraction trends from projected and from physical pair selection criteria points to the IllustrisTNG simulation's robust ability to reproduce the characteristics of galaxy pairs from observations.

Additionally, we conclude that:
\begin{itemize}
    \item Dwarf galaxy pairs and massive galaxy pairs likely have different evolutionary and merger processes which result in the opposing behavior of dwarf and massive pair fractions as a function of redshift.
    \item The separation criteria used to observationally identify pairs likely results in an incompleteness of at least XX\% by $z=0$, though is less problematic for high redshift pairs where pairs tend to have smaller separations. 
\end{itemize}

Our conclusions point to the importance of time-evolving pair selection criteria that account for the natural separation increase of pairs at the universe expands.

\kc{other main takeaways?}

\begin{itemize}
    \item otherMain takeaways: (maybe include these within main findings bullets~)
        \begin{itemize}
            \item lit comp.
            \item dwarfs not equal massives 
            \item JWST imps.
        \end{itemize}
    \item Future work
\end{itemize}

% Findings:
% \begin{itemize}
%     \item 
%     \item Median pair separations increase and relative velocities decrease from high to low redshift. 
% \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{refs}{}
\bibliographystyle{aasjournal}

\end{document}

### 2024-06-06 pears.tex
deploy: 25aee7d523218253c42225dd158be0e25da52704

--- 2021-09-07 paper/pears.tex
@@
-\documentclass[twocolumn]{aastex63}
+\documentclass[twocolumn]{aastex631}
 
-\newcommand\aastex{AAS\TeX}
-\newcommand\latex{La\TeX}
-\newcommand\msun{\rm{M}_{\odot}}
-\newcommand\ID{\textit{Illustris-Dark}}
-\newcommand\IH{\textit{Illustris-Hydro}}
-\newcommand\SUBFIND{\texttt{SUBFIND}}
-\definecolor{mypink}{RGB}{232,132,161}
-\newcommand{\kc}[1]{\textcolor{mypink}{\textbf{#1}} }
-\newcommand{\gb}[1]{\textcolor{olive}{\textbf{#1}} }
-%\newcolumntype{H}{>{\setbox0=\hbox\bgroup}c<{\egroup}@{}}
-%\usepackage{subcaption}
-\usepackage{nicefrac}
+% Packages
+\usepackage{microtype}  % ALWAYS!
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{multirow}
+\usepackage{tikz}
+\usepackage{xcolor}
 \usepackage{soul}
-% \usepackage{amssymb}
+\usepackage{hyperref}
 
-% \graphicspath{{./}{figures/}}
-% \graphicspath{{../}{figures/}}
+\definecolor{pink}{RGB}{232,132,161}
+\definecolor{yellow}{RGB}{255,213,0}
 
-% \shorttitle{Sample article}
-% \shortauthors{Schwarz et al.}
+\newcommand{\kc}[1]{\textcolor{yellow}{\textbf{kc: #1}} }
+\newcommand\shadetext[2][]{%
+  \setbox0=\hbox{{\special{pdf:literal 7 Tr }#2}}%
+  \tikz[baseline=0]\path [#1] \pgfextra{\rlap{\copy0}} (0,-\dp0) rectangle (\wd0,\ht0);% 
+  }
+\newcommand{\gb}[1]{\shadetext[left color=blue, right color=red, middle color=lime, shading angle=45]{\textbf{g: #1}} }
+% \newcommand{\ecite}[1]{\textcolor{pink}{\textbf{: #1}} }
+% \newcommand{\e}[1]{\textcolor{yellow}{\textbf{: #1}} }
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand{\add}[1]{\textcolor{red}{#1}}
+
+\newcommand{\mlg}{\ensuremath{M_{\rm LG}}}
+\newcommand{\mmto}{\ensuremath{M_{\rm M31}}}
+\newcommand{\mmw}{\ensuremath{M_{\rm MW}}}
+\newcommand{\vtan}{\ensuremath{v_\textrm{tan}}}
+\newcommand{\vrad}{\ensuremath{v_\textrm{rad}}}
+\newcommand{\ms}[1]{\ensuremath{M_{*{#1}}}}
+\newcommand{\reflabel}[1]{\ensuremath{^{\mbox{\scriptsize{#1}}}}}
+\newcommand{\scsep}{\ensuremath{\rm r_{sep}/r_{vir}}}
+\newcommand{\scvel}{\ensuremath{\rm v_{rel}/v_{vir}}}
+\newcommand{\subcat}{\textit{Subhalo Catalog}}
+%\newcommand{\lsubcat}{\textit{Low Mass Subhalo Catalog}}
+%\newcommand{\hsubcat}{\textit{High Mass Subhalo Catalog}}
+\newcommand{\starcat}{\textit{Subhalo + Stellar Mass Catalog}}
+\newcommand{\paircat}{\textit{Full Pair Catalog}}
+\newcommand{\Rvir}{\ensuremath{\rm R_{vir}}}
+
+% Style tweaks
+% \renewcommand{\twocolumngrid}{\onecolumngrid}
+% \setlength{\parindent}{1.1\baselineskip}
+% \sloppy\sloppypar\raggedbottom\frenchspacing
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\shorttitle{Pair fractions in TNG100}
+\shortauthors{Chamberlain et al.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\graphicspath{{./}{../plots/paper1/}}
+\input{math_definitions.tex}
+
+% Affiliations
+\newcommand{\affuofa}{University of Arizona, 933 N. Cherry Ave, Tucson, AZ 85721, USA}
+\newcommand{\affunam}{Instituto de Radioastronom\'ia y Astrof\'isica, Universidad Nacional Aut\'onoma de M\'exico, Apdo. Postal 72-3, 58089 Morelia, Mexico}
+\newcommand{\affuoff}{Department of Astronomy, University of Florida, P.O. Box 112055, Gainesville, FL 32611, USA}
+\newcommand{\affberk}{Department of Astronomy, University of California, Berkeley, 501 Campbell Hall, Berkeley, CA, 94720, USA}
+\newcommand{\affuofu}{Department of Physics and Astronomy, University of Utah, 115 South 1400 East, Salt Lake City, Utah 84112, USA}
+\newcommand{\affnyu}{The Center for Cosmology and Particle Physics, New York University, 726 Broadway, New York, NY 10003}
+\newcommand{\affnrao}{National Radio Astronomy Observatory, 520 Edgemont Road,
+Charlottesville, VA 22903, USA}
+\newcommand{\affuva}{Department of Astronomy, University of Virginia, 530 McCormick Road, Charlottesville, VA 22904, USA}
+\newcommand{\affempty}{Empty}
+\newcommand{\affnottingham}{School of Physics and Astronomy, University of Nottingham, University Park, Nottingham NG7 2RD, UK}
+\newcommand{\affkorea}{Korea Astronomy and Space Science Institute, 776 Daedeokdae-ro, Yuseong-gu, Daejeon 34055, Korea}
+\newcommand{\afftrent}{Department of Physics and Astronomy, Trent University, 1600 West Bank Drive, Peterborough, ON K9L 0G2, Canada}
+\newcommand{\affoccidental}{Occidental College, Physics Department, 1600 Campus Road, Los Angeles, CA 90041, USA}
+
+%% This is the end of the preamble.
+
 \begin{document}
 
-\title{Occurance rate of galaxy pairs across cosmic time:\\ Local Group analogs in a cosmological context}
-\correspondingauthor{Katie Chamberlain}
-\email{katiechambe@email.arizona.edu}
+\title{
+  % Pair fractions of low mass and high mass galaxy pairs in the TNG100 cosmological simulation
+  % low mass and high mass galaxy pairs evolve differently as a function of redshift
+  %A physically motivated framework for measuring\\ the mass and redshift dependence of galaxy pair fractions across cosmic time 
+  \add{A physically motivated framework to compare pair fractions\\ of isolated low and high mass galaxies across cosmic time }
 
-\author[0000-0001-8765-8670]{Katie Chamberlain}
-\affil{Steward Observatory, University of Arizona\\
-933 North Cherry Avenue\\
-Tucson, AZ, 85721, USA}
-\author{Gurtina Besla}
-\affil{Steward Observatory, University of Arizona\\
-933 North Cherry Avenue\\
-Tucson, AZ, 85721, USA}
+   % for measuring galaxy pair fractions across cosmic time
+   % measuring or recovering?
+  }
+% Differences in the redshift evolution of low mass and high mass galaxy pairs in the TNG100 cosmological simulation
+
+\author[0000-0001-8765-8670]{Katie~Chamberlain}
+\thanks{E-mail: katiechambe@arizona.edu}\affiliation{\affuofa}
+
+\author[0000-0003-0715-2173]{Gurtina Besla}
+\affiliation{\affuofa}
+
+\author[0000-0002-9820-1219]{Ekta~Patel}
+\thanks{Hubble Fellow}\affiliation{\affberk} \affiliation{\affuofu}
+
+\author[0000-0002-9495-0079]{Vicente Rodriguez-Gomez}
+\affiliation{\affunam}
+
+\author[0000-0002-5653-0786]{Paul Torrey}
+\affiliation{\affuoff}
+
+\author[0000-0003-2939-8668]{Garreth Martin}
+\affiliation{\affnottingham}\affiliation{\affkorea}\affiliation{\affuofa}
+
+\author[0000-0001-8348-2671]{Kelsey Johnson}
+\affiliation{\affuva}
+
+\author[0000-0002-3204-1742]{Nitya Kallivayalil}
+\affiliation{\affuva}
+
+\author[0000-0002-1871-4154]{David Patton}
+\affiliation{\afftrent}
+
+\author[0000-0003-0256-5446]{Sarah Pearson}
+\thanks{Hubble Fellow}\affiliation{\affnyu}
+
+\author[0000-0003-3474-1125]{George Privon}
+\affiliation{\affnrao}\affiliation{\affuoff}\affiliation{\affuva}
+
+\author[0000-0002-2596-8531]{Sabrina Stierwalt}
+\affiliation{\affoccidental}
+
 \begin{abstract} 
+    Low mass galaxy pair fractions are under-studied across cosmic time. \add{Further, it is unclear whether low mass pair fractions evolve in the same way as more massive systems over cosmic time.}
+    \add{In the era of JWST, Roman, and Rubin, selecting galaxy pairs in a self-consistent way will be critical to connect observed pair fractions to cosmological merger rates across all mass scales and redshifts.}
+    \add{We use the Illustris TNG100 simulation to create a sample of physically associated pairs between $z=0-4.2$, including low mass ($\rm 10^8<M_*<5\times10^9\,\Msun$) and high mass ($\rm 5\times10^9<M_*<10^{11}\,\Msun$) isolated subhalo pairs.}
+    The low mass pair fraction, i.e. the fraction of galaxies in pairs, increases from $z=0-2.5$, while the high mass pair fraction peaks at $z=0$ and is constant or slightly decreasing at $z>1$. 
+    At $z=0$ the low mass major (1:4 mass ratio) pair fraction is 4$\times$ lower than high mass pairs, consistent with findings for cosmological merger rates. 
+    \add{We show that separation limits that vary with the mass and redshift of the system, such as scaling by the virial radius of the host halo ($r_{\mathrm{sep}}< 1 R_{\rm vir}$), are critical for recovering pair fraction differences between low mass and high mass systems.}
+    \add{Alternatively, static physical separation limits applied equivalently to all galaxy pairs do not recover the differences between low and high mass pair fractions, even up to separations of $300\,\kpc$.}
+    Finally, we place isolated mass-analogs of Local Group galaxy pairs (i.e., MW--M31, MW--LMC, LMC--SMC) in a cosmological context, showing that isolated analogs of LMC--SMC-mass pairs, and low separation ($<50\kpc$) MW--LMC-mass pairs, are $2-3\times$ more common at $z\gtrsim2-3$.
 
-  % \textbf{Context} 
-  Dwarf galaxies are extremely common at all redshifts and often exhibit morphological disturbances that do not primarily result from galaxy mergers.
-As such, pair fractions, rather than morphological indicators (asymmetry, concentration) are needed to infer dwarf galaxy  merger rates from observational surveys.
-  However, in contrast to massive galaxies ($5\times 10^9\leq$ $\rm M_{prim,*} \leq 1\times 10^{11} \msun$), pair fractions for dwarf galaxies ($10^8 < \rm M_* < 5 \times 10^9 \msun$) have been theoretically constrained only at low redshift.
-  % \\\textbf{Aims}
-  We aim to quantify the occurence rates and kinematics of isolated dwarf and massive galaxy pairs from $z=0-4$ in the Illustris and IllustrisTNG cosmological simulations.
-  % \\\textbf{Methods} 
-  Dwarf and massive subhalo pairs are identified in each snapshot of the Illustris \texttt{SUBFIND} catalogs. 
-  % \\\textbf{Results} 
-  We find that roughly 8-10\% of dwarf galaxies will have major companion (stellar mass ratio $>1:4$) at $z=0$, increasing steadily before plateauing in \ID(\IH) at 16\%(12\%) by $z\sim 2$.
-The occurence rate of dwarf galaxies with minor companions (stellar mass ratios between $1:10$ and $1:4$) is roughly constant at $\sim 2.5\%$ from $z=1-4$.
-In contrast, the occurence rate of major and minor massive galaxy pairs remains approximately constant across time, as massive galaxies have a major (minor) companion $\sim18\%$ ($\sim14\%$) of the time.
-  % \\\textbf{Conclusions} 
-  This suggests that the hierarchical evolution of dwarf galaxies may proceed differently than that of massive galaxies.
-LMC-SMC mass analogs (dwarf minor pairs) are twice as common at redshifts greater than 2, but the present day LMC-SMC system is dynamically rare at all redshifts (in terms of pair separation and velocity).
-The M31-M33 pair is dynamically typical of massive minor pairs at $z\approx0$, while the MW-LMC has unusually high velocities and low relative separations for a major massive pair at low redshift.
-Baryonic physics impacts the occurence rate of galaxy pairs and systematically changes the kinematics of dwarf pairs, suggesting observations of dwarf galaxy pairs can be used to test subgrid physics in cosmological simulations.
-
+    % old abstract:
+    % Low mass galaxy pair fractions are under-studied across cosmic time. 
+    % In the era of JWST, Roman, and Rubin, a self-consistent framework is needed to select both low and high mass galaxy pairs to connect observed pair fractions to cosmological merger rates across all mass scales and redshifts.
+We use the Illustris TNG100 simulation to identify physically associated pairs between $z=0-4.2$.
+    % Our sample includes low mass ($\rm 10^8<M_*<5\times10^9\,\Msun$) and high mass ($\rm 5\times10^9<M_*<10^{11}\,\Msun$) isolated subhalo pairs, with stellar masses from abundance matching. 
+    % The low mass pair fraction, i.e. the fraction of galaxies in pairs, increases from $z=0-2.5$, while the high mass pair fraction peaks at $z=0$ and is constant or slightly decreasing at $z>1$. 
+    % At $z=0$ the low mass major (1:4 mass ratio) pair fraction is 4$\times$ lower than high mass pairs, consistent with findings for cosmological merger rates. 
+    % Our results indicate that pair fractions can faithfully reproduce trends in merger rates if galaxy pairs are selected appropriately. 
+    % Specifically, static pair separation limits applied equivalently to all galaxy pairs do not recover the evolution of low and high mass pair fractions. 
+    % Instead, we advocate for separation limits that vary with the mass and redshift of the system, such as separation limits scaled by the virial radius of the host halo ($r_{\mathrm{sep}}< 1 R_{\rm vir}$).
+    % Finally, we place isolated mass-analogs of Local Group galaxy pairs (i.e., MW--M31, MW--LMC, LMC--SMC) in a cosmological context, showing that isolated analogs of LMC--SMC-mass pairs, and low separation ($<50\kpc$) MW--LMC-mass pairs, are $2-3\times$ more common at $z\gtrsim2-3$.
 \end{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction} \label{sec:intro}
-%%%%%%%%%%%%%%%%%%%%%%
-Galaxy mergers are responsible for many physical processes that shape galactic evolution, including triggered star formation~\citep{mihos96, hopkins13, patton20,hani20}, increased AGN activity~\citep{hopkins08,comerford15,ellison19}, and galaxy morphology~\citep[e.g.,][]{rg17}.
-Dwarf galaxies  make up a majority of the galaxy population at all redshifts (REF) and are also expected to undergo interactions and merge.
-Such processes may be important to understand the growth and evolution of intermediate mass black holes, which are often found to be ``wandering" in low mass galaxy hosts~\citep{stemo20,reines20}.
-Despite the ubiquity of dwarf galaxies in the universe, we do not have a clear path to constrain the merger rates of these systems observationally or to place known interacting dwarf galaxy systems (stellar mass $1\times10^8<M_* < 5\times10^9\msun$) in a cosmological context.
+    Galaxy mergers have been studied in detail as a mechanism for driving galaxy evolution, and have been identified as a trigger of, for example, 
+    active galactic nuclei (AGN)~\citep[e.g.][]{Hopkins2008,Treister2010,Ramos2011,Satyapal2014,Comerford2015,Glikman2015,Blecha2018,Ellison2019}, 
+    star formation~\citep[e.g.][]{Mihos1996, DiMatteo2008,Ellison2011,Patton2013, Hopkins2013,Martin2017,Patton2020,Hani2020,Martin2021}, 
+    and changes in morphology~\citep[e.g.][]{Conselice2003,Lotz2008,Casteels2014,Patton2016,Bignone2017,RG2017,Martin2018,Jackson2019,Snyder2019,Jackson2022,Guzman-Ortega2023}. 
+    Constraining the merger rate for galaxies is critical for quantifying the importance of mergers for galaxy evolution and testing predictions for hierarchical assembly in cold dark matter theory \citep[e.g.][]{Stewart2009,Hopkins2010,RG2015}.
 
-Massive galaxy ($M_* > 5\times10^9\msun$) mergers and interactions can be observationally identified using methods like asymmetry and concentration measures~\citep{conselice2000, lotz04}.
-Numerous studies have used these measures to study the merger and interaction rates of massive galaxies as a function of time~\citep[e.g.,][]{lotz11,casteels14}.
+    In practice, merger rates cannot be measured straightforwardly from observations and, rather, are calculated by converting the observed frequency of a galaxy merger signature (i.e., asymmetry, concentration, pair fraction, etc.) to a merger rate using an observability timescale~\citep[e.g.][]{Lotz2011}.
+However, morphological signatures of mergers are often caused by non-merger phenomena.
+    For example, low mass galaxies are more commonly morphologically disturbed by fly-bys and non-merger interactions than by mergers~\citep{Martin2021}, 
+    and star-forming galaxies at high redshift tend to be clumpy and asymmetric even in isolation~\citep{Wuyts2013}.
+    Additionally, detection of these signatures can be strongly dependent on image depth or galaxy stellar mass, and identifying tidal features that rely on human classifications may be unreliable~\citep{Martin2022}.
 
-However, \citet{martin21} showed that mergers only account for 10\% of morphological disturbances in dwarfs, and that a majority of their morphological disturbances derive from non-merger interactions, such as gas inflows/outflows, close passages, and fly-bys.
-This means that the typical methods of classifying interactions and mergers for massive galaxies are unlikely to be robust in lower mass regimes.
-This is particularly true at high redshift, when gas accretion along filaments is expected to be more significant~\citep{keres09}.
-Thus, it is critical to establish an alternative, cosmologically consistent, way to determine merger and interaction rates for dwarf galaxy pairs from observations.
+    Pair fractions, on the other hand, can be calculated independently of morphological information, and thus offer a more robust method of observationally quantifying merger rates across cosmic time.
+    Pair fractions of high mass ($M_*\gtrsim10^{10}\Msun$) galaxies have been well studied across cosmic time both observationally~\citep[e.g.][]{Patton2002,Lin2004,Lin2008,Lotz2011,Ferreras2014, Man2016,Duncan2019}, and theoretically~\citep[e.g.][]{RG2015,Snyder2017,Snyder2023}, with theoretical studies typically done in projection for comparison to observational campaigns\footnote{The studies cited here have limits on the projected separation of their sample, such that the projected separations range between $5\,\kpc$ and $\sim140\,\kpc$.}.
+    Low mass galaxy pairs ($10^8<M_*<5\times10^9\Msun$) have been studied at low redshift~\citep[e.g.][]{Stierwalt2015,Pearson2016,Besla2018,Paudel2018,Luber2022},
+    but are less well understood across cosmic time owing to the difficulty in observing faint systems outside of the Local Volume. 
+    However, JWST~\citep{Gardner2006}, as well as the next generation of deep and wide-field surveys from Rubin Observatory\footnote{ \href{https://rubinobservatory.org/}{https://rubinobservatory.org}}~\citep{RUBIN2019} and Roman Space Telescope\footnote{\href{https://roman.gsfc.nasa.gov/}{https://roman.gsfc.nasa.gov}}~\citep{Spergel2015}, will significantly revolutionize our ability to identify such systems at high redshift $(z\gtrsim10)$~\citep{Behroozi2020} and in abundance at lower redshift ($z\lesssim6$)~\citep{Robertson2019a,Robertson2019b-LSST}.
 
-Another observational technique to determine merger/interaction rates relies upon the pair fraction: the ratio of the number of host galaxies with a companion to the number of potential hosts.
-Pair fractions for massive galaxies have been measured observationally as a function of time~\citep[e.g.,][]{lotz08,conselice09}, and calibrated against theoretical simulations to determine observability timescales that enable the translation of pair fractions to merger rates \citep{lotz11,kaviraj15,snyder17,qu17,oleary21b}.
-In contrast, pair fractions for dwarf primaries are only starting to be measured at high redshift \citep[e.g.][]{ventou17} and have only been studied with small sample size or calibrated against simulations at low redshift \citep{besla18, casteels14,stierwalt15, pearson18}.
-Thus we are currently missing a theoretical framework to interpret future high redshift observations of dwarf pairs, i.e.
-with \textit{JWST}.
-In this study, we quantify the dwarf galaxy pair fraction as a function of time out to $z\sim$4, and compare these results to the massive galaxy pair fraction, using the N-body and hydrodynamic \textit{Illustris-1} cosmological simulations~\citep{vogelsberger14A,nelson15}.
+    There are reasons to believe that low mass and high mass pairs evolve differently as a function of time.
+    For example, semi-empirical and cosmological studies find that galaxy merger rates vary both with redshift and the mass of the most massive galaxy of the pair~\citep[see e.g.][]{Guo2008,Stewart2009,Hopkins2010,RG2015,Martin2021}.
+    % Such differences are likely to give rise to differences in the pair fractions of low and high mass pairs.
+    It is thus reasonable to assume that the pair fractions of these two mass scales reflect these evolutionary differences as well.
 
-There are examples of galaxy pairs involving dwarf galaxies in our Local Group, including the M31-M33, MW-LMC, and the LMC-SMC (Magellanic Clouds; MCs) systems.
-The frequency of such pairs have been studied extensively observationally and theoretically at low redshift.
-In SDSS DR7, it is found that 11\% of MW/M31-like objects have one massive satellite (LMC/M33 analog) within 150 kpc and 300 km s$^{-1}$~\citep{liu11}.
-Within 250 kpc, the frequency increases to 42\% (Tollerud 2011).
-% , robotham12
-This is in agreement with $\Lambda$CDM predictions \citep{busha11, bk11, patel17a, gonzalez13}. 
-% check gonzalez
-Furthermore, 4-6\% of LMC/M33 analogs in both SDSS and cosmological simulations are expected to have a companion at least as massive as an SMC in the field \citep{besla18, sales11}.
-%% ADD SALES RESULTS ?
-% add how defined here
+    The redshift evolution of low and high mass pair fractions has not yet been studied in simulations in a self-consistent way, where high mass and low mass pairs are selected from simulations using otherwise equivalent selection criteria.
+    We aim to characterize the redshift behavior of pair fractions of low mass and high mass pairs, independent of environmental and projection effects, and to create a robust framework in which to fairly compare pair fractions of different mass scales across cosmic time.
 
-However, we do not how common these pair configurations are as a function of time in the $\Lambda$CDM framework, leaving open the question as to whether our Local Group is unique in time. 
-Recent advances in astrometry have furthermore enabled the measurement of 6D phase space information for these Local Group galaxy pairs.  
-In this study, we will examine whether not only the frequency, but also the dynamics of pairs in our Local Group are unique \textit{across cosmic time}.
-% HOW DO MASSIVE PAIRS SCALE TO DWARF REGIME
+    In particular, we take the approach of consistently selecting physically associated pairs of low mass ($10^8<M_*<5\times10^9\Msun$) and high mass $(5\times10^9<M_*<10^{11}\,\Msun)$ galaxies. 
+    Specifically, we identify major ($1-1/4$) and minor $(1/10-1/4)$ stellar mass ratio pairs from $z=0-4.2$ in the IllustrisTNG cosmological simulation, TNG100. 
+    We require that pairs are part of the same Friends of Friends (FoF) group and that no other more massive perturbers are nearby, which allows us to ensure that the recovered pair fractions are inherent to the population of selected pairs rather than a function of environment.
 
-The Local Group also contains a massive major galaxy pair (stellar mass ratio $>$1:4), the MW-M31.
-For low redshift (z$<$ $\sim$.1) massive galaxies (M$_\ast > 10^{10}$ M$_\odot$), the fraction of major pairs are expected to increase as a function of mass \citep{casteels14}, resulting in major merger rates that rise  with higher mass~\citep{rg15,ventou17,oleary21b}.
-Additionally, the fraction of major pairs is also measured to increase with increasing redshift~\citep{deravel09,bundy09,duncan19}.
-In particular \citet{duncan19} find no strong evolution in the relative number of minor to major mergers for massive hosts out to z$<$3.
-But it is unclear whether these trends for the frequency of major pairs will be the same if the host mass is in the dwarf galaxy regime.
+    Typically, 
+    \add{pair fraction studies via simulations and observations}
+    apply physical projected separation cuts that are constant over time and do not vary with the mass of the target system. 
+    \add{In this study we identify how the application of a fixed separation criteria affects inferred pair fractions, and show that a time and mass evolving separation cut is necessary to permit equitable pair fraction comparisons across different mass regimes.}
+    \add{Although implementing alternative selection criteria in future observational pair fraction studies may not always be strictly necessary, we recommend that pair selection criteria be reevaluated for observational studies that seek to compare pair fractions as a function of mass or redshift.}
+    % In this study we identify how the application of a fixed separation criteria affects inferred pair fractions, and make recommendations for a time and mass evolving separation cut to permit equitable pair fraction comparisons between different mass regimes.
+    % To fairly test for differences in the evolutionary behavior of pair fractions, especially in observational studies, it is necessary to determine whether this is an appropriate technique for accurately recovering true pair fraction behavior.
 
-It is important to study the dwarf and massive host regimes separately, as baryonic physics, including gravitational tides, star formation, and outflows, impacts the growth of dwarf galaxies more strongly~\citep{bullockbk17,jeon19,jeon21}.
-For example, it has been shown that baryonic physics implemented in the \IH\ simulation suppresses the abundance of low mass subhalos ($\leq$10$^{10}\msun$), but such a suppression is not present for massive halos~\citep{chua17}.
-Thus, the pair fractions and dynamics of dwarf major and minor pairs may change drastically between the dark-matter-only and full-physics simulations, with less differences for massive  pairs.
-In this study, we illustrate that the impact of baryonic physics on the growth of low mass halos in cosmological simulations may be directly testable with pair fraction observations.
+    Finally, there are a number of galaxy pairs in the Local Group that are mass analogs of the isolated pairs in our sample.
+    For example: the MW--M31 system is a high mass major pair, the MW--LMC and M31--M33 systems are high mass minor pairs, and the LMC--SMC are a low mass minor pair.
+    Studies have examined the frequency of such configurations, particularly at low redshift or in the form of progenitor systems of the Local Group in cosmological simulations~\citep{Bk2011,Fattahi2013,Patel2017a-Orbits,Geha2017,Mao2021}, but the prevalence of such pairs in isolation has not yet been quantified as a function of redshift.
+    We utilize our pair dataset to quantify the likelihood of finding isolated mass-analogs of Local Group pairs as a function of redshift, particularly when the present day separations of these systems are folded in.
 
-Here we present the first cosmologically motivated constraints on the dwarf pair fraction for major and minor pairs as a function of time.
-We compare these results to those found for massive major and minor pairs, and address the differences in expected pair fractions between the N-body and full hydrodynamic simulations.
-This work will furthermore, self-consistently, place known galaxy pairs in our Local Group in a cosmological and temporal context.
-In Sec.~\ref{sec:methods}, we introduce the simulations and selection criteria used to perform the analysis of our sample of pairs.
-In Sec.~\ref{sec:results}, we present the results of this pair fraction study, including preliminary results on the kinematics of dwarf pairs over cosmic time.
-In Sec.~\ref{sec:discussion}, we discuss the implications of our results on interpretations of future surveys, and what this could mean for constraints of feedback mechanisms in cosmological simulations.
-In Sec.~\ref{sec:conclusions} we present a summary of the main conclusions of this work, including expected pair fractions for dwarf and massive galaxy pairs.
+    This paper is structured as follows. 
+    In Section~\ref{sec:methods}, we outline our methodology for selecting physically associated high mass and low mass pairs from the TNG simulation. 
+    In Section~\ref{sec:pairprops}, we provide an overview of the properties of the selected sample, including the number of primaries, pairs, and their stellar mass ratios as a function of time. 
+    We present the time-evolving pair fraction of high mass and low mass pairs in Section~\ref{sec:results}, and show how they change for different separation criteria. 
+    \add{In Section~\ref{sec:discussion}, we give context to our results by drawing comparisons to Local Group pairs and other Illustris-based pair fraction studies, and discuss implications for observational campaigns.}
+        % In Section~\ref{sec:discussion}, we discuss the implications of the differences between low and high mass pair fractions for observational campaigns and give context to our results by drawing comparisons to Local Group pairs.
+    Finally, we summarize our results and conclusions in Section~\ref{sec:summary}.
 
-%%%%%%%%%%%%%%%%%
-\section{Sample Selection} \label{sec:methods}
-%%%%%%%%%%%%%%%%%
-Our sample of dwarf galaxy pairs and massive galaxy pairs from cosmological simulations was chosen following a strict set of selection criteria.
-In Sec.~\ref{sec:simData} we will detail the simulations from which we collected our data, Sec.~\ref{sec:abundanceMatching} explains the abundance matching prescription used to associate dark matter halos with stellar masses, and Sec.~\ref{sec:selectionCrit} outlines the isolation and mass criteria used to identify our sample.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsection{Simulation data}\label{sec:simData}
-We utilize data from the \textit{Illustris Project} ~\citep{vogelsberger14A,nelson15}, a set of N-body and hydrodynamic cosmological simulations, to statistically analyse the occurrence rates of dwarf and massive dark matter subhalo pairs over cosmic time.
-In particular, we are using the highest resolution dark matter only simulation, \textit{Illustris-1-Dark}, and the  full hydrodynamic simulation, \textit{Illustris-1} (hereafter \textit{Illustris-Dark} and \textit{Illustris-Hydro} respectively, see Table~\ref{table:illustris}).
-Each of these simulations follows the dynamical evolution of $1820^3$ dark matter particles from $z=127$ to $z=0$ through a periodic volume of $106.5^3$ Mpc$^3$.
-The Illustris simulations use a cosmology that is consistent with \textit{WMAP-9} ~\citep{hinshaw13}: $\Omega_m = 0.2726$, $\Omega_\Lambda = 0.7274$, $\Omega_b = 0.0456$, $\sigma_8 = 0.809$, $n_s=0.963$, and $h=0.704$.
+\section{Methodology}\label{sec:methods}
+We aim to quantify and characterize the frequency, or pair fraction, of low mass ($\rm\ms{}=10^{8}-5\times 10^{9}\Msun$) and high mass ($\rm\ms{}=5\times10^{9}-10^{11}\Msun$) galaxy pairs in cosmological simulations as a function of cosmic time.
+To this end, we utilize the \tng\ suite of simulations to select subhalo pairs as a function of redshift, according to the selection criteria outlined in the remainder of this section.
 
-% Maybe doesn't need whole paragraph but, about dark vs. hydro
-We are utilizing data from both \textit{Illustris-Dark} and \textit{Illustris-Hydro} to study the effect of baryonic content on the subhalos.
-As dwarf subhalos have more shallow dark matter potentials than their more massive counterparts, they are more likely to be subject to disruption caused by baryonic feedback at higher redshifts, which may result in fewer low mass subhalo pairs in \textit{Illustris-Hydro}.
+In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulation utilized in this study.
+Sec.~\ref{sec:methods-halos} outlines the initial mass cuts used to define our \subcat, to which we will add stellar mass information. 
+Sec.~\ref{sec:methods-am} outlines the abundance matching prescription used to associate dark matter subhalos with stellar masses, and the creation of the \starcat, from which we will select pairs.
+Sec.~\ref{sec:methods-pairs} describes the second set of selection criteria that we use to finally construct the \paircat.
 
-% Subfind paragraph: 
-We use catalogs of dark matter halos and their associated subhalos identified in each simulation using the \texttt{SUBFIND} algorithm ~\citep{springel01,dolag09}.
-Dark matter halos were identified using the Friends-of-Friends (FoF) algorithm ~\citep{davis85}, which links particles that have separations less than $0.2d$, where $d$ is the mean inter-particle separation.
-Each FoF group, which we will further refer to as a ``group", was further divided into over-dense and gravitationally bound dark matter subhalos.
+%%%%%%%%%%%%%%%%%%%%%%%
+% Sim details section %
+    \subsection{Simulation details} \label{sec:methods-sims}
+        % Brief description of TNG hydro and which run we use.
+    The IllustrisTNG project~\citep{TNG1, TNG2, TNG3, TNG4, TNG5} consists of a suite of dark-matter-only $N$-body and full physics cosmological simulations that adopt the \textit{Planck2015} \lcdm\  cosmology~\citep{Planck2015}.
 
-% Sublink paragraph:
-In order to trace the growth and histories of our subhalos, we are using the merger trees provided by the \texttt{SUBLINK} algorithm \citep{gomez15}, which tracks subhalos between snapshots using their particle data.
-These merger trees provide information about the kinematics and mass growth of subhalos in both \textit{Illustris-Dark} and \textit{Illustris-Hydro}, and in particular will be used to provide the maximal masses of each of the subhalos we investigate.
+    In this study, we utilize data from TNG100-1, the main high resolution, full physics simulation of a $(110.7\,\Mpc)^3$ volume (hereafter TNG100)\footnote{We will also use data from TNG100-1-Dark, the main high resolution dark-matter-only run (hereafter TNG100-Dark), as presented in Sec.~\ref{sec:disc-dark}.}
+    This simulation follows the evolution of baryons and $1820^3$ dark matter particles from $z=127$ to $z=0$.  
+    The volume of this simulation is sufficiently large, and the resolution is sufficiently high, to conduct a simultaneous analysis of the statistics of both low mass and high mass galaxy pairs, as shown by studies of pair statistics in similarly sized volumes~\citep{Sales2013,Patel2017a-Orbits,Patel2017b-Masses,Besla2018}.
 
-The lower mass threshold for subhalos that constitute our dwarf pairs have a halo mass greater than $1\times10^9\msun$, such that each of our halos are resolved into at least 130 particles in \textit{Illustris-Dark} and 150 particles in \textit{Illustris-Hydro}.
-% \kc{add explanation for why 100 particles is good enough for the resolution we're looking for.}
+      % subfind, sublink, and groups and subhalos
+    We utilize the group catalogs produced by the \texttt{SUBFIND} algorithm~\citep{Springel2001,Dolag2009}. 
+    This catalog was created using the Friends-of-Friends (FoF) algorithm~\citep{Davis1985}, which links nearby dark matter particles to define large halos of associated particles, from which subhalos are identified as over-dense and gravitationally bound dark matter structures.
+    In addition, we utilize the merger trees provided by the \texttt{SUBLINK} algorithm~\citep{RG2015}, which tracks subhalos between snapshots, enabling us to trace the mass evolution of our selected subhalos.
 
-\begin{table}[htb]
-\begin{tabular}{lll}
- & Illustris-Dark & Illustris-Hydro \\\hline\hline
- L$_{\rm Box}$ [Mpc] & 106.5 & 106.5 \\
-m$_{\rm DM}$ [M$_\odot$] & 7.5$\times10^6$ & 6.3$\times10^6$ \\\hline
-\end{tabular}
-\caption{\label{table:illustris}Parameters of the Illustris simulations used in this analysis.}
-\end{table}
-% when i start using TNG can add this!
-% \begin{table*}[htb]
-% \begin{tabular}{lllll}
-%  & Illustris-Dark & Illustris-Hydro & IllustrisTNG-Dark & IllustrisTNG-Hydro\\\hline\hline
-%  L$_{\rm Box}$ [Mpc] & 106.5 & 106.5 & 110.7 & 110.7 \\
-% m$_{\rm DM}$ [M$_\odot$] & 7.5$\times10^6$ & 6.3$\times10^6$ & 8.9$\times10^6$ & $7.5\times10^6$\\\hline
-% \end{tabular}
-% \caption{Parameters of the Illustris simulations used in this analysis.}
-% \end{table*}
+% End sim details     %
+%%%%%%%%%%%%%%%%%%%%%%%
 
-\begin{table*}[htb]
-  \begin{center}
-    \begin{tabular}{lcc}
-     & Dwarf Pairs & Massive Pairs \\\hline\hline
-    Group Mass & $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ & $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$  \\
-    % Subhalo Max Mass &  &  \\
-    Subhalo Current Mass & $>1\times10^{10} \msun$ & $> 5\times10^{11} \msun$ \\
-    Primary &$1\times10^{8} < \rm M_* < 5\times10^{9} \msun$ & $5\times10^{9} < \rm M_* < 1\times10^{11} \msun$\\\hline
-    \end{tabular}
-    \caption{\label{table:mass}Selection criteria for dwarf and massive pairs.}
-  \end{center}
-    \end{table*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%    
+% Choosing halos section %
+    \subsection{Choosing low and high mass subhalos in TNG100} \label{sec:methods-halos}
 
-\subsection{Abundance matching}\label{sec:abundanceMatching}
-Although \textit{Illustris-Hydro} provides stellar masses for all subhalos, however these reported masses are higher than observations suggest~\citep{genel14}.
-We assign stellar masses to dark matter halos in a consistent way between both \ID\ and \IH using the abundance matching (AM) prescription of \citet{moster13} to associate each dark matter halo with a stellar mass.
+    In this section, we outline the steps to create the \subcat, which we will utilize to assign stellar masses to each of the dark matter subhalos.
 
-The AM relationship at low stellar masses has a large spread, thus a subhalo with a dark matter halo mass of $10^{11}$ may be associated with a stellar mass anywhere between $1.2\times10^{8} - 5\times10^{9}\rm M_\odot$, as can be seen in Fig.~\ref{fig:abundanceMatching}.
+    % reworded for clarity
+    % We are interested in the intrinsic frequency of low and high mass galaxy pairs in the field, rather than in over dense environments.
+This allows us to assess whether there are fundamental differences in the frequency of pairs as a function of mass scale that are independent of environmental factors\footnote{Note that our pair fraction calculations are thus specifically for isolated systems, and the global pair fraction (including both isolated and non-isolated pairs) will be different.}.
+As such, we must ensure that our target subhalos are sufficiently isolated.
+We do this by placing limits on the virial mass of the FoF group to which our low mass or high mass samples belong.
+    \add{To assess whether the pair fractions of low mass and high mass pairs evolve in fundamentally different ways as a function of redshift, rather than as a product of their environmental conditions, we will focus on galaxy pairs in low density environments only\footnote{Note that our pair fraction calculations are thus specifically for isolated systems, and the global pair fraction (including both isolated and non-isolated pairs) will be different.}.
+    As such, we ensure that our target subhalos are sufficiently isolated by placing limits on the virial mass of the FoF group to which our low mass or high mass samples belong.}
 
-There are two inputs to the AM relationship: dark matter mass and redshift.
-As shown recently by \citet{munshi21}, the relationship between stellar mass and peak halo mass of dwarf subhalos in the Marvel and Justice League simulations is much tighter than the relationship between the stellar mass and halo mass of subhalos at $z=0$.
-We use the maximal dark matter mass of the halo to ensure that the stellar mass associated with each subhalo reflects the shape of the dark matter profile in the inner regions of the subhalo, thus preventing us from assigning very low stellar masses to halos that have been stripped of %a lot of
-their outer dark matter mass by recent interactions.
-We evaluate the AM relation using the redshift of the halo at the snapshot that we are interested in, rather than the redshift of the halo at its maximal mass, in order to account for ongoing star formation past peak halo mass.
+    The following selection process is repeated for each snapshot of the simulation over a redshift range of $z=0-4.2$.  
+    We stop our analysis at $z=4.2$ since the population of massive subhalo pairs falls off rapidly at larger redshifts, where the sample size of high mass primaries falls well below 100 subhalos per snapshot.
 
-For the collection of subhalos identified at each snapshot of the simulation, the stellar masses are drawn from the gaussian sampled AM relation.
-We thus generate 50 realizations for the stellar mass distribution of the same subhalo population in order to account for uncertainties in the AM relation.
-Each realization is treated as an independent sample of galaxies, where computed properties (stellar masses, relative speeds, etc) are averaged over each realization.
-We report the mean of all realizations and error bars indicate the 1$\sigma$ dispersion across the realizations.
+    At each snapshot, we first apply a cut on the FoF group virial mass, $M_{\rm vir}$, given by \texttt{Group\_M\_TopHat200}\footnote{The mass \texttt{Group\_M\_TopHat200} is the mass enclosed by a sphere with mean density $\Delta_c *\rho_c$, where $\Delta_c$ is the overdensity constant from~\citet{Brynorman1998} and $\rho_c$ is the critical density of the universe at the time calculated.
+The corresponding virial radius in TNG100 is given by \texttt{Group\_R\_TopHat200}.} in the TNG100 group catalogs.
+    We define the group mass range for low mass and high mass groups as: 
+    \begin{align*}
+        \mbox{\textbf{low mass:}}&\,\rm M_{G} = 8\times 10^{10}- 5\times 10^{11}\,\Msun \\ 
+        \mbox{\textbf{high mass:}}&\, \rm M_{G}=10^{12}- 6.5\times10^{12}\,\Msun.
+    \end{align*}
+    The FoF group mass criteria is fixed for all redshifts, which means that some low mass groups at high $z$ may be the progenitors of high mass systems at $z=0$.
 
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/z0.png}
-  \caption{\label{fig:abundanceMatching} Abundance matching relationship of \citet{moster13} at z=0 for dark matter halo masses between $10^{10}$ and $10^{14} \msun$.
-Note that at halo masses below $\sim10^{12} \msun$, there is more spread in stellar mass at fixed halo mass compared to halos with $\rm M_{H} > \sim10^{12} \msun$.
-This effect is illustrated by the vertical lines at $10^{11}\msun$ and $10^{13}\msun$.
-%\gb{might be useful here to indicate with horizontal lines the stellar mass range for the dwarf systems and the massive galaxy systems}
+    By requiring that the FoF group virial mass does not exceed the above limits, we ensure that there are no subhalos more massive than these limits that will perturb the dynamical state of identified pairs.
+    For example, selecting low mass pairs from the low mass FoF groups ensures that the selected pairs are not satellite systems of high mass subhalos. 
+    % reworded for clarity
+    %We have confirmed that over 99\% of subhalos selected from FoF groups that obey the listed mass limits are isolated; meaning, they are not within $1.5\,\Mpc$ of perturbers more massive than the mass of the pair.
+    \add{Over 99\% of subhalos selected from FoF groups in these mass limits are not within $1.5\,\Mpc$ of a more massive perturber at $z=0$.}
+
+    From the set of FoF groups that pass the group mass cut, we create a catalog of all subhalos within each FoF group that pass a current ``minimum mass" threshold.  
+    At the given snapshot, we require a minimum subhalo mass \Mhalo\ to be:
+    \begin{equation*}
+    \mbox{\textbf{minimum subhalo mass:}}\,
+    \Mhalo > 1\times10^{9}\Msun.
+    \end{equation*}
+    \Mhalo\ is given by the \texttt{SubhaloMass} field in the group catalogs, and is the total combined mass of all bound dark \textit{and} baryonic matter.
+    This ``minimum mass" threshold ensures that subhalos are resolved into $>100$ dark matter particles, and thus should be robustly identifiable using the \subfind\ and \sublink\ algorithms~\citep{RG2015}.
+
+    For each subhalo that passes both criteria, i.e.
+the subhalo belongs to either a high mass or low mass FoF group and also passes the ``minimum mass" threshold, we use the \sublink\ merger trees to identify the maximum subhalo mass achieved by the subhalo, \Mpeak.
+    We consider only the given snapshot and all previous snapshots in the determination of \Mpeak.
+
+    All subhalos in a given snapshot that pass both the FoF group and ``minimum mass" selection criteria form our full sample of subhalos, which we call the \subcat. 
+    The catalog contains subhalos at each snapshot from $z=0-\sim4.2$ (snapshot numbers 20-99) and their associated properties, namely: Subhalo ID, FoF Group Number, current subhalo mass \Mhalo, and peak subhalo mass \Mpeak.
+    At z=0, this selection process results in 44656 subhalos in low mass groups and 38350 subhalos in high mass groups.
+
+    From here, we will use additional selection criteria to identify pairs of subhalos in each group.
+% End choosing halos     %
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%    
+% Abundance matching section %
+    \subsection{Abundance matching} \label{sec:methods-am}
+    We utilize a stellar mass to halo mass (SMHM) relationship to assign stellar masses to each of the subhalos in our \subcat.  
+    There are a few reasons we opt to assign stellar masses to our subhalos, rather than use those computed directly from the stellar particles in TNG100.
+
+    \add{First, and primarily, utilizing an abundance matching prescription enables the direct comparison of results between dark matter only and full hydrodynamics simulations, since the stellar masses are assigned in an identical and prescriptive way.
+    We make a brief note of results for our equivalent analysis using the dark matter only, TNG100-Dark simulation, in Sec.~\ref{sec:disc-dark}.}
+
+    \add{Second, while the SMHM function of \tng{} at $z=0$ closely reproduces the profile of the SMHM relation from various abundance matching and semi-empirical models~\citep{TNG5,Nelson2019}, using stellar masses as calculated from abundance matching allows us to avoid any simulation-dependent stellar mass effects.
+    In particular, we would like to avoid a dependence between our results and the particular subgrid physics model implemented in \tng{}.}
+
+    \add{Third, abundance matching allows us to account for the observed spread in the SMHM relationship, as we can sample the relation many times to get a distribution of stellar masses for each subhalo in the simulation.
+Otherwise, we would only be able to perform this analysis once given the set of stellar masses from the simulation.
+    This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large, between $\sim 0.3$ for $M_{h}\sim 10^{10}\Msun$ up to $\sim 1$dex for $M_{h}\sim10^{8}\Msun$~\citep{Munshi2021}.
 }
-\end{figure}
 
-\subsection{Selection criteria}\label{sec:selectionCrit}
-In this section, we will outline the selection criteria used to identify dwarf subhalo and massive subhalo pairs in the \ID\ and \IH\ simulations.
-In short, we first make a series of mass cuts on the group mass to constrain the masses of the halos that may be contained in the group and to ensure that the systems are relatively isolated.
-Then, the subhalos of each identified isolated group undergo further mass cuts until we are left with a sample of both dwarf and massive subhalo pairs.
-A summary of the mass criteria used for our selection can be found in Table~\ref{table:mass}.
+    %Primarily, applying an abundance matching prescription to assign stellar masses allows us to account for the observed spread in the SMHM relationship. 
+    %This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large, between $\sim 0.3$ for $M_{h}\sim 10^{10}\Msun$ up to $\sim 1$dex for $M_{h}\sim10^{8}\Msun$~\citep{Munshi2021}.
+    %While the SMHM function of \tng{} at $z=0$ closely reproduces the profile of the SMHM relation from various abundance matching and semi-empirical models~\citep{TNG5,Nelson2019}, using stellar masses as calculated from abundance matching allows us to avoid any simulation-dependent stellar mass effects.
+    %Finally, utilizing an abundance matching prescription enables direct comparisons of results between dark matter only and full hydrodynamics simulations, since the stellar masses are assigned in an identical way.
+    %We make a brief note of results for our equivalent analysis using the dark matter only, TNG100-Dark simulation, in Sec.~\ref{sec:disc-dark}.
 
-\subsubsection{Isolation}
-We are interested in the occurrence rates of subhalo pairs in pristine environments to ensure that the dynamics of the subhalos in groups are unaffected by nearby massive perturbers.
+    We use the abundance matching relationship presented in~\citet{Moster2013}.
+    %which provides an analytic prescription to assign stellar masses to dark matter halos. 
+    \add{The SMHM relationship therein provides an analytic prescription to assign stellar masses to dark matter halos as a function of subhalo mass and redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with a larger scatter at lower halo masses.
+    We were careful to choose the input subhalo mass and redshift that would assign the most accurate stellar masses to each halo given their individual histories.}
+    %The~\citet{Moster2013} relationship is a function of subhalo mass, redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with a larger scatter at lower halo masses.
+    %incomplete thought: The subhalo mass and redshift that are used to calculate the stellar mass impacts the stellar mass that is assigned to a given halo.
+For example, a satellite subhalo may have some of its associated dark matter stripped away by its host, while the stellar mass remains roughly the same throughout the loss of a significant portion of
 
-FoF groups are large collections of nearby associated particles throughout the Illustris simulation.
-As there is no boundedness criteria for these groups, we wanted to ensure that pulling pairs of subhalos from FoF groups would yield a sample of subhalos that were dynamically unperturbed by more massive nearby structures.
-We calculated the isolation fraction
-\begin{equation}
-f_{\rm iso} = N_{\rm Hill} / N_{\rm FoF}
-\end{equation}
-where $N_{\rm Hill}$ is the number of pairs of subhalos that satisfy the Hill radius criterion (see Appendix~\ref{app:hill}), and $N_{\rm FoF}$ is the number of pairs from FoF groups, and found that $>99.8\%$ of all pairs identified in FoF groups are considered isolated by the more stringent Hill radius criterion.
-We thus used these FoF groups as a proxy for isolation, and considered \textit{all} pairs from FoF groups isolated.
+    The abundance matching prescription is calibrated for centrals of FoF groups, thus we elect to use the maximum subhalo mass \Mpeak\ in the stellar mass calculation, rather than the subhalo mass at the given snapshot \citep[see][]{Besla2018}.
+    Using \Mpeak\ mass allows us to remain robust to scenarios in which a secondary has formed most of its stars, then loses a significant portion of its dark matter content through tidal interactions with a primary, but retains the bulk of its stellar content.
+    In fact, \citet{Munshi2021} found that the stellar mass of subhalos at $z=0$ in the ``Marvel-ous Dwarfs" and ``DC Justice League" zoom simulations are more closely correlated with $M_{\mathrm{peak}}$ than the $z=0$ halo mass for halos with peak halo mass $10^8<M_{\rm peak}<10^{11} \Msun$.
 
-\subsubsection{Group mass cuts}
-% why group cuts
-We first make a series of cuts on the group masses reported in the \ID and \IH catalogs at each snapshot out to $z\sim12$.
-Since we are interested in subhalo pairs in two different mass regimes, we will use different mass criteria to isolate groups that may contain dwarf pairs, and groups that may contain more massive galaxy pairs.
-As mentioned, we do not search for dwarf pairs in massive groups
-since the central subhalos of these more massive groups would perturb the dwarf system.
+    We also use the current redshift of the given snapshot, $z_{\mathrm{snap}}$, of each subhalo in the stellar mass calculation. 
+    Using $z_{\mathrm{snap}}$ means that we account for changes in the stellar mass of both the primary and secondary halo, even after the secondary has entered the primary's halo. 
+    This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{Geha2013}, which found that dwarfs $>1.5\,\Mpc$ from a MW-type galaxy are often star forming and rarely quenched.
+    Additionally, the SAGA survey has found that large satellites of MW-type galaxies are often very blue, with infall into the halo spurring high rates of star formation due to the large gas fraction in dwarfs~\citep{Mao2021}.
+    Thus, our abundance matching prescription is of the form $\ms{}=f(\Mpeak,z_{\mathrm{snap}})$.
 
-% actual numerical values of 
-Group mass cuts are performed on the group mass provided in the SUBFIND catalogs, \texttt{Group\_M\_TopHat200}, which is the total mass enclosed in a sphere whose mean density is $\rho_c \Delta_c$.
-The {\bf dwarf groups} must have a group mass $8\times10^{10} < \rm M_g < 5\times10^{11} M_\odot$ while {\bf massive groups} have mass $1\times10^{12} < \rm M_g < 4\times10^{12} M_\odot$.
-These dwarf and massive group masses are roughly representative of Magellanic Cloud analogs~\citep{besla12,moster13} and Local Group analogs respectively~\citep{vdm12ii}.
+    We calculate the stellar mass for a given subhalo by Gaussian sampling each of the fitting parameters of the analytic framework from~\cite{Moster2013}, in order to account for the spread in the SMHM relationship.
+    %We generate a single stellar mass ``realization" of the full \subcat\ by calculating a stellar mass for each subhalo, using an independent draw from the SMHM distribution for each subhalo. 
+    \add{We generate a single stellar mass ``realization" using an independent draw from the SMHM distribution to calculate a stellar mass for each subhalo of the full \subcat.}
+    For each snapshot, we repeat this process 1000 times to generate 1000 separate realizations of assigned stellar masses for the \subcat.
+    The resulting catalog is called the \starcat, and consists of the set of all subhalos from the \subcat, as well as the 1000 stellar mass realizations. 
+    Each realization is treated as an independent sample of galaxy stellar masses, which will allow us to report realistic spreads of pair properties.
 
-In addition to %overall 
-group mass cuts, we ensure that each group has at least one subhalo that satisfies the following properties:
-\begin{itemize}
-    \item \textit{dwarf} - maximal halo mass is $8\times10^{10} < \rm M_{\rm max} < 5\times10^{11} \rm M_\odot$ with mass at the snapshot of interest M$_{\rm snap} > 1\times10^{10} \rm M_\odot$
-    \item \textit{massive} - maximal halo mass is $1\times10^{12} < \rm M_{max} < 4\times10^{12} \rm M_\odot$ with mass at the snapshot of interest M$_{\rm snap} > 5\times10^{11} \rm M_\odot$. 
-\end{itemize}
-This ensures that each group has at least one subhalo that will serve as a primary galaxy for the catalog after stellar mass cuts are applied (Sec.~\ref{sec:primaries}).
+% End Abundance matching %
+%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-We only consider subhalos in each of these groups that have subhalo masses $M_{H}>10^9M_{\odot}$ at the given snapshot.
-This ensures that each dwarf pair will consist of subhalos that are resolved into more than 100 dark matter particles at the snapshot of interest.
+%%%%%%%%%%%%%%%%%%%%%%%%%%    
+% Pair selection section %
+    \subsection{Pair selection}\label{sec:methods-pairs}
+    Starting from the \starcat, we outline the pair matching process used to generate the \paircat below. 
+    At each redshift, and for each stellar mass realization, we will identify subhalo pairs consisting of a ``primary" and a ``secondary", where primaries are the more massive of the pair by stellar mass.
 
-In practice we find that some low mass groups consist of a set of subhalos with only one or two subhalos with mass above our lower mass threshold of $10^9\msun$, while the remaining subhalos have lower mass.
-We refer to these types of groups as ``One Subhalo'' and ``Two Subhalo'' groups respectively, since they contain either one or two candidate primaries.
-Groups with three or more subhalos passing this lower mass threshold are called ``Three+ Subhalo'' groups.
+    \subsubsection{Selecting primaries}
+        Primary galaxies (equivalently, ``primary subhalos") are the most massive galaxy of their FoF group by stellar mass, such that each group will have a singular primary galaxy.  
+        Each stellar mass realization is treated independently, and so the subhalo identified as the primary of a group may change between stellar mass realizations.
 
-\begin{table*}[htb]
-  \begin{center}
-\begin{tabular}{ccccc|cccc}
-    & \multicolumn{4}{c}{Dwarfs} & \multicolumn{4}{c}{Massive} \\\hline\hline
-    z = &0&1&2&4&0&1&2&4 \\ \hline
-    Isolated Groups & \# & \# &\# &\#&\#&\#&\#&\#\\
-Primaries &  & &&&&&& \\
-Pairs &  & &&&&&& \\
-Major Pairs &  & &&&&&& \\
-Minor Pairs &  & &&&&&& \\
-Minor+ Pairs &  & &&&&&& \\\hline
-\end{tabular}
-\end{center}
-\caption{\label{table:counts}\kc{Placeholder for now} Number of groups, primaries, and pairs}
-\end{table*}
+        At a given snapshot, and for each stellar mass realization, we rank order the subhalos of each FoF group by stellar mass. 
+        Primaries are defined as the subhalo with the highest stellar mass ($M_{*1}$) in their FoF group that passes the following criteria:         
+        \begin{align*} 
+        \mbox{\textbf{low mass primaries:}}&\, 10^{8}< \rm M_{*1} < 5\times10^{9} \Msun \\ 
+        \mbox{\textbf{high mass primaries:}}&\, 5\times 10^{9}< \rm M_{*1} < 10^{11} \Msun.
+        \end{align*}
+        The stellar mass criteria is fixed, and \textit{does not change} as a function of redshift. 
+        At $z=0$, the stellar mass range for low mass primaries corresponds to isolated analogs of the LMC or M33, while the high mass primaries represent isolated analogs of the MW or M31.
 
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_counts.png}
-    \includegraphics[width=\columnwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_counts.png}
-    \caption{\label{fig:counts} The number of dwarf (top) and massive (bottom) groups primaries identified in each of the \textit{Illustris-Dark} and \textit{Illustris-Hydro}.
-The linestyle represents the different types of groups where the primaries are identified.
-The dotted (dashed) lines show the number of primaries in
-    groups with only one (two) subhalo(s) with subhalo mass greater than $10^9 \rm M_\odot$. Dot dashed lines show the number of primaries in 
-    groups with three or more subhalos with a mass greater than $10^9 \rm M_\odot$.
-We find that \textit{Illustris-Hydro} has significantly many more primaries in single and double-subhalo groups, which may be a result of different dwarf merger rates in the two simulations.
-Since there are many more single-subhalo dwarf groups in \textit{Illustris-Hydro}, the fraction of primaries with a companion will be significantly suppressed compared to \textit{Illustris-Dark}.
-    There are almost no massive groups that contain only one or two subhalos that pass our lower subhalo mass threshold, thus nearly 100\% of the identified primaries are in groups with at least 3 massive subhalos.}
-  \end{figure}
+        Since our selection is based on stellar mass, and there is a large spread in the SMHM relation, a primary subhalo may not be the most massive subhalo in terms of total subhalo mass.
 
-\subsubsection{Dwarf and Massive Primaries}\label{sec:primaries}
-Dwarf and massive primaries are defined to be the most massive subhalo in each group with the following properties:
-\begin{itemize}
-  \item \textit{dwarf} - stellar mass between $10^8 \leq \rm M_{prim,*} \leq 5\times 10^9 \msun$
-  \item \textit{massive} - stellar mass between $5\times 10^9 \rm M_{prim,*} \leq 1\times 10^{11} \msun$.
-\end{itemize}
-We make mass cuts using the stellar masses of the subhalos in order to best compare our results with observational studies.
-%as this is the data that we will be collecting observationally.
-Thus, making cuts on the stellar masses of these subhalos allows us to more directly apply our results to observational studies.
+    \subsubsection{Selecting secondary companions}
+        As before, the selection of secondary companions occurs independently for each stellar mass realization, and for each snapshot. 
+        Secondary subhalos are defined as the second most massive subhalo in a FoF group by stellar mass ($M_{*2}$). 
+        Secondary subhalos must also have a stellar mass ratio with respect to primaries of:
+        \begin{align*}
+            &\mbox{\textbf{stellar mass ratio:}}\,      
+            M_{*2}/M_{*1} > 1/10.
+        \end{align*}
 
-The average number of dwarf and massive primary subhalos  %at each of the considered redshifts 
-is plotted as a function of redshift in Fig.~\ref{fig:counts}.%, and 
-A subset of this data can be found in Table~\ref{table:counts}. Also plotted is the number of primaries in groups with the marked number of companions.
+        We do not include companions with a stellar mass ratio $M_{*2}/M_{*1} <1/10$ as we will be limiting our pair sample to traditional definitions of major and minor pairs, 
+        which are typically defined to have stellar mass ratios $M_{*2}/M_{*1} > 1/10$~\citep[i.e.][]{Lotz2011, RG2015, Snyder2017, Duncan2019, Wang2020, Guzman-Ortega2023}.
 
-We find that the number of dwarf primaries increases from $z=4$ to about $z\sim0.5$, at which point the number of primaries decreases by approximately 15\% approaching $z=0$.
-There are significant differences in the number of dwarf primaries that belong to One- and Two-Subhalo Groups in \ID\ and \IH.
-\IH\ boasts about $2\times$ more primaries in One-Subhalo groups, 1.5-2$\times$ more primaries in Two-Subhalo Groups, and ~0.6$\times$ fewer Three-Subhalo groups than \ID.
+        Our subhalo ``minimum mass" threshold of $\Mhalo=10^9\, \Msun$ (described in Sec.~\ref{sec:methods-halos}) corresponds to a mean stellar mass of approximately $10^6\,\Msun$ at $z=0$. 
+        This stellar mass is well below the 1/10 criteria for the lowest stellar mass primary considered ($M_{*1} > 10^8 \, \Msun$), ensuring that our pair sample will be complete even at the lowest stellar masses considered.
 
-The number of massive primaries increases consistently from high to low redshift.
-There are very few massive groups with only one or two large ($\rm M_{H} > 10^9\sun$) subhalos, since groups of this mass scale typically host at least one large subhalo and its companions and satellites.
-Thus, almost 100\% of the massive primaries reside in ``Three-Subhalo'' groups.
+    \subsubsection{Creating the pair catalog}
+        Pairs consist of a single primary and secondary in a FoF group as defined via the criteria above, such that only one pair is identified in a single FoF group. 
+        Each pair is categorized as either a major or minor pair based on the stellar mass ratio between the primary and secondary. Following, e.g. \cite{Lotz2011, RG2015}, 
+        the stellar mass ratio criteria for major and minor pairs are:
+        \begin{align*} 
+        \mbox{\textbf{major pair:}}&\, \frac{1}{4}\leq \frac{\rm M_{*2}}{\rm M_{*1}}< 1 \\ 
+        \mbox{\textbf{minor pair:}}&\, \frac{1}{10}\leq \frac{\rm M_{*2}}{\rm M_{*1}} < \frac{1}{4}.
+        \end{align*}
 
-\subsubsection{Pairs}
-The different pair types are defined to contain a dwarf or massive primary subhalo with a secondary subhalo:
-\begin{itemize}
-    \item \textit{Major Pairs}: with stellar mass $M_{\rm sec,*}$ such that $1/4 \leq M_{\rm sec,*}/M_{\rm prim,*} \leq 1$.
-    \item \textit{Minor pairs}: with stellar mass $M_{\rm sec,*}$ such that $1/10 \leq M_{\rm sec,*}/M_{\rm prim,*} \leq 1/4$.
-    \item \textit{Minor+ Pairs}: with stellar mass $M_{\rm sec,*}$ such that $M_{\rm sec,*}/M_{\rm prim,*} \leq 1/4$.
-This set of pairs \textit{includes} the whole set of minor pairs, but also includes pairs whose mass ratio is less than 1/10.
-\end{itemize}
-The MCs, as well as the MW+LMC system and M31+M33 system, have a stellar mass ratio of approximately 1/10, and thus would be classified as minor pairs according to our analysis.
-All pairs must be separated by at least 15 physical kpc so that the pairs are well resolved into individual component subhalos in \SUBFIND.
+        For each pair, we calculate the physical separation (proper \kpc, not comoving \kpc) between the two subhalos using the \texttt{SubhaloPos} field from the subhalo catalogs.
+We require that each pair have a minimum separation of $10 \, \kpc$ between primary and secondary to limit the impact of very close subhalos becoming indistinguishable in \subfind\ as a result of the resolution limit due to the softening length.
+        % The minimum separation cut is more than 10 times the smoothing length of the simulation at $z=0$, which ensures that  can identify the subhalos as distinct objects XXXXX ADD CITATION HERE - vicente?
+subfind paper?.
+%\citep{Besla2018}.
 
-%
-%%
-%%%
-%%%%
-%%%
-%%
-%
+        If a primary subhalo does not have a companion that meets the stellar mass ratio criteria and separation criteria, the subhalo will still be considered a primary. 
+        We refer to all primaries that do not have a companion with these criteria as ``isolated primaries," including primaries with a companion that meets the stellar mass ratio criteria but has a separation $<10\,\kpc$.
+        The total number of primaries includes both isolated primaries and those with selected companions and is larger than the total number of pairs.
 
-%%%%%%%%%%%%%%%%%
-\section{Results}\label{sec:results}
-%%%%%%%%%%%%%%%%%
-After collecting our sample of dwarf and massive pairs, we analyzed the frequency of occurrence as well as their properties, such as mass ratio and average kinematics of the pairs, as a function of time.
-By comparing results for groups identified in \ID\ and \IH , we can compare the effect that feedback prescriptions may have on the formation of low mass dwarf pairs vs.
-massive pairs, and search for differences in their kinematics, which ultimately dictate their merger rates.
+        For each snapshot and each of the 1000 realizations of the stellar mass in \starcat, we identify a set of isolated primaries and pairs. 
+        Additionally, within each realization, no single subhalo can be a part of two separate pairs, such that the primary and secondary of every pair are unique to the pair.
+        The final \paircat\ is the collection of all isolated primaries and pairs at each snapshot and includes the following information. 
+        For each isolated primary, we store the current subhalo mass (\Mhalo) and stellar mass from the given realization. 
+        For each pair, we store the primary and secondary subhalo masses (\Mhalo) and stellar masses, the pair separation, and the virial radius of the FoF group (see Sec.~\ref{sec:methods} for virial definitions).
 
-Although we collected pairs out to redshift $z\sim12$, the number of identified primaries drops significantly approaching $z\sim4$.
-As such, the following analysis will focus only on a redshift range of $z=0-\sim4$, where the statistics are more meaningful.
-In Sec.~\ref{sec:ratios}, we will discuss the stellar, current halo, and maximum halo mass ratios for our sample, which will enable us to examine the mass evolution of these systems.
-In Sec.~\ref{sec:pairFracs}, we present the main data product of this paper, namely the pair fractions for dwarf and massive major and minor pairs in \ID\ and \IH.
-In Sec.~\ref{sec:kinematics}, we discuss our findings on the kinematics of our population of pairs.
-
-%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %
-% description of the stellar and halo mass evolution
-\subsection{Stellar and Halo Masses and Ratios}\label{sec:ratios}
+%%%%%%%%%%%%%%%%%%%%%%%%%
+% begin pair prop plots %  
 \begin{figure*}[htb]
     \centering
-    \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_stellarMass.png}
-    \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_stellarMass.png}
-    \caption{\label{fig:stellarMass} The average stellar mass of primaries identified in the \ID\ (left) and \IH\ simulations, as a function of redshift.
-(Top) Mean stellar masses of dwarf pair primaries, where the shaded regions indicate the $1\sigma$ spread computed over 50 realizations of AM relation per snapshot.
-%dwarf pairs.
-    (Bottom) The same as Top panels, but for the primaries of massive pairs.
-For dwarf pairs, the average primary stellar mass of minor pairs is much higher than for major pairs, although is roughly the same for massive pairs.
-The average primary stellar mass increases as a function of time for both dwarf and massive pairs.
-There are no major differences between the primary stellar masses in \ID\ and \IH, which indicates that the max subhalo masses of the primaries in each of the simulations is roughly equivalent.
-     \kc{not sure why the spread of all massive pairs is so small.... gotta check that!}}
+    \includegraphics[width=\textwidth]{counts_1000.png}
+    \caption{(Top) Number of isolated low mass (left) and high mass (right) primaries and pairs as a function of redshift.
+    The solid and dashed lines represent the median of the set of total counts from each of the 1000 stellar mass realizations in the \paircat, while the shaded regions depict the 1-99 percentile spread of the median.
+    There are approximately 8 times as many low mass primaries as high mass primaries. 
+    % dwarf galaxies
+    The low mass primary count (left) peaks at $z=1$ (with $\sim 15000$ primary subhalos per realization), while the low mass pair count peaks at $z=2$ (with $\sim 3000$ pairs per realization). 
+    % Massive galaxies (right)
+    The high mass primary count (right) peaks at $z\sim1$ (with $\sim 1900$ primary subhalos per realization), while the high mass pair count peaks at $z=0$ (with $\sim 700$ pairs per realization). 
+    (Bottom) Total pair fraction (fraction of primaries with a major or minor secondary) as a function of redshift (see Sec.~\ref{sec:pairprops} for calculation details).
+    The low mass total pair fraction is approximately flat between $z=2.5-4$, and decreases from $z=2.5$ to $z=0$. 
+    The high mass total pair fraction is flat or decreasing from $z=1$ to $z=4$, but peaks sharply between $z=0-0.25$.}
+    \label{fig:counts}
 \end{figure*}
 
-\begin{figure*}
+\begin{figure*}[htb]
     \centering
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_massRatio.png}
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_massRatio.png}
-  \caption{\label{fig:massRatios} 
-  The median and 25\%-75\% interquartile range of stellar, current subhalo, and maximum subhalo mass ratios of major (solid) and minor (dashed) pairs in \ID\ and \IH\ for both dwarf and massive regimes.
-As expected, the stellar mass ratios for major and minor pairs, as well as dwarf and massive pairs, are nearly identical between \ID\ and \IH, as we are using the same stellar mass cuts to define these populations of subhalo pairs in %between
-  each simulation.
-  In all cases, the ratio of current subhalo masses as a function of time is always smaller than the max halo ratio.
-This indicates that the secondaries may be losing a significant portion of their mass to the primary between the time of max mass and the snapshot of interest.
-  %\kc{why don't these lines converge at high z?}. \gb{Can you quote the mean values of interest?}
+    \includegraphics[width=\textwidth]{smrdist_1000.png}
+    \caption{Stellar mass ratio distribution of all low mass (top) and high mass (bottom) pairs for all 1000 stellar mass realizations combined at each redshift.
+Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$.
+Overall, the stellar mass ratio distribution of major and minor pairs of low and high mass galaxies show little evolution from $z=4$ (right) to $z=0$ (left).
+    Major pairs make up $51-55\%$ of the total sample of pairs at every redshift for both low and high mass pairs.}
+    \label{fig:massratio}
+\end{figure*}
+% end pair prop plots %  
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%
+% Pair prop. start %
+\section{Sample: Overview of pair properties} \label{sec:pairprops}
+    Utilizing the \paircat, for each snapshot, we compute the total number of primaries (isolated and paired) and pairs (including major and minor) in each of the 1000 realizations.
+We then compute the median and 1st and 99th percentile spread on the median over all realizations\footnote{The spread on the median of each realization is very small.
+Thus, we opt to show the 1st and 99th percentile spread rather than those which align with traditional definitions of 1$\sigma$ or 2$\sigma$ measurements}.
+    Additionally, we compute the low and high mass total pair fraction for each individual realization, defined here as the ratio of the total number of pairs ($N_{\mathrm{pairs}}$) to the total number of isolated \textit{and} paired primaries ($N_{\mathrm{primaries}}$):
+    $$f_{p}=\rm \frac{N_{\mathrm{pairs}}}{N_{\mathrm{primaries}}}.$$
+    We again compute the median and spread over all 1000 realizations.
+
+    Fig.~\ref{fig:counts} shows the median number (solid and dashed lines) of identified low and high mass primaries and pairs over the redshift range $z=0-4$.   
+    The shaded regions show the 1-99\% spread of the set.
+
+    The number of identified primaries is lowest at $z=4$, and rises to a maximum around $z=1$ for both low and high mass primaries.
+    The median count of low mass primaries (green solid line in top left panel) reaches a maximum of $15,545^{+89}_{-88}$ halos at $z\sim0.6$, then decreases by $\sim22\%$ to $12,002^{+85}_{-86}$ halos at $z=0$.
+    The count of high mass primaries (pink solid line in top right panel) reaches a maximum of $1901^{+16}_{-19}$ at $z=0.5$, and slightly declines to $z=0$. 
+    Our sample of high mass primaries represents approximately 20\% of all subhalos in TNG100 with the same range of stellar masses at $z=0$.
+    There are roughly 8 times as many low mass primaries as high mass primaries. \add{Note that the comoving volume of \tng{} is the same at all redshifts.}
+
+    Unlike the primary count, the pair counts for low and high mass pairs peak at very different redshifts. 
+    The count of low mass pairs (green dashed line) peaks much earlier, at $z=1.9$ with $2956^{+99}_{-95}$ pairs, and decreases to $896^{+51}_{-50}$ pairs at $z=0$.
+    The pair count for high mass galaxies (pink dashed line), on the other hand, behaves more similarly to the primary count, increasing from $z=4$ to $z\sim1$, then decreasing to $z=0.25$ before peaking with $647\pm27$ pairs at $z=0$.
+
+    The bottom panel of Fig.~\ref{fig:counts} shows the total pair fraction for low mass and high mass pairs, or equivalently, the fraction of primaries with a major or minor companion.
+    The total pair fractions for both low and high mass pairs are roughly flat for $z=2.5-4$, and display opposite behavior for low redshifts between $z=0-2.5$. 
+    The low mass total pair fraction decreases from $0.233^{+0.008}_{-0.009}$ to $0.075\pm 0.004$, a decrease of roughly $68\%$, while the high mass total pair fraction remains flat between $z=1-2.5$, ranging between $0.275$ and $0.351$.
+    At very low redshifts, from $z=0-0.25$, the high mass total pair fraction spikes sharply from $0.288^{+0.016}_{-0.013}$ to $0.359^{+0.015}_{-0.014}$, an increase of $37\%$.
+
+    In Fig.~\ref{fig:massratio}, we show the combined distribution of stellar mass ratios of every pair from all 1000 realizations in the \paircat.
+    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both low and high mass pairs.
+    In general, the shape of the distribution remains constant from $z=0$ (left) to $z=4$ (right) for both low and high mass pairs, and changes weakly as a function of mass scale and of redshift. 
+    There are between $\sim3.3-4.8$ times more pairs with mass ratios $\sim1/4$ than $\sim1/1$, and about $1.8-2.2$ times more pairs have $1/10$ than $1/4$. 
+    Roughly 2\% of the total pair population is a 1:1 mass ratio encounter; this is true for low and high mass galaxies and across all redshifts considered.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%
+% Begin Results section %
+\section{Results: The frequency of low mass and high mass pairs}
+\label{sec:results}
+
+We have created catalogs of isolated low and high mass galaxy pairs from $z=0-4.2$ in the TNG100 simulation. 
+In this section, we will analyze the frequency of major and minor pair types across cosmic time, with the goal of identifying potential differences between high and low mass galaxies. 
+In Sec.~\ref{sec:results-frac}, we examine the redshift evolution of the fraction of primaries with a major or minor companion (the ``pair fraction") and compare the results for low mass and high mass pairs.
+In Sec.~\ref{sec:results-frac-cuts}, we examine the redshift evolution of the pair fraction as a function of pair separation. 
+In Sec.~\ref{sec:disc-dark}, we briefly describe how our equivalent pair fraction analysis utilizing the TNG100-Dark simulation compares to the TNG100 results presented in the previous two sections.
+
+In the following analysis, we will treat each stellar mass realization in the \paircat\ as an independent sample. 
+At each snapshot, we calculate the median and 1st and 99th percentile spread on the median of the pair fractions in each of the 1000 realizations of the target pair sample.
+Each of the following figures shows the median as the solid or dashed lines, and the shaded regions correspond to the spread on the median.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+% Pair fraction section %
+    \subsection{Major and minor pair fractions}\label{sec:results-frac}
+    The major and minor pair fractions are computed in the way as defined in Sec.~\ref{sec:pairprops} Eq.~\ref{eq}, where $N_{\rm pairs}$ is the total number of major \textit{or} minor pairs in the sample.
+    For example, the low mass major pair fraction is the number of low mass major pairs divided by the number of low mass primaries, which can also interpreted as the likelihood of finding a major companion of an isolated low mass primary.
+
+    Fig.~\ref{fig:pairfrac} shows the pair fractions calculated for low and high mass pairs (including both major and minor pairs separately) as a function of time for $z=0-4$. 
+    Note that, as discussed in Sec.~\ref{sec:methods-pairs}, we adopt a lower stellar mass ratio floor of $1/10$, and consequently the total pair sample is dominated by major pairs.
+
+    The low mass pair fraction evolves distinctly from that of high mass pairs.
+    Low mass pair fractions for both major and minor pairs (green) are approximately constant from $z=3-4$, then decline monotonically to $z=0$.
+At $z=0$, the major pair fraction is $0.041^{+0.003}_{-0.004}$, while the minor pair fraction is $0.034\pm0.004$.
+    At $z=3$, the pair fractions have increased by $207\%$ to $0.126^{+0.008}_{-0.007}$ for major pairs and $0.111\pm0.008$ for minor pairs.
+
+    High mass pair fractions (pink) remain approximately constant for $z>1$, where the median of the major pair fraction fluctuates between 0.150-0.179, and the median for minor pairs fluctuates between 0.135-0.151.
+    Between $z=0.3$ and $z=0$, the major pair fraction increases from $0.163^{+0.011}_{-0.010}$ to $0.207^{+0.012}_{-0.014}$, while the minor pair fraction increases from $0.125^{+0.017}_{-0.014}$ to $0.152^{+0.016}_{-0.017}$.
+
+    The bottom panels of Fig.~\ref{fig:pairfrac} shows the low mass pair fraction subtracted from the high mass pair fraction (labeled ``$\rm High-Low$").
+    The difference between high and low mass pair fractions increases with decreasing redshift, peaking at $z=0$ with a difference of $0.166\pm0.013$ for major pairs and $0.111\pm0.017$ for minor pairs.
+    Thus, at low redshift, we expect both major and minor pairs to be more common in high mass galaxies than in low mass galaxies. 
+    From $z=2.5-4$, the difference is approximately 0, and thus both major and minor pairs of high and low mass galaxies are equivalently common at high redshift.
+
+    Overall, these results show that low mass and high mass pair counts evolve differently over time, particularly at very low redshift, despite the pair fractions being roughly equal at higher redshift.
+    The implications for the difference in the evolution of pair fractions for low mass and high mass pairs across time are discussed in detail in Sec.~\ref{sec:discussion}.
+
+        % pair fraction plot
+    \begin{figure*}[htp]
+      \centering
+      \includegraphics[width=\textwidth]{pairfrac_1000.png}
+      \caption{% Top plots ~
+        (Top) Median pair fraction as a function of redshift, defined as the fraction of low mass or high mass primaries with a major (solid) or minor (dashed) companion  (see Sec.~\ref{sec:methods-pairs}).
+\add{All pairs in the \paircat\ must have a minimum separation of at least $>10\kpc$, with no constraint on the maximum separation.}
+        Shaded areas show the 1-99 percentile range on the median (solid and dashed lines) from 1000 stellar mass realizations, as discussed at the beginning of Sec.~\ref{sec:results}. 
+            % low mass
+        Low mass major and minor pair fractions (green) are both at their minima at $z=0$, and increase by about 200\% by $z\sim2-2.5$, at which point they level off and remain constant from $z=3-4$. 
+            % high mass
+        On the other hand, high mass major and minor pair fractions reach their maxima at $z=0$, then abruptly decline until $z\sim0.25$ before remaining approximately constant from $z=1-4$. 
+        % Bottom plots ~
+        (Bottom) The median and $1$-$99$ percentile range of the subtracted difference between high and low mass pair fractions. 
+        The difference peaks at $z=0$ for both major and minor pairs, and declines with increasing redshift.
+        This panel shows that the redshift evolution of the pair fractions of low and high mass pairs proceeds differently, particularly at low redshift where pairs are more common for high mass galaxies than low mass galaxies.}
+      \label{fig:pairfrac}
+    \end{figure*}
+% end pair fraction 
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% begining separation cut-pair fraction results %
+
+\subsection{Major pair fractions as a function of separation}\label{sec:results-frac-cuts}
+    In this section, we analyze subsets of the low and high mass major pairs from the previous section that pass additional separation criteria. 
+    We study two different sets of separation criteria to compare the resulting pair fractions to the full sample shown in Fig.~\ref{fig:pairfrac}.
+    In  Sec.~\ref{sec:results-frac-vircut} we apply a separation criterion that requires secondaries to be within a given factor of the virial radius of the FoF group, which is a reasonable proxy for the virial radius of the primary.
+    In Sec.~\ref{sec:results-frac-sepcut}, we use a range of limits on the 3D pair separation, where limits are consistent with values adopted in the literature.
+
+    In all cases, solid lines correspond to the median pair fraction and shaded regions to the 1st--99th percentile, as explained at the beginning of Sec.~\ref{sec:results}.
+
+\subsubsection{Pair separation limits as a function of the virial radius of the FoF group}\label{sec:results-frac-vircut}
+    We calculate the pair fraction for subsamples of low mass and high mass major pairs by selecting only pairs that have separations less than some factor of the virial radius of its FoF group. 
+    Note that a minimum separation limit of $10\kpc$ is always applied to all of our pairs (see Sec.~\ref{sec:methods-pairs}). 
+    The virial radius is taken from the \texttt{Group\_R\_TopHat200} field in the group catalogs.
+
+    % GB added the caveat below - might need to edit 
+    Major pairs typically correspond to the two most massive subhalos in their FoF group. 
+    The virial mass of their FoF group is reasonably approximated by the combined subhalo mass of both galaxies in the pair.
+    The combined mass of major low mass galaxy pairs recovers on average 98\% of the FoF group mass, and the combined mass of major high mass galaxy pairs recovers an average of 93\%. 
+    For example, the mass of the Local Group is dominated by that of the MW and M31 \citep[e.g., ][]{Chamberlain2023}. 
+    The virial radius of the FoF group is thus reasonably approximated by the virial radius of a halo with a virial mass equal to the combined subhalo mass of the two major pair members.
+% note the subhalo mass of the two major pair members could be approximated using abundance matching
+
+    By focusing our separation criteria on the FoF group virial radius, the separation cut will vary both as a function of redshift and as a function of the combined mass of the pair consistently.
+    For the high mass FoF groups, the median virial radius at $z=[0,1,2,3,4]$ is $\sim(348, 206, 134, 97, 76)\kpc$. 
+    For the low mass FoF groups, the median virial radius at $z=[0,1,2,3,4]$ is $\sim[134, 85, 59, 43, 33]\kpc$.
+
+    We choose 6 subsamples, consisting of pairs with separations less than $0.25, 0.5, 1.0, 1.5, 2.0,$ and $2.5\Rvir$. 
+    The top row of Fig.~\ref{fig:vircut} shows the median pair fraction (solid lines) for high mass (pink) and low mass (green) pairs in each of the 6 subsamples. 
+    In the bottom row, we show the recovery fraction, which is the fraction of the total pair sample that is recovered by each subsample, i.e.
+the number of pairs that pass each separation criterion divided by the total number of pairs in the full sample presented in Sec.~\ref{sec:results-frac}.
+
+    As the pair separation limits increase (left to right), the recovery fraction increases, so too does the pair fraction as expected since each consecutive selection cut is less restrictive and will contain more of the full sample.
+    More than 75\% of the full pair sample is recovered at all redshifts when the sample contains all pairs within $2\Rvir$ (the two rightmost panels of Fig.~\ref{fig:vircut}).
+
+    All subsamples of high mass pairs display broadly the same pair fraction redshift evolution as the full high mass sample (pink line in left panel of Figure~\ref{fig:pairfrac}): each of the sub-sampled high mass pair fractions peak at $z=0$ and remain roughly constant or decrease at higher redshift.
+    The finer detail trends from the full sample, particularly the upturn at low z, are reasonably captured if $r_{\mathrm{sep}} < 0.5 \Rvir$, despite the recovery being $\sim$40\%. 
+    % The magnitude of the pair fraction as a function of redshift for the full sample is best captured if $r_{\mathrm{sep}} < 2.0\Rvir$.
+
+    The subsamples of low mass pairs, however, show a different trend from the full sample (green line in left panel of Figure~\ref{fig:pairfrac}) if the separation cut is too small. 
+    For $r_{\mathrm{sep}} < 0.25\Rvir$, the pair fraction is flat or decreasing as a function of redshift (especially for $z>1$), similar to the behavior for high mass pairs. 
+    For $r_{\mathrm{sep}} < 0.5\Rvir$ and $r_{\mathrm{sep}} < 1.0\Rvir$, the pair fraction rises to a peak at $z\sim2$ and then decreases. 
+    %edited 
+    When the separation is limited to $r_{\mathrm{sep}} < 1.5\Rvir$, the trends with redshift for the full low mass sample are recovered, particularly the roughly flat behavior from $z\sim2-4$, despite a sample recovery of $<75\%$.
+    % The magnitude of the full low mass pair fraction is recovered for $r_{\mathrm{sep}} < 2.0$\Rvir. 
+    We also find that differences between the redshift evolution of high mass pairs vs. low mass pairs (particularly at $z<2$) become apparent if $r_{\mathrm{sep}} < 0.5\Rvir$ for both galaxy types. 
+    Overall we find that recovering the redshift evolution of the pair fractions of all galaxy pairs requires a separation cut that contains at least the closest $\sim40-50\%$ of pairs from the full sample at all redshifts.
+
+    %figures
+    %%%%%%%%%%%%%%%%%%%%
+    \begin{figure*}[htp]
+        \centering
+        \includegraphics[width=\textwidth]{pairfrac_vircut.png}
+        \caption{\label{fig:vircut}The median and 1-99 percentile spread are shown by the solid lines and shaded regions, respectively. 
+        (Top) The median pair fraction of the subset of high mass (pink) and low mass (green) pairs with 3D separations within a given factor of the pair's FoF group virial radius.
+        Such a separation criteria will vary as a function of both the mass of the pair and the redshift. 
+        Recovering the redshift evolution seen for the total sample (left panel of Figure~\ref{fig:pairfrac}) requires separation cuts of $r_{\mathrm{sep}} < 1.5\Rvir$ for low mass pairs and $r_{\mathrm{sep}} < 0.5\Rvir$ for high mass pairs.
+        Recovering the differences between high and low mass pair fraction trends seen for the total sample at $z>2$, requires $r_{\mathrm{sep}} < 0.5\Rvir$ for both galaxy types. 
+        (Bottom) The recovery fraction, calculated as the fraction of the total collection of pairs recovered by the subset of pairs at the given separation cut. 
+        We find that recovering the redshift evolution of the pair fractions of all galaxy pairs requires a separation cut such that the number of close pairs constitutes more than $\sim50\%$ of the full sample at all redshifts.
     }
     \end{figure*}
+    %%%%%%%%%%%%%%%%%%%%
 
-In Fig.~\ref{fig:stellarMass}, we show the average stellar masses of the primaries of major and minor dwarf and massive pairs identified in \ID\ and \IH.
-We find that the average stellar masses of primaries increases over time, typically peaking at or near $z=0$.
-The average stellar mass of the primaries of minor and minor+ \textit{dwarf} pairs is much greater than for major pairs across both simulations.
-There are two explanations for this effect.
-Firstly, if many major pairs merge by low redshift, leaving behind a more massive central halo and smaller minor satellites, the expected stellar mass of primaries of minor pairs would be significantly higher than the stellar masses of primaries in major pairs.
-Secondly, because of the stellar mass floor applied to the dwarf sample, only the largest dwarf primaries are contained in the set of minor and minor+ pairs.
-%, since smaller primaries could not have companions with low enough stellar masses to pass both our lower mass floor and be included in the selection of minor pairs.
-However, the average stellar mass of major and minor massive pairs is roughly similar.
-Since the lower mass floor for massive secondaries is lower than for primaries (see Sec.~\ref{sec:selectionCrit}), minor massive pairs may have lower mass primaries than possible for the same range of stellar mass ratios for dwarfs.
+\subsubsection{Pair separation limits based on static 3D physical separation} \label{sec:results-frac-sepcut}
+    We calculate the pair fraction for subsamples of major low mass and high mass pairs by including only pairs with separations less than $[50,70,100,150,200,\mathrm{and\, }300]\kpc$.  
+    Note that this separation criteria does not vary as a function of redshift or mass of the pair, and that a minimum separation limit of $10\kpc$ is always applied (see Sec.~\ref{sec:methods-pairs}).
+    This separation criterion creates subsamples of the \paircat\ containing low and high mass pairs with separations between $10-50\kpc$, $10-70\kpc$, and so on.
 
-The stellar and dark matter mass ratios between galaxies or subhalos impact the timescale for the interactions that will occur between pairs owing to dynamical friction (in addition to kinematics, see Sec.~\ref{sec:kinematics}).
-Interacting subhalos of roughly equal mass may end up tearing each other apart and recombining as a completely new composite subhalo.
-However, when a large subhalo interacts with a much less massive minor companion, the minor companion may disrupt, forming stellar streams around the more massive primary, with very little disruption to the primary.
-Separating our collection of pairs by mass ratios will allow us to explore dynamics and interactions separately in these two regimes~\citep{cox08}.
-%https://ui.adsabs.harvard.edu/abs/2008MNRAS.384..386C/abstract
+    Fig.~\ref{fig:sepcut} shows the median pair fractions for the subsamples of pairs with separations lower than the physical separation listed at the top of each column. 
+    The bottom row of the plot shows the recovery fraction, or the number of pairs in each subsample compared to the full sample of major pairs. 
+    Again, as the maximum separation increases (left to right), so too does the pair fraction and recovered fraction of the subsample.
 
-In the following discussion, stellar mass ratios will refer to the AM stellar mass of the secondary companion subhalo over the AM stellar mass of the primary.
-Halo mass ratios refer to the subhalo mass of the secondary reported in the simulation catalog at that redshift, over the subhalo mass of the primary at that redshift.
-Maximum (max) halo mass ratio refers to the maximum or ``peak'' subhalo mass ever achieved by the secondary subhalo, over the peak subhalo mass achieved by the primary at any point in their evolution.
-Thus, stellar and halo mass ratios are calculated using values of the stellar and halo masses at the current snapshot, while the max mass ratio may use subhalo masses for the primary and secondary from different snapshots.
+    The low mass major pair fraction (green) maintains roughly the same behavior (decreasing with decreasing redshift) for each separation cut, and first recovers the redshift evolution and magnitude of the pair fraction of the full sample (left panel of Fig.~\ref{fig:pairfrac}) for a separation cut of $r_{\mathrm{sep}} < 150\kpc$.
+    This is not surprising based on our results from the previous section as this separation is larger than the median virial radius of the sample and the recovery fraction is larger than 0.50 at all redshifts (reaching nearly 100\% at $z\sim3$).
+    The low mass pair fraction does not change significantly by excluding pairs with separations $>150\kpc$.
 
-We present the median stellar mass ratios, current halo mass ratios, and maximum mass ratios for dwarf and massive major and minor pairs in Fig.~\ref{fig:massRatios}.
-Since pairs are selected based on their stellar mass ratios in each of the stellar mass realizations, the median stellar mass ratios of major and minor pairs is relatively flat across all redshifts and shows little difference between \ID\ and \IH.
+    On the other hand, none of the subsamples of the high mass pairs accurately recover the behavior of the full high mass sample. 
+    In particular, the redshift evolution of the pair fraction between $z=0.25-2.5$ is not readily distinguishable from that of low mass pairs for any subsample from a physical separation cut.
+    At higher redshifts, the median pair fraction increases rather than leveling off or decreasing as in the full sample.
+    Even for $r_{\mathrm{sep}}<300\kpc$, the high mass pair fraction peaks at $z=4$, at odds with results using the full pair sample or any of the virial radius cuts in the previous section.
 
-Since the stellar mass of each subhalo is assigned based on the subhalo`s maximal mass, we find, as expected, that the max mass ratio to evolve with redshift in the same way as the %stellar mass to halo mass
-AM relationship for a fixed stellar mass ratio.
+    By applying a separation cut that is constant as a function of redshift and mass of the system, the recovery fraction of the total sample varies markedly as a function of redshift.  
+    This is in stark contrast to results from the previous section where the recovery fraction was roughly constant as a function of redshift.
+    Because the same separation cut is applied to low and high mass pairs, the recovery fraction for low mass pairs is universally higher than for high mass pairs at each separation cut, which erases any differences in redshift evolution between the two galaxy types.
 
-However, the halo mass ratio may tell us about how these halos have evolved since they achieved their peak halo masses, including owing to interactions.
-In particular, we find that in all cases the halo mass ratio falls well below the max halo mass ratio, implying that the secondaries may be losing much of their peak halo mass, potentially to the primaries, thus reducing the halo mass ratio at each redshift.
+% Phyiscally motivated framework for the selection criteria.
 
-The time evolution of the
-The halo mass ratio for dwarf pairs increases as a function of time, 
-%suggesting that, on average, the secondaries are becoming more massive with respect to their primaries, 
-which could indicate that a number of high mass ratio (minor) pairs have merged by low redshift.
-% GB NOTE TO THINK MORE ABOUT THIS 
-However, this is not the case for massive galaxies. Rather, the median halo mass ratio remains approximately constant throughout the considered redshift range.
+    %figures
+    %%%%%%%%%%%%%%%%%%%%
+    \begin{figure*}[htp]
+        \centering
+        \includegraphics[width=\textwidth]{pairfrac_sepcut.png}
+        \caption{% top plot
+        (Top) The major pair fraction of the subset of high mass (pink) and low mass (green) pairs with 3D separations less than the value given at the top of each column. 
+        The median and 1-99 percentile spread are shown by the solid lines and shaded regions, respectively. 
+        The 3D separation cut does not vary as a function of redshift or mass of the system. 
+        The general redshift evolution of the full high mass pair sample (decreasing with redshift for $z>1$) is not recovered for any physical separation cut, while the behavior of low mass pair fractions are well recovered by the $r_{\mathrm{sep}}<150\kpc$ subsample.
+        The pair fractions for low mass and high mass pairs are virtually indistinguishable for separation cuts less than $70\kpc$. 
+        % bottom plot
+        (Bottom) The fraction of the total collection of pairs in the subset that passes each separation cut. 
+        The recovered fraction varies as a function of redshift because a constant separation is chosen. 
+        A higher fraction of low mass pairs are recovered than high mass pairs at all separation cuts. 
+        Less than 50\% of all high mass pairs have separations $r_{\mathrm{sep}}<70\kpc$ at all redshifts, and $>50\%$ of the full high mass sample is recovered at all redshifts only for $r_{\mathrm{sep}}<300\kpc$.
+        Between 20-60\% of low mass pairs have separations $r_{\mathrm{sep}}<50\kpc$ at all redshifts, while a separation cut of $r_{\mathrm{sep}}<150\kpc$ captures roughly 50-100\% of the low mass pair population at all redshifts.
+        }
+      \label{fig:sepcut}
+    \end{figure*}
+    %%%%%%%%%%%%%%%%%%%%
 
-% \kc{make plots of the halo mass, max mass, etc for prims and secos to confirm suspicions}
+    \subsection{Comparison between TNG100-1 and TNG100-Dark}\label{sec:disc-dark}
+    We repeated the entirety of our analysis using data from the TNG100-Dark simulation.
+    Each step in our selection criteria was repeated identically, including our selection of group halos, abundance matching process, and selection of primary and secondary halos.
+    We created an equivalent catalog to the \paircat\ containing only subhalo properties from the TNG100-Dark simulation, and calculated the low and high mass pair fractions for $z=0-4.2$.
 
-% dwarf pairs vs. massive pairs
-To understand the evolution of max mass ratios for massive pairs, it is important to remember that the abundance matching relationship is quite shallow at high subhalo masses and low redshifts.
-This means that, for a fixed stellar mass ratio, the possible corresponding halo ratio drops, as shown by the max halo mass ratio of massive pairs dipping below the stellar mass ratio at low redshift in Fig.~\ref{fig:massRatios}.
-%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %
+    We found that the redshift evolution of low mass and high mass pair fractions in the TNG100-Dark simulation mimic those of the TNG100 simulation. 
+    In particular, low mass pair fractions remain flat between $z\sim2-4$, and decline from $z=2$ to a minimum at $z=0$. 
+    High mass pair fractions likewise decrease with higher redshift for $z>1$, and peak at $z=0$.
+    The numerical value of the pair fraction at all redshifts is $\sim10\%$ larger in TNG100-Dark for both low and high mass pairs, and for major and minor pairs, which is likely a result of the suppressed abundance of low mass halos due to baryonic physics~\citep{chua17}.
 
-%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %
-% Pair fractions - description of pair frac plots! 
-\subsection{Pair fractions}\label{sec:pairFracs}
+    % As mentioned in a footnote in Sec.~\ref{sec:methods-halos}, the total halo mass of subhalos in the hydro simulation includes the mass of both dark matter and baryonic particles. 
+    % In TNG100-1, the DM particle mass is decreased XX\% compared to the DM particle mass in \tng100-1 Dark to account for the additional mass of baryons, such that the total mass of the halo will remain roughly the same between the dark matter only and hydro simulations.
+    % Since the~\citet{Moster2013} AM relation was calibrated using DM subhalos from the \texttt{MilleniumII} dark matter only simulation, we will use the total subhalo mass from the TNG100 hydro simulation as a proxy for the corresponding DM halo mass in the TNG100-1 Dark run, \texttt{SubhaloMass}.
+% end results
+%%%%%%%%%%%%%%%%%%%%%%
 
-\begin{figure*}
-  \centering
-  \includegraphics[trim={2.8cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_fractions.png}
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_fractions.png}
-  \caption{\label{fig:pairFrac} The fraction of primary subhalos with companions of different types, relative to all primary subhalos, is plotted as a function of redshift.
-Results for \ID\ are on the left and for \IH\ on the right.
-Dwarf Pairs are in the top panels and Massive Pairs are shown in the bottom panels.
-(Blue) All dwarf (massive) primaries with any companion that passes the lower stellar mass threshold of $10^8 \msun$ ($10^9 \msun$).
-The fraction of dwarf galaxy pairs of all types decreases steadily from $z\sim2.5$ to today.
-Massive galaxy pairs demonstrate the opposite behavior, increasing with decreasing redshift.
-(Purple) Primaries with a companion with a stellar mass ratio between $1$ and $\frac{1}{4}$ (major pairs).
-Massive major pairs show little evolution with redshift and good agreement between \ID\ and \IH\.
-In contrast, the fraction of dwarf major pairs increases with redshift, peaking at $z\sim$2.
-The fraction is lower in \IH\ than in \ID\.
-(Yellow) Primaries with a companion with a stellar mass ratio between $\frac{1}{4}$ and $\frac{1}{10}$ (minor pairs).
-In all cases the fraction of minor pairs rises slightly with increasing redshift.
-(Orange) Primaries with a companion with a stellar mass ratio less than $\frac{1}{4}$ and a stellar mass greater than $10^8 M_\odot$ (minor+ pairs).
-Dwarf minor+ pair fractions show little evolution with redshift, while massive minor+ pair fractions increase with decreasing redshift.
-% \kc{add blurb about how the relative ratio of major pair fractions to minor pair fraction may be something that's testable to distinguish between baryonic physics implementations at low mass scales.} \gb{state values throughout, might want to include different line types in the future}
-}
-\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Begin Discussion section %
+\section{Discussion}\label{sec:discussion}
+We performed a pair fraction analysis for low mass and high mass pairs in the TNG100 simulation from $z=0-4.2$, utilizing the full spatial information that simulations enable to ensure that the pairs are physically co-located as part of the same FoF Group.
+In this section, we discuss the broader impacts and implications of the behavior of high and low mass pair fractions over time.
 
-Pair fractions provide insight as to how likely it is to find two galaxies very nearby each other in observations.
-Pair fractions can be used to back out merger rates from observations where other traditional methods of determining merger rates, such as asymmetry and concentration parameters, may fail.
-However, as pair fractions have only been calibrated as a function of time for massive pairs, it is important to separately determine expected pair fractions for dwarf pairs, rather than simply extrapolating the results for massive pairs.
+In Sec.~\ref{sec:disc-LG}, we draw comparisons between our pair sample and various Local Group pairs to quantify the likelihood of finding isolated analogs of such pairs at higher $z$.
+In Sec.~\ref{sec:disc-comp}, we compare our results to previous studies of pair fractions that utilize simulations. 
+We discuss the observational implications of the pair fraction behavior of low mass pairs and high mass pairs as a function of redshift
+%and our suggestions for appropriate separation cuts in observational pairs 
+in Sec.~\ref{sec:disc-obs}.
+\add{We conclude by discussing some possibilities for the pair fraction difference between low and high mass pairs in Sec.~\ref{sec:disc-diff}}
 
-After each group's primary was identified, we considered the second most massive halo by stellar mass, and sorted the pairs by stellar mass ratio. The pair fraction was calculated as
-$$\rm F_{pair} = \frac{\rm N_{comp}}{\rm N_{prims}},$$
-where $\rm N_{comp}$ is the number of pairs with a companion of a certain type (i.e., a major or minor companion), and $\rm N_{prims}$ is the number of primaries.
-These values are computed for each stellar mass realization independently, and are then averaged for each snapshot.
-In Fig.\ref{fig:pairFrac}, we show the pair fractions of different pair types as a function of time out to $z\sim4$.
-The shaded regions represent the $1\sigma$ error on the average of the pair fraction over time, computed by conducting 50 realizations of the stellar catalog at each redshift by sampling the AM relation.
+   \subsection{Implications for Local Group Galaxies}\label{sec:disc-LG}
+    Our study encompasses the stellar mass range and stellar mass ratios of a few well studied pairs within the Local Group and Local Volume.
+    Thus, we can make predictions for the frequency of finding isolated mass analogs of these systems at $z>0$ for the first time. 
+    For example, isolated mass analogs of the following pairs are included in each specified sample:
+    the LMC--SMC and NGC4490-4485\footnote{NGC4490-4485 is a low mass ($M_* = 7.2 \mbox{ and } 0.82 \times 10^9\Msun$, respectively) galaxy binary that is $\sim7\Mpc$ away from the MW~\citep{Theureau2007,Pearson2018}.} (low mass minor pair), the MW--LMC and M31--M33 (high mass minor pair), and the MW--M31 (high mass major pair).
+    Note that both the NGC4490-4485 and MW--M31 pair pass all of our pair selection criteria, while the LMC--SMC,  MW--LMC, and M31--M33 are non-isolated pairs within a more massive group environment.
 
-We found that dwarf primaries are much more likely to have at least one major companion at redshifts $z>2$ than at $z=0$: approximately 10\% (8\%) of primaries in \textit{Illustris-Dark} (\textit{Illustris-Hydro}) have a major companion at high redshifts ($z>2$), though this fraction drops to 4\% by $z=0$ in both simulations.
-The fraction of primaries with a minor companion remains approximately constant from redshift $z=0-4$: $\sim$3-4\%($\sim$5\%) of primaries have a minor (minor+) companion in both \textit{Illustris-Dark} and \textit{Illustris-Hydro}.
+    Mass analogs of the MW--M31 pair are most common today (pink solid line in the left panel of Fig.~\ref{fig:pairfrac}). 
+    Given their large separation of $\sim$760 kpc, they would only be included in the $<2.5\Rvir$ panel of Figure~\ref{fig:vircut}.
 
-There is a slight suppression (between 1-4\%) in the dwarf pair fractions in \IH.
-As can be seen in Fig.~\ref{fig:counts}, \IH\ contains many more One-subhalo groups than \ID, the number of potential primary subhalos with no companions is much higher, resulting in a decrease in the pair fractions across all pair types between \textit{Illustris-Dark} and \IH.
+    We find that isolated mass analogs of the LMC--SMC and NGC4490-4485 are roughly three times as common at $z>3$ than at $z=0$ (green dotted line in the right panel of Fig.~\ref{fig:pairfrac}). 
+    These high $z$ pairs may enter a more massive group halo to become satellites of a larger galaxy~\citep[like the LMC--SMC, ][]{Besla2007,Patel2017a-Orbits}, or if they remain isolated, may continue to merge in a manner similar to NGC4490-4485~\citep{Pearson2018}.
 
-The pair fraction of massive subhalos evolves dramatically differently than their dwarf counterparts, with the pair fraction either remaining constant or \textit{increasing} at low redshifts, and is much higher than the fraction of dwarf primaries with companions.
-In particular, the fraction of massive primaries with at least one major companion in \ID\ remains approximately constant for redshifts of $z=0-4$ at between $15-20\%$, while the same pair fraction in \IH\ increases from $\sim12\%$ to $20\%$ by $z=0$.
+    Isolated mass analogs of the MW--LMC and M31--M33 systems are equally likely at $z>1$ as they are at present (right panel of Figure~\ref{fig:pairfrac}). 
+    If we fold in the present-day separation of the MW--LMC system ($\sim50 \kpc$), this high mass minor pair becomes rare at low~$z$\footnote{Fig.~\ref{fig:sepcut} displays pair fraction trends for major pairs.
+The equivalent plot for minor pairs, which we did not include here, shows the same trends as the major pairs, particularly in the $<50\kpc$ panel where the pair fraction for high mass minor pairs is $<0.02$ at $z=0$.}.
+Specifically, we find that 2\% of MW's would host such a close LMC at $z=0$, which is consistent with other cosmological studies, such as \citet{Patel2017a-Orbits}, which finds that 3.8\% of MW-mass halos host an LMC-mass analog within 50 kpc at $z=0$.
+    We also find that such systems (high mass minor pairs with a low separation) are 2-3 times more common at high~$z$.
+M31--M33 analogs, which have higher separations $(\sim200\kpc)$, are more common than MW--LMC analogs at all redshifts.
 
-There is a slight difference between the behavior of the fraction of massive primaries in \ID\ and \IH\ for ``All Pairs'' and major pairs.
-In particular, there is a sharp uptick in the fraction of primaries with these types of companions at $z\sim1$ in only \ID.
-This fraction then declines to $z\sim$0.2, then rises sharply to $z=0$.
-While the sharp rise at low redshift is seen in \IH\ as well, the sharp increase at $z=1$ is not present.
-This means that there is a significant difference in the fraction of primaries expected with a major companion between the two simulations.
-In particular, the fraction of major pairs peaks at $z=0$ in \IH, while the fraction of major pairs in \ID is smaller than at $z=1-3$.
-This simulation-dependent behavior is not present in the minor pairs.
+\subsection{Comparison to existing pair fraction studies}\label{sec:disc-comp}
+    A direct comparison to pair fractions reported from observations is not straight-forward, as observationally selected pairs suffer from contamination due to projected pairs and restrictive separation criteria that exclude more widely separated pairs.
+    Instead, we compare our results to pair fractions and merger rates reported by other studies of the Illustris cosmological simulations to establish the reliability of our findings.
 
-There is a difference 
-%\gb{quantify} 
-in the relative pair fractions of major and minor dwarf pairs at high redshift, since there is such a dramatic suppression of the fraction of primaries with a major companion.
-If this can be observationally constrained, it may help us to test %say something} about
-the baryonic physics implemented in cosmological hydrodynamic simulations. %the full hydrodynamic simulation and its impact on dwarf subhalos.
-%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %
+    % low mass comparison
+        \citet{Besla2018} quantified low mass galaxy ($2\times10^{8} < M_{*} < 5\times10^{9}\,\Msun$) pair fractions at $z\sim0$ in the Illustris-1 hydrodynamic cosmological simulation, utilizing both projected and 3D pairs.
+        The selection criteria for projected pairs include a projected separation cut, $r_{p} < 150\,\kpc$, and a relative line-of-sight velocity difference $\Delta v_{\rm los} < 150\,\kms$.
 
-%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %
-% 
-\subsection{Kinematics}\label{sec:kinematics}
- We analyzed the average separations and relative velocities of dwarf and massive identified pairs in \ID\ and \IH.
-We found that there are discrepancies between the kinematics of pairs in the two simulations.
+        Searching for pairs in a projected space while having access to the true 3D positions and velocities of the galaxies allowed \cite{Besla2018} to quantify the contamination fraction of false pairs due to projection effect.
+        They found that up to $\sim40$\% of identified companions were unrelated but appeared to be close due to projection effects. 
+        The projected pair sample also enabled a direct comparison of the cosmologically-derived pair fractions with an equivalently selected low mass galaxy pair fraction from SDSS.
+        They found that the low mass major pair fraction from SDSS sample was in good agreement with the simulations.
+The~\citet{Besla2018} study points to the Illustris simulation's ability to robustly constrain pair fractions of low mass galaxies, specifically at low $z$.
 
- In all cases of massive and dwarf pairs, \IH\ boasts typically much higher relative velocities ($\sim20-40$km/s higher) between major pairs than \ID.
-While this velocity separation is less extreme for minor pairs ($\sim5-15$km/s higher), it is still evident, especially at higher redshifts ($z>2$).
+        We find reasonable agreement with the sample of physical 3D pairs in \cite{Besla2018}, which found a major pair fraction between 0.003-0.018 over a mass range of $2\times 10^8 < M_* < 5 \times 10^9$ $M_\odot$.
+        % used fig. 15 for these vals.
+        Our roughly equivalent low mass major pair sample, when adopting a separation cut of $r_{\mathrm{sep}}<150\kpc$, results in a major pair fraction of $0.022^{+0.002}_{-0.003}$ at $z=0$.
+We believe our pair fractions are somewhat higher than in \cite{Besla2018} as our stellar mass range for primaries extends to a lower value of $10^8\Msun$.
+As such, our results for low mass pairs are robust.
 
- \subsubsection{Separations}
- \begin{figure*}
-  \centering
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_separations.png}
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_separations.png}
-  \caption{\label{fig:separations} The mean magnitude of the relative 3D separation between primary and secondary subhalos in \ID\ and \IH\ as a function of time for dwarf and massive major (left) and minor (right) pairs.
-The drastic increase in average separation between subhalos as a function of time may indicate that only the longest-living, wide-separation circular-orbit pairs remain at low redshifts, since a majority of low separation pairs may have merged by low redshift.
-A more detailed analysis of the orbits of these systems will be the subject of future work.
-  (Left) Major pairs exhibit a small ($\sim 20$ kpc) separation difference between simulations across all redshifts for both dwarf and massive pairs. 
-  This may be due in part to a difference in the major merger timescales between the two simulations. 
-  (Right) Minor pairs exhibit roughly the same behavior for separations over time between the two simulations.
-  % GB : i would leave the below to the main text. 
-  %There is a population of low-separation subhalo pairs in \ID that cannot be matched to equivalent pairs in \IH.
-If merger timescales are lower or dynamical friction operates more efficiently in the hydro simulation, this could explain the lack of low separation subhalo pairs in \IH and, thus, the discrepancy between the two simulations.
-    %\gb{include LMC etc systems}.  
-  }
-\end{figure*}
+    % high mass comparison
+        For high mass pairs, \citet{Snyder2017} created mock catalogs using lightcones in the Illustris-1 simulation to select pairs in the same fashion as done in observations. 
+        They consider major pairs (stellar mass ratio $>1/4$) with: $1\times 10^{11}>M_{*,1} >1\times 10^{10.5}\Msun$, projected distances between $14\kpc-71\kpc$, and a redshift separation of $\Delta z<0.02(1+z_{pri})$, corresponding to a velocity separation of $<1.8\times10^4\kms$ at $z=2$.
+        They find that the major pair fraction is constant or decreasing for $z>1$, which is in good agreement with observational studies.
 
-Because this study utilizes subhalos selected in
-%Using 
-cosmological simulations, we can extract the
-%means we get 
-full 6D-phase information for subhalos, such as 3D position and velocity vectors. 
-%about the positions and velocities of the subhalos, and 
-We thus do not have to worry about projection effects artificially introducing projected pairs to our dataset.
-This also means that we can study the evolution of the physical separations of the subhalo pairs and how it might be impacted by mass scale or simulation physics.
-% and determine the characteristic behaviors of these systems.
+        \citet{Snyder2023} extended this work, utilizing the TNG simulation to create mock images of extragalactic survey fields mimicking future planned surveys like JADES.
+        From the mock images, they calculated the pair fraction for major pairs with projected separations between $5-70 \kpc$ and with redshift separations of $\Delta z< 0.02(1+z)$. 
+        Again, they found a flat or decreasing major pair fraction with increasing redshift above $z=1$.
 
-In Fig.~\ref{fig:separations}, we show the average separation of our selection of pairs (major and minor pairs, dwarf and massive galaxy pairs) selected in both the \ID\ and \IH simulations.
+        We cannot directly compare the values of the pair fractions in this work and \citet{Snyder2023}, since their work is done in projected space, but we can compare the trends as a function of redshift.
+        We find that the high mass major pair sample has a pair fraction that decreases with redshift above $z=1$, in agreement with \cite{Snyder2023}.
 
-We find that the average separation of all pair types increases towards lower redshift.
-This could indicate that the small separation pairs are merging, leaving behind the population of pairs that have longer-lived orbits.
-Alternatively, the population of pairs picked out with our selection criteria may be very different between lower and higher redshift.
-Following high redshift pairs and establishing their orbits through to $z=0$ will be the subject of future work.
+        In addition, \cite{RG2015} examine the merger rates of galaxies in the Illustris simulations as a function of stellar mass and redshift.
+        From their Figures~7 and 10, there is roughly a factor of 4 difference in the major merger rate for high mass ($M_* \sim 10^{11} \Msun$) vs.
+low mass ($M_* \sim 10^8 \Msun$) galaxies at $z=0$, and the difference becomes smaller at higher redshift.
+        % 1e8 -- 0.005-0.001 -- 5e9
+        % 5e9 -- 0.001 - 0.02 -- 1e11
+        A strong mass dependence of the galaxy merger rate at $z=0$ is also seen in Figure~12 of \cite{Guzman-Ortega2023}, as well as in results from semi-empirical models \citep{Stewart2009, Hopkins2010}.
+        From our Figure~\ref{fig:pairfrac}, there is also a factor of 4 difference in the pair fraction for high and low mass galaxies at $z=0$, which becomes smaller at higher redshift.
+        The consistency between our results and the variation with stellar mass and redshift of the galaxy merger rate suggests that our finding of different pair fractions between low and high mass galaxies at $z=0$, as well as their different redshift evolution trends, is indeed reliable.
 
-There is a slight ($\sim$20 kpc), but systematic, separation difference between major pairs in \ID\ and \IH\ in both of the dwarf and massive galaxy regimes.
-When we considered only subhalos that had separations $> 80$ kpc, the separation difference was resolved between the two simulations, indicating that a low separation population of pairs is absent in \IH.
-This population of subhalos may have merged earlier in the simulation.
-This will be studied in future orbital studies.
+\subsection{Implications for observational pair fraction studies}\label{sec:disc-obs}
 
-On average, minor pairs have much lower average separations than major pairs.
-This trend holds true between both simulations and both mass ranges.
-Interestingly, the separation discrepancy does not appear for minor pairs, which suffer less dynamical friction, supporting the hypothesis that major close pairs are being missed or merging faster in the \IH simulation.
+    In Sec.~\ref{sec:results-frac}, we presented the pair fraction of high mass and low mass galaxy pairs and found that the relative frequency of the two populations evolves distinctly from $z=0-4.2$.
+    High mass pair fractions peak at $z=0$, decrease from $z=0-0.3$, after which they are roughly constant or mildly decreasing with increasing redshift. 
+    In contrast, low mass pair fractions increase with increasing redshift until $z=2.5$, after which the frequency is roughly constant with increasing redshift. 
+    This behavior is seen for both major and minor pairs.
 
-\subsubsection{Velocities}
+    In Sec.~\ref{sec:results-frac-cuts}, we characterized the behavior of pair fractions for subsamples of the full pair catalog that pass additional separation cuts.
+    We found that physical separation cuts that do not vary as a function of time and mass eliminate the ability to distinguish the different redshift evolution of high and low mass pair fractions. 
+    %These rigid criteria are unable to capture trends from studies that find that the merger rate varies as a function of galaxy mass~\citep{Stewart2009, Hopkins2010}. 
+    Instead, by adopting a separation cut based on the virial radius of the group halo, we can accurately recover the different redshift evolution of low mass vs.
+high mass pair fractions, particularly at $z<2.5$.
 
-%% velocities 
-\begin{figure*}
-  \centering
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/dwarfs_comparison_velocities.png}
-  \includegraphics[trim={3cm 1cm 4cm 2.2cm}, clip,width=\textwidth]{../../papers/PairFrequency/figures/50Reals/massive_comparison_velocities.png}
-  \caption{\label{fig:velocities}The mean magnitude of the relative 3D velocity between primary and secondary subhalos in \textit{Illustris-Dark} and \textit{Illustris-Hydro} as a function of time for major (left) and minor (right) pairs.
-The relative velocities decrease significantly throughout time for all dwarf and massive galaxy pairs.
-Note that the relative velocities are systematically higher for all pairs in \textit{Illustris-Hydro} (by 15-50 km/s), though the differences are smaller for minor pairs and at low redshift.
-This discrepancy is likely related to the similar discrepancy seen in the separations (Fig.~\ref{fig:separations}).% The collection of low-separation pairs in \textit{Illustris-Dark} that do not have counterparts in \textit{Illustris-Hydro} also had very low velocities, thus accounting for the difference between the dark and hydro simulations.
-%   \kc{can include line for LMC+SMC, MW+M31 (120 Van der marel from HST), M31+M33 and the meanings behind them.
-(MW+LMC is up at 320 and is at peri so this makes sense.) also need to talk about the low separation without the abundance matching bit}
-}
-\end{figure*}
+    % rewrote this, became the paragraphs below 
+    %To study the redshift evolution of galaxy pairs and recover differences in the behavior of low mass vs.
+high mass pairs, we advocate for a pair separation cut of  $r_{\mathrm{sep}} < 1.0\Rvir$, where $\Rvir$ can be inferred using an estimate of the combined dark matter mass of the pair.
+    % Taking the observed stellar mass of each pair member, the halo mass for each pair can be estimated using the SMHM relation \citep[e.g.,][]{Moster2013}. 
+    % The combined halo mass of the pair can then be used as a proxy for the virial mass of the FoF group ($\rm M_{vir}$) to compute the virial radius, e.g. 
+    % \begin{equation}\label{eq}
+    % \Rvir = \sqrt[3]{\frac{3\rm M_{vir}}{4\pi \Delta_{c}\rho_{c}}},
+    % \end{equation}
+    % where $\rho_c$ is the critical density of the universe, and $\Delta_{c}$ is the overdensity constant~\citep[see][]{BinneyTremaine2008}. 
+    % Both $\rho_c$ and $\Delta_{c}$ are functions of redshift, such that $\Rvir$ changes as a function of both the mass of the pair and redshift.
 
-Figure~\ref{fig:velocities} illustrates the magnitude of the mean relative 3D velocities between all pair types in both simulations.
-The relative velocities decrease significantly throughout time for all pairs, where massive pairs have speeds of order 100 km/s larger than dwarf pairs.
-% GB ;is the evolution with time steeper for the hydro case in the massive galaxies than in the dwarf galaxies?
+    \add{These results indicate that future observational studies that seek to compare low mass and high mass pair fractions, particularly as a function of time, must take care when determining their pair selection criteria.}
+    \add{We advocate for separation criteria that varies as both a function of mass and redshift, such as our choice of $r_{\mathrm{sep}} < 1.0\Rvir$, where $\Rvir$ can be inferred using an estimate of the combined dark matter mass of the pair.}\footnote{Taking the observed stellar mass of each pair member, the halo mass for each pair can be estimated using the SMHM relation \citep[e.g.,][]{Moster2013}.
+    The combined halo mass of the pair can then be used as a proxy for the virial mass of the FoF group ($\rm M_{vir}$) to compute the virial radius, e.g. 
+    \begin{equation}\label{eq}
+    \Rvir = \sqrt[3]{\frac{3\rm M_{vir}}{4\pi \Delta_{c}\rho_{c}}},
+    \end{equation}
+    where $\rho_c$ is the critical density of the universe, and $\Delta_{c}$ is the overdensity constant~\citep[see][]{BinneyTremaine2008}. 
+    Both $\rho_c$ and $\Delta_{c}$ are functions of redshift, such that $\Rvir$ changes as a function of both the mass of the pair and redshift.}
+    \add{We have shown that utilizing fixed physical separation cuts can lead to significant deviation in the behavior of galaxy pair fractions for different galaxy masses and between $z=0-4$, and thus it is imperative to carefully consider the selection criteria used in future observational pair fraction studies of low and high mass pairs over time.}
 
-There is a significant $\sim$15km/s ($\sim$30-50km/s) velocity offset between major dwarf (massive) pairs in \ID\ versus \IH.
-Additionally, a small ($\sim$5-10km/s) velocity separation exists between minor pairs.
-While this velocity separation is suppressed at very low redshifts for both pair types, the vast spread between velocities suggests a significant orbital/dynamic evolution between pairs in the simulations.
+    \add{In addition, our findings are specific to systems in isolated environments, and thus may not be representative of the pair fractions of a more "standard" observational field that contains pairs in isolated and high density environments.}
+    \add{Mitigating this issue in observations would require making certain isolation cuts, such as those employed in \citet{Geha2013} to identify low mass pairs in isolated ($>1.5\,\Mpc$ away from an $\rm L^{*}$ galaxy) and non-isolated (within $1.5\,\Mpc$ of an $\rm L^{*}$ galaxy) environments.}
 
-When we exclude all pairs with relative separations $<80$kpc from our analysis, the stark velocity differences between \ID\ and \IH\ are resolved, implying that the ``missing'' population of low separation halos in \IH\ is also responsible for this velocity offset.
+    Given that chance projections will artificially boost the pair fraction as the pair separation is increased, recovering the general evolution of the pair fraction as a function of redshift may be more realistic than recovering the magnitude of the pair fraction itself, since the former requires smaller separation limits.
+    The requirement of $r_{\mathrm{sep}} < 1.0\,\Rvir$ for low mass pairs translates to median separation limits that are less than $\sim 60(30)\kpc$ at $z \sim2(4)$, which are sufficiently small as to avoid major projection effects.
+    For high mass pairs, this translates to separations less than $\sim135(75)$ at $z\sim2(4)$.
 
-In the future, we will include studies of the tangential vs.
-radial velocities to provide a first order guess about the orbital trajectories of the these systems to determine if they on average are on infalling or radial orbits.
-%\kc{Could do like.... radial/tangential velocity as a funciton of separation? did I do that already?}
+    % moved this paragraph and combined with another
+    Pair fractions are typically translated to galaxy merger rates using an observability window~\citep{Lotz2011}.
+    The good agreement between the difference in the low mass and high mass pair fractions and the mass-dependent galaxy merger rates from \cite{RG2015} suggests that applying separation cuts that can recover this mass dependency are critical to reliably translating pair fractions to galaxy merger rates.
+    In fact, JWST is expected to identify low mass galaxies ($M_* > 10^8\Msun$) out to at least $z=10$~\citep{Cowley2018,Williams2018,Behroozi2020}. 
+    We argue that the adopted pair separation criteria, particularly for low mass pairs, will greatly affect the measured pair fractions and consequently the inferred merger rates.
 
-%   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %   %
+\subsection{Underlying physical behavior of galaxy pairs}\label{sec:disc-diff}
+    \add{Though we find a distinct difference in the redshift evolution of low mass and high mass pair fractions, our study does not explicitly identify the specific driver of these differences.}
+    \add{In a \lcdm\ universe, the build-up of structure proceeds hierarchically, with smaller structures merging to form larger and larger structures at later times.}
+    \add{This may explain the significant decrease in the pair fraction of isolated low mass galaxies from $z=2$ to $z=0$, since more and more low mass systems would be accreted into larger group structures and would thus be removed from our isolated pair sample.}
 
-%\kc{make velocity vs. separation plot for hydro vs dark, dwarf and massive galaxies! Major pairs? Or major AND minor? }
+    \add{On the other hand, the inherent dynamics of the pairs themselves may dictate the redshift evolution of their respective pair fractions.}
+    \add{For example, if low mass pairs tend to have very short merger timescales, the total number of low mass pairs would decrease much more rapidly than massive pairs with a very long timescale.}
 
-%%%%%%%%%%%%%%%%%
-\section{Discussion}\label{sec:discussion}
-%%%%%%%%%%%%%%%%%
-%% summary table! %%
-\begin{table*}[tb]
-  \begin{center}
-\begin{tabular}{ccccc|cccc}
-& \multicolumn{2}{c}{Dwarf} & \multicolumn{2}{c}{Massive} & \multicolumn{4}{c}{Local Group Analogs} \\\hline\hline
-    & Major Pairs & Minor Pairs & Major Pairs & Minor Pairs & MW-M31 & M31-M33 & MW-LMC& LMC-SMC\\\hline\hline
-$\rm M_{*,prim}$ & \# & \# &\# &\#&\#&\#&\#&\#\\
-\end{tabular}
-\end{center}
-\caption{\label{table:summary}\kc{Placeholder for now} Summary table with all values from z=0 (and maybe z=1,2,3,etc)}
-\end{table*}
-%%                 %%
+    Understanding in further detail the origin of the discrepancy in the redshift evolution of low mass vs.
+high mass pairs requires tracking the specific pairs across simulation snapshots to trace their orbits and study changes in the mass and environment of the pairs across cosmic time.
+    We leave this as the focus of future work.
+% end discussion
+% %%%%%%%%%%%%%%%%%%%%%%
 
-We analyzed a set of dwarf galaxy pairs and massive galaxy pairs from the \textit{Illustris-1} simulation to place constraints on the cosmologically expected fractions of major and minor pairs as a function of time.
-Our goals include identifying any differences in the behavior of pairs as a function of primary mass (dwarf or massive galaxy) and simulation physics.
-Here we use our results to place Local Group Pairs in a cosmological and temporal context (Sec.~\ref{sec:LGimplications}).
-We further discuss implications of our findings for cosmological simulations with baryonic physics (Sec.~\ref{sec:baryonImpact}).
-Finally, we briefly compare to existing literature (Sec.~\ref{sec:litcompare}).%Finally we discuss the implications of our work for future extragalactic surveys at high redshift (Section ).
-%We found that 
-%\kc{What we did. What we found. Stuff that doesn't fit into the subsections}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary and Conclusions}\label{sec:summary}
+In this paper, we construct a sample of low mass ($\rm 10^8<M_*<5\times10^9\,\Msun$) and high mass ($\rm 5\times10^9<M_*<10^{11}\,\Msun$) pairs from the TNG100 simulation from $z=0-4.2$.
+Pairs are selected as belonging to the same FoF group such that they are isolated and physically associated, and not contaminated by projection effects.
+Major and minor pairs are determined using the stellar mass ratio (1--1/4 and 1/4--1/10, respectively) between the primary and secondary halo, where stellar masses are assigned using an abundance matching prescription from~\cite{Moster2013} to generate 1000 separate realizations of selected pairs at each redshift in order to sample the error space of the SMHM relation.
 
-\subsection{Implications for Local Group Pairs}\label{sec:LGimplications}
-\citet{patel17a} showed that the existence of the MW-LMC and M31-M33 pairs, are typical of minor massive pairs at low redshift.
-However, while the M31-M33 interaction may be characteristic of minor massive pairs, they show that the MW and LMC interaction is dynamically unique, since very high velocity and low separation pairs are dynamically rare at $z=0$.
-We found that typical minor massive pairs have separations between 200-300kpc and relative velocities between 160-200kpc at low redshifts ($z<$0.5).
-Since the M31-M33 pair has a current separation of $\sim$200kpc and relative velocity $\sim$200km/s, and the MW-LMC pair has a separation of $\sim$50kpc and relative velocity of $\sim$320km/s, our results are in good agreement with \citet{patel17a}.
-However, while the MW-LMC kinematics may not be typical at low redshift, they are more characteristic of higher redshift ($z>2$) minor massive pairs, where separations are on average $<$150kpc and velocities exceed 240km/s.
+From this pair sample, we calculate the pair fraction as a function of redshift for 4 different pair types: low mass major pairs, low mass minor pairs, high mass major pairs, and high mass minor pairs.
+Our goal is to quantify the evolution of low mass and high mass galaxy pairs across cosmic time and to identify any differences in the redshift evolution of pair fractions of low mass and high mass pairs.
+\add{We also aim to determine how separation criteria for pair selection can affect the pair fraction evolution of high and low mass pairs.}
+% We also aim to determine whether the redshift evolution of the pair fraction can be well recovered from observationally selected pairs. 
+To this end, we additionally employ both static and time+mass evolving separation cuts to explore the resulting impact on the pair fractions.
 
-Since the MCs are at a separation of only $23kpc$ and have a relative velocity of $103km/s \pm26$~\cite{zivick18}, the combination of separations and velocities is non-typical, as this separation is uncommon at low redshift, while these velocities are uncommon at higher redshift.
-These kinematic differences can be potentially reconciled by the presence of the MW, and the study of the dynamics of triples will be the topic of future work.
+Our main findings are as follows:
+\begin{itemize}
+  % overall low vs high mass
+    \item The pair fraction for low mass and high mass pairs does not proceed identically throughout cosmic time.
+    In fact, the two mass scales have opposite behaviors at $z<2.5$ (see Figure~\ref{fig:pairfrac}).
+    The pair fraction of low mass pairs increases from $z=0$ to $z\sim2.5$, while the pair fraction of high mass pairs peaks at $z=0$ and is constant or slightly decreasing at $z>1$.
+  % present values
+    \item At z=0, we find a low mass major (minor) pair fraction of $0.041^{+0.003}_{-0.004}$ ($0.034\pm0.004$), and a high mass major (minor) pair fraction of $0.207^{+0.012}_{-0.014}$ ($0.152^{+0.016}_{-0.017}$).
+    These results are consistent with other simulation-based studies that find that the merger rate for high mass pairs is $\sim4\times$ higher than for low mass galaxies \citep[e.g.][]{RG2015}. 
+  % major vs. minor pairs 
+    \item Low mass minor pairs evolve similarly to low mass major pairs as a function of redshift.
+  % virial radius results
+    \item The differences in redshift evolution of pair fractions for high and low mass pairs is well recovered using a subsample of pairs with a maximum separation cut that varies with mass and redshift, specifically for $r_{\mathrm{sep}}<1\Rvir$, where $\Rvir$ is the virial radius of the FoF group
+    % (see Eq.~\ref{eq}, where the virial radius can be estimated in observations from the combined halo mass of the pair using the SHMH relation).
+    .
+    This separation cut corresponds to separations less than [134(348), 59(134), 33(76)]$\kpc$ at z=[0,2,4] for low mass (high mass) pairs.
+    In particular, a maximum separation cut of $r_{\mathrm{sep}}<1\Rvir$ encompasses between $\sim40-60\%$ of the full population of pairs at all redshifts, and recovers the distinct differences in the redshift evolution of low mass vs.
+high mass pair fractions from $z=0-2.5$.
+  % physical separation results
+    \item The identified differences in the redshift evolution of high and low mass pairs are erased when a static physical separation cut is employed; i.e.
+a separation that does not evolve with redshift or with mass (e.g.
+$r_{\mathrm{sep}}<50\kpc$).
+    This occurs because fixed separation cuts capture roughly 10-50\% more pairs in the low mass pair sample than the high mass sample at all redshifts.  
+    Consequently, selecting the same volume to study the pair fractions for low and high mass galaxies via a static separation cut will bias inferred pair fractions. 
+  % local group results
+    \item Isolated mass-analogs of the MW--M31 are most common at $z=0$, while analogs of the MW--LMC and M31--M33 are equally common at $z=0$ as at $z>1$. 
+    However, MW--LMC-type systems with very low separations ($\lesssim50\kpc$) are 2-3 times more common at higher redshift ($z\sim$2). 
+    Isolated analogs of the LMC--SMC and  NGC4490-4485 are 3 times more common for $z>3$. 
+\end{itemize}
 
-%It is thought that the LMC+SMC system fell into the MW halo recently ($<$2Gyr ago) and is currently making its first pericentric passage around the MW~\citep{besla10,bk11} (patel20).
-This means that the MC-system system spent a majority of their interaction history in a more isolated environment than the MW halo.
-However, we have no idea if the characteristics of the orbital models for the MCs are typical of dwarf pairs in isolation.
+    A number of studies have identified a mass and redshift dependence in the galaxy merger rate as a function of time, particularly in cosmological simulations and semi-empirical models~\cite[see e.g.][]{Stewart2009,Hopkins2010,RG2015}.
+    Our results show that galaxy pair fractions for physically associated, isolated pairs, likewise evolve as a function of mass and redshift. 
+    However, we also find that the recovered pair fractions are sensitive to the separation criteria that is used to define pairs.
+    The redshift evolution of pair fractions for physically associated low mass and high mass galaxy pairs can only be distinguished when the separation criteria is a function of both mass and redshift.
 
-%  120km/s  and a separation of 782kpc$\pm$25 \cite{mcconnachie05} HST proper motions and GAIA proper motions total speed ranges from -- to -- and the separation is high!
-So MW-M31 is not typical, and is true at all points in time for groups of this mass.
+    \add{Observational campaigns that seek to recover low mass and high mass pair fractions should consider using mass and redshift evolving separation criteria to select pairs.}
+    Many observational pair fraction studies use static definitions of the maximum projected separation to determine close pairs, then translate between pair fractions and merger rates via an observability timescale.
+    The observability timescale, however, is not typically calibrated as a function of both mass and redshift, meaning that identical measured pair fractions of high and low mass pairs will yield indistinguishable merger rates.
 
-While \citet{besla18} finds that 70-85\% of dwarf pairs in their sample are major pairs, we find that between 40-45\% of all pairs are major pairs, although this fraction increases at higher redshift to $\sim$60-65\%.
-The stellar mass range of our study includes stellar masses down to $10^8\msun$ while the \citet[]{besla18} study includes stellar masses down to $2\times10^8$.
-Our lower stellar mass limits and ability to ensure that pairs are associated in the same group may increase the number of dwarf minor pairs in our sample.
+    In order to observationally recover the cosmologically expected difference between the merger rates of high and low mass galaxies, it is crucial to ensure that differences in the redshift evolution of the pair fraction for these galaxy populations can be adequately captured.
+    This will be of particular importance in the era of JWST, where more low mass ($M_*\sim10^8 \Msun$) galaxies and galaxy pairs will be discovered at higher redshift (up to $z>10$), and for future wide-field galaxy surveys enabled by the Roman Space Telescope and Rubin Observatory.
+    %Thus, we argue that pair selection criteria must be a function of both mass and redshift, rather than selecting a universal, static pair separation criterion.
 
-\subsection{Impact of Mass Scales and Baryonic Physics}\label{sec:baryonImpact}
-The mass scale of our galaxy pairs heavily influences the behaviour of the pair fractions as a function of time.
-The pair fractions of dwarf major pairs are $\sim$4\% at z=0 in both simulations, however the pair fraction grows steadily and peaks at $z=2$, where the values plateau.
-This time-dependent evolution is very different from our results for massive pairs, since massive major pair fractions stay roughly constant or \textit{decrease} at higher redshift.
-This indicates that the evolution of dwarf and massive galaxy pairs proceeds very differently and on different timescales.
+% fin
+%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%
 
-We also found that the evolution of dwarf pair fractions between $z=0-4$ is dramatically different between \ID\ and \IH.
-In particular, the pair fractions in \IH\ are approximately $20-25\%$ lower than those of \ID.
-This suppression effect is not seen with massive pairs, implying that the implementation of baryonic physics in \IH\ impacts the evolution of dwarf pairs much more strongly than massive pairs.
+\section*{Acknowledgements}
+KC would like to thank Greg Snyder for fruitful early conversations during this work. 
+KC and GB are supported by NSF CAREER award AST-1941096. 
+EP acknowledges financial support provided by NASA through grant number HST-GO-16628. 
+Support for this work was also provided by NASA through the NASA Hubble Fellowship grant \# HST-HF2-51540.001-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Incorporated, under NASA contract NAS5-26555.
+Support for SP was provided by NASA through the NASA Hubble Fellowship grant \#HST-HF2-51466.001-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Incorporated, under NASA contract NAS5-26555.
+The work of S. Stierwalt is supported by the National Science Foundation Astronomy \& Astrophysics Research Grant No 1911107.
 
-\subsection{Comparison to existing work}\label{sec:litcompare}
-% Although dwarf pairs such as the Magellanic Clouds are rare at low redshift ~\citep{besla18}, many more dwarf pairs may be observable with future high redshift observations!
-We expect that at $z\sim2$, roughly 10\% of roughly LMC-mass dwarfs will have at least one major companion, and an additional 4\% will have at least one minor companion.
+The \textsc{IllustrisTNG} simulations were undertaken with compute time awarded by the Gauss Centre for Supercomputing (GCS) under GCS Large-Scale Projects GCS-ILLU and GCS-DWAR on the GCS share of the supercomputer Hazel Hen at the High Performance Computing Center Stuttgart (HLRS), as well as on the machines of the Max Planck Computing and Data Facility (MPCDF) in Garching, Germany.
 
-%GB: Discuss here general trends -- expected behavior as a function of time. and relative trends between massive vs low mass or major vs minor pairs. 
-\citet{lotz08} finds that the merger fraction of massive major galaxy pairs (M$_*>10^{10}\msun$) is approximately constant at 10$\pm$2\% between $0.2<z<1.2$, which is consistent with our findings that massive major pair fraction evolves very little (only $\pm$2\%) as a function of redshift.
-While the redshift evolution of our pairs is consistent with \citet{lotz08}, we do find higher pair fractions across this same redshift range (with pair fractions ranging between 16-20\%), which may be due to our increased sample of massive major pairs at high separation.
+The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.
 
-\citet[]{casteels14} found that the major merger fraction for galaxies with $10^{9.5}< M_* < 10^{11.5}\msun$ (roughly equivalent to our massive pair criteria) is approximately 1.3-2\% at low redshift, but increased to $4\%$ at lower masses.
-We find that massive major pairs have a pair fraction of $f_{pair}\sim18-20$\% at low redshift, which is inconsistent with the \citet{casteels14} work, but close to 4\% for dwarf galaxy major pairs, which is consistent with observations.
-However, \citet{casteels14} uses morphological signatures of mergers to calculate merger fractions.
-Since massive galaxies will only have morphological signatures from recent close passages of other massive galaxies, these methods will preferentially select close pairs compared to larger separation pairs.
-Since our study includes many low redshift, highly separated pairs, it is not unreasonable to assume that the major pair fraction difference between the two studies arises from these selection criteria.
+This work is based upon High Performance Computing (HPC) resources supported by the University of Arizona TRIF, UITS, and Research, Innovation, and Impact (RII) and maintained by the UArizona Research Technologies department.
 
-\citet{duncan19} found that the observational massive major pair fraction increases with redshift from $z=0$ (where f$_{pair}\sim0.07$) to $z=4$ (f$_{pair}\sim0.2$).
-This is in contrast to our finding that the massive major pair fraction is constant/slightly decreasing from $z=0-4$ (from f$_{pair}\sim0.2$ to f$_{pair}\sim0.14$)).
-This is likely due to the strict projected separation cuts that are made on the observational data, where massive major pairs must have $5<r_{proj}<30kpc$, while our massive major pairs includes low separation \textit{and} high separation (r$_{sep}>$30kpc) pairs.
-This accounts for our inflated pair fraction at all redshifts compared to the \citet[]{duncan19} work.
+We respectfully acknowledge the University of Arizona is on the land and territories of Indigenous peoples.
+Today, Arizona is home to 22 federally recognized tribes, with Tucson being home to the O’odham and the Yaqui.
+Committed to diversity and inclusion, the University strives to build sustainable relationships with sovereign Native Nations and Indigenous communities through education offerings, partnerships, and community service
 
-In general, our study finds inflated pair fraction results because of our ability to determine associated, but well separated, dwarf and massive galaxy pairs.
-
-% https://ui.adsabs.harvard.edu/abs/2019ApJ...872...24V/abstract
-  % v 34 36, 123 25, 19 37 km s . M31,DR2 HST
-% https://ui.adsabs.harvard.edu/abs/2020arXiv201209204S/abstract
-
-% Zivick https://iopscience.iop.org/article/10.3847/1538-4357/aad4b0/pdf
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}\label{sec:conclusions}
-In this paper we presented a study of isolated pairs of dwarf and massive subhalos in the large volume cosmological simulation \textit{Illustris-1}, using data from both the N-body (dark matter only) and full hydrodynamic simulations, \textit{Illustris-Dark} and \textit{Illustris-Hydro} respectively.
-Our criteria requires that all pairs are a part of the same FoF group (see Sec.~\ref{sec:selectionCrit}).
-We ensure isolation of our selection of pairs using a Hill Radius criteria to ensure that pairs are not gravitationally influenced by nearby massive perturbers.
-
-We define dwarf galaxies as having stellar mass $10^8\msun <M_* < 5\times10^9 \msun$, and massive galaxies as $5\times10^9<M_*<10^{11}\msun$.
-Major pairs have secondary to primary stellar mass ratios between 1-1:4, minor pairs have stellar mass ratios between 1:4-1:10, and minor+ pairs have stellar mass ratios $<$1:4, thus including the population of minor pairs.
-
-We found that there is a difference in the evolution of the pair fraction for dwarf pairs and massive pairs over time, and that baryonic physics has an impact on the expected pair fractions and kinematics of these systems.
-
-% state a main high level conclusion - are the pair fractions different between massive galaxies and dwarfs ? (which is more common, is their behavior with z the same?)  Does hydrodynamics matter?
-
-Our pair fraction results are summarized as follows:
-
-% Dwarf Pairs : 
-(i.) \textbf{The pair fractions for all dwarf primaries with a companion with stellar mass $>10^8\msun$ (All Pairs) peaks at $z=2$ and remains constant to $z=4$.} In \ID, the pair fraction is approximately $8\%$ at $z=0$ and increases to peak at 16\% at $z=2$, while in \IH, the pair fraction is $8\%$ at $z=0$, increasing to $\sim$12\% at $z=2$.
-In both simulations, the trends with redshift are determined by the major pairs, which are the most common class of dwarf galaxy pair at all redshifts.
-
-(ii.) \textbf{Magellanic Cloud mass analogs (dwarf minor pairs) are approximately 1.5x more common at $z>2$ than at the present day.} In \IH, $\sim$2-3\% of dwarf primaries (LMC analogs) host a minor companion (SMC analog) across all redshifts, with only a slight increase in the pair fraction between $z=0$ and $z=2$.
-There is slightly more evolution in the case of \ID, with $\sim$4\% of primaries hosting a minor companion for $z>2$, and declining to 2\% at $z=0$.
-Thus, we expect to find isolated minor dwarf pairs with approximately the same frequency out to $z=4$.
-
-(iii.) \textbf{Dwarf primaries are 2-2.5$\times$ more likely to have major companions at $z>2$ than at $z=0$.} We expect that roughly $\sim$4\% of dwarf primaries will have a major companion at $z=0$, increasing to $z=2$ before leveling off at 10\% (8\%) in \ID\ (\IH) for $z>2$.
-
-% comparison between dark and hydro with dwarfs
-(iv.) \textbf{The pair fraction of dwarf primaries with companions of all types (major, minor, minor+) is between $1-4\%$ less common in \IH\ than in \ID.} This indicates that the baryonic physics of the \IH simulation has a non-negligible impact on the expected pair fractions for low mass systems.
-The same suppression of pair fractions for these pair types is not seen for massive pairs.
-
-% Massive galaxies 
-(v.) \textbf{The pair fractions for all massive galaxy primaries with a companion with a stellar mass $>10^8 \msun$ increases over time and peaks between $z=0-1$.} This behaviour is primarily driven by the pair fraction of massive minor+ pairs, as the pair fractions for massive major and minor pairs is relatively flat across $z=0-4$.
-This is very different than the behaviour of low mass galaxy pairs, where the major dwarf pairs drive the evolution of pair fractions for dwarf pairs.
-
-(vi.) \textbf{$\sim$15\% of MW/M31 analogs host a LMC/M33 mass analog at all redshifts (minor pairs for massive galaxies).}  The behavior is similar in \ID and \IH.
-It is also similar to the behavior of dwarf galaxy minor pairs (LMC/SMC analogs) with time.
-% MW/LMC and M31/M33 analogs are only slightly more common at $z>1$ than at z=0.}
-
-(vii.) \textbf{The frequency of MW-M31-type pairs (major massive galaxy pairs) may be impacted by baryonic physics,} as demonstrated by differences in the time evolution of pair fractions between \ID\ and \IH.
-In the case of \ID, the pair fraction of massive major pairs is $\sim$17-18\% at $z=0$, and increases to roughly $20\%$ between $z=1-3$.
-However, in \IH, the pair fraction of massive major pairs peaks at 20\% at $z=0$, and declines steadily to $15\%$ at $z=4$.
-The evolution of major galaxy pairs is markedly different than for dwarf galaxies
-
-(viii.) \textbf{These results are/are not consistent with observations.}
-
-Our results for pairs in terms of their kinematics are as follows:
-
-(i.) \textbf{The relative separation between dwarf (massive) galaxy major pairs increases by $\sim$100kpc ($\sim$250kpc) from $z=4$ to $z=0$.} The minor pairs show similar trends with the relative separations increasing by $\sim$90kpc ($\sim$180kpc) from $z=4$ to $z=0$.
-There is a relative separation difference between major pairs in \ID\ vs.
-\IH of approximately 10-15kpc (20-40kpc), with average separations higher across all redshifts in \IH.
-At $z=0$, the average separation of dwarf minor pairs is $\sim$140-150 in both simulations.
-
-(ii.) \textbf{The relative velocities of between dwarf (massive) galaxy major pairs decreases by $\sim$30km/s ($\sim$90km/s) from $z=4$ to $z=0$.} The dwarf (massive) minor pairs show similar trends, where the average velocity decreases by $40$km/s ($100$km/s) from $z=4$ to $z=0$.
-There is a significant impact on the average velocities of pairs in this sample from baryonic physics, as there is a velocity separation between the two simulations of approximately $20$km/s (40km/s) for dwarf (massive)  major pairs, and 10km/s (20km/s) for dwarf (massive) minor pairs.
-
-(iii.) \textbf{The MCs are dynamically unique compared to the population of dwarf minor pairs at $z=0$.} Their separation is much smaller and their velocities much larger than is typical for dwarf minor pairs.
-
-(iv.) \textbf{While the M31-M33 pair is dynamically typical of massive minor pairs at low redshift, the MW-LMC pair is extremely unique both in terms of its small separation and large velocities.}
-
-(v.) \textbf{MW-M31 pair has lower relative velocities and higher separations than typical massive major pairs at low redshift.}
-
-We've shown that there is a difference in pair fractions between dwarf pairs and massive pairs.
-In addition, baryonic effects implemented in \IH\ have a non-negligible impact on the behaviour of the evolution of pair fractions and on the typical kinematics, and we'll be able to see how these discrepancies play out in the era of \textit{JWST.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section{Post prelim focus}
-% After prelim I will work on:
-% \begin{itemize}
-%   \item adding TNG results!
-%   \item completing this study for 1000 realizations of the abundance matching prescription
-% \end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliography{refs}{}
 \bibliographystyle{aasjournal}
-\bibliography{biblio2021.bib}
-
-\appendix{Hill Radius Criteria\label{app:hill}}
-The Hill radius is the distance from the center of a group, $G$, at which circular orbits of particles within $G$ will no longer be stable due to the presence of a massive perturber $P$.
-
-The Hill radius is defined as:
-\begin{equation}
-  R_{\rm Hill} = R_{\rm sep} \bigg( \frac{ M_{\rm G} }{ 3M_{\rm P} } \bigg)^{1/3},
-\end{equation}
-where $M_{\rm P}$ is the mass of the perturber, $M_{\rm G}$ is the mass of the group under consideration, and $R_{\rm sep}$ is the physical separation between the two groups ~\citep{hahn09}.
-\l
-As the Hill radius is a measure of the distance from center that particles in $G$ can sustain circular orbits, we consider the group $G$ isolated if the radius of the group is less than the Hill radius.
-The radius of the group is taken to be \texttt{Group\_R\_TopHat200} provided in the \texttt{SUBFIND} catalog, which is the radius of a sphere, centered on the group, whose mean density is $\rho_c \Delta_c$, where $\rho_c$ is the critical density of the universe and $\Delta_c$ is given by the spherical top-hat collapse model of \citet{brynorman98}.
-This ensures that the particles belonging to $G$ are gravitationally bound to $G$ and that the intrinsic dynamics of the subhalo pairs contained within are not affected by massive perturbers.
 
 \end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
